### 2021-03-23 0_archive/paper_backup.Rmd
replication files

---
title: "Vaccine Acceptability in Developing Countries"
author: 
 - Elliot Collins^[IPA]
 - Macartan Humphreys^[WZB, Columbia University]
 - Dean Karlan^[IPA and Northwestern University]
 - Rebecca Littman^[University of Illinois Chicago]
 - Niccolo Meriggi^[IGC]
 - Mushfiq Mobarak^[Yale University]
 - Saad Omer^[Yale Institute for Global Health]
 - Alexandra Scacco^[WZB]
 - Julio S. Solís Arce, WZB
 - Matthieu Teachout, IGC
 - Maarten Voors^[Wageningen University]
 - Shana Warren*
abstract: "We describe reported acceptability of Covid vaccines across x countries. For the most recent version of this paper see [here](https://www.dropbox.com/s/2baybxsji9t7q17/paper.pdf?dl=0)"  
toc: false
output: 
  bookdown::pdf_document2:
    keep_tex: true
bibliography: bib.bib
linestretch: 1.5

---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = FALSE)
```

```{r, child = "1_cleaning.Rmd", include = FALSE, eval = FALSE}

```

```{r, eval = FALSE, include = FALSE}
Summary (50 words)
Background (less than 100 words)
Methods (less than 100 words)
Findings (less than 100 words)
Interpretation (40 words)
Funding
Introduction (360 words)
```

# Introduction

A safe and effective vaccine against COVID-19 will be a critical tool to control the COVID-19 pandemic. As per late November 2020, pharmaceutical companies Pfizer, Moderna and AstraZeneca have announced that their newly developed vaccines have passed the third stage of experimentation, showing high effectiveness levels. The Pfizer vaccine has now been approved by XXX [regulatory body in the UK : Medicines and Healthcare products Regulatory Agency (MHRA), @mhra2020]. In many high income countries, vaccination campaigns are due to start in December 2020 and January 2021.

Yet decades of efforts to promote universal vaccination of [insert disease list of the most standard ones] has shown significant variation in adoption rates around the world, and some insights but rarely one clear explanation for why adoption is not universal. [summarize theories? Info? Price? Trust?]. However, COVID-19 may be different, given the publicity, perception, and worldwide attention to the pandemic.

We report on [xx] in countries of over [] individuals in order to assess intentions and perceptions of upcoming COVID-19 vaccines. This information should inform public health campaigns…..

Delivering a COVID-19 vaccine globally will undoubtedly create significant challenges both in managing the distribution (or ‘supply’) of the vaccine as well as its adoption (or ‘demand’) by population. Acceptance of the vaccine and trust in the institutions administering the vaccine are key determinants of the success of any vaccination campaign [@defigueiredo2020lancet]. While several studies have documented the willingness to take a potential COVID-19 vaccine in high income or in OECD countries [@lazarus2020nature; @boyon2020ipsos], little is known about rates of acceptance in LMICs.^[The majority of the world population resides in LMICs – put figure and reference] Willingness to adopt a COVID-19 vaccine, the reasons for refusing to take it and trust in institutions, can differ considerably across countries and across [socioeconomic?] groups within countries. Understanding these factors is a key first step in developing effective and targeted communication campaigns to enhance trust in, and acceptance of, a COVID-19 vaccine.

We use data from XXX respondents in XX original household surveys from 17 countries from Low and Middle Income Countries (LIMC) in Africa (Burkina Faso, Côte d'Ivoire, Ghana, Kenya, Mozambique, Nigeria, Rwanda, Sierra Leone, Uganda, Zambia), Asia (Bangladesh, India, Nepal, Myanmar, Pakistan(?), Philippines), and Latin America (Colombia). We document wide variation on vaccine acceptance rates, both across countries and within subgroups. In particular, XX. Main reasons for taking the vaccine are XX. We discuss potential policy responses.

@lane2018vaccine @bhopal2020vaccine @bright2017systematic

# Data and Methods

## Sample construction
We present results from XX samples from 9 countries in Sub-Saharan Africa (Burkina Faso, Ghana, Kenya, Mozambique, Nigeria, Rwanda, Sierra Leone, Uganda, Zambia), three countries in Asia (India, Nepal, Pakistan), one country in Latin America (Colombia), as well as Russia and the United States. The total population in these countries is XX.

Appendix A provides information on the timing of the spread of COVID-19 for each country in our sample. In each sample, we conducted at least one telephone survey between September - December 2020. Data thus represents phone owners, and this implies that poorer households, who may not own phones or live in areas with low connectivity, may be underrepresented.

XX of the samples (denoted XX, XX, XX, XX in Table A1) in XX countries were constructed from pre-existing studies. These samples, are randomly drawn from a population of interest for those earlier studies. The populations from which these samples are drawn varies and is elaborated in Appendix B.

XX samples (WHICH) are drawn via phone random digit dialing (RDD). These samples are thus statistically representative of the set of active mobile phone numbers held by adults.
The primary reporting unit are individual adults (associated with the phone number). Sampling weights for representativeness are described in Appendix C (?)

All survey post-COVID-19 data were conducted via telephone to minimize in-person contact and comply with government social distancing guidelines. Interviews were conducted by local enumerators in each country, 2 with procedures to match languages, dialects, and accents between respondent and enumerator.

<!-- SW: Comment: Is this true of all samples? -->

Surveying by phone made rapid and large-scale data collection possible over a large set of geographical units. Unfortunately, interviewing by telephone places limits on data collection. Surveys were designed to be short, lasting only 15–30 minutes with relatively coarse measures of income and welfare, and render anthropometric measurements infeasible.

Survey questions were coordinated across samples to the extent possible for data consistency. However, there were necessary adaptations for local context (IF ANY). We provide a detailed description of how each variable was constructed for each sample in Appendix C. Our main outcome is vaccine acceptability. Specifically, we asked “If a COVID-19 vaccine becomes available in [country], would you take it?”. We report the fraction of each sample who reported yes. To understand respondent reasons for taking a vaccine we ask “Why would you take it?” across several answer categories, including “Protect self”, “Protect community”, “Protect family”, “So that the situation can get back to normal”, “Government or health center recommended”, “Other”

To examine heterogeneity of effects across demographic strata, we further subdivide our analysis by gender, age group (18-29, 29-45, 45-60, 60+) and education levels (Less than primary, Primary, More than primary).

# Statistical Analysis (approx. 400 words)

# Results
%Assigned:

```{r, child = "2_tables.Rmd", include = TRUE}

```

# Discussion
%Assigned: Saad?

%Notes on vaccine uptake interventions in LMIC, to be used based on findings and fit -- notes from Shana
* Phone and SMS Reminders *
Reminder and recall interventions using SMS alone or in combination with phone calls or monetary incentives may be effective at encouraging timely vaccination, but studies of infant vaccination reminders demonstrate modest and inconsistent outcomes. Text reminders in urban Nigeria and Zimbabwe improved timely immunization by 8 to 16 percentage points (Bangure et al., 2015; Eze & Adeleye, 2015). Yet studies in urban Burkina Faso and semi-rural Nigeria produced mixed results (Schlumberger et al., 2015; Ekhaguere et al., 2019) and a study in rural Kenya failed to produce significant gains in immunization (Gibson et al., 2017). Though sending SMS is inexpensive, it is only one component of the intervention. If the eventual covid vaccination requires multiple doses in a tight window, successful reminder intervention will require up-to-date electronic vaccination records capable of sending auto-generated messaging to individuals within the critical time window. Many LMICs still rely on paper-based systems to track vaccinations, which are labor intensive, error-prone, and not easily integrated with a large-scale SMS messaging intervention.

* Cash and in-kind incentives *
Evidence for monetary incentives to promote child vaccination in LMICs is inconsistent. A 2017 systematic review found null results for cash transfer studies on immunization, and mixed positive results for a cash transfer combined with services strengthening (Bright et al., 2017). Oya-Ita et al., (2016) found evidence that monetary incentives have little to no effect on immunization uptake and Lagarde et al., (2007) found unclear results for conditional cash transfers. Positive results for full immunization were found in rural Kenya for a small monetary incentive (200 KES) combined with SMS (Gibson et al., 2017). Evidence from Nigeria indicates that women’s tetanus toxoid vaccination is highly responsive to cash incentives: The effect of a C800 incentive is 28.2 percentage points and the effect of a C300 incentive is 19.3 percentage points (Sato & Takasaki, 2018).

In Pakistan, food/medicine coupon incentives for immunization led to a two-fold increase in DTP up-to-date coverage (Chandir et al., 2010). Reliable immunization service availability,  with an in-kind incentive (1 kg of raw lentils per immunization and a set of metal plates upon completion of full schedule) in India led to 39 percent of children being fully immunized compared to 18 percent in reliable immunization access treatment only villages, and 6 percent in control villages (Banerjee et al., 2010).

Though there is some promising evidence, the use of incentives raise issues of dependency, sustainability and scalability. Incentives may demotivate vaccine uptake and other public health behaviors when incentives are no longer offered.

* SBCC with Community Leader Engagement*
Engaging communities through traditional and religious leaders in Nigeria had no impact on up-to-date childhood vaccination, but was effective in reducing the number of unvaccinated children and improving timeliness of later vaccines (Oya-Ita et al., 2020). A grassroots mobilization campaign that engaged traditional, religious and political leadership in Nigeria led to a relative increase of 310 percent in polio vaccination uptake and a net reduction of 29 percent in never-vaccinated children (Nasiru et al., 2012). Community engagement appears to be particularly effective in contexts where community misconceptions and distrust of vaccination are key drivers of low coverage. Nigeria is a prime example of such a context: the boycott of the polio vaccine in the early 2000s over rumors and misinformation have left pockets of distrust in the country.

* Social Signalling *
Social signalling of vaccination status may simultaneously signal receipt and shape social norms in favor of immunization. A promising study in Sierra Leone provided colored bracelet treatments to signal initiation, progress, or completion of a series of child vaccinations (Karing, 2018). All three treatments led to a significant increase in the number of vaccines received, but only the completion bracelet treament led to a significant increase in full and timely vaccination. Signalling bracelets cost approximately USD$1 per child for the full set of immunizations. Covid immunization regimes are anticipated to require only 1-2 doses and to be able to be given to multiple household members in a single visit, and should therefore be much less expensive to implement.

---
nocite: '@*'
...

\newpage 
# References

<div id="refs"></div>

\newpage

# Acknowledgements

\newpage

# Supplementary Appendix

## Overview

Overview of confirmed cases and deaths for each country – as a graph? similar to LSE blog perhaps (https://
blogs.lse.ac.uk/covid19/2020/10/20/sierra-leone-locked-down-early-to-contain-covid-but-at-a-high-price/)

<!-- SW Comment: -->
<!-- do we want to present this data? It seems that the necessity of vaccination is about far more than deaths within a country, that these stats are easily accessible, and that monitoring capacity in many countries in the sample is low enough that it's less clear how to use these numbers anyway. thoughts? Data on cases and deaths as of Dec 14, 2020 in Section B -- static only-->

# Sample Descriptions

<!-- B. Sample Descriptions for each sample – for each sample details on population, how sample was selected, sample nrs, weights, else? -->

<!-- NM: Available for Mozambique, Pakistan 1, Pakistan 2, Russia, US. All SL samples were on the Science paper. Need to follow-up on Uganda and possibly Myanmar. -->
<!-- I've put IRBs for most studies in DB. Waiting for Pakistan 1 and Pakistan 2. -->

In this Appendix section we describe each sample in the study. Table XXX reports summary statistics for each sample, with comparisons to national averages based on Living Standards Measurement Study (LSMS) surveys for random digit dialing surveys and sampling frame summary statistics where available for subpopulation surveys.

## Burkina Faso, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample

\textbf{COVID-19 Experience}
\emph{Case History:}
\begin{itemize}
 \item March 9: First confirmed case
\item Total cases: 3,894 as of December 13, 2020 (World Health Organization)
\item Total deaths: 71 as of December 13, 2020 (World Health Organization)
\end{itemize}

\noindent \textbf{Target Population}: A random sample of all adults with mobile phone numbers in the country, based on national communications authority number allocation plans.

\noindent \textbf{COVID-19 Survey Design:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share for a two-round panel survey.

\emph{Sampling Frame:} All mobile phone numbers in Burkina Faso.

\emph{Survey Dates:} Round 1 June 6 and 15, 2020; Round 2

\emph{Sample size, tracking and attrition:}  1,356 individual surveys contacted through Random Digit Dialing (RDD) from the sampling frame of all mobile phone numbers in Burkina Faso. 2,313 working numbers yielded 1,383 eligible respondents for a completion rate of 98\% of eligible respondents in the first round.

\emph{Sampling Weights:} Surveyed households are weighted by geographic unit and gender of respondent, using the inverse likelihood of being sampled based on the most recent nationally representative household survey, the 2014 Enquête Multisectorielle Continue (EMC) Survey.

\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15608, and the Burkina Faso Institutional Ethics Committee for Health Sciences Research, approval A13-2020.

## Colombia, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample

\textbf{COVID-19 Experience}

\emph{Case History:}
\begin{itemize}
 \item March 6: First confirmed case
 \item Total cases: 1,417,012 as of December 14, 2020 (World Health Organization)
\item Total deaths: 38,866 as of December 14, 2020 (World Health Organization)
\end{itemize}

\noindent \textbf{Target Population}: A random sample of all numerically possible mobile phone numbers in the country, based on national communications authority number allocation plans.

\noindent \textbf{Original Study Design:} N/A

\noindent \textbf{COVID-19 Survey Design:}

\emph{Sampling Frame:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share.

\emph{Survey Dates:} Round 1, May 8-15, 2020; Round 2 (with covid questions for this study)

\emph{Sample size, tracking and attrition:} 1,507 interviews

\emph{Sampling Weights:} Surveyed households are weighted by geographic unit and gender of respondent, using the inverse likelihood of being sampled based on the most recent nationally representative household survey, the 2016 Gran Encuesta Integrada de Hogares (GEIH) Survey.

\emph{IRB Approval:} . This research was approved via IPA IRB Protocol 15582.

## India

\noindent \textbf{Target Population}:

\noindent \textbf{Original Study Design:}

\emph{Intervention:} IF APPLICABLE

\noindent \textbf{COVID-19 Survey Design:}

\emph{Sampling Frame:}

\emph{Survey Dates:}

\emph{Sample size, tracking and attrition:}

\emph{Sampling Weights:}

\emph{IRB Approval:}

##Mozambique

\noindent \textbf{Target Population}:

\noindent \textbf{Original Study Design:}

\emph{Intervention:} IF APPLICABLE

\noindent \textbf{COVID-19 Survey Design:}

\emph{Sampling Frame:}

\emph{Survey Dates:}

\emph{Sample size, tracking and attrition:}

\emph{Sampling Weights:}

\emph{IRB Approval:}

## Nigeria

\noindent \textbf{COVID-19 Experience}
\noindent \emph{Case History:}
\begin{itemize}
\item First COVID-19 case confirmed on February 28, 2020
\item Number of confirmed cases: 73,175 as of December 14, 2020 (WHO)
\item Number of deaths: 1,197 as of December 14, 2020 (WHO)
\end{itemize}

\noindent \textbf{Target Population}:

\noindent \textbf{Original Study Design:}

\emph{Intervention:} IF APPLICABLE

\noindent \textbf{COVID-19 Survey Design:}

\emph{Sampling Frame:}

\emph{Survey Dates:}

\emph{Sample size, tracking and attrition:}

\emph{Sampling Weights:}

\emph{IRB Approval:}

## Nepal,  Western Terai Panel Survey (WTPS)

<!-- SW: full project title -->

\noindent \textbf{COVID-19 Experience}

\noindent \emph{Case History:}
\begin{itemize}
\item First COVID-19 case confirmed on January 23, 2020
\item Second case confirmed on March 23, 2020
\item Number of confirmed cases: 248,423 as of December 14, 2020 (WHO)
\item Number of deaths: 1,698 as of December 14, 2020 (WHO)
\end{itemize}

<!-- Assigned @corey.vernot@yale.edu -->

\noindent \textbf{Target Population}: Rural households in the districts of Kailali and Kanchanpur.

\noindent \textbf{Original Study Design:} Initial baseline data  was collected in-person in July of 2019, and 5 rounds of phone survey data were collected between August 12, 2019 and January 4, 2020.

\emph{Sampling Frame:} The phone survey sample includes 2,636 rural households in the districts of Kailali and Kanchanpur, which represent the set of households that responded to phone surveys from an original sample of 2,935 households. This sample was constructed by randomly sampling 33 wards from 15 of the 20 sub-districts in Kailali and Kanchanpur and selecting a random 97 villages from within those wards. At the time of baseline data collection in July of 2019, 7 of these 97 villages were dropped from the sample due to flooding. Households belong to the bottom half of the wealth distribution in these villages, as estimated by a participatory wealth ranking exercise with members of the village.

\emph{Survey Dates:}December 1st - December 11, 2020

\emph{Sample size, tracking and attrition:}  1,392 households

\emph{Sampling Weights:} Included

\emph{IRB Approval:} Yale University IRB Protocol 2000025621

\emph{Sampling Frame:} The phone survey sample includes 2,636 rural households in the districts of Kailali and Kanchanpur, which represent the set of households that responded to phone surveys from an original sample of 2,935 households. This sample was constructed by randomly sampling 33 wards from 15 of the 20 sub-districts in Kanchanpur and selecting a random 97 villages from within those wards. At the time of baseline data collection in July of 2019, 7 of these 97 villages were dropped from the sample due to flooding. Households belong to the bottom half of the wealth distribution in these villages, as estimated by a participatory wealth ranking exercise with members of the village.

\noindent \textbf{COVID-19 Survey Design:} Phone surveys

\emph{Sampling Frame:} Two phone surveys were fielded in April, 2020. The first included detailed questions on social distancing and more sparse data on other socioeconomic variables. This survey attempted to reach the universe of 1,820 households that had responded to at least one prior phone call in 48 villages, and successfully reached 1,419 households. The second survey included only sparse information on social distancing and more detailed questions on socioeconomic variables. This survey attempted to reach a random sample of 500 households across the remaining 42 villages, and successfully reached 408.

## Rwanda, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample

\noindent \textbf{COVID-19 Experience}

\emph{Case History:}
\begin{itemize}
 \item First confirmed case: March 14
 \item Total cases: 6,659 as of December 14, 2020 (World Health Organization)
\item Total deaths: 56 as of December 14, 2020 (World Health Organization)
\end{itemize}

<!-- SW to be updated -->

\noindent \textbf{Target Population}: A random sample of all numerically possible mobile phone numbers in the country, based on national communications authority number allocation plans.

\noindent \textbf{Original Study Design:} N/A

\noindent \textbf{COVID-19 Survey Design:}

 \emph{Sampling Frame:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share.

\emph{Survey Dates:} Round 1, June 4 -12, 2020;

\emph{Sample size, tracking and attrition:}

\emph{Sampling Weights:} Surveyed households are weighted by geographic unit and gender of respondent, using the inverse likelihood of being sampled based on the most recent nationally representative household survey, the 2016/17 Integrated Household Living Conditions Survey (EICV5) produced by the National Institute of Statistics Rwanda (NISR) and the Ministry of Finance and Economic Planning.

\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15591, Rwanda National Institute for Scientific Research permit No.0856/2020/10/NISR; and Rwanda National Ethics Committee approval No.16/RNEC/2020.

## Russia

<!-- Assigned: Gosha -->

\noindent \textbf{Target Population}:

\noindent \textbf{Original Study Design:}

\emph{Intervention:} IF APPLICABLE

\noindent \textbf{COVID-19 Survey Design:}

\emph{Sampling Frame:}

\emph{Survey Dates:}

\emph{Sample size, tracking and attrition:}

\emph{Sampling Weights:}

\emph{IRB Approval:}

## Sierra Leone

\noindent \textbf{COVID-19 Experience}

\noindent \emph{Case History:}
\begin{itemize}
    \item First confirmed case: March 20
    \item Total cases: 2,442 as of December 14, 2020 (WHO)
    \item Total deaths: 75 as of December 14, 2020 (WHO)
\end{itemize}

<!-- assigned: @niccolo.meriggi@theigc.org @maarten.voors@wur.nl  Could you update this section? -->

\subsubsection{Sierra Leone SLE1, Towns that are Candidates for Rural Electrification}

\noindent \textbf{Project Title:} Sierra Leone Rural Electrification (SLRE)

\noindent \textbf{Target Population}: Households in 195 rural towns across all 12 districts of Sierra Leone. Of these, 97 villages were selected to benefit from an electrification program.

\noindent \textbf{Original Study Design:}

\emph{Intervention:} The Government of Sierra Leone (GoSL) in collaboration with United Nations Office for Project Services (UNOPS) and international donors is implementing the Rural Renewable Energy Project (RREP). In its first wave, during 2017, the project provided stand-alone solar photovoltaic powered mini-grids to 54 communities across the country. Construction of mini-grids in a further 43 towns is ongoing. In selected communities, engineers construct 6kW--36kW power mini-grids that provide reliable power year-round. Electricity is free for schools and clinics. Residential and commercial users can acquire connections from commercial operators.

 \emph{Village Sampling Frame:} Household data was collected in 195 towns across all 12 districts of Sierra Leone. The GoSL selected 97 towns with (planned) mini-grids. We use Propensity Score Matching to select 98 control communities. Within communities, respondents were randomly selected from a census roster stratified by occupation status of farmers, business owners and a other occupations [47 percent, 47 percent and  7 percent]. In each village, the intended sample was 43 households (20 farmers, 20 business, 3 other). Data was collected during June--July (108 communities) and November--December 2019 (87 communities). If a household on our sampling list was not available on the village visit day, we had a randomly sampled list of replacement households to survey. The replacement household would be the same occupation as the sampled household would have been so the sample ratio of 20-20-3 still held in each community.

\noindent \textbf{COVID-19 Survey Design:}

\emph{Sampling Frame:} Phone surveys were administered in 195 rural communities.  Our total household sample comprised 7047 respondents. Of these, we recorded phone numbers of 4,594. The data was first reported in \href{www.theigc.org/wp-content/uploads/2020/05/Meriggi-et-al-Data-Brief-2020.pdf}{Meriggi et al. (2020)}.
%\cite{Meriggi2020}.

\emph{Survey Dates:} April 29, 2020 – July 7, 2020

\emph{Sample size, tracking and attrition:} The first round of data collection took place between April 29 and May 15, 2020, and covered 2,411 respondents from 193 towns, for a tracking rate of 44 percent. The second round was conducted between May 15 and June 4, 2020, and covered 1,628 respondents from 179 towns, for a tracking rate of 68 percent from the first round. The third round was conducted between June 5 and June 17, 2020 with 854 of respondents from 161 towns with a tracking rate of 35 percent. The fourth round took place on June 18 to June 30, 2020 which covered 818 respondents in 157 towns, for a tracking rate of 34 percent.

\emph{Median survey time:} 33 minutes.

\emph{Sampling Weights:} None

\emph{IRB Approval:} Sierra Leone Ethics and Scientific Review Committee (SLERC 2904202) and Wageningen University (24062020).

\subsection{Sierra Leone, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample}

\noindent \textbf{Target Population}: A random sample of all numerically possible mobile phone numbers in the country, based on national communications authority number allocation plans.

\noindent \textbf{Original Study Design:} N/A

\noindent \textbf{COVID-19 Survey Design:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share

 \emph{Sampling Frame:} All active mobile phone numbers in Sierra Leone

\emph{Survey Dates:} Round 1, May 27 to June 15, 2020; Round 2...

\emph{Sample Size, Tracking and Attrition:} 1,304 surveys

\emph{Sampling Weights:} Surveyed households are weighted by geographic unit and gender of respondent, using the inverse likelihood of being sampled based on the most recent nationally representative household survey, the 2018 Sierra Leone Integrated Household Survey (SLIHS).

\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15592, and Sierra Leone Ethics and Scientific Review Committee approval (no approval number, letter available upon request).

## Uganda

<!-- assigned: Niccolo -->

\noindent \textbf{Target Population}:

\noindent \textbf{Original Study Design:}

\emph{Intervention:} IF APPLICABLE

\noindent \textbf{COVID-19 Survey Design:}

\emph{Sampling Frame:}

\emph{Survey Dates:}

\emph{Sample size, tracking and attrition:}

\emph{Sampling Weights:}

\emph{IRB Approval:}

C. Variable Construction for each sample – for each sample the way vars where defined IF different across
samples

* this should emerge from the data collation process
* combined with sample descriptions in section B

D. Additional contributors to the research programs – RAs and related

### 2021-03-23 4_paper_supplementary_files/temp_download.Rmd
replication files

<!-- COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging -->

\newpage

# Abstract {-}

We analyze COVID-19 vaccine acceptance across 15 survey samples covering ten low- and middle-income countries (LMICs) in Asia, Africa, and South America, and two higher income countries (Russia and the United States). Standardized survey responses were collected from `r nice(nrow(df))` individuals. We find generally high willingness to take a COVID-19 vaccine in LMIC samples (80% on average), considerably higher than in the United States (65%) and Russia (30%). Vaccine acceptance was primarily explained by an interest in personal protection against the disease, while concern about side effects was the most commonly expressed reason for reluctance. Health workers were the most trusted sources of information about COVID-19 vaccines. Our findings suggest that prioritizing efficient and equitable vaccine distribution to LMICs should yield high returns in promoting global immunization. Interventions to promote vaccination in these contexts should focus on translating intentions into uptake and involve trusted health workers.

\newpage

A safe and effective vaccine against COVID-19 is a critical tool to control the pandemic. As of March 2, 2021, there were 76 vaccines in clinical development and 16 had advanced to Stage 3 clinical trials [@who1]. Following clinical trials, several vaccines have been approved in multiple countries and are being distributed across the globe. At present, global vaccine distribution remains highly unequal, with much of the current supply directed toward high-income countries [@eiu].

While effective and equitable distribution of the vaccines is a key policy priority, ensuring the population’s acceptance is equally important. Acceptance of vaccines and trust in the institutions that administer them are likely key determinants of the success of any vaccination campaign [@defigueiredo2020lancet]. Several studies investigate high-income country residents’ willingness to take a potential COVID-19 vaccine [@boyon2020ipsos; @Malik2020]. Little is known about acceptance rates in low- and middle-income countries (LMICs), however, where the majority of the world’s population resides.

Acceptance of childhood vaccination for common diseases ---such as measles (MCV), Bacille Calmette-Guérin (BCG) and diphtheria, tetanus, and pertussis (DTP)---is generally high in LMICs, providing reasons for optimism about future uptake of COVID-19 vaccines. Table \ref{tab:otherv} summarizes general vaccine acceptance and uptake of common childhood vaccines for the countries included in our study. Still, existing studies on COVID-19 vaccine acceptance document large variation, both across and within countries, including in settings where overall vaccination rates are high [@boyon2020ipsos]. These studies highlight concerns about COVID-19 vaccine safety, and particularly concerns about the speed of vaccine development, as reasons for hesitancy in higher income settings. Similar concerns may apply in LMICs.

Additional reasons for hesitancy may feature more prominently in LMIC settings. Reported COVID-19 mortality rates have consistently been lower in LMICs relative to higher income countries [@mukherjee]. If individuals in LMICs feel the risk of disease is less serious, they may be less inclined to accept perceived risks associated with taking a recently-developed vaccine. Previous studies have also highlighted factors such as concerns about healthcare quality [@christensen2020building], negative historical experiences [@Lowes2018], weak support from traditional leaders [@Jegede2007], and mistrust in government [@BLAIR201789] as barriers to healthcare utilization in LMICs.

Understanding factors that may lead people in LMICs to reject COVID-19 vaccination is of global concern, since a lag in vaccination in the developing world could facilitate the spread of new variants of the virus to other countries.

In order to effectively promote vaccination against COVID-19 and devise messaging strategies, we need to know if people are willing to take COVID-19 vaccines, the reasons why they are willing or unwilling to do so, and the factors influencing their decision-making. For this purpose, we developed and deployed a common set of questions across 15 studies in ten LMICs in Africa (Burkina Faso, Mozambique, Nigeria, Rwanda, Sierra Leone, Uganda), Asia (India, Nepal, Pakistan), and Latin America (Colombia). We compare these findings in LMICs to those from two higher income countries (Russia and the United States).

# Results {-}

Our main results are shown in Figure \@ref(fig:mainfigure1) and reproduced as Table \ref{tab:maintabledis} in [Appendix A](#appendixd). The first column provides overall acceptance rates in each study, while the remaining columns show acceptance rates disaggregated by respondent characteristics. The “All LMICs” row reports averages for LMIC countries only (and so excludes Russia and the US).

We document meaningful variation in vaccine acceptance across and within LMICs, but generally high levels of acceptance in LMICs overall. The average acceptance across studies is `r ans_mean`% (95% CI `r ans_mean_low`--`r ans_mean_high`), with a median of `r ans_median`, a range of `r ans_max - ans_min` percent points and an interquartile range of `r ans_iqr`. Our estimate of $\tau^2$ is `r  round(mp_tau, 3)` which implies a standard deviation over country averages of  `r round(mp_tau^.5, 3)`.

The acceptance rate in every LMIC sample is higher than in USA (`r usa_ans %>% pull(estimate)`%, `r usa_ans %>% pull(conf.low)`--`r usa_ans %>% pull(conf.high)`) and Russia (`r rus_ans %>% pull(estimate)`%, `r rus_ans %>% pull(conf.low)`--`r rus_ans %>% pull(conf.high)`).

We find limited evidence of variation across demographic subgroups in LMICs, as shown in Table \ref{tab:dmeans}. Women were generally less willing to accept the vaccine (average difference about `r dif_gender` points, significant at $p<.01$). Younger respondents (defined as aged <55 given younger-skewing populations in LMICs) were marginally more willing to take the vaccine, but this difference was not statistically significant. Less educated people were on average more willing to take the vaccine in LMICs, but this difference was not significant.

To better understand the reasoning behind vaccine acceptance, we asked those who were willing to take the vaccine why they would take it. We summarize in Table \ref{tab:yes}, with more details in Table \ref{tab:yesall}.

The most common reason given for vaccine acceptance was personal protection against COVID-19 infection. The average across LMICs was `r yes_all$estimate`% (`r yes_all$conf.low`--`r yes_all$conf.high`). In every individual study, it ranked as the first reason. In distant second place, LMIC respondents reported willingness to take the COVID-19 vaccine in order to protect their families. The average across LMICs was `r yes_all_2$estimate`% (`r yes_all_2$conf.low`--`r yes_all_2$conf.high`). In comparison to self-protection, protecting the community did not feature prominently among the stated reasons.

Self-protection also ranked as the most commonly expressed reason for taking the vaccine in Russia (`r yes_rus$estimate`%, `r yes_rus$conf.low`--`r yes_rus$conf.high`) and the USA (`r yes_usa$estimate`%, `r yes_usa$conf.low`--`r yes_usa$conf.high`).

This evidence contrasts with appeals to altruistic behavior and prosocial motivations in order to promote vaccine acceptance [@chou2020considering]. The risks and benefits to personal well-being feature much more prominently in people’s stated reasons for vaccine acceptance.

Figure \@ref(fig:fig2paper) summarizes the reasons given among respondents who said they were not willing to take a Covid vaccine.

The most common reason expressed for reluctance to take the vaccine in LMIC studies was  concern about side effects. For studies  `r side_top$group[1]` (`r side_top$estimate[1]`% `r side_top$conf.low[1]`--`r side_top$conf.high[1]`), `r side_top$group[2]`  (`r side_top$estimate[2]`%, `r side_top$conf.low[2]`--`r side_top$conf.high[2]`), `r side_top$group[3]` (`r side_top$estimate[3]`% `r side_top$conf.low[3]`--`r side_top$conf.high[3]`) and `r side_top$group[4]` (`r side_top$estimate[4]`% `r side_top$conf.low[4]`--`r side_top$conf.high[4]`), more than half of those respondents unwilling to take the vaccine mentioned this reason. Respondents in Russia (`r side_rus$estimate`%, `r side_rus$conf.low`--`r side_rus$conf.high`) and the USA (`r side_usa$estimate`%, `r side_usa$conf.low`--`r side_usa$conf.high`), reported high levels of this same concern.

While serious adverse events that are life-threatening or require hospitalization are very rare, with only .6\% of respondents reporting at least one side effect in the Pfizer vaccine trial [@cdcadverse], one potential explanation for the outsized concern about side effects could be the lack of widespread information about features of the vaccine at the time of data collection. Media coverage of the few cases of serious adverse events and spread of fake news may contribute as well [@stein2017golden].

Concerns about side effects could also be due to a concern about mild side effects from experiences with other vaccines. In the case of available COVID-19 vaccines, we now know that mild side effects are common but transient. These include fatigue, muscle pain, joint pain and headache, which were severe in fewer than 10\% of people in the clinical trials of tens of thousands. Severe fever occurred in fewer than 2\% of them. [@wadman2020public]

Allergic reactions from the COVID-19 vaccine seem to be extremely rare. Data from trials of the Pfizer-BioNTech vaccines shows that anaphylaxis after reported administration occurs at a rate of 11.1 cases per million vaccine doses administered [@cdcallergies].  Our data reflects this --  no more than 6% of respondents expressed concern about allergies in any of our LMIC studies.

Other concerns that make many respondents unwilling to take the vaccine could be countered by accurately presenting the scientific data to the public. Studies `r effective_top$group[1]` (`r effective_top$estimate[1]`%, `r effective_top$conf.low[1]`--`r effective_top$conf.high[1]`), `r effective_top$group[2]`  (`r effective_top$estimate[2]`%, `r effective_top$conf.low[2]`--`r effective_top$conf.high[2]`) and `r effective_top$group[3]` (`r effective_top$estimate[3]`%, `r effective_top$conf.low[3]`--`r effective_top$conf.high[3]`) showed relatively high levels of skepticism about vaccine effectiveness. This is also true for respondents in Russia (`r effective_rus$estimate`%, `r effective_rus$conf.low`--`r effective_rus$conf.high`) and the USA (`r effective_usa$estimate`%, `r effective_usa$conf.low`--`r effective_usa$conf.high`). Recent clinical trials reveal very high rates of vaccine efficacy [@baden2021efficacy; @polack2020safety], and clearly communicating these results to the public is a high priority.  In contrast, conspiracy theories were rarely mentioned by respondents in any of our study samples, in spite of widespread popular discourse about anti-vaxxer movements and theories in higher-income countries [@loomba_measuring_2021].

Finally, respondents in some studies downplayed the seriousness of this disease, and listed this as a reason not to be vaccinated. Studies `r ill_top$group[1]` (`r ill_top$estimate[1]`% `r ill_top$conf.low[1]`--`r ill_top$conf.high[1]`), `r ill_top$group[2]`  (`r ill_top$estimate[2]`%, `r ill_top$conf.low[2]`--`r ill_top$conf.high[2]`) and `r ill_top$group[3]` (`r ill_top$estimate[3]`% `r ill_top$conf.low[3]`--`r ill_top$conf.high[3]`) reported high rates of respondents citing lack of concern as a reason they were hesitant.

The analysis above identifies the nature of the information gaps that any vaccine messaging should target, while in Figure \@ref(fig:fig3paper) we try to identify the actors who are best placed to deliver those messages. We asked respondents about their most trusted source of information when deciding whether to take the vaccine, because these sources are vital to disease control strategies during public health emergencies [@siegrist2014role]. Results from Figure \@ref(fig:fig3paper) are reproduced as Table \ref{tab:trust} in [Appendix A](#appendixd).

We find striking consistency across countries. In all but one study, respondents identified the health system as the most trustworthy source to help them decide whether or not to take the COVID-19 vaccine (with the exception of Rwanda, where the government in general was identified as the most trusted source, with the health system a close second). Family and friends were the next most important reference points in most samples. Across samples, women were 3 percentage points more likely to rely on family and friends than male respondents, though this difference was not significant at conventional levels (Figure \@ref(fig:genderhist) in [Appendix D](#appendixd)). By contrast, endorsements by religious leaders or celebrity figures were not seen as important sources of influence in any sample other than Nepal.

# Discussion {.unnumbered #discussion}

To our knowledge, this is the first study documenting rates of expressed COVID-19 vaccine acceptance and hesitancy in a large set of LMICs. Our findings show variable but broadly high levels of prospective COVID-19 vaccine acceptance across LMICs using data from `r nice(nrow(filter(df, country!="USA" | country!="Russia")))` respondents in `r length(unique(df$country))-2` original household surveys from Africa (Burkina Faso, Mozambique, Nigeria, Rwanda, Sierra Leone, Uganda), Asia (Bangladesh, India, Nepal, Pakistan), and Latin America (Colombia). Acceptance across LMIC averages `r ans_mean`, ranging between  `r ans_min` and `r ans_max`. We document considerably lower levels of acceptance in Russia and the United States.

Patterns of COVID-19 vaccine hesitancy are not well predicted by existing measures of concerns about the safety of other vaccines (e.g., the Wellcome Global Monitor shown in Table \ref{tab:otherv}). Compared with other vaccines, COVID-19 vaccine acceptance is lower and more variable across LMIC samples. This suggests that concerns may apply specifically to COVID-19 vaccines rather than to vaccination more broadly.

Our study also documents reasons why respondents express intentions to take (or not take) a COVID-19 vaccine. The main reason expressed for willingness to take such a vaccine was to protect oneself. The most common reasons offered by those unwilling to take the vaccine were concerns about safety (side effects) and efficacy. Across all contexts, health care workers were the most trusted source of information  about vaccines.

Our study samples offer an important window into the motivations underlying COVID-19 vaccine acceptance in LMICs, but our data are not fully nationally representative. Random digit dial samples and follow-up phone surveys, while necessary during a global pandemic, do not include individuals who reside outside coverage areas, who do not own or cannot operate cell phones, or who choose not to respond to telephone surveys. Care should also be taken in any attempt to extrapolate to the population level from the samples representative of narrow subpopulations.

If intentions reported in our LMIC samples translated into actual vaccination uptake, the rates would far exceed the range of what would be required for COVID-19 herd immunity (40-67% in recent estimates [@britten2020; @haley2020]). However, reported intent may not materialize into actual vaccine adoption [@mceachanetal2011]. The high salience of COVID-19 due to extensive media coverage and government mitigation efforts and excitement around vaccine release may have increased reported intention [@chen1996]. Results from  the first COVID-19 vaccine Phase 3 clinical trial were announced before some surveys were fielded; during others, subsequent approvals were granted. The fast-moving information environment may change people’s perceptions about vaccines by the time they are widely available in LMICs.

Nonetheless, our findings provide some specific guidance on how to design messaging to boost COVID-19 vaccine acceptance and uptake in LMICs. Our data have implications for both what the content of the message should be, and who should deliver the message.

First, high levels of trust in the advice of health workers and governments on COVID-19 vaccine decision-making suggest that social and behavioral change communication (SBCC) strategies that engage local health workers may be particularly effective tools to encourage timely and complete vaccine uptake, and to combat remaining vaccine hesitancy. The literature has  explored messaging strategies to promote welfare-improving behaviors, with considerable attention paid to celebrity endorsements [@alatas2019celebrities]. Our data strongly support the view [@bokemper2021timing] that those with the most relevant expertise - as opposed to celebrities or general opinion leaders - are most trusted on this specific topic and are therefore best positioned to deliver the message.

Second, the average COVID-19 vaccine acceptance rate across our LMIC samples is high, approximately `r ans_mean`\%. Given such positive intentions, there may be high returns to investing in straightforward “last-mile” nudges that help citizens convert intentions into actions. Reminder messages from healthcare providers and messages alerting patients that vaccines have been reserved for them at an upcoming appointment may provide a low-cost encouragement to initiate and complete two-dose COVID-19 vaccinations, as was found in two recent large-scale studies in the United States [@milkmanetal2021a; @milkmanetal2021b]. Similarly, childhood vaccination reminders plus cash incentives in Kenya substantially increased full immunization [@gibsonetal2017], and cash and in-kind incentive programs in Nigeria and India have also proven effective [@idinsight; @Banerjee2010].

Third, high coverage rates of existing vaccines, coupled with respondents’ reliance on friends and family as information sources, suggest that the general pro-vaccination stance of many citizens could be leveraged to convert intent to uptake. Social learning strategies and norm-setting are powerful drivers of information diffusion and behavior change in many related sectors [@beaman2021can]. Social signalling of positive attitudes toward COVID-19 vaccines may also help shift social norms toward even greater immunization acceptance and two-dose completion in the community at large [@karing2018social].

Finally, our findings offer guidance on the specific content of vaccine messaging that is likely to be most persuasive. Messaging should highlight the high efficacy rates of the COVID-19 vaccines currently on the market in reducing or eliminating disease, hospitalizations and death. Alluding to clinical data that addresses people’s concerns about potential side effects should be prioritized. Messaging should also emphasize the direct protective benefits of the vaccine to the adopter.

# Methods {-}

## Survey questions and sample construction {-}

Survey data were collected between June 2020 and January 2021. Our main outcome measure is vaccine acceptance. Across studies, we asked respondents, “If a COVID-19 vaccine becomes available in [your country], would you take it?”. If the respondent answered yes to this question, we followed up with the question, “Why would you take it? [the COVID-19 vaccine]”. If the respondent said they would not be willing to take the vaccine, we followed up with the question, “Why would you not take it? [the COVID-19 vaccine]”. Finally, regardless of their expressed willingness to take the vaccine, we asked about  actors and institutions who would be influential in their decision. The question was worded in the following way: “Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available?”. To examine heterogeneity across demographic strata, we collected information about the gender, age, and education level of each respondent. Slight variations in questions wording and answer options across studies are documented in [Appendix B](#appendixb).

Studies vary in terms of geographic scope, sampling methodology, and survey modality. Seven were national or nearly-national in scope. Among these, studies from Burkina Faso, Colombia, Rwanda, and Sierra Leone ("Sierra Leone 1") used nationally-representative samples of active mobile phone numbers reached through Random Digit Dialing (RDD). Studies in the USA and Russia were conducted online using quota samples obtained from private survey companies.

The remaining eight studies targeted sub-national populations. One study from Pakistan ("Pakistan 2") used RDD to reach a representative sample of active mobile phone users in Punjab province. Respondents in Mozambique, Nigeria, "Pakistan 1", "Uganda 1","Uganda 2", India, Nepal and "Sierra Leone 2” were drawn from pre-existing studies to which COVID-19 vaccine questions were subsequently added. For example, "Sierra Leone 2” has national coverage from a study on access to electricity and “Uganda 1” sampled female caregivers of households in rural and semi-rural villages as part of a large ongoing cluster-RCT implemented across 13 districts.

Table \ref{tab:sampling} in [Appendix A](#appendixd) summarizes the geographic scope, sampling methodologies and survey modalities of all 15 studies. A detailed description of each study is included in [Appendix D](#appendixa).

All LMIC surveys were conducted via telephone to minimize in-person contact and comply with local government social distancing guidelines. Interviews were conducted by local staff in each country in local language(s). Surveying by phone made rapid, large-scale data collection possible. Surveys lasted approximately 15 to 40 minutes.

Taken together, we have data from `r nice(nrow(filter(df, country!="USA" & country!="Russia")))` individuals from LMICs and `r nice(nrow(filter(df, country=="USA" | country=="Russia")))` from the USA and Russia, for a total of `r nice(nrow(df))` respondents.

# Statistical Analysis {-}

Vaccine acceptance was defined as the percentage of respondents who answered “yes” to the question, “If a COVID-19 vaccine becomes available in [country], would you take it?”. This was calculated combining all other answer options (“No”, “Don’t Know” and “Refuse”) into a single reference category. We estimated this outcome for each study with robust standard errors and employed sampling weights where available.

In addition to study-level estimates, we combined data from all studies other than the USA and Russia to calculate an aggregate estimate for all LMIC studies. For these analyses, each included study received equal weight and standard errors were clustered at the study level. Averages in the “All LMICs” group then reflect the expected share across studies. In this combined analysis we also estimated the underlying heterogeneity of vaccine acceptance across studies using the between studies variance estimator $\tau^2$ from a random effects model.

We also conducted subgroup analyses by gender, age and education level and reported differences between groups. For the “All LMICs” analyses we calculated the average of differences between subgroups within studies with standard errors clustered at the study level.

We additionally examined reported reasons for COVID-19 vaccine acceptance and hesitancy, as well as the types of actors respondents would trust when making the decision about whether to take a COVID-19 vaccine. Among respondents who expressed willingness to take the vaccine, we asked about several possible reasons why they would take it. For respondents unwilling to take the vaccine, we asked about several possible reasons why they would not take it. Finally, we asked all respondents, regardless of their answers to other questions, whom they would trust most to help them decide whether to get a COVID-19 vaccine. We report estimates of agreement with reasons for vaccine acceptance/hesitancy and trust in actors for individual studies and for the “All LMICs” group.

\newpage

# Contributors{-}
JSo, SW, NMe, AS, NMc, GS, MV and AM are co-first authors. DK, MC, MT, MH, AMM and SO are co-last authors. AMM and SO are also the corresponding authors. 
DK, AMM, MT, NMe, MC, and MV conceived of the study and provided overall guidance.
SAb and NMe led the literature search, with input from AS, NMc, SW, AMM, AM and JSo.
SW, NMe, AS, NMc, MV, GS, AA, SA, BA, AB,EB, CMB, AC, EC, MF, AG, AK, SK, RL, MBN, MP, JSh, JSv, PV, LB, BZ, MC, SAs, AC, AF, AH, MC, MT, and MH oversaw data collection as part of other research efforts.
SW, NMe, and MT coordinated the project across study samples.
The following verified the underlying data for individual study samples: EC (Burkina Faso, Colombia, Rwanda, Sierra Leone 1), BA (India), AS and RL (Nigeria), AG and MBN (Uganda 1), CMB and MH (Uganda 2), NMe and MV (Sierra Leone 2), GS (Russia), MF (Mozambique), AF and JSh (Pakistan 1), SAs (Pakistan 2), CV (Nepal), and NMc (USA).
JSo, GS, MH and SA collated and processed all datasets used for the analysis.
NMe, MH, AMM, JSo, GS, SW, AS, EC, EB, MT, MV and NMc did the data interpretation with guidance from SO and AM.
JSo, GS, EC and MH verified final datasets and analysis.
JSo and GS did the data analysis and produced output figures with input from MH, AMM, DK, SW, EC, MV, NMe and MT.
MH supervised the data analysis.
JSo, SW, NMe, AMM, AS, NMc and MV wrote the first draft of the manuscript, with guidance from AM and SO.
JSo, SW, NMe, AS, NMc, MV, SAb, EB, MP, JSh, PV, BZ, MC, MT, MH, AMM and SO revised the manuscript.
All authors approved the final version of the manuscript. All authors had full access to all the data used in this study and had final responsibility for the decision to submit for publication.

# Data Availability Statement {-}
Individual participant data (de-identified) that underlie the results reported in this article, analytic code and replication files will be available immediately following publication to no end date for anyone who wishes to access the data and use it for any purpose in a public, open access repository. A replication exercise is available here \url{https://wzb-ipi.github.io/covid_vaccines/replication.html}.

# Funding {-}
<!-- STROBE; 22- Source of funding and the role of the funders for the present study and, if applicable, for the original study on which the present article is based  -->

Beyond Conflict, Bill and Melinda Gates Foundation, Columbia University, Givewell.org, Ghent University, HSE University Basic Research Program, International Growth Centre, Jameel Poverty Action Lab Crime and Violence Initiative, London School of Economics and Political Science, Mulago Foundation, NOVAFRICA at the Nova School of Business and Economics, NYU Abu Dhabi, Oxford Policy Management, Social Science Research Council, Trinity College Dublin COVID19 Response Funding, UK Aid, UKRI GCRF/Newton Fund, United Nations Office for Project Services, Weiss Family Fund, WZB Berlin Social Science Center, Yale Institute for Global Health, Yale Macmillan Center, and anonymous donors to IPA and Y-RISE.

# Role of the funding source {-}

None of our funders played any role in the collection, analysis, interpretation, writing or decision to submit this article for publication.

# Declaration of interests {-}
We declare no competing interests.

---
nocite: '@*'
...

\newpage
# References {-}

<div id="refs"></div>

\newpage
```{r otherv}
tab_1b
```

```{=latex}
\begin{figure}[!ht]
\caption{Acceptance rates overall and broken down by respondent characteristics \label{fig:mainfigure1}}
```
```{r mainfigure1, fig.height=7.5, fig.width = 9, warning = FALSE, dev='tikz', echo = FALSE}
fig_1
```
```{=latex}
\scriptsize{Figure 1 presents average acceptance of the COVID-19 vaccine across studies and subgroups within studies. For each study, we summarize sampling information in parentheses in the following way: First, we indicate whether the geographic coverage of the sample is national or subnational. If the coverage is subnational we provide further details. Second, we list the number of observations included in the study. In the plot, points represent the estimated percentage of individuals who would take the vaccine. ``No'', ``Don't know'' and ``Refuse'' are taken as a single reference category. Bars around each point indicate a 95\% confidence interval for the estimate. An estimate of average acceptance for all studies in LMICs (excluding USA and Russia) is also shown.}
\end{figure}
```

```{r yes, results = "asis"}
tab_reasons_y
```

```{=latex}
\begin{figure}[!ht]
\caption{Reasons not to take the vaccine \label{fig:fig2paper}}
```
```{r fig2paper, fig.height=7.5, fig.width = 10, warning = FALSE, dev='tikz', echo = FALSE}
fig_2
```
```{=latex}
\scriptsize{Figure 2 shows the percentage of respondents mentioning reasons why they would not take the COVID-19 vaccine. In the plot, points represent the estimated percentage of individuals that would not take the vaccine or do not know if they would take the vaccine for each possible response option. Bars around each point indicate a 95\% confidence interval for the estimate. An estimated average for all studies in LMICs is also shown. Size of points illustrates the number of observations in each response option. Studies India and Pakistan 2 are not included because they either did not include the question or were not properly harmonized with the other studies.}
\end{figure}
```

```{=latex}
\begin{figure}[!ht]
\caption{Trusted actors and institutions, broken down by expressed willingness to take a COVID-19 vaccine \label{fig:fig3paper}}
```

\newpage

```{r fig3paper, fig.height=9, fig.width = 10, dev='tikz', echo = FALSE}
fig_hist2
```
\newpage

```{=latex}
\scriptsize{Figure 3 shows histograms of actors and institutions respondents say they would trust most to help them decide whether to take the COVID-19 vaccine. Respondents were only permitted to select one most trusted actor or institution. Studies India, Mozambique, Pakistan 1, Pakistan 2 and Uganda 1 are not included because they either did not include the question or were not properly harmonized with the other studies.}
\end{figure}
```

\clearpage

# Supplementary Appendix {-}

## Appendix A: Supplementary tables, figures and results {.unnumbered #appendixd}

```{r sampling}
tab_sampling
```
```{r, results = "asis"}
tab_fig1
```

\newpage

```{r yesall, results = "asis"}
tab_reasons_y_all
```

\newpage

```{r no, results = "asis"}
tab_fig2
```

\newpage

```{r trust, results = "asis"}
tab_trust
```
\newpage

```{=latex}
\begin{figure}[!ht]
\caption{Trusted actors and institutions, broken down by gender \label{fig:genderhist}}
```
```{r genderhist, fig.height=9, fig.width = 10, warning = FALSE, dev='tikz'}
hist_gender
```
```{=latex}
\scriptsize{Figure 4 shows histograms of actors and institutions that respondents say they would trust most to help them decide whether or not to take the COVID-19 vaccine. Respondents were only permitted to select one most trusted  actor or institution. Responses are broken down by acceptance of the COVID-19 vaccine.}
\end{figure}
```

\pagebreak

```{r, results = "asis"}
dmeans
```

\clearpage

```{r, results = "asis"}
nas
```
________________

\pagebreak

## Appendix B: Question wording and answer options per study {.unnumbered #appendixb}

```{r tabq1}
tab_question1
```

```{r tabq2}
tab_question2
```

```{r tabq3}
tab_question3
```

```{r tabq4}
tab_question4
```
________________

## Appendix C:  Additional contributors {-}

<!-- Add here  RAs and others -->
We thank Sellu Kallon and Sarah Ryan for valuable intellectual contributions and research assistance.

IPA would like to thank staff in Burkina Faso, Colombia, Rwanda, Sierra Leone and the United States for their intellectual contributions, research assistance, and support throughout the RECOVR survey: Achille Mignondo Tchibozo, Michael Rosenbaum, Hugo Salas, Filippo Cuccaro, Jean Leodomir Habarimana Mfura, Doug Kirke-Smith, Savanna Henderson, Shahana Hirji, Kyle Holloway, Margarita Cabra.

Russia team would like to thank staff at Online Market Intelligence survey agency and Kirill Chmel and Vladimir Zabolotsky for their intellectual contributions and research assistance.

\newpage

## Appendix D: Sample descriptions {.unnumbered #appendixa}

The case history data for all countries in our sample is extracted from the Johns Hopkins University Center for Systems Science and Engineering (JHU CSSE) database.^[Dong, E., Du, H., & Gardner, L. (2020). An interactive web-based dashboard to track COVID-19 in real time. The Lancet infectious diseases, 20(5), 533-534.]

### Burkina Faso, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA){-}

\textbf{COVID-19 Experience}

\begin{itemize}
\item First confirmed case: March 9, 2020 
\item Number of confirmed cases 2,335 as of  October 15, 2020 
\item Number of deaths:  65 as of October 15, 2020
\end{itemize}

\textbf{Target Population}: A random sample of all adults with mobile phone numbers in the country, based on national communications authority number allocation plans.

\textbf{Original Study Design:} N/A

\textbf{COVID-19 Survey Design:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share for a two-round panel survey.

\emph{Sampling Frame:} All mobile phone numbers in Burkina Faso.

\emph{Survey Dates:} October 15 to December 4, 2020 (Round 1 June 6-15, 2020)

\emph{Sample size, tracking and attrition:}  Sample includes 977 respondents from the second round of a panel. In the first round conducted between June 6 to 15, 2020, 1,356 individual surveys were contacted through Random Digit Dialing (RDD) from the sampling frame of all mobile phone numbers in Burkina Faso. 2,313 working numbers yielded 1,383 eligible respondents for a completion rate of 98\% of eligible respondents.

\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.

\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15608, and the Burkina Faso Institutional Ethics Committee for Health Sciences Research, approval A13-2020.

### Colombia, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA) {-}

\textbf{COVID-19 Experience}

\begin{itemize}
\item First confirmed case: March 6, 2020
\item Number of confirmed cases:  456,689 as of August 15, 2020
\item Number of deaths:  14,810 as of August 15, 2020
\end{itemize}

\textbf{Target Population}: A random sample of all numerically possible mobile phone numbers in the country, based on national communications authority number allocation plans.

\textbf{Original Study Design:} N/A

\textbf{COVID-19 Survey Design:}

\emph{Sampling Frame:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share.

\emph{Survey Dates:} August 15-25, 2020 (Round 1 May 8-15, 2020)

\emph{Sample size, tracking and attrition:} Sample includes 1,012 respondents contacted in the second round of a panel of 1,507.

\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.

\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15582.

### India, Coping with COVID-19 in Slums: Evidence from India Subnational sample, Nova School of Business and Economics, The Institute for Fiscal Studies, University of St. Andrews {-}

\textbf{COVID-19 Experience}

\begin{itemize}
\item First confirmed case: January 30, 2020
\item Number of confirmed cases: 198,370 as of June 1, 2020 
\item Number of deaths: 5,608 as of June 1, 2020 
\end{itemize}

\textbf{Target Population}:  Random subset of slum populations in Lucknow and Kanpur, Uttar Pradesh, India. Socio-economic variables are only collected for a representative sample of the population relying on community toilets or open defecation to fulfil their sanitation needs.

\textbf{Original Study Design:} Randomized controlled trial, with complete census of households within 142 slums (September to December 2017), and a series of household and caretaker surveys, objective measurements, incentivized behavioural measurements, and a Structured Community Activity, collected for a sub-set of 100 slums between April 2018 and September 2019.

\emph{Intervention:} Catchment areas of CTs were randomly allocated to two interventions. The first intervention aimed at community toilet improvements by offering caretakers the choice of a grant to be spent for improvements in the facility. Following the grant, caretakers were offered a large financial reward conditional on the cleanliness of the facility. The second intervention added to this CT improvement awareness creation among potential users through face-to-face information sessions, leaflets, monthly reminders using voice messages sent to mobile phones, and posters hung in the CTs.

<!-- \textbf{COVID-19 Survey Design:}  -->

\emph{Sampling Frame:} A two-step sampling was applied, first, study households from the main study sample were sampled, then households from the whole slum population were added.

\emph{Survey Dates:} 
Baseline: June to July 2020, Follow-up 1: October toNovember 2020, Follow-up 2:  December 16, 2020 toJanuary 18, 2021.

\emph{Sample size, tracking and attrition:} 3,991 households, with a mean of 28 households per cluster (142). Non-response Baseline: 25%, Attrition rate Baseline to Follow-up (1 and 2): 13%, Randomly selected replacement households for Follow-up (1 and 2): 1,277.

\emph{Sampling Weights:} Included

\emph{IRB Approval:} Approval was secured from London School of Economics (REC ref. 1132). The pre-analysis plan was registered on the AEA RCT registry (RCT ID AEARCTR-0006564).

### Mozambique Subnational sample, International Growth Center, Nova School of Business and Economics {-}

\textbf{COVID-19 Experience}

\begin{itemize}
\item First confirmed case: March 22, 2020
\item Number of confirmed cases:  12,777 as of October 30, 2020 
\item Number of deaths:  91 as of October 30, 2020
\end{itemize}

\textbf{Target Population}: Microentrepreneurs in urban markets of Maputo and household heads from the province of Cabo Delgado.

\textbf{Original Study Design:} Initial data were collected in-person in two different studies. For microentrepreneurs in Maputo, the data were collected between October 2013 and April 2014 (baseline), and between July and November 2015 (endline).^[Original study: http://catiabatista.org/bsv_mm_urban.pdf] For household heads in Cabo Delgado, the data were collected in-person between August and September 2016 (baseline), and between August and September 2017 (endline).^[Original study: https://www.aeaweb.org/articles?id=10.1257/aer.20190842]

\emph{Intervention:} The first study was dedicated to analyzing the impacts of interventions targeting microentrepreneurs in urban markets on financial inclusion and literacy. The second study focused on the role of information to counteract the political resource curse after a substantial natural gas discovery.

<!-- \textbf{COVID-19 Survey Design:} -->

\emph{Sampling Frame:} The first initial sample was selected by in-field random sampling in 23 urban and periurban markets in Maputo and Matola. Stratification was based on the gender of the respondent and on the type of establishment (stall vs. store). The second initial sample was selected to be representative of 206 communities in the province of Cabo Delgado, randomly drawn from the list of all 421 polling locations in the sampling frame, stratified on urban, semiurban, and rural areas. This survey in this paper was done by phone.

\emph{Survey Dates:} October 30 to November 21, 2020 (Maputo) and  November 6 to November 30, 2020 (Pemba).

\emph{Sample size, tracking and attrition:} 554 microentrepreneurs from Maputo and 308 households from Cabo Delgado.

\emph{Sampling Weights:} N/A

\emph{IRB Approval: The approval was secured from Universidade Nova de Lisboa on July 14, 2020.

### Nepal,  Western Terai Panel Survey (WTPS) Subnational sample, Yale University, Yale Research Initiative on Innovation and Scale (Y-RISE){-}

\textbf{COVID-19 Experience}

\begin{itemize}
\item First confirmed case: January 23, 2020

\item Number of confirmed cases:  233,452 as of December 1, 2020 
\item Number of deaths:   1,529 as of December 1, 2020
\end{itemize}

\textbf{Target Population}: Rural households in the districts of Kailali and Kanchanpur.

\textbf{Original Study Design:} Initial baseline data was collected in-person in July of 2019, and 5 rounds of phone survey data were collected between August 12, 2019 and January 4, 2020.

\emph{Sampling Frame:} The phone survey sample includes 2,636 rural households in the districts of Kailali and Kanchanpur, which represent the set of households that responded to phone surveys from an original sample of 2,935 households. This sample was constructed by randomly sampling 33 wards from 15 of the 20 sub-districts in Kailali and Kanchanpur and selecting a random 97 villages from within those wards. At the time of baseline data collection in July of 2019, 7 of these 97 villages were dropped from the sample due to flooding. Households belong to the bottom half of the wealth distribution in these villages, as estimated by a participatory wealth ranking exercise with members of the village.

\emph{Survey Dates:}December 1st - December 11, 2020

\emph{Sample size, tracking and attrition:}  1,392 households

<!--  \emph{Sampling Weights:} Included -->

\emph{IRB Approval:} This research was approved via Yale University IRB Protocol 2000025621.

### Nigeria Subnational sample, WZB Berlin Social Science Center, University of Illinois Chicago{-}

\textbf{COVID-19 Experience}

\begin{itemize}
\item First confirmed case: February 28, 2020
\item Number of confirmed cases: 65,693 as of November 18, 2020 
\item Number of deaths:  1,163 as of November 18, 2020 
\end{itemize}

\textbf{Target Population}: Christian and Muslim men and women, age 18 and above, living in Kaduna state, Nigeria.

\textbf{Original Study Design}:  Initial data was collected from a subset of the sample in December 2019 (in person survey) and July - Aug 2020 (phone survey) as part of an experiment testing the effects of a brief radio program on inter-religious animus. A random walk procedure and random sampling were used within households to recruit a representative sample of adults in Kaduna town. The rest of the sample was recruited for the study in Aug 2020 by purchasing phone lists for residents of Kaduna State.

\emph{Intervention:} The study examines the effects of a radio program and a TV drama on  inter-religious animus. The subset of  the sample in the radio study was randomly assigned to listen to a brief radio program on one of the following topics: (1) an inter-religious storyline, (2) an intra-religious storyline, and (3) a message about maintaining safe health practices. All respondents in the sample participated in a study examining the effect of viewing an inter-religious storyline unfolding over a full season of a popular TV drama, Dadin Kowa. The season aired from Aug - Oct 2020. A third of the sample were encouraged to watch Dadin Kowa, a third were encouraged to watch the TV station Africa Magic Hausa at the same time Dadin Kowa aired, and a third were in the treatment-as-usual group. All participants received a weekly incentivized SMS quiz from Aug - Oct 2020.

\textbf{COVID-19 Survey Design:} This survey is not primarily about COVID-19, but was designed as an endline survey to follow the TV drama intervention described above. The goal of this survey is to measure a range of attitudinal outcomes related to Christian-Muslim relations (including prejudice, intergroup threat perceptions, dehumanization, and support for the use of violence, among others). We included nine of the standardized COVID-19 vaccine-related questions collected specifically for this vaccine acceptance study in the final module of the endline survey.

\emph{Sampling Frame:} 950 respondents in the sample were recruited in person through a random sampling procedure in the Kaduna metropolitan area (pre-COVID). The remaining 1,700 respondents were recruited into the study over the phone from lists of phone numbers of Kaduna state residents that were purchased from a private vendor.

\emph{Survey Dates:} November 18 - December 18, 2020.

\emph{Sample size, tracking and attrition:} All 1,834 individuals who completed the endline survey are included.

\emph{Sampling Weights:} N/A

\emph{IRB Approval:} This study was reviewed by the IRB at the University of Pennsylvania (Protocol 834548), and it was determined on November 20, 2019 to meet the criteria for review exemption (45 CFR 46.104, category \#2).

### Pakistan {-}

\textbf{COVID-19 Experience}

\begin{itemize}
\item March 6: First confirmed case: February  26, 2020 
\item Number of confirmed cases:  271,887 as of July 24, 2020 
\item Number of deaths:  5,787 as of July 24, 2020 
\end{itemize}

### Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample, Sheikhupura Police Study Sample, Institute of Development and Economic Alternatives, Lahore University of Management Science, London School of Economics, Princeton University {-}

\textbf{Target Population}: A representative sample of adults from 108 of 151 police beats in Sheikhupura and Nankana districts of Punjab Province.

\textbf{Original Study Design:} N/A

\textbf{COVID-19 Survey Design:} The EVA survey involved calls to all households in the stratified random sample for the policing study midline survey.

\emph{Sampling Frame:} Households in Sheikhupura and Nankana districts.

\emph{Survey Dates:} July 24 to September 9, 2020

\emph{Sample size, tracking and attrition:}  Sample includes 1,473 respondents.

\emph{Sampling Weights:} Post-stratification weights are computed to adjust for the sampling process, which involved stratifying first on 27 police stations, then within each police station on beats, then PPS sampling within beats using Asiapop population data.

\emph{IRB Approval:} This research was approved via Princeton University IRB Protocol 7250.

### Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample {-}

\textbf{Target Population}: All possible mobile phone numbers (in the province of Punjab) generated based on the local mobile phone number structure in Pakistan.

\textbf{Original Study Design:} N/A

\textbf{COVID-19 Survey Design:} The EVA survey involved making calls to individuals in Punjab based on random digit dialing.

\emph{Sampling Frame:} Individuals with mobile phones in Punjab.

\emph{Survey Dates:}  September 2 to October 13, 2020

\emph{Sample size, tracking and attrition:}  Sample includes 1,492 respondents.

\emph{Sampling Weights:} N/A.

\emph{IRB Approval:} This research was approved by Lahore University of Management Sciences IRB Protocol LUMS-IRB/07012020SA.

### Rwanda, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA){-}

\textbf{COVID-19 Experience}

\begin{itemize}
 \item First confirmed case: March 14, 2020
 \item Total cases:  5,017 as of October 22, 2020 
\item Total deaths:  34 as of October 22, 2020 
\end{itemize}

\textbf{Target Population}: A random sample of all numerically possible mobile phone numbers in the country, based on national communications authority number allocation plans.

\textbf{Original Study Design:} N/A

\textbf{COVID-19 Survey Design:}Phone survey

 \emph{Sampling Frame:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share.

\emph{Survey Dates:} October 22 to November 5, 2020 (Round 1 June 4 -12, 2020)

\emph{Sample size, tracking and attrition:}Sample includes 1,355 respondents contacted in the second round of a panel of 1,480.

\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.

\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15591, Rwanda National Institute for Scientific Research permit No.0856/2020/10/NISR; and Rwanda National Ethics Committee approval No.16/RNEC/2020.

### Russian Federation, Research on COVID-19 in Russia’s Regions (RoCiRR) Subnational  sample, International Center for the Study of Institutions and Development (HSE University, Moscow, Russia) and Economics Department of Ghent University, WZB Berlin Social Science Center, Columbia University{-}

\textbf{COVID-19 Experience}
\begin{itemize}
\item First confirmed case: January 31, 2020
\item Number of confirmed cases: 1,720,063 as of November 6, 2020 
\item Number of deaths:  29,654 as of November 6, 2020 
\end{itemize}

\textbf{Target Population}: Adult internet users who reside in one of 61 federal subjects (federal cities, oblasts, republics, krais and autonomous okrug) of Russia. The regions included in the study are Republics: \emph{Bashkortostan, Karelia, Komi, Mariy El, Mordovia, Tatarstan, Udmurtia, Chuvashia}. Krais: \emph{Altai, Krasnodarsky, Krasnoyarsky, Permsky, Primorsky, Stavropolsky, Khabarovsky}. Oblasts: \emph{Arkhangelsk, Astrakhan, Belgorod, Bryansk, Vladimir, Volgograd, Vologda, Voronezh, Ivanovo, Irkutsk, Kaliningrad, Kaluga, Kemerovo, Kirov, Kostroma, Kurgan, Kursk, Leningrad, Lipetsk, Moscow, Murmansk, Nizhny Novgorod, Novgorod, Novosibirsk, Omsk, Orenburg, Orel, Pskov, Penza, Rostov, Ryazan, Samara, Saratov, Sverdlovsk, Smolensk, Tambov, Tver, Tomsk, Tula, Tyumen, Ulyanovsk, Chelyabinsk, Yaroslavl}. Other: \emph{Moscow, Saint Petersburg, Khanty-Mansiysk Autonomous Okrug -- Ugra}. The remaining 24 federal subjects were excluded from the study due to inability to enroll sample size with desired characteristics (sample size, age, gender and education group composition).

\textbf{Original Study Design:} N/A

\textbf{COVID-19 Survey Design:} The study was designed to measure the impact of pandemics on Russians, mostly those who live in cities with more than 100,000 residents. It contains a number of questions on the personal experience, norms and values, trust in government institutions, provision of social services, and mass media use. Region and geolocality of every respondent are recorded.

\emph{Sampling Frame:} In total 25,558 respondents received the module on vaccine acceptance. The sample was enrolled from the pool of Russian online survey company OMI (Online Market Intelligence). The sampling was specifically targeted at having a minimum of 150 respondents in each of the 61 regions and including respondents from all the main age and gender groups within each region. Respondents were also selected so that at least 40% of respondents did not have higher education, in accordance with higher education rates in Russia. Out of 25,558 recruited respondents, 22,125 completed the survey. Among 22,125 respondents who completed the survey, 20,821 were enrolled from the general pull of the survey company respondents, while the remaining 1,304 respondents were enrolled among residents of cities with populations below 100,000 and rural areas.

\emph{Survey Dates:} November 6 - December 1, 2020

\emph{Sample size, tracking and attrition:} 22,125 respondents who completed the survey with the vaccine acceptance module included.

\emph{Sampling Weights:} Post-stratification weights are computed to match marginal population distributions of age, gender and education with target proportions coming from the 2019 Yearbook and 2015 Microcensus released by Russian Federal Bureau of National Statistics (Rosstat).

\emph{IRB Approval:} This study was approved via Columbia University IRB Protocol IRB-AAAT4453.

### Sierra Leone {-}

\textbf{COVID-19 Experience}

\begin{itemize}
        \item First confirmed case: March 20, 2020
        \item Total cases:  2,252 as of October 2, 2020 and 3,030 as of January 20, 2021 
        \item Total deaths:  72 as of October 2, 2020 and 77 as of January 20, 2021 
\end{itemize}

#### Sierra Leone, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA) {-}

\textbf{Target Population}: A random sample of all numerically possible mobile phone numbers in the country, based on national communications authority number allocation plans.

\textbf{Original Study Design:} N/A

\textbf{COVID-19 Survey Design:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share

 \emph{Sampling Frame:} All active mobile phone numbers in Sierra Leone.

\emph{Survey Dates:} October 2-19, 2020 (Round 1 May 27 to June 15, 2020)

\emph{Sample Size, tracking and Attrition:} Sample includes 1,070 respondents contacted in the second round of a panel of 1,304.

\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.

\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15592, and Sierra Leone Ethics and Scientific Review Committee approval (no approval number, letter available upon request).

#### Sierra Leone, Towns that are Candidates for Rural Electrification Nation-wide sample, International Growth Centre (IGC), Wageningen University & Research, Yale Research Initiative on Innovation and Scale (Y-RISE), WZB Berlin Social Science Center and Columbia University {-}

\textbf{Project Title:} Sierra Leone Rural Electrification (SLRE)

\textbf{Target Population}: Households in 195 rural towns across all 14 districts of Sierra Leone. Of these, 97 villages were selected to benefit from an electrification program.

\textbf{Original Study Design:} Initial baseline data was collected during late 2019 and early 2020 as part of a study to assess the impact of Rural Electrification in rural towns in Sierra Leone.

\emph{Intervention:} The Government of Sierra Leone (GoSL) in collaboration with the United Nations Office for Project Services (UNOPS) and international donors is implementing the Rural Renewable Energy Project (RREP). In its first wave, during 2017, the project provided stand-alone solar photovoltaic powered mini-grids to 54 communities across the country. Construction of mini-grids in a further 43 towns is ongoing. In RREP communities, engineers construct 6kW--36kW power mini-grids that provide reliable power year-round. Electricity is free for schools and clinics. Residential and commercial users can acquire connections from commercial operators.

 \emph{Village Sampling Frame:} Household data was collected in 195 towns across all 12 districts of Sierra Leone. The GoSL selected 97 towns with (planned) mini-grids. We used Propensity Score Matching to select 98 control communities. Within communities, respondents were randomly selected from a census roster stratified by occupation status of farmers, business owners and other occupations [47 percent, 47 percent and  7 percent]. In each village, the intended sample was 43 households (20 farmers, 20 businesses, 3 others). Data was collected during June--July (108 communities) and November--December 2019 (87 communities). If a household on the sampling list was not available on the village visit day, we had a randomly sampled list of replacement households to survey. The replacement household would be the same occupation as the sampled household would have been so the sample ratio of 20-20-3 still held in each community.

\textbf{COVID-19 Survey Design:}  The goal was to assess households’ degree of economic vulnerability in the face of the COVID-19 pandemic.

\emph{Sampling Frame:} The COVID-19 survey data comprises 2,110 respondents from 186 towns from the original baseline survey.  Phone surveys were attempted to all 195 rural communities from the baseline survey.  The total baseline household sample comprised 7047 respondents. We recontacted all baseline respondents that listed a phone number (4,594 respondents) and obtained informed consent for the phone survey. We implemented several waves of the phone survey, recontracting a respondent about every month. In wave 7, we added questions related to Vaccine Acceptability.^[The data was first reported in https://www.theigc.org/wp-content/uploads/2020/05/Meriggi-et-al-Data-Brief-2020.pdf].

\emph{Survey Dates:} October 7, 2020 and January 20, 2021 (earlier rounds included Wave 1: April 29-May 15; Wave 2: May 15-June 4; Wave 3: June 5-June 17; Wave 4: June 17-June 30; Wave 5: July 1-August 8; Wave 6: August 19-October 1). The median survey time was 33 minutes.

\emph{Sample size, tracking and attrition:} Data collection took place between October 7 and January 20, 2021with 2,110 respondents, in 186 towns for a tracking rate of 46 percent.

\emph{Sampling Weights:} None

\emph{IRB Approval:} Approval was secured from Sierra Leone Ethics and Scientific Review Committee (SLERC 2904202) and Wageningen University (24062020).

### Uganda {-}

\textbf{COVID-19 Experience}

\begin{itemize}
        \item First confirmed case: March 21, 2020
        \item Total cases:  741 as of June 18, 2020 and 6,468 as of September 21, 2020         \item Total deaths:  0 as of June 18, 2020 and 63 as of September 21, 2020 
\end{itemize}

#### Uganda Subnational sample, International Growth Center, Trinity College Dublin, Stockholm School of Economics and Misum, Institute for International Economic Studies, Stockholm University  {-}

\textbf{Target Population}: Women from semi-rural and rural villages across 13 districts in Uganda (Iganga, Kayunga, Mbale, Mityana, Apac, Dokolo, Gulu, Adjumani, Koboko, Maracha, Nebbi, Soroti, Kumi).

\textbf{Original Study Design:} Initial baseline data was collected in 2016 as part of a large cluster randomized controlled trial, with the aim of selecting households likely to have children during the study period. Four criterias for selection were thus used, in descending order of importance: the household has a woman that is currently pregnant, or aged 16-30 years old,  with a young child less than three years old, and/or married (formally or informally). In each household, the respondent was chosen as the female household head or the primary female health care giver of the household if the household head could not be found.

<!-- \emph{Intervention:} IF APPLICABLE -->

\textbf{COVID-19 Survey Design:} The data was collected through multiple rounds of phone surveys. The variable measuring age was constructed by approximation, using the baseline data from 2016 and adding 4 years to the 2016 measure. When the baseline respondent was replaced, the initial age information was deleted.

\emph{Sampling Frame:} Households were selected within 500 clusters (the village of the household).

\emph{Survey Dates:} September 21 to December 06, 2020.

\emph{Sample size, tracking and attrition:} Out of 2,743 respondents,  1752 were included, provided that they answered the main question about vaccine uptake.

\emph{Sampling Weights:} None.

<!-- \emph{IRB Approval:} X -->

### Uganda Subnational sample, WZB Berlin Social Science Center and Columbia University, NYU Abu Dhabi, Innovations for Poverty Action (IPA)  {-}

\textbf{Target Population:} All residents of Kampala who are Ugandan citizens, above the age of 18, and agree in principle to attend a short citizen consultative meeting.

\textbf{Original Study Design:} Baseline data was collected between July and October 2019 for an intervention that randomized citizen attendance to a set of 188 consultative meetings organized across Kampala. The meetings were organized to collect citizen preferences for the design of a forthcoming municipal citizen charter. The study also aimed to assess patterns of political inequality in meeting participation, dynamics, and outcomes, as well as study the subsequent effects on prosociality of being incorporated in this participatory process. 1/3 of the sample was randomly allocated to control, while 2/3 of respondents were invited to attend a consultative meeting. The consultations took place between November 2019 and February 2020 across Kampala divisions.

\emph{Intervention:} The intervention consisted of attendance at the consultative meeting organized a few months after baseline data collection. A further randomization allocated ½ of the invited participants to a meeting moderated by a local bureaucrat, while the remaining ones attended a meeting moderated by a neutral discussion leader.

\textbf{COVID-19 Survey Design:} The COVID-19 survey sample comprises the 2,189 respondents to the baseline who were selected on the basis of their residence in the city. Having received permission to re-contact these individuals, we coordinated a 3-wave panel throughout the summer and fall of 2020, with respondents contacted via phone. The goal was to assess households’ degree of economic vulnerability in the face of the COVID-19 pandemic and respondents’ evaluations of performance of political actors in tackling the pandemic.

\emph{Sampling Frame:} The 2,189 respondents to the baseline were randomly selected from a sampling frame of all buildings in Kampala, for which information about their geographical coordinates was available. After randomly selecting a set of candidate structures, interviewers sampled respondents from the subset of structures that were residential.

\emph{Survey Dates:} Wave 1: June 18--July 23. Wave 2: September 4--29. Wave 3: November 23--December 12.

\emph{Sample size, tracking and attrition:} Of the 2,189 respondents which we aimed to contact, we were able to reach 1,333 in Wave 1, 1,289 in Wave 2, and 1,366 in Wave 3. Wave 3 contained the COVID-19 vaccine module presented in this analysis.

\emph{Sampling Weights:} None.

\emph{IRB Approval:} The study was approved by IPA Global IRB (protocol number 15018) on May 29, 2020; WZB Berlin Social Science Center Ethics Review Board (protocol number 2020/0/91) on June 10, 2020;  NYU Abu Dhabi IRB (protocol number HRPP-2020-64) on May 27, 2020; MIT Committee on the Use of Humans as Experimental Subjects (protocol number 2005000155) on June 3, 2020; and by the Mildmay Uganda Research Ethics Committee (protocol number 0604-2019) on June 11, 2020.

### United States of America Nation-wide sample, WZB Berlin Social Science Center, Cornell University, Tufts University {-}

\textbf{COVID-19 Experience}

\begin{itemize}
        \item First confirmed case: January 20, 2020
        \item Total cases:  14,499,637 as of December 4, 2020 
        \item Total deaths:  281,678 as of December 4, 2020 
\end{itemize}

\textbf{Target Population}: Nation-wide sample of adult internet users recruited through the market research firm Lucid.

\textbf{Original Study Design:} N/A

\emph{Intervention:} N/A

\textbf{COVID-19 Survey Design:}This survey was part of a panel study on attitudes toward COVID-19 technologies and public health surveillance.

\emph{Sampling Frame:} The Lucid Marketplace is an automated marketplace that connects researchers with willing online research participants. Lucid partners with a network of companies that maintain relationships with research participants by engaging them with research opportunities. While Lucid does not provide probability samples of the U.S. adult population, its quota samples approximate the marginal distributions of key demographic characteristics. Recent validation exercises have found that Lucid samples approximate nationally representative samples in terms of demographic characteristics and survey experiment effects.^[See for instance: https://journals.sagepub.com/doi/10.1177/2053168018822174]

\emph{Survey Dates:} December 4-5, 2020

\emph{Sample size, tracking and attrition:} 1,959 individual online surveys. In the main question regarding intention to take the vaccine, approximately 10% of respondents (184) did not answer 
\emph{Sampling Weights:}  Post-stratification weights are computed to match marginal population distributions of income, age, education, gender, race and region among the US adult population, with target proportions based on the 2018 American Community Survey.

\emph{IRB Approval:} This study received approval from the Cornell University IRB under Protocol #2004009569.

________________

\newpage
<!--

## Population description

In this Appendix section we describe each sample in the study. Table XXX reports summary statistics for each sample.
When possible, samples are compared to national averages based on Living Standards Measurement Study (LSMS) surveys for random digit dialing surveys and sampling frame summary statistics where available for subpopulation surveys.

<!-- 
```{r reptabcol}
tab_sum_col
```
```{r reptabrow}
tab_sum_row
```
-->

### 2021-03-23 paper.Rmd
replication files

---
title: "COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging"
author:
- name: Julio S. Solís Arce, BA^[First author]
  affiliation: WZB Berlin Social Science Center
  number: 1
- name: Shana S. Warren, PhD\(^*\)
  affiliation: Innovations for Poverty Action (IPA)
  number: 2
- name: Niccoló F. Meriggi, MSc\(^*\)
  affiliation: International Growth Centre (IGC)
  number: 3
- name: Alexandra Scacco, PhD\(^*\)
  number: 1
- name: Nina McMurry, PhD\(^*\)
  number: 1
- name: Maarten Voors, PhD\(^*\)
  affiliation: Wageningen University & Research
  number: 4
- name: Georgiy Syunyaev, MPhil\(^*\)
  affiliation: International Center for the Study of Institutions and Development (HSE University, Moscow, Russia)
  number: [1, ", ", 5, ", ",  24]
- name: Amyn Abdul Malik, PhD\(^*\)
  affiliation: Yale Institute for Global Health
  number: 6
- name: Samya Aboutajdine, MA
  number: 3
- name: Alex Armand, PhD
  affiliation: Nova School of Business and Economics
  number: 7
- name: Saher Asad, PhD
  affiliation: Lahore University of Management Sciences
  number: 8
- name: Britta Augsburg, PhD
  affiliation: The Institute for Fiscal Studies
  number: 9
- name: Antonella Bancalari, PhD
  affiliation: University of St. Andrews & The Institute for Fiscal Studies
  number: 10
- name: Martina Björkman Nyqvist, PhD
  affiliation: Stockholm School of Economics and Misum
  number: 11
- name: Ekaterina Borisova, PhD
  affiliation: Economics Department of Ghent University
  number: [5, ", ", 12]
- name: Constantin Manuel Bosancianu, PhD
  number: 1
- name: Ali Cheema, PhD
  affiliation: Institute of Development and Economic Alternatives
  number: [8, ", ", 13]
- name: Elliott Collins, PhD
  number: 2
- name: Ahsan Zia Farooqi, MA
  number: 13
- name: Mattia Fracchia, MA
  number: 7
- name: Andrea Guariso, PhD
  affiliation: Trinity College Dublin
  number: 14
- name: Ali Hasanain, PhD
  number: 8
- name: Anthony Kamwesigye, BSc
  number: 2
- name: Sarah Kreps, PhD
  affiliation: Cornell University
  number: 15
- name: Madison Levine, MSc
  number: 4 
- name: Rebecca Littman, PhD
  affiliation: University of Illinois Chicago
  number: 16
- name: Melina Platas, PhD
  affiliation: NYU Abu Dhabi
  number: 17
- name: Vasudha Ramakrishna, MSc
  affiliation: Yale Research Initiative on Innovation and Scale (Y-RISE)
  number: 18
- name: Jacob N. Shapiro, PhD
  affiliation: Princeton University
  number: 19
- name: Jakob Svensson, PhD
  affiliation: Institute for International Economic Studies (IIES), Stockholm University
  number: 20
- name: Corey Vernot, BS
  number: 18
- name: Pedro C. Vicente, PhD
  number: 7
- name: Laurin B Weissinger, DPhil
  affiliation: Tufts University
  number: 21
- name: Baobao Zhang, PhD
  number: 15
- name: Dean Karlan, PhD^[Last author]
  affiliation: Kellogg School of Management at Northwestern University
  number: [2, ", ", 22]
- name: Michael Callen, PhD\(^\dagger\)
  affiliation: London School of Economics
  number: [3, ", ", 23]
- name: Matthieu Teachout, PhD\(^\dagger\)
  number: 3
- name: Macartan Humphreys, PhD\(^\dagger\)
  affiliation: Columbia University
  number: [1, ", ", 24]
- name: Saad B. Omer, PhD^[Corresponding author. 1 Church Street, New Haven, CT 06510. Phone  203 432 3656.  Email  \href{mailto:saad.omer@yale.edu}{saad.omer@yale.edu}]
  number: 6
- name: Ahmed Mushfiq Mobarak, PhD^[Corresponding author. 165 Whitney Avenue, New Haven, CT 06520-8200. Phone 203 432 5787. Email  \href{mailto:ahmed.mobarak@yale.edu}{ahmed.mobarak@yale.edu}]
  affiliation: Yale University
  number: 25
output: 
  bookdown::pdf_document2:
    keep_tex: true
    pandoc_args:
      - --template=4_paper_supplementary_files/mytemplate.latex
    toc: false
    extra_dependencies:
      caption: ["font={bf,normalsize}"]
      mathptmx: null
      fontenc: ["T1"]
  bookdown::word_document2: default
bibliography: 4_paper_supplementary_files/bib_final.bib
csl: 4_paper_supplementary_files/nature.csl
header-includes:
  - \usepackage{titlesec}
  - \titleformat*{\subsection}{\normalsize\bfseries}
  - \titleformat*{\section}{\large\bfseries}
# linestretch: 1.5
urlcolor: blue
link-citations: yes
linkcolor: blue
fontsize: 12pt
---

```{r setup, include=FALSE}

library(knitr)

knitr::opts_chunk$set(echo = FALSE)

```

```{r cleaning, child = "1_cleaning.Rmd", include = FALSE, eval = FALSE}

```

```{r tables, include = FALSE, message = FALSE}

knitr::purl("2_tables.Rmd", documentation = 2)

source("2_tables.R")

file.remove("2_tables.R")

nice <- function(x) prettyNum(x, big.mark = ",", scientific = FALSE)

```

```{r load_gdoc, include = FALSE, eval = TRUE}

googledrive::drive_download(file = "NatureMedicine Covid vaccine hesitancy", 
                            path = "4_paper_supplementary_files/Intro Vaccine.txt", overwrite = TRUE)

file.rename(from = "4_paper_supplementary_files/Intro Vaccine.txt", 
            to = "4_paper_supplementary_files/temp_download.Rmd")

knitr::opts_chunk$set(echo = FALSE)

```

```{r main_text, child = "4_paper_supplementary_files/temp_download.Rmd"}

```

### 2021-03-23 paper.tex
replication files

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={blue},
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{titlesec}
\titleformat*{\subsection}{\normalsize\bfseries}
\titleformat*{\section}{\large\bfseries}
\usepackage[font={bf,normalsize}]{caption}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging}
    \usepackage{authblk}
    \renewcommand\Authfont{\fontsize{10}{14.4}\selectfont}
    \renewcommand\Affilfont{\fontsize{8.5}{10.8}\itshape}
                                        \author[1]{Julio S. Solís Arce, BA\footnote{First author}}
                                                            \affil{WZB Berlin Social Science Center}
                                                                                \author[2]{Shana S. Warren, PhD\(^*\)}
                                                            \affil{Innovations for Poverty Action (IPA)}
                                                                                \author[3]{Niccoló F. Meriggi, MSc\(^*\)}
                                                            \affil{International Growth Centre (IGC)}
                                                                                \author[1]{Alexandra Scacco, PhD\(^*\)}
                                                                            \author[1]{Nina McMurry, PhD\(^*\)}
                                                                            \author[4]{Maarten Voors, PhD\(^*\)}
                                                            \affil{Wageningen University \& Research}
                                                                                \author[1,5,24]{Georgiy Syunyaev, MPhil\(^*\)}
                                                            \affil{International Center for the Study of Institutions and Development (HSE University, Moscow, Russia)}
                                                                                \author[6]{Amyn Abdul Malik, PhD\(^*\)}
                                                            \affil{Yale Institute for Global Health}
                                                                                \author[3]{Samya Aboutajdine, MA}
                                                                            \author[7]{Alex Armand, PhD}
                                                            \affil{Nova School of Business and Economics}
                                                                                \author[8]{Saher Asad, PhD}
                                                            \affil{Lahore University of Management Sciences}
                                                                                \author[9]{Britta Augsburg, PhD}
                                                            \affil{The Institute for Fiscal Studies}
                                                                                \author[10]{Antonella Bancalari, PhD}
                                                            \affil{University of St.~Andrews \& The Institute for Fiscal Studies}
                                                                                \author[11]{Martina Björkman Nyqvist, PhD}
                                                            \affil{Stockholm School of Economics and Misum}
                                                                                \author[5,12]{Ekaterina Borisova, PhD}
                                                            \affil{Economics Department of Ghent University}
                                                                                \author[1]{Constantin Manuel Bosancianu, PhD}
                                                                            \author[8,13]{Ali Cheema, PhD}
                                                            \affil{Institute of Development and Economic Alternatives}
                                                                                \author[2]{Elliott Collins, PhD}
                                                                            \author[13]{Ahsan Zia Farooqi, MA}
                                                                            \author[7]{Mattia Fracchia, MA}
                                                                            \author[14]{Andrea Guariso, PhD}
                                                            \affil{Trinity College Dublin}
                                                                                \author[8]{Ali Hasanain, PhD}
                                                                            \author[2]{Anthony Kamwesigye, BSc}
                                                                            \author[15]{Sarah Kreps, PhD}
                                                            \affil{Cornell University}
                                                                                \author[4]{Madison Levine, MSc}
                                                                            \author[16]{Rebecca Littman, PhD}
                                                            \affil{University of Illinois Chicago}
                                                                                \author[17]{Melina Platas, PhD}
                                                            \affil{NYU Abu Dhabi}
                                                                                \author[18]{Vasudha Ramakrishna, MSc}
                                                            \affil{Yale Research Initiative on Innovation and Scale (Y-RISE)}
                                                                                \author[19]{Jacob N. Shapiro, PhD}
                                                            \affil{Princeton University}
                                                                                \author[20]{Jakob Svensson, PhD}
                                                            \affil{Institute for International Economic Studies (IIES), Stockholm University}
                                                                                \author[18]{Corey Vernot, BS}
                                                                            \author[7]{Pedro C. Vicente, PhD}
                                                                            \author[21]{Laurin B Weissinger, DPhil}
                                                            \affil{Tufts University}
                                                                                \author[15]{Baobao Zhang, PhD}
                                                                            \author[2,22]{Dean Karlan, PhD\footnote{Last author}}
                                                            \affil{Kellogg School of Management at Northwestern University}
                                                                                \author[3,23]{Michael Callen, PhD\(^\dagger\)}
                                                            \affil{London School of Economics}
                                                                                \author[3]{Matthieu Teachout, PhD\(^\dagger\)}
                                                                            \author[1,24]{Macartan Humphreys, PhD\(^\dagger\)}
                                                            \affil{Columbia University}
                                                                                \author[6]{Saad B. Omer, PhD\footnote{Corresponding author. 1 Church Street, New Haven, CT 06510. Phone 203 432 3656. Email \href{mailto:saad.omer@yale.edu}{saad.omer@yale.edu}}}
                                                                            \author[25]{Ahmed Mushfiq Mobarak, PhD\footnote{Corresponding author. 165 Whitney Avenue, New Haven, CT 06520-8200. Phone 203 432 5787. Email \href{mailto:ahmed.mobarak@yale.edu}{ahmed.mobarak@yale.edu}}}
                                                            \affil{Yale University}
                                            \date{}

\begin{document}
\maketitle

\newpage

\hypertarget{abstract}{%
\section*{Abstract}\label{abstract}}
\addcontentsline{toc}{section}{Abstract}

We analyze COVID-19 vaccine acceptance across 15 survey samples covering ten low- and middle-income countries (LMICs) in Asia, Africa, and South America, and two higher income countries (Russia and the United States). Standardized survey responses were collected from `45,928individuals. We find generally high willingness to take a COVID-19 vaccine in LMIC samples (80\% on average), considerably higher than in the United States (65\%) and Russia (30\%). Vaccine acceptance was primarily explained by an interest in personal protection against the disease, while concern about side effects was the most commonly expressed reason for reluctance. Health workers were the most trusted sources of information about COVID-19 vaccines. Our findings suggest that prioritizing efficient and equitable vaccine distribution to LMICs should yield high returns in promoting global immunization. Interventions to promote vaccination in these contexts should focus on translating intentions into uptake and involve trusted health workers.

\newpage

A safe and effective vaccine against COVID-19 is a critical tool to control the pandemic. As of March 2, 2021, there were 76 vaccines in clinical development and 16 had advanced to Stage 3 clinical trials.\textsuperscript{\protect\hyperlink{ref-who1}{1}} Following clinical trials, several vaccines have been approved in multiple countries and are being distributed across the globe. At present, global vaccine distribution remains highly unequal, with much of the current supply directed toward high-income countries.\textsuperscript{\protect\hyperlink{ref-eiu}{2}}

While effective and equitable distribution of the vaccines is a key policy priority, ensuring the population's acceptance is equally important. Acceptance of vaccines and trust in the institutions that administer them are likely key determinants of the success of any vaccination campaign.\textsuperscript{\protect\hyperlink{ref-defigueiredo2020lancet}{3}} Several studies investigate high-income country residents' willingness to take a potential COVID-19 vaccine.\textsuperscript{\protect\hyperlink{ref-boyon2020ipsos}{4},\protect\hyperlink{ref-Malik2020}{5}} Little is known about acceptance rates in low- and middle-income countries (LMICs), however, where the majority of the world's population resides.

Acceptance of childhood vaccination for common diseases ---such as measles (MCV), Bacille Calmette-Guérin (BCG) and diphtheria, tetanus, and pertussis (DTP)---is generally high in LMICs, providing reasons for optimism about future uptake of COVID-19 vaccines. Table \ref{tab:otherv} summarizes general vaccine acceptance and uptake of common childhood vaccines for the countries included in our study. Still, existing studies on COVID-19 vaccine acceptance document large variation, both across and within countries, including in settings where overall vaccination rates are high.\textsuperscript{\protect\hyperlink{ref-boyon2020ipsos}{4}} These studies highlight concerns about COVID-19 vaccine safety, and particularly concerns about the speed of vaccine development, as reasons for hesitancy in higher income settings. Similar concerns may apply in LMICs.

Additional reasons for hesitancy may feature more prominently in LMIC settings. Reported COVID-19 mortality rates have consistently been lower in LMICs relative to higher income countries.\textsuperscript{\protect\hyperlink{ref-mukherjee}{6}} If individuals in LMICs feel the risk of disease is less serious, they may be less inclined to accept perceived risks associated with taking a recently-developed vaccine. Previous studies have also highlighted factors such as concerns about healthcare quality,\textsuperscript{\protect\hyperlink{ref-christensen2020building}{7}} negative historical experiences,\textsuperscript{\protect\hyperlink{ref-Lowes2018}{8}} weak support from traditional leaders,\textsuperscript{\protect\hyperlink{ref-Jegede2007}{9}} and mistrust in government\textsuperscript{\protect\hyperlink{ref-BLAIR201789}{10}} as barriers to healthcare utilization in LMICs.

Understanding factors that may lead people in LMICs to reject COVID-19 vaccination is of global concern, since a lag in vaccination in the developing world could facilitate the spread of new variants of the virus to other countries.

In order to effectively promote vaccination against COVID-19 and devise messaging strategies, we need to know if people are willing to take COVID-19 vaccines, the reasons why they are willing or unwilling to do so, and the factors influencing their decision-making. For this purpose, we developed and deployed a common set of questions across 15 studies in ten LMICs in Africa (Burkina Faso, Mozambique, Nigeria, Rwanda, Sierra Leone, Uganda), Asia (India, Nepal, Pakistan), and Latin America (Colombia). We compare these findings in LMICs to those from two higher income countries (Russia and the United States).

\hypertarget{results}{%
\section*{Results}\label{results}}
\addcontentsline{toc}{section}{Results}

Our main results are shown in Figure \ref{fig:mainfigure1} and reproduced as Table \ref{tab:maintabledis} in \protect\hyperlink{appendixd}{Appendix A}. The first column provides overall acceptance rates in each study, while the remaining columns show acceptance rates disaggregated by respondent characteristics. The ``All LMICs'' row reports averages for LMIC countries only (and so excludes Russia and the US).

We document meaningful variation in vaccine acceptance across and within LMICs, but generally high levels of acceptance in LMICs overall. The average acceptance across studies is 80.3\% (95\% CI 74.9--85.6), with a median of 78, a range of 30.1 percent points and an interquartile range of 9.7. Our estimate of \(\tau^2\) is 0.007 which implies a standard deviation over country averages of 0.084.

The acceptance rate in every LMIC sample is higher than in USA (64.6\%, 61.8--67.3) and Russia (30.4\%, 29.1--31.7).

We find limited evidence of variation across demographic subgroups in LMICs, as shown in Table \ref{tab:dmeans}. Women were generally less willing to accept the vaccine (average difference about 4.3 points, significant at \(p<.01\)). Younger respondents (defined as aged \textless55 given younger-skewing populations in LMICs) were marginally more willing to take the vaccine, but this difference was not statistically significant. Less educated people were on average more willing to take the vaccine in LMICs, but this difference was not significant.

To better understand the reasoning behind vaccine acceptance, we asked those who were willing to take the vaccine why they would take it. We summarize in Table \ref{tab:yes}, with more details in Table \ref{tab:yesall}.

The most common reason given for vaccine acceptance was personal protection against COVID-19 infection. The average across LMICs was 91\% (86--96). In every individual study, it ranked as the first reason. In distant second place, LMIC respondents reported willingness to take the COVID-19 vaccine in order to protect their families. The average across LMICs was 36\% (28--43). In comparison to self-protection, protecting the community did not feature prominently among the stated reasons.

Self-protection also ranked as the most commonly expressed reason for taking the vaccine in Russia (76\%, 74--78) and the USA (94\%, 92--95).

This evidence contrasts with appeals to altruistic behavior and prosocial motivations in order to promote vaccine acceptance.\textsuperscript{\protect\hyperlink{ref-chou2020considering}{11}} The risks and benefits to personal well-being feature much more prominently in people's stated reasons for vaccine acceptance.

Figure \ref{fig:fig2paper} summarizes the reasons given among respondents who said they were not willing to take a Covid vaccine.

The most common reason expressed for reluctance to take the vaccine in LMIC studies was concern about side effects. For studies Uganda 1 (85.1\% 80.7--89.6), Sierra Leone 2 (57.9\%, 50.1--65.7), Sierra Leone 1 (53.5\% 47.1--59.9) and Uganda 2 (47.3\% 42.2--52.5), more than half of those respondents unwilling to take the vaccine mentioned this reason. Respondents in Russia (36.8\%, 35.2--38.4) and the USA (79.3\%, 74.6--84), reported high levels of this same concern.

While serious adverse events that are life-threatening or require hospitalization are very rare, with only .6\% of respondents reporting at least one side effect in the Pfizer vaccine trial,\textsuperscript{\protect\hyperlink{ref-cdcadverse}{12}} one potential explanation for the outsized concern about side effects could be the lack of widespread information about features of the vaccine at the time of data collection. Media coverage of the few cases of serious adverse events and spread of fake news may contribute as well.\textsuperscript{\protect\hyperlink{ref-stein2017golden}{13}}

Concerns about side effects could also be due to a concern about mild side effects from experiences with other vaccines. In the case of available COVID-19 vaccines, we now know that mild side effects are common but transient. These include fatigue, muscle pain, joint pain and headache, which were severe in fewer than 10\% of people in the clinical trials of tens of thousands. Severe fever occurred in fewer than 2\% of them.\textsuperscript{\protect\hyperlink{ref-wadman2020public}{14}}

Allergic reactions from the COVID-19 vaccine seem to be extremely rare. Data from trials of the Pfizer-BioNTech vaccines shows that anaphylaxis after reported administration occurs at a rate of 11.1 cases per million vaccine doses administered.\textsuperscript{\protect\hyperlink{ref-cdcallergies}{15}} Our data reflects this -- no more than 6\% of respondents expressed concern about allergies in any of our LMIC studies.

Other concerns that make many respondents unwilling to take the vaccine could be countered by accurately presenting the scientific data to the public. Studies Uganda 2 (31\%, 25.9--36.2), Mozambique (29.7\%, 18.6--40.8) and Pakistan 1 (26\%, 18--34) showed relatively high levels of skepticism about vaccine effectiveness. This is also true for respondents in Russia (29.6\%, 28.1--31.1) and the USA (46.8\%, 41--52.6). Recent clinical trials reveal very high rates of vaccine efficacy,\textsuperscript{\protect\hyperlink{ref-baden2021efficacy}{16},\protect\hyperlink{ref-polack2020safety}{17}} and clearly communicating these results to the public is a high priority. In contrast, conspiracy theories were rarely mentioned by respondents in any of our study samples, in spite of widespread popular discourse about anti-vaxxer movements and theories in higher-income countries.\textsuperscript{\protect\hyperlink{ref-loomba_measuring_2021}{18}}

Finally, respondents in some studies downplayed the seriousness of this disease, and listed this as a reason not to be vaccinated. Studies USA (39.3\% 33.5--45), Pakistan 1 (29.4\%, 20.9--37.9) and Nepal (20.4\% 6.7--34.1) reported high rates of respondents citing lack of concern as a reason they were hesitant.

The analysis above identifies the nature of the information gaps that any vaccine messaging should target, while in Figure \ref{fig:fig3paper} we try to identify the actors who are best placed to deliver those messages. We asked respondents about their most trusted source of information when deciding whether to take the vaccine, because these sources are vital to disease control strategies during public health emergencies.\textsuperscript{\protect\hyperlink{ref-siegrist2014role}{19}} Results from Figure \ref{fig:fig3paper} are reproduced as Table \ref{tab:trust} in \protect\hyperlink{appendixd}{Appendix A}.

We find striking consistency across countries. In all but one study, respondents identified the health system as the most trustworthy source to help them decide whether or not to take the COVID-19 vaccine (with the exception of Rwanda, where the government in general was identified as the most trusted source, with the health system a close second). Family and friends were the next most important reference points in most samples. Across samples, women were 3 percentage points more likely to rely on family and friends than male respondents, though this difference was not significant at conventional levels (Figure \ref{fig:genderhist} in \protect\hyperlink{appendixd}{Appendix D}). By contrast, endorsements by religious leaders or celebrity figures were not seen as important sources of influence in any sample other than Nepal.

\hypertarget{discussion}{%
\section*{Discussion}\label{discussion}}
\addcontentsline{toc}{section}{Discussion}

To our knowledge, this is the first study documenting rates of expressed COVID-19 vaccine acceptance and hesitancy in a large set of LMICs. Our findings show variable but broadly high levels of prospective COVID-19 vaccine acceptance across LMICs using data from 45,928 respondents in 13 original household surveys from Africa (Burkina Faso, Mozambique, Nigeria, Rwanda, Sierra Leone, Uganda), Asia (Bangladesh, India, Nepal, Pakistan), and Latin America (Colombia). Acceptance across LMIC averages 80.3, ranging between 66.5 and 96.6. We document considerably lower levels of acceptance in Russia and the United States.

Patterns of COVID-19 vaccine hesitancy are not well predicted by existing measures of concerns about the safety of other vaccines (e.g., the Wellcome Global Monitor shown in Table \ref{tab:otherv}). Compared with other vaccines, COVID-19 vaccine acceptance is lower and more variable across LMIC samples. This suggests that concerns may apply specifically to COVID-19 vaccines rather than to vaccination more broadly.

Our study also documents reasons why respondents express intentions to take (or not take) a COVID-19 vaccine. The main reason expressed for willingness to take such a vaccine was to protect oneself. The most common reasons offered by those unwilling to take the vaccine were concerns about safety (side effects) and efficacy. Across all contexts, health care workers were the most trusted source of information about vaccines.

Our study samples offer an important window into the motivations underlying COVID-19 vaccine acceptance in LMICs, but our data are not fully nationally representative. Random digit dial samples and follow-up phone surveys, while necessary during a global pandemic, do not include individuals who reside outside coverage areas, who do not own or cannot operate cell phones, or who choose not to respond to telephone surveys. Care should also be taken in any attempt to extrapolate to the population level from the samples representative of narrow subpopulations.

If intentions reported in our LMIC samples translated into actual vaccination uptake, the rates would far exceed the range of what would be required for COVID-19 herd immunity (40-67\% in recent estimates).\textsuperscript{\protect\hyperlink{ref-britten2020}{20},\protect\hyperlink{ref-haley2020}{21}} However, reported intent may not materialize into actual vaccine adoption.\textsuperscript{\protect\hyperlink{ref-mceachanetal2011}{22}} The high salience of COVID-19 due to extensive media coverage and government mitigation efforts and excitement around vaccine release may have increased reported intention.\textsuperscript{\protect\hyperlink{ref-chen1996}{23}} Results from the first COVID-19 vaccine Phase 3 clinical trial were announced before some surveys were fielded; during others, subsequent approvals were granted. The fast-moving information environment may change people's perceptions about vaccines by the time they are widely available in LMICs.

Nonetheless, our findings provide some specific guidance on how to design messaging to boost COVID-19 vaccine acceptance and uptake in LMICs. Our data have implications for both what the content of the message should be, and who should deliver the message.

First, high levels of trust in the advice of health workers and governments on COVID-19 vaccine decision-making suggest that social and behavioral change communication (SBCC) strategies that engage local health workers may be particularly effective tools to encourage timely and complete vaccine uptake, and to combat remaining vaccine hesitancy. The literature has explored messaging strategies to promote welfare-improving behaviors, with considerable attention paid to celebrity endorsements.\textsuperscript{\protect\hyperlink{ref-alatas2019celebrities}{24}} Our data strongly support the view\textsuperscript{\protect\hyperlink{ref-bokemper2021timing}{25}} that those with the most relevant expertise - as opposed to celebrities or general opinion leaders - are most trusted on this specific topic and are therefore best positioned to deliver the message.

Second, the average COVID-19 vaccine acceptance rate across our LMIC samples is high, approximately 80.3\%. Given such positive intentions, there may be high returns to investing in straightforward ``last-mile'' nudges that help citizens convert intentions into actions. Reminder messages from healthcare providers and messages alerting patients that vaccines have been reserved for them at an upcoming appointment may provide a low-cost encouragement to initiate and complete two-dose COVID-19 vaccinations, as was found in two recent large-scale studies in the United States.\textsuperscript{\protect\hyperlink{ref-milkmanetal2021a}{26},\protect\hyperlink{ref-milkmanetal2021b}{27}} Similarly, childhood vaccination reminders plus cash incentives in Kenya substantially increased full immunization,\textsuperscript{\protect\hyperlink{ref-gibsonetal2017}{28}} and cash and in-kind incentive programs in Nigeria and India have also proven effective.\textsuperscript{\protect\hyperlink{ref-idinsight}{29},\protect\hyperlink{ref-Banerjee2010}{30}}

Third, high coverage rates of existing vaccines, coupled with respondents' reliance on friends and family as information sources, suggest that the general pro-vaccination stance of many citizens could be leveraged to convert intent to uptake. Social learning strategies and norm-setting are powerful drivers of information diffusion and behavior change in many related sectors.\textsuperscript{\protect\hyperlink{ref-beaman2021can}{31}} Social signalling of positive attitudes toward COVID-19 vaccines may also help shift social norms toward even greater immunization acceptance and two-dose completion in the community at large.\textsuperscript{\protect\hyperlink{ref-karing2018social}{32}}

Finally, our findings offer guidance on the specific content of vaccine messaging that is likely to be most persuasive. Messaging should highlight the high efficacy rates of the COVID-19 vaccines currently on the market in reducing or eliminating disease, hospitalizations and death. Alluding to clinical data that addresses people's concerns about potential side effects should be prioritized. Messaging should also emphasize the direct protective benefits of the vaccine to the adopter.

\hypertarget{methods}{%
\section*{Methods}\label{methods}}
\addcontentsline{toc}{section}{Methods}

\hypertarget{survey-questions-and-sample-construction}{%
\subsection*{Survey questions and sample construction}\label{survey-questions-and-sample-construction}}
\addcontentsline{toc}{subsection}{Survey questions and sample construction}

Survey data were collected between June 2020 and January 2021. Our main outcome measure is vaccine acceptance. Across studies, we asked respondents, ``If a COVID-19 vaccine becomes available in {[}your country{]}, would you take it?''. If the respondent answered yes to this question, we followed up with the question, ``Why would you take it? {[}the COVID-19 vaccine{]}''. If the respondent said they would not be willing to take the vaccine, we followed up with the question, ``Why would you not take it? {[}the COVID-19 vaccine{]}''. Finally, regardless of their expressed willingness to take the vaccine, we asked about actors and institutions who would be influential in their decision. The question was worded in the following way: ``Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available?''. To examine heterogeneity across demographic strata, we collected information about the gender, age, and education level of each respondent. Slight variations in questions wording and answer options across studies are documented in \protect\hyperlink{appendixb}{Appendix B}.

Studies vary in terms of geographic scope, sampling methodology, and survey modality. Seven were national or nearly-national in scope. Among these, studies from Burkina Faso, Colombia, Rwanda, and Sierra Leone (``Sierra Leone 1'') used nationally-representative samples of active mobile phone numbers reached through Random Digit Dialing (RDD). Studies in the USA and Russia were conducted online using quota samples obtained from private survey companies.

The remaining eight studies targeted sub-national populations. One study from Pakistan (``Pakistan 2'') used RDD to reach a representative sample of active mobile phone users in Punjab province. Respondents in Mozambique, Nigeria, ``Pakistan 1'', ``Uganda 1'',``Uganda 2'', India, Nepal and ``Sierra Leone 2'' were drawn from pre-existing studies to which COVID-19 vaccine questions were subsequently added. For example, ``Sierra Leone 2'' has national coverage from a study on access to electricity and ``Uganda 1'' sampled female caregivers of households in rural and semi-rural villages as part of a large ongoing cluster-RCT implemented across 13 districts.

Table \ref{tab:sampling} in \protect\hyperlink{appendixd}{Appendix A} summarizes the geographic scope, sampling methodologies and survey modalities of all 15 studies. A detailed description of each study is included in \protect\hyperlink{appendixa}{Appendix D}.

All LMIC surveys were conducted via telephone to minimize in-person contact and comply with local government social distancing guidelines. Interviews were conducted by local staff in each country in local language(s). Surveying by phone made rapid, large-scale data collection possible. Surveys lasted approximately 15 to 40 minutes.

Taken together, we have data from 21,844 individuals from LMICs and 24,084 from the USA and Russia, for a total of 45,928 respondents.

\hypertarget{statistical-analysis}{%
\section*{Statistical Analysis}\label{statistical-analysis}}
\addcontentsline{toc}{section}{Statistical Analysis}

Vaccine acceptance was defined as the percentage of respondents who answered ``yes'' to the question, ``If a COVID-19 vaccine becomes available in {[}country{]}, would you take it?''. This was calculated combining all other answer options (``No'', ``Don't Know'' and ``Refuse'') into a single reference category. We estimated this outcome for each study with robust standard errors and employed sampling weights where available.

In addition to study-level estimates, we combined data from all studies other than the USA and Russia to calculate an aggregate estimate for all LMIC studies. For these analyses, each included study received equal weight and standard errors were clustered at the study level. Averages in the ``All LMICs'' group then reflect the expected share across studies. In this combined analysis we also estimated the underlying heterogeneity of vaccine acceptance across studies using the between studies variance estimator \(\tau^2\) from a random effects model.

We also conducted subgroup analyses by gender, age and education level and reported differences between groups. For the ``All LMICs'' analyses we calculated the average of differences between subgroups within studies with standard errors clustered at the study level.

We additionally examined reported reasons for COVID-19 vaccine acceptance and hesitancy, as well as the types of actors respondents would trust when making the decision about whether to take a COVID-19 vaccine. Among respondents who expressed willingness to take the vaccine, we asked about several possible reasons why they would take it. For respondents unwilling to take the vaccine, we asked about several possible reasons why they would not take it. Finally, we asked all respondents, regardless of their answers to other questions, whom they would trust most to help them decide whether to get a COVID-19 vaccine. We report estimates of agreement with reasons for vaccine acceptance/hesitancy and trust in actors for individual studies and for the ``All LMICs'' group.

\newpage

\hypertarget{contributors}{%
\section*{Contributors}\label{contributors}}
\addcontentsline{toc}{section}{Contributors}

JSo, SW, NMe, AS, NMc, GS, MV and AM are co-first authors. DK, MC, MT, MH, AMM and SO are co-last authors. AMM and SO are also the corresponding authors.
DK, AMM, MT, NMe, MC, and MV conceived of the study and provided overall guidance.
SAb and NMe led the literature search, with input from AS, NMc, SW, AMM, AM and JSo.
SW, NMe, AS, NMc, MV, GS, AA, SA, BA, AB,EB, CMB, AC, EC, MF, AG, AK, SK, RL, MBN, MP, JSh, JSv, PV, LB, BZ, MC, SAs, AC, AF, AH, MC, MT, and MH oversaw data collection as part of other research efforts.
SW, NMe, and MT coordinated the project across study samples.
The following verified the underlying data for individual study samples: EC (Burkina Faso, Colombia, Rwanda, Sierra Leone 1), BA (India), AS and RL (Nigeria), AG and MBN (Uganda 1), CMB and MH (Uganda 2), NMe and MV (Sierra Leone 2), GS (Russia), MF (Mozambique), AF and JSh (Pakistan 1), SAs (Pakistan 2), CV (Nepal), and NMc (USA).
JSo, GS, MH and SA collated and processed all datasets used for the analysis.
NMe, MH, AMM, JSo, GS, SW, AS, EC, EB, MT, MV and NMc did the data interpretation with guidance from SO and AM.
JSo, GS, EC and MH verified final datasets and analysis.
JSo and GS did the data analysis and produced output figures with input from MH, AMM, DK, SW, EC, MV, NMe and MT.
MH supervised the data analysis.
JSo, SW, NMe, AMM, AS, NMc and MV wrote the first draft of the manuscript, with guidance from AM and SO.
JSo, SW, NMe, AS, NMc, MV, SAb, EB, MP, JSh, PV, BZ, MC, MT, MH, AMM and SO revised the manuscript.
All authors approved the final version of the manuscript. All authors had full access to all the data used in this study and had final responsibility for the decision to submit for publication.

\hypertarget{data-availability-statement}{%
\section*{Data Availability Statement}\label{data-availability-statement}}
\addcontentsline{toc}{section}{Data Availability Statement}

Individual participant data (de-identified) that underlie the results reported in this article, analytic code and replication files will be available immediately following publication to no end date for anyone who wishes to access the data and use it for any purpose in a public, open access repository. A replication exercise is available here \url{https://wzb-ipi.github.io/covid_vaccines/replication.html}.

\hypertarget{funding}{%
\section*{Funding}\label{funding}}
\addcontentsline{toc}{section}{Funding}

Beyond Conflict, Bill and Melinda Gates Foundation, Columbia University, Givewell.org, Ghent University, HSE University Basic Research Program, International Growth Centre, Jameel Poverty Action Lab Crime and Violence Initiative, London School of Economics and Political Science, Mulago Foundation, NOVAFRICA at the Nova School of Business and Economics, NYU Abu Dhabi, Oxford Policy Management, Social Science Research Council, Trinity College Dublin COVID19 Response Funding, UK Aid, UKRI GCRF/Newton Fund, United Nations Office for Project Services, Weiss Family Fund, WZB Berlin Social Science Center, Yale Institute for Global Health, Yale Macmillan Center, and anonymous donors to IPA and Y-RISE.

\hypertarget{role-of-the-funding-source}{%
\section*{Role of the funding source}\label{role-of-the-funding-source}}
\addcontentsline{toc}{section}{Role of the funding source}

None of our funders played any role in the collection, analysis, interpretation, writing or decision to submit this article for publication.

\hypertarget{declaration-of-interests}{%
\section*{Declaration of interests}\label{declaration-of-interests}}
\addcontentsline{toc}{section}{Declaration of interests}

We declare no competing interests.

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\hypertarget{ref-who1}{}%
\CSLLeftMargin{1. }
\CSLRightInline{WHO. {World Health Organization} draft landscape and tracker of COVID-19 candidate vaccines. (2021).}

\leavevmode\hypertarget{ref-eiu}{}%
\CSLLeftMargin{2. }
\CSLRightInline{EIU. More than 85 poor countries will not have widespread access to coronavirus vaccines before 2023. \emph{The Economist} (2021).}

\leavevmode\hypertarget{ref-defigueiredo2020lancet}{}%
\CSLLeftMargin{3. }
\CSLRightInline{Figueiredo, A. de, Simas, C., Karafillakis, E., Paterson, P. \& Larson, H. J. Mapping global trends in vaccine confidence and investigating barriers to vaccine uptake : A large-scale retrospective temporal modelling study. \emph{The Lancet} \textbf{396}, 898--908 (2020).}

\leavevmode\hypertarget{ref-boyon2020ipsos}{}%
\CSLLeftMargin{4. }
\CSLRightInline{Boyon, N. Global attitudes on a covid vaccine. (2020).}

\leavevmode\hypertarget{ref-Malik2020}{}%
\CSLLeftMargin{5. }
\CSLRightInline{Malik, A., McFadden, S., Elharake, J. \& Omer, S. Determinants of COVID-19 vaccine acceptance in the US. \emph{EClinicalMedicine} \textbf{26}, 100495 (2020).}

\leavevmode\hypertarget{ref-mukherjee}{}%
\CSLLeftMargin{6. }
\CSLRightInline{Mukherjee, S. Why does the pandemic seem to be hitting some countries harder than others? \emph{New Yorker} (2021).}

\leavevmode\hypertarget{ref-christensen2020building}{}%
\CSLLeftMargin{7. }
\CSLRightInline{Christensen, D., Dube, O., Haushofer, J., Siddiqi, B. \& Voors, M. \emph{Building resilient health systems: Experimental evidence from sierra leone and the 2014 ebola outbreak}. (The Quarterly Journal of Economics, 2021).}

\leavevmode\hypertarget{ref-Lowes2018}{}%
\CSLLeftMargin{8. }
\CSLRightInline{Lowes, S. R. \& Montero, E. The legacy of colonial medicine in central africa. (2018).}

\leavevmode\hypertarget{ref-Jegede2007}{}%
\CSLLeftMargin{9. }
\CSLRightInline{Jegede, A. S. What led to the nigerian boycott of the polio vaccination campaign? \emph{PLOS Medicine} \textbf{4(3)}, (2007).}

\leavevmode\hypertarget{ref-BLAIR201789}{}%
\CSLLeftMargin{10. }
\CSLRightInline{Blair, R., Morse, B. \& Tsai, L. Public health and public trust: Survey evidence from the ebola virus disease epidemic in liberia. \emph{Social Science \& Medicine} \textbf{172}, 89--97 (2017).}

\leavevmode\hypertarget{ref-chou2020considering}{}%
\CSLLeftMargin{11. }
\CSLRightInline{Chou, W.-Y. S. \& Budenz, A. Considering emotion in COVID-19 vaccine communication: Addressing vaccine hesitancy and fostering vaccine confidence. \emph{Health communication} \textbf{35}, 1718--1722 (2020).}

\leavevmode\hypertarget{ref-cdcadverse}{}%
\CSLLeftMargin{12. }
\CSLRightInline{Centre for Disease Control and Prevention. {Local Reactions, Systemic Reactions, Adverse Events, and Serious Adverse Events: Pfizer-BioNTech COVID-19 Vaccine}. \url{https://www.cdc.gov/vaccines/covid-19/info-by-product/pfizer/reactogenicity.html} (2020).}

\leavevmode\hypertarget{ref-stein2017golden}{}%
\CSLLeftMargin{13. }
\CSLRightInline{Stein, R. A. The golden age of anti-vaccine conspiracies. \emph{Germs} \textbf{7}, 168 (2017).}

\leavevmode\hypertarget{ref-wadman2020public}{}%
\CSLLeftMargin{14. }
\CSLRightInline{Wadman, M. Public needs to prep for vaccine side effects. (2020).}

\leavevmode\hypertarget{ref-cdcallergies}{}%
\CSLLeftMargin{15. }
\CSLRightInline{CDC COVID-19 Response Team \& Food and Drug Administration. {Allergic Reactions Including Anaphylaxis After Receipt of the First Dose of Pfizer-BioNTech COVID-19 Vaccine --- United States, December 14--23, 2020}. \url{https://www.cdc.gov/mmwr/volumes/70/wr/mm7002e1.htm\#:~:text=Early\%20safety\%20monitoring\%20of\%20the,nonanaphylaxis\%20allergic\%20reactions\%2C\%20based\%20on} (2021).}

\leavevmode\hypertarget{ref-baden2021efficacy}{}%
\CSLLeftMargin{16. }
\CSLRightInline{Baden, L. R. \emph{et al.} Efficacy and safety of the mRNA-1273 SARS-CoV-2 vaccine. \emph{New England Journal of Medicine} \textbf{384}, 403--416 (2021).}

\leavevmode\hypertarget{ref-polack2020safety}{}%
\CSLLeftMargin{17. }
\CSLRightInline{Polack, F. P. \emph{et al.} Safety and efficacy of the BNT162b2 mRNA covid-19 vaccine. \emph{New England Journal of Medicine} \textbf{383}, 2603--2615 (2020).}

\leavevmode\hypertarget{ref-loomba_measuring_2021}{}%
\CSLLeftMargin{18. }
\CSLRightInline{Loomba, S., Figueiredo, A. de, Piatek, S. J., Graaf, K. de \& Larson, H. J. Measuring the impact of {COVID}-19 vaccine misinformation on vaccination intent in the {UK} and {USA}. \emph{Nature Human Behaviour} (2021) doi:\href{https://doi.org/10.1038/s41562-021-01056-1}{10.1038/s41562-021-01056-1}.}

\leavevmode\hypertarget{ref-siegrist2014role}{}%
\CSLLeftMargin{19. }
\CSLRightInline{Siegrist, M. \& Zingg, A. The role of public trust during pandemics: Implications for crisis communication. \emph{European Psychologist} \textbf{19}, 23 (2014).}

\leavevmode\hypertarget{ref-britten2020}{}%
\CSLLeftMargin{20. }
\CSLRightInline{Britton, T., Ball, F. \& Trapman, P. A mathematical model reveals the influence of population heterogeneity on herd immunity to SARS-CoV-2. \emph{Science} \textbf{369}, 846--849 (2020).}

\leavevmode\hypertarget{ref-haley2020}{}%
\CSLLeftMargin{21. }
\CSLRightInline{Randolph, H. E. \& Barreiro, L. B. Herd immunity: Understanding COVID-19. \emph{Immunity} \textbf{52}, 737--741 (2020).}

\leavevmode\hypertarget{ref-mceachanetal2011}{}%
\CSLLeftMargin{22. }
\CSLRightInline{Mceachan, R., Conner, M., Taylor, N. \& Lawton, R. Prospective prediction of health-related behaviours with the theory of planned behaviour: A meta-analysis. \emph{Health Psychology Review} \textbf{5}, 97 (2011).}

\leavevmode\hypertarget{ref-chen1996}{}%
\CSLLeftMargin{23. }
\CSLRightInline{Chen, R. T. \& Orenstein, W. A. Epidemiologic methods in immunization programs. \emph{Epidemiologic Reviews} \textbf{18}, 99--117 (1996).}

\leavevmode\hypertarget{ref-alatas2019celebrities}{}%
\CSLLeftMargin{24. }
\CSLRightInline{Alatas, V., Chandrasekhar, A. G., Mobius, M., Olken, B. A. \& Paladines, C. \emph{When celebrities speak: A nationwide twitter experiment promoting vaccination in indonesia}. (2019).}

\leavevmode\hypertarget{ref-bokemper2021timing}{}%
\CSLLeftMargin{25. }
\CSLRightInline{Bokemper, S. E., Huber, G. A., Gerber, A. S., James, E. K. \& Omer, S. B. Timing of COVID-19 vaccine approval and endorsement by public figures. \emph{Vaccine} \textbf{39}, 825--829 (2021).}

\leavevmode\hypertarget{ref-milkmanetal2021a}{}%
\CSLLeftMargin{26. }
\CSLRightInline{Milkman, K. L. \emph{et al.} A mega-study of text-based nudges encouraging patients to get vaccinated at an upcoming doctor's appointment. (2021).}

\leavevmode\hypertarget{ref-milkmanetal2021b}{}%
\CSLLeftMargin{27. }
\CSLRightInline{Milkman, K. L. \emph{et al.} A mega-study of text-message nudges encouraging patients to get vaccinated at their pharmacy. (2021).}

\leavevmode\hypertarget{ref-gibsonetal2017}{}%
\CSLLeftMargin{28. }
\CSLRightInline{Gibson, D. G. \emph{et al.} Mobile phone-delivered reminders and incentives to improve childhood immunisation coverage and timeliness in kenya (m-SIMU): A cluster randomised controlled trial. \emph{The Lancet Global Health} \textbf{5}, e428--e438 (2017).}

\leavevmode\hypertarget{ref-idinsight}{}%
\CSLLeftMargin{29. }
\CSLRightInline{Insight, I. {Impact of conditional cash transfers on routine childhood immunizations in North West Nigeria}. \url{https://files.givewell.org/files/DWDA\%202009/NewIncentives/IDinsight_Impact_Evaluation_of_New_Incentives_Final_Report.pdf} (2020).}

\leavevmode\hypertarget{ref-Banerjee2010}{}%
\CSLLeftMargin{30. }
\CSLRightInline{Banerjee, A. V., Duflo, E., Glennerster, R. \& Kothari, D. Improving immunisation coverage in rural india: Clustered randomised controlled evaluation of immunisation campaigns with and without incentives. \emph{BMJ} \textbf{340}, (2010).}

\leavevmode\hypertarget{ref-beaman2021can}{}%
\CSLLeftMargin{31. }
\CSLRightInline{Beaman, L., BenYishay, A., Magruder, J. \& Mobarak, A. M. \emph{Can network theory-based targeting increase technology adoption?} (2021).}

\leavevmode\hypertarget{ref-karing2018social}{}%
\CSLLeftMargin{32. }
\CSLRightInline{Karing, A. Social signaling and childhood immunization: A field experiment in sierra leone. \emph{University of California, Berkeley Working Paper} (2018).}

\leavevmode\hypertarget{ref-Duch2021}{}%
\CSLLeftMargin{33. }
\CSLRightInline{Duch, R. \emph{et al.} Who should be first in line for the COVID-19 vaccine? Surveys in 13 countries of the public{'}s preferences for prioritisation. \emph{medRxiv} (2021).}

\leavevmode\hypertarget{ref-lazarus2020nature}{}%
\CSLLeftMargin{34. }
\CSLRightInline{Lazarus, J. V. \emph{et al.} A global survey of potential acceptance of a COVID-19 vaccine. \emph{Nature Medecine} 1--4 (2020).}

\leavevmode\hypertarget{ref-wbinternet}{}%
\CSLLeftMargin{35. }
\CSLRightInline{World Bank, W. D. I. \url{https://data.worldbank.org/indicator/IT.NET.USER.ZS?locations=XO} (2019).}

\end{CSLReferences}

\newpage

\begin{landscape}\begin{table}[!h]

\caption{\label{tab:otherv}Vaccination beliefs and coverage for the countries in our sample}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{9em}>{\centering\arraybackslash}p{9em}>{\centering\arraybackslash}p{9em}>{\centering\arraybackslash}p{9em}>{\centering\arraybackslash}p{9em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{9em}}
\toprule
\multicolumn{1}{c}{\textbf{ }} & \multicolumn{3}{c}{\textbf{\% Respondents agreeing Vaccines are...}} & \multicolumn{3}{c}{\textbf{Vaccine coverage in 2019 (\% of infants)}} & \multicolumn{1}{c}{\textbf{ }} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
\textbf{} & \textbf{Effective} & \textbf{Safe} & \textbf{Important for children to have} & \textbf{Tuberculosis (BCG)} & \textbf{Diphtheria, Tetanus and Pertussis (DTP1)} & \textbf{Measles (MCV1)} & \textbf{\% of parents with any child that was ever vaccinated}\\
\midrule
Burkina Faso & 87 & 72 & 95 & 98 & 95 & 88 & 97\\
Colombia & 83 & 84 & 99 & 89 & 92 & 95 & 95\\
India & 96 & 97 & 98 & 92 & 94 & 95 & 92\\
Mozambique & 87 & 93 & 98 & 94 & 93 & 87 & 95\\
Nepal & 89 & 93 & 99 & 96 & 96 & 92 & 95\\
Nigeria & 82 & 92 & 96 & 67 & 65 & 54 & 95\\
Pakistan & 91 & 92 & 95 & 88 & 86 & 75 & 94\\
Rwanda & 99 & 97 & 99 & 98 & 99 & 96 & 100\\
Sierra Leone & 95 & 95 & 99 & 86 & 95 & 93 & 97\\
Uganda & 82 & 87 & 98 & 88 & 99 & 87 & 98\\
Russia & 67 & 48 & 80 & 96 & 97 & 98 & 96\\
USA & 85 & 73 & 87 & . & 97 & 90 & 95\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Table 1 presents an overview of vaccination beliefs and incidence across countries in our sample. Columns 2-4 and 8 use data from the Wellcome Global Monitor 2018. Column 8 shows the percentage of respondents who are parents and report having had any of their children ever vaccinated. Columns 2-4 show the percentage of all respondents that either strongly agree or somewhat agree with the statement above each column. All percentages are obtained using national weights. Columns 5-7 use data from the World Health Organization on vaccine incidence. Columns 5-7 report the percentage of infants per country receiving the vaccine indicated in each column.
\end{tablenotes}
\end{threeparttable}}
\end{table}
\end{landscape}

\begin{figure}[!ht]
\caption{Acceptance rates overall and broken down by respondent characteristics \label{fig:mainfigure1}}

\includegraphics{paper_files/figure-latex/mainfigure1-1.pdf}

\scriptsize{Figure 1 presents average acceptance of the COVID-19 vaccine across studies and subgroups within studies. For each study, we summarize sampling information in parentheses in the following way: First, we indicate whether the geographic coverage of the sample is national or subnational. If the coverage is subnational we provide further details. Second, we list the number of observations included in the study. In the plot, points represent the estimated percentage of individuals who would take the vaccine. ``No'', ``Don't know'' and ``Refuse'' are taken as a single reference category. Bars around each point indicate a 95\% confidence interval for the estimate. An estimate of average acceptance for all studies in LMICs (excluding USA and Russia) is also shown.}
\end{figure}

\begin{table}

\caption{\label{tab:yes}Reasons to take the vaccine}
\centering
\fontsize{10}{12}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8em}>{\centering\arraybackslash}p{4em}>{\centering\arraybackslash}p{4em}>{\centering\arraybackslash}p{4em}c}
\toprule
\multicolumn{2}{c}{\textbf{ }} & \multicolumn{3}{c}{\textbf{Protection}} \\
\cmidrule(l{3pt}r{3pt}){3-5}
\textbf{Study} & \textbf{N} & \textbf{Self} & \textbf{Family} & \textbf{Community}\\
\midrule
Burkina Faso & 651 & 76 & 42 & 7\\
 &  & (73, 79) & (38, 46) & ( 5,  9)\\
Colombia & 756 & 91 & 23 & 12\\
 &  & (88, 93) & (20, 26) & (10, 14)\\
Mozambique & 768 & 83 & 32 & 4\\
 &  & (80, 86) & (27, 38) & ( 2,  5)\\
Nepal & 1341 & 96 & 34 & 20\\
 &  & (95, 98) & (32, 37) & (17, 22)\\
Nigeria & 1424 & 89 & 35 & 21\\
 &  & (88, 91) & (33, 38) & (19, 23)\\
Rwanda & 1152 & 98 & 26 & 11\\
 &  & (97, 99) & (23, 28) & ( 9, 13)\\
Sierra Leone 1 & 836 & 94 & 37 & 21\\
 &  & (92, 96) & (34, 40) & (18, 23)\\
Sierra Leone 2 & 1855 & 91 & 62 & 21\\
 &  & (88, 93) & (57, 66) & (16, 27)\\
Uganda 1 & 2885 & 96 & 36 & 9\\
 &  & (95, 97) & (34, 38) & ( 8, 10)\\
Uganda 2 & 1045 & 96 & 28 & 11\\
 &  & (95, 97) & (25, 31) & ( 9, 12)\\
All LMICs & . & 91 & 36 & 14\\
 &  & (86, 96) & (28, 43) & ( 9, 18)\\
Russia & 5887 & 76 & 69 & 41\\
 &  & (74, 78) & (67, 71) & (38, 43)\\
USA & 1313 & 94 & 92 & 89\\
 &  & (92, 95) & (90, 94) & (87, 91)\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Table 2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine. The number of observations and percentage correponds only to people who would take the vaccine. Respondents in all countries could give more than one reason. A 95\% confidence interval is shown between parentheses. Studies India, Pakistan 1 and Pakistan 2 are not included because they either did not include the question or were not properly harmonized with the other studies.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{figure}[!ht]
\caption{Reasons not to take the vaccine \label{fig:fig2paper}}

\includegraphics{paper_files/figure-latex/fig2paper-1.pdf}

\scriptsize{Figure 2 shows the percentage of respondents mentioning reasons why they would not take the COVID-19 vaccine. In the plot, points represent the estimated percentage of individuals that would not take the vaccine or do not know if they would take the vaccine for each possible response option. Bars around each point indicate a 95\% confidence interval for the estimate. An estimated average for all studies in LMICs is also shown. Size of points illustrates the number of observations in each response option. Studies India and Pakistan 2 are not included because they either did not include the question or were not properly harmonized with the other studies.}
\end{figure}

\begin{figure}[!ht]
\caption{Trusted actors and institutions, broken down by expressed willingness to take a COVID-19 vaccine \label{fig:fig3paper}}

\newpage

\includegraphics{paper_files/figure-latex/fig3paper-1.pdf}
\newpage

\scriptsize{Figure 3 shows histograms of actors and institutions respondents say they would trust most to help them decide whether to take the COVID-19 vaccine. Respondents were only permitted to select one most trusted actor or institution. Studies India, Mozambique, Pakistan 1, Pakistan 2 and Uganda 1 are not included because they either did not include the question or were not properly harmonized with the other studies.}
\end{figure}

\clearpage

\hypertarget{supplementary-appendix}{%
\section*{Supplementary Appendix}\label{supplementary-appendix}}
\addcontentsline{toc}{section}{Supplementary Appendix}

\hypertarget{appendixd}{%
\subsection*{Appendix A: Supplementary tables, figures and results}\label{appendixd}}
\addcontentsline{toc}{subsection}{Appendix A: Supplementary tables, figures and results}

\begin{landscape}\begin{table}[!h]

\caption{\label{tab:sampling}Summary of studies sampling}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{12em}>{\raggedright\arraybackslash}p{30em}ll}
\toprule
\textbf{Study} & \textbf{Geographic scope} & \textbf{Sampling methodology} & \textbf{Survey modality} & \textbf{Weights}\\
\midrule
Burkina Faso & National & Random digit dialing (RDD) & Phone & Yes\\
Colombia & National & Random digit dialing (RDD) & Phone & Yes\\
India & Subnational, Slums in 2 cities & Representative sample of slum dwellers living in vicinity of a community toilet and located in Uttar Pradesh & Phone & Yes\\
Mozambique & Subnational, 2 cities & 1) Random sample in urban and periurban markets stratified by gender and type of establishment in Maputo; 2) Random sample representative of communities in the Cabo Delgado, stratified on urban, semiurban, and rural areas & Phone & No\\
Nepal & Subnational, 2 districts & Random sample of poor households from randomly selected villages in Kanchanpur & Phone & Yes\\
Nigeria & Subnational, 1 state & 1) Random sample of individuals in Kaduna; 2) Sample of phone numbers from a phone list of Kaduna state residents & Phone & No\\
Pakistan 1 & Subnational, 2 districts & Random sample of individuals in administrative police units in two districts of Punjab & Phone & Yes\\
Pakistan 2 & Subnational, 1 province & Random digit dialing (RDD) on a random sample of all numerically possible mobile phone numbers in the region of Punjab & Phone & No\\
Russia & Subnational, 61 regions & Sample recruited from the Russian online survey company OMI (Online Market Intelligence). Sampling targeted at having a minimum of respondents per region, as well as representation of age, gender and education groups. & Online & Yes\\
Rwanda & National & Random digit dialing (RDD) & Phone & Yes\\
Sierra Leone 1 & National & Random digit dialing (RDD) & Phone & Yes\\
Sierra Leone 2 & National & A random sample of households in 195 rural towns across all 14 districts of Sierra Leone & Phone & No\\
Uganda 1 & Subnational, 13 districts & Sample of women in households from semi-rural and rural villages across 13 districts in Uganda, selected according to the likelihood of having children & Phone & No\\
Uganda 2 & Subnational, 1 district & Random sample of households in Kampala & Phone & No\\
USA & National & Nation-wide sample of adult internet users recruited through the market research firm Lucid & Online & Yes\\
\bottomrule
\end{tabular}}
\end{table}
\end{landscape}
\begin{table}[!h]

\caption{\label{tab:maintabledis}If a COVID-19 vaccine becomes available in [country], would you take it? Disaggregated by subgroups}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{lccccccc}
\toprule
\multicolumn{1}{c}{\textbf{}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{Gender}} & \multicolumn{2}{c}{\textbf{Education}} & \multicolumn{2}{c}{\textbf{Age}} \\
\cmidrule(l{3pt}r{3pt}){3-4} \cmidrule(l{3pt}r{3pt}){5-6} \cmidrule(l{3pt}r{3pt}){7-8}
\textbf{Country} & \textbf{Average acceptability} & \textbf{Female} & \textbf{Male} & \textbf{> Secondary} & \textbf{Up to Secondary} & \textbf{<55} & \textbf{55+}\\
\midrule
Burkina Faso & 66.5 & 62.1 & 68.4 & 60.8 & 70.1 & 66.0 & 61.0\\
 & (63.5, 69.5) & (56.3, 67.9) & (65.0, 71.9) & (55.9, 65.8) & (66.4, 73.8) & (57.2,  74.8) & (-6.5, 128.6)\\
Colombia & 74.9 & 73.5 & 77.3 & 78.1 & 73.4 & 74.5 & 73.8\\
 & (72.2, 77.6) & (70.1, 77.0) & (73.0, 81.7) & (73.6, 82.5) & (70.1, 76.8) & (70.9,  78.0) & (65.0,  82.6)\\
India & 84.6 & 80.8 & 85.6 & 89.4 & 85.8 & 84.6 & 85.1\\
 & (82.8, 86.4) & (77.6, 84.1) & (83.7, 87.5) & (83.5, 95.4) & (82.6, 88.9) & (82.8,  86.4) & (80.8,  89.4)\\
Mozambique & 89.1 & 86.2 & 91.3 & 86.1 & 89.7 & 88.4 & 91.7\\
 & (86.5, 91.7) & (82.5, 90.0) & (88.4, 94.1) & (81.8, 90.4) & (86.5, 92.8) & (85.5,  91.3) & (88.1,  95.4)\\
Nepal & 96.6 & 96.4 & 96.4 & . & . & 96.8 & 93.8\\
 & (95.5, 97.6) & (94.6, 98.2) & (95.1, 97.7) & . & . & (95.6,  98.0) & (90.4,  97.2)\\
Nigeria & 76.2 & 74.9 & 77.0 & . & . & 76.3 & 74.7\\
 & (74.3, 78.2) & (71.7, 78.1) & (74.6, 79.4) & . & . & (74.3,  78.3) & (65.8,  83.6)\\
Pakistan 1 & 76.1 & 72.2 & 80.1 & 83.6 & 74.0 & 76.0 & 80.8\\
 & (70.0, 82.3) & (65.6, 78.8) & (73.8, 86.4) & (76.6, 90.5) & (67.4, 80.5) & (69.9,  82.2) & (64.9,  96.7)\\
Pakistan 2 & 66.5 & . & . & 71.4 & 64.2 & . & .\\
 & (64.1, 68.9) & . & . & (67.3, 75.5) & (61.2, 67.1) & . & .\\
Rwanda & 84.9 & 79.4 & 88.0 & 71.4 & 87.7 & 85.2 & 73.3\\
 & (82.9, 86.8) & (75.8, 83.0) & (85.8, 90.2) & (65.5, 77.2) & (85.8, 89.7) & (83.3,  87.2) & (59.2,  87.3)\\
Sierra Leone 1 & 78.0 & 74.1 & 80.1 & 74.4 & 80.2 & 78.2 & 74.0\\
 & (75.5, 80.5) & (69.5, 78.7) & (77.2, 83.1) & (70.1, 78.7) & (77.0, 83.3) & (75.7,  80.8) & (61.4,  86.6)\\
Sierra Leone 2 & 87.9 & 88.6 & 87.7 & 88.8 & 87.8 & 87.4 & 90.0\\
 & (86.2, 89.6) & (85.7, 91.5) & (85.9, 89.5) & (85.0, 92.5) & (86.0, 89.6) & (85.5,  89.3) & (87.4,  92.6)\\
Uganda 1 & 85.8 & 85.8 & . & 80.1 & 84.8 & 85.8 & .\\
 & (84.4, 87.2) & (84.4, 87.2) & . & (74.4, 85.9) & (83.2, 86.5) & (84.4,  87.2) & .\\
Uganda 2 & 76.5 & 74.9 & 78.0 & 68.6 & 79.8 & 76.9 & 73.7\\
 & (74.3, 78.7) & (71.5, 78.3) & (75.2, 80.9) & (64.3, 72.9) & (77.3, 82.2) & (74.5,  79.3) & (67.3,  80.0)\\
All LMICs & 80.3 & 79.1 & 82.7 & 77.5 & 79.8 & 81.3 & 79.3\\
 & (74.9, 85.6) & (73.3, 84.9) & (77.4, 88.0) & (71.4, 83.6) & (74.1, 85.4) & (76.1,  86.5) & (72.6,  86.0)\\
Russia & 30.4 & 22.6 & 38.5 & 31.0 & 29.6 & 28.4 & 40.0\\
 & (29.1, 31.7) & (20.9, 24.2) & (36.5, 40.5) & (29.6, 32.5) & (27.3, 32.0) & (27.1,  29.7) & (35.9,  44.0)\\
USA & 64.6 & 56.1 & 73.4 & 72.3 & 51.5 & 61.8 & 69.4\\
 & (61.8, 67.3) & (52.1, 60.1) & (69.8, 76.9) & (69.5, 75.0) & (46.0, 57.0) & (58.4,  65.2) & (64.8,  73.9)\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Table 4 shows percentage of respondents willing to take the COVID-19 vaccine as plotted in Figure 1. A 95\% confidence interval is shown between parentheses
\end{tablenotes}
\end{threeparttable}}
\end{table}

\newpage

\begin{table}[!h]

\caption{\label{tab:yesall}Reasons to take the vaccine- all categories}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}}
\toprule
\multicolumn{2}{c}{\textbf{ }} & \multicolumn{3}{c}{\textbf{Protection}} & \multicolumn{2}{c}{\textbf{If recommended by}} & \multicolumn{1}{c}{\textbf{ }} \\
\cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-7}
\textbf{Study} & \textbf{N} & \textbf{Self} & \textbf{Family} & \textbf{Community} & \textbf{Health workers} & \textbf{Government} & \textbf{Other}\\
\midrule
Burkina Faso & 651 & 76 & 42 & 7 & 6 & 19 & 2\\
 &  & (73, 79) & (38, 46) & ( 5,  9) & ( 4,  8) & (16, 22) & ( 1,  3)\\
Colombia & 756 & 91 & 23 & 12 & 1 & 2 & 6\\
 &  & (88, 93) & (20, 26) & (10, 14) & ( 0,  2) & ( 1,  3) & ( 4,  7)\\
Mozambique & 768 & 83 & 32 & 4 & . & 7 & 3\\
 &  & (80, 86) & (27, 38) & ( 2,  5) & . & ( 5,  8) & ( 2,  4)\\
Nepal & 1341 & 96 & 34 & 20 & 2 & 3 & 7\\
 &  & (95, 98) & (32, 37) & (17, 22) & ( 1,  2) & ( 2,  4) & ( 5,  9)\\
Nigeria & 1424 & 89 & 35 & 21 & . & 6 & 4\\
 &  & (88, 91) & (33, 38) & (19, 23) & . & ( 4,  7) & ( 3,  5)\\
Rwanda & 1152 & 98 & 26 & 11 & 1 & 5 & 1\\
 &  & (97, 99) & (23, 28) & ( 9, 13) & ( 0,  1) & ( 4,  6) & ( 1,  2)\\
Sierra Leone 1 & 836 & 94 & 37 & 21 & 12 & 23 & 7\\
 &  & (92, 96) & (34, 40) & (18, 23) & (10, 14) & (20, 25) & ( 5,  9)\\
Sierra Leone 2 & 1855 & 91 & 62 & 21 & 59 & . & 16\\
 &  & (88, 93) & (57, 66) & (16, 27) & (54, 63) & . & (11, 21)\\
Uganda 1 & 2885 & 96 & 36 & 9 & . & 10 & 6\\
 &  & (95, 97) & (34, 38) & ( 8, 10) & . & ( 9, 12) & ( 5,  7)\\
Uganda 2 & 1045 & 96 & 28 & 11 & 1 & 15 & 2\\
 &  & (95, 97) & (25, 31) & ( 9, 12) & ( 1,  2) & (13, 17) & ( 1,  3)\\
All LMICs & . & 91 & 36 & 14 & 12 & 10 & 5\\
 &  & (86, 96) & (28, 43) & ( 9, 18) & (-8, 31) & ( 4, 16) & ( 2,  8)\\
Russia & 5887 & 76 & 69 & 41 & 11 & 6 & 18\\
 &  & (74, 78) & (67, 71) & (38, 43) & (10, 13) & ( 5,  7) & (16, 20)\\
USA & 1313 & 94 & 92 & 89 & . & 67 & .\\
 &  & (92, 95) & (90, 94) & (87, 91) & . & (64, 70) & .\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Table 5 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine. The number of observations and percentage correponds only to people who would take the vaccine. Respondents in all countries could give more than one reason. A 95\% confidence interval is shown between parentheses
\end{tablenotes}
\end{threeparttable}}
\end{table}

\newpage

\begin{landscape}\begin{table}[!h]

\caption{\label{tab:no}Reasons not to take the vaccine}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}}
\toprule
\textbf{Study} & \textbf{N} & \textbf{Concerned about side effects} & \textbf{Concerned about getting coronavirus from the vaccine} & \textbf{Not concerned about getting seriously ill} & \textbf{Doesn't think vaccines are effective} & \textbf{Doesn't think Coronavirus outbreak is as serious as people say} & \textbf{Doesn't like needles} & \textbf{Allergic to vaccines} & \textbf{Won't have time to get vaccinated} & \textbf{Mentions a conspiracy theory} & \textbf{Other reasons}\\
\midrule
Burkina Faso & 325 & 40.9 & 8.0 & 7.4 & 19.5 & 13.5 & 3.5 & 1.5 & 0.9 & 17.9 & 8.7\\
 &  & (35.5, 46.3) & ( 5.0, 11.0) & ( 4.5, 10.2) & (15.1, 23.8) & ( 9.8, 17.2) & ( 1.5,  5.6) & ( 0.2,  2.8) & (-0.1,  1.9) & (13.7, 22.1) & ( 5.6, 11.8)\\
Colombia & 202 & 31.0 & 18.1 & 8.0 & 10.2 & 2.3 & 0.6 & 0.4 & 0.5 & 10.0 & 31.6\\
 &  & (24.4, 37.6) & (12.7, 23.4) & ( 3.9, 12.0) & ( 5.9, 14.5) & ( 0.3,  4.3) & (-0.6,  1.8) & (-0.4,  1.3) & (-0.5,  1.5) & ( 5.8, 14.2) & (25.1, 38.2)\\
Mozambique & 74 & . & . & 2.7 & 29.7 & . & . & . & . & . & 21.6\\
 &  & . & . & (-0.7,  6.1) & (18.6, 40.8) & . & . & . & . & . & (12.2, 31.0)\\
Nepal & 48 & 9.3 & 7.9 & 20.4 & 15.2 & 15.7 & 4.4 & 1.8 & . & 2.8 & 12.1\\
 &  & ( 0.3, 18.2) & (-0.4, 16.3) & ( 6.7, 34.1) & ( 3.2, 27.2) & ( 4.0, 27.3) & (-1.9, 10.6) & (-1.9,  5.5) & . & (-1.5,  7.2) & ( 0.8, 23.5)\\
Nigeria & 410 & 21.5 & 26.1 & 15.9 & 9.3 & . & . & 0.2 & . & 4.9 & 26.8\\
 &  & (17.5, 25.5) & (21.8, 30.4) & (12.3, 19.4) & ( 6.4, 12.1) & . & . & (-0.2,  0.7) & . & ( 2.8,  7.0) & (22.5, 31.1)\\
Pakistan 1 & 441 & 23.0 & 21.9 & 29.4 & 26.0 & 22.1 & 11.5 & . & . & 13.2 & 19.6\\
 &  & (15.1, 30.8) & (14.3, 29.4) & (20.9, 37.9) & (18.0, 34.0) & (12.8, 31.3) & ( 5.5, 17.4) & . & . & ( 7.1, 19.4) & (10.4, 28.8)\\
Rwanda & 70 & 38.6 & 10.1 & 18.7 & 21.5 & 5.8 & 7.0 & 5.6 & . & 21.3 & 25.8\\
 &  & (26.9, 50.3) & ( 2.8, 17.3) & ( 9.3, 28.1) & (11.6, 31.4) & ( 0.1, 11.4) & ( 0.9, 13.2) & ( 0.1, 11.1) & . & (11.5, 31.1) & (15.3, 36.3)\\
Sierra Leone 1 & 234 & 53.5 & 37.9 & 14.6 & 7.5 & 4.2 & 3.0 & 0.9 & 4.0 & 20.3 & 5.7\\
 &  & (47.1, 59.9) & (31.6, 44.2) & (10.1, 19.2) & ( 4.2, 10.9) & ( 1.6,  6.8) & ( 0.8,  5.2) & (-0.4,  2.2) & ( 1.4,  6.5) & (15.1, 25.5) & ( 2.8,  8.7)\\
Sierra Leone 2 & 254 & 57.9 & . & . & 17.3 & . & 5.1 & . & 0.0 & 3.5 & 24.8\\
 &  & (50.1, 65.7) & . & . & (11.9, 22.7) & . & ( 2.5,  7.8) & . & ( 0.0,  0.0) & ( 1.3,  5.7) & (19.3, 30.3)\\
Uganda 1 & 289 & 85.1 & . & 3.8 & 24.2 & 1.7 & 1.7 & . & 1.0 & . & 8.0\\
 &  & (80.7, 89.6) & . & ( 1.7,  5.9) & (19.2, 29.2) & ( 0.2,  3.2) & ( 0.2,  3.2) & . & (-0.1,  2.2) & . & ( 4.9, 11.0)\\
Uganda 2 & 319 & 47.3 & 10.7 & 5.0 & 31.0 & 4.1 & 1.6 & 0.3 & . & 10.3 & 6.0\\
 &  & (42.2, 52.5) & ( 7.1, 14.2) & ( 2.7,  7.3) & (25.9, 36.2) & ( 1.9,  6.2) & ( 0.2,  2.9) & (-0.3,  0.9) & . & ( 7.0, 13.7) & ( 3.4,  8.5)\\
All LMICs & . & 40.8 & 17.6 & 12.6 & 19.2 & 8.7 & 4.3 & 1.5 & 1.3 & 11.6 & 17.3\\
 &  & (25.3, 56.3) & ( 8.7, 26.5) & ( 6.4, 18.8) & (13.8, 24.7) & ( 2.4, 14.9) & ( 1.7,  6.8) & (-0.2,  3.3) & (-0.6,  3.2) & ( 6.1, 17.0) & (11.0, 23.7)\\
Russia & 16238 & 36.8 & 13.9 & 5.4 & 29.6 & 6.4 & 3.7 & 10.2 & 1.0 & 21.4 & 5.1\\
 &  & (35.2, 38.4) & (12.8, 15.1) & ( 4.6,  6.1) & (28.1, 31.1) & ( 5.6,  7.3) & ( 3.1,  4.3) & ( 9.2, 11.2) & ( 0.7,  1.4) & (20.1, 22.8) & ( 4.4,  5.8)\\
USA & 462 & 79.3 & . & 39.3 & 46.8 & . & . & . & . & 6.0 & 49.1\\
 &  & (74.6, 84.0) & . & (33.5, 45.0) & (41.0, 52.6) & . & . & . & . & ( 3.4,  8.7) & (43.3, 54.9)\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Table 6 shows percentage of respondents mentioning reasons why they would not take the Covid-19 vaccine. The number of observations and percentage correponds only to people who would NOT take the vaccine. Respondents in all countries could give more than one reason. A 95\% confidence interval is shown between parentheses
\end{tablenotes}
\end{threeparttable}}
\end{table}
\end{landscape}

\newpage

\begin{landscape}\begingroup\fontsize{10}{12}\selectfont

\begin{ThreePartTable}
\begin{TableNotes}
\item Table 7 shows percentage of respondents that mention actors who they would trust the most to help them decide whether to get a COVID-19 vaccine. For all countries the questions was asked regardless if respondent would take a vaccine, would not take it, does not know or does not respond. For India respondents were able to mention more than one actor, for the rest of countries only one actor was allowed. While rows should sum to 100\%, rounding makes number slightly above or below. A 95\% confidence interval is shown between parentheses.
\end{TableNotes}
\begin{longtable}[t]{>{\raggedright\arraybackslash}p{7em}>{\centering\arraybackslash}p{4em}>{\centering\arraybackslash}p{4em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}}
\caption{\label{tab:trust}COVID-19 Vaccination Decision-making: most trusted source}\\
\toprule
\textbf{Study} & \textbf{N} & \textbf{Take vaccine?} & \textbf{Health workers} & \textbf{Government or Ministry of Health} & \textbf{Family or friends} & \textbf{Famous person, religious leader or traditional healers} & \textbf{Newspapers, radio or online groups} & \textbf{Other} & \textbf{Don't know or Refuse}\\
\midrule
\endfirsthead
\caption[]{\label{tab:trust}COVID-19 Vaccination Decision-making: most trusted source \textit{(continued)}}\\
\toprule
\textbf{Study} & \textbf{N} & \textbf{Take vaccine?} & \textbf{Health workers} & \textbf{Government or Ministry of Health} & \textbf{Family or friends} & \textbf{Famous person, religious leader or traditional healers} & \textbf{Newspapers, radio or online groups} & \textbf{Other} & \textbf{Don't know or Refuse}\\
\midrule
\endhead

\endfoot
\bottomrule
\insertTableNotes
\endlastfoot
Burkina Faso & 651 & Yes & 57.1 & 15.1 & 19.6 & 0.9 & 2.0 & 4.8 & 0.4\\
 &  &  & (53.3, 60.9) & (12.4, 17.9) & (16.5, 22.7) & ( 0.2,  1.6) & ( 0.9,  3.1) & ( 3.2,  6.4) & (-0.1,  0.9)\\
Burkina Faso & 325 & No & 40.7 & 8.5 & 16.2 & 3.7 & 1.6 & 25.1 & 4.2\\
 &  &  & (35.3, 46.1) & ( 5.5, 11.6) & (12.1, 20.2) & ( 1.6,  5.7) & ( 0.2,  3.0) & (20.3, 29.8) & ( 2.0,  6.4)\\
Burkina Faso & 976 & All & 51.6 & 12.9 & 18.4 & 1.8 & 1.9 & 11.6 & 1.7\\
 &  &  & (48.5, 54.8) & (10.8, 15.0) & (16.0, 20.9) & ( 1.0,  2.7) & ( 1.0,  2.7) & ( 9.6, 13.6) & ( 0.9,  2.5)\\
Colombia & 756 & Yes & 41.4 & 12.7 & 36.9 & 0.9 & 1.7 & . & 6.3\\
 &  &  & (37.8, 45.0) & (10.3, 15.2) & (33.4, 40.4) & ( 0.2,  1.5) & ( 0.8,  2.7) & . & ( 4.6,  8.1)\\
Colombia & 202 & No & 31.5 & 7.6 & 35.5 & 5.3 & 1.4 & . & 18.8\\
 &  &  & (24.9, 38.1) & ( 3.8, 11.3) & (28.8, 42.1) & ( 2.2,  8.4) & (-0.2,  3.0) & . & (13.2, 24.3)\\
Colombia & 958 & All & 39.3 & 11.6 & 36.6 & 1.8 & 1.7 & . & 8.9\\
 &  &  & (36.2, 42.5) & ( 9.6, 13.7) & (33.5, 39.7) & ( 1.0,  2.6) & ( 0.9,  2.5) & . & ( 7.1, 10.7)\\
Nepal & 1341 & Yes & 44.7 & 0.7 & 36.2 & 16.1 & 0.4 & 0.5 & 1.3\\
 &  &  & (40.9, 48.6) & ( 0.3,  1.1) & (33.5, 39.0) & (13.1, 19.1) & ( 0.0,  0.9) & ( 0.1,  0.8) & ( 0.7,  2.0)\\
Nepal & 48 & No & 30.2 & 2.1 & 18.7 & 16.8 & 0.0 & 1.0 & 31.2\\
 &  &  & (14.6, 45.9) & (-2.1,  6.2) & ( 5.6, 31.7) & ( 4.0, 29.6) & ( 0.0,  0.0) & (-1.1,  3.2) & (13.6, 48.9)\\
Nepal & 1389 & All & 44.2 & 0.8 & 35.6 & 16.1 & 0.4 & 0.5 & 2.4\\
 &  &  & (40.5, 47.9) & ( 0.3,  1.2) & (32.9, 38.3) & (13.3, 18.9) & ( 0.0,  0.8) & ( 0.1,  0.8) & ( 1.5,  3.3)\\
Nigeria & 1424 & Yes & 63.8 & 21.6 & 6.3 & 5.1 & . & 2.6 & 0.6\\
 &  &  & (61.3, 66.3) & (19.4, 23.7) & ( 5.0,  7.5) & ( 4.0,  6.3) & . & ( 1.8,  3.4) & ( 0.2,  1.0)\\
Nigeria & 410 & No & 37.6 & 5.6 & 13.9 & 17.8 & . & 8.5 & 16.6\\
 &  &  & (32.9, 42.3) & ( 3.4,  7.8) & (10.5, 17.3) & (14.1, 21.5) & . & ( 5.8, 11.3) & (13.0, 20.2)\\
Nigeria & 1834 & All & 58.0 & 18.0 & 8.0 & 8.0 & . & 3.9 & 4.2\\
 &  &  & (55.7, 60.2) & (16.2, 19.8) & ( 6.7,  9.2) & ( 6.7,  9.2) & . & ( 3.0,  4.8) & ( 3.3,  5.1)\\
Rwanda & 1152 & Yes & 23.8 & 27.4 & 15.1 & 1.0 & 0.7 & 32.0 & 0.1\\
 &  &  & (21.3, 26.2) & (24.9, 30.0) & (13.0, 17.2) & ( 0.4,  1.5) & ( 0.2,  1.2) & (29.3, 34.7) & (-0.1,  0.2)\\
Rwanda & 70 & No & 10.1 & 15.6 & 12.8 & 2.9 & 0.0 & 53.2 & 5.5\\
 &  &  & ( 2.8, 17.4) & ( 6.9, 24.3) & ( 4.8, 20.8) & (-1.1,  6.9) & ( 0.0,  0.0) & (41.2, 65.1) & ( 0.1, 11.0)\\
Rwanda & 1222 & All & 23.0 & 26.7 & 15.0 & 1.1 & 0.6 & 33.2 & 0.4\\
 &  &  & (20.6, 25.3) & (24.3, 29.2) & (13.0, 17.0) & ( 0.5,  1.7) & ( 0.2,  1.1) & (30.5, 35.8) & ( 0.0,  0.8)\\
Sierra Leone 1 & 836 & Yes & 47.6 & 36.9 & 7.3 & 3.8 & 0.5 & 3.1 & 0.8\\
 &  &  & (44.2, 51.0) & (33.6, 40.2) & ( 5.5,  9.1) & ( 2.5,  5.1) & ( 0.0,  1.0) & ( 1.9,  4.2) & ( 0.2,  1.4)\\
Sierra Leone 1 & 234 & No & 31.1 & 17.1 & 12.1 & 7.7 & 0.5 & 29.4 & 2.2\\
 &  &  & (25.1, 37.1) & (12.2, 21.9) & ( 7.9, 16.3) & ( 4.3, 11.2) & (-0.4,  1.3) & (23.5, 35.3) & ( 0.3,  4.1)\\
Sierra Leone 1 & 1070 & All & 44.0 & 32.5 & 8.4 & 4.7 & 0.5 & 8.9 & 1.1\\
 &  &  & (41.0, 46.9) & (29.7, 35.4) & ( 6.7, 10.0) & ( 3.4,  6.0) & ( 0.1,  0.9) & ( 7.1, 10.6) & ( 0.5,  1.8)\\
Sierra Leone 2 & 1855 & Yes & 94.1 & . & 3.0 & 0.9 & 0.1 & 1.9 & 0.0\\
 &  &  & (92.5, 95.7) & . & ( 2.0,  4.0) & ( 0.3,  1.5) & (-0.1,  0.2) & ( 1.2,  2.7) & ( 0.0,  0.0)\\
Sierra Leone 2 & 254 & No & 54.7 & . & 3.9 & 7.5 & 0.0 & 33.9 & 0.0\\
 &  &  & (46.5, 62.9) & . & ( 1.4,  6.5) & ( 2.9, 12.0) & ( 0.0,  0.0) & (26.3, 41.4) & ( 0.0,  0.0)\\
Sierra Leone 2 & 2109 & All & 89.3 & . & 3.1 & 1.7 & 0.0 & 5.8 & 0.0\\
 &  &  & (87.2, 91.5) & . & ( 2.2,  4.1) & ( 0.8,  2.6) & ( 0.0,  0.1) & ( 4.4,  7.2) & ( 0.0,  0.0)\\
Uganda 2 & 1045 & Yes & 38.3 & 36.5 & 9.8 & 7.0 & 5.0 & 3.5 & 0.0\\
 &  &  & (35.5, 41.1) & (33.5, 39.4) & ( 7.9, 11.6) & ( 5.4,  8.6) & ( 3.6,  6.3) & ( 2.5,  4.6) & ( 0.0,  0.0)\\
Uganda 2 & 319 & No & 24.5 & 19.1 & 8.5 & 7.8 & 7.5 & 32.0 & 0.6\\
 &  &  & (19.9, 29.0) & (14.5, 23.7) & ( 5.4, 11.5) & ( 4.8, 10.9) & ( 4.5, 10.5) & (26.7, 37.3) & (-0.2,  1.5)\\
Uganda 2 & 1364 & All & 35.0 & 32.4 & 9.5 & 7.2 & 5.6 & 10.2 & 0.1\\
 &  &  & (32.7, 37.4) & (29.9, 35.0) & ( 7.9, 11.1) & ( 5.8,  8.6) & ( 4.3,  6.8) & ( 8.6, 11.8) & (-0.1,  0.3)\\
All LMICs & . & Yes & 51.3 & 21.6 & 16.8 & 4.5 & 1.5 & 6.9 & 1.2\\
 &  &  & (33.7, 68.9) & ( 9.4, 33.8) & ( 5.7, 27.9) & ( 0.1,  8.8) & (-0.1,  3.1) & (-3.4, 17.2) & (-0.6,  3.0)\\
All LMICs & . & No & 32.5 & 10.8 & 15.2 & 8.7 & 1.6 & 26.1 & 9.9\\
 &  &  & (21.8, 43.3) & ( 4.8, 16.8) & ( 7.4, 23.0) & ( 4.0, 13.4) & (-0.9,  4.1) & (10.2, 42.1) & ( 0.6, 19.2)\\
All LMICs & . & All & 48.1 & 19.3 & 16.8 & 5.3 & 1.5 & 10.6 & 2.4\\
 &  &  & (31.6, 64.5) & ( 8.3, 30.3) & ( 6.1, 27.5) & ( 1.0,  9.6) & (-0.2,  3.3) & ( 0.7, 20.5) & (-0.1,  4.9)\\
Russia & 5887 & Yes & 47.1 & 24.4 & 16.5 & 2.0 & 4.1 & 5.8 & .\\
 &  &  & (44.6, 49.7) & (22.2, 26.7) & (14.6, 18.5) & ( 1.2,  2.8) & ( 3.1,  5.1) & ( 4.5,  7.0) & .\\
Russia & 16238 & No & 31.1 & 6.9 & 33.1 & 2.2 & 5.3 & 21.3 & .\\
 &  &  & (29.6, 32.7) & ( 6.1,  7.8) & (31.5, 34.7) & ( 1.7,  2.8) & ( 4.5,  6.0) & (20.0, 22.7) & .\\
Russia & 22125 & All & 36.0 & 12.3 & 28.1 & 2.2 & 4.9 & 16.6 & .\\
 &  &  & (34.7, 37.3) & (11.3, 13.2) & (26.8, 29.3) & ( 1.7,  2.6) & ( 4.3,  5.5) & (15.6, 17.6) & .\\
USA & 1313 & Yes & 38.1 & 33.0 & 8.7 & 1.7 & . & 18.6 & 0.0\\
 &  &  & (34.8, 41.5) & (29.8, 36.1) & ( 6.7, 10.7) & ( 0.7,  2.6) & . & (16.1, 21.1) & ( 0.0,  0.0)\\
USA & 462 & No & 25.3 & 21.3 & 18.7 & 4.2 & . & 30.3 & 0.2\\
 &  &  & (20.4, 30.3) & (16.6, 26.0) & (13.9, 23.4) & ( 1.6,  6.9) & . & (25.0, 35.6) & (-0.2,  0.7)\\
USA & 1775 & All & 34.5 & 29.7 & 11.5 & 2.4 & . & 21.9 & 0.1\\
 &  &  & (31.7, 37.3) & (27.0, 32.3) & ( 9.5, 13.4) & ( 1.4,  3.4) & . & (19.5, 24.2) & (-0.1,  0.2)\\*
\end{longtable}
\end{ThreePartTable}
\endgroup{}
\end{landscape}
\newpage

\begin{figure}[!ht]
\caption{Trusted actors and institutions, broken down by gender \label{fig:genderhist}}

\includegraphics{paper_files/figure-latex/genderhist-1.pdf}

\scriptsize{Figure 4 shows histograms of actors and institutions that respondents say they would trust most to help them decide whether or not to take the COVID-19 vaccine. Respondents were only permitted to select one most trusted  actor or institution. Responses are broken down by acceptance of the COVID-19 vaccine.}
\end{figure}

\pagebreak

\begin{table}[!h]

\caption{\label{tab:dmeans}Differences in means}
\centering
\fontsize{10}{12}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{cccccc}
\toprule
\textbf{Estimate} & \textbf{Std.error} & \textbf{P.value} & \textbf{Degrees of freedom} & \textbf{Baseline category} & \textbf{Variable}\\
\midrule
0.04 & 0.01 & 0.00 & 10 & Male & Gender\\
0.00 & 0.01 & 0.71 & 10 & 55+ & Age\\
0.02 & 0.03 & 0.41 & 10 & Up to secondary & Education\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Table 8 shows the results of subgroup mean differences. Subgroup differences were generated considering only LMICs. The differences in means for gender and age do not include the Uganda 1 study, which only included female respondents under the age of 55. p-values come from a two-sided t-test from a linear regression.
\end{tablenotes}
\end{threeparttable}
\end{table}

\clearpage

\begin{table}

\caption{Observations and missingness patterns}
\centering
\fontsize{10}{12}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{lrrrrr}
\toprule
Country & N obs & Take vaccine & Gender & Education & Age\\
\midrule
Burkina Faso & 977 & 1.00 & 0.00 & 0.00 & 0.88\\
Colombia & 1,012 & 0.95 & 0.00 & 0.00 & 0.32\\
India & 3,348 & 1.00 & 0.00 & 0.78 & 0.00\\
Mozambique & 862 & 0.98 & 0.00 & 0.04 & 0.00\\
Nepal & 1,389 & 1.00 & 0.05 & 1.00 & 0.05\\
Nigeria & 1,868 & 0.98 & 0.00 & 1.00 & 0.00\\
Pakistan 1 & 1,633 & 0.99 & 0.00 & 0.01 & 0.00\\
Pakistan 2 & 1,492 & 1.00 & 1.00 & 0.00 & 1.00\\
Russia & 22,125 & 1.00 & 0.00 & 0.00 & 0.00\\
Rwanda & 1,355 & 0.90 & 0.00 & 0.00 & 0.00\\
Sierra Leone 1 & 1,070 & 1.00 & 0.00 & 0.03 & 0.00\\
Sierra Leone 2 & 2,110 & 1.00 & 0.00 & 0.00 & 0.01\\
Uganda 1 & 3,362 & 0.94 & 0.00 & 0.19 & 0.05\\
Uganda 2 & 1,366 & 1.00 & 0.00 & 0.00 & 0.00\\
USA & 1,959 & 0.91 & 0.00 & 0.00 & 0.00\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Table 9 show the percentage of observations that are not missing values for each variable included in Figure 1.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\pagebreak

\hypertarget{appendixb}{%
\subsection*{Appendix B: Question wording and answer options per study}\label{appendixb}}
\addcontentsline{toc}{subsection}{Appendix B: Question wording and answer options per study}

\begin{table}[!h]

\caption{\label{tab:q1}Question wording and answer options: vaccine acceptance}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{30em}>{\raggedright\arraybackslash}p{20em}}
\toprule
\textbf{Study} & \textbf{Question Fig. 1} & \textbf{Recoding Fig. 1}\\
\midrule
Burkina Faso & If a COVID-19 vaccine became available in Burkina Faso, would you take it? & Yes; No; Don't know; Refuse\\
Colombia & If a COVID-19 vaccine became available in Colombia, would you take it? & Yes; No\\
India & If a vaccine for coronavirus gets introduced, would you like to get it? & Yes, only for free; Yes, even if I have to pay; No\\
Mozambique & When a COVID-19 vaccine becomes available in the future, would you take it? & Yes; No; Refuse\\
Nepal & Should a vaccine against COVID become available in Nepal, would you take it? & Yes; No\\
Nigeria & If a COVID-19 vaccine became available in Niger, would you take it? & Yes/Agree; No/Disagree\\
Pakistan 1 & If a vaccine against the coronavirus becomes available, do you plan to get vaccinated? & Yes; No; Don't know; Refuse\\
Pakistan 2 & If a vaccine against the coronavirus becomes available, do you plan to get vaccinated? & Absolutely yes; Yes; Neutral; No; Absolutely no\\
Russia & If a COVID-19 vaccine became available in Russia, would you take it? & Yes, if a Russian vaccine will be available; Yes, if an imported vaccine will be available; No; Not sure\\
Rwanda & If a COVID-19 vaccine became available in Rwanda, would you take it? & Yes; No\\
Sierra Leone 1 & If a COVID-19 vaccine became available in Sierra Leone, would you take it? & Yes; No\\
Sierra Leone 2 & Should a vaccine against COVID become available in Sierra Leone, would you take it? & Yes; No\\
Uganda 1 & When a COVID-19 vaccine becomes available in Uganda, would you take it? & Yes; No\\
Uganda 2 & If a COVID-19 vaccine becomes available in Uganda, would you take it? & Yes; No; Don't know; Refuse\\
USA & If a COVID-19 vaccine becomes available in the United States, would you take it? & Definitely yes; Probably yes; Probably not; Definitely not, Refuse\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Table 10 presents question wording and answer options from answers used in Figure 1 to get estimated vaccine acceptance. Answer options are separated by a semicolon. In India options 'Yes, only for free' and 'Yes, even if I have to pay' are both recoded as 'Yes'. In Pakistan 2, 'Absolutely yes' is recoded as 'Yes', 'Neutral' is recoded as 'Don't know' and 'Absolutely no' is recoded as 'No'. In Russia, 'Yes, if a Russian vaccine will be available' and 'Yes, if an imported vaccine will be available' are both recoded as 'Yes'. In USA 'Definitely yes' and 'Probably yes' are recoded as 'Yes', and 'Probably not' and 'Definitely not' are recoded as 'No'
\end{tablenotes}
\end{threeparttable}}
\end{table}

\begin{table}[!h]

\caption{\label{tab:q2}Question wording and answer options: reasons to take vaccine}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}}
\toprule
\textbf{Study} & \textbf{Question Tab. 2} & \textbf{Protection: self} & \textbf{Protection: family} & \textbf{Protection: community}\\
\midrule
Burkina Faso & Why would you take it? & Protection: self (general); Protection: self, chronic condition & Protection: family & Protection: community\\
Colombia & Why would you take it? & Protection: self (general); Protection: self, chronic condition & Protection: family & Protection: community\\
Mozambique & Why would you take it? & I want to protect myself from having COVID-19 in the future & I want to protect my family/members of my household against having COVID-19 in the future & I want to protect my community against having COVID-19 in the future\\
Nepal & Why would you take it? & Protection: self (general); Protection: self, chronic condition/ vulnerable to covid & Protection: family & Protection: community\\
Nigeria & Why would you take it? & I want to protect myself from having COVID-19 in the future & I want to protect my family/members of my household against having COVID-19 in the future & I want to protect my community against having COVID-19 in the future\\
Russia & Why would you take it? & Protection: self & Protection: family & Protection: community\\
Rwanda & Why would you take it? & Protection: self (general); Protection: self, chronic condition & Protection: family & Protection: community\\
Sierra Leone 1 & Why would you take it? & Protection: self (general); Protection: self, chronic condition & Protection: family & Protection: community\\
Sierra Leone 2 & Why would you take it? & I will take a vaccine to protect myself from having COVID-19 in the future & I will take a vaccine to protect my family/members of my household against having COVID-19 in the future & I will take a vaccine to protect my community against having COVID-19 in the future\\
Uganda 1 & Why would you take it? & Protect myself from having COVID-19 & Protect my family/members of my household against COVID-19 & Protect my community against COVID-19\\
Uganda 2 & Why would you take it? & Protection: self (general); Protection: self, chronic condition/ vulnerable to Covid & Protection: family & Protection: community\\
USA & Why would you take it? & To protect myself from COVID-19 infection & To protect my family from COVID-19 infection & To protect my community from COVID-19 infection\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Table 11 presents question wording and answer options used in Table 2 to get an estimated percentage of reasons to take the COVID-19 vaccine. Columns 'Protection: self', 'Protection: family' and  'Protection: community' show the answer options that were recoded in each category. Answer options are separated by a semicolon.
\end{tablenotes}
\end{threeparttable}}
\end{table}

\begin{landscape}\begin{table}[!h]

\caption{\label{tab:q3}Question wording and answer options: reasons not to take the vaccine}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}}
\toprule
\textbf{Study} & \textbf{Question Fig. 2} & \textbf{Concerned about side effects} & \textbf{Concerned about getting COVID-19 from the vaccine} & \textbf{Not concerned about getting seriously ill} & \textbf{Doesn't think vaccines are effective} & \textbf{Doesn't think COVID-19 outbreak is as serious as people say} & \textbf{Doesn't like needles} & \textbf{Allergic to vaccines} & \textbf{Won't have time to get vaccinated} & \textbf{Mentions a conspiracy theory} & \textbf{Other reasons}\\
\midrule
Burkina Faso & Why would you not take it? & . & Concerned about getting coronavirus from the vaccine & Not concerned about getting seriously ill & Doesn't think vaccines work very well & Coronavirus outbreak is not as serious as people say & Doesn't like needles & Allergic to vaccines & Won't have time to get vaccinated & Conspiracy theory & Other reason\\
Colombia & Why would you not take it? & . & Concerned about getting coronavirus from the vaccine & Not concerned about getting seriously ill & Doesn't think vaccines work very well & Coronavirus outbreak is not as serious as people say & Doesn't like needles & Allergic to vaccines & Won't have time to get vaccinated & Conspiracy theory & Other reason; Already immune; Doesn't have symptoms\\
Mozambique & Why would you not take it? & . & . & I am not concerned about the risk associated with me/my relatives getting COVID-19 & I don't think vaccines are effective & The coronavirus outbreak is not as serious as people say it is & I don't like needles & . & I won't have time to go get vaccinated & . & Other\\
Nepal & Why would you not take it? & I would be concerned about the side effects from the vaccine & I would be concerned about getting infected with coronavirus from the vaccine & I'm not concerned about getting seriously ill from the virus & I don't think vaccines work very well & The coronavirus outbreak is not as serious as people say it is & I don't like needles & I'm allergic to vaccines & I won't have time to go get vaccinated & I think there is a conspiracy theory with vaccinations & Other\\
Nigeria & Why would you not take it? & I would be concerned about the side effects from the vaccine & I would be concerned about getting infected with coronavirus from the vaccine & I'm not concerned about getting seriously ill from the virus & I don't think vaccines work very well & The coronavirus outbreak is not as serious as people say it is & I don't like needles & I'm allergic to vaccines & I won't have time to go get vaccinated & The virus is a hoax / does not exist; The vaccine has microchips/ tracking devices & Other; Religious / community leaders advising me not to take it\\
Pakistan 1 & Why would you not take it? & I am concerned about side effects from the vaccine & I would be concerned about getting infected with coronavirus from the vaccine & I don't consider myself or my family members at risk of getting seriously ill & I don't think the vaccine would work well & The coronavirus infection is just like the flu and doesn't warrant a vaccine & I don't like needles & . & . & Vaccines are just Western conspiracies to stunt the growth of Muslims & Muslims are prohibited from taking a vaccine before a disease is contracted\\
Russia & Why would you not take it? & Afraid of side effects & Afraid of getting infected with coronavirus from the vaccine & Not concerned with getting seriously ill from the virus & Don't think vaccines are effective & Coronavirus outbreak is not as serious as people say it is & Afraid of needles & Can get allergic reaction & Don't have time to get vaccinated & Hoax: Virus don't exist; Hoax: Virus was designed so vaccines won't work; Profit motivation: pharmaceutical companies; Control: contain things that control our minds; Global politics: China can take advantage & Other; I already had coronavirus and don't need a vaccine\\
Rwanda & Why would you not take it? & . & Concerned about getting coronavirus from the vaccine & Not concerned about getting seriously ill & Doesn't think vaccines work very well & Coronavirus outbreak is not as serious as people say & Doesn't like needles & Allergic to vaccines & Won't have time to get vaccinated & Conspiracy theory & Other reason; Already immune; Doesn't have symptoms\\
Sierra Leone 1 & Why would you not take it? & . & Concerned about getting coronavirus from the vaccine & Not concerned about getting seriously ill & Doesn't think vaccines work very well & Coronavirus outbreak is not as serious as people say & Doesn't like needles & Allergic to vaccines & Won't have time to get vaccinated & Conspiracy theory & Other reason\\
Sierra Leone 2 & Why would you not take it? & I will not take a vaccine because I am concerned about side effects & I will not take a vaccine because I am not concerned about the risk associated with me/my relatives getting COVID-19ne is & I will not take a vaccine because I am not concerned about the risk associated with me/my relatives getting COVID-19 & I will not take a vaccine because they are not effective & . & I will not take a vaccine because I don't like needles & . & I will not take a vaccine because I don't have time & I will not take a vaccine because I don't think COVID exists & I will not take a vaccine because of other reasons; I will not take a vaccine because my community objects it; I will not take a vaccine because I don't have symptoms; I will not take a vaccine because I am immune; I will not take a vaccine because it is provided by foreign aid; I will not take a vaccine because I don't know what a vaccine is\\
Uganda 1 & Why would you not take it? & Concerned about the side effects from the vaccine/vaccines & I am not worried that my relatives will get COVID-19 & I am not worried that my relatives will get COVID-19 & I don't think vaccines are effective & Coronavirus is not as serious as people say it is & I don't like needles & . & I won't have time to go get vaccinated & . & Other; It will cost too much\\
Uganda 2 & Why would you not take it? & I would be concerned about the side effects from the vaccine & I would be concerned about getting infected with coronavirus from the vaccine & I'm not concerned about getting seriously ill from the virus & I don't think vaccines work very well & The coronavirus outbreak is not as serious as people say it is & I don't like needles & I'm allergic to vaccines & I won't have time to go get vaccinated & I think there is a conspiracy theory with vaccinations & Other\\
USA & Why would you not take it? & I am concerned about possible side effects & . & I am not concerned about getting the virus & I don't think vaccines are effective & . & . & . & . & Mentions a conspiracy theory (recoded from responses in "Other" category) & Cost or difficulty of getting the vaccine\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Table 12 presents question wording and answer options used in Figure 2 to get an estimated percentage of reasons not to take the COVID-19 vaccine. Columns 3-10 show the answer options that were recoded in each category. Answer options are separated by a semicolon.
\end{tablenotes}
\end{threeparttable}}
\end{table}
\end{landscape}

\begin{landscape}\begin{table}[!h]

\caption{\label{tab:q4}Question wording and answer options: trusted actors and institutions}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{20em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{10em}}
\toprule
\textbf{Study} & \textbf{Question Fig. 3} & \textbf{Health workers} & \textbf{Government or Ministry of Health} & \textbf{Family or friends} & \textbf{Famous person, religious leader or traditional healers} & \textbf{Newspapers, radio or online groups} & \textbf{Other}\\
\midrule
Burkina Faso & Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available? & Doctors or other staff at a community health clinic & Advice from Ministry of Health & Family members; Friends you see and talk to; Friends you-'ve made online & Famous person; Religious leaders; Traditional Healers & Traditional media (newspaper, radio);Online medical discussion groups & Other/ Someone else\\
Colombia & Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available? & Doctors or other staff at a community health clinic & Advice of the Instituto Nacional de Salud & Family members; Friends you see and talk to; Friends you've made online & Famous person; Religious leaders; Traditional Healers & Traditional media (newspaper, radio);Online medical discussion groups & Other/ Someone else\\
Nepal & Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available? & Doctors or other staff at a community health clinic & Advice of the national health service & Family members; Friends you see and talk to & Famous person; Religious leaders; Traditional healers & Traditional media (newspaper, radio); Online medical discussion groups & None of these/ Someone else; Advice of the WHO\\
Nigeria & Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available? & Medical professionals like doctors & NCDC; Government officials & Family members and friends & Religious leaders & . & Some other sourcer; Other community leaders\\
Russia & Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available? & Health workers & Government; Health Ministry & Family; Friends & Famous people; Religious leaders & Traditional media; Online medical discussion groups & Other\\
Rwanda & Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available? & Doctors or other staff at a community health clinic & Advice of the Ministry of Health & Family members; Friends you see and talk to; Friends you’ve made online & Famous person; Religious leaders; Traditional healers & Traditional media (newspaper, radio); Online medical discussion groups & None of these/ Someone else; Myself\\
Sierra Leone 1 & Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available? & Doctors or other staff at a community health clinic & Advice of the Ministry of Health and Sanitation & Family members; Friends you see and talk to; Friends you’ve made online & Famous person; Religious leaders; Traditional healers & Traditional media (newspaper, radio); Online medical discussion groups & None of these/ Someone else; I do trust NOBODY\\
Sierra Leone 2 & Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available? & A doctor, nurse or other staff at a community health clinic; A country medical staff & . & Family; Friends you see and talk to; Friends you’ve made online & A famous person; A religious leader; A traditional healer & Online medical discussion groups & None of these/ Someone else\\
Uganda 2 & Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available? & Doctors or other staff at a community health clinic & Advice of the national health service & Family; Friends you see and talk to; Friends you’ve made online & Famous person; Religious leaders; Traditional healers & Traditional media (newspaper, radio); Online medical discussion groups & None of these; Someone else\\
USA & Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available? & Your doctor or healthcare provider & Donald Trump; Anthony Fauci; Your state's governor; Local public health authority & Friends or family & Your pastor, priest, or other religious leader & . & Other; Joe Biden\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Table 13 presents question wording and answer options used in Figure 3 to get the percentage of respondents mentioning each actor or instituion that they would trust to decide whether to get the COVID-19 vaccine. Columns 3-8 show the answer options that were recoded in each category. Answer options are separated by a semicolon.
\end{tablenotes}
\end{threeparttable}}
\end{table}
\end{landscape}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{appendix-c-additional-contributors}{%
\subsection*{Appendix C: Additional contributors}\label{appendix-c-additional-contributors}}
\addcontentsline{toc}{subsection}{Appendix C: Additional contributors}

We thank Sellu Kallon and Sarah Ryan for valuable intellectual contributions and research assistance.

IPA would like to thank staff in Burkina Faso, Colombia, Rwanda, Sierra Leone and the United States for their intellectual contributions, research assistance, and support throughout the RECOVR survey: Achille Mignondo Tchibozo, Michael Rosenbaum, Hugo Salas, Filippo Cuccaro, Jean Leodomir Habarimana Mfura, Doug Kirke-Smith, Savanna Henderson, Shahana Hirji, Kyle Holloway, Margarita Cabra.

Russia team would like to thank staff at Online Market Intelligence survey agency and Kirill Chmel and Vladimir Zabolotsky for their intellectual contributions and research assistance.

\newpage

\hypertarget{appendixa}{%
\subsection*{Appendix D: Sample descriptions}\label{appendixa}}
\addcontentsline{toc}{subsection}{Appendix D: Sample descriptions}

The case history data for all countries in our sample is extracted from the Johns Hopkins University Center for Systems Science and Engineering (JHU CSSE) database.\footnote{Dong, E., Du, H., \& Gardner, L. (2020). An interactive web-based dashboard to track COVID-19 in real time. The Lancet infectious diseases, 20(5), 533-534.}

\hypertarget{burkina-faso-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}{%
\subsubsection*{Burkina Faso, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}\label{burkina-faso-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}}
\addcontentsline{toc}{subsubsection}{Burkina Faso, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}

\textbf{COVID-19 Experience}

\begin{itemize}
\item First confirmed case: March 9, 2020 
\item Number of confirmed cases 2,335 as of  October 15, 2020 
\item Number of deaths:  65 as of October 15, 2020
\end{itemize}

\textbf{Target Population}: A random sample of all adults with mobile phone numbers in the country, based on national communications authority number allocation plans.

\textbf{Original Study Design:} N/A

\textbf{COVID-19 Survey Design:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share for a two-round panel survey.

\emph{Sampling Frame:} All mobile phone numbers in Burkina Faso.

\emph{Survey Dates:} October 15 to December 4, 2020 (Round 1 June 6-15, 2020)

\emph{Sample size, tracking and attrition:} Sample includes 977 respondents from the second round of a panel. In the first round conducted between June 6 to 15, 2020, 1,356 individual surveys were contacted through Random Digit Dialing (RDD) from the sampling frame of all mobile phone numbers in Burkina Faso. 2,313 working numbers yielded 1,383 eligible respondents for a completion rate of 98\% of eligible respondents.

\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.

\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15608, and the Burkina Faso Institutional Ethics Committee for Health Sciences Research, approval A13-2020.

\hypertarget{colombia-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}{%
\subsubsection*{Colombia, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}\label{colombia-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}}
\addcontentsline{toc}{subsubsection}{Colombia, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}

\textbf{COVID-19 Experience}

\begin{itemize}
\item First confirmed case: March 6, 2020
\item Number of confirmed cases:  456,689 as of August 15, 2020
\item Number of deaths:  14,810 as of August 15, 2020
\end{itemize}

\textbf{Target Population}: A random sample of all numerically possible mobile phone numbers in the country, based on national communications authority number allocation plans.

\textbf{Original Study Design:} N/A

\textbf{COVID-19 Survey Design:}

\emph{Sampling Frame:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share.

\emph{Survey Dates:} August 15-25, 2020 (Round 1 May 8-15, 2020)

\emph{Sample size, tracking and attrition:} Sample includes 1,012 respondents contacted in the second round of a panel of 1,507.

\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.

\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15582.

\hypertarget{india-coping-with-covid-19-in-slums-evidence-from-india-subnational-sample-nova-school-of-business-and-economics-the-institute-for-fiscal-studies-university-of-st.-andrews}{%
\subsubsection*{India, Coping with COVID-19 in Slums: Evidence from India Subnational sample, Nova School of Business and Economics, The Institute for Fiscal Studies, University of St.~Andrews}\label{india-coping-with-covid-19-in-slums-evidence-from-india-subnational-sample-nova-school-of-business-and-economics-the-institute-for-fiscal-studies-university-of-st.-andrews}}
\addcontentsline{toc}{subsubsection}{India, Coping with COVID-19 in Slums: Evidence from India Subnational sample, Nova School of Business and Economics, The Institute for Fiscal Studies, University of St.~Andrews}

\textbf{COVID-19 Experience}

\begin{itemize}
\item First confirmed case: January 30, 2020
\item Number of confirmed cases: 198,370 as of June 1, 2020 
\item Number of deaths: 5,608 as of June 1, 2020 
\end{itemize}

\textbf{Target Population}: Random subset of slum populations in Lucknow and Kanpur, Uttar Pradesh, India. Socio-economic variables are only collected for a representative sample of the population relying on community toilets or open defecation to fulfil their sanitation needs.

\textbf{Original Study Design:} Randomized controlled trial, with complete census of households within 142 slums (September to December 2017), and a series of household and caretaker surveys, objective measurements, incentivized behavioural measurements, and a Structured Community Activity, collected for a sub-set of 100 slums between April 2018 and September 2019.

\emph{Intervention:} Catchment areas of CTs were randomly allocated to two interventions. The first intervention aimed at community toilet improvements by offering caretakers the choice of a grant to be spent for improvements in the facility. Following the grant, caretakers were offered a large financial reward conditional on the cleanliness of the facility. The second intervention added to this CT improvement awareness creation among potential users through face-to-face information sessions, leaflets, monthly reminders using voice messages sent to mobile phones, and posters hung in the CTs.

\emph{Sampling Frame:} A two-step sampling was applied, first, study households from the main study sample were sampled, then households from the whole slum population were added.

\emph{Survey Dates:}
Baseline: June to July 2020, Follow-up 1: October toNovember 2020, Follow-up 2: December 16, 2020 toJanuary 18, 2021.

\emph{Sample size, tracking and attrition:} 3,991 households, with a mean of 28 households per cluster (142). Non-response Baseline: 25\%, Attrition rate Baseline to Follow-up (1 and 2): 13\%, Randomly selected replacement households for Follow-up (1 and 2): 1,277.

\emph{Sampling Weights:} Included

\emph{IRB Approval:} Approval was secured from London School of Economics (REC ref. 1132). The pre-analysis plan was registered on the AEA RCT registry (RCT ID AEARCTR-0006564).

\hypertarget{mozambique-subnational-sample-international-growth-center-nova-school-of-business-and-economics}{%
\subsubsection*{Mozambique Subnational sample, International Growth Center, Nova School of Business and Economics}\label{mozambique-subnational-sample-international-growth-center-nova-school-of-business-and-economics}}
\addcontentsline{toc}{subsubsection}{Mozambique Subnational sample, International Growth Center, Nova School of Business and Economics}

\textbf{COVID-19 Experience}

\begin{itemize}
\item First confirmed case: March 22, 2020
\item Number of confirmed cases:  12,777 as of October 30, 2020 
\item Number of deaths:  91 as of October 30, 2020
\end{itemize}

\textbf{Target Population}: Microentrepreneurs in urban markets of Maputo and household heads from the province of Cabo Delgado.

\textbf{Original Study Design:} Initial data were collected in-person in two different studies. For microentrepreneurs in Maputo, the data were collected between October 2013 and April 2014 (baseline), and between July and November 2015 (endline).\footnote{Original study: \url{http://catiabatista.org/bsv_mm_urban.pdf}} For household heads in Cabo Delgado, the data were collected in-person between August and September 2016 (baseline), and between August and September 2017 (endline).\footnote{Original study: \url{https://www.aeaweb.org/articles?id=10.1257/aer.20190842}}

\emph{Intervention:} The first study was dedicated to analyzing the impacts of interventions targeting microentrepreneurs in urban markets on financial inclusion and literacy. The second study focused on the role of information to counteract the political resource curse after a substantial natural gas discovery.

\emph{Sampling Frame:} The first initial sample was selected by in-field random sampling in 23 urban and periurban markets in Maputo and Matola. Stratification was based on the gender of the respondent and on the type of establishment (stall vs.~store). The second initial sample was selected to be representative of 206 communities in the province of Cabo Delgado, randomly drawn from the list of all 421 polling locations in the sampling frame, stratified on urban, semiurban, and rural areas. This survey in this paper was done by phone.

\emph{Survey Dates:} October 30 to November 21, 2020 (Maputo) and November 6 to November 30, 2020 (Pemba).

\emph{Sample size, tracking and attrition:} 554 microentrepreneurs from Maputo and 308 households from Cabo Delgado.

\emph{Sampling Weights:} N/A

\textbackslash emph\{IRB Approval: The approval was secured from Universidade Nova de Lisboa on July 14, 2020.

\hypertarget{nepal-western-terai-panel-survey-wtps-subnational-sample-yale-university-yale-research-initiative-on-innovation-and-scale-y-rise}{%
\subsubsection*{Nepal, Western Terai Panel Survey (WTPS) Subnational sample, Yale University, Yale Research Initiative on Innovation and Scale (Y-RISE)}\label{nepal-western-terai-panel-survey-wtps-subnational-sample-yale-university-yale-research-initiative-on-innovation-and-scale-y-rise}}
\addcontentsline{toc}{subsubsection}{Nepal, Western Terai Panel Survey (WTPS) Subnational sample, Yale University, Yale Research Initiative on Innovation and Scale (Y-RISE)}

\textbf{COVID-19 Experience}

\begin{itemize}
\item First confirmed case: January 23, 2020

\item Number of confirmed cases:  233,452 as of December 1, 2020 
\item Number of deaths:   1,529 as of December 1, 2020
\end{itemize}

\textbf{Target Population}: Rural households in the districts of Kailali and Kanchanpur.

\textbf{Original Study Design:} Initial baseline data was collected in-person in July of 2019, and 5 rounds of phone survey data were collected between August 12, 2019 and January 4, 2020.

\emph{Sampling Frame:} The phone survey sample includes 2,636 rural households in the districts of Kailali and Kanchanpur, which represent the set of households that responded to phone surveys from an original sample of 2,935 households. This sample was constructed by randomly sampling 33 wards from 15 of the 20 sub-districts in Kailali and Kanchanpur and selecting a random 97 villages from within those wards. At the time of baseline data collection in July of 2019, 7 of these 97 villages were dropped from the sample due to flooding. Households belong to the bottom half of the wealth distribution in these villages, as estimated by a participatory wealth ranking exercise with members of the village.

\emph{Survey Dates:}December 1st - December 11, 2020

\emph{Sample size, tracking and attrition:} 1,392 households

\emph{IRB Approval:} This research was approved via Yale University IRB Protocol 2000025621.

\hypertarget{nigeria-subnational-sample-wzb-berlin-social-science-center-university-of-illinois-chicago}{%
\subsubsection*{Nigeria Subnational sample, WZB Berlin Social Science Center, University of Illinois Chicago}\label{nigeria-subnational-sample-wzb-berlin-social-science-center-university-of-illinois-chicago}}
\addcontentsline{toc}{subsubsection}{Nigeria Subnational sample, WZB Berlin Social Science Center, University of Illinois Chicago}

\textbf{COVID-19 Experience}

\begin{itemize}
\item First confirmed case: February 28, 2020
\item Number of confirmed cases: 65,693 as of November 18, 2020 
\item Number of deaths:  1,163 as of November 18, 2020 
\end{itemize}

\textbf{Target Population}: Christian and Muslim men and women, age 18 and above, living in Kaduna state, Nigeria.

\textbf{Original Study Design}: Initial data was collected from a subset of the sample in December 2019 (in person survey) and July - Aug 2020 (phone survey) as part of an experiment testing the effects of a brief radio program on inter-religious animus. A random walk procedure and random sampling were used within households to recruit a representative sample of adults in Kaduna town. The rest of the sample was recruited for the study in Aug 2020 by purchasing phone lists for residents of Kaduna State.

\emph{Intervention:} The study examines the effects of a radio program and a TV drama on inter-religious animus. The subset of the sample in the radio study was randomly assigned to listen to a brief radio program on one of the following topics: (1) an inter-religious storyline, (2) an intra-religious storyline, and (3) a message about maintaining safe health practices. All respondents in the sample participated in a study examining the effect of viewing an inter-religious storyline unfolding over a full season of a popular TV drama, Dadin Kowa. The season aired from Aug - Oct 2020. A third of the sample were encouraged to watch Dadin Kowa, a third were encouraged to watch the TV station Africa Magic Hausa at the same time Dadin Kowa aired, and a third were in the treatment-as-usual group. All participants received a weekly incentivized SMS quiz from Aug - Oct 2020.

\textbf{COVID-19 Survey Design:} This survey is not primarily about COVID-19, but was designed as an endline survey to follow the TV drama intervention described above. The goal of this survey is to measure a range of attitudinal outcomes related to Christian-Muslim relations (including prejudice, intergroup threat perceptions, dehumanization, and support for the use of violence, among others). We included nine of the standardized COVID-19 vaccine-related questions collected specifically for this vaccine acceptance study in the final module of the endline survey.

\emph{Sampling Frame:} 950 respondents in the sample were recruited in person through a random sampling procedure in the Kaduna metropolitan area (pre-COVID). The remaining 1,700 respondents were recruited into the study over the phone from lists of phone numbers of Kaduna state residents that were purchased from a private vendor.

\emph{Survey Dates:} November 18 - December 18, 2020.

\emph{Sample size, tracking and attrition:} All 1,834 individuals who completed the endline survey are included.

\emph{Sampling Weights:} N/A

\emph{IRB Approval:} This study was reviewed by the IRB at the University of Pennsylvania (Protocol 834548), and it was determined on November 20, 2019 to meet the criteria for review exemption (45 CFR 46.104, category \#2).

\hypertarget{pakistan}{%
\subsubsection*{Pakistan}\label{pakistan}}
\addcontentsline{toc}{subsubsection}{Pakistan}

\textbf{COVID-19 Experience}

\begin{itemize}
\item March 6: First confirmed case: February  26, 2020 
\item Number of confirmed cases:  271,887 as of July 24, 2020 
\item Number of deaths:  5,787 as of July 24, 2020 
\end{itemize}

\hypertarget{pakistan-economic-vulnerability-assessment-eva-subnational-sample-sheikhupura-police-study-sample-institute-of-development-and-economic-alternatives-lahore-university-of-management-science-london-school-of-economics-princeton-university}{%
\subsubsection*{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample, Sheikhupura Police Study Sample, Institute of Development and Economic Alternatives, Lahore University of Management Science, London School of Economics, Princeton University}\label{pakistan-economic-vulnerability-assessment-eva-subnational-sample-sheikhupura-police-study-sample-institute-of-development-and-economic-alternatives-lahore-university-of-management-science-london-school-of-economics-princeton-university}}
\addcontentsline{toc}{subsubsection}{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample, Sheikhupura Police Study Sample, Institute of Development and Economic Alternatives, Lahore University of Management Science, London School of Economics, Princeton University}

\textbf{Target Population}: A representative sample of adults from 108 of 151 police beats in Sheikhupura and Nankana districts of Punjab Province.

\textbf{Original Study Design:} N/A

\textbf{COVID-19 Survey Design:} The EVA survey involved calls to all households in the stratified random sample for the policing study midline survey.

\emph{Sampling Frame:} Households in Sheikhupura and Nankana districts.

\emph{Survey Dates:} July 24 to September 9, 2020

\emph{Sample size, tracking and attrition:} Sample includes 1,473 respondents.

\emph{Sampling Weights:} Post-stratification weights are computed to adjust for the sampling process, which involved stratifying first on 27 police stations, then within each police station on beats, then PPS sampling within beats using Asiapop population data.

\emph{IRB Approval:} This research was approved via Princeton University IRB Protocol 7250.

\hypertarget{pakistan-economic-vulnerability-assessment-eva-subnational-sample}{%
\subsubsection*{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample}\label{pakistan-economic-vulnerability-assessment-eva-subnational-sample}}
\addcontentsline{toc}{subsubsection}{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample}

\textbf{Target Population}: All possible mobile phone numbers (in the province of Punjab) generated based on the local mobile phone number structure in Pakistan.

\textbf{Original Study Design:} N/A

\textbf{COVID-19 Survey Design:} The EVA survey involved making calls to individuals in Punjab based on random digit dialing.

\emph{Sampling Frame:} Individuals with mobile phones in Punjab.

\emph{Survey Dates:} September 2 to October 13, 2020

\emph{Sample size, tracking and attrition:} Sample includes 1,492 respondents.

\emph{Sampling Weights:} N/A.

\emph{IRB Approval:} This research was approved by Lahore University of Management Sciences IRB Protocol LUMS-IRB/07012020SA.

\hypertarget{rwanda-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}{%
\subsubsection*{Rwanda, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}\label{rwanda-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}}
\addcontentsline{toc}{subsubsection}{Rwanda, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}

\textbf{COVID-19 Experience}

\begin{itemize}
 \item First confirmed case: March 14, 2020
 \item Total cases:  5,017 as of October 22, 2020 
\item Total deaths:  34 as of October 22, 2020 
\end{itemize}

\textbf{Target Population}: A random sample of all numerically possible mobile phone numbers in the country, based on national communications authority number allocation plans.

\textbf{Original Study Design:} N/A

\textbf{COVID-19 Survey Design:}Phone survey

\emph{Sampling Frame:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share.

\emph{Survey Dates:} October 22 to November 5, 2020 (Round 1 June 4 -12, 2020)

\emph{Sample size, tracking and attrition:}Sample includes 1,355 respondents contacted in the second round of a panel of 1,480.

\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.

\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15591, Rwanda National Institute for Scientific Research permit No.0856/2020/10/NISR; and Rwanda National Ethics Committee approval No.16/RNEC/2020.

\hypertarget{russian-federation-research-on-covid-19-in-russias-regions-rocirr-subnational-sample-international-center-for-the-study-of-institutions-and-development-hse-university-moscow-russia-and-economics-department-of-ghent-university-wzb-berlin-social-science-center-columbia-university}{%
\subsubsection*{Russian Federation, Research on COVID-19 in Russia's Regions (RoCiRR) Subnational sample, International Center for the Study of Institutions and Development (HSE University, Moscow, Russia) and Economics Department of Ghent University, WZB Berlin Social Science Center, Columbia University}\label{russian-federation-research-on-covid-19-in-russias-regions-rocirr-subnational-sample-international-center-for-the-study-of-institutions-and-development-hse-university-moscow-russia-and-economics-department-of-ghent-university-wzb-berlin-social-science-center-columbia-university}}
\addcontentsline{toc}{subsubsection}{Russian Federation, Research on COVID-19 in Russia's Regions (RoCiRR) Subnational sample, International Center for the Study of Institutions and Development (HSE University, Moscow, Russia) and Economics Department of Ghent University, WZB Berlin Social Science Center, Columbia University}

\textbf{COVID-19 Experience}

\begin{itemize}
\item First confirmed case: January 31, 2020
\item Number of confirmed cases: 1,720,063 as of November 6, 2020 
\item Number of deaths:  29,654 as of November 6, 2020 
\end{itemize}

\textbf{Target Population}: Adult internet users who reside in one of 61 federal subjects (federal cities, oblasts, republics, krais and autonomous okrug) of Russia. The regions included in the study are Republics: \emph{Bashkortostan, Karelia, Komi, Mariy El, Mordovia, Tatarstan, Udmurtia, Chuvashia}. Krais: \emph{Altai, Krasnodarsky, Krasnoyarsky, Permsky, Primorsky, Stavropolsky, Khabarovsky}. Oblasts: \emph{Arkhangelsk, Astrakhan, Belgorod, Bryansk, Vladimir, Volgograd, Vologda, Voronezh, Ivanovo, Irkutsk, Kaliningrad, Kaluga, Kemerovo, Kirov, Kostroma, Kurgan, Kursk, Leningrad, Lipetsk, Moscow, Murmansk, Nizhny Novgorod, Novgorod, Novosibirsk, Omsk, Orenburg, Orel, Pskov, Penza, Rostov, Ryazan, Samara, Saratov, Sverdlovsk, Smolensk, Tambov, Tver, Tomsk, Tula, Tyumen, Ulyanovsk, Chelyabinsk, Yaroslavl}. Other: \emph{Moscow, Saint Petersburg, Khanty-Mansiysk Autonomous Okrug -- Ugra}. The remaining 24 federal subjects were excluded from the study due to inability to enroll sample size with desired characteristics (sample size, age, gender and education group composition).

\textbf{Original Study Design:} N/A

\textbf{COVID-19 Survey Design:} The study was designed to measure the impact of pandemics on Russians, mostly those who live in cities with more than 100,000 residents. It contains a number of questions on the personal experience, norms and values, trust in government institutions, provision of social services, and mass media use. Region and geolocality of every respondent are recorded.

\emph{Sampling Frame:} In total 25,558 respondents received the module on vaccine acceptance. The sample was enrolled from the pool of Russian online survey company OMI (Online Market Intelligence). The sampling was specifically targeted at having a minimum of 150 respondents in each of the 61 regions and including respondents from all the main age and gender groups within each region. Respondents were also selected so that at least 40\% of respondents did not have higher education, in accordance with higher education rates in Russia. Out of 25,558 recruited respondents, 22,125 completed the survey. Among 22,125 respondents who completed the survey, 20,821 were enrolled from the general pull of the survey company respondents, while the remaining 1,304 respondents were enrolled among residents of cities with populations below 100,000 and rural areas.

\emph{Survey Dates:} November 6 - December 1, 2020

\emph{Sample size, tracking and attrition:} 22,125 respondents who completed the survey with the vaccine acceptance module included.

\emph{Sampling Weights:} Post-stratification weights are computed to match marginal population distributions of age, gender and education with target proportions coming from the 2019 Yearbook and 2015 Microcensus released by Russian Federal Bureau of National Statistics (Rosstat).

\emph{IRB Approval:} This study was approved via Columbia University IRB Protocol IRB-AAAT4453.

\hypertarget{sierra-leone}{%
\subsubsection*{Sierra Leone}\label{sierra-leone}}
\addcontentsline{toc}{subsubsection}{Sierra Leone}

\textbf{COVID-19 Experience}

\begin{itemize}
        \item First confirmed case: March 20, 2020
        \item Total cases:  2,252 as of October 2, 2020 and 3,030 as of January 20, 2021 
        \item Total deaths:  72 as of October 2, 2020 and 77 as of January 20, 2021 
\end{itemize}

\hypertarget{sierra-leone-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}{%
\paragraph*{Sierra Leone, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}\label{sierra-leone-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}}
\addcontentsline{toc}{paragraph}{Sierra Leone, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}

\textbf{Target Population}: A random sample of all numerically possible mobile phone numbers in the country, based on national communications authority number allocation plans.

\textbf{Original Study Design:} N/A

\textbf{COVID-19 Survey Design:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share

\emph{Sampling Frame:} All active mobile phone numbers in Sierra Leone.

\emph{Survey Dates:} October 2-19, 2020 (Round 1 May 27 to June 15, 2020)

\emph{Sample Size, tracking and Attrition:} Sample includes 1,070 respondents contacted in the second round of a panel of 1,304.

\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.

\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15592, and Sierra Leone Ethics and Scientific Review Committee approval (no approval number, letter available upon request).

\hypertarget{sierra-leone-towns-that-are-candidates-for-rural-electrification-nation-wide-sample-international-growth-centre-igc-wageningen-university-research-yale-research-initiative-on-innovation-and-scale-y-rise-wzb-berlin-social-science-center-and-columbia-university}{%
\paragraph*{Sierra Leone, Towns that are Candidates for Rural Electrification Nation-wide sample, International Growth Centre (IGC), Wageningen University \& Research, Yale Research Initiative on Innovation and Scale (Y-RISE), WZB Berlin Social Science Center and Columbia University}\label{sierra-leone-towns-that-are-candidates-for-rural-electrification-nation-wide-sample-international-growth-centre-igc-wageningen-university-research-yale-research-initiative-on-innovation-and-scale-y-rise-wzb-berlin-social-science-center-and-columbia-university}}
\addcontentsline{toc}{paragraph}{Sierra Leone, Towns that are Candidates for Rural Electrification Nation-wide sample, International Growth Centre (IGC), Wageningen University \& Research, Yale Research Initiative on Innovation and Scale (Y-RISE), WZB Berlin Social Science Center and Columbia University}

\textbf{Project Title:} Sierra Leone Rural Electrification (SLRE)

\textbf{Target Population}: Households in 195 rural towns across all 14 districts of Sierra Leone. Of these, 97 villages were selected to benefit from an electrification program.

\textbf{Original Study Design:} Initial baseline data was collected during late 2019 and early 2020 as part of a study to assess the impact of Rural Electrification in rural towns in Sierra Leone.

\emph{Intervention:} The Government of Sierra Leone (GoSL) in collaboration with the United Nations Office for Project Services (UNOPS) and international donors is implementing the Rural Renewable Energy Project (RREP). In its first wave, during 2017, the project provided stand-alone solar photovoltaic powered mini-grids to 54 communities across the country. Construction of mini-grids in a further 43 towns is ongoing. In RREP communities, engineers construct 6kW--36kW power mini-grids that provide reliable power year-round. Electricity is free for schools and clinics. Residential and commercial users can acquire connections from commercial operators.

\emph{Village Sampling Frame:} Household data was collected in 195 towns across all 12 districts of Sierra Leone. The GoSL selected 97 towns with (planned) mini-grids. We used Propensity Score Matching to select 98 control communities. Within communities, respondents were randomly selected from a census roster stratified by occupation status of farmers, business owners and other occupations {[}47 percent, 47 percent and 7 percent{]}. In each village, the intended sample was 43 households (20 farmers, 20 businesses, 3 others). Data was collected during June--July (108 communities) and November--December 2019 (87 communities). If a household on the sampling list was not available on the village visit day, we had a randomly sampled list of replacement households to survey. The replacement household would be the same occupation as the sampled household would have been so the sample ratio of 20-20-3 still held in each community.

\textbf{COVID-19 Survey Design:} The goal was to assess households' degree of economic vulnerability in the face of the COVID-19 pandemic.

\emph{Sampling Frame:} The COVID-19 survey data comprises 2,110 respondents from 186 towns from the original baseline survey. Phone surveys were attempted to all 195 rural communities from the baseline survey. The total baseline household sample comprised 7047 respondents. We recontacted all baseline respondents that listed a phone number (4,594 respondents) and obtained informed consent for the phone survey. We implemented several waves of the phone survey, recontracting a respondent about every month. In wave 7, we added questions related to Vaccine Acceptability.\footnote{The data was first reported in \url{https://www.theigc.org/wp-content/uploads/2020/05/Meriggi-et-al-Data-Brief-2020.pdf}}.

\emph{Survey Dates:} October 7, 2020 and January 20, 2021 (earlier rounds included Wave 1: April 29-May 15; Wave 2: May 15-June 4; Wave 3: June 5-June 17; Wave 4: June 17-June 30; Wave 5: July 1-August 8; Wave 6: August 19-October 1). The median survey time was 33 minutes.

\emph{Sample size, tracking and attrition:} Data collection took place between October 7 and January 20, 2021with 2,110 respondents, in 186 towns for a tracking rate of 46 percent.

\emph{Sampling Weights:} None

\emph{IRB Approval:} Approval was secured from Sierra Leone Ethics and Scientific Review Committee (SLERC 2904202) and Wageningen University (24062020).

\hypertarget{uganda}{%
\subsubsection*{Uganda}\label{uganda}}
\addcontentsline{toc}{subsubsection}{Uganda}

\textbf{COVID-19 Experience}

\begin{itemize}
        \item First confirmed case: March 21, 2020
        \item Total cases:  741 as of June 18, 2020 and 6,468 as of September 21, 2020         \item Total deaths:  0 as of June 18, 2020 and 63 as of September 21, 2020 
\end{itemize}

\hypertarget{uganda-subnational-sample-international-growth-center-trinity-college-dublin-stockholm-school-of-economics-and-misum-institute-for-international-economic-studies-stockholm-university}{%
\paragraph*{Uganda Subnational sample, International Growth Center, Trinity College Dublin, Stockholm School of Economics and Misum, Institute for International Economic Studies, Stockholm University}\label{uganda-subnational-sample-international-growth-center-trinity-college-dublin-stockholm-school-of-economics-and-misum-institute-for-international-economic-studies-stockholm-university}}
\addcontentsline{toc}{paragraph}{Uganda Subnational sample, International Growth Center, Trinity College Dublin, Stockholm School of Economics and Misum, Institute for International Economic Studies, Stockholm University}

\textbf{Target Population}: Women from semi-rural and rural villages across 13 districts in Uganda (Iganga, Kayunga, Mbale, Mityana, Apac, Dokolo, Gulu, Adjumani, Koboko, Maracha, Nebbi, Soroti, Kumi).

\textbf{Original Study Design:} Initial baseline data was collected in 2016 as part of a large cluster randomized controlled trial, with the aim of selecting households likely to have children during the study period. Four criterias for selection were thus used, in descending order of importance: the household has a woman that is currently pregnant, or aged 16-30 years old, with a young child less than three years old, and/or married (formally or informally). In each household, the respondent was chosen as the female household head or the primary female health care giver of the household if the household head could not be found.

\textbf{COVID-19 Survey Design:} The data was collected through multiple rounds of phone surveys. The variable measuring age was constructed by approximation, using the baseline data from 2016 and adding 4 years to the 2016 measure. When the baseline respondent was replaced, the initial age information was deleted.

\emph{Sampling Frame:} Households were selected within 500 clusters (the village of the household).

\emph{Survey Dates:} September 21 to December 06, 2020.

\emph{Sample size, tracking and attrition:} Out of 2,743 respondents, 1752 were included, provided that they answered the main question about vaccine uptake.

\emph{Sampling Weights:} None.

\hypertarget{uganda-subnational-sample-wzb-berlin-social-science-center-and-columbia-university-nyu-abu-dhabi-innovations-for-poverty-action-ipa}{%
\subsubsection*{Uganda Subnational sample, WZB Berlin Social Science Center and Columbia University, NYU Abu Dhabi, Innovations for Poverty Action (IPA)}\label{uganda-subnational-sample-wzb-berlin-social-science-center-and-columbia-university-nyu-abu-dhabi-innovations-for-poverty-action-ipa}}
\addcontentsline{toc}{subsubsection}{Uganda Subnational sample, WZB Berlin Social Science Center and Columbia University, NYU Abu Dhabi, Innovations for Poverty Action (IPA)}

\textbf{Target Population:} All residents of Kampala who are Ugandan citizens, above the age of 18, and agree in principle to attend a short citizen consultative meeting.

\textbf{Original Study Design:} Baseline data was collected between July and October 2019 for an intervention that randomized citizen attendance to a set of 188 consultative meetings organized across Kampala. The meetings were organized to collect citizen preferences for the design of a forthcoming municipal citizen charter. The study also aimed to assess patterns of political inequality in meeting participation, dynamics, and outcomes, as well as study the subsequent effects on prosociality of being incorporated in this participatory process. 1/3 of the sample was randomly allocated to control, while 2/3 of respondents were invited to attend a consultative meeting. The consultations took place between November 2019 and February 2020 across Kampala divisions.

\emph{Intervention:} The intervention consisted of attendance at the consultative meeting organized a few months after baseline data collection. A further randomization allocated ½ of the invited participants to a meeting moderated by a local bureaucrat, while the remaining ones attended a meeting moderated by a neutral discussion leader.

\textbf{COVID-19 Survey Design:} The COVID-19 survey sample comprises the 2,189 respondents to the baseline who were selected on the basis of their residence in the city. Having received permission to re-contact these individuals, we coordinated a 3-wave panel throughout the summer and fall of 2020, with respondents contacted via phone. The goal was to assess households' degree of economic vulnerability in the face of the COVID-19 pandemic and respondents' evaluations of performance of political actors in tackling the pandemic.

\emph{Sampling Frame:} The 2,189 respondents to the baseline were randomly selected from a sampling frame of all buildings in Kampala, for which information about their geographical coordinates was available. After randomly selecting a set of candidate structures, interviewers sampled respondents from the subset of structures that were residential.

\emph{Survey Dates:} Wave 1: June 18--July 23. Wave 2: September 4--29. Wave 3: November 23--December 12.

\emph{Sample size, tracking and attrition:} Of the 2,189 respondents which we aimed to contact, we were able to reach 1,333 in Wave 1, 1,289 in Wave 2, and 1,366 in Wave 3. Wave 3 contained the COVID-19 vaccine module presented in this analysis.

\emph{Sampling Weights:} None.

\emph{IRB Approval:} The study was approved by IPA Global IRB (protocol number 15018) on May 29, 2020; WZB Berlin Social Science Center Ethics Review Board (protocol number 2020/0/91) on June 10, 2020; NYU Abu Dhabi IRB (protocol number HRPP-2020-64) on May 27, 2020; MIT Committee on the Use of Humans as Experimental Subjects (protocol number 2005000155) on June 3, 2020; and by the Mildmay Uganda Research Ethics Committee (protocol number 0604-2019) on June 11, 2020.

\hypertarget{united-states-of-america-nation-wide-sample-wzb-berlin-social-science-center-cornell-university-tufts-university}{%
\subsubsection*{United States of America Nation-wide sample, WZB Berlin Social Science Center, Cornell University, Tufts University}\label{united-states-of-america-nation-wide-sample-wzb-berlin-social-science-center-cornell-university-tufts-university}}
\addcontentsline{toc}{subsubsection}{United States of America Nation-wide sample, WZB Berlin Social Science Center, Cornell University, Tufts University}

\textbf{COVID-19 Experience}

\begin{itemize}
        \item First confirmed case: January 20, 2020
        \item Total cases:  14,499,637 as of December 4, 2020 
        \item Total deaths:  281,678 as of December 4, 2020 
\end{itemize}

\textbf{Target Population}: Nation-wide sample of adult internet users recruited through the market research firm Lucid.

\textbf{Original Study Design:} N/A

\emph{Intervention:} N/A

\textbf{COVID-19 Survey Design:}This survey was part of a panel study on attitudes toward COVID-19 technologies and public health surveillance.

\emph{Sampling Frame:} The Lucid Marketplace is an automated marketplace that connects researchers with willing online research participants. Lucid partners with a network of companies that maintain relationships with research participants by engaging them with research opportunities. While Lucid does not provide probability samples of the U.S. adult population, its quota samples approximate the marginal distributions of key demographic characteristics. Recent validation exercises have found that Lucid samples approximate nationally representative samples in terms of demographic characteristics and survey experiment effects.\footnote{See for instance: \url{https://journals.sagepub.com/doi/10.1177/2053168018822174}}

\emph{Survey Dates:} December 4-5, 2020

\emph{Sample size, tracking and attrition:} 1,959 individual online surveys. In the main question regarding intention to take the vaccine, approximately 10\% of respondents (184) did not answer
\emph{Sampling Weights:} Post-stratification weights are computed to match marginal population distributions of income, age, education, gender, race and region among the US adult population, with target proportions based on the 2018 American Community Survey.

\emph{IRB Approval:} This study received approval from the Cornell University IRB under Protocol \#2004009569.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\newpage

\end{document}

### 2021-03-23 paper_files/figure-latex/fig2paper-1.tex
replication files

% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:30
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

\nonstopmode

\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (722.70,542.02);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (722.70,542.02);
\end{scope}
\begin{scope}
\path[clip] ( 78.32, 67.14) rectangle (137.25,464.78);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 78.32, 67.14) rectangle (137.25,464.78);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 87.69, 67.14) --
	( 87.69,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (101.09, 67.14) --
	(101.09,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (114.48, 67.14) --
	(114.48,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (127.88, 67.14) --
	(127.88,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32, 83.94) --
	(137.25, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,111.94) --
	(137.25,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,139.95) --
	(137.25,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,167.95) --
	(137.25,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,195.95) --
	(137.25,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,223.96) --
	(137.25,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,251.96) --
	(137.25,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,279.96) --
	(137.25,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,307.96) --
	(137.25,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,335.97) --
	(137.25,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,363.97) --
	(137.25,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,391.97) --
	(137.25,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,419.98) --
	(137.25,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,447.98) --
	(137.25,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.00, 67.14) --
	( 81.00,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.39, 67.14) --
	( 94.39,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.79, 67.14) --
	(107.79,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (121.18, 67.14) --
	(121.18,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (134.58, 67.14) --
	(134.58,464.78);
\definecolor{drawColor}{RGB}{204,102,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.16,137.15) --
	(111.16,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.16,139.95) --
	( 94.55,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.55,137.15) --
	( 94.55,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (105.80,445.18) --
	(105.80,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (105.80,447.98) --
	(100.02,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.02,445.18) --
	(100.02,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.14,417.18) --
	(101.14,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.14,419.98) --
	( 94.07,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.07,417.18) --
	( 94.07,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.75,361.17) --
	( 90.75,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.75,363.97) --
	( 81.16,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.16,361.17) --
	( 81.16,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.66,333.17) --
	( 94.66,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.66,335.97) --
	( 90.37,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.37,333.17) --
	( 90.37,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 97.50,305.16) --
	( 97.50,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 97.50,307.96) --
	( 89.09,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.09,305.16) --
	( 89.09,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.57,109.14) --
	(101.57,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.57,111.94) --
	( 99.86,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.86,109.14) --
	( 99.86,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.95,277.16) --
	(107.95,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.95,279.96) --
	( 95.41,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.41,277.16) --
	( 95.41,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.09,249.16) --
	(113.09,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.09,251.96) --
	(106.23,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (106.23,249.16) --
	(106.23,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.20,221.16) --
	(116.20,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.20,223.96) --
	(107.84,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.84,221.16) --
	(107.84,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.00,193.15) --
	(129.00,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.00,195.95) --
	(124.23,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (124.23,193.15) --
	(124.23,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (109.13,165.15) --
	(109.13,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (109.13,167.95) --
	(103.61,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (103.61,165.15) --
	(103.61,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.00, 81.14) --
	(126.00, 86.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.00, 83.94) --
	(120.97, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.97, 81.14) --
	(120.97, 86.74);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (102.86,139.95) circle (  3.57);

\path[fill=fillColor] (102.91,447.98) circle (  3.57);

\path[fill=fillColor] ( 97.61,419.98) circle (  3.57);

\path[fill=fillColor] ( 85.98,363.97) circle (  1.43);

\path[fill=fillColor] ( 92.52,335.97) circle (  3.57);

\path[fill=fillColor] ( 93.32,307.96) circle (  3.57);

\path[fill=fillColor] (100.71,111.94) circle (  3.57);

\path[fill=fillColor] (101.68,279.96) circle (  3.57);

\path[fill=fillColor] (109.66,251.96) circle (  3.57);

\path[fill=fillColor] (112.02,223.96) circle (  3.57);

\path[fill=fillColor] (126.59,195.95) circle (  3.57);

\path[fill=fillColor] (106.34,167.95) circle (  3.57);

\path[fill=fillColor] (123.48, 83.94) circle (  3.57);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,153.95) -- (137.25,153.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,125.95) -- (137.25,125.95);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 78.32, 67.14) rectangle (137.25,464.78);
\end{scope}
\begin{scope}
\path[clip] (142.75, 67.14) rectangle (201.69,464.78);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (142.75, 67.14) rectangle (201.69,464.78);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (152.13, 67.14) --
	(152.13,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (165.53, 67.14) --
	(165.53,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (178.92, 67.14) --
	(178.92,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (192.32, 67.14) --
	(192.32,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75, 83.94) --
	(201.69, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,111.94) --
	(201.69,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,139.95) --
	(201.69,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,167.95) --
	(201.69,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,195.95) --
	(201.69,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,223.96) --
	(201.69,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,251.96) --
	(201.69,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,279.96) --
	(201.69,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,307.96) --
	(201.69,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,335.97) --
	(201.69,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,363.97) --
	(201.69,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,391.97) --
	(201.69,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,419.98) --
	(201.69,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,447.98) --
	(201.69,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.43, 67.14) --
	(145.43,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (158.83, 67.14) --
	(158.83,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.22, 67.14) --
	(172.22,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (185.62, 67.14) --
	(185.62,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (199.01, 67.14) --
	(199.01,464.78);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.63,137.15) --
	(159.63,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.63,139.95) --
	(150.10,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.10,137.15) --
	(150.10,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.33,445.18) --
	(151.33,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.33,447.98) --
	(148.11,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (148.11,445.18) --
	(148.11,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.97,417.18) --
	(157.97,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.97,419.98) --
	(152.24,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.24,417.18) --
	(152.24,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.17,361.17) --
	(154.17,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.72,333.17) --
	(161.72,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.72,335.97) --
	(157.11,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.11,333.17) --
	(157.11,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.19,305.16) --
	(161.19,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.19,307.96) --
	(153.10,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.10,305.16) --
	(153.10,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.52,109.14) --
	(153.52,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.52,111.94) --
	(152.29,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.29,109.14) --
	(152.29,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.70,277.16) --
	(154.70,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.70,279.96) --
	(146.93,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (146.93,277.16) --
	(146.93,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (169.12,249.16) --
	(169.12,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (169.12,251.96) --
	(162.37,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.37,249.16) --
	(162.37,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.04,165.15) --
	(153.04,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.04,167.95) --
	(149.24,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (149.24,165.15) --
	(149.24,170.75);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (154.86,139.95) circle (  3.57);

\path[fill=fillColor] (149.72,447.98) circle (  3.57);

\path[fill=fillColor] (155.13,419.98) circle (  3.57);

\path[fill=fillColor] (149.67,363.97) circle (  1.43);

\path[fill=fillColor] (159.42,335.97) circle (  3.57);

\path[fill=fillColor] (157.17,307.96) circle (  3.57);

\path[fill=fillColor] (152.88,111.94) circle (  3.57);

\path[fill=fillColor] (150.85,279.96) circle (  3.57);

\path[fill=fillColor] (165.74,251.96) circle (  3.57);

\path[fill=fillColor] (151.17,167.95) circle (  3.57);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,153.95) -- (201.69,153.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,125.95) -- (201.69,125.95);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.75, 67.14) rectangle (201.69,464.78);
\end{scope}
\begin{scope}
\path[clip] (207.19, 67.14) rectangle (266.13,464.78);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (207.19, 67.14) rectangle (266.13,464.78);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (216.57, 67.14) --
	(216.57,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (229.96, 67.14) --
	(229.96,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (243.36, 67.14) --
	(243.36,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (256.76, 67.14) --
	(256.76,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19, 83.94) --
	(266.13, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,111.94) --
	(266.13,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,139.95) --
	(266.13,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,167.95) --
	(266.13,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,195.95) --
	(266.13,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,223.96) --
	(266.13,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,251.96) --
	(266.13,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,279.96) --
	(266.13,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,307.96) --
	(266.13,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,335.97) --
	(266.13,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,363.97) --
	(266.13,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,391.97) --
	(266.13,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,419.98) --
	(266.13,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,447.98) --
	(266.13,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.87, 67.14) --
	(209.87,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.27, 67.14) --
	(223.27,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (236.66, 67.14) --
	(236.66,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.06, 67.14) --
	(250.06,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (263.45, 67.14) --
	(263.45,464.78);
\definecolor{drawColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (219.95,137.15) --
	(219.95,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (219.95,139.95) --
	(213.30,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.30,137.15) --
	(213.30,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (215.34,445.18) --
	(215.34,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (215.34,447.98) --
	(212.28,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (212.28,445.18) --
	(212.28,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.30,417.18) --
	(216.30,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.30,419.98) --
	(211.96,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.96,417.18) --
	(211.96,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.14,389.17) --
	(213.14,394.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.14,361.17) --
	(228.14,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.14,363.97) --
	(213.46,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.46,361.17) --
	(213.46,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.27,333.17) --
	(220.27,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.27,335.97) --
	(216.46,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.46,333.17) --
	(216.46,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.18,305.16) --
	(230.18,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.18,307.96) --
	(221.07,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (221.07,305.16) --
	(221.07,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.14,109.14) --
	(213.14,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.14,111.94) --
	(212.34,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (212.34,109.14) --
	(212.34,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (224.93,277.16) --
	(224.93,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (224.93,279.96) --
	(214.86,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.86,277.16) --
	(214.86,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.16,249.16) --
	(220.16,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.16,251.96) --
	(215.28,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (215.28,249.16) --
	(215.28,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.03,193.15) --
	(213.03,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.03,195.95) --
	(210.78,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (210.78,193.15) --
	(210.78,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.78,165.15) --
	(213.78,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.78,167.95) --
	(211.32,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.32,165.15) --
	(211.32,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (233.98, 81.14) --
	(233.98, 86.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (233.98, 83.94) --
	(227.82, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (227.82, 81.14) --
	(227.82, 86.74);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (216.62,139.95) circle (  3.57);

\path[fill=fillColor] (213.84,447.98) circle (  3.57);

\path[fill=fillColor] (214.16,419.98) circle (  3.57);

\path[fill=fillColor] (211.32,391.97) circle (  1.43);

\path[fill=fillColor] (220.80,363.97) circle (  3.57);

\path[fill=fillColor] (218.39,335.97) circle (  3.57);

\path[fill=fillColor] (225.62,307.96) circle (  3.57);

\path[fill=fillColor] (212.77,111.94) circle (  3.57);

\path[fill=fillColor] (219.89,279.96) circle (  3.57);

\path[fill=fillColor] (217.70,251.96) circle (  3.57);

\path[fill=fillColor] (211.91,195.95) circle (  3.57);

\path[fill=fillColor] (212.55,167.95) circle (  3.57);

\path[fill=fillColor] (230.93, 83.94) circle (  3.57);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,153.95) -- (266.13,153.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,125.95) -- (266.13,125.95);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (207.19, 67.14) rectangle (266.13,464.78);
\end{scope}
\begin{scope}
\path[clip] (271.63, 67.14) rectangle (330.57,464.78);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (271.63, 67.14) rectangle (330.57,464.78);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (281.01, 67.14) --
	(281.01,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (294.40, 67.14) --
	(294.40,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (307.80, 67.14) --
	(307.80,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (321.19, 67.14) --
	(321.19,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63, 83.94) --
	(330.57, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,111.94) --
	(330.57,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,139.95) --
	(330.57,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,167.95) --
	(330.57,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,195.95) --
	(330.57,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,223.96) --
	(330.57,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,251.96) --
	(330.57,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,279.96) --
	(330.57,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,307.96) --
	(330.57,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,335.97) --
	(330.57,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,363.97) --
	(330.57,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,391.97) --
	(330.57,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,419.98) --
	(330.57,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,447.98) --
	(330.57,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.31, 67.14) --
	(274.31,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (287.71, 67.14) --
	(287.71,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (301.10, 67.14) --
	(301.10,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (314.50, 67.14) --
	(314.50,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (327.89, 67.14) --
	(327.89,464.78);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (287.55,137.15) --
	(287.55,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (287.55,139.95) --
	(281.70,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (281.70,137.15) --
	(281.70,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (287.06,445.18) --
	(287.06,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (287.06,447.98) --
	(282.40,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (282.40,445.18) --
	(282.40,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (282.08,417.18) --
	(282.08,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (282.08,419.98) --
	(277.47,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (277.47,417.18) --
	(277.47,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (296.17,389.17) --
	(296.17,394.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (296.17,391.97) --
	(284.28,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (284.28,389.17) --
	(284.28,394.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (288.88,361.17) --
	(288.88,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (288.88,363.97) --
	(276.03,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (276.03,361.17) --
	(276.03,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (280.79,333.17) --
	(280.79,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (280.79,335.97) --
	(277.74,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (277.74,333.17) --
	(277.74,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (292.53,305.16) --
	(292.53,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (292.53,307.96) --
	(283.96,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (283.96,305.16) --
	(283.96,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (290.97,109.14) --
	(290.97,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (290.97,111.94) --
	(289.37,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (289.37,109.14) --
	(289.37,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (291.13,277.16) --
	(291.13,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (291.13,279.96) --
	(280.53,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (280.53,277.16) --
	(280.53,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (280.15,249.16) --
	(280.15,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (280.15,251.96) --
	(276.56,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (276.56,249.16) --
	(276.56,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (286.47,221.16) --
	(286.47,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (286.47,223.96) --
	(280.69,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (280.69,221.16) --
	(280.69,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (289.96,193.15) --
	(289.96,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (289.96,195.95) --
	(284.60,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (284.60,193.15) --
	(284.60,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (293.71,165.15) --
	(293.71,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (293.71,167.95) --
	(288.19,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (288.19,165.15) --
	(288.19,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (302.49, 81.14) --
	(302.49, 86.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (302.49, 83.94) --
	(296.28, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (296.28, 81.14) --
	(296.28, 86.74);
\definecolor{fillColor}{RGB}{51,34,136}

\path[fill=fillColor] (284.60,139.95) circle (  3.57);

\path[fill=fillColor] (284.76,447.98) circle (  3.57);

\path[fill=fillColor] (279.78,419.98) circle (  3.57);

\path[fill=fillColor] (290.22,391.97) circle (  3.57);

\path[fill=fillColor] (282.45,363.97) circle (  3.57);

\path[fill=fillColor] (279.29,335.97) circle (  3.57);

\path[fill=fillColor] (288.24,307.96) circle (  3.57);

\path[fill=fillColor] (290.17,111.94) circle (  3.57);

\path[fill=fillColor] (285.83,279.96) circle (  3.57);

\path[fill=fillColor] (278.33,251.96) circle (  3.57);

\path[fill=fillColor] (283.58,223.96) circle (  3.57);

\path[fill=fillColor] (287.28,195.95) circle (  3.57);

\path[fill=fillColor] (290.92,167.95) circle (  3.57);

\path[fill=fillColor] (299.39, 83.94) circle (  3.57);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,153.95) -- (330.57,153.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,125.95) -- (330.57,125.95);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.63, 67.14) rectangle (330.57,464.78);
\end{scope}
\begin{scope}
\path[clip] (336.07, 67.14) rectangle (395.01,464.78);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (336.07, 67.14) rectangle (395.01,464.78);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (345.45, 67.14) --
	(345.45,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (358.84, 67.14) --
	(358.84,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (372.24, 67.14) --
	(372.24,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (385.63, 67.14) --
	(385.63,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07, 83.94) --
	(395.01, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,111.94) --
	(395.01,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,139.95) --
	(395.01,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,167.95) --
	(395.01,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,195.95) --
	(395.01,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,223.96) --
	(395.01,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,251.96) --
	(395.01,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,279.96) --
	(395.01,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,307.96) --
	(395.01,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,335.97) --
	(395.01,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,363.97) --
	(395.01,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,391.97) --
	(395.01,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,419.98) --
	(395.01,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,447.98) --
	(395.01,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (338.75, 67.14) --
	(338.75,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (352.14, 67.14) --
	(352.14,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.54, 67.14) --
	(365.54,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (378.93, 67.14) --
	(378.93,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (392.33, 67.14) --
	(392.33,464.78);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (346.73,137.15) --
	(346.73,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (346.73,139.95) --
	(340.03,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (340.03,137.15) --
	(340.03,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (347.96,445.18) --
	(347.96,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (347.96,447.98) --
	(344.00,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.00,445.18) --
	(344.00,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (341.05,417.18) --
	(341.05,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (341.05,419.98) --
	(338.91,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (338.91,417.18) --
	(338.91,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (353.38,361.17) --
	(353.38,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (353.38,363.97) --
	(340.89,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (340.89,361.17) --
	(340.89,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (355.52,305.16) --
	(355.52,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (355.52,307.96) --
	(345.61,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (345.61,305.16) --
	(345.61,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.66,109.14) --
	(342.66,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.66,111.94) --
	(341.75,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (341.75,109.14) --
	(341.75,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.86,277.16) --
	(344.86,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.86,279.96) --
	(338.80,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (338.80,277.16) --
	(338.80,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.39,249.16) --
	(342.39,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.39,251.96) --
	(339.61,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (339.61,249.16) --
	(339.61,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (340.46,193.15) --
	(340.46,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (340.46,195.95) --
	(338.86,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (338.86,193.15) --
	(338.86,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.07,165.15) --
	(342.07,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (342.07,167.95) --
	(339.77,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (339.77,165.15) --
	(339.77,170.75);
\definecolor{fillColor}{RGB}{170,68,153}

\path[fill=fillColor] (343.41,139.95) circle (  3.57);

\path[fill=fillColor] (345.98,447.98) circle (  3.57);

\path[fill=fillColor] (339.98,419.98) circle (  1.43);

\path[fill=fillColor] (347.16,363.97) circle (  3.57);

\path[fill=fillColor] (350.59,307.96) circle (  3.57);

\path[fill=fillColor] (342.18,111.94) circle (  3.57);

\path[fill=fillColor] (341.86,279.96) circle (  1.43);

\path[fill=fillColor] (341.00,251.96) circle (  3.57);

\path[fill=fillColor] (339.66,195.95) circle (  1.43);

\path[fill=fillColor] (340.95,167.95) circle (  3.57);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,153.95) -- (395.01,153.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,125.95) -- (395.01,125.95);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (336.07, 67.14) rectangle (395.01,464.78);
\end{scope}
\begin{scope}
\path[clip] (400.51, 67.14) rectangle (459.45,464.78);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (400.51, 67.14) rectangle (459.45,464.78);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (409.88, 67.14) --
	(409.88,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (423.28, 67.14) --
	(423.28,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (436.68, 67.14) --
	(436.68,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (450.07, 67.14) --
	(450.07,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51, 83.94) --
	(459.45, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,111.94) --
	(459.45,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,139.95) --
	(459.45,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,167.95) --
	(459.45,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,195.95) --
	(459.45,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,223.96) --
	(459.45,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,251.96) --
	(459.45,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,279.96) --
	(459.45,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,307.96) --
	(459.45,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,335.97) --
	(459.45,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,363.97) --
	(459.45,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,391.97) --
	(459.45,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,419.98) --
	(459.45,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,447.98) --
	(459.45,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (403.19, 67.14) --
	(403.19,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (416.58, 67.14) --
	(416.58,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (429.98, 67.14) --
	(429.98,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (443.37, 67.14) --
	(443.37,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (456.77, 67.14) --
	(456.77,464.78);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (406.83,137.15) --
	(406.83,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (406.83,139.95) --
	(404.10,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (404.10,137.15) --
	(404.10,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (406.19,445.18) --
	(406.19,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (406.19,447.98) --
	(403.99,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (403.99,445.18) --
	(403.99,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (404.15,417.18) --
	(404.15,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (408.87,361.17) --
	(408.87,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (412.51,305.16) --
	(412.51,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (412.51,307.96) --
	(406.13,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (406.13,305.16) --
	(406.13,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (405.49,109.14) --
	(405.49,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (405.49,111.94) --
	(404.85,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (404.85,109.14) --
	(404.85,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (410.26,277.16) --
	(410.26,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (410.26,279.96) --
	(403.67,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (403.67,277.16) --
	(403.67,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (405.97,249.16) --
	(405.97,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (405.97,251.96) --
	(403.62,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (403.62,249.16) --
	(403.62,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (407.37,221.16) --
	(407.37,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (407.37,223.96) --
	(404.53,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (404.53,221.16) --
	(404.53,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (404.90,193.15) --
	(404.90,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (404.90,195.95) --
	(403.29,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (403.29,193.15) --
	(403.29,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (404.74,165.15) --
	(404.74,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (404.74,167.95) --
	(403.29,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (403.29,165.15) --
	(403.29,170.75);
\definecolor{fillColor}{RGB}{68,170,153}

\path[fill=fillColor] (405.49,139.95) circle (  3.57);

\path[fill=fillColor] (405.06,447.98) circle (  3.57);

\path[fill=fillColor] (403.51,419.98) circle (  1.43);

\path[fill=fillColor] (405.54,363.97) circle (  1.43);

\path[fill=fillColor] (409.35,307.96) circle (  3.57);

\path[fill=fillColor] (405.17,111.94) circle (  3.57);

\path[fill=fillColor] (406.94,279.96) circle (  1.43);

\path[fill=fillColor] (404.79,251.96) circle (  3.57);

\path[fill=fillColor] (405.92,223.96) circle (  3.57);

\path[fill=fillColor] (404.10,195.95) circle (  1.43);

\path[fill=fillColor] (404.04,167.95) circle (  3.57);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,153.95) -- (459.45,153.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,125.95) -- (459.45,125.95);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (400.51, 67.14) rectangle (459.45,464.78);
\end{scope}
\begin{scope}
\path[clip] (464.95, 67.14) rectangle (523.88,464.78);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (464.95, 67.14) rectangle (523.88,464.78);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (474.32, 67.14) --
	(474.32,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (487.72, 67.14) --
	(487.72,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (501.11, 67.14) --
	(501.11,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (514.51, 67.14) --
	(514.51,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95, 83.94) --
	(523.88, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,111.94) --
	(523.88,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,139.95) --
	(523.88,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,167.95) --
	(523.88,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,195.95) --
	(523.88,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,223.96) --
	(523.88,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,251.96) --
	(523.88,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,279.96) --
	(523.88,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,307.96) --
	(523.88,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,335.97) --
	(523.88,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,363.97) --
	(523.88,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,391.97) --
	(523.88,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,419.98) --
	(523.88,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,447.98) --
	(523.88,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (467.63, 67.14) --
	(467.63,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (481.02, 67.14) --
	(481.02,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (494.42, 67.14) --
	(494.42,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (507.81, 67.14) --
	(507.81,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (521.21, 67.14) --
	(521.21,464.78);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (469.39,137.15) --
	(469.39,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (469.13,445.18) --
	(469.13,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (469.13,447.98) --
	(467.73,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (467.73,445.18) --
	(467.73,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (468.32,417.18) --
	(468.32,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (470.57,361.17) --
	(470.57,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (468.00,333.17) --
	(468.00,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (473.63,109.14) --
	(473.63,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (473.63,111.94) --
	(472.56,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (472.56,109.14) --
	(472.56,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (473.57,277.16) --
	(473.57,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (473.57,279.96) --
	(467.68,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (467.68,277.16) --
	(467.68,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (468.80,249.16) --
	(468.80,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (468.11,165.15) --
	(468.11,170.75);
\definecolor{fillColor}{RGB}{153,153,51}

\path[fill=fillColor] (468.43,139.95) circle (  3.57);

\path[fill=fillColor] (468.43,447.98) circle (  1.43);

\path[fill=fillColor] (467.84,419.98) circle (  1.43);

\path[fill=fillColor] (468.59,363.97) circle (  1.43);

\path[fill=fillColor] (467.73,335.97) circle (  1.43);

\path[fill=fillColor] (473.09,111.94) circle (  3.57);

\path[fill=fillColor] (470.63,279.96) circle (  1.43);

\path[fill=fillColor] (468.11,251.96) circle (  1.43);

\path[fill=fillColor] (467.79,167.95) circle (  1.43);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,153.95) -- (523.88,153.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,125.95) -- (523.88,125.95);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (464.95, 67.14) rectangle (523.88,464.78);
\end{scope}
\begin{scope}
\path[clip] (529.38, 67.14) rectangle (588.32,464.78);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (529.38, 67.14) rectangle (588.32,464.78);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (538.76, 67.14) --
	(538.76,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (552.16, 67.14) --
	(552.16,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (565.55, 67.14) --
	(565.55,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (578.95, 67.14) --
	(578.95,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38, 83.94) --
	(588.32, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,111.94) --
	(588.32,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,139.95) --
	(588.32,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,167.95) --
	(588.32,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,195.95) --
	(588.32,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,223.96) --
	(588.32,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,251.96) --
	(588.32,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,279.96) --
	(588.32,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,307.96) --
	(588.32,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,335.97) --
	(588.32,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,363.97) --
	(588.32,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,391.97) --
	(588.32,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,419.98) --
	(588.32,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,447.98) --
	(588.32,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (532.06, 67.14) --
	(532.06,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (545.46, 67.14) --
	(545.46,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (558.85, 67.14) --
	(558.85,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (572.25, 67.14) --
	(572.25,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (585.64, 67.14) --
	(585.64,464.78);
\definecolor{drawColor}{RGB}{136,34,85}

\path[draw=drawColor,line width= 0.6pt,line join=round] (533.78,137.15) --
	(533.78,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (533.08,445.18) --
	(533.08,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (532.87,417.18) --
	(532.87,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (532.81,109.14) --
	(532.81,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (532.81,111.94) --
	(532.44,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (532.44,109.14) --
	(532.44,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (535.55,249.16) --
	(535.55,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (535.55,251.96) --
	(532.81,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (532.81,249.16) --
	(532.81,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (533.24,193.15) --
	(533.24,198.75);
\definecolor{fillColor}{RGB}{136,34,85}

\path[fill=fillColor] (532.76,139.95) circle (  3.57);

\path[fill=fillColor] (532.55,447.98) circle (  1.43);

\path[fill=fillColor] (532.33,419.98) circle (  1.43);

\path[fill=fillColor] (532.60,111.94) circle (  3.57);

\path[fill=fillColor] (534.21,251.96) circle (  3.57);

\path[fill=fillColor] (532.60,195.95) circle (  1.43);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,153.95) -- (588.32,153.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,125.95) -- (588.32,125.95);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (529.38, 67.14) rectangle (588.32,464.78);
\end{scope}
\begin{scope}
\path[clip] (593.82, 67.14) rectangle (652.76,464.78);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (593.82, 67.14) rectangle (652.76,464.78);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (603.20, 67.14) --
	(603.20,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (616.59, 67.14) --
	(616.59,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (629.99, 67.14) --
	(629.99,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (643.39, 67.14) --
	(643.39,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82, 83.94) --
	(652.76, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,111.94) --
	(652.76,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,139.95) --
	(652.76,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,167.95) --
	(652.76,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,195.95) --
	(652.76,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,223.96) --
	(652.76,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,251.96) --
	(652.76,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,279.96) --
	(652.76,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,307.96) --
	(652.76,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,335.97) --
	(652.76,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,363.97) --
	(652.76,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,391.97) --
	(652.76,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,419.98) --
	(652.76,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,447.98) --
	(652.76,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (596.50, 67.14) --
	(596.50,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (609.90, 67.14) --
	(609.90,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (623.29, 67.14) --
	(623.29,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (636.69, 67.14) --
	(636.69,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (650.08, 67.14) --
	(650.08,464.78);
\definecolor{drawColor}{RGB}{102,17,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (605.61,137.15) --
	(605.61,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (605.61,139.95) --
	(599.77,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (599.77,137.15) --
	(599.77,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (608.34,445.18) --
	(608.34,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (608.34,447.98) --
	(603.84,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (603.84,445.18) --
	(603.84,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (604.11,417.18) --
	(604.11,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (604.11,419.98) --
	(599.61,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (599.61,417.18) --
	(599.61,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (600.36,361.17) --
	(600.36,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (600.25,333.17) --
	(600.25,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (600.25,335.97) --
	(598.00,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (598.00,333.17) --
	(598.00,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (606.90,305.16) --
	(606.90,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (606.90,307.96) --
	(600.31,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (600.31,305.16) --
	(600.31,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (608.72,109.14) --
	(608.72,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (608.72,111.94) --
	(607.27,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (607.27,109.14) --
	(607.27,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (613.17,277.16) --
	(613.17,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (613.17,279.96) --
	(602.66,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (602.66,277.16) --
	(602.66,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (610.17,249.16) --
	(610.17,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (610.17,251.96) --
	(604.59,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (604.59,249.16) --
	(604.59,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (599.56,221.16) --
	(599.56,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (599.56,223.96) --
	(597.20,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (597.20,221.16) --
	(597.20,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (603.84,165.15) --
	(603.84,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (603.84,167.95) --
	(600.25,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (600.25,165.15) --
	(600.25,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (601.16, 81.14) --
	(601.16, 86.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (601.16, 83.94) --
	(598.32, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (598.32, 81.14) --
	(598.32, 86.74);
\definecolor{fillColor}{RGB}{102,17,0}

\path[fill=fillColor] (602.72,139.95) circle (  3.57);

\path[fill=fillColor] (606.09,447.98) circle (  3.57);

\path[fill=fillColor] (601.86,419.98) circle (  3.57);

\path[fill=fillColor] (598.00,363.97) circle (  1.43);

\path[fill=fillColor] (599.13,335.97) circle (  3.57);

\path[fill=fillColor] (603.57,307.96) circle (  3.57);

\path[fill=fillColor] (607.97,111.94) circle (  3.57);

\path[fill=fillColor] (607.91,279.96) circle (  3.57);

\path[fill=fillColor] (607.38,251.96) circle (  3.57);

\path[fill=fillColor] (598.38,223.96) circle (  3.57);

\path[fill=fillColor] (602.02,167.95) circle (  3.57);

\path[fill=fillColor] (599.72, 83.94) circle (  3.57);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,153.95) -- (652.76,153.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,125.95) -- (652.76,125.95);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (593.82, 67.14) rectangle (652.76,464.78);
\end{scope}
\begin{scope}
\path[clip] (658.26, 67.14) rectangle (717.20,464.78);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (658.26, 67.14) rectangle (717.20,464.78);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (667.64, 67.14) --
	(667.64,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (681.03, 67.14) --
	(681.03,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (694.43, 67.14) --
	(694.43,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (707.82, 67.14) --
	(707.82,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26, 83.94) --
	(717.20, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,111.94) --
	(717.20,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,139.95) --
	(717.20,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,167.95) --
	(717.20,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,195.95) --
	(717.20,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,223.96) --
	(717.20,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,251.96) --
	(717.20,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,279.96) --
	(717.20,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,307.96) --
	(717.20,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,335.97) --
	(717.20,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,363.97) --
	(717.20,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,391.97) --
	(717.20,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,419.98) --
	(717.20,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,447.98) --
	(717.20,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (660.94, 67.14) --
	(660.94,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (674.34, 67.14) --
	(674.34,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (687.73, 67.14) --
	(687.73,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (701.13, 67.14) --
	(701.13,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (714.52, 67.14) --
	(714.52,464.78);
\definecolor{drawColor}{RGB}{102,153,204}

\path[draw=drawColor,line width= 0.6pt,line join=round] (673.64,137.15) --
	(673.64,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (673.64,139.95) --
	(666.83,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (666.83,137.15) --
	(666.83,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (667.26,445.18) --
	(667.26,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (667.26,447.98) --
	(663.94,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (663.94,445.18) --
	(663.94,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (681.41,417.18) --
	(681.41,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (681.41,419.98) --
	(674.39,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (674.39,417.18) --
	(674.39,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (677.55,389.17) --
	(677.55,394.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (677.55,391.97) --
	(667.48,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (667.48,389.17) --
	(667.48,394.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (673.53,361.17) --
	(673.53,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (673.53,363.97) --
	(661.37,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (661.37,361.17) --
	(661.37,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (677.60,333.17) --
	(677.60,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (677.60,335.97) --
	(673.00,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (673.00,333.17) --
	(673.00,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (676.37,305.16) --
	(676.37,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (676.37,307.96) --
	(666.51,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (666.51,305.16) --
	(666.51,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (664.05,109.14) --
	(664.05,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (664.05,111.94) --
	(663.30,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (663.30,109.14) --
	(663.30,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (680.39,277.16) --
	(680.39,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (680.39,279.96) --
	(669.14,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (669.14,277.16) --
	(669.14,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (665.60,249.16) --
	(665.60,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (665.60,251.96) --
	(662.44,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (662.44,249.16) --
	(662.44,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (677.18,221.16) --
	(677.18,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (677.18,223.96) --
	(671.28,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (671.28,221.16) --
	(671.28,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (666.83,193.15) --
	(666.83,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (666.83,195.95) --
	(663.57,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (663.57,193.15) --
	(663.57,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (665.50,165.15) --
	(665.50,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (665.50,167.95) --
	(662.76,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (662.76,165.15) --
	(662.76,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (690.36, 81.14) --
	(690.36, 86.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (690.36, 83.94) --
	(684.14, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (684.14, 81.14) --
	(684.14, 86.74);
\definecolor{fillColor}{RGB}{102,153,204}

\path[fill=fillColor] (670.21,139.95) circle (  3.57);

\path[fill=fillColor] (665.60,447.98) circle (  3.57);

\path[fill=fillColor] (677.87,419.98) circle (  3.57);

\path[fill=fillColor] (672.51,391.97) circle (  3.57);

\path[fill=fillColor] (667.42,363.97) circle (  3.57);

\path[fill=fillColor] (675.30,335.97) circle (  3.57);

\path[fill=fillColor] (671.44,307.96) circle (  3.57);

\path[fill=fillColor] (663.67,111.94) circle (  3.57);

\path[fill=fillColor] (674.76,279.96) circle (  3.57);

\path[fill=fillColor] (663.99,251.96) circle (  3.57);

\path[fill=fillColor] (674.23,223.96) circle (  3.57);

\path[fill=fillColor] (665.23,195.95) circle (  3.57);

\path[fill=fillColor] (664.16,167.95) circle (  3.57);

\path[fill=fillColor] (687.25, 83.94) circle (  3.57);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,153.95) -- (717.20,153.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,125.95) -- (717.20,125.95);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (658.26, 67.14) rectangle (717.20,464.78);
\end{scope}
\begin{scope}
\path[clip] ( 78.32,464.78) rectangle (137.25,519.37);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 78.32,464.78) rectangle (137.25,519.37);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (107.79,498.55) {Concerned};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (107.79,489.04) {about side};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (107.79,479.54) {effects};
\end{scope}
\begin{scope}
\path[clip] (142.75,464.78) rectangle (201.69,519.37);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (142.75,464.78) rectangle (201.69,519.37);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.22,508.05) {Concerned};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.22,498.55) {about getting};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.22,489.04) {coronavirus};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.22,479.54) {from the};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.22,470.04) {vaccine};
\end{scope}
\begin{scope}
\path[clip] (207.19,464.78) rectangle (266.13,519.37);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (207.19,464.78) rectangle (266.13,519.37);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (236.66,498.55) {Not concerned};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (236.66,489.04) {about getting};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (236.66,479.54) {seriously ill};
\end{scope}
\begin{scope}
\path[clip] (271.63,464.78) rectangle (330.57,519.37);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (271.63,464.78) rectangle (330.57,519.37);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (301.10,498.55) {Doesn't think};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (301.10,489.04) {vaccines are};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (301.10,479.54) {effective};
\end{scope}
\begin{scope}
\path[clip] (336.07,464.78) rectangle (395.01,519.37);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (336.07,464.78) rectangle (395.01,519.37);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (365.54,508.05) {Doesn't think};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (365.54,498.55) {Coronavirus};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (365.54,489.04) {outbreak is as};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (365.54,479.54) {serious as};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (365.54,470.04) {people say};
\end{scope}
\begin{scope}
\path[clip] (400.51,464.78) rectangle (459.45,519.37);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (400.51,464.78) rectangle (459.45,519.37);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (429.98,493.80) {Doesn't like};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (429.98,484.29) {needles};
\end{scope}
\begin{scope}
\path[clip] (464.95,464.78) rectangle (523.88,519.37);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (464.95,464.78) rectangle (523.88,519.37);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (494.42,493.80) {Allergic to};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (494.42,484.29) {vaccines};
\end{scope}
\begin{scope}
\path[clip] (529.38,464.78) rectangle (588.32,519.37);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (529.38,464.78) rectangle (588.32,519.37);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (558.85,498.55) {Won't have};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (558.85,489.04) {time to get};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (558.85,479.54) {vaccinated};
\end{scope}
\begin{scope}
\path[clip] (593.82,464.78) rectangle (652.76,519.37);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (593.82,464.78) rectangle (652.76,519.37);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (623.29,498.55) {Mentions a};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (623.29,489.04) {conspiracy};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (623.29,479.54) {theory};
\end{scope}
\begin{scope}
\path[clip] (658.26,464.78) rectangle (717.20,519.37);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (658.26,464.78) rectangle (717.20,519.37);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (687.73,489.04) {Other reasons};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.00, 64.39) --
	( 81.00, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.39, 64.39) --
	( 94.39, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.79, 64.39) --
	(107.79, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (121.18, 64.39) --
	(121.18, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (134.58, 64.39) --
	(134.58, 67.14);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 81.00, 56.13) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 94.39, 56.13) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (107.79, 56.13) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (121.18, 56.13) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (134.58, 56.13) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.43, 64.39) --
	(145.43, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (158.83, 64.39) --
	(158.83, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.22, 64.39) --
	(172.22, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (185.62, 64.39) --
	(185.62, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (199.01, 64.39) --
	(199.01, 67.14);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (145.43, 56.13) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (158.83, 56.13) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.22, 56.13) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (185.62, 56.13) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (199.01, 56.13) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.87, 64.39) --
	(209.87, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.27, 64.39) --
	(223.27, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (236.66, 64.39) --
	(236.66, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.06, 64.39) --
	(250.06, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (263.45, 64.39) --
	(263.45, 67.14);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (209.87, 56.13) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (223.27, 56.13) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (236.66, 56.13) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (250.06, 56.13) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (263.45, 56.13) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.31, 64.39) --
	(274.31, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (287.71, 64.39) --
	(287.71, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (301.10, 64.39) --
	(301.10, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (314.50, 64.39) --
	(314.50, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (327.89, 64.39) --
	(327.89, 67.14);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (274.31, 56.13) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (287.71, 56.13) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (301.10, 56.13) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.50, 56.13) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (327.89, 56.13) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (338.75, 64.39) --
	(338.75, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (352.14, 64.39) --
	(352.14, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.54, 64.39) --
	(365.54, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (378.93, 64.39) --
	(378.93, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (392.33, 64.39) --
	(392.33, 67.14);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (338.75, 56.13) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (352.14, 56.13) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (365.54, 56.13) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (378.93, 56.13) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (392.33, 56.13) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (403.19, 64.39) --
	(403.19, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (416.58, 64.39) --
	(416.58, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (429.98, 64.39) --
	(429.98, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (443.37, 64.39) --
	(443.37, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (456.77, 64.39) --
	(456.77, 67.14);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (403.19, 56.13) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (416.58, 56.13) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (429.98, 56.13) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (443.37, 56.13) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (456.77, 56.13) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (467.63, 64.39) --
	(467.63, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (481.02, 64.39) --
	(481.02, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (494.42, 64.39) --
	(494.42, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (507.81, 64.39) --
	(507.81, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (521.21, 64.39) --
	(521.21, 67.14);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (467.63, 56.13) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (481.02, 56.13) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (494.42, 56.13) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (507.81, 56.13) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (521.21, 56.13) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (532.06, 64.39) --
	(532.06, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (545.46, 64.39) --
	(545.46, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (558.85, 64.39) --
	(558.85, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (572.25, 64.39) --
	(572.25, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (585.64, 64.39) --
	(585.64, 67.14);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (532.06, 56.13) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (545.46, 56.13) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (558.85, 56.13) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (572.25, 56.13) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (585.64, 56.13) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (596.50, 64.39) --
	(596.50, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (609.90, 64.39) --
	(609.90, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (623.29, 64.39) --
	(623.29, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (636.69, 64.39) --
	(636.69, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (650.08, 64.39) --
	(650.08, 67.14);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (596.50, 56.13) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (609.90, 56.13) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (623.29, 56.13) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (636.69, 56.13) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (650.08, 56.13) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (660.94, 64.39) --
	(660.94, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (674.34, 64.39) --
	(674.34, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (687.73, 64.39) --
	(687.73, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (701.13, 64.39) --
	(701.13, 67.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (714.52, 64.39) --
	(714.52, 67.14);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (660.94, 56.13) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (674.34, 56.13) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (687.73, 56.13) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (701.13, 56.13) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (714.52, 56.13) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96, 80.91) {USA};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,108.91) {Russia};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,136.92) {All LMICs};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,164.92) {Uganda 2};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,192.92) {Uganda 1};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,220.93) {Sierra Leone 2};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,248.93) {Sierra Leone 1};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,276.93) {Rwanda};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,304.93) {Pakistan 1};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,332.94) {Nigeria};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,360.94) {Nepal};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,388.94) {Mozambique};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,416.95) {Colombia};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,444.95) {Burkina Faso};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57, 83.94) --
	( 78.32, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,111.94) --
	( 78.32,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,139.95) --
	( 78.32,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,167.95) --
	( 78.32,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,195.95) --
	( 78.32,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,223.96) --
	( 78.32,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,251.96) --
	( 78.32,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,279.96) --
	( 78.32,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,307.96) --
	( 78.32,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,335.97) --
	( 78.32,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,363.97) --
	( 78.32,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,391.97) --
	( 78.32,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,419.98) --
	( 78.32,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,447.98) --
	( 78.32,447.98);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (397.76, 44.09) {estimate};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (284.57,  5.50) rectangle (510.95, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (290.07, 14.44) {Number of observations};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (409.70, 11.00) rectangle (424.15, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (416.92, 18.23) circle (  1.43);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (465.45, 11.00) rectangle (479.91, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] (472.68, 18.23) circle (  3.57);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (429.65, 15.20) {[50,500)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (485.41, 15.20) {500+};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  5.50,527.43) {Why would you not take the COVID-19 vaccine?};
\end{scope}
\end{tikzpicture}

\end{document}

### 2021-03-23 paper_files/figure-latex/fig3paper-1.tex
replication files

% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:37
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

\nonstopmode

\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (722.70,650.43);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (722.70,650.43);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,547.64) rectangle (371.71,627.77);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,547.64) rectangle (371.71,627.77);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,560.96) --
	(371.71,560.96);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,580.31) --
	(371.71,580.31);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,599.67) --
	(371.71,599.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,619.02) --
	(371.71,619.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,551.28) --
	(371.71,551.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,570.64) --
	(371.71,570.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,589.99) --
	(371.71,589.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,609.34) --
	(371.71,609.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,547.64) --
	( 75.24,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,547.64) --
	(120.16,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,547.64) --
	(165.08,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,547.64) --
	(209.99,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,547.64) --
	(254.91,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,547.64) --
	(299.83,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,547.64) --
	(344.75,627.77);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (171.81,551.28) rectangle (185.29,565.53);

\path[fill=fillColor] (261.65,551.28) rectangle (275.13,552.76);

\path[fill=fillColor] (216.73,551.28) rectangle (230.21,552.68);

\path[fill=fillColor] (306.57,551.28) rectangle (320.05,560.26);

\path[fill=fillColor] (351.49,551.28) rectangle (364.97,552.60);

\path[fill=fillColor] ( 81.97,551.28) rectangle ( 95.45,591.23);

\path[fill=fillColor] (126.89,551.28) rectangle (140.37,561.27);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,551.28) rectangle (171.81,566.46);

\path[fill=fillColor] (248.18,551.28) rectangle (261.65,552.83);

\path[fill=fillColor] (203.26,551.28) rectangle (216.73,551.98);

\path[fill=fillColor] (293.10,551.28) rectangle (306.57,555.00);

\path[fill=fillColor] (338.02,551.28) rectangle (351.49,551.59);

\path[fill=fillColor] ( 68.50,551.28) rectangle ( 81.97,595.49);

\path[fill=fillColor] (113.42,551.28) rectangle (126.89,562.97);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,551.28) rectangle (158.34,563.83);

\path[fill=fillColor] (234.70,551.28) rectangle (248.18,552.52);

\path[fill=fillColor] (189.78,551.28) rectangle (203.26,554.15);

\path[fill=fillColor] (279.62,551.28) rectangle (293.10,570.72);

\path[fill=fillColor] (324.54,551.28) rectangle (338.02,554.54);

\path[fill=fillColor] ( 55.02,551.28) rectangle ( 68.50,582.79);

\path[fill=fillColor] ( 99.94,551.28) rectangle (113.42,557.86);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,547.64) rectangle (371.71,627.77);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,462.01) rectangle (371.71,542.14);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,462.01) rectangle (371.71,542.14);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,475.33) --
	(371.71,475.33);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,494.68) --
	(371.71,494.68);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,514.04) --
	(371.71,514.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,533.39) --
	(371.71,533.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,465.65) --
	(371.71,465.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,485.01) --
	(371.71,485.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,504.36) --
	(371.71,504.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,523.71) --
	(371.71,523.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,462.01) --
	( 75.24,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,462.01) --
	(120.16,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,462.01) --
	(165.08,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,462.01) --
	(209.99,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,462.01) --
	(254.91,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,462.01) --
	(299.83,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,462.01) --
	(344.75,542.14);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (171.81,465.65) rectangle (185.29,493.21);

\path[fill=fillColor] (254.91,465.65) rectangle (275.13,465.96);

\path[fill=fillColor] (216.73,465.65) rectangle (230.21,478.12);

\path[fill=fillColor] (306.57,465.65) rectangle (320.05,466.04);

\path[fill=fillColor] (351.49,465.65) rectangle (364.97,467.51);

\path[fill=fillColor] ( 81.97,465.65) rectangle ( 95.45,499.87);

\path[fill=fillColor] (126.89,465.65) rectangle (140.37,466.27);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,465.65) rectangle (171.81,493.68);

\path[fill=fillColor] (234.70,465.65) rectangle (254.91,465.96);

\path[fill=fillColor] (203.26,465.65) rectangle (216.73,478.12);

\path[fill=fillColor] (293.10,465.65) rectangle (306.57,466.04);

\path[fill=fillColor] (338.02,465.65) rectangle (351.49,466.66);

\path[fill=fillColor] ( 68.50,465.65) rectangle ( 81.97,500.26);

\path[fill=fillColor] (113.42,465.65) rectangle (126.89,466.20);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,465.65) rectangle (158.34,480.13);

\path[fill=fillColor] (189.78,465.65) rectangle (203.26,478.66);

\path[fill=fillColor] (279.62,465.65) rectangle (293.10,466.43);

\path[fill=fillColor] (324.54,465.65) rectangle (338.02,489.81);

\path[fill=fillColor] ( 55.02,465.65) rectangle ( 68.50,489.03);

\path[fill=fillColor] ( 99.94,465.65) rectangle (113.42,467.28);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,462.01) rectangle (371.71,542.14);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,376.38) rectangle (371.71,456.51);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,376.38) rectangle (371.71,456.51);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,389.70) --
	(371.71,389.70);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,409.05) --
	(371.71,409.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,428.41) --
	(371.71,428.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,447.76) --
	(371.71,447.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,380.02) --
	(371.71,380.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,399.38) --
	(371.71,399.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,418.73) --
	(371.71,418.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,438.08) --
	(371.71,438.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,376.38) --
	( 75.24,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,376.38) --
	(120.16,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,376.38) --
	(165.08,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,376.38) --
	(209.99,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,376.38) --
	(254.91,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,376.38) --
	(299.83,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,376.38) --
	(344.75,456.51);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (171.81,380.02) rectangle (185.29,391.63);

\path[fill=fillColor] (254.91,380.02) rectangle (275.13,380.49);

\path[fill=fillColor] (216.73,380.02) rectangle (230.21,380.87);

\path[fill=fillColor] (306.57,380.02) rectangle (320.05,405.72);

\path[fill=fillColor] (351.49,380.02) rectangle (364.97,380.33);

\path[fill=fillColor] ( 81.97,380.02) rectangle ( 95.45,397.83);

\path[fill=fillColor] (126.89,380.02) rectangle (140.37,400.69);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,380.02) rectangle (171.81,391.71);

\path[fill=fillColor] (234.70,380.02) rectangle (254.91,380.56);

\path[fill=fillColor] (203.26,380.02) rectangle (216.73,380.80);

\path[fill=fillColor] (293.10,380.02) rectangle (306.57,404.79);

\path[fill=fillColor] (338.02,380.02) rectangle (351.49,380.10);

\path[fill=fillColor] ( 68.50,380.02) rectangle ( 81.97,398.45);

\path[fill=fillColor] (113.42,380.02) rectangle (126.89,401.23);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,380.02) rectangle (158.34,389.93);

\path[fill=fillColor] (189.78,380.02) rectangle (203.26,382.27);

\path[fill=fillColor] (279.62,380.02) rectangle (293.10,421.21);

\path[fill=fillColor] (324.54,380.02) rectangle (338.02,384.28);

\path[fill=fillColor] ( 55.02,380.02) rectangle ( 68.50,387.84);

\path[fill=fillColor] ( 99.94,380.02) rectangle (113.42,392.10);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,376.38) rectangle (371.71,456.51);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,290.75) rectangle (371.71,370.88);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,290.75) rectangle (371.71,370.88);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,304.07) --
	(371.71,304.07);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,323.42) --
	(371.71,323.42);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,342.78) --
	(371.71,342.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,362.13) --
	(371.71,362.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,294.39) --
	(371.71,294.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,313.74) --
	(371.71,313.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,333.10) --
	(371.71,333.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,352.45) --
	(371.71,352.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,290.75) --
	( 75.24,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,290.75) --
	(120.16,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,290.75) --
	(165.08,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,290.75) --
	(209.99,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,290.75) --
	(254.91,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,290.75) --
	(299.83,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,290.75) --
	(344.75,370.88);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (171.81,294.39) rectangle (185.29,296.79);

\path[fill=fillColor] (254.91,294.39) rectangle (275.13,294.39);

\path[fill=fillColor] (216.73,294.39) rectangle (230.21,295.71);

\path[fill=fillColor] (306.57,294.39) rectangle (320.05,298.88);

\path[fill=fillColor] ( 81.97,294.39) rectangle ( 95.45,363.52);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,294.39) rectangle (171.81,296.71);

\path[fill=fillColor] (234.70,294.39) rectangle (254.91,294.47);

\path[fill=fillColor] (203.26,294.39) rectangle (216.73,295.09);

\path[fill=fillColor] (293.10,294.39) rectangle (306.57,295.86);

\path[fill=fillColor] ( 68.50,294.39) rectangle ( 81.97,367.24);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,294.39) rectangle (158.34,297.41);

\path[fill=fillColor] (189.78,294.39) rectangle (203.26,300.20);

\path[fill=fillColor] (279.62,294.39) rectangle (293.10,320.63);

\path[fill=fillColor] ( 55.02,294.39) rectangle ( 68.50,336.74);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,290.75) rectangle (371.71,370.88);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,205.12) rectangle (371.71,285.25);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,205.12) rectangle (371.71,285.25);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,218.44) --
	(371.71,218.44);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,237.79) --
	(371.71,237.79);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,257.14) --
	(371.71,257.14);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,276.50) --
	(371.71,276.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,208.76) --
	(371.71,208.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,228.11) --
	(371.71,228.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,247.47) --
	(371.71,247.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,266.82) --
	(371.71,266.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,205.12) --
	( 75.24,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,205.12) --
	(120.16,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,205.12) --
	(165.08,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,205.12) --
	(209.99,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,205.12) --
	(254.91,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,205.12) --
	(299.83,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,205.12) --
	(344.75,285.25);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (171.81,208.76) rectangle (185.29,221.77);

\path[fill=fillColor] (261.65,208.76) rectangle (275.13,209.92);

\path[fill=fillColor] (216.73,208.76) rectangle (230.21,212.86);

\path[fill=fillColor] (306.57,208.76) rectangle (320.05,216.97);

\path[fill=fillColor] (351.49,208.76) rectangle (364.97,210.62);

\path[fill=fillColor] ( 81.97,208.76) rectangle ( 95.45,246.00);

\path[fill=fillColor] (126.89,208.76) rectangle (140.37,223.70);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,208.76) rectangle (171.81,221.77);

\path[fill=fillColor] (248.18,208.76) rectangle (261.65,209.92);

\path[fill=fillColor] (203.26,208.76) rectangle (216.73,212.24);

\path[fill=fillColor] (293.10,208.76) rectangle (306.57,214.10);

\path[fill=fillColor] (338.02,208.76) rectangle (351.49,209.69);

\path[fill=fillColor] ( 68.50,208.76) rectangle ( 81.97,248.47);

\path[fill=fillColor] (113.42,208.76) rectangle (126.89,225.48);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,208.76) rectangle (158.34,220.53);

\path[fill=fillColor] (234.70,208.76) rectangle (248.18,210.00);

\path[fill=fillColor] (189.78,208.76) rectangle (203.26,215.50);

\path[fill=fillColor] (279.62,208.76) rectangle (293.10,228.97);

\path[fill=fillColor] (324.54,208.76) rectangle (338.02,216.42);

\path[fill=fillColor] ( 55.02,208.76) rectangle ( 68.50,233.92);

\path[fill=fillColor] ( 99.94,208.76) rectangle (113.42,217.12);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,205.12) rectangle (371.71,285.25);
\end{scope}
\begin{scope}
\path[clip] ( 48.28,119.49) rectangle (371.71,199.62);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 48.28,119.49) rectangle (371.71,199.62);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,132.81) --
	(371.71,132.81);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,152.16) --
	(371.71,152.16);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,171.51) --
	(371.71,171.51);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,190.87) --
	(371.71,190.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,123.13) --
	(371.71,123.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,142.48) --
	(371.71,142.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,161.84) --
	(371.71,161.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,181.19) --
	(371.71,181.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,119.49) --
	( 75.24,199.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,119.49) --
	(120.16,199.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,119.49) --
	(165.08,199.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,119.49) --
	(209.99,199.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,119.49) --
	(254.91,199.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,119.49) --
	(299.83,199.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,119.49) --
	(344.75,199.62);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (171.81,123.13) rectangle (185.29,132.03);

\path[fill=fillColor] (216.73,123.13) rectangle (230.21,124.99);

\path[fill=fillColor] (306.57,123.13) rectangle (320.05,140.08);

\path[fill=fillColor] (344.75,123.13) rectangle (364.97,123.21);

\path[fill=fillColor] ( 81.97,123.13) rectangle ( 95.45,149.84);

\path[fill=fillColor] (126.89,123.13) rectangle (140.37,146.12);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (158.34,123.13) rectangle (171.81,129.86);

\path[fill=fillColor] (203.26,123.13) rectangle (216.73,124.45);

\path[fill=fillColor] (293.10,123.13) rectangle (306.57,137.53);

\path[fill=fillColor] ( 68.50,123.13) rectangle ( 81.97,152.62);

\path[fill=fillColor] (113.42,123.13) rectangle (126.89,148.68);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (144.86,123.13) rectangle (158.34,137.61);

\path[fill=fillColor] (189.78,123.13) rectangle (203.26,126.38);

\path[fill=fillColor] (279.62,123.13) rectangle (293.10,146.59);

\path[fill=fillColor] (324.54,123.13) rectangle (344.75,123.28);

\path[fill=fillColor] ( 55.02,123.13) rectangle ( 68.50,142.72);

\path[fill=fillColor] ( 99.94,123.13) rectangle (113.42,139.62);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,119.49) rectangle (371.71,199.62);
\end{scope}
\begin{scope}
\path[clip] (393.78,547.64) rectangle (717.20,627.77);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (393.78,547.64) rectangle (717.20,627.77);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,560.96) --
	(717.20,560.96);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,580.31) --
	(717.20,580.31);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,599.67) --
	(717.20,599.67);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,619.02) --
	(717.20,619.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,551.28) --
	(717.20,551.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,570.64) --
	(717.20,570.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,589.99) --
	(717.20,589.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,609.34) --
	(717.20,609.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,547.64) --
	(420.73,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,547.64) --
	(465.65,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,547.64) --
	(510.57,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,547.64) --
	(555.49,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,547.64) --
	(600.41,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,547.64) --
	(645.33,627.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,547.64) --
	(690.25,627.77);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (517.31,551.28) rectangle (530.78,579.62);

\path[fill=fillColor] (607.15,551.28) rectangle (620.62,552.60);

\path[fill=fillColor] (562.23,551.28) rectangle (575.70,552.68);

\path[fill=fillColor] (696.99,551.28) rectangle (710.46,558.17);

\path[fill=fillColor] (427.47,551.28) rectangle (440.94,581.71);

\path[fill=fillColor] (472.39,551.28) rectangle (485.86,560.26);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (503.83,551.28) rectangle (517.31,579.85);

\path[fill=fillColor] (593.67,551.28) rectangle (607.15,552.60);

\path[fill=fillColor] (548.75,551.28) rectangle (562.23,551.98);

\path[fill=fillColor] (683.51,551.28) rectangle (696.99,556.16);

\path[fill=fillColor] (413.99,551.28) rectangle (427.47,583.33);

\path[fill=fillColor] (458.91,551.28) rectangle (472.39,561.12);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (490.36,551.28) rectangle (503.83,578.77);

\path[fill=fillColor] (580.19,551.28) rectangle (593.67,552.37);

\path[fill=fillColor] (535.27,551.28) rectangle (548.75,555.39);

\path[fill=fillColor] (670.03,551.28) rectangle (683.51,565.84);

\path[fill=fillColor] (400.52,551.28) rectangle (413.99,575.67);

\path[fill=fillColor] (445.44,551.28) rectangle (458.91,557.17);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,547.64) rectangle (717.20,627.77);
\end{scope}
\begin{scope}
\path[clip] (393.78,462.01) rectangle (717.20,542.14);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (393.78,462.01) rectangle (717.20,542.14);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,475.33) --
	(717.20,475.33);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,494.68) --
	(717.20,494.68);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,514.04) --
	(717.20,514.04);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,533.39) --
	(717.20,533.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,465.65) --
	(717.20,465.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,485.01) --
	(717.20,485.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,504.36) --
	(717.20,504.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,523.71) --
	(717.20,523.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,462.01) --
	(420.73,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,462.01) --
	(465.65,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,462.01) --
	(510.57,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,462.01) --
	(555.49,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,462.01) --
	(600.41,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,462.01) --
	(645.33,542.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,462.01) --
	(690.25,542.14);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (517.31,465.65) rectangle (530.78,471.85);

\path[fill=fillColor] (562.23,465.65) rectangle (575.70,471.85);

\path[fill=fillColor] (652.07,465.65) rectangle (665.54,468.67);

\path[fill=fillColor] (696.99,465.65) rectangle (710.46,468.90);

\path[fill=fillColor] (427.47,465.65) rectangle (440.94,510.55);

\path[fill=fillColor] (472.39,465.65) rectangle (485.86,479.59);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (503.83,465.65) rectangle (517.31,470.53);

\path[fill=fillColor] (548.75,465.65) rectangle (562.23,469.60);

\path[fill=fillColor] (638.59,465.65) rectangle (652.07,467.67);

\path[fill=fillColor] (683.51,465.65) rectangle (696.99,466.12);

\path[fill=fillColor] (413.99,465.65) rectangle (427.47,515.04);

\path[fill=fillColor] (458.91,465.65) rectangle (472.39,482.37);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (490.36,465.65) rectangle (503.83,476.41);

\path[fill=fillColor] (535.27,465.65) rectangle (548.75,479.43);

\path[fill=fillColor] (625.11,465.65) rectangle (638.59,472.23);

\path[fill=fillColor] (670.03,465.65) rectangle (683.51,478.50);

\path[fill=fillColor] (400.52,465.65) rectangle (413.99,494.76);

\path[fill=fillColor] (445.44,465.65) rectangle (458.91,469.99);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,462.01) rectangle (717.20,542.14);
\end{scope}
\begin{scope}
\path[clip] (393.78,376.38) rectangle (717.20,456.51);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (393.78,376.38) rectangle (717.20,456.51);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,389.70) --
	(717.20,389.70);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,409.05) --
	(717.20,409.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,428.41) --
	(717.20,428.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,447.76) --
	(717.20,447.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,380.02) --
	(717.20,380.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,399.38) --
	(717.20,399.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,418.73) --
	(717.20,418.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,438.08) --
	(717.20,438.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,376.38) --
	(420.73,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,376.38) --
	(465.65,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,376.38) --
	(510.57,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,376.38) --
	(555.49,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,376.38) --
	(600.41,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,376.38) --
	(645.33,456.51);

\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,376.38) --
	(690.25,456.51);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (517.31,380.02) rectangle (530.78,386.53);

\path[fill=fillColor] (607.15,380.02) rectangle (620.62,380.41);

\path[fill=fillColor] (562.23,380.02) rectangle (575.70,383.66);

\path[fill=fillColor] (652.07,380.02) rectangle (665.54,386.91);

\path[fill=fillColor] (696.99,380.02) rectangle (710.46,380.87);

\path[fill=fillColor] (427.47,380.02) rectangle (440.94,414.08);

\path[fill=fillColor] (472.39,380.02) rectangle (485.86,405.18);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (503.83,380.02) rectangle (517.31,385.67);

\path[fill=fillColor] (593.67,380.02) rectangle (607.15,380.41);

\path[fill=fillColor] (548.75,380.02) rectangle (562.23,382.96);

\path[fill=fillColor] (638.59,380.02) rectangle (652.07,382.42);

\path[fill=fillColor] (683.51,380.02) rectangle (696.99,380.64);

\path[fill=fillColor] (413.99,380.02) rectangle (427.47,416.87);

\path[fill=fillColor] (458.91,380.02) rectangle (472.39,408.59);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (490.36,380.02) rectangle (503.83,389.39);

\path[fill=fillColor] (580.19,380.02) rectangle (593.67,380.41);

\path[fill=fillColor] (535.27,380.02) rectangle (548.75,385.98);

\path[fill=fillColor] (625.11,380.02) rectangle (638.59,402.78);

\path[fill=fillColor] (670.03,380.02) rectangle (683.51,381.73);

\path[fill=fillColor] (400.52,380.02) rectangle (413.99,404.10);

\path[fill=fillColor] (445.44,380.02) rectangle (458.91,393.26);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,376.38) rectangle (717.20,456.51);
\end{scope}
\begin{scope}
\path[clip] (393.78,290.75) rectangle (717.20,370.88);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (393.78,290.75) rectangle (717.20,370.88);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,304.07) --
	(717.20,304.07);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,323.42) --
	(717.20,323.42);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,342.78) --
	(717.20,342.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,362.13) --
	(717.20,362.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,294.39) --
	(717.20,294.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,313.74) --
	(717.20,313.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,333.10) --
	(717.20,333.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,352.45) --
	(717.20,352.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,290.75) --
	(420.73,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,290.75) --
	(465.65,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,290.75) --
	(510.57,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,290.75) --
	(555.49,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,290.75) --
	(600.41,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,290.75) --
	(645.33,370.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,290.75) --
	(690.25,370.88);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (517.31,294.39) rectangle (530.78,301.75);

\path[fill=fillColor] (607.15,294.39) rectangle (620.62,298.73);

\path[fill=fillColor] (562.23,294.39) rectangle (575.70,299.97);

\path[fill=fillColor] (652.07,294.39) rectangle (665.54,302.29);

\path[fill=fillColor] (690.25,294.39) rectangle (710.46,294.47);

\path[fill=fillColor] (427.47,294.39) rectangle (440.94,321.49);

\path[fill=fillColor] (472.39,294.39) rectangle (485.86,319.47);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (503.83,294.39) rectangle (517.31,301.98);

\path[fill=fillColor] (593.67,294.39) rectangle (607.15,298.26);

\path[fill=fillColor] (548.75,294.39) rectangle (562.23,299.81);

\path[fill=fillColor] (638.59,294.39) rectangle (652.07,297.10);

\path[fill=fillColor] (413.99,294.39) rectangle (427.47,324.04);

\path[fill=fillColor] (458.91,294.39) rectangle (472.39,322.65);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (490.36,294.39) rectangle (503.83,300.97);

\path[fill=fillColor] (580.19,294.39) rectangle (593.67,300.20);

\path[fill=fillColor] (535.27,294.39) rectangle (548.75,300.43);

\path[fill=fillColor] (625.11,294.39) rectangle (638.59,319.16);

\path[fill=fillColor] (670.03,294.39) rectangle (690.25,294.86);

\path[fill=fillColor] (400.52,294.39) rectangle (413.99,313.36);

\path[fill=fillColor] (445.44,294.39) rectangle (458.91,309.18);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,290.75) rectangle (717.20,370.88);
\end{scope}
\begin{scope}
\path[clip] (393.78,205.12) rectangle (717.20,285.25);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (393.78,205.12) rectangle (717.20,285.25);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,218.44) --
	(717.20,218.44);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,237.79) --
	(717.20,237.79);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,257.14) --
	(717.20,257.14);

\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,276.50) --
	(717.20,276.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,208.76) --
	(717.20,208.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,228.11) --
	(717.20,228.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,247.47) --
	(717.20,247.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,266.82) --
	(717.20,266.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,205.12) --
	(420.73,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,205.12) --
	(465.65,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,205.12) --
	(510.57,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,205.12) --
	(555.49,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,205.12) --
	(600.41,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,205.12) --
	(645.33,285.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,205.12) --
	(690.25,285.25);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (517.31,208.76) rectangle (530.78,230.51);

\path[fill=fillColor] (607.15,208.76) rectangle (620.62,212.55);

\path[fill=fillColor] (562.23,208.76) rectangle (575.70,210.46);

\path[fill=fillColor] (652.07,208.76) rectangle (665.54,221.61);

\path[fill=fillColor] (427.47,208.76) rectangle (440.94,236.63);

\path[fill=fillColor] (472.39,208.76) rectangle (485.86,218.28);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (503.83,208.76) rectangle (517.31,221.53);

\path[fill=fillColor] (593.67,208.76) rectangle (607.15,211.93);

\path[fill=fillColor] (548.75,208.76) rectangle (562.23,210.31);

\path[fill=fillColor] (638.59,208.76) rectangle (652.07,213.25);

\path[fill=fillColor] (413.99,208.76) rectangle (427.47,245.22);

\path[fill=fillColor] (458.91,208.76) rectangle (472.39,227.65);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (490.36,208.76) rectangle (503.83,234.38);

\path[fill=fillColor] (580.19,208.76) rectangle (593.67,212.86);

\path[fill=fillColor] (535.27,208.76) rectangle (548.75,210.46);

\path[fill=fillColor] (625.11,208.76) rectangle (638.59,225.25);

\path[fill=fillColor] (400.52,208.76) rectangle (413.99,232.84);

\path[fill=fillColor] (445.44,208.76) rectangle (458.91,214.10);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,205.12) rectangle (717.20,285.25);
\end{scope}
\begin{scope}
\path[clip] (377.21,547.64) rectangle (393.78,627.77);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,547.64) rectangle (393.78,627.77);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,587.71) {Colombia};
\end{scope}
\begin{scope}
\path[clip] (377.21,462.01) rectangle (393.78,542.14);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,462.01) rectangle (393.78,542.14);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,502.08) {Nigeria};
\end{scope}
\begin{scope}
\path[clip] (377.21,376.38) rectangle (393.78,456.51);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,376.38) rectangle (393.78,456.51);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,416.45) {Sierra Leone 1};
\end{scope}
\begin{scope}
\path[clip] (377.21,290.75) rectangle (393.78,370.88);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,290.75) rectangle (393.78,370.88);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,330.81) {Uganda 2};
\end{scope}
\begin{scope}
\path[clip] (377.21,205.12) rectangle (393.78,285.25);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,205.12) rectangle (393.78,285.25);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,245.18) {Russia};
\end{scope}
\begin{scope}
\path[clip] ( 31.71,547.64) rectangle ( 48.28,627.77);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,547.64) rectangle ( 48.28,627.77);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,587.71) {Burkina Faso};
\end{scope}
\begin{scope}
\path[clip] ( 31.71,462.01) rectangle ( 48.28,542.14);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,462.01) rectangle ( 48.28,542.14);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,502.08) {Nepal};
\end{scope}
\begin{scope}
\path[clip] ( 31.71,376.38) rectangle ( 48.28,456.51);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,376.38) rectangle ( 48.28,456.51);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,416.45) {Rwanda};
\end{scope}
\begin{scope}
\path[clip] ( 31.71,290.75) rectangle ( 48.28,370.88);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,290.75) rectangle ( 48.28,370.88);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,330.81) {Sierra Leone 2};
\end{scope}
\begin{scope}
\path[clip] ( 31.71,205.12) rectangle ( 48.28,285.25);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,205.12) rectangle ( 48.28,285.25);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,245.18) {All LMICs};
\end{scope}
\begin{scope}
\path[clip] ( 31.71,119.49) rectangle ( 48.28,199.62);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,119.49) rectangle ( 48.28,199.62);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,159.55) {USA};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,116.74) --
	( 75.24,119.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,116.74) --
	(120.16,119.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,116.74) --
	(165.08,119.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,116.74) --
	(209.99,119.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,116.74) --
	(254.91,119.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,116.74) --
	(299.83,119.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,116.74) --
	(344.75,119.49);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 78.27,114.54) {Health workers};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (118.43,114.54) {Government or};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (127.94,114.54) {MoH};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (163.35,114.54) {Family or};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.86,114.54) {Friends};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (198.77,114.54) {Famous person,};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (208.27,114.54) {religious leader};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (217.78,114.54) {or traditional};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (227.28,114.54) {healers};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (248.44,114.54) {Newspapers,};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (257.95,114.54) {radio or online};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (267.45,114.54) {groups};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (302.86,114.54) {Other};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (343.03,114.54) {Don't know or};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (352.54,114.54) {Refuse};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,202.37) --
	(420.73,205.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,202.37) --
	(465.65,205.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,202.37) --
	(510.57,205.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,202.37) --
	(555.49,205.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,202.37) --
	(600.41,205.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,202.37) --
	(645.33,205.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,202.37) --
	(690.25,205.12);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (423.76,200.17) {Health workers};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (463.93,200.17) {Government or};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (473.43,200.17) {MoH};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (508.85,200.17) {Family or};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (518.35,200.17) {Friends};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (544.26,200.17) {Famous person,};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (553.77,200.17) {religious leader};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (563.27,200.17) {or traditional};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (572.78,200.17) {healers};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (593.93,200.17) {Newspapers,};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (603.44,200.17) {radio or online};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (612.94,200.17) {groups};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (648.36,200.17) {Other};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (688.53,200.17) {Don't know or};

\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (698.03,200.17) {Refuse};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,548.25) {0};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,567.61) {25};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,586.96) {50};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,606.31) {75};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,551.28) --
	( 31.71,551.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,570.64) --
	( 31.71,570.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,589.99) --
	( 31.71,589.99);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,609.34) --
	( 31.71,609.34);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,462.62) {0};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,481.98) {25};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,501.33) {50};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,520.68) {75};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,465.65) --
	( 31.71,465.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,485.01) --
	( 31.71,485.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,504.36) --
	( 31.71,504.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,523.71) --
	( 31.71,523.71);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,376.99) {0};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,396.35) {25};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,415.70) {50};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,435.05) {75};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,380.02) --
	( 31.71,380.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,399.38) --
	( 31.71,399.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,418.73) --
	( 31.71,418.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,438.08) --
	( 31.71,438.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,291.36) {0};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,310.71) {25};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,330.07) {50};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,349.42) {75};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,294.39) --
	( 31.71,294.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,313.74) --
	( 31.71,313.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,333.10) --
	( 31.71,333.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,352.45) --
	( 31.71,352.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,205.73) {0};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,225.08) {25};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,244.44) {50};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,263.79) {75};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,208.76) --
	( 31.71,208.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,228.11) --
	( 31.71,228.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,247.47) --
	( 31.71,247.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,266.82) --
	( 31.71,266.82);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,120.10) {0};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,139.45) {25};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,158.81) {50};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,178.16) {75};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,123.13) --
	( 31.71,123.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,142.48) --
	( 31.71,142.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,161.84) --
	( 31.71,161.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,181.19) --
	( 31.71,181.19);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,373.63) {estimate};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (276.12,  5.50) rectangle (489.36, 30.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (281.62, 14.44) {Answer};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (322.65, 11.00) rectangle (337.10, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (323.36, 11.71) rectangle (336.39, 24.74);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (409.32, 11.00) rectangle (423.78, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (410.03, 11.71) rectangle (423.07, 24.74);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (448.02, 11.00) rectangle (462.48, 25.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (448.73, 11.71) rectangle (461.77, 24.74);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (342.60, 15.20) {No, Don't know};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (429.28, 15.20) {Yes};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (467.98, 15.20) {Any};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  5.50,635.84) {Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine?};
\end{scope}
\end{tikzpicture}

\end{document}

### 2021-03-23 paper_files/figure-latex/genderhist-1.tex
replication files

--- 2021-03-23 paper_files/figure-latex/fig3paper-1.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:37
+% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:44
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,560.96) --
-	(371.71,560.96);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,580.31) --
-	(371.71,580.31);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,599.67) --
-	(371.71,599.67);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,619.02) --
-	(371.71,619.02);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,561.31) --
+	(371.71,561.31);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,581.37) --
+	(371.71,581.37);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,601.43) --
+	(371.71,601.43);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,621.48) --
+	(371.71,621.48);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,570.64) --
-	(371.71,570.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,589.99) --
-	(371.71,589.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,609.34) --
-	(371.71,609.34);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,571.34) --
+	(371.71,571.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,591.40) --
+	(371.71,591.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,611.45) --
+	(371.71,611.45);
 
@@
 
-\path[fill=fillColor] (171.81,551.28) rectangle (185.29,565.53);
-
-\path[fill=fillColor] (261.65,551.28) rectangle (275.13,552.76);
-
-\path[fill=fillColor] (216.73,551.28) rectangle (230.21,552.68);
-
-\path[fill=fillColor] (306.57,551.28) rectangle (320.05,560.26);
-
-\path[fill=fillColor] (351.49,551.28) rectangle (364.97,552.60);
-
-\path[fill=fillColor] ( 81.97,551.28) rectangle ( 95.45,591.23);
-
-\path[fill=fillColor] (126.89,551.28) rectangle (140.37,561.27);
+\path[fill=fillColor] (171.81,551.28) rectangle (185.29,566.05);
+
+\path[fill=fillColor] (261.65,551.28) rectangle (275.13,552.81);
+
+\path[fill=fillColor] (216.73,551.28) rectangle (230.21,552.73);
+
+\path[fill=fillColor] (306.57,551.28) rectangle (320.05,560.59);
+
+\path[fill=fillColor] (351.49,551.28) rectangle (364.97,552.65);
+
+\path[fill=fillColor] ( 81.97,551.28) rectangle ( 95.45,592.68);
+
+\path[fill=fillColor] (126.89,551.28) rectangle (140.37,561.63);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,551.28) rectangle (171.81,566.46);
-
-\path[fill=fillColor] (248.18,551.28) rectangle (261.65,552.83);
-
-\path[fill=fillColor] (203.26,551.28) rectangle (216.73,551.98);
-
-\path[fill=fillColor] (293.10,551.28) rectangle (306.57,555.00);
-
-\path[fill=fillColor] (338.02,551.28) rectangle (351.49,551.59);
-
-\path[fill=fillColor] ( 68.50,551.28) rectangle ( 81.97,595.49);
-
-\path[fill=fillColor] (113.42,551.28) rectangle (126.89,562.97);
+\path[fill=fillColor] (158.34,551.28) rectangle (171.81,564.68);
+
+\path[fill=fillColor] (248.18,551.28) rectangle (261.65,552.41);
+
+\path[fill=fillColor] (203.26,551.28) rectangle (216.73,552.65);
+
+\path[fill=fillColor] (293.10,551.28) rectangle (306.57,561.47);
+
+\path[fill=fillColor] (338.02,551.28) rectangle (351.49,552.73);
+
+\path[fill=fillColor] ( 68.50,551.28) rectangle ( 81.97,592.52);
+
+\path[fill=fillColor] (113.42,551.28) rectangle (126.89,562.68);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,551.28) rectangle (158.34,563.83);
-
-\path[fill=fillColor] (234.70,551.28) rectangle (248.18,552.52);
-
-\path[fill=fillColor] (189.78,551.28) rectangle (203.26,554.15);
-
-\path[fill=fillColor] (279.62,551.28) rectangle (293.10,570.72);
-
-\path[fill=fillColor] (324.54,551.28) rectangle (338.02,554.54);
-
-\path[fill=fillColor] ( 55.02,551.28) rectangle ( 68.50,582.79);
-
-\path[fill=fillColor] ( 99.94,551.28) rectangle (113.42,557.86);
+\path[fill=fillColor] (144.86,551.28) rectangle (158.34,569.17);
+
+\path[fill=fillColor] (234.70,551.28) rectangle (248.18,553.53);
+
+\path[fill=fillColor] (189.78,551.28) rectangle (203.26,552.97);
+
+\path[fill=fillColor] (279.62,551.28) rectangle (293.10,558.58);
+
+\path[fill=fillColor] (324.54,551.28) rectangle (338.02,552.41);
+
+\path[fill=fillColor] ( 55.02,551.28) rectangle ( 68.50,593.08);
+
+\path[fill=fillColor] ( 99.94,551.28) rectangle (113.42,559.31);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,475.33) --
-	(371.71,475.33);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,494.68) --
-	(371.71,494.68);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,514.04) --
-	(371.71,514.04);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,533.39) --
-	(371.71,533.39);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,475.68) --
+	(371.71,475.68);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,495.74) --
+	(371.71,495.74);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,515.80) --
+	(371.71,515.80);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,535.85) --
+	(371.71,535.85);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,485.01) --
-	(371.71,485.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,504.36) --
-	(371.71,504.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,523.71) --
-	(371.71,523.71);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,485.71) --
+	(371.71,485.71);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,505.77) --
+	(371.71,505.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,525.82) --
+	(371.71,525.82);
 
@@
 
-\path[fill=fillColor] (171.81,465.65) rectangle (185.29,493.21);
-
-\path[fill=fillColor] (254.91,465.65) rectangle (275.13,465.96);
-
-\path[fill=fillColor] (216.73,465.65) rectangle (230.21,478.12);
-
-\path[fill=fillColor] (306.57,465.65) rectangle (320.05,466.04);
-
-\path[fill=fillColor] (351.49,465.65) rectangle (364.97,467.51);
-
-\path[fill=fillColor] ( 81.97,465.65) rectangle ( 95.45,499.87);
-
-\path[fill=fillColor] (126.89,465.65) rectangle (140.37,466.27);
+\path[fill=fillColor] (171.81,465.65) rectangle (185.29,494.21);
+
+\path[fill=fillColor] (254.91,465.65) rectangle (275.13,465.97);
+
+\path[fill=fillColor] (216.73,465.65) rectangle (230.21,478.81);
+
+\path[fill=fillColor] (306.57,465.65) rectangle (320.05,466.05);
+
+\path[fill=fillColor] (351.49,465.65) rectangle (364.97,467.58);
+
+\path[fill=fillColor] ( 81.97,465.65) rectangle ( 95.45,500.79);
+
+\path[fill=fillColor] (126.89,465.65) rectangle (140.37,466.30);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,465.65) rectangle (171.81,493.68);
-
-\path[fill=fillColor] (234.70,465.65) rectangle (254.91,465.96);
-
-\path[fill=fillColor] (203.26,465.65) rectangle (216.73,478.12);
-
-\path[fill=fillColor] (293.10,465.65) rectangle (306.57,466.04);
-
-\path[fill=fillColor] (338.02,465.65) rectangle (351.49,466.66);
-
-\path[fill=fillColor] ( 68.50,465.65) rectangle ( 81.97,500.26);
-
-\path[fill=fillColor] (113.42,465.65) rectangle (126.89,466.20);
+\path[fill=fillColor] (158.34,465.65) rectangle (171.81,491.41);
+
+\path[fill=fillColor] (234.70,465.65) rectangle (254.91,466.30);
+
+\path[fill=fillColor] (203.26,465.65) rectangle (216.73,478.97);
+
+\path[fill=fillColor] (293.10,465.65) rectangle (306.57,466.30);
+
+\path[fill=fillColor] (338.02,465.65) rectangle (351.49,466.62);
+
+\path[fill=fillColor] ( 68.50,465.65) rectangle ( 81.97,503.92);
+
+\path[fill=fillColor] (113.42,465.65) rectangle (126.89,466.38);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,465.65) rectangle (158.34,480.13);
-
-\path[fill=fillColor] (189.78,465.65) rectangle (203.26,478.66);
-
-\path[fill=fillColor] (279.62,465.65) rectangle (293.10,466.43);
-
-\path[fill=fillColor] (324.54,465.65) rectangle (338.02,489.81);
-
-\path[fill=fillColor] ( 55.02,465.65) rectangle ( 68.50,489.03);
-
-\path[fill=fillColor] ( 99.94,465.65) rectangle (113.42,467.28);
+\path[fill=fillColor] (144.86,465.65) rectangle (158.34,498.15);
+
+\path[fill=fillColor] (189.78,465.65) rectangle (203.26,478.49);
+
+\path[fill=fillColor] (279.62,465.65) rectangle (293.10,465.81);
+
+\path[fill=fillColor] (324.54,465.65) rectangle (338.02,468.86);
+
+\path[fill=fillColor] ( 55.02,465.65) rectangle ( 68.50,496.62);
+
+\path[fill=fillColor] ( 99.94,465.65) rectangle (113.42,466.21);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,389.70) --
-	(371.71,389.70);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,409.05) --
-	(371.71,409.05);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,428.41) --
-	(371.71,428.41);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,447.76) --
-	(371.71,447.76);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,390.05) --
+	(371.71,390.05);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,410.11) --
+	(371.71,410.11);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,430.16) --
+	(371.71,430.16);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,450.22) --
+	(371.71,450.22);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,399.38) --
-	(371.71,399.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,418.73) --
-	(371.71,418.73);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,438.08) --
-	(371.71,438.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,400.08) --
+	(371.71,400.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,420.14) --
+	(371.71,420.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,440.19) --
+	(371.71,440.19);
 
@@
 
-\path[fill=fillColor] (171.81,380.02) rectangle (185.29,391.63);
-
-\path[fill=fillColor] (254.91,380.02) rectangle (275.13,380.49);
-
-\path[fill=fillColor] (216.73,380.02) rectangle (230.21,380.87);
-
-\path[fill=fillColor] (306.57,380.02) rectangle (320.05,405.72);
-
-\path[fill=fillColor] (351.49,380.02) rectangle (364.97,380.33);
-
-\path[fill=fillColor] ( 81.97,380.02) rectangle ( 95.45,397.83);
-
-\path[fill=fillColor] (126.89,380.02) rectangle (140.37,400.69);
+\path[fill=fillColor] (171.81,380.02) rectangle (185.29,392.06);
+
+\path[fill=fillColor] (261.65,380.02) rectangle (275.13,380.50);
+
+\path[fill=fillColor] (216.73,380.02) rectangle (230.21,380.90);
+
+\path[fill=fillColor] (306.57,380.02) rectangle (320.05,406.66);
+
+\path[fill=fillColor] (344.75,380.02) rectangle (364.97,380.34);
+
+\path[fill=fillColor] ( 81.97,380.02) rectangle ( 95.45,398.47);
+
+\path[fill=fillColor] (126.89,380.02) rectangle (140.37,401.44);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,380.02) rectangle (171.81,391.71);
-
-\path[fill=fillColor] (234.70,380.02) rectangle (254.91,380.56);
-
-\path[fill=fillColor] (203.26,380.02) rectangle (216.73,380.80);
-
-\path[fill=fillColor] (293.10,380.02) rectangle (306.57,404.79);
-
-\path[fill=fillColor] (338.02,380.02) rectangle (351.49,380.10);
-
-\path[fill=fillColor] ( 68.50,380.02) rectangle ( 81.97,398.45);
-
-\path[fill=fillColor] (113.42,380.02) rectangle (126.89,401.23);
+\path[fill=fillColor] (158.34,380.02) rectangle (171.81,391.41);
+
+\path[fill=fillColor] (248.18,380.02) rectangle (261.65,380.74);
+
+\path[fill=fillColor] (203.26,380.02) rectangle (216.73,380.90);
+
+\path[fill=fillColor] (293.10,380.02) rectangle (306.57,405.86);
+
+\path[fill=fillColor] (324.54,380.02) rectangle (344.75,380.50);
+
+\path[fill=fillColor] ( 68.50,380.02) rectangle ( 81.97,399.36);
+
+\path[fill=fillColor] (113.42,380.02) rectangle (126.89,401.52);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,380.02) rectangle (158.34,389.93);
-
-\path[fill=fillColor] (189.78,380.02) rectangle (203.26,382.27);
-
-\path[fill=fillColor] (279.62,380.02) rectangle (293.10,421.21);
-
-\path[fill=fillColor] (324.54,380.02) rectangle (338.02,384.28);
-
-\path[fill=fillColor] ( 55.02,380.02) rectangle ( 68.50,387.84);
-
-\path[fill=fillColor] ( 99.94,380.02) rectangle (113.42,392.10);
+\path[fill=fillColor] (144.86,380.02) rectangle (158.34,393.18);
+
+\path[fill=fillColor] (234.70,380.02) rectangle (248.18,380.18);
+
+\path[fill=fillColor] (189.78,380.02) rectangle (203.26,380.82);
+
+\path[fill=fillColor] (279.62,380.02) rectangle (293.10,408.10);
+
+\path[fill=fillColor] ( 55.02,380.02) rectangle ( 68.50,396.71);
+
+\path[fill=fillColor] ( 99.94,380.02) rectangle (113.42,401.36);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,304.07) --
-	(371.71,304.07);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,323.42) --
-	(371.71,323.42);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,342.78) --
-	(371.71,342.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,362.13) --
-	(371.71,362.13);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,304.42) --
+	(371.71,304.42);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,324.48) --
+	(371.71,324.48);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,344.53) --
+	(371.71,344.53);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,364.59) --
+	(371.71,364.59);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,313.74) --
-	(371.71,313.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,333.10) --
-	(371.71,333.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,352.45) --
-	(371.71,352.45);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,314.45) --
+	(371.71,314.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,334.51) --
+	(371.71,334.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,354.56) --
+	(371.71,354.56);
 
@@
 
-\path[fill=fillColor] (171.81,294.39) rectangle (185.29,296.79);
+\path[fill=fillColor] (171.81,294.39) rectangle (185.29,296.88);
 
@@
 
-\path[fill=fillColor] (216.73,294.39) rectangle (230.21,295.71);
-
-\path[fill=fillColor] (306.57,294.39) rectangle (320.05,298.88);
-
-\path[fill=fillColor] ( 81.97,294.39) rectangle ( 95.45,363.52);
+\path[fill=fillColor] (216.73,294.39) rectangle (230.21,295.76);
+
+\path[fill=fillColor] (306.57,294.39) rectangle (320.05,299.04);
+
+\path[fill=fillColor] ( 81.97,294.39) rectangle ( 95.45,366.03);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,294.39) rectangle (171.81,296.71);
+\path[fill=fillColor] (158.34,294.39) rectangle (171.81,296.56);
 
@@
 
-\path[fill=fillColor] (203.26,294.39) rectangle (216.73,295.09);
-
-\path[fill=fillColor] (293.10,294.39) rectangle (306.57,295.86);
-
-\path[fill=fillColor] ( 68.50,294.39) rectangle ( 81.97,367.24);
+\path[fill=fillColor] (203.26,294.39) rectangle (216.73,295.84);
+
+\path[fill=fillColor] (293.10,294.39) rectangle (306.57,299.69);
+
+\path[fill=fillColor] ( 68.50,294.39) rectangle ( 81.97,365.63);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,294.39) rectangle (158.34,297.41);
-
-\path[fill=fillColor] (189.78,294.39) rectangle (203.26,300.20);
-
-\path[fill=fillColor] (279.62,294.39) rectangle (293.10,320.63);
-
-\path[fill=fillColor] ( 55.02,294.39) rectangle ( 68.50,336.74);
+\path[fill=fillColor] (144.86,294.39) rectangle (158.34,297.92);
+
+\path[fill=fillColor] (189.78,294.39) rectangle (203.26,295.59);
+
+\path[fill=fillColor] (279.62,294.39) rectangle (293.10,297.04);
+
+\path[fill=fillColor] ( 55.02,294.39) rectangle ( 68.50,367.24);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,218.44) --
-	(371.71,218.44);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,237.79) --
-	(371.71,237.79);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,257.14) --
-	(371.71,257.14);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,276.50) --
-	(371.71,276.50);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,218.79) --
+	(371.71,218.79);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,238.85) --
+	(371.71,238.85);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,258.90) --
+	(371.71,258.90);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,278.96) --
+	(371.71,278.96);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,228.11) --
-	(371.71,228.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,247.47) --
-	(371.71,247.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,266.82) --
-	(371.71,266.82);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,228.82) --
+	(371.71,228.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,248.87) --
+	(371.71,248.87);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,268.93) --
+	(371.71,268.93);
 
@@
 
-\path[fill=fillColor] (171.81,208.76) rectangle (185.29,221.77);
-
-\path[fill=fillColor] (261.65,208.76) rectangle (275.13,209.92);
-
-\path[fill=fillColor] (216.73,208.76) rectangle (230.21,212.86);
-
-\path[fill=fillColor] (306.57,208.76) rectangle (320.05,216.97);
-
-\path[fill=fillColor] (351.49,208.76) rectangle (364.97,210.62);
-
-\path[fill=fillColor] ( 81.97,208.76) rectangle ( 95.45,246.00);
-
-\path[fill=fillColor] (126.89,208.76) rectangle (140.37,223.70);
+\path[fill=fillColor] (171.81,208.76) rectangle (185.29,222.24);
+
+\path[fill=fillColor] (261.65,208.76) rectangle (275.13,209.96);
+
+\path[fill=fillColor] (216.73,208.76) rectangle (230.21,213.01);
+
+\path[fill=fillColor] (306.57,208.76) rectangle (320.05,217.26);
+
+\path[fill=fillColor] (351.49,208.76) rectangle (364.97,210.69);
+
+\path[fill=fillColor] ( 81.97,208.76) rectangle ( 95.45,247.27);
+
+\path[fill=fillColor] (126.89,208.76) rectangle (140.37,224.24);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,208.76) rectangle (171.81,221.77);
-
-\path[fill=fillColor] (248.18,208.76) rectangle (261.65,209.92);
-
-\path[fill=fillColor] (203.26,208.76) rectangle (216.73,212.24);
-
-\path[fill=fillColor] (293.10,208.76) rectangle (306.57,214.10);
-
-\path[fill=fillColor] (338.02,208.76) rectangle (351.49,209.69);
-
-\path[fill=fillColor] ( 68.50,208.76) rectangle ( 81.97,248.47);
-
-\path[fill=fillColor] (113.42,208.76) rectangle (126.89,225.48);
+\path[fill=fillColor] (158.34,208.76) rectangle (171.81,221.20);
+
+\path[fill=fillColor] (248.18,208.76) rectangle (261.65,210.12);
+
+\path[fill=fillColor] (203.26,208.76) rectangle (216.73,212.93);
+
+\path[fill=fillColor] (293.10,208.76) rectangle (306.57,217.59);
+
+\path[fill=fillColor] (338.02,208.76) rectangle (351.49,210.77);
+
+\path[fill=fillColor] ( 68.50,208.76) rectangle ( 81.97,247.27);
+
+\path[fill=fillColor] (113.42,208.76) rectangle (126.89,224.97);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,208.76) rectangle (158.34,220.53);
-
-\path[fill=fillColor] (234.70,208.76) rectangle (248.18,210.00);
-
-\path[fill=fillColor] (189.78,208.76) rectangle (203.26,215.50);
-
-\path[fill=fillColor] (279.62,208.76) rectangle (293.10,228.97);
-
-\path[fill=fillColor] (324.54,208.76) rectangle (338.02,216.42);
-
-\path[fill=fillColor] ( 55.02,208.76) rectangle ( 68.50,233.92);
-
-\path[fill=fillColor] ( 99.94,208.76) rectangle (113.42,217.12);
+\path[fill=fillColor] (144.86,208.76) rectangle (158.34,224.00);
+
+\path[fill=fillColor] (234.70,208.76) rectangle (248.18,209.88);
+
+\path[fill=fillColor] (189.78,208.76) rectangle (203.26,213.17);
+
+\path[fill=fillColor] (279.62,208.76) rectangle (293.10,216.54);
+
+\path[fill=fillColor] (324.54,208.76) rectangle (338.02,210.61);
+
+\path[fill=fillColor] ( 55.02,208.76) rectangle ( 68.50,247.03);
+
+\path[fill=fillColor] ( 99.94,208.76) rectangle (113.42,223.12);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,132.81) --
-	(371.71,132.81);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,152.16) --
-	(371.71,152.16);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,171.51) --
-	(371.71,171.51);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,190.87) --
-	(371.71,190.87);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,133.16) --
+	(371.71,133.16);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,153.21) --
+	(371.71,153.21);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,173.27) --
+	(371.71,173.27);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,193.33) --
+	(371.71,193.33);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,142.48) --
-	(371.71,142.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,161.84) --
-	(371.71,161.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,181.19) --
-	(371.71,181.19);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,143.19) --
+	(371.71,143.19);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,163.24) --
+	(371.71,163.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,183.30) --
+	(371.71,183.30);
 
@@
 
-\path[fill=fillColor] (171.81,123.13) rectangle (185.29,132.03);
-
-\path[fill=fillColor] (216.73,123.13) rectangle (230.21,124.99);
-
-\path[fill=fillColor] (306.57,123.13) rectangle (320.05,140.08);
+\path[fill=fillColor] (171.81,123.13) rectangle (185.29,132.36);
+
+\path[fill=fillColor] (216.73,123.13) rectangle (230.21,125.06);
+
+\path[fill=fillColor] (306.57,123.13) rectangle (320.05,140.70);
 
@@
 
-\path[fill=fillColor] ( 81.97,123.13) rectangle ( 95.45,149.84);
-
-\path[fill=fillColor] (126.89,123.13) rectangle (140.37,146.12);
+\path[fill=fillColor] ( 81.97,123.13) rectangle ( 95.45,150.81);
+
+\path[fill=fillColor] (126.89,123.13) rectangle (140.37,146.96);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,123.13) rectangle (171.81,129.86);
-
-\path[fill=fillColor] (203.26,123.13) rectangle (216.73,124.45);
-
-\path[fill=fillColor] (293.10,123.13) rectangle (306.57,137.53);
-
-\path[fill=fillColor] ( 68.50,123.13) rectangle ( 81.97,152.62);
-
-\path[fill=fillColor] (113.42,123.13) rectangle (126.89,148.68);
+\path[fill=fillColor] (158.34,123.13) rectangle (171.81,131.71);
+
+\path[fill=fillColor] (203.26,123.13) rectangle (216.73,124.73);
+
+\path[fill=fillColor] (293.10,123.13) rectangle (306.57,142.71);
+
+\path[fill=fillColor] (324.54,123.13) rectangle (344.75,123.21);
+
+\path[fill=fillColor] ( 68.50,123.13) rectangle ( 81.97,149.44);
+
+\path[fill=fillColor] (113.42,123.13) rectangle (126.89,147.20);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,123.13) rectangle (158.34,137.61);
-
-\path[fill=fillColor] (189.78,123.13) rectangle (203.26,126.38);
-
-\path[fill=fillColor] (279.62,123.13) rectangle (293.10,146.59);
-
-\path[fill=fillColor] (324.54,123.13) rectangle (344.75,123.28);
-
-\path[fill=fillColor] ( 55.02,123.13) rectangle ( 68.50,142.72);
-
-\path[fill=fillColor] ( 99.94,123.13) rectangle (113.42,139.62);
+\path[fill=fillColor] (144.86,123.13) rectangle (158.34,133.00);
+
+\path[fill=fillColor] (189.78,123.13) rectangle (203.26,125.30);
+
+\path[fill=fillColor] (279.62,123.13) rectangle (293.10,138.61);
+
+\path[fill=fillColor] ( 55.02,123.13) rectangle ( 68.50,152.25);
+
+\path[fill=fillColor] ( 99.94,123.13) rectangle (113.42,146.72);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,560.96) --
-	(717.20,560.96);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,580.31) --
-	(717.20,580.31);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,599.67) --
-	(717.20,599.67);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,619.02) --
-	(717.20,619.02);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,561.31) --
+	(717.20,561.31);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,581.37) --
+	(717.20,581.37);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,601.43) --
+	(717.20,601.43);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,621.48) --
+	(717.20,621.48);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,570.64) --
-	(717.20,570.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,589.99) --
-	(717.20,589.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,609.34) --
-	(717.20,609.34);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,571.34) --
+	(717.20,571.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,591.40) --
+	(717.20,591.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,611.45) --
+	(717.20,611.45);
 
@@
 
-\path[fill=fillColor] (517.31,551.28) rectangle (530.78,579.62);
-
-\path[fill=fillColor] (607.15,551.28) rectangle (620.62,552.60);
-
-\path[fill=fillColor] (562.23,551.28) rectangle (575.70,552.68);
-
-\path[fill=fillColor] (696.99,551.28) rectangle (710.46,558.17);
-
-\path[fill=fillColor] (427.47,551.28) rectangle (440.94,581.71);
-
-\path[fill=fillColor] (472.39,551.28) rectangle (485.86,560.26);
+\path[fill=fillColor] (517.31,551.28) rectangle (530.78,580.65);
+
+\path[fill=fillColor] (607.15,551.28) rectangle (620.62,552.65);
+
+\path[fill=fillColor] (562.23,551.28) rectangle (575.70,552.73);
+
+\path[fill=fillColor] (696.99,551.28) rectangle (710.46,558.42);
+
+\path[fill=fillColor] (427.47,551.28) rectangle (440.94,582.81);
+
+\path[fill=fillColor] (472.39,551.28) rectangle (485.86,560.59);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (503.83,551.28) rectangle (517.31,579.85);
-
-\path[fill=fillColor] (593.67,551.28) rectangle (607.15,552.60);
-
-\path[fill=fillColor] (548.75,551.28) rectangle (562.23,551.98);
-
-\path[fill=fillColor] (683.51,551.28) rectangle (696.99,556.16);
-
-\path[fill=fillColor] (413.99,551.28) rectangle (427.47,583.33);
-
-\path[fill=fillColor] (458.91,551.28) rectangle (472.39,561.12);
+\path[fill=fillColor] (503.83,551.28) rectangle (517.31,580.57);
+
+\path[fill=fillColor] (593.67,551.28) rectangle (607.15,553.37);
+
+\path[fill=fillColor] (548.75,551.28) rectangle (562.23,552.65);
+
+\path[fill=fillColor] (683.51,551.28) rectangle (696.99,559.47);
+
+\path[fill=fillColor] (413.99,551.28) rectangle (427.47,580.09);
+
+\path[fill=fillColor] (458.91,551.28) rectangle (472.39,561.79);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (490.36,551.28) rectangle (503.83,578.77);
-
-\path[fill=fillColor] (580.19,551.28) rectangle (593.67,552.37);
-
-\path[fill=fillColor] (535.27,551.28) rectangle (548.75,555.39);
-
-\path[fill=fillColor] (670.03,551.28) rectangle (683.51,565.84);
-
-\path[fill=fillColor] (400.52,551.28) rectangle (413.99,575.67);
-
-\path[fill=fillColor] (445.44,551.28) rectangle (458.91,557.17);
+\path[fill=fillColor] (490.36,551.28) rectangle (503.83,580.73);
+
+\path[fill=fillColor] (580.19,551.28) rectangle (593.67,552.17);
+
+\path[fill=fillColor] (535.27,551.28) rectangle (548.75,552.81);
+
+\path[fill=fillColor] (670.03,551.28) rectangle (683.51,557.86);
+
+\path[fill=fillColor] (400.52,551.28) rectangle (413.99,584.50);
+
+\path[fill=fillColor] (445.44,551.28) rectangle (458.91,559.95);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,475.33) --
-	(717.20,475.33);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,494.68) --
-	(717.20,494.68);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,514.04) --
-	(717.20,514.04);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,533.39) --
-	(717.20,533.39);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,475.68) --
+	(717.20,475.68);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,495.74) --
+	(717.20,495.74);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,515.80) --
+	(717.20,515.80);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,535.85) --
+	(717.20,535.85);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,485.01) --
-	(717.20,485.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,504.36) --
-	(717.20,504.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,523.71) --
-	(717.20,523.71);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,485.71) --
+	(717.20,485.71);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,505.77) --
+	(717.20,505.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,525.82) --
+	(717.20,525.82);
 
@@
 
-\path[fill=fillColor] (517.31,465.65) rectangle (530.78,471.85);
-
-\path[fill=fillColor] (562.23,465.65) rectangle (575.70,471.85);
-
-\path[fill=fillColor] (652.07,465.65) rectangle (665.54,468.67);
-
-\path[fill=fillColor] (696.99,465.65) rectangle (710.46,468.90);
-
-\path[fill=fillColor] (427.47,465.65) rectangle (440.94,510.55);
-
-\path[fill=fillColor] (472.39,465.65) rectangle (485.86,479.59);
+\path[fill=fillColor] (517.31,465.65) rectangle (530.78,472.07);
+
+\path[fill=fillColor] (562.23,465.65) rectangle (575.70,472.07);
+
+\path[fill=fillColor] (652.07,465.65) rectangle (665.54,468.78);
+
+\path[fill=fillColor] (696.99,465.65) rectangle (710.46,469.02);
+
+\path[fill=fillColor] (427.47,465.65) rectangle (440.94,512.19);
+
+\path[fill=fillColor] (472.39,465.65) rectangle (485.86,480.09);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (503.83,465.65) rectangle (517.31,470.53);
-
-\path[fill=fillColor] (548.75,465.65) rectangle (562.23,469.60);
-
-\path[fill=fillColor] (638.59,465.65) rectangle (652.07,467.67);
-
-\path[fill=fillColor] (683.51,465.65) rectangle (696.99,466.12);
-
-\path[fill=fillColor] (413.99,465.65) rectangle (427.47,515.04);
-
-\path[fill=fillColor] (458.91,465.65) rectangle (472.39,482.37);
+\path[fill=fillColor] (503.83,465.65) rectangle (517.31,470.63);
+
+\path[fill=fillColor] (548.75,465.65) rectangle (562.23,471.51);
+
+\path[fill=fillColor] (638.59,465.65) rectangle (652.07,469.34);
+
+\path[fill=fillColor] (683.51,465.65) rectangle (696.99,469.18);
+
+\path[fill=fillColor] (413.99,465.65) rectangle (427.47,512.91);
+
+\path[fill=fillColor] (458.91,465.65) rectangle (472.39,480.58);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (490.36,465.65) rectangle (503.83,476.41);
-
-\path[fill=fillColor] (535.27,465.65) rectangle (548.75,479.43);
-
-\path[fill=fillColor] (625.11,465.65) rectangle (638.59,472.23);
-
-\path[fill=fillColor] (670.03,465.65) rectangle (683.51,478.50);
-
-\path[fill=fillColor] (400.52,465.65) rectangle (413.99,494.76);
-
-\path[fill=fillColor] (445.44,465.65) rectangle (458.91,469.99);
+\path[fill=fillColor] (490.36,465.65) rectangle (503.83,474.40);
+
+\path[fill=fillColor] (535.27,465.65) rectangle (548.75,472.87);
+
+\path[fill=fillColor] (625.11,465.65) rectangle (638.59,467.90);
+
+\path[fill=fillColor] (670.03,465.65) rectangle (683.51,468.70);
+
+\path[fill=fillColor] (400.52,465.65) rectangle (413.99,510.90);
+
+\path[fill=fillColor] (445.44,465.65) rectangle (458.91,479.37);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,389.70) --
-	(717.20,389.70);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,409.05) --
-	(717.20,409.05);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,428.41) --
-	(717.20,428.41);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,447.76) --
-	(717.20,447.76);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,390.05) --
+	(717.20,390.05);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,410.11) --
+	(717.20,410.11);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,430.16) --
+	(717.20,430.16);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,450.22) --
+	(717.20,450.22);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,399.38) --
-	(717.20,399.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,418.73) --
-	(717.20,418.73);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,438.08) --
-	(717.20,438.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,400.08) --
+	(717.20,400.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,420.14) --
+	(717.20,420.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,440.19) --
+	(717.20,440.19);
 
@@
 
-\path[fill=fillColor] (517.31,380.02) rectangle (530.78,386.53);
-
-\path[fill=fillColor] (607.15,380.02) rectangle (620.62,380.41);
-
-\path[fill=fillColor] (562.23,380.02) rectangle (575.70,383.66);
-
-\path[fill=fillColor] (652.07,380.02) rectangle (665.54,386.91);
-
-\path[fill=fillColor] (696.99,380.02) rectangle (710.46,380.87);
-
-\path[fill=fillColor] (427.47,380.02) rectangle (440.94,414.08);
-
-\path[fill=fillColor] (472.39,380.02) rectangle (485.86,405.18);
+\path[fill=fillColor] (517.31,380.02) rectangle (530.78,386.76);
+
+\path[fill=fillColor] (607.15,380.02) rectangle (620.62,380.42);
+
+\path[fill=fillColor] (562.23,380.02) rectangle (575.70,383.79);
+
+\path[fill=fillColor] (652.07,380.02) rectangle (665.54,387.16);
+
+\path[fill=fillColor] (696.99,380.02) rectangle (710.46,380.90);
+
+\path[fill=fillColor] (427.47,380.02) rectangle (440.94,415.32);
+
+\path[fill=fillColor] (472.39,380.02) rectangle (485.86,406.10);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (503.83,380.02) rectangle (517.31,385.67);
-
-\path[fill=fillColor] (593.67,380.02) rectangle (607.15,380.41);
-
-\path[fill=fillColor] (548.75,380.02) rectangle (562.23,382.96);
-
-\path[fill=fillColor] (638.59,380.02) rectangle (652.07,382.42);
-
-\path[fill=fillColor] (683.51,380.02) rectangle (696.99,380.64);
-
-\path[fill=fillColor] (413.99,380.02) rectangle (427.47,416.87);
-
-\path[fill=fillColor] (458.91,380.02) rectangle (472.39,408.59);
+\path[fill=fillColor] (503.83,380.02) rectangle (517.31,385.64);
+
+\path[fill=fillColor] (593.67,380.02) rectangle (607.15,380.26);
+
+\path[fill=fillColor] (548.75,380.02) rectangle (562.23,383.47);
+
+\path[fill=fillColor] (638.59,380.02) rectangle (652.07,387.48);
+
+\path[fill=fillColor] (683.51,380.02) rectangle (696.99,381.07);
+
+\path[fill=fillColor] (413.99,380.02) rectangle (427.47,414.60);
+
+\path[fill=fillColor] (458.91,380.02) rectangle (472.39,407.94);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (490.36,380.02) rectangle (503.83,389.39);
-
-\path[fill=fillColor] (580.19,380.02) rectangle (593.67,380.41);
-
-\path[fill=fillColor] (535.27,380.02) rectangle (548.75,385.98);
-
-\path[fill=fillColor] (625.11,380.02) rectangle (638.59,402.78);
-
-\path[fill=fillColor] (670.03,380.02) rectangle (683.51,381.73);
-
-\path[fill=fillColor] (400.52,380.02) rectangle (413.99,404.10);
-
-\path[fill=fillColor] (445.44,380.02) rectangle (458.91,393.26);
+\path[fill=fillColor] (490.36,380.02) rectangle (503.83,388.77);
+
+\path[fill=fillColor] (580.19,380.02) rectangle (593.67,380.74);
+
+\path[fill=fillColor] (535.27,380.02) rectangle (548.75,384.35);
+
+\path[fill=fillColor] (625.11,380.02) rectangle (638.59,386.52);
+
+\path[fill=fillColor] (670.03,380.02) rectangle (683.51,380.74);
+
+\path[fill=fillColor] (400.52,380.02) rectangle (413.99,416.61);
+
+\path[fill=fillColor] (445.44,380.02) rectangle (458.91,402.81);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,304.07) --
-	(717.20,304.07);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,323.42) --
-	(717.20,323.42);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,342.78) --
-	(717.20,342.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,362.13) --
-	(717.20,362.13);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,304.42) --
+	(717.20,304.42);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,324.48) --
+	(717.20,324.48);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,344.53) --
+	(717.20,344.53);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,364.59) --
+	(717.20,364.59);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,313.74) --
-	(717.20,313.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,333.10) --
-	(717.20,333.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,352.45) --
-	(717.20,352.45);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,314.45) --
+	(717.20,314.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,334.51) --
+	(717.20,334.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,354.56) --
+	(717.20,354.56);
 
@@
 
-\path[fill=fillColor] (517.31,294.39) rectangle (530.78,301.75);
-
-\path[fill=fillColor] (607.15,294.39) rectangle (620.62,298.73);
-
-\path[fill=fillColor] (562.23,294.39) rectangle (575.70,299.97);
-
-\path[fill=fillColor] (652.07,294.39) rectangle (665.54,302.29);
-
-\path[fill=fillColor] (690.25,294.39) rectangle (710.46,294.47);
-
-\path[fill=fillColor] (427.47,294.39) rectangle (440.94,321.49);
-
-\path[fill=fillColor] (472.39,294.39) rectangle (485.86,319.47);
+\path[fill=fillColor] (517.31,294.39) rectangle (530.78,302.01);
+
+\path[fill=fillColor] (607.15,294.39) rectangle (620.62,298.88);
+
+\path[fill=fillColor] (562.23,294.39) rectangle (575.70,300.17);
+
+\path[fill=fillColor] (652.07,294.39) rectangle (665.54,302.57);
+
+\path[fill=fillColor] (696.99,294.39) rectangle (710.46,294.47);
+
+\path[fill=fillColor] (427.47,294.39) rectangle (440.94,322.47);
+
+\path[fill=fillColor] (472.39,294.39) rectangle (485.86,320.39);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (503.83,294.39) rectangle (517.31,301.98);
-
-\path[fill=fillColor] (593.67,294.39) rectangle (607.15,298.26);
-
-\path[fill=fillColor] (548.75,294.39) rectangle (562.23,299.81);
-
-\path[fill=fillColor] (638.59,294.39) rectangle (652.07,297.10);
-
-\path[fill=fillColor] (413.99,294.39) rectangle (427.47,324.04);
-
-\path[fill=fillColor] (458.91,294.39) rectangle (472.39,322.65);
+\path[fill=fillColor] (503.83,294.39) rectangle (517.31,301.53);
+
+\path[fill=fillColor] (593.67,294.39) rectangle (607.15,299.37);
+
+\path[fill=fillColor] (548.75,294.39) rectangle (562.23,300.09);
+
+\path[fill=fillColor] (638.59,294.39) rectangle (652.07,303.06);
+
+\path[fill=fillColor] (683.51,294.39) rectangle (696.99,294.47);
+
+\path[fill=fillColor] (413.99,294.39) rectangle (427.47,321.75);
+
+\path[fill=fillColor] (458.91,294.39) rectangle (472.39,320.71);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (490.36,294.39) rectangle (503.83,300.97);
-
-\path[fill=fillColor] (580.19,294.39) rectangle (593.67,300.20);
-
-\path[fill=fillColor] (535.27,294.39) rectangle (548.75,300.43);
-
-\path[fill=fillColor] (625.11,294.39) rectangle (638.59,319.16);
-
-\path[fill=fillColor] (670.03,294.39) rectangle (690.25,294.86);
-
-\path[fill=fillColor] (400.52,294.39) rectangle (413.99,313.36);
-
-\path[fill=fillColor] (445.44,294.39) rectangle (458.91,309.18);
+\path[fill=fillColor] (490.36,294.39) rectangle (503.83,302.41);
+
+\path[fill=fillColor] (580.19,294.39) rectangle (593.67,298.32);
+
+\path[fill=fillColor] (535.27,294.39) rectangle (548.75,300.25);
+
+\path[fill=fillColor] (625.11,294.39) rectangle (638.59,302.09);
+
+\path[fill=fillColor] (670.03,294.39) rectangle (683.51,294.47);
+
+\path[fill=fillColor] (400.52,294.39) rectangle (413.99,323.27);
+
+\path[fill=fillColor] (445.44,294.39) rectangle (458.91,320.06);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,218.44) --
-	(717.20,218.44);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,237.79) --
-	(717.20,237.79);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,257.14) --
-	(717.20,257.14);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,276.50) --
-	(717.20,276.50);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,218.79) --
+	(717.20,218.79);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,238.85) --
+	(717.20,238.85);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,258.90) --
+	(717.20,258.90);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,278.96) --
+	(717.20,278.96);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,228.11) --
-	(717.20,228.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,247.47) --
-	(717.20,247.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,266.82) --
-	(717.20,266.82);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,228.82) --
+	(717.20,228.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,248.87) --
+	(717.20,248.87);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,268.93) --
+	(717.20,268.93);
 
@@
 
-\path[fill=fillColor] (517.31,208.76) rectangle (530.78,230.51);
-
-\path[fill=fillColor] (607.15,208.76) rectangle (620.62,212.55);
-
-\path[fill=fillColor] (562.23,208.76) rectangle (575.70,210.46);
-
-\path[fill=fillColor] (652.07,208.76) rectangle (665.54,221.61);
-
-\path[fill=fillColor] (427.47,208.76) rectangle (440.94,236.63);
-
-\path[fill=fillColor] (472.39,208.76) rectangle (485.86,218.28);
+\path[fill=fillColor] (517.31,208.76) rectangle (530.78,231.30);
+
+\path[fill=fillColor] (607.15,208.76) rectangle (620.62,212.69);
+
+\path[fill=fillColor] (562.23,208.76) rectangle (575.70,210.53);
+
+\path[fill=fillColor] (652.07,208.76) rectangle (665.54,222.08);
+
+\path[fill=fillColor] (427.47,208.76) rectangle (440.94,237.64);
+
+\path[fill=fillColor] (472.39,208.76) rectangle (485.86,218.63);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (503.83,208.76) rectangle (517.31,221.53);
-
-\path[fill=fillColor] (593.67,208.76) rectangle (607.15,211.93);
-
-\path[fill=fillColor] (548.75,208.76) rectangle (562.23,210.31);
-
-\path[fill=fillColor] (638.59,208.76) rectangle (652.07,213.25);
-
-\path[fill=fillColor] (413.99,208.76) rectangle (427.47,245.22);
-
-\path[fill=fillColor] (458.91,208.76) rectangle (472.39,227.65);
+\path[fill=fillColor] (503.83,208.76) rectangle (517.31,230.66);
+
+\path[fill=fillColor] (593.67,208.76) rectangle (607.15,212.53);
+
+\path[fill=fillColor] (548.75,208.76) rectangle (562.23,210.69);
+
+\path[fill=fillColor] (638.59,208.76) rectangle (652.07,221.04);
+
+\path[fill=fillColor] (413.99,208.76) rectangle (427.47,238.12);
+
+\path[fill=fillColor] (458.91,208.76) rectangle (472.39,219.67);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (490.36,208.76) rectangle (503.83,234.38);
-
-\path[fill=fillColor] (580.19,208.76) rectangle (593.67,212.86);
-
-\path[fill=fillColor] (535.27,208.76) rectangle (548.75,210.46);
-
-\path[fill=fillColor] (625.11,208.76) rectangle (638.59,225.25);
-
-\path[fill=fillColor] (400.52,208.76) rectangle (413.99,232.84);
-
-\path[fill=fillColor] (445.44,208.76) rectangle (458.91,214.10);
+\path[fill=fillColor] (490.36,208.76) rectangle (503.83,231.87);
+
+\path[fill=fillColor] (580.19,208.76) rectangle (593.67,212.85);
+
+\path[fill=fillColor] (535.27,208.76) rectangle (548.75,210.28);
+
+\path[fill=fillColor] (625.11,208.76) rectangle (638.59,223.12);
+
+\path[fill=fillColor] (400.52,208.76) rectangle (413.99,237.16);
+
+\path[fill=fillColor] (445.44,208.76) rectangle (458.91,217.51);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,567.61) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,586.96) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,606.31) {75};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,568.31) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,588.37) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,608.42) {75};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,570.64) --
-	( 31.71,570.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,589.99) --
-	( 31.71,589.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,609.34) --
-	( 31.71,609.34);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,571.34) --
+	( 31.71,571.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,591.40) --
+	( 31.71,591.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,611.45) --
+	( 31.71,611.45);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,481.98) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,501.33) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,520.68) {75};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,482.68) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,502.74) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,522.79) {75};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,485.01) --
-	( 31.71,485.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,504.36) --
-	( 31.71,504.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,523.71) --
-	( 31.71,523.71);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,485.71) --
+	( 31.71,485.71);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,505.77) --
+	( 31.71,505.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,525.82) --
+	( 31.71,525.82);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,396.35) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,415.70) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,435.05) {75};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,397.05) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,417.11) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,437.16) {75};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,399.38) --
-	( 31.71,399.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,418.73) --
-	( 31.71,418.73);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,438.08) --
-	( 31.71,438.08);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,400.08) --
+	( 31.71,400.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,420.14) --
+	( 31.71,420.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,440.19) --
+	( 31.71,440.19);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,310.71) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,330.07) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,349.42) {75};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,311.42) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,331.47) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,351.53) {75};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,313.74) --
-	( 31.71,313.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,333.10) --
-	( 31.71,333.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,352.45) --
-	( 31.71,352.45);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,314.45) --
+	( 31.71,314.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,334.51) --
+	( 31.71,334.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,354.56) --
+	( 31.71,354.56);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,225.08) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,244.44) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,263.79) {75};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,225.79) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,245.84) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,265.90) {75};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,228.11) --
-	( 31.71,228.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,247.47) --
-	( 31.71,247.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,266.82) --
-	( 31.71,266.82);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,228.82) --
+	( 31.71,228.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,248.87) --
+	( 31.71,248.87);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,268.93) --
+	( 31.71,268.93);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,139.45) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,158.81) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,178.16) {75};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,140.16) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,160.21) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,180.27) {75};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,142.48) --
-	( 31.71,142.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,161.84) --
-	( 31.71,161.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,181.19) --
-	( 31.71,181.19);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,143.19) --
+	( 31.71,143.19);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,163.24) --
+	( 31.71,163.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,183.30) --
+	( 31.71,183.30);
 \end{scope}
@@
 
-\path[fill=fillColor] (276.12,  5.50) rectangle (489.36, 30.95);
+\path[fill=fillColor] (292.64,  5.50) rectangle (472.84, 30.95);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (281.62, 14.44) {Answer};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (322.65, 11.00) rectangle (337.10, 25.45);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (298.14, 14.44) {Answer};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (339.17, 11.00) rectangle (353.62, 25.45);
 \end{scope}
@@
 
-\path[fill=fillColor] (323.36, 11.71) rectangle (336.39, 24.74);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (409.32, 11.00) rectangle (423.78, 25.45);
+\path[fill=fillColor] (339.88, 11.71) rectangle (352.91, 24.74);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (391.63, 11.00) rectangle (406.08, 25.45);
 \end{scope}
@@
 
-\path[fill=fillColor] (410.03, 11.71) rectangle (423.07, 24.74);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (448.02, 11.00) rectangle (462.48, 25.45);
+\path[fill=fillColor] (392.34, 11.71) rectangle (405.37, 24.74);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (435.90, 11.00) rectangle (450.35, 25.45);
 \end{scope}
@@
 
-\path[fill=fillColor] (448.73, 11.71) rectangle (461.77, 24.74);
+\path[fill=fillColor] (436.61, 11.71) rectangle (449.64, 24.74);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (342.60, 15.20) {No, Don't know};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (359.12, 15.20) {Female};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (429.28, 15.20) {Yes};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (411.58, 15.20) {Male};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (467.98, 15.20) {Any};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (455.85, 15.20) {All};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  5.50,635.84) {Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine?};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  5.50,635.84) {If a COVID-19 vaccine becomes available in [country], would you take it?};
 \end{scope}

### 2021-03-23 paper_files/figure-latex/mainfigure1-1.tex
replication files

% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:22
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

\nonstopmode

\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (650.43,542.02);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (650.43,542.02);
\end{scope}
\begin{scope}
\path[clip] (152.00, 76.80) rectangle (271.61,506.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (152.00, 76.80) rectangle (271.61,506.36);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (171.03, 76.80) --
	(171.03,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (198.21, 76.80) --
	(198.21,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (225.40, 76.80) --
	(225.40,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (252.58, 76.80) --
	(252.58,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00, 92.71) --
	(271.61, 92.71);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,119.23) --
	(271.61,119.23);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,145.75) --
	(271.61,145.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,172.26) --
	(271.61,172.26);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,198.78) --
	(271.61,198.78);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,225.29) --
	(271.61,225.29);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,251.81) --
	(271.61,251.81);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,278.33) --
	(271.61,278.33);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,304.84) --
	(271.61,304.84);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,331.36) --
	(271.61,331.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,357.87) --
	(271.61,357.87);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,384.39) --
	(271.61,384.39);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,410.91) --
	(271.61,410.91);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,437.42) --
	(271.61,437.42);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,463.94) --
	(271.61,463.94);

\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,490.45) --
	(271.61,490.45);

\path[draw=drawColor,line width= 0.5pt,line join=round] (157.44, 76.80) --
	(157.44,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (184.62, 76.80) --
	(184.62,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (211.80, 76.80) --
	(211.80,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (238.99, 76.80) --
	(238.99,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (266.17, 76.80) --
	(266.17,506.36);
\definecolor{drawColor}{RGB}{204,102,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.51,143.09) --
	(250.51,148.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.51,145.75) --
	(238.88,145.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (238.88,143.09) --
	(238.88,148.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (233.01,487.80) --
	(233.01,493.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] (233.01,490.45) --
	(226.48,490.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] (226.48,487.80) --
	(226.48,493.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] (241.81,461.29) --
	(241.81,466.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (241.81,463.94) --
	(235.94,463.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (235.94,461.29) --
	(235.94,466.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.38,434.77) --
	(251.38,440.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.38,437.42) --
	(247.47,437.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.47,434.77) --
	(247.47,440.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] (257.15,408.25) --
	(257.15,413.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (257.15,410.91) --
	(251.49,410.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.49,408.25) --
	(251.49,413.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (263.56,381.74) --
	(263.56,387.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (263.56,384.39) --
	(261.28,384.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] (261.28,381.74) --
	(261.28,387.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (242.47,355.22) --
	(242.47,360.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (242.47,357.87) --
	(238.23,357.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] (238.23,355.22) --
	(238.23,360.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (246.92,328.71) --
	(246.92,334.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (246.92,331.36) --
	(233.55,331.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] (233.55,328.71) --
	(233.55,334.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (232.35,302.19) --
	(232.35,307.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (232.35,304.84) --
	(227.13,304.84);

\path[draw=drawColor,line width= 0.6pt,line join=round] (227.13,302.19) --
	(227.13,307.49);

\path[draw=drawColor,line width= 0.6pt,line join=round] (191.91,116.58) --
	(191.91,121.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (191.91,119.23) --
	(189.08,119.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (189.08,116.58) --
	(189.08,121.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.82,275.67) --
	(251.82,280.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.82,278.33) --
	(247.58,278.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (247.58,275.67) --
	(247.58,280.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.97,249.16) --
	(244.97,254.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.97,251.81) --
	(239.53,251.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (239.53,249.16) --
	(239.53,254.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.86,222.64) --
	(254.86,227.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (254.86,225.29) --
	(251.17,225.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (251.17,222.64) --
	(251.17,227.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (252.25,196.13) --
	(252.25,201.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (252.25,198.78) --
	(249.21,198.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (249.21,196.13) --
	(249.21,201.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (243.01,169.61) --
	(243.01,174.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (243.01,172.26) --
	(238.23,172.26);

\path[draw=drawColor,line width= 0.6pt,line join=round] (238.23,169.61) --
	(238.23,174.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.61, 90.06) --
	(230.61, 95.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.61, 92.71) --
	(224.63, 92.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (224.63, 90.06) --
	(224.63, 95.37);
\definecolor{fillColor}{RGB}{204,102,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (244.75,145.75) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (229.74,490.45) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (238.88,463.94) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (249.43,437.42) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.32,410.91) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (262.47,384.39) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (240.29,357.87) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (240.18,331.36) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (229.74,304.84) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.49,119.23) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (249.75,278.33) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (242.25,251.81) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (253.01,225.29) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (250.73,198.78) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (240.62,172.26) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (227.68, 92.71) circle (  1.96);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.00,159.00) -- (271.61,159.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.00,132.49) -- (271.61,132.49);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] (152.00, 76.80) rectangle (271.61,506.36);
\end{scope}
\begin{scope}
\path[clip] (276.61, 76.80) rectangle (396.21,506.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (276.61, 76.80) rectangle (396.21,506.36);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (295.64, 76.80) --
	(295.64,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (322.82, 76.80) --
	(322.82,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (350.00, 76.80) --
	(350.00,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (377.19, 76.80) --
	(377.19,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61, 92.71) --
	(396.21, 92.71);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,119.23) --
	(396.21,119.23);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,145.75) --
	(396.21,145.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,172.26) --
	(396.21,172.26);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,198.78) --
	(396.21,198.78);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,225.29) --
	(396.21,225.29);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,251.81) --
	(396.21,251.81);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,278.33) --
	(396.21,278.33);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,304.84) --
	(396.21,304.84);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,331.36) --
	(396.21,331.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,357.87) --
	(396.21,357.87);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,384.39) --
	(396.21,384.39);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,410.91) --
	(396.21,410.91);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,437.42) --
	(396.21,437.42);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,463.94) --
	(396.21,463.94);

\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,490.45) --
	(396.21,490.45);

\path[draw=drawColor,line width= 0.5pt,line join=round] (282.04, 76.80) --
	(282.04,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (309.23, 76.80) --
	(309.23,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (336.41, 76.80) --
	(336.41,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (363.59, 76.80) --
	(363.59,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (390.78, 76.80) --
	(390.78,506.36);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (374.36,148.40) --
	(374.36,151.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (374.36,149.72) --
	(361.75,149.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (361.75,148.40) --
	(361.75,151.05);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (377.73,140.44) --
	(377.73,143.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (377.73,141.77) --
	(366.20,141.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (366.20,140.44) --
	(366.20,143.09);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (355.87,493.10) --
	(355.87,495.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (355.87,494.43) --
	(343.26,494.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (343.26,493.10) --
	(343.26,495.76);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (360.22,485.15) --
	(360.22,487.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] (360.22,486.48) --
	(352.72,486.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (352.72,485.15) --
	(352.72,487.80);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.77,466.59) --
	(365.77,469.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.77,467.91) --
	(358.27,467.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (358.27,466.59) --
	(358.27,469.24);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (370.88,458.63) --
	(370.88,461.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (370.88,459.96) --
	(361.42,459.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (361.42,458.63) --
	(361.42,461.29);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (373.49,440.07) --
	(373.49,442.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (373.49,441.40) --
	(366.42,441.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (366.42,440.07) --
	(366.42,442.72);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (377.19,432.12) --
	(377.19,434.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (377.19,433.44) --
	(373.05,433.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (373.05,432.12) --
	(373.05,434.77);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (379.90,413.56) --
	(379.90,416.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (379.90,414.88) --
	(371.75,414.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (371.75,413.56) --
	(371.75,416.21);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (384.36,405.60) --
	(384.36,408.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (384.36,406.93) --
	(378.16,406.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] (378.16,405.60) --
	(378.16,408.25);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (388.82,387.04) --
	(388.82,389.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (388.82,388.37) --
	(384.91,388.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (384.91,387.04) --
	(384.91,389.69);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (388.28,379.09) --
	(388.28,381.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (388.28,380.41) --
	(385.45,380.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (385.45,379.09) --
	(385.45,381.74);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (366.97,360.52) --
	(366.97,363.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (366.97,361.85) --
	(360.01,361.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (360.01,360.52) --
	(360.01,363.18);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (368.38,352.57) --
	(368.38,355.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] (368.38,353.90) --
	(363.16,353.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] (363.16,352.57) --
	(363.16,355.22);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (367.73,334.01) --
	(367.73,336.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (367.73,335.33) --
	(353.37,335.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (353.37,334.01) --
	(353.37,336.66);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.99,326.05) --
	(375.99,328.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.99,327.38) --
	(362.29,327.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.29,326.05) --
	(362.29,328.71);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (308.36,121.88) --
	(308.36,124.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (308.36,123.21) --
	(304.77,123.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (304.77,121.88) --
	(304.77,124.53);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (326.08,113.93) --
	(326.08,116.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (326.08,115.25) --
	(321.73,115.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (321.73,113.93) --
	(321.73,116.58);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (372.29,280.98) --
	(372.29,283.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (372.29,282.30) --
	(364.46,282.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (364.46,280.98) --
	(364.46,283.63);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (380.12,273.02) --
	(380.12,275.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (380.12,274.35) --
	(375.34,274.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.34,273.02) --
	(375.34,275.67);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (367.62,254.46) --
	(367.62,257.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] (367.62,255.79) --
	(357.61,255.79);

\path[draw=drawColor,line width= 0.6pt,line join=round] (357.61,254.46) --
	(357.61,257.11);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (372.40,246.51) --
	(372.40,249.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] (372.40,247.83) --
	(365.99,247.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.99,246.51) --
	(365.99,249.16);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (381.54,227.95) --
	(381.54,230.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] (381.54,229.27) --
	(375.23,229.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.23,227.95) --
	(375.23,230.60);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (379.36,219.99) --
	(379.36,222.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (379.36,221.32) --
	(375.45,221.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.45,219.99) --
	(375.45,222.64);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (376.86,196.13) --
	(376.86,201.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (376.86,198.78) --
	(373.82,198.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (373.82,196.13) --
	(373.82,201.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (367.18,174.91) --
	(367.18,177.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (367.18,176.24) --
	(359.79,176.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (359.79,174.91) --
	(359.79,177.56);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (370.01,166.96) --
	(370.01,169.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (370.01,168.28) --
	(363.81,168.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] (363.81,166.96) --
	(363.81,169.61);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (347.39, 95.37) --
	(347.39, 98.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (347.39, 96.69) --
	(338.69, 96.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (338.69, 95.37) --
	(338.69, 98.02);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.66, 87.41) --
	(365.66, 90.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] (365.66, 88.74) --
	(357.94, 88.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (357.94, 87.41) --
	(357.94, 90.06);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (368.05,149.72) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (371.97,141.77) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (349.57,494.43) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (356.42,486.48) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (361.96,467.91) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (366.10,459.96) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.90,441.40) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.12,433.44) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.77,414.88) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (381.32,406.93) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.86,388.37) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.86,380.41) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.49,361.85) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (365.77,353.90) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (360.55,335.33) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.14,327.38) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (306.62,123.21) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (323.91,115.25) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (368.38,282.30) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (377.73,274.35) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.62,255.79) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.14,247.83) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (378.38,229.27) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (377.40,221.32) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.34,198.78) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.49,176.24) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (366.86,168.28) circle (  1.96);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (343.04, 96.69) circle (  1.96);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (361.85, 88.74) circle (  1.96);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (276.61,159.00) -- (396.21,159.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (276.61,132.49) -- (396.21,132.49);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] (276.61, 76.80) rectangle (396.21,506.36);
\end{scope}
\begin{scope}
\path[clip] (401.21, 76.80) rectangle (520.82,506.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (401.21, 76.80) rectangle (520.82,506.36);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (420.24, 76.80) --
	(420.24,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (447.43, 76.80) --
	(447.43,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (474.61, 76.80) --
	(474.61,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (501.79, 76.80) --
	(501.79,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21, 92.71) --
	(520.82, 92.71);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,119.23) --
	(520.82,119.23);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,145.75) --
	(520.82,145.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,172.26) --
	(520.82,172.26);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,198.78) --
	(520.82,198.78);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,225.29) --
	(520.82,225.29);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,251.81) --
	(520.82,251.81);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,278.33) --
	(520.82,278.33);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,304.84) --
	(520.82,304.84);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,331.36) --
	(520.82,331.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,357.87) --
	(520.82,357.87);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,384.39) --
	(520.82,384.39);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,410.91) --
	(520.82,410.91);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,437.42) --
	(520.82,437.42);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,463.94) --
	(520.82,463.94);

\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,490.45) --
	(520.82,490.45);

\path[draw=drawColor,line width= 0.5pt,line join=round] (406.65, 76.80) --
	(406.65,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (433.84, 76.80) --
	(433.84,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (461.02, 76.80) --
	(461.02,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (488.20, 76.80) --
	(488.20,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (515.39, 76.80) --
	(515.39,506.36);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (497.55,140.44) --
	(497.55,143.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (497.55,141.77) --
	(484.29,141.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (484.29,140.44) --
	(484.29,143.09);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (499.51,148.40) --
	(499.51,151.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (499.51,149.72) --
	(487.22,149.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (487.22,148.40) --
	(487.22,151.05);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (478.20,485.15) --
	(478.20,487.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] (478.20,486.48) --
	(467.43,486.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (467.43,485.15) --
	(467.43,487.80);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (486.90,493.10) --
	(486.90,495.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (486.90,494.43) --
	(478.85,494.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (478.85,493.10) --
	(478.85,495.76);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (496.36,458.63) --
	(496.36,461.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (496.36,459.96) --
	(486.68,459.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (486.68,458.63) --
	(486.68,461.29);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (490.16,466.59) --
	(490.16,469.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (490.16,467.91) --
	(482.87,467.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (482.87,466.59) --
	(482.87,469.24);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (510.38,432.12) --
	(510.38,434.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (510.38,433.44) --
	(497.44,433.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (497.44,432.12) --
	(497.44,434.77);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (503.32,440.07) --
	(503.32,442.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (503.32,441.40) --
	(496.47,441.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (496.47,440.07) --
	(496.47,442.72);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (504.95,405.60) --
	(504.95,408.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (504.95,406.93) --
	(495.60,406.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] (495.60,405.60) --
	(495.60,408.25);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (507.56,413.56) --
	(507.56,416.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (507.56,414.88) --
	(500.71,414.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (500.71,413.56) --
	(500.71,416.21);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (505.06,326.05) --
	(505.06,328.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (505.06,327.38) --
	(489.94,327.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] (489.94,326.05) --
	(489.94,328.71);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (494.18,334.01) --
	(494.18,336.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (494.18,335.33) --
	(479.94,335.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (479.94,334.01) --
	(479.94,336.66);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (488.75,299.54) --
	(488.75,302.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] (488.75,300.86) --
	(479.83,300.86);

\path[draw=drawColor,line width= 0.6pt,line join=round] (479.83,299.54) --
	(479.83,302.19);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (479.61,307.49) --
	(479.61,310.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] (479.61,308.82) --
	(473.20,308.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (473.20,307.49) --
	(473.20,310.14);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (441.99,113.93) --
	(441.99,116.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (441.99,115.25) --
	(438.84,115.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (438.84,113.93) --
	(438.84,116.58);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (441.45,121.88) --
	(441.45,124.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (441.45,123.21) --
	(436.34,123.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (436.34,121.88) --
	(436.34,124.53);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (490.59,273.02) --
	(490.59,275.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (490.59,274.35) --
	(477.87,274.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] (477.87,273.02) --
	(477.87,275.67);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (504.19,280.98) --
	(504.19,283.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (504.19,282.30) --
	(499.95,282.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (499.95,280.98) --
	(499.95,283.63);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (492.23,246.51) --
	(492.23,249.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] (492.23,247.83) --
	(482.87,247.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (482.87,246.51) --
	(482.87,249.16);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (497.23,254.46) --
	(497.23,257.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] (497.23,255.79) --
	(490.38,255.79);

\path[draw=drawColor,line width= 0.6pt,line join=round] (490.38,254.46) --
	(490.38,257.11);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (507.23,219.99) --
	(507.23,222.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (507.23,221.32) --
	(499.08,221.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] (499.08,219.99) --
	(499.08,222.64);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (504.08,227.95) --
	(504.08,230.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] (504.08,229.27) --
	(500.16,229.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (500.16,227.95) --
	(500.16,230.60);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (500.05,193.47) --
	(500.05,196.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (500.05,194.80) --
	(487.55,194.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] (487.55,193.47) --
	(487.55,196.13);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (500.71,201.43) --
	(500.71,204.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (500.71,202.75) --
	(497.12,202.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (497.12,201.43) --
	(497.12,204.08);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (485.92,166.96) --
	(485.92,169.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (485.92,168.28) --
	(476.57,168.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] (476.57,166.96) --
	(476.57,169.61);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (496.03,174.91) --
	(496.03,177.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (496.03,176.24) --
	(490.70,176.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (490.70,174.91) --
	(490.70,177.56);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (488.20, 87.41) --
	(488.20, 90.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] (488.20, 88.74) --
	(482.22, 88.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (482.22, 87.41) --
	(482.22, 90.06);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (468.63, 95.37) --
	(468.63, 98.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (468.63, 96.69) --
	(456.67, 96.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (456.67, 95.37) --
	(456.67, 98.02);
\definecolor{drawColor}{RGB}{51,34,136}
\definecolor{fillColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (490.92,141.77) circle (  1.96);
\definecolor{drawColor}{RGB}{170,68,153}
\definecolor{fillColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.42,149.72) circle (  1.96);
\definecolor{drawColor}{RGB}{51,34,136}
\definecolor{fillColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (472.76,486.48) circle (  1.96);
\definecolor{drawColor}{RGB}{170,68,153}
\definecolor{fillColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (482.87,494.43) circle (  1.96);
\definecolor{drawColor}{RGB}{51,34,136}
\definecolor{fillColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (491.57,459.96) circle (  1.96);
\definecolor{drawColor}{RGB}{170,68,153}
\definecolor{fillColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (486.46,467.91) circle (  1.96);
\definecolor{drawColor}{RGB}{51,34,136}
\definecolor{fillColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (503.86,433.44) circle (  1.96);
\definecolor{drawColor}{RGB}{170,68,153}
\definecolor{fillColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (499.95,441.40) circle (  1.96);
\definecolor{drawColor}{RGB}{51,34,136}
\definecolor{fillColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (500.27,406.93) circle (  1.96);
\definecolor{drawColor}{RGB}{170,68,153}
\definecolor{fillColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (504.19,414.88) circle (  1.96);
\definecolor{drawColor}{RGB}{51,34,136}
\definecolor{fillColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (497.55,327.38) circle (  1.96);
\definecolor{drawColor}{RGB}{170,68,153}
\definecolor{fillColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.11,335.33) circle (  1.96);
\definecolor{drawColor}{RGB}{51,34,136}
\definecolor{fillColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (484.29,300.86) circle (  1.96);
\definecolor{drawColor}{RGB}{170,68,153}
\definecolor{fillColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (476.46,308.82) circle (  1.96);
\definecolor{drawColor}{RGB}{51,34,136}
\definecolor{fillColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (440.36,115.25) circle (  1.96);
\definecolor{drawColor}{RGB}{170,68,153}
\definecolor{fillColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (438.84,123.21) circle (  1.96);
\definecolor{drawColor}{RGB}{51,34,136}
\definecolor{fillColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (484.29,274.35) circle (  1.96);
\definecolor{drawColor}{RGB}{170,68,153}
\definecolor{fillColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (502.01,282.30) circle (  1.96);
\definecolor{drawColor}{RGB}{51,34,136}
\definecolor{fillColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.55,247.83) circle (  1.96);
\definecolor{drawColor}{RGB}{170,68,153}
\definecolor{fillColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.86,255.79) circle (  1.96);
\definecolor{drawColor}{RGB}{51,34,136}
\definecolor{fillColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (503.21,221.32) circle (  1.96);
\definecolor{drawColor}{RGB}{170,68,153}
\definecolor{fillColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (502.12,229.27) circle (  1.96);
\definecolor{drawColor}{RGB}{51,34,136}
\definecolor{fillColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.75,194.80) circle (  1.96);
\definecolor{drawColor}{RGB}{170,68,153}
\definecolor{fillColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (498.86,202.75) circle (  1.96);
\definecolor{drawColor}{RGB}{51,34,136}
\definecolor{fillColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (481.24,168.28) circle (  1.96);
\definecolor{drawColor}{RGB}{170,68,153}
\definecolor{fillColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.42,176.24) circle (  1.96);
\definecolor{drawColor}{RGB}{51,34,136}
\definecolor{fillColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.27, 88.74) circle (  1.96);
\definecolor{drawColor}{RGB}{170,68,153}
\definecolor{fillColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (462.65, 96.69) circle (  1.96);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (401.21,159.00) -- (520.82,159.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (401.21,132.49) -- (520.82,132.49);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] (401.21, 76.80) rectangle (520.82,506.36);
\end{scope}
\begin{scope}
\path[clip] (525.82, 76.80) rectangle (645.43,506.36);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (525.82, 76.80) rectangle (645.43,506.36);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (544.85, 76.80) --
	(544.85,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (572.03, 76.80) --
	(572.03,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (599.22, 76.80) --
	(599.22,506.36);

\path[draw=drawColor,line width= 0.3pt,line join=round] (626.40, 76.80) --
	(626.40,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82, 92.71) --
	(645.43, 92.71);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,119.23) --
	(645.43,119.23);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,145.75) --
	(645.43,145.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,172.26) --
	(645.43,172.26);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,198.78) --
	(645.43,198.78);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,225.29) --
	(645.43,225.29);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,251.81) --
	(645.43,251.81);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,278.33) --
	(645.43,278.33);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,304.84) --
	(645.43,304.84);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,331.36) --
	(645.43,331.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,357.87) --
	(645.43,357.87);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,384.39) --
	(645.43,384.39);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,410.91) --
	(645.43,410.91);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,437.42) --
	(645.43,437.42);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,463.94) --
	(645.43,463.94);

\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,490.45) --
	(645.43,490.45);

\path[draw=drawColor,line width= 0.5pt,line join=round] (531.26, 76.80) --
	(531.26,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (558.44, 76.80) --
	(558.44,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (585.63, 76.80) --
	(585.63,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (612.81, 76.80) --
	(612.81,506.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (639.99, 76.80) --
	(639.99,506.36);
\definecolor{drawColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (625.31,148.40) --
	(625.31,151.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (625.31,149.72) --
	(614.01,149.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (614.01,148.40) --
	(614.01,151.05);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (624.77,140.44) --
	(624.77,143.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (624.77,141.77) --
	(610.20,141.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (610.20,140.44) --
	(610.20,143.09);
\definecolor{drawColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (612.59,493.10) --
	(612.59,495.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (612.59,494.43) --
	(593.46,494.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (593.46,493.10) --
	(593.46,495.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (616.07,466.59) --
	(616.07,469.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (616.07,467.91) --
	(608.35,467.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (608.35,466.59) --
	(608.35,469.24);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (621.07,458.63) --
	(621.07,461.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (621.07,459.96) --
	(601.94,459.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (601.94,458.63) --
	(601.94,461.29);
\definecolor{drawColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (625.21,440.07) --
	(625.21,442.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] (625.21,441.40) --
	(621.29,441.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (621.29,440.07) --
	(621.29,442.72);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (628.47,432.12) --
	(628.47,434.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (628.47,433.44) --
	(619.12,433.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] (619.12,432.12) --
	(619.12,434.77);
\definecolor{drawColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (630.53,413.56) --
	(630.53,416.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (630.53,414.88) --
	(624.23,414.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (624.23,413.56) --
	(624.23,416.21);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (634.99,405.60) --
	(634.99,408.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (634.99,406.93) --
	(627.05,406.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] (627.05,405.60) --
	(627.05,408.25);
\definecolor{drawColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (637.82,387.04) --
	(637.82,389.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (637.82,388.37) --
	(635.21,388.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (635.21,387.04) --
	(635.21,389.69);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (636.95,379.09) --
	(636.95,381.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (636.95,380.41) --
	(629.55,380.41);

\path[draw=drawColor,line width= 0.6pt,line join=round] (629.55,379.09) --
	(629.55,381.74);
\definecolor{drawColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (616.40,360.52) --
	(616.40,363.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (616.40,361.85) --
	(612.05,361.85);

\path[draw=drawColor,line width= 0.6pt,line join=round] (612.05,360.52) --
	(612.05,363.18);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (622.16,352.57) --
	(622.16,355.22);

\path[draw=drawColor,line width= 0.6pt,line join=round] (622.16,353.90) --
	(602.81,353.90);

\path[draw=drawColor,line width= 0.6pt,line join=round] (602.81,352.57) --
	(602.81,355.22);
\definecolor{drawColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (620.64,334.01) --
	(620.64,336.66);

\path[draw=drawColor,line width= 0.6pt,line join=round] (620.64,335.33) --
	(607.26,335.33);

\path[draw=drawColor,line width= 0.6pt,line join=round] (607.26,334.01) --
	(607.26,336.66);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (636.41,326.05) --
	(636.41,328.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (636.41,327.38) --
	(601.83,327.38);

\path[draw=drawColor,line width= 0.6pt,line join=round] (601.83,326.05) --
	(601.83,328.71);
\definecolor{drawColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (563.55,121.88) --
	(563.55,124.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (563.55,123.21) --
	(560.73,123.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (560.73,121.88) --
	(560.73,124.53);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (579.10,113.93) --
	(579.10,116.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (579.10,115.25) --
	(570.29,115.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (570.29,113.93) --
	(570.29,116.58);
\definecolor{drawColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (626.08,280.98) --
	(626.08,283.63);

\path[draw=drawColor,line width= 0.6pt,line join=round] (626.08,282.30) --
	(621.83,282.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (621.83,280.98) --
	(621.83,283.63);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (626.18,273.02) --
	(626.18,275.67);

\path[draw=drawColor,line width= 0.6pt,line join=round] (626.18,274.35) --
	(595.63,274.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] (595.63,273.02) --
	(595.63,275.67);
\definecolor{drawColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (619.12,254.46) --
	(619.12,257.11);

\path[draw=drawColor,line width= 0.6pt,line join=round] (619.12,255.79) --
	(613.57,255.79);

\path[draw=drawColor,line width= 0.6pt,line join=round] (613.57,254.46) --
	(613.57,257.11);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (625.42,246.51) --
	(625.42,249.16);

\path[draw=drawColor,line width= 0.6pt,line join=round] (625.42,247.83) --
	(598.02,247.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (598.02,246.51) --
	(598.02,249.16);
\definecolor{drawColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (628.36,227.95) --
	(628.36,230.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] (628.36,229.27) --
	(624.23,229.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (624.23,227.95) --
	(624.23,230.60);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (631.95,219.99) --
	(631.95,222.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (631.95,221.32) --
	(626.29,221.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] (626.29,219.99) --
	(626.29,222.64);
\definecolor{drawColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (626.08,196.13) --
	(626.08,201.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (626.08,198.78) --
	(623.03,198.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (623.03,196.13) --
	(623.03,201.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (617.49,174.91) --
	(617.49,177.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] (617.49,176.24) --
	(612.27,176.24);

\path[draw=drawColor,line width= 0.6pt,line join=round] (612.27,174.91) --
	(612.27,177.56);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (618.25,166.96) --
	(618.25,169.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (618.25,168.28) --
	(604.44,168.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] (604.44,166.96) --
	(604.44,169.61);
\definecolor{drawColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (602.15, 95.37) --
	(602.15, 98.02);

\path[draw=drawColor,line width= 0.6pt,line join=round] (602.15, 96.69) --
	(594.76, 96.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] (594.76, 95.37) --
	(594.76, 98.02);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (611.61, 87.41) --
	(611.61, 90.06);

\path[draw=drawColor,line width= 0.6pt,line join=round] (611.61, 88.74) --
	(601.72, 88.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (601.72, 87.41) --
	(601.72, 90.06);
\definecolor{drawColor}{RGB}{17,119,51}
\definecolor{fillColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (619.66,149.72) circle (  1.96);
\definecolor{drawColor}{RGB}{221,204,119}
\definecolor{fillColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (617.49,141.77) circle (  1.96);
\definecolor{drawColor}{RGB}{17,119,51}
\definecolor{fillColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (603.02,494.43) circle (  1.96);
\definecolor{drawColor}{RGB}{221,204,119}
\definecolor{fillColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (597.59,486.48) circle (  1.96);
\definecolor{drawColor}{RGB}{17,119,51}
\definecolor{fillColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (612.27,467.91) circle (  1.96);
\definecolor{drawColor}{RGB}{221,204,119}
\definecolor{fillColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (611.50,459.96) circle (  1.96);
\definecolor{drawColor}{RGB}{17,119,51}
\definecolor{fillColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (623.25,441.40) circle (  1.96);
\definecolor{drawColor}{RGB}{221,204,119}
\definecolor{fillColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (623.79,433.44) circle (  1.96);
\definecolor{drawColor}{RGB}{17,119,51}
\definecolor{fillColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (627.38,414.88) circle (  1.96);
\definecolor{drawColor}{RGB}{221,204,119}
\definecolor{fillColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (630.97,406.93) circle (  1.96);
\definecolor{drawColor}{RGB}{17,119,51}
\definecolor{fillColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (636.51,388.37) circle (  1.96);
\definecolor{drawColor}{RGB}{221,204,119}
\definecolor{fillColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (633.25,380.41) circle (  1.96);
\definecolor{drawColor}{RGB}{17,119,51}
\definecolor{fillColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (614.22,361.85) circle (  1.96);
\definecolor{drawColor}{RGB}{221,204,119}
\definecolor{fillColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (612.48,353.90) circle (  1.96);
\definecolor{drawColor}{RGB}{17,119,51}
\definecolor{fillColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (613.90,335.33) circle (  1.96);
\definecolor{drawColor}{RGB}{221,204,119}
\definecolor{fillColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (619.12,327.38) circle (  1.96);
\definecolor{drawColor}{RGB}{17,119,51}
\definecolor{fillColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (562.14,123.21) circle (  1.96);
\definecolor{drawColor}{RGB}{221,204,119}
\definecolor{fillColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (574.75,115.25) circle (  1.96);
\definecolor{drawColor}{RGB}{17,119,51}
\definecolor{fillColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (623.90,282.30) circle (  1.96);
\definecolor{drawColor}{RGB}{221,204,119}
\definecolor{fillColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (610.96,274.35) circle (  1.96);
\definecolor{drawColor}{RGB}{17,119,51}
\definecolor{fillColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (616.29,255.79) circle (  1.96);
\definecolor{drawColor}{RGB}{221,204,119}
\definecolor{fillColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (611.72,247.83) circle (  1.96);
\definecolor{drawColor}{RGB}{17,119,51}
\definecolor{fillColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (626.29,229.27) circle (  1.96);
\definecolor{drawColor}{RGB}{221,204,119}
\definecolor{fillColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (629.12,221.32) circle (  1.96);
\definecolor{drawColor}{RGB}{17,119,51}
\definecolor{fillColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (624.55,198.78) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (614.88,176.24) circle (  1.96);
\definecolor{drawColor}{RGB}{221,204,119}
\definecolor{fillColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (611.40,168.28) circle (  1.96);
\definecolor{drawColor}{RGB}{17,119,51}
\definecolor{fillColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (598.46, 96.69) circle (  1.96);
\definecolor{drawColor}{RGB}{221,204,119}
\definecolor{fillColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (606.72, 88.74) circle (  1.96);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (525.82,159.00) -- (645.43,159.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (525.82,132.49) -- (645.43,132.49);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] (525.82, 76.80) rectangle (645.43,506.36);
\end{scope}
\begin{scope}
\path[clip] (152.00,506.36) rectangle (271.61,521.43);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (152.00,506.36) rectangle (271.61,521.43);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (211.80,511.14) {All};
\end{scope}
\begin{scope}
\path[clip] (276.61,506.36) rectangle (396.21,521.43);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (276.61,506.36) rectangle (396.21,521.43);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (336.41,511.14) {By gender};
\end{scope}
\begin{scope}
\path[clip] (401.21,506.36) rectangle (520.82,521.43);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (401.21,506.36) rectangle (520.82,521.43);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (461.02,511.14) {By education};
\end{scope}
\begin{scope}
\path[clip] (525.82,506.36) rectangle (645.43,521.43);
\definecolor{drawColor}{gray}{0.20}
\definecolor{fillColor}{gray}{0.85}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (525.82,506.36) rectangle (645.43,521.43);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (585.63,511.14) {By age};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round] (157.44, 74.30) --
	(157.44, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (184.62, 74.30) --
	(184.62, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (211.80, 74.30) --
	(211.80, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (238.99, 74.30) --
	(238.99, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (266.17, 74.30) --
	(266.17, 76.80);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (157.44, 66.79) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (184.62, 66.79) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (211.80, 66.79) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (238.99, 66.79) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (266.17, 66.79) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round] (282.04, 74.30) --
	(282.04, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (309.23, 74.30) --
	(309.23, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (336.41, 74.30) --
	(336.41, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (363.59, 74.30) --
	(363.59, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (390.78, 74.30) --
	(390.78, 76.80);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (282.04, 66.79) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (309.23, 66.79) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (336.41, 66.79) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (363.59, 66.79) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (390.78, 66.79) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round] (406.65, 74.30) --
	(406.65, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (433.84, 74.30) --
	(433.84, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (461.02, 74.30) --
	(461.02, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (488.20, 74.30) --
	(488.20, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (515.39, 74.30) --
	(515.39, 76.80);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (406.65, 66.79) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (433.84, 66.79) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (461.02, 66.79) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (488.20, 66.79) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (515.39, 66.79) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round] (531.26, 74.30) --
	(531.26, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (558.44, 74.30) --
	(558.44, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (585.63, 74.30) --
	(585.63, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (612.81, 74.30) --
	(612.81, 76.80);

\path[draw=drawColor,line width= 0.5pt,line join=round] (639.99, 74.30) --
	(639.99, 76.80);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (531.26, 66.79) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (558.44, 66.79) {25};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (585.63, 66.79) {50};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (612.81, 66.79) {75};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (639.99, 66.79) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33, 94.28) {USA};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33, 85.64) {(National, 1959)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,120.79) {Russia};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,112.15) {(Subnational, 61 regions, 22125)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,142.99) {All LMICs};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,173.83) {Uganda 2};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,165.19) {(Subnational, 1 district, 1366)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,200.34) {Uganda 1};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,191.70) {(Subnational, 13 districts, 3362)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,226.86) {Sierra Leone 2};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,218.22) {(National, 2110)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,253.37) {Sierra Leone 1};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,244.73) {(National, 1070)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,279.89) {Rwanda};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,271.25) {(National, 1355)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,306.41) {Pakistan 2};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,297.77) {(Subnational, 1 province, 1492)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,332.92) {Pakistan 1};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,324.28) {(Subnational, 2 districts, 1633)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,359.44) {Nigeria};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,350.80) {(Subnational, 1 state, 1868)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,385.95) {Nepal};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,377.31) {(Subnational, 2 districts, 1389)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,412.47) {Mozambique};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,403.83) {(Subnational, 2 cities, 862)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,438.99) {India};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,430.35) {(Subnational, Slums in 2 cities, 3348)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,465.50) {Colombia};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,456.86) {(National, 1012)};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,492.02) {Burkina Faso};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,483.38) {(National, 977)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50, 92.71) --
	(152.00, 92.71);

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,119.23) --
	(152.00,119.23);

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,145.75) --
	(152.00,145.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,172.26) --
	(152.00,172.26);

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,198.78) --
	(152.00,198.78);

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,225.29) --
	(152.00,225.29);

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,251.81) --
	(152.00,251.81);

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,278.33) --
	(152.00,278.33);

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,304.84) --
	(152.00,304.84);

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,331.36) --
	(152.00,331.36);

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,357.87) --
	(152.00,357.87);

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,384.39) --
	(152.00,384.39);

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,410.91) --
	(152.00,410.91);

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,437.42) --
	(152.00,437.42);

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,463.94) --
	(152.00,463.94);

\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,490.45) --
	(152.00,490.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (398.71, 55.85) {estimate};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (258.71,  5.00) rectangle (538.72, 43.91);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (263.71, 21.01) {Subgroups};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (314.33, 24.45) rectangle (328.79, 38.91);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (315.78, 31.68) -- (327.34, 31.68);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{153,153,51}
\definecolor{fillColor}{RGB}{153,153,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (321.56, 31.68) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (314.33, 10.00) rectangle (328.79, 24.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (315.78, 17.23) -- (327.34, 17.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{68,170,153}
\definecolor{fillColor}{RGB}{68,170,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (321.56, 17.23) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (363.34, 24.45) rectangle (377.79, 38.91);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.6pt,line join=round] (364.78, 31.68) -- (376.35, 31.68);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{170,68,153}
\definecolor{fillColor}{RGB}{170,68,153}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (370.56, 31.68) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (363.34, 10.00) rectangle (377.79, 24.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.6pt,line join=round] (364.78, 17.23) -- (376.35, 17.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{51,34,136}
\definecolor{fillColor}{RGB}{51,34,136}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (370.56, 17.23) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (462.93, 24.45) rectangle (477.38, 38.91);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.37, 31.68) -- (475.94, 31.68);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{17,119,51}
\definecolor{fillColor}{RGB}{17,119,51}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (470.16, 31.68) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (462.93, 10.00) rectangle (477.38, 24.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (464.37, 17.23) -- (475.94, 17.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{221,204,119}
\definecolor{fillColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (470.16, 17.23) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (503.83, 24.45) rectangle (518.28, 38.91);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{204,102,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (505.27, 31.68) -- (516.84, 31.68);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{204,102,119}
\definecolor{fillColor}{RGB}{204,102,119}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (511.05, 31.68) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (333.79, 28.93) {Female};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (333.79, 14.47) {Male};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (382.79, 28.93) {Up to Secondary};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (382.79, 14.47) {More than Secondary};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (482.38, 28.93) {$< 55$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (482.38, 14.47) {$55 +$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (523.28, 28.93) {All};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.20] at (  5.00,528.76) {If a COVID-19 vaccine becomes available in [country], would you take it?};
\end{scope}
\end{tikzpicture}

\end{document}

### 2021-03-23 paper.tex
drop drive calls
update

@@
 Burkina Faso & Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available?
-& Doctors or other staff at a community health clinic & Advice from Ministry of Health & Family members; Friends you see and talk to; Friends you-'ve made online & Famous person; Religious leaders; Traditional Healers & Traditional media (newspaper, radio);Online medical discussion groups & Other/ Someone else\\
+& Doctors or other staff at a community health clinic & Advice from Ministry of Health & Family members; Friends you see and talk to; Friends you-'ve made online & Famous person; Religious leaders; Traditional Healers & Traditional media (newspaper, radio); Online medical discussion groups & Other/ Someone else\\
 Colombia & Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available?
-& Doctors or other staff at a community health clinic & Advice of the Instituto Nacional de Salud & Family members; Friends you see and talk to; Friends you've made online & Famous person; Religious leaders; Traditional Healers & Traditional media (newspaper, radio);Online medical discussion groups & Other/ Someone else\\
+& Doctors or other staff at a community health clinic & Advice of the Instituto Nacional de Salud & Family members; Friends you see and talk to; Friends you've made online & Famous person; Religious leaders; Traditional Healers & Traditional media (newspaper, radio); Online medical discussion groups & Other/ Someone else\\
 Nepal & Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available?

### 2021-03-23 2_tables.Rmd
no google drive

---
title: 'COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging: Replication Code'
date: "11/03/2021"
output:
  html_document:
    number_sections: yes
    theme: cosmo
    code_folding: hide
    toc: yes
  bookdown::html_document2: default
---

```{r setup3, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

if (!require(pacman)) install.packages("pacman")

pacman::p_load(tidyverse, magrittr, knitr, kableExtra, DT, lazyeval, 
               labelled, forcats, readxl, estimatr, ggforce, fastDummies,
               stringr, RColorBrewer, readstata13, metaplus, sjlabelled, ggrepel, tikzDevice)

options(knitr.kable.NA = '.')

base_font_size <- 12

```

# Set up

This code takes cleaned and aggregated data as input. Cleaning and aggregation is done in `1_cleaning.Rmd`.

## Helper functions

```{r}

# The helper renormalizes weights so that each study gets the 
# same total weight even if they are missing data

country_weighting <- function(data)
  data %>% 
    dplyr::group_by(country) %>% 
    dplyr::mutate(weight = weight/sum(weight)) %>% 
    dplyr::ungroup()

lm_helper <- function(data,...) {
  data %>% 
    country_weighting() %>% 
    estimatr::lm_robust(data = .,...) %>% 
    {bind_cols( tidy(.), n = nobs(.) )}
}

# Subgroup analysis : Function to apply analysis function over groups

grp_analysis <- function(df, y, x)

  df %>%
    dplyr::filter(if_all(c(all_of(x), all_of(y), cluster, weight), ~ !is.na(.))) %>%
    dplyr::nest_by(group, get(x)) %>%
    dplyr::summarize(
      lm_helper(data = data, 
                formula = as.formula(paste0(y, "~ 1")), cluster = cluster,
                weight = weight, se_type = "stata"), .groups = "drop") %>% 
    dplyr::rename(!!x := "get(x)")

# Reasons analysis: Function to apply analysis function over groups

reasons_together <- function(df, reason, num = "Yes")

  df %>%
    dplyr::filter(take_vaccine %in% num, 
                  if_all(c(all_of(reason), cluster, weight), ~ !is.na(.))) %>%
    dplyr::nest_by(group) %>%
    dplyr::summarize(
      lm_helper(data = data, 
                formula = as.formula(paste0(reason, "~ 1")), 
                cluster = cluster,
                weight = weight, se_type = "stata"), .groups = "drop")

reasons_together_subgroup <- function(df, reason, num = "Yes", 
                                      dem_group = NA, dem_subgroup = NA){

  if (dem_group == "gender")
    df <- filter(df, gender %in% dem_subgroup)

  df %>%
    dplyr::filter(take_vaccine %in% num,
                  !is.na(get(reason))) %>%
    dplyr::nest_by(group) %>%
    dplyr::summarize(
      lm_helper(data = data, 
                formula = as.formula(paste0(reason, "~ 1")), cluster = cluster,
                weight = weight, se_type = "stata"), .groups = "drop")
}

```

## Final cleaning and harmonization of weights

```{r df2}

# Call data created in 1_cleaning.Rmd
df <- readr::read_csv("3_rep_data/combined.csv", guess_max = 30000)

# If no cluster information given for a study then individuals are clusters 
# Ensure cluster ids are distinct across studies
df <- 
  df %>% 
  dplyr::group_by(study) %>% 
  dplyr::mutate(
    cluster = ifelse(is.na(cluster), paste(1:n()), cluster),
    cluster = paste0(gsub(" ", "_", tolower(country)), "_", cluster))

# Weights sum to 1 in each study and recode age and education into binary bins
df <- 
  df %>% 
  dplyr::group_by(study) %>% 
  dplyr::mutate(
         weight_replace = mean(weight, rm.na = TRUE),
         weight = if_else(is.na(weight), if_else(is.na(weight_replace), 1, weight_replace), weight),
         weight = weight/sum(weight)) %>% 
  dplyr::ungroup() %>%
  dplyr::mutate(
    age_groups = as.character(cut(x = age, breaks = c(-Inf, 18, 30, 45, 60, +Inf), right = F)),
    age_groups_binary = ifelse(age >= 55, "55+", "<55"),
    educ_binary = if_else(educ == "More than secondary", "> Secondary", "Up to Secondary"))

# We create a new dataframe with countries and with "All" (only LMICs). Countries are clusters in "All" analysis
# USA and Russia excluded from "All" set

df2 <- 
  dplyr::bind_rows(
    mutate(df, group = country),
    mutate(filter(df, country != "USA" & country != "Russia"), group = "All")) %>% 
  mutate(
    cluster = if_else(group == "All", 
                      gsub(pattern = " ", replacement = "_", x = tolower(country)), 
                      cluster)) 
```

## Data checks

Checks on data structure. Note `n`, missingness, presence of data on weights or clusters.

### Data structure

```{r}

df %>% group_by(country) %>%
  summarize(n = n(), 
            sd_wt = sd(weight, na.rm = TRUE)/mean(weight, na.rm = TRUE), 
            cl_size = n()/length(unique(cluster)), 
            take_1 = mean((take_vaccine == "Yes")[take_vaccine == "Yes" | take_vaccine == "No" ], na.rm = TRUE),
            take_2 = mean((take_vaccine == "Yes"), na.rm = TRUE),
            take_3 = mean(take_vaccine_num, na.rm = TRUE),
            take_dk = mean(take_vaccine == "DK"),
            .take = mean(is.na(take_vaccine_num)), .age = mean(is.na(age)),
            .gender = mean(is.na(gender)), .educ = mean(is.na(educ))) %>%
  kable(digits = 2, 
        caption = "Observations, missingness patterns, data structure. Column .var is the share missing for variable var.", booktabs = TRUE, linesep = "", format.args = list(big.mark = ",", 
  scientific = FALSE))

```

```{r, include=FALSE}

nas <- df %>% group_by(country) %>%
  summarize(n = n(),
            take_vaccine_na = mean(!is.na(take_vaccine)),
            gender_na = mean(is.na(gender)),
            educ_na= mean(is.na(educ)),
            age_na= mean(is.na(age))) %>%
  kable(digits = 2, 
        col.names= c("Country", "N obs", "Take vaccine", "Gender", "Education", "Age"),
        caption = "Observations and missingness patterns", 
        booktabs = TRUE, linesep = "", 
        format.args = list(big.mark = ",", scientific = FALSE),
  format = "latex") %>% 
  kableExtra::kable_styling(font_size = base_font_size - 2, full_width = FALSE) %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 9 show the percentage of observations that are not missing values for each variable included in Figure 1.",
    threeparttable = T)

df %>% group_by(country) %>%
  summarize(n = n(),
            take_vaccine_na = mean(!is.na(take_vaccine)),
            gender_na = mean(is.na(gender)),
            educ_na= mean(is.na(educ)),
            age_na= mean(is.na(age))) %>%
  kable(digits = 2, 
        col.names= c("Country", "N obs", "Take vaccine", "Gender", "Education", "Age"),
        caption = "Observations and missingness patterns.", 
        linesep = "", 
        format.args = list(big.mark = ",", scientific = FALSE),
  format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 9 show the percentage of observations that are not missing values for each variable included in Figure 1.",
    threeparttable = T)

```

### Age distribution

```{r, fig.height = 6, fig.width = 6}
df %>% 
  select(country, age) %>%
  gather(category, value, -country) %>%
  mutate(value = as.numeric(value)) %>%
  ggplot(aes(value)) + geom_density() + facet_wrap(~country, ncol = 3)
```

### Gender, education distribution

```{r, fig.height = 13, fig.width = 6}
df %>% 
  select(country, gender, educ) %>%
  gather(category, value, -country) %>%
    ggplot(aes(value)) +  geom_bar() + facet_grid(country ~ category, scales = "free")

```

# Tables and Figures

## Table 1: Vaccine data from WGM, WHO

```{r tab1}

# Call data from WGM
dfwgm <- read.csv("3_rep_data/table_wgm.csv")

# Call data from WHO
df_vacc_coveragebis <- read.csv("3_rep_data/vacc_cov.csv")

# Put together and order labels

table_1b <- dfwgm %>%
  left_join(df_vacc_coveragebis) %>%
  mutate(country = as.factor(country),
         country = forcats::fct_relevel(country, "Russia", "USA", after = Inf)) %>% 
  arrange(country) %>%
  select(country, Effectiveness, Safety, Important, BCG, DTP1, MCV1, Coverage)

# To Latex

tab_1b <- 
knitr::kable(
  table_1b,
  caption =  "Vaccination beliefs and coverage for the countries in our sample",
  col.names = c("",
                "Effective","Safe","Important for children to have",
                "Tuberculosis (BCG)", "Diphtheria, Tetanus and Pertussis (DTP1)",
                "Measles (MCV1)",
                "% of parents with any child that was ever vaccinated"),
  format = "latex", booktabs = T, linesep = "", align = c("l", rep("c", 7)), label = "otherv") %>% 
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"), 
                            full_width = FALSE, font_size = base_font_size - 2)  %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::add_header_above(c(" " = 1, 
                                 "% Respondents agreeing Vaccines are..." = 3,
                                 "Vaccine coverage in 2019 (% of infants)" = 3,
                                 " " = 1), bold = TRUE) %>%
  kableExtra::column_spec(1:5, width = "9em") %>% 
  kableExtra::column_spec(6:7, width = "5em") %>%
  kableExtra::column_spec(8, width = "9em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 1 presents an overview of vaccination beliefs and incidence across countries in our sample. Columns 2-4 and 8 use data from the Wellcome Global Monitor 2018. Column 8 shows the percentage of respondents who are parents and report having had any of their children ever vaccinated. Columns 2-4 show the percentage of all respondents that either strongly agree or somewhat agree with the statement above each column. All percentages are obtained using national weights. Columns 5-7 use data from the World Health Organization on vaccine incidence. Columns 5-7 report the percentage of infants per country receiving the vaccine indicated in each column.", 
    threeparttable = T) %>%
  kableExtra::landscape()

knitr::kable(
  table_1b,
  caption =  "Vaccination beliefs and coverage for the countries in our sample",
  col.names = c("",
                "Effective","Safe","Important for children to have",
                "Tuberculosis (BCG)", "Diphtheria, Tetanus and Pertussis (DTP1)",
                "Measles (MCV1)",
                "% of parents with any child that was ever vaccinated"),
  format = "html", booktabs = T, linesep = "", align = c("l", rep("c", 7)), label = "otherv") %>% 
  kableExtra::kable_styling(full_width = FALSE)  %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::add_header_above(c(" " = 1, 
                                 "% Respondents agreeing Vaccines are..." = 3,
                                 "Vaccine coverage in 2019 (% of infants)" = 3,
                                 " " = 1), bold = TRUE) %>%
  kableExtra::column_spec(1:5, width = "9em") %>% 
  kableExtra::column_spec(6:7, width = "5em") %>%
  kableExtra::column_spec(8, width = "9em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 1 presents an overview of vaccination beliefs and incidence across countries in our sample. Columns 2-5 use data from the Wellcome Global Monitor 2018. Column 2 shows the percentage of respondents who are parents and report having had any of their children ever vaccinated. Columns 3-5 show the percentage of all respondents that either strongly agree or somewhat agree with the statement above each column. All percentages are obtained using national weights. Columns 6-8 use data from the World Health Organization on vaccine incidence. Columns 6-8 report the percentage of infants per country receiving the vaccine indicated in each column.", 
    threeparttable = T)

```

## Table with summary of samples

```{r sampling, fig.width = 6, fig.height = 8}

tab_sampling <- 
  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select("Study" = "country", 
                "Geographic scope", "Sampling methodology", "Survey modality", "Weights") %>%
  knitr::kable(
    caption =  "Summary of studies sampling",
    format = "latex", booktabs = T, linesep = "", label = "sampling") %>% 
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
                            font_size = base_font_size - 2) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>%
  kableExtra::column_spec(2, width = "12em")  %>%
  kableExtra::column_spec(3, width = "30em") %>% 
  kableExtra::landscape()

readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select("Study" = "country", 
                "Geographic scope", "Sampling methodology", "Survey modality", "Weights") %>%
  knitr::kable(caption =  "Summary of studies' sampling", linesep = "", format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>%
  kableExtra::column_spec(2, width = "12em")  %>%
  kableExtra::column_spec(3, width = "30em")
```
## Main Results: Acceptance Rates (disaggregated by group)

### Figure

```{r fig1, fig.width = 7, fig.height = 7}

# Prep levels

main_results <- 
  df2 %>% 
  dplyr::filter(dplyr::if_all(c(take_vaccine_num, cluster, weight), ~ !is.na(.))) %>% 
  dplyr::nest_by(group) %>%
  dplyr::summarize(
    lm_helper(data = data, 
              formula = take_vaccine_num ~ 1, cluster = cluster,
              weight = weight, se_type = "stata"),
    .groups = "drop")

# Gender
acc_by_gender <- grp_analysis(df2, y = "take_vaccine_num", x = "gender")

# Education (all original categories and binary recoding)
acc_by_educ        <- grp_analysis(df2, y = "take_vaccine_num", x = "educ")
acc_by_educ_binary <- grp_analysis(df2, y = "take_vaccine_num", x = "educ_binary")

# Age (all original categories and binary recoding)
# acc_by_age <- grp_analysis(df2, y = "take_vaccine_num", x = "age_groups")
acc_by_age_binary <- grp_analysis(df2, y = "take_vaccine_num", x = "age_groups_binary")

# Put them together in a single df. Make estimates "percentages" and round
ans <- 
  dplyr::bind_rows(
    main_results %>% mutate(cat = "All", var = "All"),
    acc_by_gender %>% rename(cat = gender) %>% mutate(var = "By gender"),
    acc_by_educ_binary %>% rename(cat = educ_binary) %>% mutate(var = "By education"),
    acc_by_age_binary %>% rename(cat = age_groups_binary) %>% mutate(var = "By age")) %>%
  dplyr::mutate(across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 1)))

# Join with a tags df, which includes details on the study (national or subnational)
tags <- 
  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select(group = country, tag = "Geographic scope") %>%
  dplyr::left_join(filter(ans, cat == "All"), by = "group") %>%
  dplyr::mutate(tag = paste0(group, " (", tag, ", ", n, ")")) %>%
  dplyr::select(group, tag)

# Prepare df to plot. Important but ugly relevel of factors, happening all over the code

ans %<>% 
  dplyr::left_join(tags) %>%
  dplyr::mutate(tag = ifelse(group == "All", "All LMICs", tag)) %>%
  # group_by(var) %>% 
  # arrange(cat) %>%
  dplyr::mutate(
    var = factor(var, levels = c("All", "By gender", "By education", "By age")),
    cat = factor(
      cat, ordered = TRUE,
      levels = rev(c(c("Female", "Male", "Up to Secondary", 
                       "> Secondary", "<55", "55+", "All"))),
      labels = rev(c("Female", "Male", "Up to Secondary", 
                     "More than Secondary", "$< 55$", "$55 +$", "All"))),
    tag = gsub(pattern = " \\(", "\\\n\\(", tag))

special_cases <- 
  sort(unique(ans$tag)[grep(unique(ans$tag), pattern = "All LMICs|Russia|USA")])

ans %<>% 
  dplyr::mutate(
    tag = 
      factor(x = tag, ordered = TRUE,
             levels = rev(c(sort(unique(tag)[!(unique(tag) %in% special_cases)]), special_cases))))

#Colour blind palette (available palletes are smaller so we expand it)
safe_colorblind_palette <- c("#CC6677", "#DDCC77", "#117733", "#332288", "#AA4499", 
                             "#44AA99", "#999933", "#882255", "#661100", "#6699CC", "#888888", 
                             "#88CCEE")

#Plot
fig_1 <- 
  ans %>% 
  ggplot(data = ., aes(x = tag, y = estimate, color = cat)) + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
                size = .5, width = .2, position = position_dodge(0.6)) + 
  geom_point(position = position_dodge(0.6)) +
  facet_grid(. ~ var, scales = "free_x", space = "free") + 
  coord_flip() +
  guides(color = guide_legend(reverse = TRUE, nrow = 2)) +
  geom_vline(xintercept = 3.5, color = "darkgrey") +
  geom_vline(xintercept = 2.5, color = "darkgrey") +
  scale_colour_manual(values = safe_colorblind_palette) +
  labs(title = "If a COVID-19 vaccine becomes available in [country], would you take it?", 
       color = "Subgroups", x = "") +
  theme_bw(base_size = (base_font_size - 2)) + ylim(c(0,100)) +
  theme(legend.position = "bottom",
        plot.caption = element_text(hjust = 0), #Default is hjust=1
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot",
        axis.text.y = element_text(hjust = 0))

fig_1
```

### Differences in means

```{r analysis}

# Analysis of differences in means only LMICs
# Notice that Uganda 1 is dropped, because of it does not have reference categories for gender or age
# Notice that we are using df (and not df2) as data, since it does not include "All"

# Population estimate (clustering on country)

differences_means_gen_age <- 
  lapply(c("gender", "age_groups_binary"), function(i) {
    df %>% 
      dplyr::filter(country != "USA" & country != "Russia" & country != "Uganda 1") %>%
      dplyr::filter(if_all(c(all_of(i), all_of("take_vaccine_num")), ~ !is.na(.))) %>%
      country_weighting() %>%
      estimatr::lm_robust(as.formula(paste("take_vaccine_num ~", i)),
                          fixed_effects = ~country,
                          weight = weight,
                          cluster = country,
                          se_type = "stata",
                          data = .) %>% 
      tidy %>% 
      dplyr::select(estimate, std.error, p.value, df, term)
  }) %>% 
  dplyr::bind_rows(.)

differences_means_educ <- 
    df %>% 
      dplyr::filter(country != "USA" & country != "Russia") %>% 
      dplyr::filter(if_all(c(all_of("educ_binary"), all_of("take_vaccine_num")), ~ !is.na(.))) %>%
      country_weighting() %>%
      estimatr::lm_robust(
        take_vaccine_num ~educ_binary, 
        fixed_effects = ~country, 
        weight = weight, 
        cluster = country,
        se_type = "stata",
        data = .) %>% 
      tidy %>% 
      dplyr::select(estimate, std.error, p.value, df, term)

dif_gender <- 
  differences_means_gen_age %>% 
  dplyr::filter(term == "genderMale") %>% 
  pull(estimate) %>% 
  {. * 100} %>% 
  round(., 1)

dif_age <- 
  differences_means_gen_age %>% 
  dplyr::filter(term == "age_groups_binary55+") %>% 
  pull(estimate) %>% 
  {. * 100} %>% 
  round(., 1)

dif_educ <- 
  differences_means_educ %>% 
  dplyr::filter(term == "educ_binaryUp to Secondary") %>% 
  pull(estimate) %>% 
  {. * 100} %>% 
  round(., 1)

diffmeans <- 
  rbind(differences_means_gen_age, differences_means_educ) %>%
  dplyr::rename(Estimate = estimate,
         Std.error = std.error,
         P.value = p.value,
         "Degrees of freedom" = df,
         "Baseline category" = term) %>%
  dplyr::mutate(
    Variable = ifelse(`Baseline category` == "genderMale", 
                      "Gender", ""),
    Variable = ifelse(`Baseline category` == "age_groups_binary55+", 
                      "Age", Variable),
    Variable = ifelse(`Baseline category` == "educ_binaryUp to Secondary", 
                      "Education", Variable),
    `Baseline category` = ifelse(`Baseline category` == "genderMale", 
                                 "Male", `Baseline category`),
    `Baseline category` = ifelse(`Baseline category` == "age_groups_binary55+", 
                                 "55+", `Baseline category`),
    `Baseline category` = ifelse(`Baseline category` == "educ_binaryUp to Secondary", 
                                 "Up to secondary", `Baseline category`))

dmeans <- diffmeans %>%
  knitr::kable(
    digits = 2,
    caption =  "Differences in means",
    format = "latex", booktabs = T, linesep = "", label = "dmeans", align = "c") %>% 
  kableExtra::kable_styling(latex_options = c("hold_position"),
    font_size = base_font_size - 2, full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 8 shows the results of subgroup mean differences. Subgroup differences were generated considering only LMICs. The differences in means for gender and age do not include the Uganda 1 study, which only included female respondents under the age of 55. p-values come from a two-sided t-test from a linear regression.",
    threeparttable = T)

diffmeans %>%
  knitr::kable(
  caption =  "Differences in means",
  booktabs = T, linesep = "", label = "dmeans", digits = 2) %>% 
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 8 shows the results of subgroup mean differences. Subgroup differences were generated considering only LMICs. The differences in means for gender and age do not include the Uganda 1 study, which only included female respondents under the age of 55.",
    threeparttable = T)

```

### Differences in means: by study

```{r}
country_differences <-
  unique(df$country) %>%
  lapply(function(j){{
    dff <- filter(df, country == j)

    lapply(c("gender", "age_groups_binary", "educ_binary"), function(i){
      if (length(table(dff[[i]])) != 2)  {
        return(NULL)
      } else {
        estimatr::lm_robust(as.formula(paste("take_vaccine_num ~", i)),
                            weight = weight,
                            data = dff) %>%
          tidy %>%
          dplyr::select(estimate, std.error, p.value, df, term)}}
    ) } %>%
      dplyr::bind_rows() %>% 
      dplyr::mutate(country = j)}) %>% 
  dplyr::bind_rows() %>% 
  dplyr::arrange(term, country) %>% 
  dplyr::relocate(country, term) %>%
  dplyr::filter(term != "(Intercept)") %>% 
  dplyr::mutate(significant = p.value <= .05)

country_differences_summary <- 
  country_differences %>% 
  dplyr::filter(!(country %in% c("Russia", "USA"))) %>% 
  dplyr::group_by(term) %>% summarize(
    "positive " = sum(estimate > 0),
    "positive and significant" = sum(estimate > 0 & significant),
    "negative and significant" = sum(estimate < 0 & significant),
    "not significant" = sum(!significant),
    n = n())

knitr::kable(country_differences, 
             digits = 2, caption = "Differences between groups within studies ")

knitr::kable(country_differences_summary, 
             digits = 2, caption = "Differences between groups within studies (Summary)")

```

### Metaplus analysis

```{r, comment = ""}
# Metaplus (variance between countries, included in text)
mp <- metaplus::metaplus(
  yi  = main_results %>% filter(!(group %in% c("USA", "Russia", "All"))) %>% pull(estimate),
  sei = main_results %>% filter(!(group %in% c("USA", "Russia", "All"))) %>% pull(std.error))
mp_tau =  mp$results[2,1]

mp$results %>% kable(caption = "Metaplus  results")

```

### Generate quantities used in text

```{r}

# Mean of LMICs
ans_mean <- 
  ans %>% 
  dplyr::filter(cat == "All", group == "All") %>% 
  pull(estimate)

# Lowest and highest bounds for All mean estimate
ans_mean_low <- 
  ans %>% 
  dplyr::filter(cat == "All", group == "All") %>% 
  pull(conf.low)

ans_mean_high <-  
  ans %>% 
  dplyr::filter(cat == "All", group == "All") %>% 
  pull(conf.high)

# df of LMICs (no USA, Russia or All)
ans_stats <- 
  ans %>% 
  dplyr::filter(cat == "All", !(group %in% c("USA", "Russia", "All")))

# Median of LMICs
ans_median <- median(ans_stats$estimate)

# Interquartile range of LMIcs
ans_iqr <- IQR(ans_stats$estimate)

# Smallest and biggest acceptability of LMICs
ans_min <- 
  ans %>% 
  dplyr::filter(cat == "All" & group != "Russia" & group != "USA") %>% 
  pull(estimate) %>% min

ans_max <- 
  ans %>% 
  dplyr::filter(cat == "All" & group != "Russia" & group != "USA") %>% 
  pull(estimate) %>% max

# Rank by estimate
top_all <- 
  ans %>%
  dplyr::filter(cat == "All") %>% 
  dplyr::arrange(desc(estimate))

bottom_all <- 
  ans %>%
  dplyr::filter(cat == "All" & group != "Russia" & group != "USA") %>% 
  dplyr::arrange(estimate)

# USA and Russia estimate acceptability
usa_ans <- 
  ans %>%
  dplyr::filter(cat == "All" & group == "USA")

rus_ans <- 
  ans %>%
  dplyr::filter(cat == "All" & group == "Russia")

```

### Table version of Figure 1

```{r tabfig1}

# Here we are making "percentages" from the estimates and putting them together with confidence intervals
# Also we are going from long to wide

main_table <- 
  main_results %>%
  dplyr::mutate(
    across(c(estimate, conf.low, conf.high), list("_main" = ~ format(round(100 * ., 1), nsmall = 1))),
    conf_int__main = paste0("(", conf.low__main, ", ", conf.high__main, ")")) %>%
  dplyr::select(group, estimate__main, conf_int__main)

gender_table <- 
  acc_by_gender %>%
  dplyr::mutate(
    across(c(estimate, conf.low, conf.high), ~ format(round(100 * ., 1), nsmall = 1)),
    conf_int = paste0("(", conf.low, ", ", conf.high, ")")) %>%
  dplyr::select(group, gender, estimate, conf_int) %>% 
  tidyr::pivot_wider(names_from = gender, 
                     values_from = c(estimate, conf_int), 
                     names_sep = "__")

educ_table <- 
  acc_by_educ_binary %>%
  dplyr::mutate(
    across(c(estimate, conf.low, conf.high), ~ format(round(100 * ., 1), nsmall = 1)),
    conf_int = paste0("(", conf.low, ", ", conf.high, ")")) %>%
  dplyr::select(group, educ_binary, estimate, conf_int) %>% 
  tidyr::pivot_wider(names_from = educ_binary, 
                     values_from = c(estimate, conf_int), 
                     names_sep = "__")

age_table <- 
  acc_by_age_binary %>%
  dplyr::mutate(
    across(c(estimate, conf.low, conf.high), ~ format(round(100 * ., 1), nsmall = 1)),
    conf_int = paste0("(", conf.low, ", ", conf.high, ")")) %>%
  dplyr::select(group, age_groups_binary, estimate, conf_int) %>% 
  tidyr::pivot_wider(names_from = age_groups_binary, 
                     values_from = c(estimate, conf_int), 
                     names_sep = "__")

all_tables <- 
  main_table %>% 
  dplyr::left_join(gender_table) %>%
  dplyr::left_join(educ_table) %>% 
  dplyr::left_join(age_table) %>%
  dplyr::select(group, everything()) %>%
  dplyr::mutate(group = as.factor(group),
                group = forcats::fct_relevel(group, "All", "Russia", "USA", after = Inf)) %>% 
  dplyr::arrange(group) %>% 
  tidyr::pivot_longer(cols = c(starts_with("estimate__"), starts_with("conf_int__")),
                      names_to = c("type", ".value"),
                      names_pattern = "(.*)__(.*)") %>% 
  dplyr::mutate(group = ifelse(type == "conf_int", "", as.character(group)),
                group = ifelse(group == "All", "All LMICs", group)) %>% 
  dplyr::select(-type) %>% 
  dplyr::rename("Country" = "group", 
                "Average acceptability" = "main")

tab_fig1 <- 
  all_tables %>%
  knitr::kable(
    all_tables,
    caption = "If a COVID-19 vaccine becomes available in [country], would you take it? Disaggregated by subgroups", 
    format = "latex",  booktabs = T, linesep = "", 
    format.args = list(big.mark = ",", scientific = FALSE), 
    escape = F, align = "lccccccc", label = "maintabledis")  %>% 
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
                            font_size = base_font_size - 2, full_width = FALSE) %>%
  kableExtra::add_header_above(c("", "", "Gender" = 2, "Education" = 2, "Age" = 2), bold = TRUE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 4 shows percentage of respondents willing to take the COVID-19 vaccine as plotted in Figure 1. A 95% confidence interval is shown between parentheses",
    threeparttable = T)

all_tables %>%
  knitr::kable(
    caption = "If a COVID-19 vaccine becomes available in [country], would you take it? Disaggregated by subgroups", 
    align = "lccccccc", booktabs = T) %>% 
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::add_header_above(c("", "", "Gender" = 2, "Education" = 2, "Age" = 2), bold = TRUE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 4 shows percentage of respondents willing to take the COVID-19 vaccine as plotted in Figure 1. A 95% confidence interval is shown between parentheses",
    threeparttable = T)

```

## Reasons to take or not to take

### Table: Reasons to take the vaccine.

```{r tab2, fig.width = 12}

#There are idiosyncratic reasons why people would take the vaccine. I recoded them. But we keep only the core, which is common almost in all studies.
yes_vars <- 
  df2 %>% 
  dplyr::select(yes_vaccine_1, yes_vaccine_2, yes_vaccine_3) %>% 
  names

## Generate data for analysis of yes reasons
yes_vacc1 <- 
  lapply(yes_vars, reasons_together, df = df2, num = "Yes") %>%
  dplyr::bind_rows() %>%
  dplyr::mutate(across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 0)))

#Get percentage per yes reason category and make wide table
yes_vacc2 <- 
  yes_vacc1 %>%
  dplyr::mutate(estimate = format(estimate, nsmall = 0),
                conf_int = paste0("(", format(conf.low, nsmall = 0), 
                                  ", ", format(conf.high, nsmall = 0), ")")) %>%
  dplyr::select(group, estimate, conf_int, outcome, n) %>%
  tidyr::pivot_wider(names_from = outcome, values_from = c(estimate, conf_int, n), names_sep = "__") %>%
  tidyr::pivot_longer(cols = c(starts_with("estimate__"), starts_with("conf_int__")),
                      names_to = c("type", ".value"),
                      names_pattern = "(.*)__(.*)") %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    n = ifelse(group == "All", NA, unique(na.omit(c_across(starts_with("n__")))))) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(
    group = forcats::fct_relevel(as.factor(group), "All", "Russia", "USA", after = Inf)) %>% 
  dplyr::arrange(group) %>% 
  dplyr::mutate(across(c(group, n), ~ifelse(type == "conf_int", "", as.character(.))),
                group = ifelse(group == "All", "All LMICs", group)) %>% 
  dplyr::select(group, n, type, starts_with("yes_vaccine_"), -starts_with("n_yes_vaccine"), -type)

cnames <- c("Study", "N", "Self", "Family", 
          "Community")

#Table to Latex
tab_reasons_y <- 
  yes_vacc2 %>%
  knitr::kable(col.names = cnames,
      caption = "Reasons to take the vaccine", format = "latex", booktabs = T, 
      linesep = "", label = "yes", 
      format.args = list(big.mark = ",", scientific = FALSE), 
      escape = F, align = "lcccc") %>%
  kableExtra::kable_styling(full_width = FALSE, 
                            font_size = base_font_size - 2) %>%
  kableExtra::add_header_above(c(" " = 2, "Protection" = 3), bold = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>% 
  kableExtra::column_spec(2:4, width = "4em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine. The number of observations and percentage correponds only to people who would take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses. Studies India, Pakistan 1 and Pakistan 2 are not included because they either did not include the question or were not properly harmonized with the other studies.",
    threeparttable = T)

yes_vacc2 %>%
  knitr::kable(col.names = cnames,
      caption = "\\label{yes}Reasons to take the vaccine", 
      booktabs = T, linesep = "", 
      format.args = list(big.mark = ",", scientific = FALSE)) %>% 
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::add_header_above(c(" " = 2, "Protection" = 3), bold = TRUE) %>% 
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>% 
  kableExtra::column_spec(2:4, width = "4em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine. The number of observations and percentage correponds only to people who would take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses. Studies India, Pakistan 1 and Pakistan 2 are not included because they either did not include the question or were not properly harmonized with the other studies.",
    threeparttable = T)

```

### Calculate numbers used in text for acceptance

```{r analysis_yes, fig.width = 12, fig.height=10}

# All LMIcs estimate of self protection
yes_all <- 
  yes_vacc1 %>% 
  dplyr::filter(group == "All" & outcome == "yes_vaccine_1")

# Top and bottom LMICs countries for category self protection
yes_ <- 
  yes_vacc1 %>% 
  dplyr::filter(group != "All" & group != "USA" & group != "Russia" & outcome == "yes_vaccine_1")

yes_top <- yes_ %>% dplyr::arrange(desc(estimate))
yes_bottom <- yes_ %>% dplyr::arrange(estimate)

# All LMICs estimate of protection of family
yes_all_2 <- 
  yes_vacc1 %>% 
  dplyr::filter(group == "All" & outcome == "yes_vaccine_2")

# Top and bottom LMICs countries for category protection of family
yes_2 <- 
  yes_vacc1 %>% 
  dplyr::filter(group != "All" & group != "USA" & group != "Russia" & outcome == "yes_vaccine_2")

yes2_top <- yes_2 %>% dplyr::arrange(desc(estimate))
yes2_bottom <- yes_2 %>% dplyr::arrange(estimate)

# Estimate of self protection for Russia and the US
yes_usa <- 
  yes_vacc1 %>% 
  dplyr::filter(group != "All" & group == "USA" & outcome == "yes_vaccine_1")

yes_rus <- 
  yes_vacc1 %>% 
  dplyr::filter(group != "All" & group == "Russia" & outcome == "yes_vaccine_1")

# Estimate of protection of family for Russia and the US
yes2_usa <- 
  yes_vacc1 %>% 
  dplyr::filter(group != "All" & group == "USA" & outcome == "yes_vaccine_2")

yes2_rus <- 
  yes_vacc1 %>% 
  dplyr::filter(group != "All" & group == "Russia" & outcome == "yes_vaccine_2")

#Import df with tags (names of categories)
dictionary <- read_excel("2_input_data/dictionary.xlsx")

#Select core variables to be included in figure
no_vars <- 
  df2 %>% 
  dplyr::select(starts_with("no_vaccine_")) %>% 
  names

#Create estimates of % of each reason, re-level factors and get and categorize number of observations by subgroup
no_vacc <- 
  lapply(no_vars, reasons_together, df = df2, num = c("No", "DK")) %>%
  dplyr::bind_rows() %>% 
  dplyr::arrange(outcome) %>% 
  dplyr::mutate(
    across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 1)),
    n_sub = round(n * estimate, 0),
    n_sub = ifelse(n_sub == 0, NA_integer_, n_sub),
    group = 
      factor(group, 
             levels = rev(c("Burkina Faso", "Colombia", "Mozambique", 
                            "Nepal", "Nigeria", "Pakistan 1", "Rwanda", 
                            "Sierra Leone 1", "Sierra Leone 2", "Uganda 1", 
                            "Uganda 2", "All", "Russia", "USA" )))
  ) %>%
  dplyr::left_join(dictionary, by = "outcome") %>%
  dplyr::mutate(
    size = cut(n_sub, c(0, 50, 500, Inf), right = FALSE, include.lowest = FALSE),
    size = forcats::fct_recode(size, "500+" = "[500,Inf)"),
    tag = as.factor(tag),
    tag = 
      forcats::fct_relevel(tag,  
                           "Concerned about side effects", 
                           "Concerned about getting coronavirus from the vaccine", 
                           "Not concerned about getting seriously ill", 
                           "Doesn't think vaccines are effective", 
                           "Doesn't think Coronavirus outbreak is as serious as people say", 
                           "Doesn't like needles", 
                           "Allergic to vaccines", 
                           "Won't have time to get vaccinated", 
                           "Mentions a conspiracy theory", 
                           "Other reasons"))

```

```{r tab2all, fig.width = 12}

yes_vars <- 
  df2 %>% 
  dplyr::select(yes_vaccine_1, yes_vaccine_2, 
                yes_vaccine_3, yes_vaccine_4, 
                yes_vaccine_5, yes_vaccine_666) %>% 
  names

## Generate data for analysis of yes reasons
yes_vacc1 <- 
  lapply(yes_vars, reasons_together, df = df2, num = "Yes") %>%
  dplyr::bind_rows() %>%
  dplyr::mutate(across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 0)))

#Get percentage per yes reason category and make wide table
yes_vacc2 <- 
  yes_vacc1 %>%
  dplyr::mutate(estimate = format(estimate, nsmall = 0),
                conf_int = paste0("(", format(conf.low, nsmall = 0), 
                                  ", ", format(conf.high, nsmall = 0), ")")) %>%
  dplyr::select(group, estimate, conf_int, outcome, n) %>%
  tidyr::pivot_wider(names_from = outcome, values_from = c(estimate, conf_int, n), names_sep = "__") %>%
  tidyr::pivot_longer(cols = c(starts_with("estimate__"), starts_with("conf_int__")),
                      names_to = c("type", ".value"),
                      names_pattern = "(.*)__(.*)") %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(
    n = ifelse(group == "All", NA, unique(na.omit(c_across(starts_with("n__")))))) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(
    group = forcats::fct_relevel(as.factor(group), "All", "Russia", "USA", after = Inf)) %>% 
  dplyr::arrange(group) %>% 
  dplyr::mutate(across(c(group, n), ~ifelse(type == "conf_int", "", as.character(.))),
                group = ifelse(group == "All", "All LMICs", group)) %>% 
  dplyr::select(group, n, type, starts_with("yes_vaccine_"), -starts_with("n_yes_vaccine"), -type)

cnames <- c("Study", "N", "Self", "Family", 
          "Community", "Health workers", "Government", "Other")

#Table to Latex
tab_reasons_y_all <- 
  yes_vacc2  %>% 
  knitr::kable(col.names = cnames,
        caption = "Reasons to take the vaccine- all categories", 
        format = "latex", booktabs = T, linesep = "", 
        label = "yesall", 
        format.args = list(big.mark = ",", scientific = FALSE), 
        escape = F, align = c("l", rep("c", 7))) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
                            font_size = base_font_size - 2, full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::add_header_above(c(" " = 2, "Protection" = 3, "If recommended by" = 2, " " = 1), 
                               bold = TRUE) %>% 
  kableExtra::column_spec(1:8, width = "7em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 5 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine. The number of observations and percentage correponds only to people who would take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses",
    threeparttable = T)

yes_vacc2 %>%
  knitr::kable(col.names = cnames,
               caption = "Reasons to take the vaccine. All categories", 
               booktabs = T, linesep = "", align = c("l", rep("c", 7)),
               format.args = list(big.mark = ",", scientific = FALSE)) %>% 
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::add_header_above(c(" " = 2, "Protection" = 3, "If recommended by" = 2, " " = 1), 
                               bold = TRUE) %>% 
  kableExtra::column_spec(1:8, width = "7em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 5 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine. The number of observations and percentage correponds only to people who would take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses",
    threeparttable = T)

```

## Figure 2: reasons not to take

### Figure

```{r, fig.width = 10, fig.height = 7}
fig_2 <- 
  no_vacc %>% 
  dplyr::filter(!is.na(n_sub)) %>%
  dplyr::mutate(group = plyr::mapvalues(group, "All", "All LMICs")) %>% 
  ggplot(aes(group, estimate, color = tag)) + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
                size = .5, width = .2, position = position_dodge(0.6)) + 
  geom_point(shape = 16, position = position_dodge(0.6), aes(size = size)) +
  facet_grid(.~tag,  space = "free", labeller = label_wrap_gen(width = 15)) +
  scale_size_discrete(range = c(1,3), name = "Number of observations" ) +
  geom_vline(xintercept = 3.5, color = "darkgrey") +
  geom_vline(xintercept = 2.5, color = "darkgrey") + 
  guides(color = FALSE) +
  scale_colour_manual(values = safe_colorblind_palette) + 
  coord_flip() + theme_bw() +
  labs(title = "Why would you not take the COVID-19 vaccine?",
       x = "") +
  theme_bw() + ylim(c(0,100)) +
  theme(legend.position = "bottom",
        plot.caption = element_text(hjust = 0), #Default is hjust=1
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        plot.caption.position =  "plot",
        axis.text.y = element_text(hjust = 0))

fig_2
```

### Calculate numbers used in text for refusal

```{r analysis_no}

## Generate data for analysis of no reasons

# Top LMIC countries concerned about side effects
side_top <- 
  no_vacc %>% 
  dplyr::filter(tag == "Concerned about side effects" & group != "All" & 
                  group != "USA" & group != "Russia") %>%
  dplyr::arrange(desc(estimate))

# Concern about side effects in Russia and the US
side_rus <- 
  no_vacc %>% 
  dplyr::filter(tag == "Concerned about side effects" &  group == "Russia") %>% 
  dplyr::arrange(desc(estimate))

side_usa <- 
  no_vacc %>% 
  dplyr::filter(tag == "Concerned about side effects" & group == "USA") %>% 
  dplyr::arrange(desc(estimate))

# Top LMIC counties that are allergic to vaccines
allergies_top <- 
  no_vacc %>% 
  dplyr::filter(tag == "Allergic to vaccines" & group != "All") %>% 
  dplyr::arrange(desc(estimate))

# Top LMIC countries that do not like needles
needles_top <- 
  no_vacc %>% 
  dplyr::filter(tag == "Doesn't like needles" & group != "All" ) %>% 
  dplyr::arrange(desc(estimate))

# Top LMIC countries that wont have time to get vaccinated
time_top <- 
  no_vacc %>% 
  dplyr::filter(tag == "Won't have time to get vaccinated" & group != "All" ) %>% 
  dplyr::arrange(desc(estimate))

# Top LMIC countries that are concerned about getting covid from the vaccine
get_top <- 
  no_vacc %>% 
  dplyr::filter(tag == "Concerned about getting coronavirus from the vaccine" & group != "All" ) %>%
  dplyr::arrange(desc(estimate))

# Top LMIC countries that thinks vaccines are not effective
effective_top <- 
  no_vacc %>% 
  dplyr::filter(tag == "Doesn't think vaccines are effective" & group != "All" & group != "USA" & 
           group != "Russia") %>% 
  dplyr::arrange(desc(estimate))

# Estimate of Doesn't think vaccines are effective in Russia and the USA
effective_rus <- 
  no_vacc %>% 
  dplyr::filter(tag == "Doesn't think vaccines are effective" & group == "Russia") %>% 
  dplyr::arrange(desc(estimate))

effective_usa <- 
  no_vacc %>% 
  dplyr::filter(tag == "Doesn't think vaccines are effective" & group == "USA" ) %>% 
  dplyr::arrange(desc(estimate))

# Top LMIC countries that are not concerned of getting seriously ill
ill_top <- 
  no_vacc %>% 
  dplyr::filter(tag == "Not concerned about getting seriously ill" & group != "All" ) %>% 
  dplyr::arrange(desc(estimate))

# Top LMIC countries that do not think covid outbreak is as serious as people say
serious_top <- 
  no_vacc %>% 
  dplyr::filter(tag == "Doesn't think Coronavirus outbreak is as serious as people say" & 
                  group != "All") %>% 
  dplyr::arrange(desc(estimate))

```

### Table version

```{r tabfig2}

no_vacc2 <- 
  no_vacc %>%
  dplyr::mutate(estimate = format(estimate, nsmall = 0),
                conf_int = paste0("(", format(conf.low, nsmall = 0), 
                                  ", ", format(conf.high, nsmall = 0), ")")) %>%
  dplyr::select(group, estimate, conf_int, outcome, n) %>%
  tidyr::pivot_wider(names_from = outcome, values_from = c(estimate, conf_int, n), names_sep = "__") %>%
  tidyr::pivot_longer(cols = c(starts_with("estimate__"), starts_with("conf_int__")),
                      names_to = c("type", ".value"),
                      names_pattern = "(.*)__(.*)") %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(
    n = ifelse(group == "All", NA, unique(na.omit(c_across(starts_with("n__")))))) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(
    group = forcats::fct_relevel(forcats::fct_rev(group), "All", "Russia", "USA", after = Inf)) %>% 
  dplyr::arrange(group) %>% 
  dplyr::mutate(across(c(group, n), ~ifelse(type == "conf_int", "", as.character(.))),
                group = ifelse(group == "All", "All LMICs", group)) %>% 
  dplyr::select(group, n, starts_with("no_vaccine_"), -starts_with("n__no_vaccine"), -type) %>% 
  dplyr::relocate("no_vaccine_666", .after = last_col())

tab_fig2 <- 
  no_vacc2 %>%
  knitr::kable(
    col.names = 
      c("Study", "N", 
        "Concerned about side effects", 
        "Concerned about getting coronavirus from the vaccine", 
        "Not concerned about getting seriously ill", 
        "Doesn't think vaccines are effective", 
        "Doesn't think Coronavirus outbreak is as serious as people say", 
        "Doesn't like needles", 
        "Allergic to vaccines", 
        "Won't have time to get vaccinated", 
        "Mentions a conspiracy theory", 
        "Other reasons"),
    caption = "Reasons not to take the vaccine",
    align = c("l", rep("c", 11)),
    format = "latex", booktabs = T, linesep = "", 
    format.args = list(big.mark = ",", scientific = FALSE), 
    label = "no") %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
                            font_size = base_font_size - 2, full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1:12, width = "7em") %>%
  # kableExtra::column_spec(1, width = "7em") %>%
  kableExtra::footnote(
    general_title = "",
    general = "Table 6 shows percentage of respondents mentioning reasons why they would not take the Covid-19 vaccine. The number of observations and percentage correponds only to people who would NOT take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses",
    threeparttable = T)  %>%
  kableExtra::landscape()

no_vacc2 %>%
  knitr::kable(
    col.names = c("Study", "N", 
                  "Concerned about side effects", 
                  "Concerned about getting coronavirus from the vaccine", 
                  "Not concerned about getting seriously ill", 
                  "Doesn't think vaccines are effective", 
                  "Doesn't think Coronavirus outbreak is as serious as people say", 
                  "Doesn't like needles", 
                  "Allergic to vaccines", 
                  "Won't have time to get vaccinated", 
                  "Mentions a conspiracy theory", 
                  "Other reasons"),
    caption = "\\label{no}Reasons not to take the vaccine", 
    booktabs = T, linesep = "", 
    format.args = list(big.mark = ",",scientific = FALSE)) %>%
  kableExtra::kable_styling(full_width = F) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1:12, width = "7em") %>%
  # kableExtra::column_spec(1, width = "7em") %>%
  kableExtra::footnote(
    general_title = "",
    general = "Table 6 shows percentage of respondents mentioning reasons why they would not take the Covid-19 vaccine. The number of observations and percentage correponds only to people who would NOT take the vaccine. Respondents in all countries could give more than one reason. A 95% confidence interval is shown between parentheses",
    threeparttable = T)
```

## Figure 3: Trust vaccines

### Figure

```{r fig3, fig.width = 12,  fig.height = 10}

#Group together categories

df2 %<>% 
  dplyr::mutate(
    trust_recode_1 = ifelse(trust_vaccine_1 == 1 | trust_vaccine_2 == 1, 1, 0),
    trust_recode_1 = ifelse((country=="Nigeria"| country=="USA") & is.na(trust_recode_1), 0, trust_recode_1),

    trust_recode_2 = ifelse(trust_vaccine_8 == 1 | trust_vaccine_9 == 1, 1, 0),
    trust_recode_2 = ifelse((country=="Sierra Leone 2") & is.na(trust_recode_2), 0, trust_recode_2),

    trust_recode_3 = ifelse(trust_vaccine_3 == 1 | 
                              trust_vaccine_7 == 1 | 
                              trust_vaccine_4 == 1, 1, 0),
    trust_recode_3 = ifelse((country=="Nigeria"| country=="USA" | country=="Russia") & is.na(trust_recode_3), 0, trust_recode_3),

    trust_recode_4 = ifelse(trust_vaccine_666 == 1 | trust_vaccine_other == 1, 1, 0),
    trust_recode_4 = ifelse((country=="Burkina Faso"| country=="Sierra Leone 2" | country=="Russia") & is.na(trust_recode_4), 0, trust_recode_4),

    trust_recode_5 = ifelse(trust_vaccine_dk == 1 | 
                              trust_vaccine_refuse == 1 | 
                              trust_vaccine_nr == 1, 1, 0),
    trust_recode_5 = ifelse((country=="Nigeria"| country=="Sierra Leone 2" | country=="USA") & is.na(trust_recode_5), 0, trust_recode_5))

#Recoded groups
trust_names <- c("trust_recode_1", "trust_recode_2", "trust_recode_3", 
           "trust_recode_4", "trust_recode_5", "trust_vaccine_5", "trust_vaccine_6")

studies_levels <- 
  c("Burkina Faso", "Colombia", "India", "Mozambique",
    "Nepal", "Nigeria", "Pakistan 1", "Rwanda",
    "Sierra Leone 1", "Sierra Leone 2", "Uganda 2",
    "All", "Russia", "USA" )

#Get estimates
trust_vacc_together <-
  list(
    All = lapply(trust_names, reasons_together, 
                 df = df2, num = c("Yes", "No", "DK")) %>% 
      dplyr::bind_rows(),
    Yes = lapply(trust_names, reasons_together, 
                 df = df2, num = c("Yes")) %>% 
      dplyr::bind_rows(),
    No = lapply(trust_names, reasons_together, 
                df = df2, num = c("No", "DK")) %>% 
      dplyr::bind_rows()) %>% 
  dplyr::bind_rows(.id = "sub") %>%
  dplyr::filter(!is.nan(statistic)) %>%
  dplyr::mutate(
    across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 1)),
    n_sub = round(n * estimate, 0),
    n_sub = ifelse(n_sub == 0, NA_integer_, n_sub),
    group = factor(group, levels = studies_levels)) %>%
  dplyr::left_join(dictionary, by = "outcome") %>%
  dplyr::mutate(
    size = cut(n_sub, c(0, 50, 500, Inf), include.lowest = TRUE),
    size = forcats::fct_recode(size, "500+" = "(500,Inf]"),
    tag = as.factor(tag),
    tag = forcats::fct_relevel(tag, 
                               "Health workers", 
                               "Government or MoH", 
                               "Family or Friends", 
                               "Famous person, religious leader or traditional healers", 
                               "Newspapers, radio or online groups", 
                               "Other", 
                               "Don't know or Refuse"),
    sub = forcats::fct_relevel(as.factor(sub), "No", "Yes", "All"),
    sub = plyr::mapvalues(sub, from = c("No", "Yes", "All"),
                          to = c("No, Don't know", "Yes", "Any")))

#Plot
fig_hist2 <- 
  trust_vacc_together %>%
  dplyr::mutate(group = plyr::mapvalues(group, "All", "All LMICs")) %>% 
  ggplot(aes(estimate, tag, fill = sub)) + 
  geom_bar(stat = "identity", position = "dodge") + 
  facet_wrap(~group, ncol = 2, strip.position = "left")  +
  coord_flip() +
  scale_fill_manual(
    name = "Answer", 
    values = safe_colorblind_palette[c(1,3,2)]) + 
  scale_y_discrete(labels = function(x) stringr::str_wrap(x, width = 16), 
                   guide = guide_axis(angle = 90)) +
  labs(title = "Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine?",
       y = "") +
  theme_bw() + 
  theme(legend.position = "bottom",
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        axis.text.y = element_text(hjust = 0))

fig_hist2
```

### By gender

```{r fig3gender, fig.width = 12,  fig.height = 10}

trust_vacc_gender <-  
  list(
    All = lapply(trust_names, reasons_together_subgroup, 
                 df = df2, 
                 num = c("Yes", "No", "DK"), 
                 dem_group = "gender", 
                 dem_subgroup = c("Female", "Male")) %>% dplyr::bind_rows(),
    Male = lapply(trust_names, reasons_together_subgroup, 
                  df = df2, 
                  num = c("Yes", "No", "DK"), 
                  dem_group = "gender", 
                  dem_subgroup = "Male") %>%
      dplyr::bind_rows(),
  Female = lapply(trust_names, reasons_together_subgroup, 
                  df = df2, 
                  num = c("Yes", "No", "DK"), 
                  dem_group = "gender", 
                  dem_subgroup = "Female") %>% 
  dplyr::bind_rows()) %>% 
  dplyr::bind_rows(.id = "sub") %>%
  dplyr::filter(!is.nan(statistic)) %>%
  dplyr::mutate(
    across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 1)),
    n_sub = round(n * estimate, 0),
    n_sub = ifelse(n_sub == 0, NA_integer_, n_sub),
    group = factor(group, levels = studies_levels)) %>%
  dplyr::left_join(dictionary, by = "outcome") %>%
  dplyr::mutate(
    size = cut(n_sub, c(0, 50, 500, Inf), include.lowest = TRUE),
    size = forcats::fct_recode(size, "500+" = "(500,Inf]"),
    tag = as.factor(tag),
    tag = forcats::fct_relevel(tag, 
                               "Health workers", 
                               "Government or MoH", 
                               "Family or Friends", 
                               "Famous person, religious leader or traditional healers", 
                               "Newspapers, radio or online groups", 
                               "Other", 
                               "Don't know or Refuse"),
    sub = forcats::fct_relevel(as.factor(sub), "Female", "Male", "All"))

#Plot
hist_gender <- 
  trust_vacc_gender %>%
  dplyr::mutate(group = plyr::mapvalues(group, "All", "All LMICs")) %>% 
  ggplot(aes(estimate, tag, fill = sub)) + 
  geom_bar(stat = "identity", position = "dodge") + 
  facet_wrap(~group, ncol = 2, strip.position = "left")  +
  coord_flip() +
  scale_fill_manual(
    name = "Answer", 
    values = safe_colorblind_palette[c(1,3,2)]) + 
  scale_y_discrete(labels = function(x) stringr::str_wrap(x, width = 16), 
                   guide = guide_axis(angle = 90)) +
  labs(title = "If a COVID-19 vaccine becomes available in [country], would you take it?",
       y = "") +
  theme_bw() + 
  theme(legend.position = "bottom",
        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
        axis.text.y = element_text(hjust = 0))

hist_gender

```

### Gender difference means

```{r gendif}

differences_means_gen <- 
  lapply(trust_names, function(i) {
    df2 %>% 
      dplyr::filter(group != "All" & group != "USA" & group != "Russia" & group != "Uganda 1") %>% 
      estimatr::lm_robust(as.formula(paste(i, "~gender")),
                          fixed_effects = ~country,
                          weight = weight,
                          cluster = country,
                          se_type = "stata",
                          data = .) %>% 
      tidy %>% 
      dplyr::select(estimate, std.error, p.value, df, term)%>%
      dplyr::mutate(outcome = paste(i))
  }) %>% 
  dplyr::bind_rows(.) %>%
  dplyr::left_join(dictionary) %>%
  dplyr::select(-outcome)

differences_means_gen %>% 
  dplyr::mutate(adjusted_p = p.adjust(p.value, method = "BH")) %>%
  knitr::kable(digits = 3, caption = "Differences in means trust actors (BH adjustment)")

```

### Table version

```{r tabfig3}

trust_vacc <- 
  plyr::ldply(
    .data = list("Yes", "No", "All"), 
    .fun = function(take_vac) {
      list(Yes = "Yes", 
           No = c("No", "DK"), 
           All = c("Yes", "No", "DK")) %>% 
        .[[take_vac]] %>% 
        plyr::ldply(trust_names, reasons_together, df = df2, num = .) %>%
        dplyr::mutate(
          across(c(conf.low, conf.high, estimate), 
                 ~ format(round(. * 100, digits = 1), nsmall = 1)),        
          conf_int = paste0("(", conf.low, ", ", conf.high, ")")) %>%
        dplyr::select(group, estimate, conf_int, outcome, n) %>%
        tidyr::pivot_wider(names_from = outcome, values_from = c(estimate, conf_int, n), 
                           names_sep = "__") %>%
        tidyr::pivot_longer(cols = c(starts_with("estimate__"), starts_with("conf_int__")),
                            names_to = c("type", ".value"),
                            names_pattern = "(.*)__(.*)") %>%
        dplyr::rowwise() %>% 
        dplyr::mutate(
          n = ifelse(group == "All", NA, unique(na.omit(c_across(starts_with("n__")))))) %>% 
        dplyr::ungroup() %>% 
        dplyr::mutate("Take vaccine?" = take_vac) %>%
        dplyr::select(group, n, type, "Take vaccine?", starts_with("trust_")) %>%
        dplyr::filter(!(group %in% c("Mozambique", "Pakistan 1", "Pakistan 2", "Uganda 1", "India")))
    }
  ) %>% 
  dplyr::mutate(
    group = as.factor(group),
    group = forcats::fct_relevel(group, "All", "Russia", "USA", after = Inf)) %>% 
  dplyr::arrange(group) %>% 
  dplyr::mutate(across(c(group, n, `Take vaccine?`), ~ifelse(type == "conf_int", "", as.character(.))),
                group = ifelse(group == "All", "All LMICs", group)) %>% 
  dplyr::select(-type)

tab_trust <- 
  trust_vacc %>%
  dplyr::select("group", "n", 
                "Take vaccine?", "trust_vaccine_5", 
                "trust_vaccine_6", "trust_recode_1", 
                "trust_recode_3", "trust_recode_2", 
                "trust_recode_4", "trust_recode_5") %>%
  knitr::kable(
    col.names = c("Study", "N", "Take vaccine?", "Health workers", 
                  "Government or Ministry of Health", 
                  "Family or friends", 
                  "Famous person, religious leader or traditional healers", 
                  "Newspapers, radio or online groups", "Other", 
                  "Don't know or Refuse"),
    caption = "COVID-19 Vaccination Decision-making: most trusted source",
    align = c("l", rep("c", 9)),
    format = "latex", booktabs = T, linesep = "", longtable = TRUE,
    format.args = list(big.mark = ",", scientific = FALSE), 
    label = "trust") %>% 
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position", "repeat_header"),
                            font_size = base_font_size - 2, full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "7em") %>% 
  kableExtra::column_spec(2:10, width = "4em") %>% 
  kableExtra::column_spec(4:10, width = "6em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 7 shows percentage of respondents that mention actors who they would trust the most to help them decide whether to get a COVID-19 vaccine. For all countries the questions was asked regardless if respondent would take a vaccine, would not take it, does not know or does not respond. For India respondents were able to mention more than one actor, for the rest of countries only one actor was allowed. While rows should sum to 100%, rounding makes number slightly above or below. A 95% confidence interval is shown between parentheses.",
    threeparttable = T) %>%
  kableExtra::landscape()

trust_vacc %>%
  dplyr::select("group", "n", 
                "Take vaccine?", "trust_vaccine_5", 
                "trust_vaccine_6", "trust_recode_1", 
                "trust_recode_3", "trust_recode_2", 
                "trust_recode_4", "trust_recode_5") %>%
  knitr::kable(
    col.names = c("Study", "N", "Take vaccine?", "Health workers", 
                  "Government or \n Ministry of Health", 
                  "Family or friends", 
                  "Famous person, \n religious leader or \n traditional healers", 
                  "Newspapers, radio \n or online groups", "Other", 
                  "Don't know or Refuse"),
    caption = "COVID-19 Vaccination Decision-making: most trusted source", 
    format.args = list(big.mark = ",", scientific = FALSE)) %>% 
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "7em") %>% 
  kableExtra::column_spec(2:10, width = "4em") %>% 
  kableExtra::column_spec(4:10, width = "6em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 7 shows percentage of respondents that mention actors who they would trust the most to help them decide whether to get a COVID-19 vaccine. For all countries the questions was asked regardless if respondent would take a vaccine, would not take it, does not know or does not respond. For India respondents were able to mention more than one actor, for the rest of countries only one actor was allowed. While rows should sum to 100%, rounding makes number slightly above or below. A 95% confidence interval is shown between parentheses.",
    threeparttable = T)

```

```{r question1, include=FALSE}

tab_question1 <- 
  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select(
    "Study" = "country", 
    "Question Fig. 1", 
    "Recoding Fig. 1") %>%
  knitr::kable(
    caption =  "Question wording and answer options: vaccine acceptance",
    format = "latex", booktabs = T, linesep = "", label = "q1") %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
                            font_size = base_font_size - 2, full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>%
  kableExtra::column_spec(2, width = "30em")  %>%
  kableExtra::column_spec(3, width = "20em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 10 presents question wording and answer options from answers used in Figure 1 to get estimated vaccine acceptance. Answer options are separated by a semicolon. In India options 'Yes, only for free' and 'Yes, even if I have to pay' are both recoded as 'Yes'. In Pakistan 2, 'Absolutely yes' is recoded as 'Yes', 'Neutral' is recoded as 'Don't know' and 'Absolutely no' is recoded as 'No'. In Russia, 'Yes, if a Russian vaccine will be available' and 'Yes, if an imported vaccine will be available' are both recoded as 'Yes'. In USA 'Definitely yes' and 'Probably yes' are recoded as 'Yes', and 'Probably not' and 'Definitely not' are recoded as 'No'" ,
    threeparttable = T)

readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select("Study" = "country", "Question Fig. 1", "Recoding Fig. 1") %>%
  knitr::kable(
    caption =  "Question wording and answer options: vaccine acceptance", format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>%
  kableExtra::column_spec(2, width = "30em")  %>%
  kableExtra::column_spec(3, width = "20em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 10 presents question wording and answer options from answers used in Figure 1 to get estimated vaccine acceptance. Answer options are separated by a semicolon. In India options 'Yes, only for free' and 'Yes, even if I have to pay' are both recoded as 'Yes'. In Pakistan 2, 'Absolutely yes' is recoded as 'Yes', 'Neutral' is recoded as 'Don't know' and 'Absolutely no' is recoded as 'No'. In Russia, 'Yes, if a Russian vaccine will be available' and 'Yes, if an imported vaccine will be available' are both recoded as 'Yes'. In USA 'Definitely yes' and 'Probably yes' are recoded as 'Yes', and 'Probably not' and 'Definitely not' are recoded as 'No'" ,
    threeparttable = T)
```

```{r question2, include=FALSE}

tab_question2 <- 
  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select(
    "Study" = "country",
    "Question Tab. 2",
    "Protection: self", 
    "Protection: family",
    "Protection: community") %>%
  dplyr::filter(!is.na(`Question Tab. 2`)) %>%
  knitr::kable(
    caption =  "Question wording and answer options: reasons to take vaccine",
    format = "latex", booktabs = T, linesep = "", label = "q2") %>% 
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
                            font_size = base_font_size - 2, full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>%
  kableExtra::column_spec(2, width = "8em")  %>%
  kableExtra::column_spec(3:5, width = "10em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 11 presents question wording and answer options used in Table 2 to get an estimated percentage of reasons to take the COVID-19 vaccine. Columns 'Protection: self', 'Protection: family' and  'Protection: community' show the answer options that were recoded in each category. Answer options are separated by a semicolon." ,
    threeparttable = T)

readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select(
    "Study" = "country", 
    "Question Tab. 2", 
    "Protection: self", 
    "Protection: family", 
    "Protection: community") %>%
  knitr::kable(
    caption =  "Question wording and answer options: reasons to take vaccine", format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>%
  kableExtra::column_spec(2, width = "8em")  %>%
  kableExtra::column_spec(3:5, width = "10em") %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 11 presents question wording and answer options used in Table 2 to get an estimated percentage of reasons to take the COVID-19 vaccine. Columns 'Protection: self', 'Protection: family' and  'Protection: community' show the answer options that were recoded in each category. Answer options are separated by a semicolon." ,
    threeparttable = T)

```

```{r question3, include=FALSE}

tab_question3 <- 
  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select(
    "Study" = "country", 
    "Question Fig. 2", 
    "Concerned about side effects", 
    "Concerned about getting COVID-19 from the vaccine", 
    "Not concerned about getting seriously ill", 
    "Doesn't think vaccines are effective", 
    "Doesn't think COVID-19 outbreak is as serious as people say", 
    "Doesn't like needles", 
    "Allergic to vaccines", 
    "Won't have time to get vaccinated", 
    "Mentions a conspiracy theory",
    "Other reasons") %>%
  dplyr::filter(!is.na(`Question Fig. 2`)) %>%
  knitr::kable(
    caption =  "Question wording and answer options: reasons not to take the vaccine",
    format = "latex", booktabs = T, linesep = "", label = "q3") %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
                            font_size = base_font_size - 2, full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1:2, width = "5em") %>%
  kableExtra::column_spec(3:12, width = "10em")  %>%
  kableExtra::footnote(
    general_title = "",
    general = "Table 12 presents question wording and answer options used in Figure 2 to get an estimated percentage of reasons not to take the COVID-19 vaccine. Columns 3-10 show the answer options that were recoded in each category. Answer options are separated by a semicolon." ,
    threeparttable = T) %>% 
  kableExtra::landscape()

readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select(
    "Study" = "country", 
    "Question Fig. 2", 
    "Concerned about side effects", 
    "Concerned about getting COVID-19 from the vaccine", 
    "Not concerned about getting seriously ill", 
    "Doesn't think vaccines are effective", 
    "Doesn't think COVID-19 outbreak is as serious as people say", 
    "Doesn't like needles", 
    "Allergic to vaccines", 
    "Won't have time to get vaccinated", 
    "Mentions a conspiracy theory",
    "Other reasons") %>%
  dplyr::filter(!is.na(`Question Fig. 2`)) %>%
  knitr::kable(
    caption =  "Question wording and answer options: reasons not to take the vaccine",
    format = "html", linesep = "") %>%
  kableExtra::kable_styling(full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1:2, width = "5em") %>%
  kableExtra::column_spec(3:12, width = "10em")  %>%
  kableExtra::footnote(
    general_title = "",
    general = "Table 12 presents question wording and answer options used in Figure 2 to get an estimated percentage of reasons not to take the COVID-19 vaccine. Columns 3-10 show the answer options that were recoded in each category. Answer options are separated by a semicolon." ,
    threeparttable = T)
```

```{r question4, include=FALSE}

tab_question4 <- 
  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select(
    "Study" = "country", 
    "Question Fig. 3", 
    "Health workers", 
    "Government or Ministry of Health", 
    "Family or friends", 
    "Famous person, religious leader or traditional healers", 
    "Newspapers, radio or online groups", 
    "Other") %>%
  dplyr::filter(!is.na(`Question Fig. 3`)) %>%
  knitr::kable(
    caption =  "Question wording and answer options: trusted actors and institutions",
    format = "latex", booktabs = T, linesep = "", label = "q4") %>% 
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
                            font_size = base_font_size - 2, full_width = FALSE) %>%
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>%
  kableExtra::column_spec(2, width = "20em")  %>%
  kableExtra::column_spec(3:8, width = "10em") %>% 
  kableExtra::landscape() %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 13 presents question wording and answer options used in Figure 3 to get the percentage of respondents mentioning each actor or instituion that they would trust to decide whether to get the COVID-19 vaccine. Columns 3-8 show the answer options that were recoded in each category. Answer options are separated by a semicolon." ,
    threeparttable = T)

readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
  dplyr::select(
    "Study" = "country",
    "Question Fig. 3",
    "Health workers",
    "Government or Ministry of Health",
    "Family or friends",
    "Famous person, religious leader or traditional healers",
    "Newspapers, radio or online groups",
    "Other") %>%
  knitr::kable(
    caption =  "Question wording and answer options: trusted actors and institutions", 
    format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::row_spec(0, bold = TRUE) %>% 
  kableExtra::column_spec(1, width = "8em") %>%
  kableExtra::column_spec(2, width = "20em")  %>%
  kableExtra::column_spec(3:8, width = "10em") %>% 
  kableExtra::landscape() %>% 
  kableExtra::footnote(
    general_title = "",
    general = "Table 13 presents question wording and answer options used in Figure 3 to get the percentage of respondents mentioning each actor or instituion that they would trust to decide whether to get the COVID-19 vaccine. Columns 3-8 show the answer options that were recoded in each category. Answer options are separated by a semicolon." ,
    threeparttable = T)

```

## Summary stats

```{r tab5, fig.width = 12}
# Summary statistics table
# transform the categorical variables into dummy variables
df2 %<>% 
  fastDummies::dummy_cols(select_columns = c("age_groups","educ_binary","gender"))

get_stat <- function(.var, .data, ...) {
  return(
    paste0("`", .var, "` ~ 1") %>% 
      as.formula() %>% 
      lm_robust(formula = ., data = .data, ...) %>% 
      coef()
  )
}

data_sumstat <- 
  df2 %>% 
  dplyr::nest_by(group) %>% 
  dplyr::mutate(
    Female = get_stat("gender_Female", .data = data),
    age_18_30 = get_stat("age_groups_[18,30)", data),
    age_30_45 = get_stat("age_groups_[30,45)", data),
    age_45_60 = get_stat("age_groups_[45,60)", data),
    age_60    = get_stat("age_groups_[60, Inf)", data),
    Less_than_secondary = get_stat("educ_binary_Up to Secondary", data),
    More_than_secondary = get_stat("educ_binary_> Secondary", data)
    ) %>% 
  dplyr::select(-data, country = group) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(across(where(is.double), ~ . * 100))

#WGM data
wgmdata <- 
  readr::read_csv("2_input_data/wgm_2018_publiccsv.csv") %>% 
  dplyr::filter(WP5 %in% c(1,9,31,35,41,63,65,76,78,80,105,157),
                Age >= 18) %>% 
  dplyr::mutate(
    country = 
      plyr::mapvalues(WP5, 
                      from = c(1, 9, 31, 35, 41, 63, 65, 76, 78, 80, 105, 157),
                      to = c("USA","Pakistan","India","Nigeria","Uganda",
                             "Mozambique","Rwanda","Russia", 
                             "Burkina Faso", "Sierra Leone","Colombia","Nepal")),
    age_groups = cut(x = Age, breaks = c(-Inf, 18, 30, 45, 60, +Inf), right = F)) %>% 
  dplyr::select(country, wgt, gender = Gender, age = Age, educ = Education,
                age_groups) %>%
  fastDummies::dummy_cols(select_columns = "age_groups") %>% 
  dplyr::mutate(
    gender_Female = if_else(gender == 2, 1, 0), 
    `educ_binary_Up to Secondary` = if_else(educ == 1 | educ == 2, 1, 0),
    `educ_binary_> Secondary` = if_else(educ == 3, 1, 0))

wgmdata_sumstat <- 
  wgmdata %>% 
  dplyr::nest_by(country) %>% 
  dplyr::mutate(
    Female = get_stat("gender_Female", data, weight = wgt),
    age_18_30 = get_stat("age_groups_[18,30)", data, weight = wgt),
    age_30_45 = get_stat("age_groups_[30,45)", data, weight = wgt),
    age_45_60 = get_stat("age_groups_[45,60)", data, weight = wgt),
    age_60    = get_stat("age_groups_[60, Inf)", data, weight = wgt),
    Less_than_secondary = get_stat("educ_binary_Up to Secondary", data, weight = wgt),
    More_than_secondary = get_stat("educ_binary_> Secondary", data, weight = wgt)
    ) %>% 
  dplyr::select(-data) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(across(where(is.double), ~ . * 100))

sum_stat_col <- 
  dplyr::left_join(data_sumstat, 
                   wgmdata_sumstat, 
                   by = "country", all = TRUE, suffix = c("", "_wgm")) %>% 
  dplyr::select(
    country,
    starts_with("Female"),
    starts_with("age_18_30"),
    starts_with("age_30_45"),
    starts_with("age_45_60"),
    starts_with("age_60"),
    starts_with("Less_than_secondary"),
    starts_with("More_than_secondary")
  )

tab_sum_col <-
  knitr::kable(
    sum_stat_col, 
    caption = "Summary statistics for gender, age, education",
    col.names = c("Study", rep(c("COVID-19 Study", "Population"), 7)),
    digits = 1,
    format = "latex", 
    align = c("l", rep("c", 14)), 
    booktabs = T, linesep = "") %>%
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::add_header_above(
    c(" " = 1, 
      "% Women" = 2, 
      "% Age in [18,30)" = 2, 
      "% Age in [30,45)" = 2, 
      "% Age in [45,60)" = 2,
      "% Age 60+" = 2,
      "% Up to Secondary" = 2, 
      "% More than Secondary" = 2)) %>%
  kableExtra::column_spec(2:16, width = "3em") %>% 
  kableExtra::column_spec(1, width = "5em") %>% 
  kableExtra::footnote(
    general = "This table presents summarys statistics for our data and compares it with estimates from other sources of data. For each category, the left column and the right column correspond respectively to the statistics computed from our sample and from previous surveys. Data for Russia comes from census data from the Statistical Agency. For the USA, we use data from the 2019 American Community Survey. For all other countries, the Wellcome Global Monitor 2018 was used. Statistics for our surveys are not weighted, while estimates from benchmark sources are obtained using sampling weights.",
    threeparttable = T) %>% 
  kableExtra::landscape()

wgmdata_sumstat_label <-
  wgmdata_sumstat %>% 
  dplyr::mutate(country = paste0(country, " (WGM)"))

sum_stat_row <- 
  dplyr::bind_rows(data_sumstat, wgmdata_sumstat_label) %>%
  arrange(country) %>% 
  .[c(1:13,15,16,14,19,20,22,23,21,25,26,24,17,18,27,28),]

tab_sum_row <- 
  knitr::kable(
    sum_stat_row,caption = "Summary statistics for gender, age, education",
    col.names = c("Study", "% Women",
                  "% Age in [18,30)", "% Age in [30,45)","% Age in [45,60)","% Age 60+",
                  "% Up to Secondary", "% More than Secondary"),
    format = "latex", booktabs = T, linesep = "", align = c("l", rep("c", 7)), digits = 1) %>%
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::footnote(
    general = "This table presents summarys statistics for our data and compares it with estimates from other sources of data. Data for Russia comes from census data from the Statistical Agency. For the USA, we use data from the 2019 American Community Survey. For all other countries, the Wellcome Global Monitor 2018 was used. Statistics for our surveys are not weighted, while estimates from benchmark sources are obtained using sampling weights.",
    threeparttable = T) %>%
  kableExtra::column_spec(1:8, width = "5em")

knitr::kable(
  sum_stat_row,
  caption = "Summary statistics for gender, age, education",
  col.names = c("Study", "% Women", 
                "% Age in [18,30)", "% Age in [30,45)", "% Age in [45,60)", "% Age 60+",
                "% Up to Secondary", "% More than Secondary"),  
  booktabs = T, linesep = "", align = c("l", rep("c", 7)), digits = 1) %>%
  kableExtra::kable_styling(full_width = FALSE) %>% 
  kableExtra::footnote(
    general = "This table presents summarys statistics for our data and compares it with estimates from other sources of data. Data for Russia comes from census data from the Statistical Agency. For the USA, we use data from the 2019 American Community Survey. For all other countries, the Wellcome Global Monitor 2018 was used. Statistics for our surveys are not weighted, while estimates from benchmark sources are obtained using sampling weights.") %>%
  kableExtra::column_spec(1:8, width = "5em")

```

### 2021-03-23 paper.Rmd
no google drive

@@
 
-```{r load_gdoc, include = FALSE, eval = TRUE}
-
-googledrive::drive_download(file = "NatureMedicine Covid vaccine hesitancy", 
-                            path = "4_paper_supplementary_files/Intro Vaccine.txt", overwrite = TRUE)
-
-file.rename(from = "4_paper_supplementary_files/Intro Vaccine.txt", 
-            to = "4_paper_supplementary_files/temp_download.Rmd")
-
-knitr::opts_chunk$set(echo = FALSE)
-
-```
-
 ```{r main_text, child = "4_paper_supplementary_files/temp_download.Rmd"}

### 2021-03-23 4_paper_supplementary_files/temp_download.Rmd
paper

@@
 \newpage
-```{r otherv}
+```{r otherv, echo=FALSE}
 tab_1b
@@
 
-```{r yes, results = "asis"}
+```{r yes, results = "asis", echo=FALSE}
 tab_reasons_y
@@
 
-```{r sampling}
+```{r sampling, echo=FALSE}
 tab_sampling
 ```
-```{r, results = "asis"}
+
+```{r, results = "asis", echo=FALSE}
 tab_fig1
@@
 
-```{r yesall, results = "asis"}
+```{r yesall, results = "asis", echo=FALSE}
 tab_reasons_y_all
@@
 
-```{r no, results = "asis"}
+```{r no, results = "asis", echo=FALSE}
 tab_fig2
@@
 
-```{r trust, results = "asis"}
+```{r trust, results = "asis", echo=FALSE}
 tab_trust
@@
 
-```{r, results = "asis"}
+```{r, results = "asis", echo=FALSE}
 dmeans
@@
 
-```{r, results = "asis"}
+```{r, results = "asis", echo=FALSE}
 nas
@@
 
-```{r tabq1}
+```{r tabq1, echo=FALSE}
 tab_question1
@@
 
-```{r tabq2}
+```{r tabq2, echo=FALSE}
 tab_question2
@@
 
-```{r tabq3}
+```{r tabq3, echo=FALSE}
 tab_question3
@@
 
-```{r tabq4}
+```{r tabq4, echo=FALSE}
 tab_question4

### 2021-04-29 2_tables.Rmd
add analysis with country as unit

@@
 ```
+
 ## Main Results: Acceptance Rates (disaggregated by group)
@@
 ```
+
+## Invariance to aggregation at country level
+
+```{r}
+df_country <- 
+  df %>% 
+  filter(!is.na(take_vaccine_num)) %>%
+  filter(!(country %in% c("USA", "Russia"))) %>%
+  mutate(cluster_1 = country,
+         cluster_2 = recode(country, 
+                          "Pakistan 1" = "Pakistan",
+                          "Pakistan 2" = "Pakistan",
+                          "Sierra Leone 1" = "Sierra Leone",
+                          "Sierra Leone 2" = "Sierra Leone",
+                          "Uganda 1" = "Uganda",
+                          "Uganda 2" = "Uganda",
+                          )) %>%
+  group_by(country) %>% mutate(weight_1 = weight/sum(weight)) %>% ungroup() %>%
+  group_by(cluster_2) %>% mutate(weight_2 = weight_1/sum(weight_1)) %>% ungroup()
+
+# Inspect weights 
+df_country %>% group_by(country) %>% summarize(w1 = sum(weight_1), w2 = sum(weight_2)) %>% kable
+
+unit_check <- 
+  list(
+    study = lm_robust(data = df_country, 
+              formula = take_vaccine_num ~ 1, cluster = cluster_1,
+              weight = weight_1, se_type = "stata"),
+
+    country = lm_robust(data = df_country, 
+              formula = take_vaccine_num ~ 1, cluster = cluster_2,
+              weight = weight_2, se_type = "stata")) %>%
+
+  lapply(tidy) %>% bind_rows(.id = "Unit")
+
+unit_check %>% kable(digits = 2)
+```

### 2021-05-04 2_tables.Rmd
update files

--- 2021-03-23 2_tables.Rmd
@@
 title: 'COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging: Replication Code'
-date: "11/03/2021"
+date: "30 April 2021"
 output:
@@
 pacman::p_load(tidyverse, magrittr, knitr, kableExtra, DT, lazyeval, 
-               labelled, forcats, readxl, estimatr, ggforce, fastDummies,
+               labelled, forcats, readxl, googledrive, estimatr, ggforce, fastDummies,
                stringr, RColorBrewer, readstata13, metaplus, sjlabelled, ggrepel, tikzDevice)
@@
 
-country_weighting <- function(data)
+study_weighting <- function(data)
   data %>% 
@@
   data %>% 
-    country_weighting() %>% 
+    study_weighting() %>% 
     estimatr::lm_robust(data = .,...) %>% 
@@
 
+# Age analysis for reasons
+
+age_analysis <- function(df, reason, num = "Yes", filter_by=NA){
+  df %>%
+    dplyr::filter({{filter_by}}==1)  %>%
+    dplyr::filter(take_vaccine %in% num, 
+                  if_all(c(all_of(reason), cluster, weight), ~ !is.na(.))) %>%
+    dplyr::nest_by(group) %>%
+    dplyr::summarize(
+      lm_helper(data = data, 
+                formula = as.formula(paste0(reason, "~ 1")), 
+                cluster = cluster,
+                weight = weight, se_type = "stata"), .groups = "drop")
+}
+
 ```
@@
 # Call data created in 1_cleaning.Rmd
-df <- readr::read_csv("3_rep_data/combined.csv", guess_max = 30000)
+df <- readr::read_csv("2_rep_data/combined.csv", guess_max = 30000)
 
@@
 
-# Weights sum to 1 in each study and recode age and education into binary bins
+# Weights sum to 1 in each study and recode age and education into bins
 df <- 
@@
     age_groups = as.character(cut(x = age, breaks = c(-Inf, 18, 30, 45, 60, +Inf), right = F)),
-    age_groups_binary = ifelse(age >= 55, "55+", "<55"),
+    age_groups_binary = ifelse(age >= 55, "55+", NA),
+    age_groups_binary = ifelse(age < 55, "<55", age_groups_binary),
+    age_less24=ifelse(age<=24, 1, 0),
+    age_25_54=ifelse(age>=25 & age<=54, 1, 0),
+    age_55_more=ifelse(age>=55, 1, 0),
+    age_groups_three=ifelse(age<=24, "<25", NA),
+    age_groups_three=ifelse(age>=25 & age<=54, "25-54", age_groups_three),
+    age_groups_three=ifelse(age>=55, "55+", age_groups_three),
     educ_binary = if_else(educ == "More than secondary", "> Secondary", "Up to Secondary"))
@@
   summarize(n = n(),
-            take_vaccine_na = mean(!is.na(take_vaccine)),
-            gender_na = mean(is.na(gender)),
-            educ_na= mean(is.na(educ)),
-            age_na= mean(is.na(age))) %>%
+            take_vaccine_na = mean(!is.na(take_vaccine))*100,
+            gender_na = mean(!is.na(gender))*100,
+            educ_na= mean(!is.na(educ))*100,
+            age_na= mean(!is.na(age))*100) %>%
   kable(digits = 2, 
@@
     general_title = "",
-    general = "Table 9 show the percentage of observations that are not missing values for each variable included in Figure 1.",
+    general = "Table 10 show the proportion of observations that are not missing values for each variable included in Figure 1.",
     threeparttable = T)
@@
   summarize(n = n(),
-            take_vaccine_na = mean(!is.na(take_vaccine)),
-            gender_na = mean(is.na(gender)),
-            educ_na= mean(is.na(educ)),
-            age_na= mean(is.na(age))) %>%
+            take_vaccine_na = mean(!is.na(take_vaccine)) *100,
+            gender_na = mean(is.na(gender))*100,
+            educ_na= mean(is.na(educ))*100,
+            age_na= mean(is.na(age))*100) %>%
   kable(digits = 2, 
@@
 # Call data from WGM
-dfwgm <- read.csv("3_rep_data/table_wgm.csv")
+dfwgm <- read.csv("2_rep_data/table_wgm.csv")
 
 # Call data from WHO
-df_vacc_coveragebis <- read.csv("3_rep_data/vacc_cov.csv")
+df_vacc_coveragebis <- read.csv("2_rep_data/vacc_cov.csv")
 
@@
 tab_sampling <- 
-  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
-  dplyr::select("Study" = "country", 
+  readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
+  dplyr::select("Study" = "country", "Date"="date",
                 "Geographic scope", "Sampling methodology", "Survey modality", "Weights") %>%
@@
   kableExtra::row_spec(0, bold = TRUE) %>% 
-  kableExtra::column_spec(1, width = "8em") %>%
-  kableExtra::column_spec(2, width = "12em")  %>%
-  kableExtra::column_spec(3, width = "30em") %>% 
+  kableExtra::column_spec(1:2, width = "8em") %>%
+  kableExtra::column_spec(3, width = "12em")  %>%
+  kableExtra::column_spec(4, width = "30em") %>% 
   kableExtra::landscape()
 
-readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
-  dplyr::select("Study" = "country", 
+readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
+  dplyr::select("Study" = "country", "Date"="date",
                 "Geographic scope", "Sampling methodology", "Survey modality", "Weights") %>%
@@
 # Age (all original categories and binary recoding)
-# acc_by_age <- grp_analysis(df2, y = "take_vaccine_num", x = "age_groups")
+acc_by_age <- grp_analysis(df2, y = "take_vaccine_num", x = "age_groups_three") %>%
+  dplyr::filter(statistic!=Inf) %>%
+  dplyr::filter(conf.low>0)
 acc_by_age_binary <- grp_analysis(df2, y = "take_vaccine_num", x = "age_groups_binary")
@@
 tags <- 
-  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
+  readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select(group = country, tag = "Geographic scope") %>%
@@
 
+```{r fig1ages}
+
+# Put them together in a single df. Make estimates "percentages" and round
+
+ans <- 
+  dplyr::bind_rows(
+    main_results %>% mutate(cat = "All", var = "All"),
+    acc_by_gender %>% rename(cat = gender) %>% mutate(var = "By gender"),
+    acc_by_educ_binary %>% rename(cat = educ_binary) %>% mutate(var = "By education"),
+    acc_by_age %>% rename(cat = age_groups_three) %>% mutate(var = "By age")) %>%
+  dplyr::mutate(across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 1)))
+
+# Join with a tags df, which includes details on the study (national or subnational)
+tags <- 
+  readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
+  dplyr::select(group = country, tag = "Geographic scope") %>%
+  dplyr::left_join(filter(ans, cat == "All"), by = "group") %>%
+  dplyr::mutate(tag = paste0(group, " (", tag, ", ", n, ")")) %>%
+  dplyr::select(group, tag)
+
+# Prepare df to plot. Important but ugly relevel of factors, happening all over the code
+
+ans %<>% 
+  dplyr::left_join(tags) %>%
+  dplyr::mutate(tag = ifelse(group == "All", "All LMICs", tag)) %>%
+  # group_by(var) %>% 
+  # arrange(cat) %>%
+  dplyr::mutate(
+    var = factor(var, levels = c("All", "By gender", "By education", "By age")),
+    cat = factor(
+      cat, ordered = TRUE,
+      levels = rev(c(c("Female", "Male", "Up to Secondary", 
+                       "> Secondary", "<25", "25-54", "55+", "All"))),
+      labels = rev(c("Female", "Male", "Up to Secondary", 
+                     "More than Secondary", "$< 25$", "$25-54$", "$55 +$", "All"))),
+    tag = gsub(pattern = " \\(", "\\\n\\(", tag))
+
+special_cases <- 
+  sort(unique(ans$tag)[grep(unique(ans$tag), pattern = "All LMICs|Russia|USA")])
+
+ans %<>% 
+  dplyr::mutate(
+    tag = 
+      factor(x = tag, ordered = TRUE,
+             levels = rev(c(sort(unique(tag)[!(unique(tag) %in% special_cases)]), special_cases))))
+
+#Colour blind palette (available palletes are smaller so we expand it)
+safe_colorblind_palette <- c("#CC6677", "#DDCC77", "#117733", "#332288", "#AA4499", 
+                             "#44AA99", "#999933", "#882255", "#661100", "#6699CC", "#888888", 
+                             "#88CCEE")
+
+#Plot
+fig_1_ages <- 
+  ans %>% 
+  ggplot(data = ., aes(x = tag, y = estimate, color = cat)) + 
+  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
+                size = .5, width = .2, position = position_dodge(0.6)) + 
+  geom_point(position = position_dodge(0.6)) +
+  facet_grid(. ~ var, scales = "free_x", space = "free") + 
+  coord_flip() +
+  guides(color = guide_legend(reverse = TRUE, nrow = 2)) +
+  geom_vline(xintercept = 3.5, color = "darkgrey") +
+  geom_vline(xintercept = 2.5, color = "darkgrey") +
+  scale_colour_manual(values = safe_colorblind_palette) +
+  labs(title = "If a COVID-19 vaccine becomes available in [country], would you take it?", 
+       color = "Subgroups", x = "") +
+  theme_bw(base_size = (base_font_size - 2)) + ylim(c(0,100)) +
+  theme(legend.position = "bottom",
+        plot.caption = element_text(hjust = 0), #Default is hjust=1
+        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
+        plot.caption.position =  "plot",
+        axis.text.y = element_text(hjust = 0))
+
+fig_1_ages
+```
+
+### Invariance to aggregation at country level
+
+Weighting so that each country (rather than each study) has equal weight has only a marginal impact on estimated LMIC average acceptance.
+
+```{r}
+df_country <- 
+  df %>% 
+  filter(!is.na(take_vaccine_num)) %>%
+  filter(!(country %in% c("USA", "Russia"))) %>%
+  mutate(cluster_1 = country,
+         cluster_2 = recode(country, 
+                          "Pakistan 1" = "Pakistan",
+                          "Pakistan 2" = "Pakistan",
+                          "Sierra Leone 1" = "Sierra Leone",
+                          "Sierra Leone 2" = "Sierra Leone",
+                          "Uganda 1" = "Uganda",
+                          "Uganda 2" = "Uganda",
+                          )) %>%
+  group_by(country) %>% mutate(weight_1 = weight/sum(weight)) %>% ungroup() %>%
+  group_by(cluster_2) %>% mutate(weight_2 = weight_1/sum(weight_1)) %>% ungroup() 
+# Inspect weights 
+df_country %>% group_by(country) %>% summarize(w1 = sum(weight_1), w2 = sum(weight_2)) %>% kable
+unit_check <- 
+  list(
+    study = lm_robust(data = df_country, 
+              formula = take_vaccine_num ~ 1, cluster = cluster_1,
+              weight = weight_1, se_type = "stata"),
+
+    country = lm_robust(data = df_country, 
+              formula = take_vaccine_num ~ 1, cluster = cluster_2,
+              weight = weight_2, se_type = "stata")) %>%
+
+  lapply(tidy) %>% bind_rows(.id = "Unit")
+unit_check %>% kable(digits = 2)
+```
 ### Differences in means
@@
 differences_means_gen_age <- 
-  lapply(c("gender", "age_groups_binary"), function(i) {
+  lapply(c("gender", "age_groups_binary", "age_groups_three"), function(i) {
     df %>% 
@@
       dplyr::filter(if_all(c(all_of(i), all_of("take_vaccine_num")), ~ !is.na(.))) %>%
-      country_weighting() %>%
+      study_weighting() %>%
       estimatr::lm_robust(as.formula(paste("take_vaccine_num ~", i)),
@@
       dplyr::filter(if_all(c(all_of("educ_binary"), all_of("take_vaccine_num")), ~ !is.na(.))) %>%
-      country_weighting() %>%
+      study_weighting() %>%
       estimatr::lm_robust(
@@
 
+dif_age_three <- 
+  differences_means_gen_age %>%
+  dplyr::filter(term == "age_groups_three25-54" | term == "age_groups_three55+") %>%
+  pull(estimate) %>% 
+  {. * 100} %>% 
+  round(., 1)
+
 dif_educ <- 
@@
     Variable = ifelse(`Baseline category` == "genderMale", 
-                      "Gender", ""),
+                      "Gender (Female)", ""),
     Variable = ifelse(`Baseline category` == "age_groups_binary55+", 
@@
     Variable = ifelse(`Baseline category` == "educ_binaryUp to Secondary", 
-                      "Education", Variable),
+                      "Education (Secondary +)", Variable),
     `Baseline category` = ifelse(`Baseline category` == "genderMale", 
@@
 dmeans <- diffmeans %>%
+  filter(Variable!="") %>%
   knitr::kable(
@@
     general_title = "",
+    general = "Table 9 shows the results of subgroup mean differences. Subgroup differences were generated considering only LMICs. p-values come from a two-sided t-test from a linear regression.",
+    threeparttable = T)
+
+diffmeans %>%
+  filter(Variable!="") %>%
+  knitr::kable(
+  caption =  "Differences in means",
+  booktabs = T, linesep = "", label = "dmeans", digits = 2) %>% 
+  kableExtra::kable_styling(full_width = FALSE) %>%
+  kableExtra::row_spec(0, bold = TRUE) %>% 
+  kableExtra::footnote(
+    general_title = "",
     general = "Table 8 shows the results of subgroup mean differences.
 Subgroup differences were generated considering only LMICs.
-The differences in means for gender and age do not include the Uganda 1 study, which only included female respondents under the age of 55.
-p-values come from a two-sided t-test from a linear regression.",
-    threeparttable = T)
-
+The differences in means for gender and age do not include the Uganda 1 study, which only included female respondents under the age of 55.",
+    threeparttable = T)
+
+```
+
+### Differences in means: Age with three categories
+
+```{r}
+
+diffmeans <- 
   diffmeans %>%
+  filter(Variable!="Age") %>%
+  dplyr::mutate(
+    Variable = ifelse(`Baseline category` == "age_groups_three25-54", 
+                      "Age (25-54)", Variable),
+    Variable = ifelse(`Baseline category` == "age_groups_three55+", 
+                      "Age (55+)", Variable),
+    `Baseline category` = ifelse(`Baseline category` == "age_groups_three25-54", 
+                                 "<25", `Baseline category`),
+    `Baseline category` = ifelse(`Baseline category` == "age_groups_three55+", 
+                                 "<25", `Baseline category`))
+
+dmeans <- diffmeans %>%
+  filter(Variable!="") %>%
+  knitr::kable(
+    digits = 2,
+    caption =  "Differences in means",
+    format = "latex", booktabs = T, linesep = "", label = "dmeans", align = "c") %>% 
+  kableExtra::kable_styling(latex_options = c("hold_position"),
+    font_size = base_font_size - 2, full_width = FALSE) %>%
+  kableExtra::row_spec(0, bold = TRUE) %>% 
+  kableExtra::footnote(
+    general_title = "",
+    general = "Table 9 shows the results of subgroup mean differences. Subgroup differences were generated considering only LMICs. p-values come from a two-sided t-test from a linear regression.",
+    threeparttable = T)
+
+diffmeans %>%
+  filter(Variable!="") %>%
   knitr::kable(
@@
 
-    lapply(c("gender", "age_groups_binary", "educ_binary"), function(i){
-      if (length(table(dff[[i]])) != 2)  {
+    lapply(c("gender", "age_groups_binary", "age_groups_three", "educ_binary"), function(i){
+      if (length(table(dff[[i]])) < 2)  {
         return(NULL)
       } else {
-        estimatr::lm_robust(as.formula(paste("take_vaccine_num ~", i)),
+        m <- estimatr::lm_robust(as.formula(paste("take_vaccine_num ~", i)),
                             weight = weight,
-                            data = dff) %>%
-          tidy %>%
-          dplyr::select(estimate, std.error, p.value, df, term)}}
+                            cluster = cluster,
+                            se_type = "stata",
+                            data = dff) 
+          m %>% tidy %>%
+          dplyr::select(estimate, std.error, p.value, df, term) %>%
+          mutate(n = m$nobs)
+        }}
     ) } %>%
@@
   dplyr::filter(term != "(Intercept)") %>% 
-  dplyr::mutate(significant = p.value <= .05)
+  dplyr::mutate(significant = p.value <= .05) %>%
+  dplyr::mutate(term=ifelse(term=="age_groups_three25-54", "25-54", term),
+                term=ifelse(term=="age_groups_three55+", "55+", term),
+                term=ifelse(term=="educ_binaryUp to Secondary", "Up to secondary", term),
+                term=ifelse(term=="age_groups_binary55+", "55+ (binary measure)", term),
+
+                term=ifelse(term=="genderMale", "Male", term))
 
@@
 
-knitr::kable(country_differences, 
+t_country_differences1 <- country_differences %>%
+  dplyr::filter(!grepl("55+ (binary measure)", term))%>%
+  dplyr::mutate(
+                baseline=ifelse(term=="Male", "Female", NA),
+                baseline=ifelse(term=="Up to secondary", "Secondary +", baseline),
+                baseline=ifelse(is.na(baseline), "<25", baseline),
+                group=ifelse(baseline=="<25", "Age", NA),
+                group=ifelse(baseline=="Secondary +", "Education", group),
+                group=ifelse(baseline=="Female", "Gender", group),
+                estimate=round(estimate, 2),
+                std.error=round(std.error, 2),
+                p.value=round(p.value, 2)) %>%
+  dplyr::select(country, group, baseline, term, everything(), - significant)
+
+t_country_differences <- t_country_differences1 %>%
+  kable(digits = 2, 
+        col.names= c("Country", "Variable", "Baseline category", "Group", "Estimate", "Std. Error", "p.value", "Degrees of freedom"),
+        caption = "Differences between groups within studies", 
+        booktabs = TRUE, linesep = "", 
+        format.args = list(big.mark = ",", scientific = FALSE),
+  format = "latex", label = "countrydiff") %>% 
+  kableExtra::kable_styling(latex_options = c("scale_down"), font_size = base_font_size - 2, full_width = FALSE) %>% 
+  kableExtra::footnote(
+    general_title = "",
+    general = "Table 11 shows differences of means between groups within single studies.
+Estimates are calculated through OLS and represent the difference in the average acceptance rate between the subgroup in column Group and that in column Baseline category.",
+    threeparttable = T)
+
+knitr::kable(t_country_differences1, 
              digits = 2, caption = "Differences between groups within studies ")
@@
   tidyr::pivot_wider(names_from = age_groups_binary, 
+                     values_from = c(estimate, conf_int), 
+                     names_sep = "__")
+
+age_table <- 
+  acc_by_age %>%
+  dplyr::mutate(
+    across(c(estimate, conf.low, conf.high), ~ format(round(100 * ., 1), nsmall = 1)),
+    conf_int = paste0("(", conf.low, ", ", conf.high, ")")) %>%
+  dplyr::select(group, age_groups_three, estimate, conf_int) %>% 
+  tidyr::pivot_wider(names_from = age_groups_three, 
                      values_from = c(estimate, conf_int), 
@@
     format.args = list(big.mark = ",", scientific = FALSE), 
-    escape = F, align = "lccccccc", label = "maintabledis")  %>% 
+    escape = F, align = "lcccccccc", label = "maintabledis")  %>% 
   kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
                             font_size = base_font_size - 2, full_width = FALSE) %>%
-  kableExtra::add_header_above(c("", "", "Gender" = 2, "Education" = 2, "Age" = 2), bold = TRUE) %>%
+  kableExtra::add_header_above(c("", "", "Gender" = 2, "Education" = 2, "Age" = 3), bold = TRUE) %>%
   kableExtra::row_spec(0, bold = TRUE) %>% 
@@
     caption = "If a COVID-19 vaccine becomes available in [country], would you take it? Disaggregated by subgroups", 
-    align = "lccccccc", booktabs = T) %>% 
+    align = "lcccccccc", booktabs = T) %>% 
   kableExtra::kable_styling(full_width = FALSE) %>%
-  kableExtra::add_header_above(c("", "", "Gender" = 2, "Education" = 2, "Age" = 2), bold = TRUE) %>%
+  kableExtra::add_header_above(c("", "", "Gender" = 2, "Education" = 2, "Age" = 3), bold = TRUE) %>%
   kableExtra::row_spec(0, bold = TRUE) %>% 
@@
   dplyr::mutate(estimate = format(estimate, nsmall = 0),
-                conf_int = paste0("(", format(conf.low, nsmall = 0), 
-                                  ", ", format(conf.high, nsmall = 0), ")")) %>%
+                conf_int = paste0("(", conf.low, 
+                                  ", ", conf.high, ")")) %>%
   dplyr::select(group, estimate, conf_int, outcome, n) %>%
@@
     general_title = "",
-    general = "Table 2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
-The number of observations and percentage correponds only to people who would take the vaccine.
+    general = "Table 3 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
+The number of observations and percentage corresponds only to people who would take the vaccine.
 Respondents in all countries could give more than one reason.
@@
   kableExtra::column_spec(1, width = "8em") %>% 
-  kableExtra::column_spec(2:4, width = "4em") %>% 
+  kableExtra::column_spec(2:5, width = "8em") %>% 
   kableExtra::footnote(
@@
 
+```
+
+```{r tab2all, fig.width = 12}
+
+yes_vars <- 
+  df2 %>% 
+  dplyr::select(yes_vaccine_1, yes_vaccine_2, 
+                yes_vaccine_3, yes_vaccine_4, 
+                yes_vaccine_5, yes_vaccine_666) %>% 
+  names
+
+## Generate data for analysis of yes reasons
+yes_vacc1 <- 
+  lapply(yes_vars, reasons_together, df = df2, num = "Yes") %>%
+  dplyr::bind_rows() %>%
+  dplyr::mutate(across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 0)))
+
+#Get percentage per yes reason category and make wide table
+yes_vacc2 <- 
+  yes_vacc1 %>%
+  dplyr::mutate(estimate = format(estimate, nsmall = 0),
+                conf_int = paste0("(", conf.low, 
+                                  ", ", conf.high, ")")) %>%
+  dplyr::select(group, estimate, conf_int, outcome, n) %>%
+  tidyr::pivot_wider(names_from = outcome, values_from = c(estimate, conf_int, n), names_sep = "__") %>%
+  tidyr::pivot_longer(cols = c(starts_with("estimate__"), starts_with("conf_int__")),
+                      names_to = c("type", ".value"),
+                      names_pattern = "(.*)__(.*)") %>%
+  dplyr::rowwise() %>% 
+  dplyr::mutate(
+    n = ifelse(group == "All", NA, unique(na.omit(c_across(starts_with("n__")))))) %>% 
+  dplyr::ungroup() %>% 
+  dplyr::mutate(
+    group = forcats::fct_relevel(as.factor(group), "All", "Russia", "USA", after = Inf)) %>% 
+  dplyr::arrange(group) %>% 
+  dplyr::mutate(across(c(group, n), ~ifelse(type == "conf_int", "", as.character(.))),
+                group = ifelse(group == "All", "All LMICs", group)) %>% 
+  dplyr::select(group, n, type, starts_with("yes_vaccine_"), -starts_with("n_yes_vaccine"), -type)
+
+cnames <- c("Study", "N", "Self", "Family", 
+          "Community", "Health workers", "Government", "Other")
+
+#Table to Latex
+tab_reasons_y_all <- 
+  yes_vacc2  %>% 
+  knitr::kable(col.names = cnames,
+        caption = "Reasons to take the vaccine- all categories", 
+        format = "latex", booktabs = T, linesep = "", 
+        label = "yesall", 
+        format.args = list(big.mark = ",", scientific = FALSE), 
+        escape = F, align = c("l", rep("c", 7))) %>%
+  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
+                            font_size = base_font_size - 2, full_width = FALSE) %>%
+  kableExtra::row_spec(0, bold = TRUE) %>% 
+  kableExtra::add_header_above(c(" " = 2, "Protection" = 3, "If recommended by" = 2, " " = 1), 
+                               bold = TRUE) %>% 
+  kableExtra::column_spec(1:8, width = "7em") %>% 
+  kableExtra::footnote(
+    general_title = "",
+    general = "Table 5 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
+The number of observations and percentage correponds only to people who would take the vaccine.
+Respondents in all countries could give more than one reason.
+A 95% confidence interval is shown between parentheses",
+    threeparttable = T)
+
+yes_vacc2 %>%
+  knitr::kable(col.names = cnames,
+               caption = "Reasons to take the vaccine. All categories", 
+               booktabs = T, linesep = "", align = c("l", rep("c", 7)),
+               format.args = list(big.mark = ",", scientific = FALSE)) %>% 
+  kableExtra::kable_styling(full_width = FALSE) %>%
+  kableExtra::row_spec(0, bold = TRUE) %>% 
+  kableExtra::add_header_above(c(" " = 2, "Protection" = 3, "If recommended by" = 2, " " = 1), 
+                               bold = TRUE) %>% 
+  kableExtra::column_spec(1:8, width = "7em") %>% 
+  kableExtra::footnote(
+    general_title = "",
+    general = "Table 5 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
+The number of observations and percentage correponds only to people who would take the vaccine.
+Respondents in all countries could give more than one reason.
+A 95% confidence interval is shown between parentheses",
+    threeparttable = T)
+
+```
+## Reasons to take by age
+```{r, fig.width = 10, fig.height = 7}
+
+yes_vars <- 
+  df2 %>% 
+  dplyr::select(yes_vaccine_1, yes_vaccine_2, yes_vaccine_3) %>% 
+  names
+
+## Generate data for analysis of yes reasons for different age groups
+yes_vacc_age_1 <- 
+  lapply(yes_vars, age_analysis, df = df2, num = "Yes", filter_by=`age_less24`) %>%
+  dplyr::bind_rows() %>%
+  mutate(age="<25")
+
+yes_vacc_age_2 <- 
+  lapply(yes_vars, age_analysis, df = df2, num = "Yes", filter_by=`age_25_54`) %>%
+  dplyr::bind_rows() %>%
+  mutate(age="25-54")
+
+yes_vacc_age_3 <- 
+  lapply(yes_vars, age_analysis, df = df2, num = "Yes", filter_by=`age_55_more`) %>%
+  dplyr::bind_rows() %>%
+  mutate(age="55+")
+
+#Get percentage per yes reason category and make wide table
+yes_vacc_age <- 
+  rbind(yes_vacc_age_1, yes_vacc_age_2, yes_vacc_age_3) %>%
+  dplyr::mutate(across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 0))) %>%
+  dplyr::mutate(estimate = format(estimate, nsmall = 0),
+                conf_int = paste0("(", conf.low, 
+                                  ", ", conf.high, ")"),
+                n=as.character(n)) %>%
+  dplyr::select(group, estimate, conf_int, outcome, age, n) %>%
+  tidyr::pivot_wider(names_from = c(outcome, age), values_from = c(estimate, conf_int, n), names_sep = "__") %>%
+  tidyr::pivot_longer(cols = c(starts_with("estimate__"), starts_with("conf_int__"), starts_with("n__")),
+                      names_to = c("type", ".value"),
+                      names_pattern = "(.*)__(.*)")
+
+y1 <- yes_vacc_age %>%
+  dplyr::filter(grepl("yes_vaccine_1", type)) %>%
+  mutate(type=ifelse(grepl("estimate", type), "estimate", type),
+         type=ifelse(grepl("conf_int", type), "conf_int", type),
+         type=ifelse(grepl("n__", type), "n", type))
+
+y2 <- yes_vacc_age %>%
+  dplyr::filter(grepl("yes_vaccine_2", type))%>%
+  mutate(type=ifelse(grepl("estimate", type), "estimate", type),
+         type=ifelse(grepl("conf_int", type), "conf_int", type),
+         type=ifelse(grepl("n__", type), "n", type))
+
+y3 <- yes_vacc_age %>%
+  dplyr::filter(grepl("yes_vaccine_3", type))%>%
+  mutate(type=ifelse(grepl("estimate", type), "estimate", type),
+         type=ifelse(grepl("conf_int", type), "conf_int", type),
+         type=ifelse(grepl("n__", type), "n", type))
+
+yes_vacc_age <- left_join(y1, y2, by=c("group", "type")) %>%
+  left_join(y3, by=c("group", "type")) %>% 
+  dplyr::mutate(
+    group = forcats::fct_relevel(as.factor(group), "All", "Russia", "USA", after = Inf)) %>% 
+  dplyr::arrange(group) %>% 
+  dplyr::mutate(across(c(group), ~ifelse(type == "conf_int", "Conf. interval", as.character(.))),
+                across(c(group), ~ifelse(type == "n", "n", as.character(.))),
+                group = ifelse(group == "All", "All LMICs", group)) %>% 
+  dplyr::select(-type)
+
+cnames <- c("Study", "<25", "25-54", "55+", "<25", "25-54", "55+", "<25", "25-54", "55+")
+
+#Table to Latex
+tab_reasons_y_age <- 
+  yes_vacc_age %>%
+  knitr::kable(col.names = cnames,
+      caption = "Reasons to take the vaccine- by age groups", format = "latex", booktabs = T, 
+      linesep = "", label = "yes1", 
+      format.args = list(big.mark = ",", scientific = FALSE), 
+      escape = F, align = c("l", rep("c", 9))) %>%
+  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
+                            font_size = base_font_size - 2, full_width = FALSE) %>%
+  kableExtra::add_header_above(c(" " = 1, "Self" = 3, "Family" = 3, "Community" = 3), bold = TRUE) %>% 
+  kableExtra::row_spec(0, bold = TRUE) %>% 
+  kableExtra::row_spec(seq(from = 3, to = 36, by = 3), hline_after = TRUE) %>%
+  kableExtra::column_spec(1, width = "7em") %>% 
+  kableExtra::column_spec(2:10, width = "5em") %>% 
+  kableExtra::footnote(
+    general_title = "",
+    general = "Table 6 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine by age groups.
+The number of observations and percentage correponds only to people who would take the vaccine.
+Respondents in all countries could give more than one reason.
+A 95% confidence interval is shown between parentheses",
+    threeparttable = T)
+
+yes_vacc_age %>%
+  knitr::kable(col.names = cnames,
+      caption = "\\label{yes1}Reasons to take the vaccine", 
+      booktabs = T, linesep = "", 
+      format.args = list(big.mark = ",", scientific = FALSE)) %>% 
+  kableExtra::kable_styling(full_width = FALSE) %>%
+  kableExtra::add_header_above(c(" " = 1, "Self" = 3, "Family" = 3, "Community" = 3), bold = TRUE) %>% 
+  kableExtra::row_spec(0, bold = TRUE) %>% 
+  kableExtra::column_spec(1, width = "8em") %>% 
+  kableExtra::column_spec(2:10, width = "4em") %>% 
+  kableExtra::footnote(
+    general_title = "",
+    general = "Table 2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
+The number of observations and percentage correponds only to people who would take the vaccine.
+Respondents in all countries could give more than one reason.
+A 95% confidence interval is shown between parentheses.
+Studies India, Pakistan 1 and Pakistan 2 are not included because they either did not include the question or were not properly harmonized with the other studies.",
+    threeparttable = T)
+
+```
+
+## Figure 2: reasons not to take
+
+### Figure
+
+```{r, fig.width = 10, fig.height = 7}
+
 #Import df with tags (names of categories)
-dictionary <- read_excel("2_input_data/dictionary.xlsx")
+dictionary <- read_excel("1_input_data/dictionary.xlsx")
 
@@
 
-```
-
-```{r tab2all, fig.width = 12}
-
-yes_vars <- 
-  df2 %>% 
-  dplyr::select(yes_vaccine_1, yes_vaccine_2, 
-                yes_vaccine_3, yes_vaccine_4, 
-                yes_vaccine_5, yes_vaccine_666) %>% 
-  names
-
-## Generate data for analysis of yes reasons
-yes_vacc1 <- 
-  lapply(yes_vars, reasons_together, df = df2, num = "Yes") %>%
-  dplyr::bind_rows() %>%
-  dplyr::mutate(across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 0)))
-
-#Get percentage per yes reason category and make wide table
-yes_vacc2 <- 
-  yes_vacc1 %>%
-  dplyr::mutate(estimate = format(estimate, nsmall = 0),
-                conf_int = paste0("(", format(conf.low, nsmall = 0), 
-                                  ", ", format(conf.high, nsmall = 0), ")")) %>%
-  dplyr::select(group, estimate, conf_int, outcome, n) %>%
-  tidyr::pivot_wider(names_from = outcome, values_from = c(estimate, conf_int, n), names_sep = "__") %>%
-  tidyr::pivot_longer(cols = c(starts_with("estimate__"), starts_with("conf_int__")),
-                      names_to = c("type", ".value"),
-                      names_pattern = "(.*)__(.*)") %>%
-  dplyr::rowwise() %>% 
-  dplyr::mutate(
-    n = ifelse(group == "All", NA, unique(na.omit(c_across(starts_with("n__")))))) %>% 
-  dplyr::ungroup() %>% 
-  dplyr::mutate(
-    group = forcats::fct_relevel(as.factor(group), "All", "Russia", "USA", after = Inf)) %>% 
-  dplyr::arrange(group) %>% 
-  dplyr::mutate(across(c(group, n), ~ifelse(type == "conf_int", "", as.character(.))),
-                group = ifelse(group == "All", "All LMICs", group)) %>% 
-  dplyr::select(group, n, type, starts_with("yes_vaccine_"), -starts_with("n_yes_vaccine"), -type)
-
-cnames <- c("Study", "N", "Self", "Family", 
-          "Community", "Health workers", "Government", "Other")
-
-#Table to Latex
-tab_reasons_y_all <- 
-  yes_vacc2  %>% 
-  knitr::kable(col.names = cnames,
-        caption = "Reasons to take the vaccine- all categories", 
-        format = "latex", booktabs = T, linesep = "", 
-        label = "yesall", 
-        format.args = list(big.mark = ",", scientific = FALSE), 
-        escape = F, align = c("l", rep("c", 7))) %>%
-  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"),
-                            font_size = base_font_size - 2, full_width = FALSE) %>%
-  kableExtra::row_spec(0, bold = TRUE) %>% 
-  kableExtra::add_header_above(c(" " = 2, "Protection" = 3, "If recommended by" = 2, " " = 1), 
-                               bold = TRUE) %>% 
-  kableExtra::column_spec(1:8, width = "7em") %>% 
-  kableExtra::footnote(
-    general_title = "",
-    general = "Table 5 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
-The number of observations and percentage correponds only to people who would take the vaccine.
-Respondents in all countries could give more than one reason.
-A 95% confidence interval is shown between parentheses",
-    threeparttable = T)
-
-yes_vacc2 %>%
-  knitr::kable(col.names = cnames,
-               caption = "Reasons to take the vaccine. All categories", 
-               booktabs = T, linesep = "", align = c("l", rep("c", 7)),
-               format.args = list(big.mark = ",", scientific = FALSE)) %>% 
-  kableExtra::kable_styling(full_width = FALSE) %>%
-  kableExtra::row_spec(0, bold = TRUE) %>% 
-  kableExtra::add_header_above(c(" " = 2, "Protection" = 3, "If recommended by" = 2, " " = 1), 
-                               bold = TRUE) %>% 
-  kableExtra::column_spec(1:8, width = "7em") %>% 
-  kableExtra::footnote(
-    general_title = "",
-    general = "Table 5 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
-The number of observations and percentage correponds only to people who would take the vaccine.
-Respondents in all countries could give more than one reason.
-A 95% confidence interval is shown between parentheses",
-    threeparttable = T)
-
-```
-
-## Figure 2: reasons not to take
-
-### Figure
-
-```{r, fig.width = 10, fig.height = 7}
 fig_2 <- 
@@
        x = "") +
-  theme_bw() + ylim(c(0,100)) +
+  theme_bw() + ylim(c(-2,100)) +
   theme(legend.position = "bottom",
@@
   no_vacc %>% 
-  dplyr::filter(tag == "Doesn't think vaccines are effective" & group != "All" & group != "USA" & 
+  dplyr::filter(tag == "Doesn't think vaccines are effective" & group != "USA" & 
            group != "Russia") %>% 
@@
     general_title = "",
-    general = "Table 6 shows percentage of respondents mentioning reasons why they would not take the Covid-19 vaccine.
+    general = "Table 7 shows percentage of respondents mentioning reasons why they would not take the Covid-19 vaccine.
 The number of observations and percentage correponds only to people who would NOT take the vaccine.
@@
   dplyr::mutate(group = plyr::mapvalues(group, "All", "All LMICs")) %>% 
+  dplyr::filter(sub=="Any") %>% 
+  ggplot(aes(estimate, tag)) + 
+  geom_bar(stat = "identity", position = "dodge", fill="#DDCC77") + 
+  facet_wrap(~group, ncol = 2, strip.position = "left")  +
+  coord_flip() +
+  scale_fill_manual(
+    name = "Answer", 
+    values = safe_colorblind_palette[c(1,3,2)]) + 
+  scale_y_discrete(labels = function(x) stringr::str_wrap(x, width = 16), 
+                   guide = guide_axis(angle = 90)) +
+  labs(title = "Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine?",
+       y = "") +
+  theme_bw() + 
+  theme(legend.position = "bottom",
+        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
+        axis.text.y = element_text(hjust = 0))
+
+fig_hist2
+```
+
+```{r fig3quantities, fig.width = 12,  fig.height = 10}
+
+trust <- filter(trust_vacc_together, sub=="Any")
+
+# All LMIcs estimate of trust HW
+
+trust_all <- 
+  trust %>% 
+  dplyr::filter(group == "All" & tag=="Health workers") %>%
+  dplyr::arrange(desc(estimate))
+
+# Top and bottom LMICs countries for trust in Health works
+trust_ <- 
+  trust %>% 
+  dplyr::filter(group != "All" & group != "USA" & group != "Russia" & tag == "Health workers")
+
+trust_top <- trust_ %>% dplyr::arrange(desc(estimate))
+
+trust_rwa <- 
+  trust %>% 
+  dplyr::filter(group == "Rwanda") %>%
+  dplyr::arrange(desc(estimate))
+
+trust_npl <- 
+  trust %>% 
+  dplyr::filter(group == "Nepal" & tag=="Famous person, religious leader or traditional healers") %>%
+  dplyr::arrange(desc(estimate))
+
+# Top and bottom LMICs countries for trust in Family and friends
+trust_fam <- 
+  trust %>% 
+  dplyr::filter(group != "All" & tag == "Family or Friends") %>%
+  dplyr::arrange(desc(estimate))
+
+# Top and bottom LMICs countries for trust in Gov
+trust_gov <- 
+  trust %>% 
+  dplyr::filter(group != "All" & group!="Rwanda" & tag == "Government or MoH") %>%
+  dplyr::arrange(desc(estimate))
+
+```
+
+## Figure broken down by acceptance
+
+```{r fig3categories, fig.width = 12,  fig.height = 10}
+
+#Plot
+fig_hist_categories <- 
+  trust_vacc_together %>%
+  dplyr::mutate(group = plyr::mapvalues(group, "All", "All LMICs")) %>% 
   ggplot(aes(estimate, tag, fill = sub)) + 
@@
 
-fig_hist2
+fig_hist_categories
 ```
@@
                    guide = guide_axis(angle = 90)) +
-  labs(title = "If a COVID-19 vaccine becomes available in [country], would you take it?",
+  labs(title = "Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine?",
        y = "") +
@@
     general_title = "",
-    general = "Table 7 shows percentage of respondents that mention actors who they would trust the most to help them decide whether to get a COVID-19 vaccine.
+    general = "Table 8 shows percentage of respondents that mention actors who they would trust the most to help them decide whether to get a COVID-19 vaccine.
 For all countries the questions was asked regardless if respondent would take a vaccine, would not take it, does not know or does not respond.
@@
 tab_question1 <- 
-  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
+  readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select(
@@
     general_title = "",
-    general = "Table 10 presents question wording and answer options from answers used in Figure 1 to get estimated vaccine acceptance.
+    general = "Table 12 presents question wording and answer options from answers used in Figure 1 to get estimated vaccine acceptance.
 Answer options are separated by a semicolon.
@@
 
-readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
+readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select("Study" = "country", "Question Fig. 1", "Recoding Fig. 1") %>%
@@
     general_title = "",
-    general = "Table 10 presents question wording and answer options from answers used in Figure 1 to get estimated vaccine acceptance.
+    general = "Table 11 presents question wording and answer options from answers used in Figure 1 to get estimated vaccine acceptance.
 Answer options are separated by a semicolon.
@@
 tab_question2 <- 
-  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
+  readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select(
@@
     general_title = "",
-    general = "Table 11 presents question wording and answer options used in Table 2 to get an estimated percentage of reasons to take the COVID-19 vaccine.
+    general = "Table 13 presents question wording and answer options used in Table 2 to get an estimated percentage of reasons to take the COVID-19 vaccine.
 Columns 'Protection: self', 'Protection: family' and  'Protection: community' show the answer options that were recoded in each category.
@@
 
-readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
+readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select(
@@
     general_title = "",
-    general = "Table 11 presents question wording and answer options used in Table 2 to get an estimated percentage of reasons to take the COVID-19 vaccine.
+    general = "Table 12 presents question wording and answer options used in Table 3 to get an estimated percentage of reasons to take the COVID-19 vaccine.
 Columns 'Protection: self', 'Protection: family' and  'Protection: community' show the answer options that were recoded in each category.
@@
 tab_question3 <- 
-  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
+  readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select(
@@
     general_title = "",
-    general = "Table 12 presents question wording and answer options used in Figure 2 to get an estimated percentage of reasons not to take the COVID-19 vaccine.
+    general = "Table 14 presents question wording and answer options used in Figure 2 to get an estimated percentage of reasons not to take the COVID-19 vaccine.
 Columns 3-10 show the answer options that were recoded in each category.
@@
     general_title = "",
-    general = "Table 12 presents question wording and answer options used in Figure 2 to get an estimated percentage of reasons not to take the COVID-19 vaccine.
+    general = "Table 13 presents question wording and answer options used in Figure 2 to get an estimated percentage of reasons not to take the COVID-19 vaccine.
 Columns 3-10 show the answer options that were recoded in each category.
@@
 tab_question4 <- 
-  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
+  readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select(
@@
     general_title = "",
-    general = "Table 13 presents question wording and answer options used in Figure 3 to get the percentage of respondents mentioning each actor or instituion that they would trust to decide whether to get the COVID-19 vaccine.
+    general = "Table 15 presents question wording and answer options used in Figure 3 to get the percentage of respondents mentioning each actor or instituion that they would trust to decide whether to get the COVID-19 vaccine.
 Columns 3-8 show the answer options that were recoded in each category.
@@
     general_title = "",
-    general = "Table 13 presents question wording and answer options used in Figure 3 to get the percentage of respondents mentioning each actor or instituion that they would trust to decide whether to get the COVID-19 vaccine.
+    general = "Table 14 presents question wording and answer options used in Figure 3 to get the percentage of respondents mentioning each actor or instituion that they would trust to decide whether to get the COVID-19 vaccine.
 Columns 3-8 show the answer options that were recoded in each category.
@@
 wgmdata <- 
-  readr::read_csv("2_input_data/wgm_2018_publiccsv.csv") %>% 
+  readr::read_csv("1_input_data/wgm_2018_publiccsv.csv") %>% 
   dplyr::filter(WP5 %in% c(1,9,31,35,41,63,65,76,78,80,105,157),

### 2021-05-04 4_paper_supplementary_files/temp_download.Rmd
update files

@@
+<!-- KEEP ALL REVISIONS IN SUGGESTING MODE FOR VERSION CONTROL - DO NOT ACCEPT CHANGES -->
 <!-- COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging -->
@@
 
+```{r, include=FALSE} 
+empty = " " 
+```
+`r empty`
+
 # Abstract {-}
 
-We analyze COVID-19 vaccine acceptance across 15 survey samples covering ten low- and middle-income countries (LMICs) in Asia, Africa, and South America, and two higher income countries (Russia and the United States).
-Standardized survey responses were collected from `r nice(nrow(df))` individuals.
-We find generally high willingness to take a COVID-19 vaccine in LMIC samples (80% on average), considerably higher than in the United States (65%) and Russia (30%).
-Vaccine acceptance was primarily explained by an interest in personal protection against the disease, while concern about side effects was the most commonly expressed reason for reluctance.
+We analyze COVID-19 vaccine acceptance across 15 survey samples covering ten low- and middle-income countries (LMICs) in Asia, Africa, and South America, Russia (an upper-middle-income country), and the United States, using survey responses from  `r nice(nrow(df))` individuals.
+We find considerably higher willingness to take a COVID-19 vaccine in LMIC samples (80% on average) compared to the United States (65%) and Russia (30%).
+Vaccine acceptance was primarily explained by an interest in personal protection against COVID-19, while concern about side effects was the most commonly expressed reason for reluctance.
 Health workers were the most trusted sources of information about COVID-19 vaccines.
-Our findings suggest that prioritizing efficient and equitable vaccine distribution to LMICs should yield high returns in promoting global immunization.
-Interventions to promote vaccination in these contexts should focus on translating intentions into uptake and involve trusted health workers.
+Our findings suggest that prioritizing vaccine distribution to LMICs should yield high returns in promoting global immunization coverage, and that vaccination campaigns in these countries should focus on translating acceptance into uptake.
+Messaging highlighting vaccine efficacy and safety, delivered by healthcare workers, may be most effective in addressing remaining hesitancy.
 
@@
 A safe and effective vaccine against COVID-19 is a critical tool to control the pandemic.
-As of March 2, 2021, there were 76 vaccines in clinical development and 16 had advanced to Stage 3 clinical trials [@who1].
-Following clinical trials, several vaccines have been approved in multiple countries and are being distributed across the globe.
-At present, global vaccine distribution remains highly unequal, with much of the current supply directed toward high-income countries [@eiu].
+As of April 27, 2021, 22 vaccines had advanced to Stage 3 clinical trials [@who1] and more than a dozen vaccines had been approved in multiple countries[@track].
+For example, as of April 27, 2021, Comirnaty (BioNTech/Pfizer) had been approved in  more than 80 countries, while the AstraZeneca vaccine had the most country authorizations at 92.
+[@track] At present, however, global vaccine distribution remains highly unequal, with much of the current supply directed toward high-income countries [@wouters2021challenges].
 
-While effective and equitable distribution of the vaccines is a key policy priority, ensuring the population’s acceptance is equally important.
-Acceptance of vaccines and trust in the institutions that administer them are likely key determinants of the success of any vaccination campaign [@defigueiredo2020lancet].
-Several studies investigate high-income country residents’ willingness to take a potential COVID-19 vaccine [@boyon2020ipsos; @Malik2020].
-Little is known about acceptance rates in low- and middle-income countries (LMICs), however, where the majority of the world’s population resides.
+While effective and equitable distribution of COVID-19 vaccines is a key policy priority, ensuring the population’s acceptance is equally important.
+Trust in vaccines and the institutions that administer them are key determinants of the success of any vaccination campaign [@defigueiredo2020lancet].
+Several studies have investigated willingness to take a potential COVID-19 vaccine in high-income countries [@boyon2020ipsos; @Malik2020; @kreps2020factors; @shekhar2021covid; @dror2020vaccine; @fisher2020attitudes], and some studies have included middle-income countries [@lazarus2020nature; @wouters2021challenges].
+Less is known, however, about vaccine acceptance in low-income countries where large-scale vaccination  has yet to begin.
+Understanding the drivers of COVID-19 vaccine acceptance is of global concern, since a lag in vaccination in any country may result in the emergence and spread of new variants that can overcome vaccine- and prior disease-conferred immunity [@ong2021lack; @lancettask].
 
-Acceptance of childhood vaccination for common diseases ---such as measles (MCV), Bacille Calmette-Guérin (BCG) and diphtheria, tetanus, and pertussis (DTP)---is generally high in LMICs, providing reasons for optimism about future uptake of COVID-19 vaccines.
-Table \ref{tab:otherv} summarizes general vaccine acceptance and uptake of common childhood vaccines for the countries included in our study.
-Still, existing studies on COVID-19 vaccine acceptance document large variation, both across and within countries, including in settings where overall vaccination rates are high [@boyon2020ipsos].
-These studies highlight concerns about COVID-19 vaccine safety, and particularly concerns about the speed of vaccine development, as reasons for hesitancy in higher income settings.
-Similar concerns may apply in LMICs.
+Our study complements the emerging global picture of COVID-19 vaccine acceptance by focusing primarily on lower income countries.
+We construct a sample of low- and middle-income countries (LMICs) with wide geographic coverage across Africa, Asia and Latin America.
+We move beyond documenting vaccine acceptance rates and analyze data on the reasons for acceptance and hesitancy, which is critical for informing the design of effective vaccine distribution and messaging.
 
-Additional reasons for hesitancy may feature more prominently in LMIC settings.
-Reported COVID-19 mortality rates have consistently been lower in LMICs relative to higher income countries [@mukherjee].
-If individuals in LMICs feel the risk of disease is less serious, they may be less inclined to accept perceived risks associated with taking a recently-developed vaccine.
-Previous studies have also highlighted factors such as concerns about healthcare quality [@christensen2020building], negative historical experiences [@Lowes2018], weak support from traditional leaders [@Jegede2007], and mistrust in government [@BLAIR201789] as barriers to healthcare utilization in LMICs.
+Acceptance of childhood vaccination for common diseases---such as measles (MCV), Bacille Calmette-Guérin (BCG) and diphtheria, tetanus, and pertussis (DTP)---is generally high in LMICs, providing cause for optimism about the prospects for COVID-19 vaccine uptake.
+Table \ref{tab:otherv} summarizes general vaccine acceptance and coverage rates of childhood vaccines in 2018, prior to the current pandemic,  for the countries included in our study.
+Agreement on the importance of childhood vaccinations is markedly higher in these LMICs compared to Russia and the United States.
+Still, existing studies on COVID-19 vaccine acceptance document substantial variation, both across and within countries, including in settings with high background levels of other vaccinations [@defigueiredo2020lancet; @lazarus2020nature; @wouters2021challenges].
 
-Understanding factors that may lead people in LMICs to reject COVID-19 vaccination is of global concern, since a lag in vaccination in the developing world could facilitate the spread of new variants of the virus to other countries.
+This literature cites concerns about COVID-19 vaccine safety, including concerns about the rapid pace of vaccine development, as reasons for hesitancy in higher-income settings [@boyon2020ipsos; @wouters2021challenges], but other reasons  may feature more prominently in LMICs.
+For instance, reported COVID-19 mortality rates have been consistently lower in LMICs relative to higher income countries [@mukherjee].
+If individuals feel the risk of disease is less serious, they may be less willing to accept any perceived risks of vaccination [@brewer2007meta].
+Previous studies of healthcare utilization in LMICs have also highlighted factors such as healthcare quality concerns [@christensen2020building], negative historical experiences involving foreign actors  [@Lowes2018; @martinez2021vaccines], weak support from traditional leaders [@Jegede2007], and mistrust in government [@BLAIR201789] as barriers to uptake, which could apply to COVID-19 vaccination as well.
 
-In order to effectively promote vaccination against COVID-19 and devise messaging strategies, we need to know if people are willing to take COVID-19 vaccines, the reasons why they are willing or unwilling to do so, and the factors influencing their decision-making.
-For this purpose, we developed and deployed a common set of questions across 15 studies in ten LMICs in Africa (Burkina Faso, Mozambique, Nigeria, Rwanda, Sierra Leone, Uganda), Asia (India, Nepal, Pakistan), and Latin America (Colombia).
-We compare these findings in LMICs to those from two higher income countries (Russia and the United States).
+To promote vaccination against COVID-19 and develop effective messaging strategies, we need to know whether people are willing to take COVID-19 vaccines, the reasons why they are willing or unwilling to do so, and the most trusted  sources in their decision-making.
+Our study investigates these questions using a common set of survey items deployed across 13 studies in Africa, South Asia, and Latin America: seven in low-income countries (Burkina Faso, Mozambique, Rwanda, Sierra Leone, Uganda), five in lower-middle-income countries (India, Nepal, Nigeria, Pakistan), and one in an upper-middle-income country (Colombia).
+We compare these findings to those from two countries at the forefront of vaccine research and development, Russia and the United States.
+To select studies to include in our sample, we conducted an internal search within Innovations for Poverty Action (IPA), the International Growth Center (IGC), and the Berlin Social Science Center (WZB) for projects with plans to collect survey data in the second half of 2020.
+Study PIs agreed to include a set of common questions about COVID-19 vaccine attitudes.
+This strategy was guided by the need to collect information quickly and cost effectively using a survey modality (phone) that was both safe given pandemic conditions and appropriate for contexts with limited internet coverage.
+The final set of samples included in our study therefore reflects populations that fall under the current research priorities at IGC, IPA and WZB and, in the case of IPA and IGC, donors that prioritize working in the Global South.
 
@@
 
-Our main results are shown in Figure \@ref(fig:mainfigure1) and reproduced as Table \ref{tab:maintabledis} in [Appendix A](#appendixd).
-The first column provides overall acceptance rates in each study, while the remaining columns show acceptance rates disaggregated by respondent characteristics.
-The “All LMICs” row reports averages for LMIC countries only (and so excludes Russia and the US).
+Our main results are shown in Figure \@ref(fig:mainfigure1) and reproduced as [Appendix A](#appendixd) Table \ref{tab:maintabledis}.
+The first column provides overall acceptance rates in each study, while the remaining columns disaggregate acceptance rates by respondent characteristics.
+The “All LMICs” row reports averages for LMIC countries and excludes Russia and the USA.
 
 We document meaningful variation in vaccine acceptance across and within LMICs, but generally high levels of acceptance in LMICs overall.
-The average acceptance across studies is `r ans_mean`% (95% CI `r ans_mean_low`--`r ans_mean_high`), with a median of `r ans_median`, a range of `r ans_max - ans_min` percent points and an interquartile range of `r ans_iqr`.
+The average acceptance rate across studies was `r ans_mean`% (95% CI `r ans_mean_low`--`r ans_mean_high`%), with a median of `r ans_median`, a range of `r ans_max - ans_min` percent points and an interquartile range of `r ans_iqr`.
 Our estimate of $\tau^2$ is `r  round(mp_tau, 3)` which implies a standard deviation over country averages of  `r round(mp_tau^.5, 3)`.
 
-The acceptance rate in every LMIC sample is higher than in USA (`r usa_ans %>% pull(estimate)`%, `r usa_ans %>% pull(conf.low)`--`r usa_ans %>% pull(conf.high)`) and Russia (`r rus_ans %>% pull(estimate)`%, `r rus_ans %>% pull(conf.low)`--`r rus_ans %>% pull(conf.high)`).
+The acceptance rate in every LMIC sample was higher than in the USA (`r usa_ans %>% pull(estimate)`%, `r usa_ans %>% pull(conf.low)`--`r usa_ans %>% pull(conf.high)`%) and Russia (`r rus_ans %>% pull(estimate)`%, `r rus_ans %>% pull(conf.low)`--`r rus_ans %>% pull(conf.high)`%).
+Reported acceptance was lowest in `r bottom_all$group[1]` (`r bottom_all$estimate[1]`% `r bottom_all$conf.low[1]`--`r bottom_all$conf.high[1]`%) and `r bottom_all$group[2]`  (`r bottom_all$estimate[2]`%, `r bottom_all$conf.low[2]`--`r bottom_all$conf.high[2]`%).
+The case of Pakistan may be linked to negative historical experiences with foreign-led vaccination campaigns [@ali2019polio; @robbins2012cia].
+This hesitancy may be particularly problematic, given the magnitude of the second wave in neighboring India just as vaccines are becoming available, with accelerating cases in Bangladesh, Pakistan and India threatening to overwhelm health infrastructure.
 
-We find limited evidence of variation across demographic subgroups in LMICs, as shown in Table \ref{tab:dmeans}.
+We find limited evidence of variation across demographic subgroups in our LMIC samples, as shown in [Appendix A](#appendixd) Table \ref{tab:dmeans}.
 Women were generally less willing to accept the vaccine (average difference about `r dif_gender` points, significant at $p<.01$).
-Younger respondents (defined as aged <55 given younger-skewing populations in LMICs) were marginally more willing to take the vaccine, but this difference was not statistically significant.
-Less educated people were on average more willing to take the vaccine in LMICs, but this difference was not significant.
+Respondents under age 24 and less educated respondents were marginally more willing to take the vaccine, but these differences were not statistically significant.
+The acceptance advantage among the less educated was most pronounced in Rwanda, Burkina Faso, and Uganda, and stands in contrast to the USA, where more educated respondents were significantly more willing to be vaccinated.
 
 To better understand the reasoning behind vaccine acceptance, we asked those who were willing to take the vaccine why they would take it.
-We summarize in Table \ref{tab:yes}, with more details in Table \ref{tab:yesall}.
+We summarize these results in Table \ref{tab:yes}, with additional details in [Appendix A](#appendixd) Table \ref{tab:yesall}.
+The reason most commonly given for vaccine acceptance across samples was personal protection against COVID-19 infection.
+The average across the LMIC samples was `r yes_all$estimate`% (`r yes_all$conf.low`--`r yes_all$conf.high`%).
+In every individual study, this ranked as the most popular reason.
+In distant second place among LMIC respondents was family protection with an average of `r yes_all_2$estimate`% (`r yes_all_2$conf.low`--`r yes_all_2$conf.high`%).
+In comparison to protecting oneself and one’s family,  protecting one’s community did not feature prominently among stated reasons for acceptance.
+These reasons do not vary substantially by age group, as shown in Table \ref{tab:countrydiff}.
+Self-protection also ranked as the most common reason for taking the vaccine in Russia (`r yes_rus$estimate`%, `r yes_rus$conf.low`--`r yes_rus$conf.high`%) and the USA (`r yes_usa$estimate`%, `r yes_usa$conf.low`--`r yes_usa$conf.high`%).
 
-The most common reason given for vaccine acceptance was personal protection against COVID-19 infection.
-The average across LMICs was `r yes_all$estimate`% (`r yes_all$conf.low`--`r yes_all$conf.high`).
-In every individual study, it ranked as the first reason.
-In distant second place, LMIC respondents reported willingness to take the COVID-19 vaccine in order to protect their families.
-The average across LMICs was `r yes_all_2$estimate`% (`r yes_all_2$conf.low`--`r yes_all_2$conf.high`).
-In comparison to self-protection, protecting the community did not feature prominently among the stated reasons.
+Figure \@ref(fig:fig2paper) summarizes the reasons given by respondents who said they were not willing to take a COVID-19 vaccine.
+Concern about side effects was the most frequently expressed reason for reluctance in our  LMIC samples.
+This concern was particularly evident among African country samples.
+In studies  `r side_top$group[1]` (`r side_top$estimate[1]`% `r side_top$conf.low[1]`--`r side_top$conf.high[1]`%), `r side_top$group[2]`  (`r side_top$estimate[2]`%, `r side_top$conf.low[2]`--`r side_top$conf.high[2]`%), `r side_top$group[3]` (`r side_top$estimate[3]`% `r side_top$conf.low[3]`--`r side_top$conf.high[3]`%) and `r side_top$group[4]` (`r side_top$estimate[4]`% `r side_top$conf.low[4]`--`r side_top$conf.high[4]`%), more than half of respondents unwilling to take the vaccine cited worries about side effects.
+Respondents in Russia (`r side_rus$estimate`%, `r side_rus$conf.low`--`r side_rus$conf.high`%) and even more in the USA (`r side_usa$estimate`%, `r side_usa$conf.low`--`r side_usa$conf.high`%), frequently reported this same concern.
 
-Self-protection also ranked as the most commonly expressed reason for taking the vaccine in Russia (`r yes_rus$estimate`%, `r yes_rus$conf.low`--`r yes_rus$conf.high`) and the USA (`r yes_usa$estimate`%, `r yes_usa$conf.low`--`r yes_usa$conf.high`).
+Study samples `r effective_top$group[1]` (`r effective_top$estimate[1]`%, `r effective_top$conf.low[1]`--`r effective_top$conf.high[1]`%), `r effective_top$group[2]`  (`r effective_top$estimate[2]`%, `r effective_top$conf.low[2]`--`r effective_top$conf.high[2]`%) and `r effective_top$group[3]` (`r effective_top$estimate[3]`%, `r effective_top$conf.low[3]`--`r effective_top$conf.high[3]`%) showed relatively high levels of skepticism about vaccine effectiveness among hesitant respondents.
+This was also true in Russia (`r effective_rus$estimate`%, `r effective_rus$conf.low`--`r effective_rus$conf.high`%) and the USA (`r effective_usa$estimate`%, `r effective_usa$conf.low`--`r effective_usa$conf.high`%).
+In addition, hesitant respondents listed lack of concern about COVID-19 infection as a reason not to be vaccinated.
+Study samples `r ill_top$group[1]` (`r ill_top$estimate[1]`% `r ill_top$conf.low[1]`--`r ill_top$conf.high[1]`%), `r ill_top$group[2]`  (`r ill_top$estimate[2]`%, `r ill_top$conf.low[2]`--`r ill_top$conf.high[2]`%) and `r ill_top$group[3]` (`r ill_top$estimate[3]`% `r ill_top$conf.low[3]`--`r ill_top$conf.high[3]`%) reported high rates of this answer among hesitant respondents.
 
-This evidence contrasts with appeals to altruistic behavior and prosocial motivations in order to promote vaccine acceptance [@chou2020considering].
-The risks and benefits to personal well-being feature much more prominently in people’s stated reasons for vaccine acceptance.
+In Figure \@ref(fig:fig3paper) we report respondents’ most trusted source of guidance when deciding whether to take a COVID-19 vaccine.
+Results from Figure \@ref(fig:fig3paper) are reproduced as  [Appendix A](#appendixd) Table \ref{tab:trust}.
+[Appendix B](#appendixb) Table \ref{tab:q4} presents a complete description of response recoding from individual studies.
 
-Figure \@ref(fig:fig2paper) summarizes the reasons given among respondents who said they were not willing to take a Covid vaccine.
+We find striking consistency in most trusted sources across studies.
+In all but one sample, including those from Russia and the USA, respondents identified the health system as the most trustworthy source to help them decide whether to take the COVID-19 vaccine.
+The average across LMICs was `r trust_all$estimate`% (`r trust_all$conf.low`--`r trust_all$conf.high`%).
+Respondents in `r trust_top$group[1]` (`r trust_top$estimate[1]`%, `r trust_top$conf.low[1]`--`r trust_top$conf.high[1]`%), `r trust_top$group[2]`  (`r trust_top$estimate[2]`%, `r trust_top$conf.low[2]`--`r trust_top$conf.high[2]`%) and `r trust_top$group[3]` (`r trust_top$estimate[3]`%, `r trust_top$conf.low[3]`--`r trust_top$conf.high[3]`%) cited  health workers most often.
+Sierra Leone had the highest trust in health workers and the Ministry of Health, potentially due to investments in public health following the 2014-2015 Ebola epidemic [@deserrano].
 
-The most common reason expressed for reluctance to take the vaccine in LMIC studies was  concern about side effects.
-For studies  `r side_top$group[1]` (`r side_top$estimate[1]`% `r side_top$conf.low[1]`--`r side_top$conf.high[1]`), `r side_top$group[2]`  (`r side_top$estimate[2]`%, `r side_top$conf.low[2]`--`r side_top$conf.high[2]`), `r side_top$group[3]` (`r side_top$estimate[3]`% `r side_top$conf.low[3]`--`r side_top$conf.high[3]`) and `r side_top$group[4]` (`r side_top$estimate[4]`% `r side_top$conf.low[4]`--`r side_top$conf.high[4]`), more than half of those respondents unwilling to take the vaccine mentioned this reason.
-Respondents in Russia (`r side_rus$estimate`%, `r side_rus$conf.low`--`r side_rus$conf.high`) and the USA (`r side_usa$estimate`%, `r side_usa$conf.low`--`r side_usa$conf.high`), reported high levels of this same concern.
+The next most cited sources were family and/or friends in  `r trust_fam$group[1]` (`r trust_fam$estimate[1]`%, `r trust_fam$conf.low[1]`--`r trust_fam$conf.high[1]`%), `r trust_fam$group[2]`  (`r trust_fam$estimate[2]`%, `r trust_fam$conf.low[2]`--`r trust_fam$conf.high[2]`%), `r trust_fam$group[3]` (`r trust_fam$estimate[3]`%, `r trust_fam$conf.low[3]`--`r trust_fam$conf.high[3]`%) and `r trust_fam$group[4]` (`r trust_fam$estimate[4]`%, `r trust_fam$conf.low[4]`--`r trust_fam$conf.high[4]`%).
+Across the pooled samples, women were 3 percentage points more likely to rely on family and friends than male respondents, though this difference was not statistically significant (Figure \@ref(fig:genderhist) in [Appendix D](#appendixd)).
 
-While serious adverse events that are life-threatening or require hospitalization are very rare, with only .6\% of respondents reporting at least one side effect in the Pfizer vaccine trial [@cdcadverse], one potential explanation for the outsized concern about side effects could be the lack of widespread information about features of the vaccine at the time of data collection.
-Media coverage of the few cases of serious adverse events and spread of fake news may contribute as well [@stein2017golden].
+By contrast, in `r trust_gov$group[1]` (`r trust_gov$estimate[1]`%, `r trust_gov$conf.low[1]`--`r trust_gov$conf.high[1]`%), `r trust_gov$group[2]`  (`r trust_gov$estimate[2]`%, `r trust_gov$conf.low[2]`--`r trust_gov$conf.high[2]`%), `r trust_gov$group[3]` (`r trust_gov$estimate[3]`%, `r trust_gov$conf.low[3]`--`r trust_gov$conf.high[3]`%) and `r trust_gov$group[4]` (`r trust_gov$estimate[4]`%, `r trust_gov$conf.low[4]`--`r trust_gov$conf.high[4]`%), government was the second most frequently cited.
+Religious leaders and celebrities were not seen as the top sources of guidance by many respondents in any sample other than Nepal, where many respondents most trusted famous people (`r trust_npl$estimate`%, `r trust_npl$conf.low`--`r trust_npl$conf.high`%).
 
-Concerns about side effects could also be due to a concern about mild side effects from experiences with other vaccines.
-In the case of available COVID-19 vaccines, we now know that mild side effects are common but transient.
-These include fatigue, muscle pain, joint pain and headache, which were severe in fewer than 10\% of people in the clinical trials of tens of thousands.
-Severe fever occurred in fewer than 2\% of them.
-[@wadman2020public]
-
-Allergic reactions from the COVID-19 vaccine seem to be extremely rare.
-Data from trials of the Pfizer-BioNTech vaccines shows that anaphylaxis after reported administration occurs at a rate of 11.1 cases per million vaccine doses administered [@cdcallergies].
-Our data reflects this --  no more than 6% of respondents expressed concern about allergies in any of our LMIC studies.
-
-Other concerns that make many respondents unwilling to take the vaccine could be countered by accurately presenting the scientific data to the public.
-Studies `r effective_top$group[1]` (`r effective_top$estimate[1]`%, `r effective_top$conf.low[1]`--`r effective_top$conf.high[1]`), `r effective_top$group[2]`  (`r effective_top$estimate[2]`%, `r effective_top$conf.low[2]`--`r effective_top$conf.high[2]`) and `r effective_top$group[3]` (`r effective_top$estimate[3]`%, `r effective_top$conf.low[3]`--`r effective_top$conf.high[3]`) showed relatively high levels of skepticism about vaccine effectiveness.
-This is also true for respondents in Russia (`r effective_rus$estimate`%, `r effective_rus$conf.low`--`r effective_rus$conf.high`) and the USA (`r effective_usa$estimate`%, `r effective_usa$conf.low`--`r effective_usa$conf.high`).
-Recent clinical trials reveal very high rates of vaccine efficacy [@baden2021efficacy; @polack2020safety], and clearly communicating these results to the public is a high priority.
-In contrast, conspiracy theories were rarely mentioned by respondents in any of our study samples, in spite of widespread popular discourse about anti-vaxxer movements and theories in higher-income countries [@loomba_measuring_2021].
-
-Finally, respondents in some studies downplayed the seriousness of this disease, and listed this as a reason not to be vaccinated.
-Studies `r ill_top$group[1]` (`r ill_top$estimate[1]`% `r ill_top$conf.low[1]`--`r ill_top$conf.high[1]`), `r ill_top$group[2]`  (`r ill_top$estimate[2]`%, `r ill_top$conf.low[2]`--`r ill_top$conf.high[2]`) and `r ill_top$group[3]` (`r ill_top$estimate[3]`% `r ill_top$conf.low[3]`--`r ill_top$conf.high[3]`) reported high rates of respondents citing lack of concern as a reason they were hesitant.
-
-The analysis above identifies the nature of the information gaps that any vaccine messaging should target, while in Figure \@ref(fig:fig3paper) we try to identify the actors who are best placed to deliver those messages.
-We asked respondents about their most trusted source of information when deciding whether to take the vaccine, because these sources are vital to disease control strategies during public health emergencies [@siegrist2014role].
-Results from Figure \@ref(fig:fig3paper) are reproduced as Table \ref{tab:trust} in [Appendix A](#appendixd).
-
-We find striking consistency across countries.
-In all but one study, respondents identified the health system as the most trustworthy source to help them decide whether or not to take the COVID-19 vaccine (with the exception of Rwanda, where the government in general was identified as the most trusted source, with the health system a close second).
-Family and friends were the next most important reference points in most samples.
-Across samples, women were 3 percentage points more likely to rely on family and friends than male respondents, though this difference was not significant at conventional levels (Figure \@ref(fig:genderhist) in [Appendix D](#appendixd)).
-By contrast, endorsements by religious leaders or celebrity figures were not seen as important sources of influence in any sample other than Nepal.
+Finally, we highlight two idiosyncratic, yet frequently mentioned, trusted sources of information in deciding whether to take a COVID-19 vaccine.
+In Rwanda, 34% of respondents would most trust “themselves” for guidance, the most frequent response in this sample.
+In the USA, 14% of respondents cited Joe Biden, then president-elect and therefore excluded from the “government” category, as their most trusted source.
 
@@
 
-To our knowledge, this is the first study documenting rates of expressed COVID-19 vaccine acceptance and hesitancy in a large set of LMICs.
-Our findings show variable but broadly high levels of prospective COVID-19 vaccine acceptance across LMICs using data from `r nice(nrow(filter(df, country!="USA" | country!="Russia")))` respondents in `r length(unique(df$country))-2` original household surveys from Africa (Burkina Faso, Mozambique, Nigeria, Rwanda, Sierra Leone, Uganda), Asia (Bangladesh, India, Nepal, Pakistan), and Latin America (Colombia).
-Acceptance across LMIC averages `r ans_mean`, ranging between  `r ans_min` and `r ans_max`.
-We document considerably lower levels of acceptance in Russia and the United States.
+<!-- Temp subheading: interpretation of results -->
+To our knowledge, this is the first study focusing on COVID-19 vaccine attitudes in a large set of low-income and lower-middle-income countries.
+Our findings showed variable but broadly high levels of prospective COVID-19 vaccine acceptance across LMICs, using data from `r nice(nrow(filter(df, country!="USA" | country!="Russia")))` respondents in `r length(unique(df$country))-2` studies in ten LMICs in Africa, South Asia, and Latin America.
+Acceptance across these LMIC samples  averaged `r ans_mean`%, ranging between `r ans_min`% and `r ans_max`%.
+The two benchmark countries, Russia and the USA, demonstrated lower COVID-19 vaccine acceptance, consistent with relatively lower pre-pandemic vaccine confidence.
 
-Patterns of COVID-19 vaccine hesitancy are not well predicted by existing measures of concerns about the safety of other vaccines (e.g., the Wellcome Global Monitor shown in Table \ref{tab:otherv}).
-Compared with other vaccines, COVID-19 vaccine acceptance is lower and more variable across LMIC samples.
-This suggests that concerns may apply specifically to COVID-19 vaccines rather than to vaccination more broadly.
+Many metrics and indices measure vaccine acceptance and hesitancy globally [@betsch2018beyond; @domek2018measuring; @shapiro2018vaccine; @gilkey2014vaccination,].
+Our surveys used measures employed in other COVID-19 vaccine acceptance studies [@fisher2020attitudes;  @Malik2020; @wouters2021challenges; @lazarus2020nature; @kreps2020factors; @shekhar2021covid; @dror2020vaccine] and recommended by the WHO Data for Action guidance [@whodata], allowing for meaningful cross-study and cross-country comparisons.
+We measure trust in sources of information about COVID-19 vaccination using a measure similar to that used in the Vaccine Confidence Index (VCI), a widely used survey tool [@defigueiredo2020lancet].
 
-Our study also documents reasons why respondents express intentions to take (or not take) a COVID-19 vaccine.
-The main reason expressed for willingness to take such a vaccine was to protect oneself.
-The most common reasons offered by those unwilling to take the vaccine were concerns about safety (side effects) and efficacy.
-Across all contexts, health care workers were the most trusted source of information  about vaccines.
+Consistent with other studies, we find higher vaccine acceptance among men than women [@kreps2020factors; @shekhar2021covid; @dror2020vaccine;  @fisher2020attitudes; @wouters2021challenges].
+In contrast to studies focused primarily on higher-income countries, we find no consistently significant differences with respect to age [@kreps2020factors; @dror2020vaccine] or education in our LMIC samples.
 
-Our study samples offer an important window into the motivations underlying COVID-19 vaccine acceptance in LMICs, but our data are not fully nationally representative.
-Random digit dial samples and follow-up phone surveys, while necessary during a global pandemic, do not include individuals who reside outside coverage areas, who do not own or cannot operate cell phones, or who choose not to respond to telephone surveys.
-Care should also be taken in any attempt to extrapolate to the population level from the samples representative of narrow subpopulations.
+A key contribution of our study relative to the previous literature is its focus on the reasons why respondents express intentions to take (or refuse) a COVID-19 vaccine.
+Other work has highlighted appeals to altruistic behavior or other prosocial motivations to promote vaccine acceptance [@chou2020considering].
+Yet we find that the potential risks and benefits to personal well-being feature much more prominently in our respondents’ reasoning, suggesting that appeals about personal protection may be more effective in LMICs.
 
-If intentions reported in our LMIC samples translated into actual vaccination uptake, the rates would far exceed the range of what would be required for COVID-19 herd immunity (40-67% in recent estimates [@britten2020; @haley2020]).
-However, reported intent may not materialize into actual vaccine adoption [@mceachanetal2011].
-The high salience of COVID-19 due to extensive media coverage and government mitigation efforts and excitement around vaccine release may have increased reported intention [@chen1996].
-Results from  the first COVID-19 vaccine Phase 3 clinical trial were announced before some surveys were fielded; during others, subsequent approvals were granted.
-The fast-moving information environment may change people’s perceptions about vaccines by the time they are widely available in LMICs.
+The most commonly stated reason for vaccine refusal was concern about safety (side effects).
+Around 86% of our surveys were conducted as reports from Phase 2 and 3 clinical trial data were emerging for the earliest commercially available vaccines, but prior to the first Emergency Use Authorization of any vaccine (Pfizer-BioNTech approved by the USA on December 11, 2020).
+Early trial data showed that severe adverse effects were extremely rare [@mulligan2020phase; @logunov2021safety; @folegatti2020safety; @voysey2021safety; @baden2021efficacy; @polack2020safety], occurring in fewer than 10\% of people in clinical trials [@wadman2020public].
+Our respondents’ outsized concern about side effects could reflect the rapid pace of vaccine development, [@callaway2020russia] and limited information available about potential COVID-19 vaccine safety at the time of data collection.
+These concerns could also reflect worries about mild, yet common and transient side effects, such as fatigue, muscle pain, joint pain and headache.
 
-Nonetheless, our findings provide some specific guidance on how to design messaging to boost COVID-19 vaccine acceptance and uptake in LMICs.
-Our data have implications for both what the content of the message should be, and who should deliver the message.
+Prominent media coverage of adverse events may exacerbate concerns about side effects [@stein2017golden].
+In particular, new information about rare but severe cases of thrombosis associated with the Astra-Zeneca vaccine that appeared after our data collection period could affect hesitancy levels.
+This is of particular relevance to LMICs, which are likely to rely on the Astra-Zeneca vaccine in their immunization campaigns, through initiatives such as COVAX.
 
-First, high levels of trust in the advice of health workers and governments on COVID-19 vaccine decision-making suggest that social and behavioral change communication (SBCC) strategies that engage local health workers may be particularly effective tools to encourage timely and complete vaccine uptake, and to combat remaining vaccine hesitancy.
-The literature has  explored messaging strategies to promote welfare-improving behaviors, with considerable attention paid to celebrity endorsements [@alatas2019celebrities].
-Our data strongly support the view [@bokemper2021timing] that those with the most relevant expertise - as opposed to celebrities or general opinion leaders - are most trusted on this specific topic and are therefore best positioned to deliver the message.
+Concerns about vaccine efficacy, averaging approximately `r filter(effective_top, group=="All") %>% pull(estimate)`% in the LMIC samples, may also reflect a lack of information about vaccines at the time of our surveys.
+Strikingly, even in low-information environments, respondents in our samples rarely cited conspiracy theories about ulterior motives on the part of corporations, politicians or the pharmaceutical industry, despite widespread popular fears about these issues in higher-income countries [@loomba_measuring_2021].
 
-Second, the average COVID-19 vaccine acceptance rate across our LMIC samples is high, approximately `r ans_mean`\%.
-Given such positive intentions, there may be high returns to investing in straightforward “last-mile” nudges that help citizens convert intentions into actions.
-Reminder messages from healthcare providers and messages alerting patients that vaccines have been reserved for them at an upcoming appointment may provide a low-cost encouragement to initiate and complete two-dose COVID-19 vaccinations, as was found in two recent large-scale studies in the United States [@milkmanetal2021a; @milkmanetal2021b].
-Similarly, childhood vaccination reminders plus cash incentives in Kenya substantially increased full immunization [@gibsonetal2017], and cash and in-kind incentive programs in Nigeria and India have also proven effective [@idinsight; @Banerjee2010].
+<!-- Temp subheading: limitations -->
+An important limitation of our study is that our samples are not fully nationally representative.
+Phone surveys, while necessary during a global pandemic, do not include individuals who reside outside coverage areas, lack access to a cell phone, or do not respond to calls.
+In addition, as shown in Table \ref{tab:sampling}, several studies focus on sub-populations of interest in pre-existing studies to which questions about COVID-19 vaccination were added.
+Particular care should be taken in any attempt to extrapolate to the national population level from these samples.
+Furthermore, we emphasize that our data are not representative of all LMICs.
+They represent a convenience sample of studies in countries in which our organizations could quickly mobilize coordinated data collection.
 
-Third, high coverage rates of existing vaccines, coupled with respondents’ reliance on friends and family as information sources, suggest that the general pro-vaccination stance of many citizens could be leveraged to convert intent to uptake.
-Social learning strategies and norm-setting are powerful drivers of information diffusion and behavior change in many related sectors [@beaman2021can].
-Social signalling of positive attitudes toward COVID-19 vaccines may also help shift social norms toward even greater immunization acceptance and two-dose completion in the community at large [@karing2018social].
+The expressed intentions to take a COVID-19 vaccine that we document in our LMIC samples, if translated into behavior, would meet or exceed the current herd immunity threshold for COVID-19 (estimated at 60-80%, based on the predominant variant in circulation in these countries [@omer2020herd; @aschwanden2021five; @mcneil_2021]).
+However, reported intent may not always convert vaccine uptake [@mceachanetal2011].
+The high salience of COVID-19 due to extensive media coverage may have increased reported intentions.
+Conversely, reports about side effects and risks associated with expedited vaccine development may have increased hesitancy.
+The fast-moving pandemic and vaccine development context may change perceptions about vaccines by the time they are widely available in LMICs.
 
-Finally, our findings offer guidance on the specific content of vaccine messaging that is likely to be most persuasive.
-Messaging should highlight the high efficacy rates of the COVID-19 vaccines currently on the market in reducing or eliminating disease, hospitalizations and death.
-Alluding to clinical data that addresses people’s concerns about potential side effects should be prioritized.
-Messaging should also emphasize the direct protective benefits of the vaccine to the adopter.
+Indeed, previous research on vaccine hesitancy has emphasized how concerns that arise surrounding vaccination campaigns are often case- and context-specific [@larson2011addressing], making it difficult to predict exactly how COVID-19 vaccines will be received in any given setting.
+The lower COVID-19 vaccine acceptance rates we observe in Russia and the USA, for example, may reflect the politicization of this specific pandemic and vaccine development [@hornsey2020donald; @bokemper2021timing; @aaslund2020responses; @burki2020russian], in addition to generally greater vaccine skepticism.
+
+<!-- Temp subheading: implications of results -->
+
+Nonetheless, our findings suggest several concrete implications for policy relating to vaccine roll-out in LMICs.
+First and foremost, we document high levels of COVID-19 vaccine acceptance in LMICs compared to Russia and the USA.
+While global vaccine distribution has skewed heavily toward higher-income countries to date [@wouters2021challenges],  our findings suggest that prioritizing distribution to LMICs is justified not only on equity grounds, but on the expectation of “better value” in maximizing global coverage more quickly.
+
+Our findings also imply that, once vaccine distribution to LMICs begins in earnest, interventions should focus on converting positive intentions into action.
+Straightforward, low-cost nudges may be particularly effective in this regard.
+Two recent large-scale studies in the USA found that vaccination appointment reminder messages from healthcare providers increased influenza vaccine uptake [@milkmanetal2021a; @milkmanetal2021b].
+Similar interventions have proven effective in increasing immunization in LMIC contexts.
+In Ghana and Kenya, vaccination reminders plus small cash incentives increased childhood immunization coverage [@levine2021; @gibsonetal2017].
+Cash and in-kind incentives programs were also effective in Nigeria and India [@idinsight; @Banerjee2010].
+
+This recommendation is consistent with accepted frameworks, such as the WHO’s Behavioral and Social Drivers of vaccination (BeSD) model, which suggests leveraging favorable intentions through reminders and primes, and reducing access barriers when the vast majority of people intend to be vaccinated [@brewer2017increasing; @whodata].
+Particularly since COVID-19 vaccination may be more collectively than individually optimal, ease of access is critical to achieve high coverage [@betsch2013inviting].
+
+Our findings also suggest directions for the design and delivery of messaging to boost COVID-19 vaccine acceptance and uptake in LMICs.
+We highlight four potential implications.
+First, our data strongly support the view that respondents from LMICs prefer to follow the guidance of actors with the most relevant knowledge and expertise.
+We find high levels of trust in health workers, which suggests that social and behavioral change communication (SBCC) strategies engaging local health workers may be particularly effective in encouraging efficient and comprehensive vaccine uptake and combating remaining hesitancy [@who2020behavioral; @bokemper2021timing].
+Health workers have been the first group to receive the COVID-19 vaccine and are therefore best-positioned to share locally credible experiences of vaccination [@katzman2021primary].
+While celebrities were not identified as a particularly trustworthy source for COVID-19 advice in our study, celebrity endorsements have proven effective in other contexts and may complement a strategy that primarily focuses on health workers [@alatas2019celebrities].
+
+Second, our findings offer guidance on the specific content of vaccine messaging that is likely to be most persuasive.
+Hesitant respondents were most concerned about side effects and vaccine efficacy.
+This suggests that messaging should highlight the high efficacy rates of the COVID-19 vaccines currently on the market in reducing or eliminating disease, hospitalizations, and death, and communicate accurate information about potential side effects.
+Our data also suggest that messaging should emphasize the direct protective benefits of the vaccine to the adopter, since personal protection, rather than broader concerns about protecting public health, was the top reason expressed for vaccine-acceptance by our respondents.
+
+Third, consistent with previous studies on COVID-19 vaccination [@kreps2020factors; @shekhar2021covid; @dror2020vaccine;  @fisher2020attitudes; @wouters2021challenges] our study finds lower vaccine acceptance among women than men, suggesting that messaging strategies should focus on women.
+Recent work in Latin America on COVID-19 vaccine messaging found that the provision of basic information about the vaccines was particularly effective in persuading hesitant women [@argote2021messaging].
+
+Finally, high coverage rates of existing vaccines, coupled with respondents’ reliance on friends and family as information sources, suggest that the general pro-vaccination stance of many LMIC citizens could be leveraged to increase uptake of COVID-19 vaccines as they become available.
+Social learning strategies and norm-setting are powerful drivers of  behavior in many related sectors [@beaman2021can].
+Social signaling of positive attitudes toward and uptake of COVID-19 vaccines may also help shift social norms toward even greater immunization acceptance and two-dose completion in the community at large [@karing2018social].
 
@@
 Across studies, we asked respondents, “If a COVID-19 vaccine becomes available in [your country], would you take it?”.
+This measure aligns with widely reported COVID-19 vaccine acceptance measures [@fisher2020attitudes;  @Malik2020; @wouters2021challenges; @lazarus2020nature; @kreps2020factors; @shekhar2021covid; @dror2020vaccine].
 If the respondent answered yes to this question, we followed up with the question, “Why would you take it?
@@
 [the COVID-19 vaccine]”.
-Finally, regardless of their expressed willingness to take the vaccine, we asked about  actors and institutions who would be influential in their decision.
-The question was worded in the following way: “Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available?”.
-To examine heterogeneity across demographic strata, we collected information about the gender, age, and education level of each respondent.
-Slight variations in questions wording and answer options across studies are documented in [Appendix B](#appendixb).
+Finally, regardless of their expressed willingness to take the vaccine, we asked about actors and institutions that would be most influential in their decision: “Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available?” following [@defigueiredo2020lancet].
+To examine heterogeneity across demographic strata, we collected information about gender, age, and education.
+Slight variations in question wording and answer options across studies are documented in [Appendix B](#appendixb).
 
@@
 Seven were national or nearly-national in scope.
-Among these, studies from Burkina Faso, Colombia, Rwanda, and Sierra Leone ("Sierra Leone 1") used nationally-representative samples of active mobile phone numbers reached through Random Digit Dialing (RDD).
+Studies from Burkina Faso, Colombia, Rwanda, and Sierra Leone ("Sierra Leone 1") used nationally-representative samples of active mobile phone numbers reached through Random Digit Dialing (RDD).
 Studies in the USA and Russia were conducted online using quota samples obtained from private survey companies.
@@
 The remaining eight studies targeted sub-national populations.
-One study from Pakistan ("Pakistan 2") used RDD to reach a representative sample of active mobile phone users in Punjab province.
-Respondents in Mozambique, Nigeria, "Pakistan 1", "Uganda 1","Uganda 2", India, Nepal and "Sierra Leone 2” were drawn from pre-existing studies to which COVID-19 vaccine questions were subsequently added.
-For example, "Sierra Leone 2” has national coverage from a study on access to electricity and “Uganda 1” sampled female caregivers of households in rural and semi-rural villages as part of a large ongoing cluster-RCT implemented across 13 districts.
+One study from Pakistan ("Pakistan 2") used RDD in Punjab province.
+Respondents in Mozambique, Nigeria, Pakistan ("Pakistan 1"), Uganda ("Uganda 1","Uganda 2"), India, Nepal and Sierra Leone ("Sierra Leone 2”) were drawn from pre-existing studies to which COVID-19 vaccine questions were subsequently added.
+For example, Sierra Leone 2 has national coverage from a study on access to electricity and Uganda 1 sampled female caregivers of households in rural and semi-rural villages as part of a large ongoing cluster-RCT implemented across 13 districts.
 
 Table \ref{tab:sampling} in [Appendix A](#appendixd) summarizes the geographic scope, sampling methodologies and survey modalities of all 15 studies.
-A detailed description of each study is included in [Appendix D](#appendixa).
+A detailed description of each study is included in [Appendix C](#appendixa).
 
-All LMIC surveys were conducted via telephone to minimize in-person contact and comply with local government social distancing guidelines.
+All surveys were conducted remotely to minimize in-person contact and comply with social distancing guidelines.
 Interviews were conducted by local staff in each country in local language(s).
 Surveying by phone made rapid, large-scale data collection possible.
-Surveys lasted approximately 15 to 40 minutes.
+In two samples, the USA and Russia, surveys occurred via online polling.
+All surveys lasted approximately 15 to 40 minutes.
 
-Taken together, we have data from `r nice(nrow(filter(df, country!="USA" & country!="Russia")))` individuals from LMICs and `r nice(nrow(filter(df, country=="USA" | country=="Russia")))` from the USA and Russia, for a total of `r nice(nrow(df))` respondents.
+Taken together, we have data from `r nice(nrow(filter(df, country!="USA" & country!="Russia")))` individuals from 10 LMICs and `r nice(nrow(filter(df, country=="USA" | country=="Russia")))` from the USA and Russia, for a total of `r nice(nrow(df))` respondents.
 
@@
 This was calculated combining all other answer options (“No”, “Don’t Know” and “Refuse”) into a single reference category.
-We estimated this outcome for each study with robust standard errors and employed sampling weights where available.
+We estimated average acceptance for each individual sample via ordinary least squares (OLS) weighted by respective study population weights and robust standard errors clustered at the level relevant for the sample.
 
-In addition to study-level estimates, we combined data from all studies other than the USA and Russia to calculate an aggregate estimate for all LMIC studies.
-For these analyses, each included study received equal weight and standard errors were clustered at the study level.
-Averages in the “All LMICs” group then reflect the expected share across studies.
-In this combined analysis we also estimated the underlying heterogeneity of vaccine acceptance across studies using the between studies variance estimator $\tau^2$ from a random effects model.
+In addition to study-level estimates, we combined data from all studies other than the USA and Russia to calculate an aggregate “All LMIC studies” estimate.
+For these analyses, we estimated average acceptance by OLS with weights for each study normalized such that the total weight given to observations was constant across studies.
+Robust standard errors for these analyses were clustered at the study level.
 
-We also conducted subgroup analyses by gender, age and education level and reported differences between groups.
-For the “All LMICs” analyses we calculated the average of differences between subgroups within studies with standard errors clustered at the study level.
+We note the core results would be virtually unchanged at `r round(100*unit_check$estimate[2], 1)`% (`r round(100*unit_check$conf.low[2], 1)`--`r round(100*unit_check$conf.high[2], 1)`) rather than `r round(100*unit_check$estimate[1], 1)`% (`r round(100*unit_check$conf.low[1], 1)` -`r round(100*unit_check$conf.high[1], 1)`) using countries rather than studies as groups in the pooled analysis, that is if we set weights so that the sum of weights in each country (rather than in each study) sum to a constant and cluster standard errors at the country level (rather than the study level).
 
-We additionally examined reported reasons for COVID-19 vaccine acceptance and hesitancy, as well as the types of actors respondents would trust when making the decision about whether to take a COVID-19 vaccine.
-Among respondents who expressed willingness to take the vaccine, we asked about several possible reasons why they would take it.
-For respondents unwilling to take the vaccine, we asked about several possible reasons why they would not take it.
-Finally, we asked all respondents, regardless of their answers to other questions, whom they would trust most to help them decide whether to get a COVID-19 vaccine.
-We report estimates of agreement with reasons for vaccine acceptance/hesitancy and trust in actors for individual studies and for the “All LMICs” group.
+In this combined analysis, we also estimated the underlying heterogeneity of vaccine acceptance across studies using the between studies variance estimator $\tau^2$ from a random effects model.
+
+We conducted subgroup analyses by gender, age and education level and reported differences between groups.
+For age, we selected cut-offs below 25, between age 25 and 54, and above 55 years old, closely following the age breakdown proposed by recent work on COVID-19 vaccine acceptance [@lazarus2020nature].
+However, the lower life expectancy (63 years on average [@wbage]) and younger-skewing populations (only 5% of the population is above 65 years old [@WorldBanksubSahara]) of low-income countries in particular, precluded further disaggregation at the upper end of the age distribution.
+For education, we divided the sample between respondents who had completed secondary school and those that had not.
+We defined these two groups to reflect broader schooling trends in LMICs, where out of every 100 students entering primary education, 61% complete lower secondary education [@world2017world].
+The subgroup analyses estimates are calculated in exactly the same way as the overall acceptance rate---with weights again normalized to sum to a constant within each study---with the exception that the subsample used in the analysis is limited to those respondents fitting each demographic group.
+
+We then investigated stated reasons for COVID-19 vaccine acceptance and hesitancy, and the types of actors respondents would trust most when making the decision about whether to take a COVID-19 vaccine.
+We report estimates of agreement with reasons for vaccine acceptance/hesitancy and trust in actors for individual studies and for the “All LMICs” group, which includes all study samples except Russia and the USA.
+Estimates were calculated with the same procedure as above, varying only the quantity of interest; i.e.
+one model is run for each reason why a respondent would (or would not) take the vaccine and each trusted actor.
 
@@
 
-# Contributors{-}
+# Data Availability Statement {-}
+Individual participant data (de-identified) that underlie the results reported in this article, are available without restrictions at \url{https://github.com/wzb-ipi/covid_vaccines_nmed}.
+
+# Code Availability {-}
+All code has been deposited into the publicly available GitHub repository at \url{https://github.com/wzb-ipi/covid_vaccines_nmed}.
+The code and output for all analyses can be easily inspected at \url{https://wzb-ipi.github.io/covid_vaccines_nmed/replication.html}.
+
+# Acknowledgements {-}
+
+This work would not have been possible without the hard work and ingenuity of many.
+For valuable contributions to data collection during the challenging context of the global pandemic, we would like to thank:
+
+Burkina Faso: Béchir Wendemi Ouédraogo (M&E Associate), Achille Mignondo Tchibozo (Research Manager) and Touba Bakary Pare (Senior Field Manager) at IPA Burkina Faso in Ouagadougou for their work on the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+
+Colombia: Margarita Rosa Cabra Gacia (Senior Research Associate), Laura Polanco, María Juliana Otálora (Research Analyst), Sofía Jaramillo (Research Manager) and Mery Galindo (Field Coordinator) at IPA Colombia in Bogotá  for their work on the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+
+India: Bhartendu Trivedi, Yashashvi Singh, Tatheer Fatima and the field team of Morsel Research and Development.
+
+Mozambique: Alberto Arlindo, Imamo Mussa, Ismail Mussa, Frederica Mendonça and Simão Paiva from NOVAFRICA Mozambique office.
+
+Nepal: Arjun Kharel and field staff at the Centre for the Study of Labour and Mobility (CESLAM) in Kathmandu.
+
+Nigeria:  Opeyemi Adeojo (Department of Sociology, University of Lagos), Deborah Anigo, Isaac Obara, Segun Fayomi, and Aishwarya Kumar at the Busara Center for Behavioral Economics, and Sarah Ryan (University of Illinois at Chicago) for research assistance.
+
+Pakistan 1: Ahsan Tariq and Shan e Muhammad Malik at the Institute for Development and Economic Alternatives (IDEAS) in Lahore as survey wing leads and Hamid Ali Tiwana for research assistance.
+
+Pakistan 2: Staff and the internal survey firm at the Centre for Economic Research Pakistan (CERP).
+
+Rwanda: Jean Leodomir Habarimana Mfura (Research and Policy Coordinator), Jean Aime Nsabimana and Gisele Manirabaruta (Field Manager) at IPA Rwanda in Kigali for their work on the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+
+Russia: Staff at Online Market Intelligence Survey Agency, Kirill Chmel (HSE University) and Vladimir Zabolotsky (HSE University and University of Bologna) for their intellectual contributions and research assistance.
+
+Sierra Leone 1: Filippo Cuccaro (Research Coordinator) and Fatoma Momoh (Senior Field Manager) at IPA Sierra Leone in Freetown for their work on the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+
+Sierra Leone 2: Sellu Kallon (Field Manager), Junisa Nabieu (Field Supervisor), Momoh Flee (Field Supervisor), Hamid Kai, Mohamed Lamin (Field Supervisor) and all enumerators at IGC-Sierra Leone Freetown office and Wageningen University’s Project “Tracking the Economic Consequences of COVID-19 in Sierra Leone”.
+
+Uganda 1: Staff at IPA Uganda, especially Sarene Shaked and Gloria Ayesiga, for their intellectual contributions, research assistance, and support throughout the Uganda 1 study.
+
+Uganda 2: Co-PIs Ana Garcia Hernandez, Leah Rosenzweig, Lily Tsai, and Elly Atuhumuza, Martin Atyera, and their team of survey enumerators and support staff at IPA Uganda.
+
+United States: Staff at Lucid (survey firm) for distributing the survey and providing the online survey sample.
+
+IGC thanks their resident country teams in Sierra Leone, Uganda, Pakistan, and Mozambique for their continued guidance, coordination of activities with researchers and direct engagement and dissemination activities with national policymakers:
+
+* Herbert McLeod (Country Director) and Abou Bakarr Kamara (Country Economist) at IGC Sierra Leone
+* Richard Newfarmer (Country Director), Priya Manwaring (Country Economist), and Jakob Rauschendorfer (Country Economist) at IGC - Uganda
+* Ijaz Nabi (Country Director), Hina Shaikh (Country Economist), and Usman Naeem (Country Economist) at IGC - Pakistan
+* Claudio Frischtak (Country Director)  and Egas Daniel (Country Economist) at IGC - Mozambique
+
+IPA thanks staff from its global offices for their research assistance and support throughout the RECOVR survey.
+Hugo Salas (IPA Mexico) contributed to data analysis for Burkina Faso, Rwanda and Sierra Leone.
+Margarita Rosa Cabra Garcia also contributed to data analysis for Colombia.
+At IPA New York and Washington, DC, Michael Rosenbaum and Savanna Henderson provided research assistance.
+
+NOVAFRICA thanks Cátia Batista (NOVA SBE), Sandra Sequeira (LSE) and Inês Vilela (Royal Holloway, University of London and NOVAFRICA) for their intellectual contributions.
+
+Centre for Economic Research Pakistan (CERP) thanks Javaeria Qureshi (University of Illinois Chicago), Taimur Shah (CERP), and Basit Zafar (University of Michigan) for their contributions to the Economic Vulnerability Assessment (EVA) project from which the questions used in the Pakistan 2 study were drawn.
+
+# Contributors {-}
 JSo, SW, NMe, AS, NMc, GS, MV and AM are co-first authors. DK, MC, MT, MH, AMM and SO are co-last authors. AMM and SO are also the corresponding authors. 
@@
 SAb and NMe led the literature search, with input from AS, NMc, SW, AMM, AM and JSo.
-SW, NMe, AS, NMc, MV, GS, AA, SA, BA, AB,EB, CMB, AC, EC, MF, AG, AK, SK, RL, MBN, MP, JSh, JSv, PV, LB, BZ, MC, SAs, AC, AF, AH, MC, MT, and MH oversaw data collection as part of other research efforts.
+SW, NMe, AS, NMc, MV, GS, AA, SA, BA, AB, EB, CMB, AC, EC, MF, AG, AK, SK, RL, MBN, MP, JSh, JSv, PV, LB, BZ, MC, SAs, AC, AF, AH, MC, MT, and MH oversaw data collection as part of other research efforts.
 SW, NMe, and MT coordinated the project across study samples.
-The following verified the underlying data for individual study samples: EC (Burkina Faso, Colombia, Rwanda, Sierra Leone 1), BA (India), AS and RL (Nigeria), AG and MBN (Uganda 1), CMB and MH (Uganda 2), NMe and MV (Sierra Leone 2), GS (Russia), MF (Mozambique), AF and JSh (Pakistan 1), SAs (Pakistan 2), CV (Nepal), and NMc (USA).
+The following verified the underlying data for individual study samples: EC (Burkina Faso, Colombia, Rwanda, Sierra Leone 1), BA and AB (India), AS and RL (Nigeria), AG, JSv and MBN (Uganda 1), CMB and MH (Uganda 2), NMe and MV (Sierra Leone 2), GS (Russia), MF (Mozambique), AF and JSh (Pakistan 1), SAs (Pakistan 2), CV (Nepal), and NMc (USA).
 JSo, GS, MH and SA collated and processed all datasets used for the analysis.
@@
 
-# Data Availability Statement {-}
-Individual participant data (de-identified) that underlie the results reported in this article, analytic code and replication files will be available immediately following publication to no end date for anyone who wishes to access the data and use it for any purpose in a public, open access repository.
-A replication exercise is available here \url{https://wzb-ipi.github.io/covid_vaccines/replication.html}.
-
 # Funding {-}
@@
 
-Beyond Conflict, Bill and Melinda Gates Foundation, Columbia University, Givewell.org, Ghent University, HSE University Basic Research Program, International Growth Centre, Jameel Poverty Action Lab Crime and Violence Initiative, London School of Economics and Political Science, Mulago Foundation, NOVAFRICA at the Nova School of Business and Economics, NYU Abu Dhabi, Oxford Policy Management, Social Science Research Council, Trinity College Dublin COVID19 Response Funding, UK Aid, UKRI GCRF/Newton Fund, United Nations Office for Project Services, Weiss Family Fund, WZB Berlin Social Science Center, Yale Institute for Global Health, Yale Macmillan Center, and anonymous donors to IPA and Y-RISE.
+Funding was provided by Beyond Conflict, Bill and Melinda Gates Foundation, Columbia University, Givewell.org, Ghent University, HSE University Basic Research Program, International Growth Centre, Jameel Poverty Action Lab Crime and Violence Initiative, London School of Economics and Political Science, Mulago Foundation, NOVAFRICA at the Nova School of Business and Economics, NYU Abu Dhabi, Oxford Policy Management, Princeton University, Social Science Research Council, Trinity College Dublin COVID19 Response Funding, UK Aid, UKRI GCRF/Newton Fund, United Nations Office for Project Services, Weiss Family Fund, WZB Berlin Social Science Center, Yale Institute for Global Health, Yale Macmillan Center, and anonymous donors to IPA and Y-RISE.
 
@@
 
+```{r sampling, echo=FALSE}
+tab_sampling
+```
+
 ```{=latex}
@@
 ```{r mainfigure1, fig.height=7.5, fig.width = 9, warning = FALSE, dev='tikz', echo = FALSE}
-fig_1
+fig_1_ages
 ```
@@
 
-```{r yes, results = "asis", echo=FALSE}
+```{r yes, results = "asis"}
 tab_reasons_y
@@
 
-```{r sampling, echo=FALSE}
-tab_sampling
-```
-
 ```{r, results = "asis", echo=FALSE}
@@
 tab_reasons_y_all
+```
+
+\newpage
+
+```{r yesall1, results = "asis", echo=FALSE}
+tab_reasons_y_age
 ```
@@
 Respondents were only permitted to select one most trusted  actor or institution.
-Responses are broken down by acceptance of the COVID-19 vaccine.}
+Responses are broken down by acceptance of the COVID-19 vaccine.
+The color of the bars reflect the answer given to the question ``If a COVID-19 vaccine becomes available in [country], would you take it?'' with ``No'' and ``Don't know'' pooled together and ``All'' combined average of ``Yes'' and ``No / Don't know''}
+\end{figure}
+```
+
+\pagebreak
+
+```{=latex}
+\begin{figure}[!ht]
+\caption{Trusted actors and institutions, broken down by vaccine acceptance \label{fig:genderhist}}
+```
+```{r histcattrust, fig.height=9, fig.width = 10, warning = FALSE, dev='tikz', echo=FALSE}
+fig_hist_categories
+```
+```{=latex}
+\scriptsize{Figure 5 shows histograms of actors and institutions that respondents say they would trust most to help them decide whether or not to take the COVID-19 vaccine.
+Respondents were only permitted to select one most trusted  actor or institution.
+Responses are broken down by acceptance of the COVID-19 vaccine.
+The color of the bars reflect the answer given to the question ``If a COVID-19 vaccine becomes available in [country], would you take it?'' with ``No'' and ``Don't know'' pooled together and ``All'' combined average of ``Yes'' and ``No / Don't know''}
 \end{figure}
@@
 
-\clearpage
+\pagebreak
 
@@
 nas
+```
+
+\newpage
+
+```{r tcds, echo=FALSE}
+t_country_differences
 ```
@@
 ________________
-
-## Appendix C:  Additional contributors {-}
-
-<!-- Add here  RAs and others -->
-We thank Sellu Kallon and Sarah Ryan for valuable intellectual contributions and research assistance.
-
-IPA would like to thank staff in Burkina Faso, Colombia, Rwanda, Sierra Leone and the United States for their intellectual contributions, research assistance, and support throughout the RECOVR survey: Achille Mignondo Tchibozo, Michael Rosenbaum, Hugo Salas, Filippo Cuccaro, Jean Leodomir Habarimana Mfura, Doug Kirke-Smith, Savanna Henderson, Shahana Hirji, Kyle Holloway, Margarita Cabra.
-
-Russia team would like to thank staff at Online Market Intelligence survey agency and Kirill Chmel and Vladimir Zabolotsky for their intellectual contributions and research assistance.
-
 \newpage
 
-## Appendix D: Sample descriptions {.unnumbered #appendixa}
+## Appendix C: Sample descriptions {.unnumbered #appendixa}
 
@@
 
-<!-- \textbf{COVID-19 Survey Design:}  -->
-
 \emph{Sampling Frame:} A two-step sampling was applied, first, study households from the main study sample were sampled, then households from the whole slum population were added.
@@
 \emph{Survey Dates:} 
-Baseline: June to July 2020, Follow-up 1: October toNovember 2020, Follow-up 2:  December 16, 2020 toJanuary 18, 2021.
+Baseline: June to July 2020, Follow-up 1: October to November 2020, Follow-up 2:  December 16, 2020 to January 18, 2021.
 
@@
 The second study focused on the role of information to counteract the political resource curse after a substantial natural gas discovery.
-
-<!-- \textbf{COVID-19 Survey Design:} -->
 
@@
 \emph{Sample size, tracking and attrition:}  1,392 households
-
-<!--  \emph{Sampling Weights:} Included -->
 
@@
 
-### Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample, Sheikhupura Police Study Sample, Institute of Development and Economic Alternatives, Lahore University of Management Science, London School of Economics, Princeton University {-}
+### Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample, Sheikhupura Police Study Sample, Institute of Development and Economic Alternatives, Lahore University of Management Science, London School of Economics, Princeton University (Pakistan 1) {-}
 
@@
 
-### Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample {-}
+### Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample (Pakistan 2) {-}
 
@@
 Other: \emph{Moscow, Saint Petersburg, Khanty-Mansiysk Autonomous Okrug -- Ugra}.
-The remaining 24 federal subjects were excluded from the study due to inability to enroll sample size with desired characteristics (sample size, age, gender and education group composition).
+The remaining 24 federal subjects were excluded from the study due to inability to enroll sample size with desired characteristics (sample size, age, gender and education group composition) and account for less than 14% of the total adult population of Russia.
 
@@
 
-\emph{Sampling Weights:} Post-stratification weights are computed to match marginal population distributions of age, gender and education with target proportions coming from the 2019 Yearbook and 2015 Microcensus released by Russian Federal Bureau of National Statistics (Rosstat).
+\emph{Sampling Weights:} Post-stratification weights are computed to match marginal distributions of age, gender and education among the adult population of Russia with target proportions coming from the 2019 Yearbook and 2015 Microcensus released by Russian Federal Bureau of National Statistics (Rosstat).
 
@@
 
-#### Sierra Leone, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA) {-}
+#### Sierra Leone, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA) (Sierra Leone 1) {-}
 
@@
 
-#### Sierra Leone, Towns that are Candidates for Rural Electrification Nation-wide sample, International Growth Centre (IGC), Wageningen University & Research, Yale Research Initiative on Innovation and Scale (Y-RISE), WZB Berlin Social Science Center and Columbia University {-}
+#### Sierra Leone, Towns that are Candidates for Rural Electrification Nation-wide sample, International Growth Centre (IGC), Wageningen University & Research, Yale Research Initiative on Innovation and Scale (Y-RISE), WZB Berlin Social Science Center and Columbia University (Sierra Leone 2) {-}
 
@@
 
-\emph{Survey Dates:} October 7, 2020 and January 20, 2021 (earlier rounds included Wave 1: April 29-May 15; Wave 2: May 15-June 4; Wave 3: June 5-June 17; Wave 4: June 17-June 30; Wave 5: July 1-August 8; Wave 6: August 19-October 1).
+\emph{Survey Dates:} October 7, 2020 to January 20, 2021 (earlier rounds included Wave 1: April 29-May 15; Wave 2: May 15-June 4; Wave 3: June 5-June 17; Wave 4: June 17-June 30; Wave 5: July 1-August 8; Wave 6: August 19-October 1).
 The median survey time was 33 minutes.
@@
 
-#### Uganda Subnational sample, International Growth Center, Trinity College Dublin, Stockholm School of Economics and Misum, Institute for International Economic Studies, Stockholm University  {-}
+#### Uganda Subnational sample, International Growth Center, Trinity College Dublin, Stockholm School of Economics and Misum, Institute for International Economic Studies, Stockholm University (Uganda 1) {-}
 
@@
 In each household, the respondent was chosen as the female household head or the primary female health care giver of the household if the household head could not be found.
-
-<!-- \emph{Intervention:} IF APPLICABLE -->
 
@@
 
-<!-- \emph{IRB Approval:} X -->
+\emph{IRB Approval:} Mildmay Uganda Research Ethics Committee (protocol number 0109-2015) on September 21, 2020.
 
-### Uganda Subnational sample, WZB Berlin Social Science Center and Columbia University, NYU Abu Dhabi, Innovations for Poverty Action (IPA)  {-}
+### Uganda Subnational sample, WZB Berlin Social Science Center and Columbia University, NYU Abu Dhabi, Innovations for Poverty Action (IPA) (Uganda 2) {-}
 

### 2021-05-04 paper.Rmd
update files

@@
 author:
-- name: Julio S. Solís Arce, BA^[First author]
+- name: Julio S. Solís Arce, BA^[First author.]
   affiliation: WZB Berlin Social Science Center
@@
 - name: Georgiy Syunyaev, MPhil\(^*\)
-  affiliation: International Center for the Study of Institutions and Development (HSE University, Moscow, Russia)
+  affiliation: International Center for the Study of Institutions and Development, HSE University
   number: [1, ", ", 5, ", ",  24]
@@
 - name: Ekaterina Borisova, PhD
-  affiliation: Economics Department of Ghent University
+  affiliation: Department of Economics, Ghent University
   number: [5, ", ", 12]
@@
   number: 15
-- name: Dean Karlan, PhD^[Last author]
+- name: Dean Karlan, PhD^[Last author.]
   affiliation: Kellogg School of Management at Northwestern University
@@
   - \titleformat*{\section}{\large\bfseries}
+#  - \usepackage{lineno}
+#  - \linenumbers
 # linestretch: 1.5
@@
 ```{r main_text, child = "4_paper_supplementary_files/temp_download.Rmd"}
-
+knitr::opts_chunk$set(echo = FALSE)
 ```

### 2021-05-04 paper_files/figure-latex/fig2paper-1.tex
drop drive calls
update
no google drive
paper
update files

@@
-% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:30
+% Created by tikzDevice version 0.12.3.1 on 2021-05-04 13:12:53
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 87.69, 67.14) --
-	( 87.69,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (101.09, 67.14) --
-	(101.09,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (114.48, 67.14) --
-	(114.48,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (127.88, 67.14) --
-	(127.88,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 88.61, 67.14) --
+	( 88.61,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (101.74, 67.14) --
+	(101.74,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (114.88, 67.14) --
+	(114.88,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (128.01, 67.14) --
+	(128.01,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.00, 67.14) --
-	( 81.00,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.39, 67.14) --
-	( 94.39,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (107.79, 67.14) --
-	(107.79,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (121.18, 67.14) --
-	(121.18,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 82.05, 67.14) --
+	( 82.05,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.18, 67.14) --
+	( 95.18,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (108.31, 67.14) --
+	(108.31,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (121.44, 67.14) --
+	(121.44,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (111.16,137.15) --
-	(111.16,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (111.16,139.95) --
-	( 94.55,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.55,137.15) --
-	( 94.55,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (105.80,445.18) --
-	(105.80,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (105.80,447.98) --
-	(100.02,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.02,445.18) --
-	(100.02,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (101.14,417.18) --
-	(101.14,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (101.14,419.98) --
-	( 94.07,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.07,417.18) --
-	( 94.07,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.75,361.17) --
-	( 90.75,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.75,363.97) --
-	( 81.16,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.16,361.17) --
-	( 81.16,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.66,333.17) --
-	( 94.66,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.66,335.97) --
-	( 90.37,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.37,333.17) --
-	( 90.37,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 97.50,305.16) --
-	( 97.50,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 97.50,307.96) --
-	( 89.09,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.09,305.16) --
-	( 89.09,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (101.57,109.14) --
-	(101.57,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (101.57,111.94) --
-	( 99.86,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.86,109.14) --
-	( 99.86,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (107.95,277.16) --
-	(107.95,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (107.95,279.96) --
-	( 95.41,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.41,277.16) --
-	( 95.41,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (113.09,249.16) --
-	(113.09,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (113.09,251.96) --
-	(106.23,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (106.23,249.16) --
-	(106.23,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (116.20,221.16) --
-	(116.20,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (116.20,223.96) --
-	(107.84,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (107.84,221.16) --
-	(107.84,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (129.00,193.15) --
-	(129.00,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (129.00,195.95) --
-	(124.23,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (124.23,193.15) --
-	(124.23,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (109.13,165.15) --
-	(109.13,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (109.13,167.95) --
-	(103.61,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (103.61,165.15) --
-	(103.61,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (126.00, 81.14) --
-	(126.00, 86.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (126.00, 83.94) --
-	(120.97, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.97, 81.14) --
-	(120.97, 86.74);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (111.62,137.15) --
+	(111.62,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (111.62,139.95) --
+	( 95.34,139.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.34,137.15) --
+	( 95.34,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (106.37,445.18) --
+	(106.37,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (106.37,447.98) --
+	(100.69,447.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (100.69,445.18) --
+	(100.69,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.80,417.18) --
+	(101.80,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.80,419.98) --
+	( 94.86,419.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.86,417.18) --
+	( 94.86,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 91.61,361.17) --
+	( 91.61,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 91.61,363.97) --
+	( 82.20,363.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 82.20,361.17) --
+	( 82.20,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.44,333.17) --
+	( 95.44,338.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.44,335.97) --
+	( 91.24,335.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 91.24,333.17) --
+	( 91.24,338.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 98.23,305.16) --
+	( 98.23,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 98.23,307.96) --
+	( 89.98,307.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.98,305.16) --
+	( 89.98,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (102.22,109.14) --
+	(102.22,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (102.22,111.94) --
+	(100.54,111.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (100.54,109.14) --
+	(100.54,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (108.47,277.16) --
+	(108.47,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (108.47,279.96) --
+	( 96.18,279.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.18,277.16) --
+	( 96.18,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (113.51,249.16) --
+	(113.51,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (113.51,251.96) --
+	(106.79,251.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (106.79,249.16) --
+	(106.79,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (116.56,221.16) --
+	(116.56,226.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (116.56,223.96) --
+	(108.36,223.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (108.36,221.16) --
+	(108.36,226.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (129.11,193.15) --
+	(129.11,198.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (129.11,195.95) --
+	(124.44,195.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (124.44,193.15) --
+	(124.44,198.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (109.62,165.15) --
+	(109.62,170.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (109.62,167.95) --
+	(104.21,167.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (104.21,165.15) --
+	(104.21,170.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (126.17, 81.14) --
+	(126.17, 86.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (126.17, 83.94) --
+	(121.23, 83.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (121.23, 81.14) --
+	(121.23, 86.74);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (102.86,139.95) circle (  3.57);
-
-\path[fill=fillColor] (102.91,447.98) circle (  3.57);
-
-\path[fill=fillColor] ( 97.61,419.98) circle (  3.57);
-
-\path[fill=fillColor] ( 85.98,363.97) circle (  1.43);
-
-\path[fill=fillColor] ( 92.52,335.97) circle (  3.57);
-
-\path[fill=fillColor] ( 93.32,307.96) circle (  3.57);
-
-\path[fill=fillColor] (100.71,111.94) circle (  3.57);
-
-\path[fill=fillColor] (101.68,279.96) circle (  3.57);
-
-\path[fill=fillColor] (109.66,251.96) circle (  3.57);
-
-\path[fill=fillColor] (112.02,223.96) circle (  3.57);
-
-\path[fill=fillColor] (126.59,195.95) circle (  3.57);
-
-\path[fill=fillColor] (106.34,167.95) circle (  3.57);
-
-\path[fill=fillColor] (123.48, 83.94) circle (  3.57);
+\path[fill=fillColor] (103.48,139.95) circle (  3.57);
+
+\path[fill=fillColor] (103.53,447.98) circle (  3.57);
+
+\path[fill=fillColor] ( 98.33,419.98) circle (  3.57);
+
+\path[fill=fillColor] ( 86.93,363.97) circle (  1.43);
+
+\path[fill=fillColor] ( 93.34,335.97) circle (  3.57);
+
+\path[fill=fillColor] ( 94.13,307.96) circle (  3.57);
+
+\path[fill=fillColor] (101.38,111.94) circle (  3.57);
+
+\path[fill=fillColor] (102.32,279.96) circle (  3.57);
+
+\path[fill=fillColor] (110.15,251.96) circle (  3.57);
+
+\path[fill=fillColor] (112.46,223.96) circle (  3.57);
+
+\path[fill=fillColor] (126.75,195.95) circle (  3.57);
+
+\path[fill=fillColor] (106.89,167.95) circle (  3.57);
+
+\path[fill=fillColor] (123.70, 83.94) circle (  3.57);
 \definecolor{drawColor}{RGB}{169,169,169}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (152.13, 67.14) --
-	(152.13,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (165.53, 67.14) --
-	(165.53,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (178.92, 67.14) --
-	(178.92,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (192.32, 67.14) --
-	(192.32,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (153.05, 67.14) --
+	(153.05,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (166.18, 67.14) --
+	(166.18,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (179.32, 67.14) --
+	(179.32,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (192.45, 67.14) --
+	(192.45,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (145.43, 67.14) --
-	(145.43,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (158.83, 67.14) --
-	(158.83,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (172.22, 67.14) --
-	(172.22,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (185.62, 67.14) --
-	(185.62,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (146.48, 67.14) --
+	(146.48,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.62, 67.14) --
+	(159.62,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (172.75, 67.14) --
+	(172.75,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (185.88, 67.14) --
+	(185.88,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (159.63,137.15) --
-	(159.63,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (159.63,139.95) --
-	(150.10,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (150.10,137.15) --
-	(150.10,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (151.33,445.18) --
-	(151.33,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (151.33,447.98) --
-	(148.11,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (148.11,445.18) --
-	(148.11,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (157.97,417.18) --
-	(157.97,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (157.97,419.98) --
-	(152.24,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (152.24,417.18) --
-	(152.24,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (154.17,361.17) --
-	(154.17,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.72,333.17) --
-	(161.72,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.72,335.97) --
-	(157.11,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (157.11,333.17) --
-	(157.11,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.19,305.16) --
-	(161.19,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.19,307.96) --
-	(153.10,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (153.10,305.16) --
-	(153.10,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (153.52,109.14) --
-	(153.52,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (153.52,111.94) --
-	(152.29,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (152.29,109.14) --
-	(152.29,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (154.70,277.16) --
-	(154.70,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (154.70,279.96) --
-	(146.93,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (146.93,277.16) --
-	(146.93,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (169.12,249.16) --
-	(169.12,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (169.12,251.96) --
-	(162.37,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (162.37,249.16) --
-	(162.37,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (153.04,165.15) --
-	(153.04,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (153.04,167.95) --
-	(149.24,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (149.24,165.15) --
-	(149.24,170.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (160.40,137.15) --
+	(160.40,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (160.40,139.95) --
+	(151.05,139.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (151.05,137.15) --
+	(151.05,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (152.26,445.18) --
+	(152.26,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (152.26,447.98) --
+	(149.11,447.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (149.11,445.18) --
+	(149.11,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (158.78,417.18) --
+	(158.78,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (158.78,419.98) --
+	(153.16,419.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (153.16,417.18) --
+	(153.16,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (155.05,361.17) --
+	(155.05,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (155.05,363.97) --
+	(146.27,363.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (146.27,361.17) --
+	(146.27,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (162.45,333.17) --
+	(162.45,338.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (162.45,335.97) --
+	(157.94,335.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (157.94,333.17) --
+	(157.94,338.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (161.93,305.16) --
+	(161.93,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (161.93,307.96) --
+	(154.00,307.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.00,305.16) --
+	(154.00,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.42,109.14) --
+	(154.42,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.42,111.94) --
+	(153.21,111.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (153.21,109.14) --
+	(153.21,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (155.57,277.16) --
+	(155.57,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (155.57,279.96) --
+	(147.96,279.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (147.96,277.16) --
+	(147.96,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (169.70,249.16) --
+	(169.70,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (169.70,251.96) --
+	(163.08,251.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (163.08,249.16) --
+	(163.08,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (153.94,165.15) --
+	(153.94,170.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (153.94,167.95) --
+	(150.21,167.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.21,165.15) --
+	(150.21,170.75);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (154.86,139.95) circle (  3.57);
-
-\path[fill=fillColor] (149.72,447.98) circle (  3.57);
-
-\path[fill=fillColor] (155.13,419.98) circle (  3.57);
-
-\path[fill=fillColor] (149.67,363.97) circle (  1.43);
-
-\path[fill=fillColor] (159.42,335.97) circle (  3.57);
-
-\path[fill=fillColor] (157.17,307.96) circle (  3.57);
-
-\path[fill=fillColor] (152.88,111.94) circle (  3.57);
-
-\path[fill=fillColor] (150.85,279.96) circle (  3.57);
-
-\path[fill=fillColor] (165.74,251.96) circle (  3.57);
-
-\path[fill=fillColor] (151.17,167.95) circle (  3.57);
+\path[fill=fillColor] (155.73,139.95) circle (  3.57);
+
+\path[fill=fillColor] (150.69,447.98) circle (  3.57);
+
+\path[fill=fillColor] (155.99,419.98) circle (  3.57);
+
+\path[fill=fillColor] (150.63,363.97) circle (  1.43);
+
+\path[fill=fillColor] (160.19,335.97) circle (  3.57);
+
+\path[fill=fillColor] (157.99,307.96) circle (  3.57);
+
+\path[fill=fillColor] (153.79,111.94) circle (  3.57);
+
+\path[fill=fillColor] (151.79,279.96) circle (  3.57);
+
+\path[fill=fillColor] (166.39,251.96) circle (  3.57);
+
+\path[fill=fillColor] (152.11,167.95) circle (  3.57);
 \definecolor{drawColor}{RGB}{169,169,169}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (216.57, 67.14) --
-	(216.57,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (229.96, 67.14) --
-	(229.96,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (243.36, 67.14) --
-	(243.36,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (256.76, 67.14) --
-	(256.76,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (217.49, 67.14) --
+	(217.49,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (230.62, 67.14) --
+	(230.62,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (243.75, 67.14) --
+	(243.75,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (256.89, 67.14) --
+	(256.89,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.87, 67.14) --
-	(209.87,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (223.27, 67.14) --
-	(223.27,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (236.66, 67.14) --
-	(236.66,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (250.06, 67.14) --
-	(250.06,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (210.92, 67.14) --
+	(210.92,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (224.06, 67.14) --
+	(224.06,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (237.19, 67.14) --
+	(237.19,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.32, 67.14) --
+	(250.32,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (219.95,137.15) --
-	(219.95,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (219.95,139.95) --
-	(213.30,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.30,137.15) --
-	(213.30,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (215.34,445.18) --
-	(215.34,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (215.34,447.98) --
-	(212.28,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (212.28,445.18) --
-	(212.28,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.30,417.18) --
-	(216.30,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.30,419.98) --
-	(211.96,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (211.96,417.18) --
-	(211.96,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.14,389.17) --
-	(213.14,394.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (228.14,361.17) --
-	(228.14,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (228.14,363.97) --
-	(213.46,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.46,361.17) --
-	(213.46,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (220.27,333.17) --
-	(220.27,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (220.27,335.97) --
-	(216.46,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.46,333.17) --
-	(216.46,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (230.18,305.16) --
-	(230.18,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (230.18,307.96) --
-	(221.07,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (221.07,305.16) --
-	(221.07,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.14,109.14) --
-	(213.14,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.14,111.94) --
-	(212.34,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (212.34,109.14) --
-	(212.34,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (224.93,277.16) --
-	(224.93,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (224.93,279.96) --
-	(214.86,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (214.86,277.16) --
-	(214.86,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (220.16,249.16) --
-	(220.16,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (220.16,251.96) --
-	(215.28,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (215.28,249.16) --
-	(215.28,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.03,193.15) --
-	(213.03,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.03,195.95) --
-	(210.78,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (210.78,193.15) --
-	(210.78,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.78,165.15) --
-	(213.78,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.78,167.95) --
-	(211.32,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (211.32,165.15) --
-	(211.32,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (233.98, 81.14) --
-	(233.98, 86.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (233.98, 83.94) --
-	(227.82, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (227.82, 81.14) --
-	(227.82, 86.74);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (220.80,137.15) --
+	(220.80,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (220.80,139.95) --
+	(214.28,139.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.28,137.15) --
+	(214.28,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (216.28,445.18) --
+	(216.28,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (216.28,447.98) --
+	(213.29,447.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (213.29,445.18) --
+	(213.29,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (217.23,417.18) --
+	(217.23,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (217.23,419.98) --
+	(212.97,419.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (212.97,417.18) --
+	(212.97,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.13,389.17) --
+	(214.13,394.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.13,391.97) --
+	(210.56,391.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (210.56,389.17) --
+	(210.56,394.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (228.84,361.17) --
+	(228.84,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (228.84,363.97) --
+	(214.44,363.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.44,361.17) --
+	(214.44,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (221.11,333.17) --
+	(221.11,338.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (221.11,335.97) --
+	(217.38,335.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (217.38,333.17) --
+	(217.38,338.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (230.83,305.16) --
+	(230.83,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (230.83,307.96) --
+	(221.90,307.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (221.90,305.16) --
+	(221.90,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.13,109.14) --
+	(214.13,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.13,111.94) --
+	(213.34,111.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (213.34,109.14) --
+	(213.34,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (225.68,277.16) --
+	(225.68,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (225.68,279.96) --
+	(215.81,279.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (215.81,277.16) --
+	(215.81,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (221.01,249.16) --
+	(221.01,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (221.01,251.96) --
+	(216.23,251.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (216.23,249.16) --
+	(216.23,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.02,193.15) --
+	(214.02,198.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.02,195.95) --
+	(211.82,195.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (211.82,193.15) --
+	(211.82,198.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.76,165.15) --
+	(214.76,170.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.76,167.95) --
+	(212.34,167.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (212.34,165.15) --
+	(212.34,170.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (234.56, 81.14) --
+	(234.56, 86.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (234.56, 83.94) --
+	(228.52, 83.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (228.52, 81.14) --
+	(228.52, 86.74);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (216.62,139.95) circle (  3.57);
-
-\path[fill=fillColor] (213.84,447.98) circle (  3.57);
-
-\path[fill=fillColor] (214.16,419.98) circle (  3.57);
-
-\path[fill=fillColor] (211.32,391.97) circle (  1.43);
-
-\path[fill=fillColor] (220.80,363.97) circle (  3.57);
-
-\path[fill=fillColor] (218.39,335.97) circle (  3.57);
-
-\path[fill=fillColor] (225.62,307.96) circle (  3.57);
-
-\path[fill=fillColor] (212.77,111.94) circle (  3.57);
-
-\path[fill=fillColor] (219.89,279.96) circle (  3.57);
-
-\path[fill=fillColor] (217.70,251.96) circle (  3.57);
-
-\path[fill=fillColor] (211.91,195.95) circle (  3.57);
-
-\path[fill=fillColor] (212.55,167.95) circle (  3.57);
-
-\path[fill=fillColor] (230.93, 83.94) circle (  3.57);
+\path[fill=fillColor] (217.54,139.95) circle (  3.57);
+
+\path[fill=fillColor] (214.81,447.98) circle (  3.57);
+
+\path[fill=fillColor] (215.13,419.98) circle (  3.57);
+
+\path[fill=fillColor] (212.34,391.97) circle (  1.43);
+
+\path[fill=fillColor] (221.64,363.97) circle (  3.57);
+
+\path[fill=fillColor] (219.28,335.97) circle (  3.57);
+
+\path[fill=fillColor] (226.37,307.96) circle (  3.57);
+
+\path[fill=fillColor] (213.76,111.94) circle (  3.57);
+
+\path[fill=fillColor] (220.75,279.96) circle (  3.57);
+
+\path[fill=fillColor] (218.59,251.96) circle (  3.57);
+
+\path[fill=fillColor] (212.92,195.95) circle (  3.57);
+
+\path[fill=fillColor] (213.55,167.95) circle (  3.57);
+
+\path[fill=fillColor] (231.57, 83.94) circle (  3.57);
 \definecolor{drawColor}{RGB}{169,169,169}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (281.01, 67.14) --
-	(281.01,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (294.40, 67.14) --
-	(294.40,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (307.80, 67.14) --
-	(307.80,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (321.19, 67.14) --
-	(321.19,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (281.93, 67.14) --
+	(281.93,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (295.06, 67.14) --
+	(295.06,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (308.19, 67.14) --
+	(308.19,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (321.32, 67.14) --
+	(321.32,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (274.31, 67.14) --
-	(274.31,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (287.71, 67.14) --
-	(287.71,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (301.10, 67.14) --
-	(301.10,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (314.50, 67.14) --
-	(314.50,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (275.36, 67.14) --
+	(275.36,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (288.49, 67.14) --
+	(288.49,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (301.63, 67.14) --
+	(301.63,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (314.76, 67.14) --
+	(314.76,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (287.55,137.15) --
-	(287.55,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (287.55,139.95) --
-	(281.70,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (281.70,137.15) --
-	(281.70,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (287.06,445.18) --
-	(287.06,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (287.06,447.98) --
-	(282.40,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (282.40,445.18) --
-	(282.40,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (282.08,417.18) --
-	(282.08,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (282.08,419.98) --
-	(277.47,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (277.47,417.18) --
-	(277.47,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (296.17,389.17) --
-	(296.17,394.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (296.17,391.97) --
-	(284.28,391.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (284.28,389.17) --
-	(284.28,394.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (288.88,361.17) --
-	(288.88,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (288.88,363.97) --
-	(276.03,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (276.03,361.17) --
-	(276.03,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.79,333.17) --
-	(280.79,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.79,335.97) --
-	(277.74,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (277.74,333.17) --
-	(277.74,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (292.53,305.16) --
-	(292.53,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (292.53,307.96) --
-	(283.96,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (283.96,305.16) --
-	(283.96,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (290.97,109.14) --
-	(290.97,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (290.97,111.94) --
-	(289.37,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (289.37,109.14) --
-	(289.37,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (291.13,277.16) --
-	(291.13,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (291.13,279.96) --
-	(280.53,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.53,277.16) --
-	(280.53,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.15,249.16) --
-	(280.15,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.15,251.96) --
-	(276.56,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (276.56,249.16) --
-	(276.56,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (286.47,221.16) --
-	(286.47,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (286.47,223.96) --
-	(280.69,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.69,221.16) --
-	(280.69,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (289.96,193.15) --
-	(289.96,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (289.96,195.95) --
-	(284.60,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (284.60,193.15) --
-	(284.60,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (293.71,165.15) --
-	(293.71,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (293.71,167.95) --
-	(288.19,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (288.19,165.15) --
-	(288.19,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (302.49, 81.14) --
-	(302.49, 86.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (302.49, 83.94) --
-	(296.28, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (296.28, 81.14) --
-	(296.28, 86.74);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (288.34,137.15) --
+	(288.34,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (288.34,139.95) --
+	(282.61,139.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (282.61,137.15) --
+	(282.61,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (287.86,445.18) --
+	(287.86,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (287.86,447.98) --
+	(283.29,447.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (283.29,445.18) --
+	(283.29,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (282.98,417.18) --
+	(282.98,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (282.98,419.98) --
+	(278.46,419.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (278.46,417.18) --
+	(278.46,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.79,389.17) --
+	(296.79,394.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.79,391.97) --
+	(285.13,391.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (285.13,389.17) --
+	(285.13,394.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (289.65,361.17) --
+	(289.65,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (289.65,363.97) --
+	(277.04,363.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (277.04,361.17) --
+	(277.04,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (281.72,333.17) --
+	(281.72,338.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (281.72,335.97) --
+	(278.72,335.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (278.72,333.17) --
+	(278.72,338.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (293.22,305.16) --
+	(293.22,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (293.22,307.96) --
+	(284.82,307.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (284.82,305.16) --
+	(284.82,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (291.70,109.14) --
+	(291.70,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (291.70,111.94) --
+	(290.12,111.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (290.12,109.14) --
+	(290.12,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (291.86,277.16) --
+	(291.86,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (291.86,279.96) --
+	(281.45,279.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (281.45,277.16) --
+	(281.45,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (281.09,249.16) --
+	(281.09,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (281.09,251.96) --
+	(277.57,251.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (277.57,249.16) --
+	(277.57,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (287.29,221.16) --
+	(287.29,226.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (287.29,223.96) --
+	(281.61,223.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (281.61,221.16) --
+	(281.61,226.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (290.70,193.15) --
+	(290.70,198.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (290.70,195.95) --
+	(285.45,195.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (285.45,193.15) --
+	(285.45,198.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (294.38,165.15) --
+	(294.38,170.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (294.38,167.95) --
+	(288.97,167.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (288.97,165.15) --
+	(288.97,170.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (302.99, 81.14) --
+	(302.99, 86.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (302.99, 83.94) --
+	(296.90, 83.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.90, 81.14) --
+	(296.90, 86.74);
 \definecolor{fillColor}{RGB}{51,34,136}
 
-\path[fill=fillColor] (284.60,139.95) circle (  3.57);
-
-\path[fill=fillColor] (284.76,447.98) circle (  3.57);
-
-\path[fill=fillColor] (279.78,419.98) circle (  3.57);
-
-\path[fill=fillColor] (290.22,391.97) circle (  3.57);
-
-\path[fill=fillColor] (282.45,363.97) circle (  3.57);
-
-\path[fill=fillColor] (279.29,335.97) circle (  3.57);
-
-\path[fill=fillColor] (288.24,307.96) circle (  3.57);
-
-\path[fill=fillColor] (290.17,111.94) circle (  3.57);
-
-\path[fill=fillColor] (285.83,279.96) circle (  3.57);
-
-\path[fill=fillColor] (278.33,251.96) circle (  3.57);
-
-\path[fill=fillColor] (283.58,223.96) circle (  3.57);
-
-\path[fill=fillColor] (287.28,195.95) circle (  3.57);
-
-\path[fill=fillColor] (290.92,167.95) circle (  3.57);
-
-\path[fill=fillColor] (299.39, 83.94) circle (  3.57);
+\path[fill=fillColor] (285.45,139.95) circle (  3.57);
+
+\path[fill=fillColor] (285.60,447.98) circle (  3.57);
+
+\path[fill=fillColor] (280.72,419.98) circle (  3.57);
+
+\path[fill=fillColor] (290.96,391.97) circle (  3.57);
+
+\path[fill=fillColor] (283.35,363.97) circle (  3.57);
+
+\path[fill=fillColor] (280.25,335.97) circle (  3.57);
+
+\path[fill=fillColor] (289.02,307.96) circle (  3.57);
+
+\path[fill=fillColor] (290.91,111.94) circle (  3.57);
+
+\path[fill=fillColor] (286.66,279.96) circle (  3.57);
+
+\path[fill=fillColor] (279.30,251.96) circle (  3.57);
+
+\path[fill=fillColor] (284.45,223.96) circle (  3.57);
+
+\path[fill=fillColor] (288.07,195.95) circle (  3.57);
+
+\path[fill=fillColor] (291.65,167.95) circle (  3.57);
+
+\path[fill=fillColor] (299.95, 83.94) circle (  3.57);
 \definecolor{drawColor}{RGB}{169,169,169}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (345.45, 67.14) --
-	(345.45,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (358.84, 67.14) --
-	(358.84,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (372.24, 67.14) --
-	(372.24,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (385.63, 67.14) --
-	(385.63,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (346.37, 67.14) --
+	(346.37,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (359.50, 67.14) --
+	(359.50,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (372.63, 67.14) --
+	(372.63,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (385.76, 67.14) --
+	(385.76,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.75, 67.14) --
-	(338.75,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (352.14, 67.14) --
-	(352.14,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (365.54, 67.14) --
-	(365.54,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (378.93, 67.14) --
-	(378.93,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.80, 67.14) --
+	(339.80,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (352.93, 67.14) --
+	(352.93,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (366.06, 67.14) --
+	(366.06,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (379.20, 67.14) --
+	(379.20,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (346.73,137.15) --
-	(346.73,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (346.73,139.95) --
-	(340.03,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (340.03,137.15) --
-	(340.03,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (347.96,445.18) --
-	(347.96,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (347.96,447.98) --
-	(344.00,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.00,445.18) --
-	(344.00,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (341.05,417.18) --
-	(341.05,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (341.05,419.98) --
-	(338.91,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.91,417.18) --
-	(338.91,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (353.38,361.17) --
-	(353.38,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (353.38,363.97) --
-	(340.89,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (340.89,361.17) --
-	(340.89,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (355.52,305.16) --
-	(355.52,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (355.52,307.96) --
-	(345.61,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (345.61,305.16) --
-	(345.61,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (342.66,109.14) --
-	(342.66,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (342.66,111.94) --
-	(341.75,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (341.75,109.14) --
-	(341.75,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.86,277.16) --
-	(344.86,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.86,279.96) --
-	(338.80,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.80,277.16) --
-	(338.80,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (342.39,249.16) --
-	(342.39,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (342.39,251.96) --
-	(339.61,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (339.61,249.16) --
-	(339.61,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (340.46,193.15) --
-	(340.46,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (340.46,195.95) --
-	(338.86,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.86,193.15) --
-	(338.86,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (342.07,165.15) --
-	(342.07,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (342.07,167.95) --
-	(339.77,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (339.77,165.15) --
-	(339.77,170.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (347.63,137.15) --
+	(347.63,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (347.63,139.95) --
+	(341.06,139.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (341.06,137.15) --
+	(341.06,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.83,445.18) --
+	(348.83,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.83,447.98) --
+	(344.95,447.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (344.95,445.18) --
+	(344.95,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.06,417.18) --
+	(342.06,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.06,419.98) --
+	(339.96,419.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.96,417.18) --
+	(339.96,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (354.14,361.17) --
+	(354.14,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (354.14,363.97) --
+	(341.90,363.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (341.90,361.17) --
+	(341.90,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (356.24,305.16) --
+	(356.24,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (356.24,307.96) --
+	(346.52,307.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (346.52,305.16) --
+	(346.52,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (343.63,109.14) --
+	(343.63,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (343.63,111.94) --
+	(342.74,111.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.74,109.14) --
+	(342.74,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (345.79,277.16) --
+	(345.79,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (345.79,279.96) --
+	(339.85,279.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.85,277.16) --
+	(339.85,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (343.37,249.16) --
+	(343.37,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (343.37,251.96) --
+	(340.64,251.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (340.64,249.16) --
+	(340.64,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (341.48,193.15) --
+	(341.48,198.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (341.48,195.95) --
+	(339.90,195.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.90,193.15) --
+	(339.90,198.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (343.06,165.15) --
+	(343.06,170.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (343.06,167.95) --
+	(340.80,167.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (340.80,165.15) --
+	(340.80,170.75);
 \definecolor{fillColor}{RGB}{170,68,153}
 
-\path[fill=fillColor] (343.41,139.95) circle (  3.57);
-
-\path[fill=fillColor] (345.98,447.98) circle (  3.57);
-
-\path[fill=fillColor] (339.98,419.98) circle (  1.43);
-
-\path[fill=fillColor] (347.16,363.97) circle (  3.57);
-
-\path[fill=fillColor] (350.59,307.96) circle (  3.57);
-
-\path[fill=fillColor] (342.18,111.94) circle (  3.57);
-
-\path[fill=fillColor] (341.86,279.96) circle (  1.43);
-
-\path[fill=fillColor] (341.00,251.96) circle (  3.57);
-
-\path[fill=fillColor] (339.66,195.95) circle (  1.43);
-
-\path[fill=fillColor] (340.95,167.95) circle (  3.57);
+\path[fill=fillColor] (344.37,139.95) circle (  3.57);
+
+\path[fill=fillColor] (346.89,447.98) circle (  3.57);
+
+\path[fill=fillColor] (341.01,419.98) circle (  1.43);
+
+\path[fill=fillColor] (348.05,363.97) circle (  3.57);
+
+\path[fill=fillColor] (351.41,307.96) circle (  3.57);
+
+\path[fill=fillColor] (343.16,111.94) circle (  3.57);
+
+\path[fill=fillColor] (342.85,279.96) circle (  1.43);
+
+\path[fill=fillColor] (342.01,251.96) circle (  3.57);
+
+\path[fill=fillColor] (340.69,195.95) circle (  1.43);
+
+\path[fill=fillColor] (341.95,167.95) circle (  3.57);
 \definecolor{drawColor}{RGB}{169,169,169}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (409.88, 67.14) --
-	(409.88,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (423.28, 67.14) --
-	(423.28,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (436.68, 67.14) --
-	(436.68,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (450.07, 67.14) --
-	(450.07,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (410.80, 67.14) --
+	(410.80,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (423.94, 67.14) --
+	(423.94,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (437.07, 67.14) --
+	(437.07,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (450.20, 67.14) --
+	(450.20,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (403.19, 67.14) --
-	(403.19,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (416.58, 67.14) --
-	(416.58,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (429.98, 67.14) --
-	(429.98,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (443.37, 67.14) --
-	(443.37,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.24, 67.14) --
+	(404.24,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (417.37, 67.14) --
+	(417.37,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (430.50, 67.14) --
+	(430.50,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (443.64, 67.14) --
+	(443.64,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (406.83,137.15) --
-	(406.83,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (406.83,139.95) --
-	(404.10,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.10,137.15) --
-	(404.10,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (406.19,445.18) --
-	(406.19,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (406.19,447.98) --
-	(403.99,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (403.99,445.18) --
-	(403.99,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.15,417.18) --
-	(404.15,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (408.87,361.17) --
-	(408.87,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (412.51,305.16) --
-	(412.51,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (412.51,307.96) --
-	(406.13,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (406.13,305.16) --
-	(406.13,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (405.49,109.14) --
-	(405.49,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (405.49,111.94) --
-	(404.85,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.85,109.14) --
-	(404.85,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (410.26,277.16) --
-	(410.26,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (410.26,279.96) --
-	(403.67,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (403.67,277.16) --
-	(403.67,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (405.97,249.16) --
-	(405.97,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (405.97,251.96) --
-	(403.62,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (403.62,249.16) --
-	(403.62,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (407.37,221.16) --
-	(407.37,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (407.37,223.96) --
-	(404.53,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.53,221.16) --
-	(404.53,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.90,193.15) --
-	(404.90,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.90,195.95) --
-	(403.29,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (403.29,193.15) --
-	(403.29,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.74,165.15) --
-	(404.74,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.74,167.95) --
-	(403.29,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (403.29,165.15) --
-	(403.29,170.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (407.81,137.15) --
+	(407.81,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (407.81,139.95) --
+	(405.13,139.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.13,137.15) --
+	(405.13,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (407.18,445.18) --
+	(407.18,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (407.18,447.98) --
+	(405.03,447.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.03,445.18) --
+	(405.03,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.18,417.18) --
+	(405.18,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.18,419.98) --
+	(403.92,419.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (403.92,417.18) --
+	(403.92,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (409.81,361.17) --
+	(409.81,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (409.81,363.97) --
+	(403.24,363.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (403.24,361.17) --
+	(403.24,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (413.38,305.16) --
+	(413.38,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (413.38,307.96) --
+	(407.13,307.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (407.13,305.16) --
+	(407.13,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (406.50,109.14) --
+	(406.50,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (406.50,111.94) --
+	(405.87,111.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.87,109.14) --
+	(405.87,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (411.17,277.16) --
+	(411.17,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (411.17,279.96) --
+	(404.71,279.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.71,277.16) --
+	(404.71,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (406.97,249.16) --
+	(406.97,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (406.97,251.96) --
+	(404.66,251.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.66,249.16) --
+	(404.66,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (408.34,221.16) --
+	(408.34,226.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (408.34,223.96) --
+	(405.55,223.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.55,221.16) --
+	(405.55,226.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.92,193.15) --
+	(405.92,198.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.92,195.95) --
+	(404.34,195.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.34,193.15) --
+	(404.34,198.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.76,165.15) --
+	(405.76,170.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (405.76,167.95) --
+	(404.34,167.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.34,165.15) --
+	(404.34,170.75);
 \definecolor{fillColor}{RGB}{68,170,153}
 
-\path[fill=fillColor] (405.49,139.95) circle (  3.57);
-
-\path[fill=fillColor] (405.06,447.98) circle (  3.57);
-
-\path[fill=fillColor] (403.51,419.98) circle (  1.43);
-
-\path[fill=fillColor] (405.54,363.97) circle (  1.43);
-
-\path[fill=fillColor] (409.35,307.96) circle (  3.57);
-
-\path[fill=fillColor] (405.17,111.94) circle (  3.57);
-
-\path[fill=fillColor] (406.94,279.96) circle (  1.43);
-
-\path[fill=fillColor] (404.79,251.96) circle (  3.57);
-
-\path[fill=fillColor] (405.92,223.96) circle (  3.57);
-
-\path[fill=fillColor] (404.10,195.95) circle (  1.43);
-
-\path[fill=fillColor] (404.04,167.95) circle (  3.57);
+\path[fill=fillColor] (406.50,139.95) circle (  3.57);
+
+\path[fill=fillColor] (406.08,447.98) circle (  3.57);
+
+\path[fill=fillColor] (404.55,419.98) circle (  1.43);
+
+\path[fill=fillColor] (406.55,363.97) circle (  1.43);
+
+\path[fill=fillColor] (410.28,307.96) circle (  3.57);
+
+\path[fill=fillColor] (406.18,111.94) circle (  3.57);
+
+\path[fill=fillColor] (407.92,279.96) circle (  1.43);
+
+\path[fill=fillColor] (405.81,251.96) circle (  3.57);
+
+\path[fill=fillColor] (406.92,223.96) circle (  3.57);
+
+\path[fill=fillColor] (405.13,195.95) circle (  1.43);
+
+\path[fill=fillColor] (405.08,167.95) circle (  3.57);
 \definecolor{drawColor}{RGB}{169,169,169}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (474.32, 67.14) --
-	(474.32,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (487.72, 67.14) --
-	(487.72,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (501.11, 67.14) --
-	(501.11,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (514.51, 67.14) --
-	(514.51,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (475.24, 67.14) --
+	(475.24,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (488.37, 67.14) --
+	(488.37,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (501.51, 67.14) --
+	(501.51,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (514.64, 67.14) --
+	(514.64,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (467.63, 67.14) --
-	(467.63,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (481.02, 67.14) --
-	(481.02,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (494.42, 67.14) --
-	(494.42,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (507.81, 67.14) --
-	(507.81,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (468.68, 67.14) --
+	(468.68,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (481.81, 67.14) --
+	(481.81,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (494.94, 67.14) --
+	(494.94,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (508.07, 67.14) --
+	(508.07,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (469.39,137.15) --
-	(469.39,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (469.13,445.18) --
-	(469.13,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (469.13,447.98) --
-	(467.73,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (467.73,445.18) --
-	(467.73,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (468.32,417.18) --
-	(468.32,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (470.57,361.17) --
-	(470.57,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (468.00,333.17) --
-	(468.00,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (473.63,109.14) --
-	(473.63,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (473.63,111.94) --
-	(472.56,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (472.56,109.14) --
-	(472.56,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (473.57,277.16) --
-	(473.57,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (473.57,279.96) --
-	(467.68,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (467.68,277.16) --
-	(467.68,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (468.80,249.16) --
-	(468.80,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (468.11,165.15) --
-	(468.11,170.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (470.41,137.15) --
+	(470.41,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (470.41,139.95) --
+	(468.57,139.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (468.57,137.15) --
+	(468.57,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (470.15,445.18) --
+	(470.15,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (470.15,447.98) --
+	(468.78,447.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (468.78,445.18) --
+	(468.78,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.36,417.18) --
+	(469.36,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.36,419.98) --
+	(468.47,419.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (468.47,417.18) --
+	(468.47,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (471.57,361.17) --
+	(471.57,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (471.57,363.97) --
+	(467.68,363.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (467.68,361.17) --
+	(467.68,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.04,333.17) --
+	(469.04,338.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.04,335.97) --
+	(468.57,335.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (468.57,333.17) --
+	(468.57,338.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (474.56,109.14) --
+	(474.56,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (474.56,111.94) --
+	(473.51,111.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (473.51,109.14) --
+	(473.51,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (474.51,277.16) --
+	(474.51,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (474.51,279.96) --
+	(468.73,279.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (468.73,277.16) --
+	(468.73,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.83,249.16) --
+	(469.83,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.83,251.96) --
+	(468.47,251.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (468.47,249.16) --
+	(468.47,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.15,165.15) --
+	(469.15,170.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.15,167.95) --
+	(468.52,167.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (468.52,165.15) --
+	(468.52,170.75);
 \definecolor{fillColor}{RGB}{153,153,51}
 
-\path[fill=fillColor] (468.43,139.95) circle (  3.57);
-
-\path[fill=fillColor] (468.43,447.98) circle (  1.43);
-
-\path[fill=fillColor] (467.84,419.98) circle (  1.43);
-
-\path[fill=fillColor] (468.59,363.97) circle (  1.43);
-
-\path[fill=fillColor] (467.73,335.97) circle (  1.43);
-
-\path[fill=fillColor] (473.09,111.94) circle (  3.57);
-
-\path[fill=fillColor] (470.63,279.96) circle (  1.43);
-
-\path[fill=fillColor] (468.11,251.96) circle (  1.43);
-
-\path[fill=fillColor] (467.79,167.95) circle (  1.43);
+\path[fill=fillColor] (469.46,139.95) circle (  3.57);
+
+\path[fill=fillColor] (469.46,447.98) circle (  1.43);
+
+\path[fill=fillColor] (468.89,419.98) circle (  1.43);
+
+\path[fill=fillColor] (469.62,363.97) circle (  1.43);
+
+\path[fill=fillColor] (468.78,335.97) circle (  1.43);
+
+\path[fill=fillColor] (474.03,111.94) circle (  3.57);
+
+\path[fill=fillColor] (471.62,279.96) circle (  1.43);
+
+\path[fill=fillColor] (469.15,251.96) circle (  1.43);
+
+\path[fill=fillColor] (468.83,167.95) circle (  1.43);
 \definecolor{drawColor}{RGB}{169,169,169}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (538.76, 67.14) --
-	(538.76,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (552.16, 67.14) --
-	(552.16,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (565.55, 67.14) --
-	(565.55,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (578.95, 67.14) --
-	(578.95,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (539.68, 67.14) --
+	(539.68,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (552.81, 67.14) --
+	(552.81,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (565.95, 67.14) --
+	(565.95,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (579.08, 67.14) --
+	(579.08,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (532.06, 67.14) --
-	(532.06,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (545.46, 67.14) --
-	(545.46,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (558.85, 67.14) --
-	(558.85,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (572.25, 67.14) --
-	(572.25,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.11, 67.14) --
+	(533.11,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (546.25, 67.14) --
+	(546.25,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (559.38, 67.14) --
+	(559.38,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (572.51, 67.14) --
+	(572.51,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (533.78,137.15) --
-	(533.78,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (533.08,445.18) --
-	(533.08,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (532.87,417.18) --
-	(532.87,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (532.81,109.14) --
-	(532.81,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (532.81,111.94) --
-	(532.44,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (532.44,109.14) --
-	(532.44,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (535.55,249.16) --
-	(535.55,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (535.55,251.96) --
-	(532.81,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (532.81,249.16) --
-	(532.81,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (533.24,193.15) --
-	(533.24,198.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (534.80,137.15) --
+	(534.80,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (534.80,139.95) --
+	(532.80,139.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (532.80,137.15) --
+	(532.80,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (534.11,445.18) --
+	(534.11,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (534.11,447.98) --
+	(533.06,447.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.06,445.18) --
+	(533.06,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.90,417.18) --
+	(533.90,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.90,419.98) --
+	(532.85,419.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (532.85,417.18) --
+	(532.85,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.85,109.14) --
+	(533.85,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.85,111.94) --
+	(533.48,111.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.48,109.14) --
+	(533.48,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (536.53,249.16) --
+	(536.53,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (536.53,251.96) --
+	(533.85,251.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.85,249.16) --
+	(533.85,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (534.27,193.15) --
+	(534.27,198.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (534.27,195.95) --
+	(533.06,195.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.06,193.15) --
+	(533.06,198.75);
 \definecolor{fillColor}{RGB}{136,34,85}
 
-\path[fill=fillColor] (532.76,139.95) circle (  3.57);
-
-\path[fill=fillColor] (532.55,447.98) circle (  1.43);
-
-\path[fill=fillColor] (532.33,419.98) circle (  1.43);
-
-\path[fill=fillColor] (532.60,111.94) circle (  3.57);
-
-\path[fill=fillColor] (534.21,251.96) circle (  3.57);
-
-\path[fill=fillColor] (532.60,195.95) circle (  1.43);
+\path[fill=fillColor] (533.80,139.95) circle (  3.57);
+
+\path[fill=fillColor] (533.59,447.98) circle (  1.43);
+
+\path[fill=fillColor] (533.38,419.98) circle (  1.43);
+
+\path[fill=fillColor] (533.64,111.94) circle (  3.57);
+
+\path[fill=fillColor] (535.22,251.96) circle (  3.57);
+
+\path[fill=fillColor] (533.64,195.95) circle (  1.43);
 \definecolor{drawColor}{RGB}{169,169,169}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (603.20, 67.14) --
-	(603.20,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (616.59, 67.14) --
-	(616.59,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (629.99, 67.14) --
-	(629.99,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (643.39, 67.14) --
-	(643.39,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (604.12, 67.14) --
+	(604.12,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (617.25, 67.14) --
+	(617.25,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (630.38, 67.14) --
+	(630.38,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (643.52, 67.14) --
+	(643.52,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (596.50, 67.14) --
-	(596.50,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (609.90, 67.14) --
-	(609.90,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (623.29, 67.14) --
-	(623.29,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (636.69, 67.14) --
-	(636.69,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (597.55, 67.14) --
+	(597.55,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (610.69, 67.14) --
+	(610.69,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (623.82, 67.14) --
+	(623.82,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (636.95, 67.14) --
+	(636.95,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (605.61,137.15) --
-	(605.61,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (605.61,139.95) --
-	(599.77,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (599.77,137.15) --
-	(599.77,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (608.34,445.18) --
-	(608.34,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (608.34,447.98) --
-	(603.84,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (603.84,445.18) --
-	(603.84,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (604.11,417.18) --
-	(604.11,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (604.11,419.98) --
-	(599.61,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (599.61,417.18) --
-	(599.61,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.36,361.17) --
-	(600.36,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.25,333.17) --
-	(600.25,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.25,335.97) --
-	(598.00,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (598.00,333.17) --
-	(598.00,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (606.90,305.16) --
-	(606.90,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (606.90,307.96) --
-	(600.31,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.31,305.16) --
-	(600.31,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (608.72,109.14) --
-	(608.72,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (608.72,111.94) --
-	(607.27,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (607.27,109.14) --
-	(607.27,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (613.17,277.16) --
-	(613.17,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (613.17,279.96) --
-	(602.66,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (602.66,277.16) --
-	(602.66,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (610.17,249.16) --
-	(610.17,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (610.17,251.96) --
-	(604.59,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (604.59,249.16) --
-	(604.59,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (599.56,221.16) --
-	(599.56,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (599.56,223.96) --
-	(597.20,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (597.20,221.16) --
-	(597.20,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (603.84,165.15) --
-	(603.84,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (603.84,167.95) --
-	(600.25,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.25,165.15) --
-	(600.25,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (601.16, 81.14) --
-	(601.16, 86.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (601.16, 83.94) --
-	(598.32, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (598.32, 81.14) --
-	(598.32, 86.74);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (606.48,137.15) --
+	(606.48,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (606.48,139.95) --
+	(600.76,139.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (600.76,137.15) --
+	(600.76,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (609.16,445.18) --
+	(609.16,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (609.16,447.98) --
+	(604.75,447.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (604.75,445.18) --
+	(604.75,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (605.01,417.18) --
+	(605.01,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (605.01,419.98) --
+	(600.60,419.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (600.60,417.18) --
+	(600.60,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (601.34,361.17) --
+	(601.34,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (601.34,363.97) --
+	(596.76,363.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (596.76,361.17) --
+	(596.76,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (601.23,333.17) --
+	(601.23,338.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (601.23,335.97) --
+	(599.02,335.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (599.02,333.17) --
+	(599.02,338.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (607.74,305.16) --
+	(607.74,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (607.74,307.96) --
+	(601.28,307.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (601.28,305.16) --
+	(601.28,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (609.53,109.14) --
+	(609.53,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (609.53,111.94) --
+	(608.11,111.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (608.11,109.14) --
+	(608.11,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (613.89,277.16) --
+	(613.89,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (613.89,279.96) --
+	(603.59,279.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (603.59,277.16) --
+	(603.59,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (610.95,249.16) --
+	(610.95,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (610.95,251.96) --
+	(605.48,251.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (605.48,249.16) --
+	(605.48,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (600.55,221.16) --
+	(600.55,226.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (600.55,223.96) --
+	(598.24,223.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.24,221.16) --
+	(598.24,226.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (604.75,165.15) --
+	(604.75,170.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (604.75,167.95) --
+	(601.23,167.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (601.23,165.15) --
+	(601.23,170.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (602.12, 81.14) --
+	(602.12, 86.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (602.12, 83.94) --
+	(599.34, 83.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (599.34, 81.14) --
+	(599.34, 86.74);
 \definecolor{fillColor}{RGB}{102,17,0}
 
-\path[fill=fillColor] (602.72,139.95) circle (  3.57);
-
-\path[fill=fillColor] (606.09,447.98) circle (  3.57);
-
-\path[fill=fillColor] (601.86,419.98) circle (  3.57);
-
-\path[fill=fillColor] (598.00,363.97) circle (  1.43);
-
-\path[fill=fillColor] (599.13,335.97) circle (  3.57);
-
-\path[fill=fillColor] (603.57,307.96) circle (  3.57);
-
-\path[fill=fillColor] (607.97,111.94) circle (  3.57);
-
-\path[fill=fillColor] (607.91,279.96) circle (  3.57);
-
-\path[fill=fillColor] (607.38,251.96) circle (  3.57);
-
-\path[fill=fillColor] (598.38,223.96) circle (  3.57);
-
-\path[fill=fillColor] (602.02,167.95) circle (  3.57);
-
-\path[fill=fillColor] (599.72, 83.94) circle (  3.57);
+\path[fill=fillColor] (603.65,139.95) circle (  3.57);
+
+\path[fill=fillColor] (606.96,447.98) circle (  3.57);
+
+\path[fill=fillColor] (602.81,419.98) circle (  3.57);
+
+\path[fill=fillColor] (599.02,363.97) circle (  1.43);
+
+\path[fill=fillColor] (600.13,335.97) circle (  3.57);
+
+\path[fill=fillColor] (604.49,307.96) circle (  3.57);
+
+\path[fill=fillColor] (608.79,111.94) circle (  3.57);
+
+\path[fill=fillColor] (608.74,279.96) circle (  3.57);
+
+\path[fill=fillColor] (608.22,251.96) circle (  3.57);
+
+\path[fill=fillColor] (599.39,223.96) circle (  3.57);
+
+\path[fill=fillColor] (602.96,167.95) circle (  3.57);
+
+\path[fill=fillColor] (600.70, 83.94) circle (  3.57);
 \definecolor{drawColor}{RGB}{169,169,169}
@@
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (667.64, 67.14) --
-	(667.64,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (681.03, 67.14) --
-	(681.03,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (694.43, 67.14) --
-	(694.43,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (707.82, 67.14) --
-	(707.82,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (668.56, 67.14) --
+	(668.56,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (681.69, 67.14) --
+	(681.69,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (694.82, 67.14) --
+	(694.82,464.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (707.95, 67.14) --
+	(707.95,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (660.94, 67.14) --
-	(660.94,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (674.34, 67.14) --
-	(674.34,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (687.73, 67.14) --
-	(687.73,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (701.13, 67.14) --
-	(701.13,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (661.99, 67.14) --
+	(661.99,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (675.12, 67.14) --
+	(675.12,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (688.26, 67.14) --
+	(688.26,464.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (701.39, 67.14) --
+	(701.39,464.78);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (673.64,137.15) --
-	(673.64,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (673.64,139.95) --
-	(666.83,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (666.83,137.15) --
-	(666.83,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (667.26,445.18) --
-	(667.26,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (667.26,447.98) --
-	(663.94,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (663.94,445.18) --
-	(663.94,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (681.41,417.18) --
-	(681.41,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (681.41,419.98) --
-	(674.39,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (674.39,417.18) --
-	(674.39,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (677.55,389.17) --
-	(677.55,394.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (677.55,391.97) --
-	(667.48,391.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (667.48,389.17) --
-	(667.48,394.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (673.53,361.17) --
-	(673.53,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (673.53,363.97) --
-	(661.37,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (661.37,361.17) --
-	(661.37,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (677.60,333.17) --
-	(677.60,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (677.60,335.97) --
-	(673.00,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (673.00,333.17) --
-	(673.00,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (676.37,305.16) --
-	(676.37,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (676.37,307.96) --
-	(666.51,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (666.51,305.16) --
-	(666.51,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (664.05,109.14) --
-	(664.05,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (664.05,111.94) --
-	(663.30,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (663.30,109.14) --
-	(663.30,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (680.39,277.16) --
-	(680.39,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (680.39,279.96) --
-	(669.14,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (669.14,277.16) --
-	(669.14,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (665.60,249.16) --
-	(665.60,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (665.60,251.96) --
-	(662.44,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (662.44,249.16) --
-	(662.44,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (677.18,221.16) --
-	(677.18,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (677.18,223.96) --
-	(671.28,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (671.28,221.16) --
-	(671.28,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (666.83,193.15) --
-	(666.83,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (666.83,195.95) --
-	(663.57,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (663.57,193.15) --
-	(663.57,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (665.50,165.15) --
-	(665.50,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (665.50,167.95) --
-	(662.76,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (662.76,165.15) --
-	(662.76,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.36, 81.14) --
-	(690.36, 86.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.36, 83.94) --
-	(684.14, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (684.14, 81.14) --
-	(684.14, 86.74);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (674.44,137.15) --
+	(674.44,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (674.44,139.95) --
+	(667.77,139.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (667.77,137.15) --
+	(667.77,142.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (668.19,445.18) --
+	(668.19,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (668.19,447.98) --
+	(664.93,447.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (664.93,445.18) --
+	(664.93,450.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (682.06,417.18) --
+	(682.06,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (682.06,419.98) --
+	(675.18,419.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (675.18,417.18) --
+	(675.18,422.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (678.28,389.17) --
+	(678.28,394.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (678.28,391.97) --
+	(668.40,391.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (668.40,389.17) --
+	(668.40,394.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (674.34,361.17) --
+	(674.34,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (674.34,363.97) --
+	(662.41,363.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (662.41,361.17) --
+	(662.41,366.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (678.33,333.17) --
+	(678.33,338.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (678.33,335.97) --
+	(673.81,335.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (673.81,333.17) --
+	(673.81,338.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (677.12,305.16) --
+	(677.12,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (677.12,307.96) --
+	(667.45,307.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (667.45,305.16) --
+	(667.45,310.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (665.04,109.14) --
+	(665.04,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (665.04,111.94) --
+	(664.30,111.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (664.30,109.14) --
+	(664.30,114.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (681.06,277.16) --
+	(681.06,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (681.06,279.96) --
+	(670.03,279.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (670.03,277.16) --
+	(670.03,282.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (666.56,249.16) --
+	(666.56,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (666.56,251.96) --
+	(663.46,251.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (663.46,249.16) --
+	(663.46,254.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (677.91,221.16) --
+	(677.91,226.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (677.91,223.96) --
+	(672.13,223.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (672.13,221.16) --
+	(672.13,226.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (667.77,193.15) --
+	(667.77,198.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (667.77,195.95) --
+	(664.57,195.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (664.57,193.15) --
+	(664.57,198.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (666.46,165.15) --
+	(666.46,170.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (666.46,167.95) --
+	(663.78,167.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (663.78,165.15) --
+	(663.78,170.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (690.83, 81.14) --
+	(690.83, 86.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (690.83, 83.94) --
+	(684.74, 83.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (684.74, 81.14) --
+	(684.74, 86.74);
 \definecolor{fillColor}{RGB}{102,153,204}
 
-\path[fill=fillColor] (670.21,139.95) circle (  3.57);
-
-\path[fill=fillColor] (665.60,447.98) circle (  3.57);
-
-\path[fill=fillColor] (677.87,419.98) circle (  3.57);
-
-\path[fill=fillColor] (672.51,391.97) circle (  3.57);
-
-\path[fill=fillColor] (667.42,363.97) circle (  3.57);
-
-\path[fill=fillColor] (675.30,335.97) circle (  3.57);
-
-\path[fill=fillColor] (671.44,307.96) circle (  3.57);
-
-\path[fill=fillColor] (663.67,111.94) circle (  3.57);
-
-\path[fill=fillColor] (674.76,279.96) circle (  3.57);
-
-\path[fill=fillColor] (663.99,251.96) circle (  3.57);
-
-\path[fill=fillColor] (674.23,223.96) circle (  3.57);
-
-\path[fill=fillColor] (665.23,195.95) circle (  3.57);
-
-\path[fill=fillColor] (664.16,167.95) circle (  3.57);
-
-\path[fill=fillColor] (687.25, 83.94) circle (  3.57);
+\path[fill=fillColor] (671.08,139.95) circle (  3.57);
+
+\path[fill=fillColor] (666.56,447.98) circle (  3.57);
+
+\path[fill=fillColor] (678.59,419.98) circle (  3.57);
+
+\path[fill=fillColor] (673.34,391.97) circle (  3.57);
+
+\path[fill=fillColor] (668.35,363.97) circle (  3.57);
+
+\path[fill=fillColor] (676.07,335.97) circle (  3.57);
+
+\path[fill=fillColor] (672.29,307.96) circle (  3.57);
+
+\path[fill=fillColor] (664.67,111.94) circle (  3.57);
+
+\path[fill=fillColor] (675.54,279.96) circle (  3.57);
+
+\path[fill=fillColor] (664.99,251.96) circle (  3.57);
+
+\path[fill=fillColor] (675.02,223.96) circle (  3.57);
+
+\path[fill=fillColor] (666.19,195.95) circle (  3.57);
+
+\path[fill=fillColor] (665.14,167.95) circle (  3.57);
+
+\path[fill=fillColor] (687.78, 83.94) circle (  3.57);
 \definecolor{drawColor}{RGB}{169,169,169}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.00, 64.39) --
-	( 81.00, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.39, 64.39) --
-	( 94.39, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (107.79, 64.39) --
-	(107.79, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (121.18, 64.39) --
-	(121.18, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 82.05, 64.39) --
+	( 82.05, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.18, 64.39) --
+	( 95.18, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (108.31, 64.39) --
+	(108.31, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (121.44, 64.39) --
+	(121.44, 67.14);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 81.00, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 94.39, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (107.79, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (121.18, 56.13) {75};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 82.05, 56.13) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 95.18, 56.13) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (108.31, 56.13) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (121.44, 56.13) {75};
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (145.43, 64.39) --
-	(145.43, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (158.83, 64.39) --
-	(158.83, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (172.22, 64.39) --
-	(172.22, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (185.62, 64.39) --
-	(185.62, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (146.48, 64.39) --
+	(146.48, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.62, 64.39) --
+	(159.62, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (172.75, 64.39) --
+	(172.75, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (185.88, 64.39) --
+	(185.88, 67.14);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (145.43, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (158.83, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.22, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (185.62, 56.13) {75};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (146.48, 56.13) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (159.62, 56.13) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.75, 56.13) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (185.88, 56.13) {75};
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.87, 64.39) --
-	(209.87, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (223.27, 64.39) --
-	(223.27, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (236.66, 64.39) --
-	(236.66, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (250.06, 64.39) --
-	(250.06, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (210.92, 64.39) --
+	(210.92, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (224.06, 64.39) --
+	(224.06, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (237.19, 64.39) --
+	(237.19, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.32, 64.39) --
+	(250.32, 67.14);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (209.87, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (223.27, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (236.66, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (250.06, 56.13) {75};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (210.92, 56.13) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (224.06, 56.13) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (237.19, 56.13) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (250.32, 56.13) {75};
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (274.31, 64.39) --
-	(274.31, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (287.71, 64.39) --
-	(287.71, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (301.10, 64.39) --
-	(301.10, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (314.50, 64.39) --
-	(314.50, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (275.36, 64.39) --
+	(275.36, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (288.49, 64.39) --
+	(288.49, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (301.63, 64.39) --
+	(301.63, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (314.76, 64.39) --
+	(314.76, 67.14);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (274.31, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (287.71, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (301.10, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.50, 56.13) {75};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (275.36, 56.13) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (288.49, 56.13) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (301.63, 56.13) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.76, 56.13) {75};
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.75, 64.39) --
-	(338.75, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (352.14, 64.39) --
-	(352.14, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (365.54, 64.39) --
-	(365.54, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (378.93, 64.39) --
-	(378.93, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.80, 64.39) --
+	(339.80, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (352.93, 64.39) --
+	(352.93, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (366.06, 64.39) --
+	(366.06, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (379.20, 64.39) --
+	(379.20, 67.14);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (338.75, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (352.14, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (365.54, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (378.93, 56.13) {75};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (339.80, 56.13) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (352.93, 56.13) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (366.06, 56.13) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (379.20, 56.13) {75};
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (403.19, 64.39) --
-	(403.19, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (416.58, 64.39) --
-	(416.58, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (429.98, 64.39) --
-	(429.98, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (443.37, 64.39) --
-	(443.37, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.24, 64.39) --
+	(404.24, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (417.37, 64.39) --
+	(417.37, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (430.50, 64.39) --
+	(430.50, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (443.64, 64.39) --
+	(443.64, 67.14);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (403.19, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (416.58, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (429.98, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (443.37, 56.13) {75};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (404.24, 56.13) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (417.37, 56.13) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (430.50, 56.13) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (443.64, 56.13) {75};
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (467.63, 64.39) --
-	(467.63, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (481.02, 64.39) --
-	(481.02, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (494.42, 64.39) --
-	(494.42, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (507.81, 64.39) --
-	(507.81, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (468.68, 64.39) --
+	(468.68, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (481.81, 64.39) --
+	(481.81, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (494.94, 64.39) --
+	(494.94, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (508.07, 64.39) --
+	(508.07, 67.14);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (467.63, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (481.02, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (494.42, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (507.81, 56.13) {75};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (468.68, 56.13) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (481.81, 56.13) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (494.94, 56.13) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (508.07, 56.13) {75};
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (532.06, 64.39) --
-	(532.06, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (545.46, 64.39) --
-	(545.46, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (558.85, 64.39) --
-	(558.85, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (572.25, 64.39) --
-	(572.25, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (533.11, 64.39) --
+	(533.11, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (546.25, 64.39) --
+	(546.25, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (559.38, 64.39) --
+	(559.38, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (572.51, 64.39) --
+	(572.51, 67.14);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (532.06, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (545.46, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (558.85, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (572.25, 56.13) {75};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (533.11, 56.13) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (546.25, 56.13) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (559.38, 56.13) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (572.51, 56.13) {75};
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (596.50, 64.39) --
-	(596.50, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (609.90, 64.39) --
-	(609.90, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (623.29, 64.39) --
-	(623.29, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (636.69, 64.39) --
-	(636.69, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (597.55, 64.39) --
+	(597.55, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (610.69, 64.39) --
+	(610.69, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (623.82, 64.39) --
+	(623.82, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (636.95, 64.39) --
+	(636.95, 67.14);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (596.50, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (609.90, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (623.29, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (636.69, 56.13) {75};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (597.55, 56.13) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (610.69, 56.13) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (623.82, 56.13) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (636.95, 56.13) {75};
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (660.94, 64.39) --
-	(660.94, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (674.34, 64.39) --
-	(674.34, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (687.73, 64.39) --
-	(687.73, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (701.13, 64.39) --
-	(701.13, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (661.99, 64.39) --
+	(661.99, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (675.12, 64.39) --
+	(675.12, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (688.26, 64.39) --
+	(688.26, 67.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (701.39, 64.39) --
+	(701.39, 67.14);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (660.94, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (674.34, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (687.73, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (701.13, 56.13) {75};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (661.99, 56.13) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (675.12, 56.13) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (688.26, 56.13) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (701.39, 56.13) {75};
 

### 2021-05-04 paper_files/figure-latex/fig3paper-1.tex
drop drive calls
update
no google drive
paper
update files

@@
-% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:37
+% Created by tikzDevice version 0.12.3.1 on 2021-05-04 13:13:00
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 48.28,547.64) rectangle (371.71,627.77);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,547.64) rectangle (371.71,627.77);
+\path[clip] ( 48.28,541.57) rectangle (371.71,627.77);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 48.28,541.57) rectangle (371.71,627.77);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,560.96) --
-	(371.71,560.96);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,580.31) --
-	(371.71,580.31);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,599.67) --
-	(371.71,599.67);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,619.02) --
-	(371.71,619.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,551.28) --
-	(371.71,551.28);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,570.64) --
-	(371.71,570.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,589.99) --
-	(371.71,589.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,609.34) --
-	(371.71,609.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,547.64) --
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,556.45) --
+	(371.71,556.45);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,578.39) --
+	(371.71,578.39);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,600.33) --
+	(371.71,600.33);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,622.27) --
+	(371.71,622.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,545.48) --
+	(371.71,545.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,567.42) --
+	(371.71,567.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,589.36) --
+	(371.71,589.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,611.30) --
+	(371.71,611.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,541.57) --
 	( 75.24,627.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,547.64) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,541.57) --
 	(120.16,627.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,547.64) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,541.57) --
 	(165.08,627.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,547.64) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,541.57) --
 	(209.99,627.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,547.64) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,541.57) --
 	(254.91,627.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,547.64) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,541.57) --
 	(299.83,627.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,547.64) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,541.57) --
 	(344.75,627.77);
@@
 
-\path[fill=fillColor] (171.81,551.28) rectangle (185.29,565.53);
-
-\path[fill=fillColor] (261.65,551.28) rectangle (275.13,552.76);
-
-\path[fill=fillColor] (216.73,551.28) rectangle (230.21,552.68);
-
-\path[fill=fillColor] (306.57,551.28) rectangle (320.05,560.26);
-
-\path[fill=fillColor] (351.49,551.28) rectangle (364.97,552.60);
-
-\path[fill=fillColor] ( 81.97,551.28) rectangle ( 95.45,591.23);
-
-\path[fill=fillColor] (126.89,551.28) rectangle (140.37,561.27);
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[fill=fillColor] (158.34,551.28) rectangle (171.81,566.46);
-
-\path[fill=fillColor] (248.18,551.28) rectangle (261.65,552.83);
-
-\path[fill=fillColor] (203.26,551.28) rectangle (216.73,551.98);
-
-\path[fill=fillColor] (293.10,551.28) rectangle (306.57,555.00);
-
-\path[fill=fillColor] (338.02,551.28) rectangle (351.49,551.59);
-
-\path[fill=fillColor] ( 68.50,551.28) rectangle ( 81.97,595.49);
-
-\path[fill=fillColor] (113.42,551.28) rectangle (126.89,562.97);
-\definecolor{fillColor}{RGB}{204,102,119}
-
-\path[fill=fillColor] (144.86,551.28) rectangle (158.34,563.83);
-
-\path[fill=fillColor] (234.70,551.28) rectangle (248.18,552.52);
-
-\path[fill=fillColor] (189.78,551.28) rectangle (203.26,554.15);
-
-\path[fill=fillColor] (279.62,551.28) rectangle (293.10,570.72);
-
-\path[fill=fillColor] (324.54,551.28) rectangle (338.02,554.54);
-
-\path[fill=fillColor] ( 55.02,551.28) rectangle ( 68.50,582.79);
-
-\path[fill=fillColor] ( 99.94,551.28) rectangle (113.42,557.86);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,547.64) rectangle (371.71,627.77);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,462.01) rectangle (371.71,542.14);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,462.01) rectangle (371.71,542.14);
+\path[fill=fillColor] (144.86,545.48) rectangle (185.29,561.63);
+
+\path[fill=fillColor] (234.70,545.48) rectangle (275.13,547.15);
+
+\path[fill=fillColor] (189.78,545.48) rectangle (230.21,547.06);
+
+\path[fill=fillColor] (279.62,545.48) rectangle (320.05,555.66);
+
+\path[fill=fillColor] (324.54,545.48) rectangle (364.97,546.98);
+
+\path[fill=fillColor] ( 55.02,545.48) rectangle ( 95.45,590.77);
+
+\path[fill=fillColor] ( 99.94,545.48) rectangle (140.37,556.81);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,541.57) rectangle (371.71,627.77);
+\end{scope}
+\begin{scope}
+\path[clip] ( 48.28,449.86) rectangle (371.71,536.07);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 48.28,449.86) rectangle (371.71,536.07);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,475.33) --
-	(371.71,475.33);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,494.68) --
-	(371.71,494.68);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,514.04) --
-	(371.71,514.04);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,533.39) --
-	(371.71,533.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,465.65) --
-	(371.71,465.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,485.01) --
-	(371.71,485.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,504.36) --
-	(371.71,504.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,523.71) --
-	(371.71,523.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,462.01) --
-	( 75.24,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,462.01) --
-	(120.16,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,462.01) --
-	(165.08,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,462.01) --
-	(209.99,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,462.01) --
-	(254.91,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,462.01) --
-	(299.83,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,462.01) --
-	(344.75,542.14);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,464.75) --
+	(371.71,464.75);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,486.69) --
+	(371.71,486.69);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,508.63) --
+	(371.71,508.63);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,530.57) --
+	(371.71,530.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,453.78) --
+	(371.71,453.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,475.72) --
+	(371.71,475.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,497.66) --
+	(371.71,497.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,519.60) --
+	(371.71,519.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,449.86) --
+	( 75.24,536.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,449.86) --
+	(120.16,536.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,449.86) --
+	(165.08,536.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,449.86) --
+	(209.99,536.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,449.86) --
+	(254.91,536.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,449.86) --
+	(299.83,536.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,449.86) --
+	(344.75,536.07);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,465.65) rectangle (185.29,493.21);
-
-\path[fill=fillColor] (254.91,465.65) rectangle (275.13,465.96);
-
-\path[fill=fillColor] (216.73,465.65) rectangle (230.21,478.12);
-
-\path[fill=fillColor] (306.57,465.65) rectangle (320.05,466.04);
-
-\path[fill=fillColor] (351.49,465.65) rectangle (364.97,467.51);
-
-\path[fill=fillColor] ( 81.97,465.65) rectangle ( 95.45,499.87);
-
-\path[fill=fillColor] (126.89,465.65) rectangle (140.37,466.27);
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[fill=fillColor] (158.34,465.65) rectangle (171.81,493.68);
-
-\path[fill=fillColor] (234.70,465.65) rectangle (254.91,465.96);
-
-\path[fill=fillColor] (203.26,465.65) rectangle (216.73,478.12);
-
-\path[fill=fillColor] (293.10,465.65) rectangle (306.57,466.04);
-
-\path[fill=fillColor] (338.02,465.65) rectangle (351.49,466.66);
-
-\path[fill=fillColor] ( 68.50,465.65) rectangle ( 81.97,500.26);
-
-\path[fill=fillColor] (113.42,465.65) rectangle (126.89,466.20);
-\definecolor{fillColor}{RGB}{204,102,119}
-
-\path[fill=fillColor] (144.86,465.65) rectangle (158.34,480.13);
-
-\path[fill=fillColor] (189.78,465.65) rectangle (203.26,478.66);
-
-\path[fill=fillColor] (279.62,465.65) rectangle (293.10,466.43);
-
-\path[fill=fillColor] (324.54,465.65) rectangle (338.02,489.81);
-
-\path[fill=fillColor] ( 55.02,465.65) rectangle ( 68.50,489.03);
-
-\path[fill=fillColor] ( 99.94,465.65) rectangle (113.42,467.28);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,462.01) rectangle (371.71,542.14);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,376.38) rectangle (371.71,456.51);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,376.38) rectangle (371.71,456.51);
+\path[fill=fillColor] (144.86,453.78) rectangle (185.29,485.02);
+
+\path[fill=fillColor] (234.70,453.78) rectangle (275.13,454.13);
+
+\path[fill=fillColor] (189.78,453.78) rectangle (230.21,467.91);
+
+\path[fill=fillColor] (279.62,453.78) rectangle (320.05,454.22);
+
+\path[fill=fillColor] (324.54,453.78) rectangle (364.97,455.88);
+
+\path[fill=fillColor] ( 55.02,453.78) rectangle ( 95.45,492.57);
+
+\path[fill=fillColor] ( 99.94,453.78) rectangle (140.37,454.48);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,449.86) rectangle (371.71,536.07);
+\end{scope}
+\begin{scope}
+\path[clip] ( 48.28,358.15) rectangle (371.71,444.36);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 48.28,358.15) rectangle (371.71,444.36);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,389.70) --
-	(371.71,389.70);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,409.05) --
-	(371.71,409.05);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,428.41) --
-	(371.71,428.41);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,447.76) --
-	(371.71,447.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,380.02) --
-	(371.71,380.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,399.38) --
-	(371.71,399.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,418.73) --
-	(371.71,418.73);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,438.08) --
-	(371.71,438.08);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,376.38) --
-	( 75.24,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,376.38) --
-	(120.16,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,376.38) --
-	(165.08,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,376.38) --
-	(209.99,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,376.38) --
-	(254.91,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,376.38) --
-	(299.83,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,376.38) --
-	(344.75,456.51);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,373.04) --
+	(371.71,373.04);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,394.98) --
+	(371.71,394.98);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,416.92) --
+	(371.71,416.92);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,438.86) --
+	(371.71,438.86);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,362.07) --
+	(371.71,362.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,384.01) --
+	(371.71,384.01);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,405.95) --
+	(371.71,405.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,427.89) --
+	(371.71,427.89);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,358.15) --
+	( 75.24,444.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,358.15) --
+	(120.16,444.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,358.15) --
+	(165.08,444.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,358.15) --
+	(209.99,444.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,358.15) --
+	(254.91,444.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,358.15) --
+	(299.83,444.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,358.15) --
+	(344.75,444.36);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,380.02) rectangle (185.29,391.63);
-
-\path[fill=fillColor] (254.91,380.02) rectangle (275.13,380.49);
-
-\path[fill=fillColor] (216.73,380.02) rectangle (230.21,380.87);
-
-\path[fill=fillColor] (306.57,380.02) rectangle (320.05,405.72);
-
-\path[fill=fillColor] (351.49,380.02) rectangle (364.97,380.33);
-
-\path[fill=fillColor] ( 81.97,380.02) rectangle ( 95.45,397.83);
-
-\path[fill=fillColor] (126.89,380.02) rectangle (140.37,400.69);
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[fill=fillColor] (158.34,380.02) rectangle (171.81,391.71);
-
-\path[fill=fillColor] (234.70,380.02) rectangle (254.91,380.56);
-
-\path[fill=fillColor] (203.26,380.02) rectangle (216.73,380.80);
-
-\path[fill=fillColor] (293.10,380.02) rectangle (306.57,404.79);
-
-\path[fill=fillColor] (338.02,380.02) rectangle (351.49,380.10);
-
-\path[fill=fillColor] ( 68.50,380.02) rectangle ( 81.97,398.45);
-
-\path[fill=fillColor] (113.42,380.02) rectangle (126.89,401.23);
-\definecolor{fillColor}{RGB}{204,102,119}
-
-\path[fill=fillColor] (144.86,380.02) rectangle (158.34,389.93);
-
-\path[fill=fillColor] (189.78,380.02) rectangle (203.26,382.27);
-
-\path[fill=fillColor] (279.62,380.02) rectangle (293.10,421.21);
-
-\path[fill=fillColor] (324.54,380.02) rectangle (338.02,384.28);
-
-\path[fill=fillColor] ( 55.02,380.02) rectangle ( 68.50,387.84);
-
-\path[fill=fillColor] ( 99.94,380.02) rectangle (113.42,392.10);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,376.38) rectangle (371.71,456.51);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,290.75) rectangle (371.71,370.88);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,290.75) rectangle (371.71,370.88);
+\path[fill=fillColor] (144.86,362.07) rectangle (185.29,375.24);
+
+\path[fill=fillColor] (234.70,362.07) rectangle (275.13,362.60);
+
+\path[fill=fillColor] (189.78,362.07) rectangle (230.21,363.04);
+
+\path[fill=fillColor] (279.62,362.07) rectangle (320.05,391.21);
+
+\path[fill=fillColor] (324.54,362.07) rectangle (364.97,362.42);
+
+\path[fill=fillColor] ( 55.02,362.07) rectangle ( 95.45,382.26);
+
+\path[fill=fillColor] ( 99.94,362.07) rectangle (140.37,385.50);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,358.15) rectangle (371.71,444.36);
+\end{scope}
+\begin{scope}
+\path[clip] ( 48.28,266.45) rectangle (371.71,352.65);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 48.28,266.45) rectangle (371.71,352.65);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,304.07) --
-	(371.71,304.07);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,323.42) --
-	(371.71,323.42);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,342.78) --
-	(371.71,342.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,362.13) --
-	(371.71,362.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,294.39) --
-	(371.71,294.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,313.74) --
-	(371.71,313.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,333.10) --
-	(371.71,333.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,352.45) --
-	(371.71,352.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,290.75) --
-	( 75.24,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,290.75) --
-	(120.16,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,290.75) --
-	(165.08,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,290.75) --
-	(209.99,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,290.75) --
-	(254.91,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,290.75) --
-	(299.83,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,290.75) --
-	(344.75,370.88);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,281.33) --
+	(371.71,281.33);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,303.27) --
+	(371.71,303.27);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,325.21) --
+	(371.71,325.21);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,347.15) --
+	(371.71,347.15);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,270.36) --
+	(371.71,270.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,292.30) --
+	(371.71,292.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,314.24) --
+	(371.71,314.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,336.18) --
+	(371.71,336.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,266.45) --
+	( 75.24,352.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,266.45) --
+	(120.16,352.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,266.45) --
+	(165.08,352.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,266.45) --
+	(209.99,352.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,266.45) --
+	(254.91,352.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,266.45) --
+	(299.83,352.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,266.45) --
+	(344.75,352.65);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,294.39) rectangle (185.29,296.79);
-
-\path[fill=fillColor] (254.91,294.39) rectangle (275.13,294.39);
-
-\path[fill=fillColor] (216.73,294.39) rectangle (230.21,295.71);
-
-\path[fill=fillColor] (306.57,294.39) rectangle (320.05,298.88);
-
-\path[fill=fillColor] ( 81.97,294.39) rectangle ( 95.45,363.52);
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[fill=fillColor] (158.34,294.39) rectangle (171.81,296.71);
-
-\path[fill=fillColor] (234.70,294.39) rectangle (254.91,294.47);
-
-\path[fill=fillColor] (203.26,294.39) rectangle (216.73,295.09);
-
-\path[fill=fillColor] (293.10,294.39) rectangle (306.57,295.86);
-
-\path[fill=fillColor] ( 68.50,294.39) rectangle ( 81.97,367.24);
-\definecolor{fillColor}{RGB}{204,102,119}
-
-\path[fill=fillColor] (144.86,294.39) rectangle (158.34,297.41);
-
-\path[fill=fillColor] (189.78,294.39) rectangle (203.26,300.20);
-
-\path[fill=fillColor] (279.62,294.39) rectangle (293.10,320.63);
-
-\path[fill=fillColor] ( 55.02,294.39) rectangle ( 68.50,336.74);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,290.75) rectangle (371.71,370.88);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,205.12) rectangle (371.71,285.25);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,205.12) rectangle (371.71,285.25);
+\path[fill=fillColor] (144.86,270.36) rectangle (185.29,273.09);
+
+\path[fill=fillColor] (234.70,270.36) rectangle (275.13,270.36);
+
+\path[fill=fillColor] (189.78,270.36) rectangle (230.21,271.86);
+
+\path[fill=fillColor] (279.62,270.36) rectangle (320.05,275.46);
+
+\path[fill=fillColor] ( 55.02,270.36) rectangle ( 95.45,348.73);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,266.45) rectangle (371.71,352.65);
+\end{scope}
+\begin{scope}
+\path[clip] ( 48.28,174.74) rectangle (371.71,260.95);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 48.28,174.74) rectangle (371.71,260.95);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,218.44) --
-	(371.71,218.44);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,237.79) --
-	(371.71,237.79);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,257.14) --
-	(371.71,257.14);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,276.50) --
-	(371.71,276.50);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,208.76) --
-	(371.71,208.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,228.11) --
-	(371.71,228.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,247.47) --
-	(371.71,247.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,266.82) --
-	(371.71,266.82);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,205.12) --
-	( 75.24,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,205.12) --
-	(120.16,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,205.12) --
-	(165.08,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,205.12) --
-	(209.99,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,205.12) --
-	(254.91,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,205.12) --
-	(299.83,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,205.12) --
-	(344.75,285.25);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,189.63) --
+	(371.71,189.63);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,211.57) --
+	(371.71,211.57);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,233.51) --
+	(371.71,233.51);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,255.45) --
+	(371.71,255.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,178.66) --
+	(371.71,178.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,200.60) --
+	(371.71,200.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,222.54) --
+	(371.71,222.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,244.48) --
+	(371.71,244.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,174.74) --
+	( 75.24,260.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,174.74) --
+	(120.16,260.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,174.74) --
+	(165.08,260.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,174.74) --
+	(209.99,260.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,174.74) --
+	(254.91,260.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,174.74) --
+	(299.83,260.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,174.74) --
+	(344.75,260.95);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,208.76) rectangle (185.29,221.77);
-
-\path[fill=fillColor] (261.65,208.76) rectangle (275.13,209.92);
-
-\path[fill=fillColor] (216.73,208.76) rectangle (230.21,212.86);
-
-\path[fill=fillColor] (306.57,208.76) rectangle (320.05,216.97);
-
-\path[fill=fillColor] (351.49,208.76) rectangle (364.97,210.62);
-
-\path[fill=fillColor] ( 81.97,208.76) rectangle ( 95.45,246.00);
-
-\path[fill=fillColor] (126.89,208.76) rectangle (140.37,223.70);
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[fill=fillColor] (158.34,208.76) rectangle (171.81,221.77);
-
-\path[fill=fillColor] (248.18,208.76) rectangle (261.65,209.92);
-
-\path[fill=fillColor] (203.26,208.76) rectangle (216.73,212.24);
-
-\path[fill=fillColor] (293.10,208.76) rectangle (306.57,214.10);
-
-\path[fill=fillColor] (338.02,208.76) rectangle (351.49,209.69);
-
-\path[fill=fillColor] ( 68.50,208.76) rectangle ( 81.97,248.47);
-
-\path[fill=fillColor] (113.42,208.76) rectangle (126.89,225.48);
-\definecolor{fillColor}{RGB}{204,102,119}
-
-\path[fill=fillColor] (144.86,208.76) rectangle (158.34,220.53);
-
-\path[fill=fillColor] (234.70,208.76) rectangle (248.18,210.00);
-
-\path[fill=fillColor] (189.78,208.76) rectangle (203.26,215.50);
-
-\path[fill=fillColor] (279.62,208.76) rectangle (293.10,228.97);
-
-\path[fill=fillColor] (324.54,208.76) rectangle (338.02,216.42);
-
-\path[fill=fillColor] ( 55.02,208.76) rectangle ( 68.50,233.92);
-
-\path[fill=fillColor] ( 99.94,208.76) rectangle (113.42,217.12);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,205.12) rectangle (371.71,285.25);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,119.49) rectangle (371.71,199.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,119.49) rectangle (371.71,199.62);
+\path[fill=fillColor] (144.86,178.66) rectangle (185.29,193.40);
+
+\path[fill=fillColor] (234.70,178.66) rectangle (275.13,179.97);
+
+\path[fill=fillColor] (189.78,178.66) rectangle (230.21,183.31);
+
+\path[fill=fillColor] (279.62,178.66) rectangle (320.05,187.96);
+
+\path[fill=fillColor] (324.54,178.66) rectangle (364.97,180.76);
+
+\path[fill=fillColor] ( 55.02,178.66) rectangle ( 95.45,220.87);
+
+\path[fill=fillColor] ( 99.94,178.66) rectangle (140.37,195.60);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,174.74) rectangle (371.71,260.95);
+\end{scope}
+\begin{scope}
+\path[clip] ( 48.28, 83.03) rectangle (371.71,169.24);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 48.28, 83.03) rectangle (371.71,169.24);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,132.81) --
-	(371.71,132.81);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,152.16) --
-	(371.71,152.16);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,171.51) --
-	(371.71,171.51);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,190.87) --
-	(371.71,190.87);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,123.13) --
-	(371.71,123.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,142.48) --
-	(371.71,142.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,161.84) --
-	(371.71,161.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,181.19) --
-	(371.71,181.19);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,119.49) --
-	( 75.24,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,119.49) --
-	(120.16,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,119.49) --
-	(165.08,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,119.49) --
-	(209.99,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,119.49) --
-	(254.91,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,119.49) --
-	(299.83,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,119.49) --
-	(344.75,199.62);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28, 97.92) --
+	(371.71, 97.92);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,119.86) --
+	(371.71,119.86);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,141.80) --
+	(371.71,141.80);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,163.74) --
+	(371.71,163.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28, 86.95) --
+	(371.71, 86.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,108.89) --
+	(371.71,108.89);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,130.83) --
+	(371.71,130.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,152.77) --
+	(371.71,152.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24, 83.03) --
+	( 75.24,169.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16, 83.03) --
+	(120.16,169.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08, 83.03) --
+	(165.08,169.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99, 83.03) --
+	(209.99,169.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91, 83.03) --
+	(254.91,169.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83, 83.03) --
+	(299.83,169.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75, 83.03) --
+	(344.75,169.24);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,123.13) rectangle (185.29,132.03);
-
-\path[fill=fillColor] (216.73,123.13) rectangle (230.21,124.99);
-
-\path[fill=fillColor] (306.57,123.13) rectangle (320.05,140.08);
-
-\path[fill=fillColor] (344.75,123.13) rectangle (364.97,123.21);
-
-\path[fill=fillColor] ( 81.97,123.13) rectangle ( 95.45,149.84);
-
-\path[fill=fillColor] (126.89,123.13) rectangle (140.37,146.12);
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[fill=fillColor] (158.34,123.13) rectangle (171.81,129.86);
-
-\path[fill=fillColor] (203.26,123.13) rectangle (216.73,124.45);
-
-\path[fill=fillColor] (293.10,123.13) rectangle (306.57,137.53);
-
-\path[fill=fillColor] ( 68.50,123.13) rectangle ( 81.97,152.62);
-
-\path[fill=fillColor] (113.42,123.13) rectangle (126.89,148.68);
-\definecolor{fillColor}{RGB}{204,102,119}
-
-\path[fill=fillColor] (144.86,123.13) rectangle (158.34,137.61);
-
-\path[fill=fillColor] (189.78,123.13) rectangle (203.26,126.38);
-
-\path[fill=fillColor] (279.62,123.13) rectangle (293.10,146.59);
-
-\path[fill=fillColor] (324.54,123.13) rectangle (344.75,123.28);
-
-\path[fill=fillColor] ( 55.02,123.13) rectangle ( 68.50,142.72);
-
-\path[fill=fillColor] ( 99.94,123.13) rectangle (113.42,139.62);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,119.49) rectangle (371.71,199.62);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,547.64) rectangle (717.20,627.77);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (393.78,547.64) rectangle (717.20,627.77);
+\path[fill=fillColor] (144.86, 86.95) rectangle (185.29, 97.04);
+
+\path[fill=fillColor] (189.78, 86.95) rectangle (230.21, 89.06);
+
+\path[fill=fillColor] (279.62, 86.95) rectangle (320.05,106.17);
+
+\path[fill=fillColor] (324.54, 86.95) rectangle (364.97, 87.04);
+
+\path[fill=fillColor] ( 55.02, 86.95) rectangle ( 95.45,117.23);
+
+\path[fill=fillColor] ( 99.94, 86.95) rectangle (140.37,113.02);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28, 83.03) rectangle (371.71,169.24);
+\end{scope}
+\begin{scope}
+\path[clip] (393.78,541.57) rectangle (717.20,627.77);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (393.78,541.57) rectangle (717.20,627.77);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,560.96) --
-	(717.20,560.96);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,580.31) --
-	(717.20,580.31);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,599.67) --
-	(717.20,599.67);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,619.02) --
-	(717.20,619.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,551.28) --
-	(717.20,551.28);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,570.64) --
-	(717.20,570.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,589.99) --
-	(717.20,589.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,609.34) --
-	(717.20,609.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,547.64) --
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,556.45) --
+	(717.20,556.45);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,578.39) --
+	(717.20,578.39);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,600.33) --
+	(717.20,600.33);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,622.27) --
+	(717.20,622.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,545.48) --
+	(717.20,545.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,567.42) --
+	(717.20,567.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,589.36) --
+	(717.20,589.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,611.30) --
+	(717.20,611.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,541.57) --
 	(420.73,627.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,547.64) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,541.57) --
 	(465.65,627.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,547.64) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,541.57) --
 	(510.57,627.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,547.64) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,541.57) --
 	(555.49,627.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,547.64) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,541.57) --
 	(600.41,627.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,547.64) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,541.57) --
 	(645.33,627.77);
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,547.64) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,541.57) --
 	(690.25,627.77);
@@
 
-\path[fill=fillColor] (517.31,551.28) rectangle (530.78,579.62);
-
-\path[fill=fillColor] (607.15,551.28) rectangle (620.62,552.60);
-
-\path[fill=fillColor] (562.23,551.28) rectangle (575.70,552.68);
-
-\path[fill=fillColor] (696.99,551.28) rectangle (710.46,558.17);
-
-\path[fill=fillColor] (427.47,551.28) rectangle (440.94,581.71);
-
-\path[fill=fillColor] (472.39,551.28) rectangle (485.86,560.26);
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[fill=fillColor] (503.83,551.28) rectangle (517.31,579.85);
-
-\path[fill=fillColor] (593.67,551.28) rectangle (607.15,552.60);
-
-\path[fill=fillColor] (548.75,551.28) rectangle (562.23,551.98);
-
-\path[fill=fillColor] (683.51,551.28) rectangle (696.99,556.16);
-
-\path[fill=fillColor] (413.99,551.28) rectangle (427.47,583.33);
-
-\path[fill=fillColor] (458.91,551.28) rectangle (472.39,561.12);
-\definecolor{fillColor}{RGB}{204,102,119}
-
-\path[fill=fillColor] (490.36,551.28) rectangle (503.83,578.77);
-
-\path[fill=fillColor] (580.19,551.28) rectangle (593.67,552.37);
-
-\path[fill=fillColor] (535.27,551.28) rectangle (548.75,555.39);
-
-\path[fill=fillColor] (670.03,551.28) rectangle (683.51,565.84);
-
-\path[fill=fillColor] (400.52,551.28) rectangle (413.99,575.67);
-
-\path[fill=fillColor] (445.44,551.28) rectangle (458.91,557.17);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,547.64) rectangle (717.20,627.77);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,462.01) rectangle (717.20,542.14);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (393.78,462.01) rectangle (717.20,542.14);
+\path[fill=fillColor] (490.36,545.48) rectangle (530.78,577.60);
+
+\path[fill=fillColor] (580.19,545.48) rectangle (620.62,546.98);
+
+\path[fill=fillColor] (535.27,545.48) rectangle (575.70,547.06);
+
+\path[fill=fillColor] (670.03,545.48) rectangle (710.46,553.30);
+
+\path[fill=fillColor] (400.52,545.48) rectangle (440.94,579.97);
+
+\path[fill=fillColor] (445.44,545.48) rectangle (485.86,555.66);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,541.57) rectangle (717.20,627.77);
+\end{scope}
+\begin{scope}
+\path[clip] (393.78,449.86) rectangle (717.20,536.07);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (393.78,449.86) rectangle (717.20,536.07);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,475.33) --
-	(717.20,475.33);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,494.68) --
-	(717.20,494.68);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,514.04) --
-	(717.20,514.04);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,533.39) --
-	(717.20,533.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,465.65) --
-	(717.20,465.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,485.01) --
-	(717.20,485.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,504.36) --
-	(717.20,504.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,523.71) --
-	(717.20,523.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,462.01) --
-	(420.73,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,462.01) --
-	(465.65,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,462.01) --
-	(510.57,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,462.01) --
-	(555.49,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,462.01) --
-	(600.41,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,462.01) --
-	(645.33,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,462.01) --
-	(690.25,542.14);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,464.75) --
+	(717.20,464.75);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,486.69) --
+	(717.20,486.69);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,508.63) --
+	(717.20,508.63);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,530.57) --
+	(717.20,530.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,453.78) --
+	(717.20,453.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,475.72) --
+	(717.20,475.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,497.66) --
+	(717.20,497.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,519.60) --
+	(717.20,519.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,449.86) --
+	(420.73,536.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,449.86) --
+	(465.65,536.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,449.86) --
+	(510.57,536.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,449.86) --
+	(555.49,536.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,449.86) --
+	(600.41,536.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,449.86) --
+	(645.33,536.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,449.86) --
+	(690.25,536.07);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (517.31,465.65) rectangle (530.78,471.85);
-
-\path[fill=fillColor] (562.23,465.65) rectangle (575.70,471.85);
-
-\path[fill=fillColor] (652.07,465.65) rectangle (665.54,468.67);
-
-\path[fill=fillColor] (696.99,465.65) rectangle (710.46,468.90);
-
-\path[fill=fillColor] (427.47,465.65) rectangle (440.94,510.55);
-
-\path[fill=fillColor] (472.39,465.65) rectangle (485.86,479.59);
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[fill=fillColor] (503.83,465.65) rectangle (517.31,470.53);
-
-\path[fill=fillColor] (548.75,465.65) rectangle (562.23,469.60);
-
-\path[fill=fillColor] (638.59,465.65) rectangle (652.07,467.67);
-
-\path[fill=fillColor] (683.51,465.65) rectangle (696.99,466.12);
-
-\path[fill=fillColor] (413.99,465.65) rectangle (427.47,515.04);
-
-\path[fill=fillColor] (458.91,465.65) rectangle (472.39,482.37);
-\definecolor{fillColor}{RGB}{204,102,119}
-
-\path[fill=fillColor] (490.36,465.65) rectangle (503.83,476.41);
-
-\path[fill=fillColor] (535.27,465.65) rectangle (548.75,479.43);
-
-\path[fill=fillColor] (625.11,465.65) rectangle (638.59,472.23);
-
-\path[fill=fillColor] (670.03,465.65) rectangle (683.51,478.50);
-
-\path[fill=fillColor] (400.52,465.65) rectangle (413.99,494.76);
-
-\path[fill=fillColor] (445.44,465.65) rectangle (458.91,469.99);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,462.01) rectangle (717.20,542.14);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,376.38) rectangle (717.20,456.51);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (393.78,376.38) rectangle (717.20,456.51);
+\path[fill=fillColor] (490.36,453.78) rectangle (530.78,460.80);
+
+\path[fill=fillColor] (535.27,453.78) rectangle (575.70,460.80);
+
+\path[fill=fillColor] (625.11,453.78) rectangle (665.54,457.20);
+
+\path[fill=fillColor] (670.03,453.78) rectangle (710.46,457.46);
+
+\path[fill=fillColor] (400.52,453.78) rectangle (440.94,504.68);
+
+\path[fill=fillColor] (445.44,453.78) rectangle (485.86,469.57);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,449.86) rectangle (717.20,536.07);
+\end{scope}
+\begin{scope}
+\path[clip] (393.78,358.15) rectangle (717.20,444.36);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (393.78,358.15) rectangle (717.20,444.36);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,389.70) --
-	(717.20,389.70);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,409.05) --
-	(717.20,409.05);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,428.41) --
-	(717.20,428.41);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,447.76) --
-	(717.20,447.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,380.02) --
-	(717.20,380.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,399.38) --
-	(717.20,399.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,418.73) --
-	(717.20,418.73);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,438.08) --
-	(717.20,438.08);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,376.38) --
-	(420.73,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,376.38) --
-	(465.65,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,376.38) --
-	(510.57,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,376.38) --
-	(555.49,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,376.38) --
-	(600.41,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,376.38) --
-	(645.33,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,376.38) --
-	(690.25,456.51);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,373.04) --
+	(717.20,373.04);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,394.98) --
+	(717.20,394.98);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,416.92) --
+	(717.20,416.92);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,438.86) --
+	(717.20,438.86);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,362.07) --
+	(717.20,362.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,384.01) --
+	(717.20,384.01);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,405.95) --
+	(717.20,405.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,427.89) --
+	(717.20,427.89);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,358.15) --
+	(420.73,444.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,358.15) --
+	(465.65,444.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,358.15) --
+	(510.57,444.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,358.15) --
+	(555.49,444.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,358.15) --
+	(600.41,444.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,358.15) --
+	(645.33,444.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,358.15) --
+	(690.25,444.36);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (517.31,380.02) rectangle (530.78,386.53);
-
-\path[fill=fillColor] (607.15,380.02) rectangle (620.62,380.41);
-
-\path[fill=fillColor] (562.23,380.02) rectangle (575.70,383.66);
-
-\path[fill=fillColor] (652.07,380.02) rectangle (665.54,386.91);
-
-\path[fill=fillColor] (696.99,380.02) rectangle (710.46,380.87);
-
-\path[fill=fillColor] (427.47,380.02) rectangle (440.94,414.08);
-
-\path[fill=fillColor] (472.39,380.02) rectangle (485.86,405.18);
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[fill=fillColor] (503.83,380.02) rectangle (517.31,385.67);
-
-\path[fill=fillColor] (593.67,380.02) rectangle (607.15,380.41);
-
-\path[fill=fillColor] (548.75,380.02) rectangle (562.23,382.96);
-
-\path[fill=fillColor] (638.59,380.02) rectangle (652.07,382.42);
-
-\path[fill=fillColor] (683.51,380.02) rectangle (696.99,380.64);
-
-\path[fill=fillColor] (413.99,380.02) rectangle (427.47,416.87);
-
-\path[fill=fillColor] (458.91,380.02) rectangle (472.39,408.59);
-\definecolor{fillColor}{RGB}{204,102,119}
-
-\path[fill=fillColor] (490.36,380.02) rectangle (503.83,389.39);
-
-\path[fill=fillColor] (580.19,380.02) rectangle (593.67,380.41);
-
-\path[fill=fillColor] (535.27,380.02) rectangle (548.75,385.98);
-
-\path[fill=fillColor] (625.11,380.02) rectangle (638.59,402.78);
-
-\path[fill=fillColor] (670.03,380.02) rectangle (683.51,381.73);
-
-\path[fill=fillColor] (400.52,380.02) rectangle (413.99,404.10);
-
-\path[fill=fillColor] (445.44,380.02) rectangle (458.91,393.26);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,376.38) rectangle (717.20,456.51);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,290.75) rectangle (717.20,370.88);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (393.78,290.75) rectangle (717.20,370.88);
+\path[fill=fillColor] (490.36,362.07) rectangle (530.78,369.44);
+
+\path[fill=fillColor] (580.19,362.07) rectangle (620.62,362.51);
+
+\path[fill=fillColor] (535.27,362.07) rectangle (575.70,366.20);
+
+\path[fill=fillColor] (625.11,362.07) rectangle (665.54,369.88);
+
+\path[fill=fillColor] (670.03,362.07) rectangle (710.46,363.04);
+
+\path[fill=fillColor] (400.52,362.07) rectangle (440.94,400.69);
+
+\path[fill=fillColor] (445.44,362.07) rectangle (485.86,390.59);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,358.15) rectangle (717.20,444.36);
+\end{scope}
+\begin{scope}
+\path[clip] (393.78,266.45) rectangle (717.20,352.65);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (393.78,266.45) rectangle (717.20,352.65);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,304.07) --
-	(717.20,304.07);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,323.42) --
-	(717.20,323.42);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,342.78) --
-	(717.20,342.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,362.13) --
-	(717.20,362.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,294.39) --
-	(717.20,294.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,313.74) --
-	(717.20,313.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,333.10) --
-	(717.20,333.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,352.45) --
-	(717.20,352.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,290.75) --
-	(420.73,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,290.75) --
-	(465.65,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,290.75) --
-	(510.57,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,290.75) --
-	(555.49,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,290.75) --
-	(600.41,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,290.75) --
-	(645.33,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,290.75) --
-	(690.25,370.88);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,281.33) --
+	(717.20,281.33);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,303.27) --
+	(717.20,303.27);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,325.21) --
+	(717.20,325.21);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,347.15) --
+	(717.20,347.15);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,270.36) --
+	(717.20,270.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,292.30) --
+	(717.20,292.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,314.24) --
+	(717.20,314.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,336.18) --
+	(717.20,336.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,266.45) --
+	(420.73,352.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,266.45) --
+	(465.65,352.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,266.45) --
+	(510.57,352.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,266.45) --
+	(555.49,352.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,266.45) --
+	(600.41,352.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,266.45) --
+	(645.33,352.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,266.45) --
+	(690.25,352.65);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (517.31,294.39) rectangle (530.78,301.75);
-
-\path[fill=fillColor] (607.15,294.39) rectangle (620.62,298.73);
-
-\path[fill=fillColor] (562.23,294.39) rectangle (575.70,299.97);
-
-\path[fill=fillColor] (652.07,294.39) rectangle (665.54,302.29);
-
-\path[fill=fillColor] (690.25,294.39) rectangle (710.46,294.47);
-
-\path[fill=fillColor] (427.47,294.39) rectangle (440.94,321.49);
-
-\path[fill=fillColor] (472.39,294.39) rectangle (485.86,319.47);
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[fill=fillColor] (503.83,294.39) rectangle (517.31,301.98);
-
-\path[fill=fillColor] (593.67,294.39) rectangle (607.15,298.26);
-
-\path[fill=fillColor] (548.75,294.39) rectangle (562.23,299.81);
-
-\path[fill=fillColor] (638.59,294.39) rectangle (652.07,297.10);
-
-\path[fill=fillColor] (413.99,294.39) rectangle (427.47,324.04);
-
-\path[fill=fillColor] (458.91,294.39) rectangle (472.39,322.65);
-\definecolor{fillColor}{RGB}{204,102,119}
-
-\path[fill=fillColor] (490.36,294.39) rectangle (503.83,300.97);
-
-\path[fill=fillColor] (580.19,294.39) rectangle (593.67,300.20);
-
-\path[fill=fillColor] (535.27,294.39) rectangle (548.75,300.43);
-
-\path[fill=fillColor] (625.11,294.39) rectangle (638.59,319.16);
-
-\path[fill=fillColor] (670.03,294.39) rectangle (690.25,294.86);
-
-\path[fill=fillColor] (400.52,294.39) rectangle (413.99,313.36);
-
-\path[fill=fillColor] (445.44,294.39) rectangle (458.91,309.18);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,290.75) rectangle (717.20,370.88);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,205.12) rectangle (717.20,285.25);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (393.78,205.12) rectangle (717.20,285.25);
+\path[fill=fillColor] (490.36,270.36) rectangle (530.78,278.70);
+
+\path[fill=fillColor] (580.19,270.36) rectangle (620.62,275.28);
+
+\path[fill=fillColor] (535.27,270.36) rectangle (575.70,276.68);
+
+\path[fill=fillColor] (625.11,270.36) rectangle (665.54,279.32);
+
+\path[fill=fillColor] (670.03,270.36) rectangle (710.46,270.45);
+
+\path[fill=fillColor] (400.52,270.36) rectangle (440.94,301.08);
+
+\path[fill=fillColor] (445.44,270.36) rectangle (485.86,298.80);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,266.45) rectangle (717.20,352.65);
+\end{scope}
+\begin{scope}
+\path[clip] (393.78,174.74) rectangle (717.20,260.95);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (393.78,174.74) rectangle (717.20,260.95);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,218.44) --
-	(717.20,218.44);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,237.79) --
-	(717.20,237.79);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,257.14) --
-	(717.20,257.14);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,276.50) --
-	(717.20,276.50);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,208.76) --
-	(717.20,208.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,228.11) --
-	(717.20,228.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,247.47) --
-	(717.20,247.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,266.82) --
-	(717.20,266.82);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,205.12) --
-	(420.73,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,205.12) --
-	(465.65,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,205.12) --
-	(510.57,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,205.12) --
-	(555.49,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,205.12) --
-	(600.41,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,205.12) --
-	(645.33,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,205.12) --
-	(690.25,285.25);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,189.63) --
+	(717.20,189.63);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,211.57) --
+	(717.20,211.57);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,233.51) --
+	(717.20,233.51);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,255.45) --
+	(717.20,255.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,178.66) --
+	(717.20,178.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,200.60) --
+	(717.20,200.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,222.54) --
+	(717.20,222.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,244.48) --
+	(717.20,244.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,174.74) --
+	(420.73,260.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,174.74) --
+	(465.65,260.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,174.74) --
+	(510.57,260.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,174.74) --
+	(555.49,260.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,174.74) --
+	(600.41,260.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,174.74) --
+	(645.33,260.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,174.74) --
+	(690.25,260.95);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (517.31,208.76) rectangle (530.78,230.51);
-
-\path[fill=fillColor] (607.15,208.76) rectangle (620.62,212.55);
-
-\path[fill=fillColor] (562.23,208.76) rectangle (575.70,210.46);
-
-\path[fill=fillColor] (652.07,208.76) rectangle (665.54,221.61);
-
-\path[fill=fillColor] (427.47,208.76) rectangle (440.94,236.63);
-
-\path[fill=fillColor] (472.39,208.76) rectangle (485.86,218.28);
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[fill=fillColor] (503.83,208.76) rectangle (517.31,221.53);
-
-\path[fill=fillColor] (593.67,208.76) rectangle (607.15,211.93);
-
-\path[fill=fillColor] (548.75,208.76) rectangle (562.23,210.31);
-
-\path[fill=fillColor] (638.59,208.76) rectangle (652.07,213.25);
-
-\path[fill=fillColor] (413.99,208.76) rectangle (427.47,245.22);
-
-\path[fill=fillColor] (458.91,208.76) rectangle (472.39,227.65);
-\definecolor{fillColor}{RGB}{204,102,119}
-
-\path[fill=fillColor] (490.36,208.76) rectangle (503.83,234.38);
-
-\path[fill=fillColor] (580.19,208.76) rectangle (593.67,212.86);
-
-\path[fill=fillColor] (535.27,208.76) rectangle (548.75,210.46);
-
-\path[fill=fillColor] (625.11,208.76) rectangle (638.59,225.25);
-
-\path[fill=fillColor] (400.52,208.76) rectangle (413.99,232.84);
-
-\path[fill=fillColor] (445.44,208.76) rectangle (458.91,214.10);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,205.12) rectangle (717.20,285.25);
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,547.64) rectangle (393.78,627.77);
+\path[fill=fillColor] (490.36,178.66) rectangle (530.78,203.32);
+
+\path[fill=fillColor] (580.19,178.66) rectangle (620.62,182.96);
+
+\path[fill=fillColor] (535.27,178.66) rectangle (575.70,180.59);
+
+\path[fill=fillColor] (625.11,178.66) rectangle (665.54,193.23);
+
+\path[fill=fillColor] (400.52,178.66) rectangle (440.94,210.25);
+
+\path[fill=fillColor] (445.44,178.66) rectangle (485.86,189.45);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,174.74) rectangle (717.20,260.95);
+\end{scope}
+\begin{scope}
+\path[clip] (377.21,541.57) rectangle (393.78,627.77);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,547.64) rectangle (393.78,627.77);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,541.57) rectangle (393.78,627.77);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,587.71) {Colombia};
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,462.01) rectangle (393.78,542.14);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,584.67) {Colombia};
+\end{scope}
+\begin{scope}
+\path[clip] (377.21,449.86) rectangle (393.78,536.07);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,462.01) rectangle (393.78,542.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,449.86) rectangle (393.78,536.07);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,502.08) {Nigeria};
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,376.38) rectangle (393.78,456.51);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,492.96) {Nigeria};
+\end{scope}
+\begin{scope}
+\path[clip] (377.21,358.15) rectangle (393.78,444.36);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,376.38) rectangle (393.78,456.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,358.15) rectangle (393.78,444.36);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,416.45) {Sierra Leone 1};
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,290.75) rectangle (393.78,370.88);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,401.26) {Sierra Leone 1};
+\end{scope}
+\begin{scope}
+\path[clip] (377.21,266.45) rectangle (393.78,352.65);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,290.75) rectangle (393.78,370.88);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,266.45) rectangle (393.78,352.65);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,330.81) {Uganda 2};
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,205.12) rectangle (393.78,285.25);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,309.55) {Uganda 2};
+\end{scope}
+\begin{scope}
+\path[clip] (377.21,174.74) rectangle (393.78,260.95);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,205.12) rectangle (393.78,285.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,174.74) rectangle (393.78,260.95);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,245.18) {Russia};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,547.64) rectangle ( 48.28,627.77);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,217.84) {Russia};
+\end{scope}
+\begin{scope}
+\path[clip] ( 31.71,541.57) rectangle ( 48.28,627.77);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,547.64) rectangle ( 48.28,627.77);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,541.57) rectangle ( 48.28,627.77);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,587.71) {Burkina Faso};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,462.01) rectangle ( 48.28,542.14);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,584.67) {Burkina Faso};
+\end{scope}
+\begin{scope}
+\path[clip] ( 31.71,449.86) rectangle ( 48.28,536.07);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,462.01) rectangle ( 48.28,542.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,449.86) rectangle ( 48.28,536.07);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,502.08) {Nepal};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,376.38) rectangle ( 48.28,456.51);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,492.96) {Nepal};
+\end{scope}
+\begin{scope}
+\path[clip] ( 31.71,358.15) rectangle ( 48.28,444.36);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,376.38) rectangle ( 48.28,456.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,358.15) rectangle ( 48.28,444.36);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,416.45) {Rwanda};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,290.75) rectangle ( 48.28,370.88);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,401.26) {Rwanda};
+\end{scope}
+\begin{scope}
+\path[clip] ( 31.71,266.45) rectangle ( 48.28,352.65);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,290.75) rectangle ( 48.28,370.88);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,266.45) rectangle ( 48.28,352.65);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,330.81) {Sierra Leone 2};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,205.12) rectangle ( 48.28,285.25);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,309.55) {Sierra Leone 2};
+\end{scope}
+\begin{scope}
+\path[clip] ( 31.71,174.74) rectangle ( 48.28,260.95);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,205.12) rectangle ( 48.28,285.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,174.74) rectangle ( 48.28,260.95);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,245.18) {All LMICs};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,119.49) rectangle ( 48.28,199.62);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,217.84) {All LMICs};
+\end{scope}
+\begin{scope}
+\path[clip] ( 31.71, 83.03) rectangle ( 48.28,169.24);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,119.49) rectangle ( 48.28,199.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71, 83.03) rectangle ( 48.28,169.24);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,159.55) {USA};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,116.74) --
-	( 75.24,119.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,116.74) --
-	(120.16,119.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,116.74) --
-	(165.08,119.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,116.74) --
-	(209.99,119.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,116.74) --
-	(254.91,119.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,116.74) --
-	(299.83,119.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,116.74) --
-	(344.75,119.49);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,126.14) {USA};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24, 80.28) --
+	( 75.24, 83.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16, 80.28) --
+	(120.16, 83.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08, 80.28) --
+	(165.08, 83.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99, 80.28) --
+	(209.99, 83.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91, 80.28) --
+	(254.91, 83.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83, 80.28) --
+	(299.83, 83.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75, 80.28) --
+	(344.75, 83.03);
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 78.27,114.54) {Health workers};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (118.43,114.54) {Government or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (127.94,114.54) {MoH};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (163.35,114.54) {Family or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.86,114.54) {Friends};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (198.77,114.54) {Famous person,};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (208.27,114.54) {religious leader};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (217.78,114.54) {or traditional};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (227.28,114.54) {healers};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (248.44,114.54) {Newspapers,};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (257.95,114.54) {radio or online};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (267.45,114.54) {groups};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (302.86,114.54) {Other};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (343.03,114.54) {Don't know or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (352.54,114.54) {Refuse};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,202.37) --
-	(420.73,205.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,202.37) --
-	(465.65,205.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,202.37) --
-	(510.57,205.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,202.37) --
-	(555.49,205.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,202.37) --
-	(600.41,205.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,202.37) --
-	(645.33,205.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,202.37) --
-	(690.25,205.12);
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 78.27, 78.08) {Health workers};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (118.43, 78.08) {Government or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (127.94, 78.08) {MoH};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (163.35, 78.08) {Family or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.86, 78.08) {Friends};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (198.77, 78.08) {Famous person,};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (208.27, 78.08) {religious leader};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (217.78, 78.08) {or traditional};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (227.28, 78.08) {healers};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (248.44, 78.08) {Newspapers,};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (257.95, 78.08) {radio or online};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (267.45, 78.08) {groups};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (302.86, 78.08) {Other};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (343.03, 78.08) {Don't know or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (352.54, 78.08) {Refuse};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,171.99) --
+	(420.73,174.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,171.99) --
+	(465.65,174.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,171.99) --
+	(510.57,174.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,171.99) --
+	(555.49,174.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,171.99) --
+	(600.41,174.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,171.99) --
+	(645.33,174.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,171.99) --
+	(690.25,174.74);
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (423.76,200.17) {Health workers};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (463.93,200.17) {Government or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (473.43,200.17) {MoH};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (508.85,200.17) {Family or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (518.35,200.17) {Friends};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (544.26,200.17) {Famous person,};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (553.77,200.17) {religious leader};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (563.27,200.17) {or traditional};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (572.78,200.17) {healers};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (593.93,200.17) {Newspapers,};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (603.44,200.17) {radio or online};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (612.94,200.17) {groups};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (648.36,200.17) {Other};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (688.53,200.17) {Don't know or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (698.03,200.17) {Refuse};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (423.76,169.79) {Health workers};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (463.93,169.79) {Government or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (473.43,169.79) {MoH};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (508.85,169.79) {Family or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (518.35,169.79) {Friends};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (544.26,169.79) {Famous person,};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (553.77,169.79) {religious leader};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (563.27,169.79) {or traditional};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (572.78,169.79) {healers};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (593.93,169.79) {Newspapers,};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (603.44,169.79) {radio or online};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (612.94,169.79) {groups};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (648.36,169.79) {Other};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (688.53,169.79) {Don't know or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (698.03,169.79) {Refuse};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,548.25) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,567.61) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,586.96) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,606.31) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,551.28) --
-	( 31.71,551.28);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,570.64) --
-	( 31.71,570.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,589.99) --
-	( 31.71,589.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,609.34) --
-	( 31.71,609.34);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,542.45) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,564.39) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,586.33) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,608.27) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,545.48) --
+	( 31.71,545.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,567.42) --
+	( 31.71,567.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,589.36) --
+	( 31.71,589.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,611.30) --
+	( 31.71,611.30);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,462.62) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,481.98) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,501.33) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,520.68) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,465.65) --
-	( 31.71,465.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,485.01) --
-	( 31.71,485.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,504.36) --
-	( 31.71,504.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,523.71) --
-	( 31.71,523.71);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,450.75) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,472.69) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,494.63) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,516.57) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,453.78) --
+	( 31.71,453.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,475.72) --
+	( 31.71,475.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,497.66) --
+	( 31.71,497.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,519.60) --
+	( 31.71,519.60);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,376.99) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,396.35) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,415.70) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,435.05) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,380.02) --
-	( 31.71,380.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,399.38) --
-	( 31.71,399.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,418.73) --
-	( 31.71,418.73);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,438.08) --
-	( 31.71,438.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,359.04) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,380.98) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,402.92) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,424.86) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,362.07) --
+	( 31.71,362.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,384.01) --
+	( 31.71,384.01);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,405.95) --
+	( 31.71,405.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,427.89) --
+	( 31.71,427.89);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,291.36) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,310.71) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,330.07) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,349.42) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,294.39) --
-	( 31.71,294.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,313.74) --
-	( 31.71,313.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,333.10) --
-	( 31.71,333.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,352.45) --
-	( 31.71,352.45);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,267.33) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,289.27) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,311.21) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,333.15) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,270.36) --
+	( 31.71,270.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,292.30) --
+	( 31.71,292.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,314.24) --
+	( 31.71,314.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,336.18) --
+	( 31.71,336.18);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,205.73) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,225.08) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,244.44) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,263.79) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,208.76) --
-	( 31.71,208.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,228.11) --
-	( 31.71,228.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,247.47) --
-	( 31.71,247.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,266.82) --
-	( 31.71,266.82);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,175.63) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,197.57) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,219.51) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,241.45) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,178.66) --
+	( 31.71,178.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,200.60) --
+	( 31.71,200.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,222.54) --
+	( 31.71,222.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,244.48) --
+	( 31.71,244.48);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,120.10) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,139.45) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,158.81) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,178.16) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,123.13) --
-	( 31.71,123.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,142.48) --
-	( 31.71,142.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,161.84) --
-	( 31.71,161.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,181.19) --
-	( 31.71,181.19);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96, 83.92) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,105.86) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,127.80) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,149.74) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 86.95) --
+	( 31.71, 86.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,108.89) --
+	( 31.71,108.89);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,130.83) --
+	( 31.71,130.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,152.77) --
+	( 31.71,152.77);
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,373.63) {estimate};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (276.12,  5.50) rectangle (489.36, 30.95);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,355.40) {estimate};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (281.62, 14.44) {Answer};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (322.65, 11.00) rectangle (337.10, 25.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{204,102,119}
-
-\path[fill=fillColor] (323.36, 11.71) rectangle (336.39, 24.74);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (409.32, 11.00) rectangle (423.78, 25.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[fill=fillColor] (410.03, 11.71) rectangle (423.07, 24.74);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (448.02, 11.00) rectangle (462.48, 25.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[fill=fillColor] (448.73, 11.71) rectangle (461.77, 24.74);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (342.60, 15.20) {No, Don't know};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (429.28, 15.20) {Yes};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (467.98, 15.20) {Any};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{RGB}{0,0,0}
-
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  5.50,635.84) {Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine?};

### 2021-05-04 paper_files/figure-latex/genderhist-1.tex
drop drive calls
update
no google drive
paper
update files

@@
-% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:44
+% Created by tikzDevice version 0.12.3.1 on 2021-05-04 13:13:07
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  5.50,635.84) {If a COVID-19 vaccine becomes available in [country], would you take it?};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  5.50,635.84) {Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine?};
 \end{scope}

### 2021-05-04 paper_files/figure-latex/mainfigure1-1.tex
drop drive calls
update
no google drive
paper
update files

@@
-% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:22
+% Created by tikzDevice version 0.12.3.1 on 2021-05-04 13:12:45
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (251.38,434.77) --
-	(251.38,440.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (251.38,437.42) --
-	(247.47,437.42);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (247.47,434.77) --
-	(247.47,440.07);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (251.27,434.77) --
+	(251.27,440.07);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (251.27,437.42) --
+	(246.92,437.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (246.92,434.77) --
+	(246.92,440.07);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (249.43,437.42) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (249.10,437.42) circle (  1.96);
 
@@
 	(390.78,506.36);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (374.36,148.40) --
-	(374.36,151.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (374.36,149.72) --
-	(361.75,149.72);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (361.75,148.40) --
-	(361.75,151.05);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (377.73,140.44) --
-	(377.73,143.09);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (377.73,141.77) --
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (374.47,148.40) --
+	(374.47,151.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (374.47,149.72) --
+	(361.85,149.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (361.85,148.40) --
+	(361.85,151.05);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (377.62,140.44) --
+	(377.62,143.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (377.62,141.77) --
 	(366.20,141.77);
@@
 	(366.20,143.09);
-\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{drawColor}{RGB}{136,34,85}
 
@@
 	(343.26,495.76);
-\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{drawColor}{RGB}{153,153,51}
 
@@
 	(352.72,487.80);
-\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{drawColor}{RGB}{136,34,85}
 
@@
 	(358.27,469.24);
-\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{drawColor}{RGB}{153,153,51}
 
@@
 	(361.42,461.29);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (373.49,440.07) --
-	(373.49,442.72);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (373.49,441.40) --
-	(366.42,441.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (366.42,440.07) --
-	(366.42,442.72);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (377.19,432.12) --
-	(377.19,434.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (377.19,433.44) --
-	(373.05,433.44);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (373.05,432.12) --
-	(373.05,434.77);
-\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (375.34,440.07) --
+	(375.34,442.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (375.34,441.40) --
+	(367.94,441.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (367.94,440.07) --
+	(367.94,442.72);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (376.64,432.12) --
+	(376.64,434.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (376.64,433.44) --
+	(371.75,433.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (371.75,432.12) --
+	(371.75,434.77);
+\definecolor{drawColor}{RGB}{136,34,85}
 
@@
 	(371.75,416.21);
-\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{drawColor}{RGB}{153,153,51}
 
@@
 	(378.16,408.25);
-\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{drawColor}{RGB}{136,34,85}
 
@@
 	(384.91,389.69);
-\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{drawColor}{RGB}{153,153,51}
 
@@
 	(385.45,381.74);
-\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{drawColor}{RGB}{136,34,85}
 
@@
 	(360.01,363.18);
-\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{drawColor}{RGB}{153,153,51}
 
@@
 	(363.16,355.22);
-\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{drawColor}{RGB}{136,34,85}
 
@@
 	(353.37,336.66);
-\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{drawColor}{RGB}{153,153,51}
 
@@
 	(362.29,328.71);
-\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{drawColor}{RGB}{136,34,85}
 
@@
 	(304.77,124.53);
-\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{drawColor}{RGB}{153,153,51}
 
@@
 	(321.73,116.58);
-\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{drawColor}{RGB}{136,34,85}
 
@@
 	(364.46,283.63);
-\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{drawColor}{RGB}{153,153,51}
 
@@
 	(375.34,275.67);
-\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{drawColor}{RGB}{136,34,85}
 
@@
 	(357.61,257.11);
-\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{drawColor}{RGB}{153,153,51}
 
@@
 	(365.99,249.16);
-\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{drawColor}{RGB}{136,34,85}
 
@@
 	(375.23,230.60);
-\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{drawColor}{RGB}{153,153,51}
 
@@
 	(375.45,222.64);
-\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{drawColor}{RGB}{136,34,85}
 
@@
 	(359.79,177.56);
-\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{drawColor}{RGB}{153,153,51}
 
@@
 	(363.81,169.61);
-\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{drawColor}{RGB}{136,34,85}
 
@@
 	(338.69, 98.02);
-\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{drawColor}{RGB}{153,153,51}
 
@@
 	(357.94, 90.06);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (368.16,149.72) circle (  1.96);
 \definecolor{drawColor}{RGB}{153,153,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (368.05,149.72) circle (  1.96);
-\definecolor{drawColor}{RGB}{68,170,153}
-\definecolor{fillColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (371.97,141.77) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (371.86,141.77) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (349.57,494.43) circle (  1.96);
 \definecolor{drawColor}{RGB}{153,153,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (349.57,494.43) circle (  1.96);
-\definecolor{drawColor}{RGB}{68,170,153}
-\definecolor{fillColor}{RGB}{68,170,153}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (356.42,486.48) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (361.96,467.91) circle (  1.96);
 \definecolor{drawColor}{RGB}{153,153,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (361.96,467.91) circle (  1.96);
-\definecolor{drawColor}{RGB}{68,170,153}
-\definecolor{fillColor}{RGB}{68,170,153}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (366.10,459.96) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (371.64,441.40) circle (  1.96);
 \definecolor{drawColor}{RGB}{153,153,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.90,441.40) circle (  1.96);
-\definecolor{drawColor}{RGB}{68,170,153}
-\definecolor{fillColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.12,433.44) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (374.14,433.44) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.77,414.88) circle (  1.96);
 \definecolor{drawColor}{RGB}{153,153,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.77,414.88) circle (  1.96);
-\definecolor{drawColor}{RGB}{68,170,153}
-\definecolor{fillColor}{RGB}{68,170,153}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (381.32,406.93) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.86,388.37) circle (  1.96);
 \definecolor{drawColor}{RGB}{153,153,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.86,388.37) circle (  1.96);
-\definecolor{drawColor}{RGB}{68,170,153}
-\definecolor{fillColor}{RGB}{68,170,153}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.86,380.41) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.49,361.85) circle (  1.96);
 \definecolor{drawColor}{RGB}{153,153,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.49,361.85) circle (  1.96);
-\definecolor{drawColor}{RGB}{68,170,153}
-\definecolor{fillColor}{RGB}{68,170,153}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (365.77,353.90) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (360.55,335.33) circle (  1.96);
 \definecolor{drawColor}{RGB}{153,153,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (360.55,335.33) circle (  1.96);
-\definecolor{drawColor}{RGB}{68,170,153}
-\definecolor{fillColor}{RGB}{68,170,153}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.14,327.38) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (306.62,123.21) circle (  1.96);
 \definecolor{drawColor}{RGB}{153,153,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (306.62,123.21) circle (  1.96);
-\definecolor{drawColor}{RGB}{68,170,153}
-\definecolor{fillColor}{RGB}{68,170,153}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (323.91,115.25) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (368.38,282.30) circle (  1.96);
 \definecolor{drawColor}{RGB}{153,153,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (368.38,282.30) circle (  1.96);
-\definecolor{drawColor}{RGB}{68,170,153}
-\definecolor{fillColor}{RGB}{68,170,153}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (377.73,274.35) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.62,255.79) circle (  1.96);
 \definecolor{drawColor}{RGB}{153,153,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.62,255.79) circle (  1.96);
-\definecolor{drawColor}{RGB}{68,170,153}
-\definecolor{fillColor}{RGB}{68,170,153}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.14,247.83) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (378.38,229.27) circle (  1.96);
 \definecolor{drawColor}{RGB}{153,153,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (378.38,229.27) circle (  1.96);
-\definecolor{drawColor}{RGB}{68,170,153}
-\definecolor{fillColor}{RGB}{68,170,153}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (377.40,221.32) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.34,198.78) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.49,176.24) circle (  1.96);
 \definecolor{drawColor}{RGB}{153,153,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.34,198.78) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.49,176.24) circle (  1.96);
-\definecolor{drawColor}{RGB}{68,170,153}
-\definecolor{fillColor}{RGB}{68,170,153}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (366.86,168.28) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (343.04, 96.69) circle (  1.96);
 \definecolor{drawColor}{RGB}{153,153,51}
 \definecolor{fillColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (343.04, 96.69) circle (  1.96);
-\definecolor{drawColor}{RGB}{68,170,153}
-\definecolor{fillColor}{RGB}{68,170,153}
 
@@
 	(515.39,506.36);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (497.55,140.44) --
-	(497.55,143.09);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (497.55,141.77) --
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (497.34,140.44) --
+	(497.34,143.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (497.34,141.77) --
 	(484.29,141.77);
@@
 	(484.29,143.09);
-\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{drawColor}{RGB}{68,170,153}
 
@@
 	(487.22,151.05);
-\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{drawColor}{RGB}{170,68,153}
 
@@
 	(467.43,487.80);
-\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{drawColor}{RGB}{68,170,153}
 
@@
 	(478.85,495.76);
-\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{drawColor}{RGB}{170,68,153}
 
@@
 	(486.68,461.29);
-\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{drawColor}{RGB}{68,170,153}
 
@@
 	(482.87,469.24);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.38,432.12) --
-	(510.38,434.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.38,433.44) --
-	(497.44,433.44);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (497.44,432.12) --
-	(497.44,434.77);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (503.32,440.07) --
-	(503.32,442.72);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (503.32,441.40) --
-	(496.47,441.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (496.47,440.07) --
-	(496.47,442.72);
-\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (509.51,432.12) --
+	(509.51,434.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (509.51,433.44) --
+	(494.83,433.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (494.83,432.12) --
+	(494.83,434.77);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (503.64,440.07) --
+	(503.64,442.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (503.64,441.40) --
+	(496.36,441.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (496.36,440.07) --
+	(496.36,442.72);
+\definecolor{drawColor}{RGB}{170,68,153}
 
@@
 	(495.60,408.25);
-\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{drawColor}{RGB}{68,170,153}
 
@@
 	(500.71,416.21);
-\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{drawColor}{RGB}{170,68,153}
 
@@
 	(489.94,328.71);
-\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{drawColor}{RGB}{68,170,153}
 
@@
 	(479.94,336.66);
-\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{drawColor}{RGB}{170,68,153}
 
@@
 	(479.83,302.19);
-\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{drawColor}{RGB}{68,170,153}
 
@@
 	(473.20,310.14);
-\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{drawColor}{RGB}{170,68,153}
 
@@
 	(438.84,116.58);
-\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{drawColor}{RGB}{68,170,153}
 
@@
 	(436.34,124.53);
-\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{drawColor}{RGB}{170,68,153}
 
@@
 	(477.87,275.67);
-\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{drawColor}{RGB}{68,170,153}
 
@@
 	(499.95,283.63);
-\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{drawColor}{RGB}{170,68,153}
 
@@
 	(482.87,249.16);
-\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{drawColor}{RGB}{68,170,153}
 
@@
 	(490.38,257.11);
-\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{drawColor}{RGB}{170,68,153}
 
@@
 	(499.08,222.64);
-\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{drawColor}{RGB}{68,170,153}
 
@@
 	(500.16,230.60);
-\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{drawColor}{RGB}{170,68,153}
 
@@
 	(487.55,196.13);
-\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{drawColor}{RGB}{68,170,153}
 
@@
 	(497.12,204.08);
-\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{drawColor}{RGB}{170,68,153}
 
@@
 	(476.57,169.61);
-\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{drawColor}{RGB}{68,170,153}
 
@@
 	(490.70,177.56);
-\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{drawColor}{RGB}{170,68,153}
 
@@
 	(482.22, 90.06);
-\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{drawColor}{RGB}{68,170,153}
 
@@
 	(456.67, 98.02);
-\definecolor{drawColor}{RGB}{51,34,136}
-\definecolor{fillColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (490.92,141.77) circle (  1.96);
 \definecolor{drawColor}{RGB}{170,68,153}
@@
 
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (490.81,141.77) circle (  1.96);
+\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{fillColor}{RGB}{68,170,153}
+
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.42,149.72) circle (  1.96);
-\definecolor{drawColor}{RGB}{51,34,136}
-\definecolor{fillColor}{RGB}{51,34,136}
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (472.76,486.48) circle (  1.96);
+\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{fillColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (482.87,494.43) circle (  1.96);
 \definecolor{drawColor}{RGB}{170,68,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (482.87,494.43) circle (  1.96);
-\definecolor{drawColor}{RGB}{51,34,136}
-\definecolor{fillColor}{RGB}{51,34,136}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (491.57,459.96) circle (  1.96);
+\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{fillColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (486.46,467.91) circle (  1.96);
 \definecolor{drawColor}{RGB}{170,68,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (486.46,467.91) circle (  1.96);
-\definecolor{drawColor}{RGB}{51,34,136}
-\definecolor{fillColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (503.86,433.44) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (502.12,433.44) circle (  1.96);
+\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{fillColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (500.05,441.40) circle (  1.96);
 \definecolor{drawColor}{RGB}{170,68,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (499.95,441.40) circle (  1.96);
-\definecolor{drawColor}{RGB}{51,34,136}
-\definecolor{fillColor}{RGB}{51,34,136}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (500.27,406.93) circle (  1.96);
+\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{fillColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (504.19,414.88) circle (  1.96);
 \definecolor{drawColor}{RGB}{170,68,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (504.19,414.88) circle (  1.96);
-\definecolor{drawColor}{RGB}{51,34,136}
-\definecolor{fillColor}{RGB}{51,34,136}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (497.55,327.38) circle (  1.96);
+\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{fillColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.11,335.33) circle (  1.96);
 \definecolor{drawColor}{RGB}{170,68,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.11,335.33) circle (  1.96);
-\definecolor{drawColor}{RGB}{51,34,136}
-\definecolor{fillColor}{RGB}{51,34,136}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (484.29,300.86) circle (  1.96);
+\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{fillColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (476.46,308.82) circle (  1.96);
 \definecolor{drawColor}{RGB}{170,68,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (476.46,308.82) circle (  1.96);
-\definecolor{drawColor}{RGB}{51,34,136}
-\definecolor{fillColor}{RGB}{51,34,136}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (440.36,115.25) circle (  1.96);
+\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{fillColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (438.84,123.21) circle (  1.96);
 \definecolor{drawColor}{RGB}{170,68,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (438.84,123.21) circle (  1.96);
-\definecolor{drawColor}{RGB}{51,34,136}
-\definecolor{fillColor}{RGB}{51,34,136}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (484.29,274.35) circle (  1.96);
+\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{fillColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (502.01,282.30) circle (  1.96);
 \definecolor{drawColor}{RGB}{170,68,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (502.01,282.30) circle (  1.96);
-\definecolor{drawColor}{RGB}{51,34,136}
-\definecolor{fillColor}{RGB}{51,34,136}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.55,247.83) circle (  1.96);
+\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{fillColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.86,255.79) circle (  1.96);
 \definecolor{drawColor}{RGB}{170,68,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.86,255.79) circle (  1.96);
-\definecolor{drawColor}{RGB}{51,34,136}
-\definecolor{fillColor}{RGB}{51,34,136}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (503.21,221.32) circle (  1.96);
+\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{fillColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (502.12,229.27) circle (  1.96);
 \definecolor{drawColor}{RGB}{170,68,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (502.12,229.27) circle (  1.96);
-\definecolor{drawColor}{RGB}{51,34,136}
-\definecolor{fillColor}{RGB}{51,34,136}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.75,194.80) circle (  1.96);
+\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{fillColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (498.86,202.75) circle (  1.96);
 \definecolor{drawColor}{RGB}{170,68,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (498.86,202.75) circle (  1.96);
-\definecolor{drawColor}{RGB}{51,34,136}
-\definecolor{fillColor}{RGB}{51,34,136}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (481.24,168.28) circle (  1.96);
+\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{fillColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.42,176.24) circle (  1.96);
 \definecolor{drawColor}{RGB}{170,68,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.42,176.24) circle (  1.96);
-\definecolor{drawColor}{RGB}{51,34,136}
-\definecolor{fillColor}{RGB}{51,34,136}
-
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.27, 88.74) circle (  1.96);
-\definecolor{drawColor}{RGB}{170,68,153}
-\definecolor{fillColor}{RGB}{170,68,153}
+\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{fillColor}{RGB}{68,170,153}
 
@@
 	(639.99,506.36);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (625.31,148.40) --
-	(625.31,151.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (625.31,149.72) --
-	(614.01,149.72);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (614.01,148.40) --
-	(614.01,151.05);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (624.77,140.44) --
-	(624.77,143.09);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (624.77,141.77) --
-	(610.20,141.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (610.20,140.44) --
-	(610.20,143.09);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (612.59,493.10) --
-	(612.59,495.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (612.59,494.43) --
-	(593.46,494.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.46,493.10) --
-	(593.46,495.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (616.07,466.59) --
-	(616.07,469.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (616.07,467.91) --
-	(608.35,467.91);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (608.35,466.59) --
-	(608.35,469.24);
-\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (627.71,150.16) --
+	(627.71,151.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (627.71,151.05) --
+	(614.88,151.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (614.88,150.16) --
+	(614.88,151.93);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (625.42,144.86) --
+	(625.42,146.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (625.42,145.75) --
+	(613.46,145.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (613.46,144.86) --
+	(613.46,146.63);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (624.44,139.56) --
+	(624.44,141.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (624.44,140.44) --
+	(610.09,140.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (610.09,139.56) --
+	(610.09,141.33);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (633.47,493.10) --
+	(633.47,495.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (633.47,494.43) --
+	(594.32,494.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (594.32,493.10) --
+	(594.32,495.76);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (611.07,485.15) --
+	(611.07,487.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (611.07,486.48) --
+	(588.89,486.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (588.89,485.15) --
+	(588.89,487.80);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (621.94,468.36) --
+	(621.94,470.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (621.94,469.24) --
+	(604.65,469.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (604.65,468.36) --
+	(604.65,470.12);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (616.40,463.05) --
+	(616.40,464.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (616.40,463.94) --
+	(607.59,463.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (607.59,463.05) --
+	(607.59,464.82);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (621.07,457.75) --
+	(621.07,459.52);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] (621.07,458.63) --
-	(621.07,461.29);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (621.07,459.96) --
-	(601.94,459.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (601.94,458.63) --
-	(601.94,461.29);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (625.21,440.07) --
-	(625.21,442.72);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (625.21,441.40) --
-	(621.29,441.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (621.29,440.07) --
-	(621.29,442.72);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (628.47,432.12) --
-	(628.47,434.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (628.47,433.44) --
-	(619.12,433.44);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (619.12,432.12) --
-	(619.12,434.77);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (630.53,413.56) --
-	(630.53,416.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (630.53,414.88) --
-	(624.23,414.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (624.23,413.56) --
-	(624.23,416.21);
+	(601.94,458.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (601.94,457.75) --
+	(601.94,459.52);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (622.16,441.84) --
+	(622.16,443.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (622.16,442.72) --
+	(609.11,442.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (609.11,441.84) --
+	(609.11,443.61);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (626.18,436.54) --
+	(626.18,438.31);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (626.18,437.42) --
+	(621.94,437.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (621.94,436.54) --
+	(621.94,438.31);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (627.49,431.23) --
+	(627.49,433.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (627.49,432.12) --
+	(615.64,432.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (615.64,431.23) --
+	(615.64,433.00);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (630.42,413.56) --
+	(630.42,416.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (630.42,414.88) --
+	(624.01,414.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (624.01,413.56) --
+	(624.01,416.21);
 \definecolor{drawColor}{RGB}{221,204,119}
@@
 	(627.05,408.25);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (637.82,387.04) --
-	(637.82,389.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (637.82,388.37) --
-	(635.21,388.37);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (635.21,387.04) --
-	(635.21,389.69);
-\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (639.78,388.81) --
+	(639.78,390.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (639.78,389.69) --
+	(635.32,389.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (635.32,388.81) --
+	(635.32,390.58);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (637.71,383.51) --
+	(637.71,385.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (637.71,384.39) --
+	(634.77,384.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (634.77,383.51) --
+	(634.77,385.27);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (636.95,378.20) --
+	(636.95,379.97);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] (636.95,379.09) --
-	(636.95,381.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (636.95,380.41) --
-	(629.55,380.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (629.55,379.09) --
-	(629.55,381.74);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (616.40,360.52) --
-	(616.40,363.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (616.40,361.85) --
-	(612.05,361.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (612.05,360.52) --
-	(612.05,363.18);
-\definecolor{drawColor}{RGB}{221,204,119}
+	(629.55,379.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (629.55,378.20) --
+	(629.55,379.97);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (612.48,362.29) --
+	(612.48,364.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (612.48,363.18) --
+	(600.09,363.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (600.09,362.29) --
+	(600.09,364.06);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (617.92,356.99) --
+	(617.92,358.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (617.92,357.87) --
+	(613.35,357.87);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (613.35,356.99) --
+	(613.35,358.76);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (622.16,351.69) --
+	(622.16,353.45);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] (622.16,352.57) --
-	(622.16,355.22);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (622.16,353.90) --
-	(602.81,353.90);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (602.81,352.57) --
-	(602.81,355.22);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (620.64,334.01) --
-	(620.64,336.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (620.64,335.33) --
-	(607.26,335.33);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (607.26,334.01) --
-	(607.26,336.66);
-\definecolor{drawColor}{RGB}{221,204,119}
+	(602.81,352.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (602.81,351.69) --
+	(602.81,353.45);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (633.58,335.78) --
+	(633.58,337.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (633.58,336.66) --
+	(616.51,336.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (616.51,335.78) --
+	(616.51,337.54);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (620.20,330.47) --
+	(620.20,332.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (620.20,331.36) --
+	(606.61,331.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (606.61,330.47) --
+	(606.61,332.24);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (636.41,325.17) --
+	(636.41,326.94);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] (636.41,326.05) --
-	(636.41,328.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (636.41,327.38) --
-	(601.83,327.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (601.83,326.05) --
-	(601.83,328.71);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (563.55,121.88) --
-	(563.55,124.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (563.55,123.21) --
-	(560.73,123.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (560.73,121.88) --
-	(560.73,124.53);
-\definecolor{drawColor}{RGB}{221,204,119}
+	(601.83,326.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (601.83,325.17) --
+	(601.83,326.94);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (572.25,123.65) --
+	(572.25,125.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (572.25,124.53) --
+	(563.01,124.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (563.01,123.65) --
+	(563.01,125.42);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (562.68,118.35) --
+	(562.68,120.11);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (562.68,119.23) --
+	(559.75,119.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (559.75,118.35) --
+	(559.75,120.11);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (579.10,113.04) --
+	(579.10,114.81);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] (579.10,113.93) --
-	(579.10,116.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (579.10,115.25) --
-	(570.29,115.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (570.29,113.93) --
-	(570.29,116.58);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (626.08,280.98) --
-	(626.08,283.63);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (626.08,282.30) --
-	(621.83,282.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (621.83,280.98) --
-	(621.83,283.63);
-\definecolor{drawColor}{RGB}{221,204,119}
+	(570.29,113.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (570.29,113.04) --
+	(570.29,114.81);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (630.32,282.74) --
+	(630.32,284.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (630.32,283.63) --
+	(623.68,283.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (623.68,282.74) --
+	(623.68,284.51);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (625.10,277.44) --
+	(625.10,279.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (625.10,278.33) --
+	(619.66,278.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (619.66,277.44) --
+	(619.66,279.21);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (626.18,272.14) --
+	(626.18,273.91);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] (626.18,273.02) --
-	(626.18,275.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (626.18,274.35) --
-	(595.63,274.35);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (595.63,273.02) --
-	(595.63,275.67);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (619.12,254.46) --
-	(619.12,257.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (619.12,255.79) --
-	(613.57,255.79);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (613.57,254.46) --
-	(613.57,257.11);
-\definecolor{drawColor}{RGB}{221,204,119}
+	(595.63,273.02);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (595.63,272.14) --
+	(595.63,273.91);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (622.16,256.23) --
+	(622.16,258.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (622.16,257.11) --
+	(609.98,257.11);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (609.98,256.23) --
+	(609.98,258.00);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (619.44,250.93) --
+	(619.44,252.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (619.44,251.81) --
+	(613.24,251.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (613.24,250.93) --
+	(613.24,252.69);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (625.42,245.62) --
+	(625.42,247.39);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] (625.42,246.51) --
-	(625.42,249.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (625.42,247.83) --
-	(598.02,247.83);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (598.02,246.51) --
-	(598.02,249.16);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (628.36,227.95) --
-	(628.36,230.60);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (628.36,229.27) --
-	(624.23,229.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (624.23,227.95) --
-	(624.23,230.60);
-\definecolor{drawColor}{RGB}{221,204,119}
+	(598.02,246.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.02,245.62) --
+	(598.02,247.39);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (631.19,229.71) --
+	(631.19,231.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (631.19,230.60) --
+	(611.61,230.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (611.61,229.71) --
+	(611.61,231.48);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (628.58,224.41) --
+	(628.58,226.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (628.58,225.29) --
+	(624.34,225.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (624.34,224.41) --
+	(624.34,226.18);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (631.95,219.11) --
+	(631.95,220.87);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] (631.95,219.99) --
-	(631.95,222.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (631.95,221.32) --
-	(626.29,221.32);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (626.29,219.99) --
-	(626.29,222.64);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (626.08,196.13) --
-	(626.08,201.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (626.08,198.78) --
-	(623.03,198.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (623.03,196.13) --
-	(623.03,201.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (617.49,174.91) --
-	(617.49,177.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (617.49,176.24) --
-	(612.27,176.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (612.27,174.91) --
-	(612.27,177.56);
-\definecolor{drawColor}{RGB}{221,204,119}
+	(626.29,219.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (626.29,219.11) --
+	(626.29,220.87);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (627.38,201.43) --
+	(627.38,204.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (627.38,202.75) --
+	(621.18,202.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (621.18,201.43) --
+	(621.18,204.08);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (626.29,193.47) --
+	(626.29,196.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (626.29,194.80) --
+	(622.92,194.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (622.92,193.47) --
+	(622.92,196.13);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (620.53,176.68) --
+	(620.53,178.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (620.53,177.56) --
+	(608.46,177.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (608.46,176.68) --
+	(608.46,178.45);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (617.81,171.38) --
+	(617.81,173.15);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (617.81,172.26) --
+	(612.16,172.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (612.16,171.38) --
+	(612.16,173.15);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (618.25,166.07) --
+	(618.25,167.84);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] (618.25,166.96) --
-	(618.25,169.61);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (618.25,168.28) --
-	(604.44,168.28);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (604.44,166.96) --
-	(604.44,169.61);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (602.15, 95.37) --
-	(602.15, 98.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (602.15, 96.69) --
-	(594.76, 96.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (594.76, 95.37) --
-	(594.76, 98.02);
-\definecolor{drawColor}{RGB}{221,204,119}
+	(604.44,166.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (604.44,166.07) --
+	(604.44,167.84);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (594.98, 97.13) --
+	(594.98, 98.90);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (594.98, 98.02) --
+	(578.56, 98.02);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (578.56, 97.13) --
+	(578.56, 98.90);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (605.96, 91.83) --
+	(605.96, 93.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (605.96, 92.71) --
+	(597.70, 92.71);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (597.70, 91.83) --
+	(597.70, 93.60);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (611.61, 86.53) --
+	(611.61, 88.29);
 
 \path[draw=drawColor,line width= 0.6pt,line join=round] (611.61, 87.41) --
-	(611.61, 90.06);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (611.61, 88.74) --
-	(601.72, 88.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (601.72, 87.41) --
-	(601.72, 90.06);
+	(601.72, 87.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (601.72, 86.53) --
+	(601.72, 88.29);
+\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{fillColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (621.29,151.05) circle (  1.96);
 \definecolor{drawColor}{RGB}{17,119,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (619.66,149.72) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (619.44,145.75) circle (  1.96);
 \definecolor{drawColor}{RGB}{221,204,119}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (617.49,141.77) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (617.27,140.44) circle (  1.96);
+\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{fillColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (613.90,494.43) circle (  1.96);
 \definecolor{drawColor}{RGB}{17,119,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (603.02,494.43) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (599.98,486.48) circle (  1.96);
+\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{fillColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (613.24,469.24) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (611.94,463.94) circle (  1.96);
 \definecolor{drawColor}{RGB}{221,204,119}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (597.59,486.48) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (611.50,458.63) circle (  1.96);
+\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{fillColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (615.64,442.72) circle (  1.96);
 \definecolor{drawColor}{RGB}{17,119,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (612.27,467.91) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (624.12,437.42) circle (  1.96);
 \definecolor{drawColor}{RGB}{221,204,119}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (611.50,459.96) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (621.62,432.12) circle (  1.96);
 \definecolor{drawColor}{RGB}{17,119,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (623.25,441.40) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (627.27,414.88) circle (  1.96);
 \definecolor{drawColor}{RGB}{221,204,119}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (623.79,433.44) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (630.97,406.93) circle (  1.96);
+\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{fillColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (637.60,389.69) circle (  1.96);
 \definecolor{drawColor}{RGB}{17,119,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (627.38,414.88) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (636.30,384.39) circle (  1.96);
 \definecolor{drawColor}{RGB}{221,204,119}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (630.97,406.93) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (633.25,379.09) circle (  1.96);
+\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{fillColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (606.29,363.18) circle (  1.96);
 \definecolor{drawColor}{RGB}{17,119,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (636.51,388.37) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (615.64,357.87) circle (  1.96);
 \definecolor{drawColor}{RGB}{221,204,119}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (633.25,380.41) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (612.48,352.57) circle (  1.96);
+\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{fillColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (625.10,336.66) circle (  1.96);
 \definecolor{drawColor}{RGB}{17,119,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (614.22,361.85) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (613.46,331.36) circle (  1.96);
 \definecolor{drawColor}{RGB}{221,204,119}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (612.48,353.90) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (619.12,326.05) circle (  1.96);
+\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{fillColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (567.69,124.53) circle (  1.96);
 \definecolor{drawColor}{RGB}{17,119,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (613.90,335.33) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (561.27,119.23) circle (  1.96);
 \definecolor{drawColor}{RGB}{221,204,119}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (619.12,327.38) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (574.75,113.93) circle (  1.96);
+\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{fillColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (627.05,283.63) circle (  1.96);
 \definecolor{drawColor}{RGB}{17,119,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (562.14,123.21) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (622.38,278.33) circle (  1.96);
 \definecolor{drawColor}{RGB}{221,204,119}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (574.75,115.25) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (610.96,273.02) circle (  1.96);
+\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{fillColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (616.07,257.11) circle (  1.96);
 \definecolor{drawColor}{RGB}{17,119,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (623.90,282.30) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (616.40,251.81) circle (  1.96);
 \definecolor{drawColor}{RGB}{221,204,119}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (610.96,274.35) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (611.72,246.51) circle (  1.96);
+\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{fillColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (621.40,230.60) circle (  1.96);
 \definecolor{drawColor}{RGB}{17,119,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (616.29,255.79) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (626.51,225.29) circle (  1.96);
 \definecolor{drawColor}{RGB}{221,204,119}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (611.72,247.83) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (629.12,219.99) circle (  1.96);
+\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{fillColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (624.23,202.75) circle (  1.96);
 \definecolor{drawColor}{RGB}{17,119,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (626.29,229.27) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (624.66,194.80) circle (  1.96);
+\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{fillColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (614.44,177.56) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (614.98,172.26) circle (  1.96);
 \definecolor{drawColor}{RGB}{221,204,119}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (629.12,221.32) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (611.40,166.96) circle (  1.96);
+\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{fillColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (586.71, 98.02) circle (  1.96);
 \definecolor{drawColor}{RGB}{17,119,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (624.55,198.78) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (614.88,176.24) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (601.83, 92.71) circle (  1.96);
 \definecolor{drawColor}{RGB}{221,204,119}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (611.40,168.28) circle (  1.96);
-\definecolor{drawColor}{RGB}{17,119,51}
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (598.46, 96.69) circle (  1.96);
-\definecolor{drawColor}{RGB}{221,204,119}
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (606.72, 88.74) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (606.72, 87.41) circle (  1.96);
 \definecolor{drawColor}{RGB}{169,169,169}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,430.35) {(Subnational, Slums in 2 cities, 3348)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,430.35) {(Subnational, Slums in 2 cities, 1680)};
 
@@
 
-\path[fill=fillColor] (258.71,  5.00) rectangle (538.72, 43.91);
+\path[fill=fillColor] (252.15,  5.00) rectangle (545.28, 43.91);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (263.71, 21.01) {Subgroups};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (257.15, 21.01) {Subgroups};
 \end{scope}
@@
 
-\path[fill=fillColor] (314.33, 24.45) rectangle (328.79, 38.91);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (315.78, 31.68) -- (327.34, 31.68);
+\path[fill=fillColor] (307.78, 24.45) rectangle (322.23, 38.91);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (309.22, 31.68) -- (320.79, 31.68);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (315.00, 31.68) circle (  1.96);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (307.78, 10.00) rectangle (322.23, 24.45);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (309.22, 17.23) -- (320.79, 17.23);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (321.56, 31.68) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (315.00, 17.23) circle (  1.96);
 \end{scope}
@@
 
-\path[fill=fillColor] (314.33, 10.00) rectangle (328.79, 24.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (315.78, 17.23) -- (327.34, 17.23);
+\path[fill=fillColor] (356.78, 24.45) rectangle (371.23, 38.91);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (358.23, 31.68) -- (369.79, 31.68);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (321.56, 17.23) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (364.01, 31.68) circle (  1.96);
 \end{scope}
@@
 
-\path[fill=fillColor] (363.34, 24.45) rectangle (377.79, 38.91);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (364.78, 31.68) -- (376.35, 31.68);
+\path[fill=fillColor] (356.78, 10.00) rectangle (371.23, 24.45);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (358.23, 17.23) -- (369.79, 17.23);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (370.56, 31.68) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (364.01, 17.23) circle (  1.96);
 \end{scope}
@@
 
-\path[fill=fillColor] (363.34, 10.00) rectangle (377.79, 24.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (364.78, 17.23) -- (376.35, 17.23);
+\path[fill=fillColor] (456.37, 24.45) rectangle (470.83, 38.91);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (457.82, 31.68) -- (469.38, 31.68);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (370.56, 17.23) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (463.60, 31.68) circle (  1.96);
 \end{scope}
@@
 
-\path[fill=fillColor] (462.93, 24.45) rectangle (477.38, 38.91);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.37, 31.68) -- (475.94, 31.68);
+\path[fill=fillColor] (456.37, 10.00) rectangle (470.83, 24.45);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (457.82, 17.23) -- (469.38, 17.23);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (470.16, 31.68) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (463.60, 17.23) circle (  1.96);
 \end{scope}
@@
 
-\path[fill=fillColor] (462.93, 10.00) rectangle (477.38, 24.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.37, 17.23) -- (475.94, 17.23);
+\path[fill=fillColor] (506.60, 24.45) rectangle (521.06, 38.91);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (508.05, 31.68) -- (519.61, 31.68);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (470.16, 17.23) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (513.83, 31.68) circle (  1.96);
 \end{scope}
@@
 
-\path[fill=fillColor] (503.83, 24.45) rectangle (518.28, 38.91);
+\path[fill=fillColor] (506.60, 10.00) rectangle (521.06, 24.45);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (505.27, 31.68) -- (516.84, 31.68);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (508.05, 17.23) -- (519.61, 17.23);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (511.05, 31.68) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (513.83, 17.23) circle (  1.96);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (333.79, 28.93) {Female};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (327.23, 28.93) {Female};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (333.79, 14.47) {Male};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (327.23, 14.47) {Male};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (382.79, 28.93) {Up to Secondary};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (376.23, 28.93) {Up to Secondary};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (382.79, 14.47) {More than Secondary};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (376.23, 14.47) {More than Secondary};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (482.38, 28.93) {$< 55$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (475.83, 28.93) {$< 25$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (482.38, 14.47) {$55 +$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (475.83, 14.47) {$25-54$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (523.28, 28.93) {All};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (526.06, 28.93) {$55 +$};
 \end{scope}
@@
 
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (526.06, 14.47) {All};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{0,0,0}
+
 \node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.20] at (  5.00,528.76) {If a COVID-19 vaccine becomes available in [country], would you take it?};

### 2021-06-10 paper2.tex
update paper

--- 2021-03-23 paper.tex
@@
 \usepackage[margin=1in]{geometry}
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{longtable,booktabs,array}
@@
     \renewcommand\Affilfont{\fontsize{8.5}{10.8}\itshape}
-                                        \author[1]{Julio S. Solís Arce, BA\footnote{First author}}
+                                        \author[1]{Julio S. Solís Arce, BA\footnote{First author.}}
                                                             \affil{WZB Berlin Social Science Center}
@@
                                                                                 \author[1,5,24]{Georgiy Syunyaev, MPhil\(^*\)}
-                                                            \affil{International Center for the Study of Institutions and Development (HSE University, Moscow, Russia)}
+                                                            \affil{International Center for the Study of Institutions and Development, HSE University}
                                                                                 \author[6]{Amyn Abdul Malik, PhD\(^*\)}
@@
                                                                                 \author[5,12]{Ekaterina Borisova, PhD}
-                                                            \affil{Economics Department of Ghent University}
+                                                            \affil{Department of Economics, Ghent University}
                                                                                 \author[1]{Constantin Manuel Bosancianu, PhD}
@@
                                                                                 \author[15]{Baobao Zhang, PhD}
-                                                                            \author[2,22]{Dean Karlan, PhD\footnote{Last author}}
+                                                                            \author[2,22]{Dean Karlan, PhD\footnote{Last author.}}
                                                             \affil{Kellogg School of Management at Northwestern University}
@@
 
-We analyze COVID-19 vaccine acceptance across 15 survey samples covering ten low- and middle-income countries (LMICs) in Asia, Africa, and South America, and two higher income countries (Russia and the United States).
-Standardized survey responses were collected from `45,928individuals.
-We find generally high willingness to take a COVID-19 vaccine in LMIC samples (80\% on average), considerably higher than in the United States (65\%) and Russia (30\%).
-Vaccine acceptance was primarily explained by an interest in personal protection against the disease, while concern about side effects was the most commonly expressed reason for reluctance.
+We analyze COVID-19 vaccine acceptance across 15 survey samples covering ten low- and middle-income countries (LMICs) in Asia, Africa, and South America, Russia (an upper-middle-income country), and the United States, using survey responses from 44,260 individuals.
+We find considerably higher willingness to take a COVID-19 vaccine in LMIC samples (80\% on average) compared to the United States (65\%) and Russia (30\%).
+Vaccine acceptance was primarily explained by an interest in personal protection against COVID-19, while concern about side effects was the most commonly expressed reason for reluctance.
 Health workers were the most trusted sources of information about COVID-19 vaccines.
-Our findings suggest that prioritizing efficient and equitable vaccine distribution to LMICs should yield high returns in promoting global immunization.
-Interventions to promote vaccination in these contexts should focus on translating intentions into uptake and involve trusted health workers.
+Our findings suggest that prioritizing vaccine distribution to LMICs should yield high returns in promoting global immunization coverage, and that vaccination campaigns in these countries should focus on translating acceptance into uptake.
+Messaging highlighting vaccine efficacy and safety, delivered by healthcare workers, may be most effective in addressing remaining hesitancy.
 
@@
 A safe and effective vaccine against COVID-19 is a critical tool to control the pandemic.
-As of March 2, 2021, there were 76 vaccines in clinical development and 16 had advanced to Stage 3 clinical trials.\textsuperscript{\protect\hyperlink{ref-who1}{1}} Following clinical trials, several vaccines have been approved in multiple countries and are being distributed across the globe.
-At present, global vaccine distribution remains highly unequal, with much of the current supply directed toward high-income countries.\textsuperscript{\protect\hyperlink{ref-eiu}{2}}
-
-While effective and equitable distribution of the vaccines is a key policy priority, ensuring the population's acceptance is equally important.
-Acceptance of vaccines and trust in the institutions that administer them are likely key determinants of the success of any vaccination campaign.\textsuperscript{\protect\hyperlink{ref-defigueiredo2020lancet}{3}} Several studies investigate high-income country residents' willingness to take a potential COVID-19 vaccine.\textsuperscript{\protect\hyperlink{ref-boyon2020ipsos}{4},\protect\hyperlink{ref-Malik2020}{5}} Little is known about acceptance rates in low- and middle-income countries (LMICs), however, where the majority of the world's population resides.
-
-Acceptance of childhood vaccination for common diseases ---such as measles (MCV), Bacille Calmette-Guérin (BCG) and diphtheria, tetanus, and pertussis (DTP)---is generally high in LMICs, providing reasons for optimism about future uptake of COVID-19 vaccines.
-Table \ref{tab:otherv} summarizes general vaccine acceptance and uptake of common childhood vaccines for the countries included in our study.
-Still, existing studies on COVID-19 vaccine acceptance document large variation, both across and within countries, including in settings where overall vaccination rates are high.\textsuperscript{\protect\hyperlink{ref-boyon2020ipsos}{4}} These studies highlight concerns about COVID-19 vaccine safety, and particularly concerns about the speed of vaccine development, as reasons for hesitancy in higher income settings.
-Similar concerns may apply in LMICs.
-
-Additional reasons for hesitancy may feature more prominently in LMIC settings.
-Reported COVID-19 mortality rates have consistently been lower in LMICs relative to higher income countries.\textsuperscript{\protect\hyperlink{ref-mukherjee}{6}} If individuals in LMICs feel the risk of disease is less serious, they may be less inclined to accept perceived risks associated with taking a recently-developed vaccine.
-Previous studies have also highlighted factors such as concerns about healthcare quality,\textsuperscript{\protect\hyperlink{ref-christensen2020building}{7}} negative historical experiences,\textsuperscript{\protect\hyperlink{ref-Lowes2018}{8}} weak support from traditional leaders,\textsuperscript{\protect\hyperlink{ref-Jegede2007}{9}} and mistrust in government\textsuperscript{\protect\hyperlink{ref-BLAIR201789}{10}} as barriers to healthcare utilization in LMICs.
-
-Understanding factors that may lead people in LMICs to reject COVID-19 vaccination is of global concern, since a lag in vaccination in the developing world could facilitate the spread of new variants of the virus to other countries.
-
-In order to effectively promote vaccination against COVID-19 and devise messaging strategies, we need to know if people are willing to take COVID-19 vaccines, the reasons why they are willing or unwilling to do so, and the factors influencing their decision-making.
-For this purpose, we developed and deployed a common set of questions across 15 studies in ten LMICs in Africa (Burkina Faso, Mozambique, Nigeria, Rwanda, Sierra Leone, Uganda), Asia (India, Nepal, Pakistan), and Latin America (Colombia).
-We compare these findings in LMICs to those from two higher income countries (Russia and the United States).
+As of April 27, 2021, 22 vaccines had advanced to Stage 3 clinical trials\textsuperscript{\protect\hyperlink{ref-who1}{1}} and more than a dozen vaccines had been approved in multiple countries\textsuperscript{\protect\hyperlink{ref-track}{2}}.
+For example, as of April 27, 2021, Comirnaty (BioNTech/Pfizer) had been approved in more than 80 countries, while the AstraZeneca vaccine had the most country authorizations at 92.\textsuperscript{\protect\hyperlink{ref-track}{2}} At present, however, global vaccine distribution remains highly unequal, with much of the current supply directed toward high-income countries.\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3}}
+
+While effective and equitable distribution of COVID-19 vaccines is a key policy priority, ensuring the population's acceptance is equally important.
+Trust in vaccines and the institutions that administer them are key determinants of the success of any vaccination campaign.\textsuperscript{\protect\hyperlink{ref-defigueiredo2020lancet}{4}} Several studies have investigated willingness to take a potential COVID-19 vaccine in high-income countries,\textsuperscript{\protect\hyperlink{ref-boyon2020ipsos}{5}--\protect\hyperlink{ref-fisher2020attitudes}{10}} and some studies have included middle-income countries.\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3},\protect\hyperlink{ref-lazarus2020nature}{11}} Less is known, however, about vaccine acceptance in low-income countries where large-scale vaccination has yet to begin.
+Understanding the drivers of COVID-19 vaccine acceptance is of global concern, since a lag in vaccination in any country may result in the emergence and spread of new variants that can overcome vaccine- and prior disease-conferred immunity.\textsuperscript{\protect\hyperlink{ref-ong2021lack}{12},\protect\hyperlink{ref-lancettask}{13}}
+
+Our study complements the emerging global picture of COVID-19 vaccine acceptance by focusing primarily on lower income countries.
+We construct a sample of low- and middle-income countries (LMICs) with wide geographic coverage across Africa, Asia and Latin America.
+We move beyond documenting vaccine acceptance rates and analyze data on the reasons for acceptance and hesitancy, which is critical for informing the design of effective vaccine distribution and messaging.
+
+Acceptance of childhood vaccination for common diseases---such as measles (MCV), Bacille Calmette-Guérin (BCG) and diphtheria, tetanus, and pertussis (DTP)---is generally high in LMICs, providing cause for optimism about the prospects for COVID-19 vaccine uptake.
+Table \ref{tab:otherv} summarizes general vaccine acceptance and coverage rates of childhood vaccines in 2018, prior to the current pandemic, for the countries included in our study.
+Agreement on the importance of childhood vaccinations is markedly higher in these LMICs compared to Russia and the United States.
+Still, existing studies on COVID-19 vaccine acceptance document substantial variation, both across and within countries, including in settings with high background levels of other vaccinations.\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3},\protect\hyperlink{ref-defigueiredo2020lancet}{4},\protect\hyperlink{ref-lazarus2020nature}{11}}
+
+This literature cites concerns about COVID-19 vaccine safety, including concerns about the rapid pace of vaccine development, as reasons for hesitancy in higher-income settings,\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3},\protect\hyperlink{ref-boyon2020ipsos}{5}} but other reasons may feature more prominently in LMICs.
+For instance, reported COVID-19 mortality rates have been consistently lower in LMICs relative to higher income countries.\textsuperscript{\protect\hyperlink{ref-mukherjee}{14}} If individuals feel the risk of disease is less serious, they may be less willing to accept any perceived risks of vaccination.\textsuperscript{\protect\hyperlink{ref-brewer2007meta}{15}} Previous studies of healthcare utilization in LMICs have also highlighted factors such as healthcare quality concerns,\textsuperscript{\protect\hyperlink{ref-christensen2020building}{16}} negative historical experiences involving foreign actors,\textsuperscript{\protect\hyperlink{ref-Lowes2018}{17},\protect\hyperlink{ref-martinez2021vaccines}{18}} weak support from traditional leaders,\textsuperscript{\protect\hyperlink{ref-Jegede2007}{19}} and mistrust in government\textsuperscript{\protect\hyperlink{ref-BLAIR201789}{20}} as barriers to uptake, which could apply to COVID-19 vaccination as well.
+
+To promote vaccination against COVID-19 and develop effective messaging strategies, we need to know whether people are willing to take COVID-19 vaccines, the reasons why they are willing or unwilling to do so, and the most trusted sources in their decision-making.
+Our study investigates these questions using a common set of survey items deployed across 13 studies in Africa, South Asia, and Latin America: seven in low-income countries (Burkina Faso, Mozambique, Rwanda, Sierra Leone, Uganda), five in lower-middle-income countries (India, Nepal, Nigeria, Pakistan), and one in an upper-middle-income country (Colombia).
+We compare these findings to those from two countries at the forefront of vaccine research and development, Russia and the United States.
+To select studies to include in our sample, we conducted an internal search within Innovations for Poverty Action (IPA), the International Growth Center (IGC), and the Berlin Social Science Center (WZB) for projects with plans to collect survey data in the second half of 2020.
+Study PIs agreed to include a set of common questions about COVID-19 vaccine attitudes.
+This strategy was guided by the need to collect information quickly and cost effectively using a survey modality (phone) that was both safe given pandemic conditions and appropriate for contexts with limited internet coverage.
+The final set of samples included in our study therefore reflects populations that fall under the current research priorities at IGC, IPA and WZB and, in the case of IPA and IGC, donors that prioritize working in the Global South.
 
@@
 
-Our main results are shown in Figure \ref{fig:mainfigure1} and reproduced as Table \ref{tab:maintabledis} in \protect\hyperlink{appendixd}{Appendix A}.
-The first column provides overall acceptance rates in each study, while the remaining columns show acceptance rates disaggregated by respondent characteristics.
-The ``All LMICs'' row reports averages for LMIC countries only (and so excludes Russia and the US).
+Our main results are shown in Figure \ref{fig:mainfigure1} and reproduced as \protect\hyperlink{appendixd}{Appendix A} Table \ref{tab:maintabledis}.
+The first column provides overall acceptance rates in each study, while the remaining columns disaggregate acceptance rates by respondent characteristics.
+The ``All LMICs'' row reports averages for LMIC countries and excludes Russia and the USA.
 
 We document meaningful variation in vaccine acceptance across and within LMICs, but generally high levels of acceptance in LMICs overall.
-The average acceptance across studies is 80.3\% (95\% CI 74.9--85.6), with a median of 78, a range of 30.1 percent points and an interquartile range of 9.7.
+The average acceptance rate across studies was 80.3\% (95\% CI 74.9--85.6\%), with a median of 78, a range of 30.1 percent points and an interquartile range of 9.7.
 Our estimate of \(\tau^2\) is 0.007 which implies a standard deviation over country averages of 0.084.
 
-The acceptance rate in every LMIC sample is higher than in USA (64.6\%, 61.8--67.3) and Russia (30.4\%, 29.1--31.7).
-
-We find limited evidence of variation across demographic subgroups in LMICs, as shown in Table \ref{tab:dmeans}.
-Women were generally less willing to accept the vaccine (average difference about 4.3 points, significant at \(p<.01\)).
-Younger respondents (defined as aged \textless55 given younger-skewing populations in LMICs) were marginally more willing to take the vaccine, but this difference was not statistically significant.
-Less educated people were on average more willing to take the vaccine in LMICs, but this difference was not significant.
+The acceptance rate in every LMIC sample was higher than in the USA (64.6\%, 61.8--67.3\%) and Russia (30.4\%, 29.1--31.7\%).
+Reported acceptance was lowest in Burkina Faso (66.5\% 63.5--69.5\%) and Pakistan 2 (66.5\%, 64.1--68.9\%).
+The case of Pakistan may be linked to negative historical experiences with foreign-led vaccination campaigns.\textsuperscript{\protect\hyperlink{ref-ali2019polio}{21},\protect\hyperlink{ref-robbins2012cia}{22}} This hesitancy may be particularly problematic, given the magnitude of the second wave in neighboring India just as vaccines are becoming available, with accelerating cases in Bangladesh, Pakistan and India threatening to overwhelm health infrastructure.
+
+We find limited evidence of variation across demographic subgroups in our LMIC samples, as shown in \protect\hyperlink{appendixd}{Appendix A} Table \ref{tab:dmeans}.
+Women were generally less willing to accept the vaccine (average difference about 4.2 points, significant at \(p<.01\)).
+Respondents under age 24 and less educated respondents were marginally more willing to take the vaccine, but these differences were not statistically significant.
+The acceptance advantage among the less educated was most pronounced in Rwanda, Burkina Faso, and Uganda, and stands in contrast to the USA, where more educated respondents were significantly more willing to be vaccinated.
 
 To better understand the reasoning behind vaccine acceptance, we asked those who were willing to take the vaccine why they would take it.
-We summarize in Table \ref{tab:yes}, with more details in Table \ref{tab:yesall}.
-
-The most common reason given for vaccine acceptance was personal protection against COVID-19 infection.
-The average across LMICs was 91\% (86--96).
-In every individual study, it ranked as the first reason.
-In distant second place, LMIC respondents reported willingness to take the COVID-19 vaccine in order to protect their families.
-The average across LMICs was 36\% (28--43).
-In comparison to self-protection, protecting the community did not feature prominently among the stated reasons.
-
-Self-protection also ranked as the most commonly expressed reason for taking the vaccine in Russia (76\%, 74--78) and the USA (94\%, 92--95).
-
-This evidence contrasts with appeals to altruistic behavior and prosocial motivations in order to promote vaccine acceptance.\textsuperscript{\protect\hyperlink{ref-chou2020considering}{11}} The risks and benefits to personal well-being feature much more prominently in people's stated reasons for vaccine acceptance.
-
-Figure \ref{fig:fig2paper} summarizes the reasons given among respondents who said they were not willing to take a Covid vaccine.
-
-The most common reason expressed for reluctance to take the vaccine in LMIC studies was concern about side effects.
-For studies Uganda 1 (85.1\% 80.7--89.6), Sierra Leone 2 (57.9\%, 50.1--65.7), Sierra Leone 1 (53.5\% 47.1--59.9) and Uganda 2 (47.3\% 42.2--52.5), more than half of those respondents unwilling to take the vaccine mentioned this reason.
-Respondents in Russia (36.8\%, 35.2--38.4) and the USA (79.3\%, 74.6--84), reported high levels of this same concern.
-
-While serious adverse events that are life-threatening or require hospitalization are very rare, with only .6\% of respondents reporting at least one side effect in the Pfizer vaccine trial,\textsuperscript{\protect\hyperlink{ref-cdcadverse}{12}} one potential explanation for the outsized concern about side effects could be the lack of widespread information about features of the vaccine at the time of data collection.
-Media coverage of the few cases of serious adverse events and spread of fake news may contribute as well.\textsuperscript{\protect\hyperlink{ref-stein2017golden}{13}}
-
-Concerns about side effects could also be due to a concern about mild side effects from experiences with other vaccines.
-In the case of available COVID-19 vaccines, we now know that mild side effects are common but transient.
-These include fatigue, muscle pain, joint pain and headache, which were severe in fewer than 10\% of people in the clinical trials of tens of thousands.
-Severe fever occurred in fewer than 2\% of them.\textsuperscript{\protect\hyperlink{ref-wadman2020public}{14}}
-
-Allergic reactions from the COVID-19 vaccine seem to be extremely rare.
-Data from trials of the Pfizer-BioNTech vaccines shows that anaphylaxis after reported administration occurs at a rate of 11.1 cases per million vaccine doses administered.\textsuperscript{\protect\hyperlink{ref-cdcallergies}{15}} Our data reflects this -- no more than 6\% of respondents expressed concern about allergies in any of our LMIC studies.
-
-Other concerns that make many respondents unwilling to take the vaccine could be countered by accurately presenting the scientific data to the public.
-Studies Uganda 2 (31\%, 25.9--36.2), Mozambique (29.7\%, 18.6--40.8) and Pakistan 1 (26\%, 18--34) showed relatively high levels of skepticism about vaccine effectiveness.
-This is also true for respondents in Russia (29.6\%, 28.1--31.1) and the USA (46.8\%, 41--52.6).
-Recent clinical trials reveal very high rates of vaccine efficacy,\textsuperscript{\protect\hyperlink{ref-baden2021efficacy}{16},\protect\hyperlink{ref-polack2020safety}{17}} and clearly communicating these results to the public is a high priority.
-In contrast, conspiracy theories were rarely mentioned by respondents in any of our study samples, in spite of widespread popular discourse about anti-vaxxer movements and theories in higher-income countries.\textsuperscript{\protect\hyperlink{ref-loomba_measuring_2021}{18}}
-
-Finally, respondents in some studies downplayed the seriousness of this disease, and listed this as a reason not to be vaccinated.
-Studies USA (39.3\% 33.5--45), Pakistan 1 (29.4\%, 20.9--37.9) and Nepal (20.4\% 6.7--34.1) reported high rates of respondents citing lack of concern as a reason they were hesitant.
-
-The analysis above identifies the nature of the information gaps that any vaccine messaging should target, while in Figure \ref{fig:fig3paper} we try to identify the actors who are best placed to deliver those messages.
-We asked respondents about their most trusted source of information when deciding whether to take the vaccine, because these sources are vital to disease control strategies during public health emergencies.\textsuperscript{\protect\hyperlink{ref-siegrist2014role}{19}} Results from Figure \ref{fig:fig3paper} are reproduced as Table \ref{tab:trust} in \protect\hyperlink{appendixd}{Appendix A}.
-
-We find striking consistency across countries.
-In all but one study, respondents identified the health system as the most trustworthy source to help them decide whether or not to take the COVID-19 vaccine (with the exception of Rwanda, where the government in general was identified as the most trusted source, with the health system a close second).
-Family and friends were the next most important reference points in most samples.
-Across samples, women were 3 percentage points more likely to rely on family and friends than male respondents, though this difference was not significant at conventional levels (Figure \ref{fig:genderhist} in \protect\hyperlink{appendixd}{Appendix D}).
-By contrast, endorsements by religious leaders or celebrity figures were not seen as important sources of influence in any sample other than Nepal.
+We summarize these results in Table \ref{tab:yes}, with additional details in \protect\hyperlink{appendixd}{Appendix A} Table \ref{tab:yesall}.
+The reason most commonly given for vaccine acceptance across samples was personal protection against COVID-19 infection.
+The average across the LMIC samples was 91\% (86--96\%).
+In every individual study, this ranked as the most popular reason.
+In distant second place among LMIC respondents was family protection with an average of 36\% (28--43\%).
+In comparison to protecting oneself and one's family, protecting one's community did not feature prominently among stated reasons for acceptance.
+These reasons do not vary substantially by age group, as shown in Table \ref{tab:countrydiff}.
+Self-protection also ranked as the most common reason for taking the vaccine in Russia (76\%, 74--78\%) and the USA (94\%, 92--95\%).
+
+Figure \ref{fig:fig2paper} summarizes the reasons given by respondents who said they were not willing to take a COVID-19 vaccine.
+Concern about side effects was the most frequently expressed reason for reluctance in our LMIC samples.
+This concern was particularly evident among African country samples.
+In studies Uganda 1 (85.1\% 80.7--89.6\%), Sierra Leone 2 (57.9\%, 50.1--65.7\%), Sierra Leone 1 (53.5\% 47.1--59.9\%) and Uganda 2 (47.3\% 42.2--52.5\%), more than half of respondents unwilling to take the vaccine cited worries about side effects.
+Respondents in Russia (36.8\%, 35.2--38.4\%) and even more in the USA (79.3\%, 74.6--84\%), frequently reported this same concern.
+
+Study samples Uganda 2 (31\%, 25.9--36.2\%), Mozambique (29.7\%, 18.6--40.8\%) and Pakistan 1 (26\%, 18--34\%) showed relatively high levels of skepticism about vaccine effectiveness among hesitant respondents.
+This was also true in Russia (29.6\%, 28.1--31.1\%) and the USA (46.8\%, 41--52.6\%).
+In addition, hesitant respondents listed lack of concern about COVID-19 infection as a reason not to be vaccinated.
+Study samples USA (39.3\% 33.5--45\%), Pakistan 1 (29.4\%, 20.9--37.9\%) and Nepal (20.4\% 6.7--34.1\%) reported high rates of this answer among hesitant respondents.
+
+In Figure \ref{fig:fig3paper} we report respondents' most trusted source of guidance when deciding whether to take a COVID-19 vaccine.
+Results from Figure \ref{fig:fig3paper} are reproduced as \protect\hyperlink{appendixd}{Appendix A} Table \ref{tab:trust}.
+\protect\hyperlink{appendixb}{Appendix B} Table \ref{tab:q4} presents a complete description of response recoding from individual studies.
+
+We find striking consistency in most trusted sources across studies.
+In all but one sample, including those from Russia and the USA, respondents identified the health system as the most trustworthy source to help them decide whether to take the COVID-19 vaccine.
+The average across LMICs was 48.1\% (31.6--64.5\%).
+Respondents in Sierra Leone 2 (89.3\%, 87.2--91.5\%), Nigeria (58\%, 55.7--60.2\%) and Burkina Faso (51.6\%, 48.5--54.8\%) cited health workers most often.
+Sierra Leone had the highest trust in health workers and the Ministry of Health, potentially due to investments in public health following the 2014-2015 Ebola epidemic.\textsuperscript{\protect\hyperlink{ref-deserrano}{23}}
+
+The next most cited sources were family and/or friends in Colombia (36.6\%, 33.5--39.7\%), Nepal (35.6\%, 32.9--38.3\%), Russia (28.1\%, 26.8--29.3\%) and Burkina Faso (18.4\%, 16--20.9\%).
+Across the pooled samples, women were 3 percentage points more likely to rely on family and friends than male respondents, though this difference was not statistically significant (Figure \ref{fig:genderhist} in \protect\hyperlink{appendixd}{Appendix D}).
+
+By contrast, in Sierra Leone 1 (32.5\%, 29.7--35.4\%), Uganda 2 (32.4\%, 29.9--35\%), USA (29.7\%, 27--32.3\%) and Nigeria (18\%, 16.2--19.8\%), government was the second most frequently cited.
+Religious leaders and celebrities were not seen as the top sources of guidance by many respondents in any sample other than Nepal, where many respondents most trusted famous people (16.1\%, 13.3--18.9\%).
+
+Finally, we highlight two idiosyncratic, yet frequently mentioned, trusted sources of information in deciding whether to take a COVID-19 vaccine.
+In Rwanda, 34\% of respondents would most trust ``themselves'' for guidance, the most frequent response in this sample.
+In the USA, 14\% of respondents cited Joe Biden, then president-elect and therefore excluded from the ``government'' category, as their most trusted source.
 
@@
 
-To our knowledge, this is the first study documenting rates of expressed COVID-19 vaccine acceptance and hesitancy in a large set of LMICs.
-Our findings show variable but broadly high levels of prospective COVID-19 vaccine acceptance across LMICs using data from 45,928 respondents in 13 original household surveys from Africa (Burkina Faso, Mozambique, Nigeria, Rwanda, Sierra Leone, Uganda), Asia (Bangladesh, India, Nepal, Pakistan), and Latin America (Colombia).
-Acceptance across LMIC averages 80.3, ranging between 66.5 and 96.6.
-We document considerably lower levels of acceptance in Russia and the United States.
-
-Patterns of COVID-19 vaccine hesitancy are not well predicted by existing measures of concerns about the safety of other vaccines (e.g., the Wellcome Global Monitor shown in Table \ref{tab:otherv}).
-Compared with other vaccines, COVID-19 vaccine acceptance is lower and more variable across LMIC samples.
-This suggests that concerns may apply specifically to COVID-19 vaccines rather than to vaccination more broadly.
-
-Our study also documents reasons why respondents express intentions to take (or not take) a COVID-19 vaccine.
-The main reason expressed for willingness to take such a vaccine was to protect oneself.
-The most common reasons offered by those unwilling to take the vaccine were concerns about safety (side effects) and efficacy.
-Across all contexts, health care workers were the most trusted source of information about vaccines.
-
-Our study samples offer an important window into the motivations underlying COVID-19 vaccine acceptance in LMICs, but our data are not fully nationally representative.
-Random digit dial samples and follow-up phone surveys, while necessary during a global pandemic, do not include individuals who reside outside coverage areas, who do not own or cannot operate cell phones, or who choose not to respond to telephone surveys.
-Care should also be taken in any attempt to extrapolate to the population level from the samples representative of narrow subpopulations.
-
-If intentions reported in our LMIC samples translated into actual vaccination uptake, the rates would far exceed the range of what would be required for COVID-19 herd immunity (40-67\% in recent estimates).\textsuperscript{\protect\hyperlink{ref-britten2020}{20},\protect\hyperlink{ref-haley2020}{21}} However, reported intent may not materialize into actual vaccine adoption.\textsuperscript{\protect\hyperlink{ref-mceachanetal2011}{22}} The high salience of COVID-19 due to extensive media coverage and government mitigation efforts and excitement around vaccine release may have increased reported intention.\textsuperscript{\protect\hyperlink{ref-chen1996}{23}} Results from the first COVID-19 vaccine Phase 3 clinical trial were announced before some surveys were fielded; during others, subsequent approvals were granted.
-The fast-moving information environment may change people's perceptions about vaccines by the time they are widely available in LMICs.
-
-Nonetheless, our findings provide some specific guidance on how to design messaging to boost COVID-19 vaccine acceptance and uptake in LMICs.
-Our data have implications for both what the content of the message should be, and who should deliver the message.
-
-First, high levels of trust in the advice of health workers and governments on COVID-19 vaccine decision-making suggest that social and behavioral change communication (SBCC) strategies that engage local health workers may be particularly effective tools to encourage timely and complete vaccine uptake, and to combat remaining vaccine hesitancy.
-The literature has explored messaging strategies to promote welfare-improving behaviors, with considerable attention paid to celebrity endorsements.\textsuperscript{\protect\hyperlink{ref-alatas2019celebrities}{24}} Our data strongly support the view\textsuperscript{\protect\hyperlink{ref-bokemper2021timing}{25}} that those with the most relevant expertise - as opposed to celebrities or general opinion leaders - are most trusted on this specific topic and are therefore best positioned to deliver the message.
-
-Second, the average COVID-19 vaccine acceptance rate across our LMIC samples is high, approximately 80.3\%.
-Given such positive intentions, there may be high returns to investing in straightforward ``last-mile'' nudges that help citizens convert intentions into actions.
-Reminder messages from healthcare providers and messages alerting patients that vaccines have been reserved for them at an upcoming appointment may provide a low-cost encouragement to initiate and complete two-dose COVID-19 vaccinations, as was found in two recent large-scale studies in the United States.\textsuperscript{\protect\hyperlink{ref-milkmanetal2021a}{26},\protect\hyperlink{ref-milkmanetal2021b}{27}} Similarly, childhood vaccination reminders plus cash incentives in Kenya substantially increased full immunization,\textsuperscript{\protect\hyperlink{ref-gibsonetal2017}{28}} and cash and in-kind incentive programs in Nigeria and India have also proven effective.\textsuperscript{\protect\hyperlink{ref-idinsight}{29},\protect\hyperlink{ref-Banerjee2010}{30}}
-
-Third, high coverage rates of existing vaccines, coupled with respondents' reliance on friends and family as information sources, suggest that the general pro-vaccination stance of many citizens could be leveraged to convert intent to uptake.
-Social learning strategies and norm-setting are powerful drivers of information diffusion and behavior change in many related sectors.\textsuperscript{\protect\hyperlink{ref-beaman2021can}{31}} Social signalling of positive attitudes toward COVID-19 vaccines may also help shift social norms toward even greater immunization acceptance and two-dose completion in the community at large.\textsuperscript{\protect\hyperlink{ref-karing2018social}{32}}
-
-Finally, our findings offer guidance on the specific content of vaccine messaging that is likely to be most persuasive.
-Messaging should highlight the high efficacy rates of the COVID-19 vaccines currently on the market in reducing or eliminating disease, hospitalizations and death.
-Alluding to clinical data that addresses people's concerns about potential side effects should be prioritized.
-Messaging should also emphasize the direct protective benefits of the vaccine to the adopter.
+To our knowledge, this is the first study focusing on COVID-19 vaccine attitudes in a large set of low-income and lower-middle-income countries.
+Our findings showed variable but broadly high levels of prospective COVID-19 vaccine acceptance across LMICs, using data from 44,260 respondents in 13 studies in ten LMICs in Africa, South Asia, and Latin America.
+Acceptance across these LMIC samples averaged 80.3\%, ranging between 66.5\% and 96.6\%.
+The two benchmark countries, Russia and the USA, demonstrated lower COVID-19 vaccine acceptance, consistent with relatively lower pre-pandemic vaccine confidence.
+
+Many metrics and indices measure vaccine acceptance and hesitancy globally.\textsuperscript{\protect\hyperlink{ref-betsch2018beyond}{24}--\protect\hyperlink{ref-shapiro2018vaccine}{26},\protect\hyperlink{ref-gilkey2014vaccination}{27},} Our surveys used measures employed in other COVID-19 vaccine acceptance studies\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3},\protect\hyperlink{ref-Malik2020}{6}--\protect\hyperlink{ref-lazarus2020nature}{11}} and recommended by the WHO Data for Action guidance,\textsuperscript{\protect\hyperlink{ref-whodata}{28}} allowing for meaningful cross-study and cross-country comparisons.
+We measure trust in sources of information about COVID-19 vaccination using a measure similar to that used in the Vaccine Confidence Index (VCI), a widely used survey tool.\textsuperscript{\protect\hyperlink{ref-defigueiredo2020lancet}{4}}
+
+Consistent with other studies, we find higher vaccine acceptance among men than women.\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3},\protect\hyperlink{ref-kreps2020factors}{7}--\protect\hyperlink{ref-fisher2020attitudes}{10}} In contrast to studies focused primarily on higher-income countries, we find no consistently significant differences with respect to age\textsuperscript{\protect\hyperlink{ref-kreps2020factors}{7},\protect\hyperlink{ref-dror2020vaccine}{9}} or education in our LMIC samples.
+
+A key contribution of our study relative to the previous literature is its focus on the reasons why respondents express intentions to take (or refuse) a COVID-19 vaccine.
+Other work has highlighted appeals to altruistic behavior or other prosocial motivations to promote vaccine acceptance.\textsuperscript{\protect\hyperlink{ref-chou2020considering}{29}} Yet we find that the potential risks and benefits to personal well-being feature much more prominently in our respondents' reasoning, suggesting that appeals about personal protection may be more effective in LMICs.
+
+The most commonly stated reason for vaccine refusal was concern about safety (side effects).
+Around 86\% of our surveys were conducted as reports from Phase 2 and 3 clinical trial data were emerging for the earliest commercially available vaccines, but prior to the first Emergency Use Authorization of any vaccine (Pfizer-BioNTech approved by the USA on December 11, 2020).
+Early trial data showed that severe adverse effects were extremely rare,\textsuperscript{\protect\hyperlink{ref-mulligan2020phase}{30}--\protect\hyperlink{ref-polack2020safety}{35}} occurring in fewer than 10\% of people in clinical trials.\textsuperscript{\protect\hyperlink{ref-wadman2020public}{36}} Our respondents' outsized concern about side effects could reflect the rapid pace of vaccine development,\textsuperscript{\protect\hyperlink{ref-callaway2020russia}{37}} and limited information available about potential COVID-19 vaccine safety at the time of data collection.
+These concerns could also reflect worries about mild, yet common and transient side effects, such as fatigue, muscle pain, joint pain and headache.
+
+Prominent media coverage of adverse events may exacerbate concerns about side effects.\textsuperscript{\protect\hyperlink{ref-stein2017golden}{38}} In particular, new information about rare but severe cases of thrombosis associated with the Astra-Zeneca vaccine that appeared after our data collection period could affect hesitancy levels.
+This is of particular relevance to LMICs, which are likely to rely on the Astra-Zeneca vaccine in their immunization campaigns, through initiatives such as COVAX.
+
+Concerns about vaccine efficacy, averaging approximately 19.2\% in the LMIC samples, may also reflect a lack of information about vaccines at the time of our surveys.
+Strikingly, even in low-information environments, respondents in our samples rarely cited conspiracy theories about ulterior motives on the part of corporations, politicians or the pharmaceutical industry, despite widespread popular fears about these issues in higher-income countries.\textsuperscript{\protect\hyperlink{ref-loomba_measuring_2021}{39}}
+
+An important limitation of our study is that our samples are not fully nationally representative.
+Phone surveys, while necessary during a global pandemic, do not include individuals who reside outside coverage areas, lack access to a cell phone, or do not respond to calls.
+In addition, as shown in Table \ref{tab:sampling}, several studies focus on sub-populations of interest in pre-existing studies to which questions about COVID-19 vaccination were added.
+Particular care should be taken in any attempt to extrapolate to the national population level from these samples.
+Furthermore, we emphasize that our data are not representative of all LMICs.
+They represent a convenience sample of studies in countries in which our organizations could quickly mobilize coordinated data collection.
+
+The expressed intentions to take a COVID-19 vaccine that we document in our LMIC samples, if translated into behavior, would meet or exceed the current herd immunity threshold for COVID-19 (estimated at 60-80\%, based on the predominant variant in circulation in these countries).\textsuperscript{\protect\hyperlink{ref-omer2020herd}{40}--\protect\hyperlink{ref-mcneil_2021}{42}} However, reported intent may not always convert vaccine uptake.\textsuperscript{\protect\hyperlink{ref-mceachanetal2011}{43}} The high salience of COVID-19 due to extensive media coverage may have increased reported intentions.
+Conversely, reports about side effects and risks associated with expedited vaccine development may have increased hesitancy.
+The fast-moving pandemic and vaccine development context may change perceptions about vaccines by the time they are widely available in LMICs.
+
+Indeed, previous research on vaccine hesitancy has emphasized how concerns that arise surrounding vaccination campaigns are often case- and context-specific,\textsuperscript{\protect\hyperlink{ref-larson2011addressing}{44}} making it difficult to predict exactly how COVID-19 vaccines will be received in any given setting.
+The lower COVID-19 vaccine acceptance rates we observe in Russia and the USA, for example, may reflect the politicization of this specific pandemic and vaccine development,\textsuperscript{\protect\hyperlink{ref-hornsey2020donald}{45}--\protect\hyperlink{ref-burki2020russian}{48}} in addition to generally greater vaccine skepticism.
+
+Nonetheless, our findings suggest several concrete implications for policy relating to vaccine roll-out in LMICs.
+First and foremost, we document high levels of COVID-19 vaccine acceptance in LMICs compared to Russia and the USA.
+While global vaccine distribution has skewed heavily toward higher-income countries to date,\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3}} our findings suggest that prioritizing distribution to LMICs is justified not only on equity grounds, but on the expectation of ``better value'' in maximizing global coverage more quickly.
+
+Our findings also imply that, once vaccine distribution to LMICs begins in earnest, interventions should focus on converting positive intentions into action.
+Straightforward, low-cost nudges may be particularly effective in this regard.
+Two recent large-scale studies in the USA found that vaccination appointment reminder messages from healthcare providers increased influenza vaccine uptake.\textsuperscript{\protect\hyperlink{ref-milkmanetal2021a}{49},\protect\hyperlink{ref-milkmanetal2021b}{50}} Similar interventions have proven effective in increasing immunization in LMIC contexts.
+In Ghana and Kenya, vaccination reminders plus small cash incentives increased childhood immunization coverage.\textsuperscript{\protect\hyperlink{ref-levine2021}{51},\protect\hyperlink{ref-gibsonetal2017}{52}} Cash and in-kind incentives programs were also effective in Nigeria and India.\textsuperscript{\protect\hyperlink{ref-idinsight}{53},\protect\hyperlink{ref-Banerjee2010}{54}}
+
+This recommendation is consistent with accepted frameworks, such as the WHO's Behavioral and Social Drivers of vaccination (BeSD) model, which suggests leveraging favorable intentions through reminders and primes, and reducing access barriers when the vast majority of people intend to be vaccinated.\textsuperscript{\protect\hyperlink{ref-whodata}{28},\protect\hyperlink{ref-brewer2017increasing}{55}} Particularly since COVID-19 vaccination may be more collectively than individually optimal, ease of access is critical to achieve high coverage.\textsuperscript{\protect\hyperlink{ref-betsch2013inviting}{56}}
+
+Our findings also suggest directions for the design and delivery of messaging to boost COVID-19 vaccine acceptance and uptake in LMICs.
+We highlight four potential implications.
+First, our data strongly support the view that respondents from LMICs prefer to follow the guidance of actors with the most relevant knowledge and expertise.
+We find high levels of trust in health workers, which suggests that social and behavioral change communication (SBCC) strategies engaging local health workers may be particularly effective in encouraging efficient and comprehensive vaccine uptake and combating remaining hesitancy.\textsuperscript{\protect\hyperlink{ref-bokemper2021timing}{46},\protect\hyperlink{ref-who2020behavioral}{57}} Health workers have been the first group to receive the COVID-19 vaccine and are therefore best-positioned to share locally credible experiences of vaccination.\textsuperscript{\protect\hyperlink{ref-katzman2021primary}{58}} While celebrities were not identified as a particularly trustworthy source for COVID-19 advice in our study, celebrity endorsements have proven effective in other contexts and may complement a strategy that primarily focuses on health workers.\textsuperscript{\protect\hyperlink{ref-alatas2019celebrities}{59}}
+
+Second, our findings offer guidance on the specific content of vaccine messaging that is likely to be most persuasive.
+Hesitant respondents were most concerned about side effects and vaccine efficacy.
+This suggests that messaging should highlight the high efficacy rates of the COVID-19 vaccines currently on the market in reducing or eliminating disease, hospitalizations, and death, and communicate accurate information about potential side effects.
+Our data also suggest that messaging should emphasize the direct protective benefits of the vaccine to the adopter, since personal protection, rather than broader concerns about protecting public health, was the top reason expressed for vaccine-acceptance by our respondents.
+
+Third, consistent with previous studies on COVID-19 vaccination\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3},\protect\hyperlink{ref-kreps2020factors}{7}--\protect\hyperlink{ref-fisher2020attitudes}{10}} our study finds lower vaccine acceptance among women than men, suggesting that messaging strategies should focus on women.
+Recent work in Latin America on COVID-19 vaccine messaging found that the provision of basic information about the vaccines was particularly effective in persuading hesitant women.\textsuperscript{\protect\hyperlink{ref-argote2021messaging}{60}}
+
+Finally, high coverage rates of existing vaccines, coupled with respondents' reliance on friends and family as information sources, suggest that the general pro-vaccination stance of many LMIC citizens could be leveraged to increase uptake of COVID-19 vaccines as they become available.
+Social learning strategies and norm-setting are powerful drivers of behavior in many related sectors.\textsuperscript{\protect\hyperlink{ref-beaman2021can}{61}} Social signaling of positive attitudes toward and uptake of COVID-19 vaccines may also help shift social norms toward even greater immunization acceptance and two-dose completion in the community at large.\textsuperscript{\protect\hyperlink{ref-karing2018social}{62}}
 
@@
 Across studies, we asked respondents, ``If a COVID-19 vaccine becomes available in {[}your country{]}, would you take it?''.
-If the respondent answered yes to this question, we followed up with the question, ``Why would you take it?
+This measure aligns with widely reported COVID-19 vaccine acceptance measures.\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3},\protect\hyperlink{ref-Malik2020}{6}--\protect\hyperlink{ref-lazarus2020nature}{11}} If the respondent answered yes to this question, we followed up with the question, ``Why would you take it?
 {[}the COVID-19 vaccine{]}''.
@@
 {[}the COVID-19 vaccine{]}''.
-Finally, regardless of their expressed willingness to take the vaccine, we asked about actors and institutions who would be influential in their decision.
-The question was worded in the following way: ``Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available?''.
-To examine heterogeneity across demographic strata, we collected information about the gender, age, and education level of each respondent.
-Slight variations in questions wording and answer options across studies are documented in \protect\hyperlink{appendixb}{Appendix B}.
+Finally, regardless of their expressed willingness to take the vaccine, we asked about actors and institutions that would be most influential in their decision: ``Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available?'' following.\textsuperscript{\protect\hyperlink{ref-defigueiredo2020lancet}{4}} To examine heterogeneity across demographic strata, we collected information about gender, age, and education.
+Slight variations in question wording and answer options across studies are documented in \protect\hyperlink{appendixb}{Appendix B}.
 
@@
 Seven were national or nearly-national in scope.
-Among these, studies from Burkina Faso, Colombia, Rwanda, and Sierra Leone (``Sierra Leone 1'') used nationally-representative samples of active mobile phone numbers reached through Random Digit Dialing (RDD).
+Studies from Burkina Faso, Colombia, Rwanda, and Sierra Leone (``Sierra Leone 1'') used nationally-representative samples of active mobile phone numbers reached through Random Digit Dialing (RDD).
 Studies in the USA and Russia were conducted online using quota samples obtained from private survey companies.
@@
 The remaining eight studies targeted sub-national populations.
-One study from Pakistan (``Pakistan 2'') used RDD to reach a representative sample of active mobile phone users in Punjab province.
-Respondents in Mozambique, Nigeria, ``Pakistan 1'', ``Uganda 1'',``Uganda 2'', India, Nepal and ``Sierra Leone 2'' were drawn from pre-existing studies to which COVID-19 vaccine questions were subsequently added.
-For example, ``Sierra Leone 2'' has national coverage from a study on access to electricity and ``Uganda 1'' sampled female caregivers of households in rural and semi-rural villages as part of a large ongoing cluster-RCT implemented across 13 districts.
+One study from Pakistan (``Pakistan 2'') used RDD in Punjab province.
+Respondents in Mozambique, Nigeria, Pakistan (``Pakistan 1''), Uganda (``Uganda 1'',``Uganda 2''), India, Nepal and Sierra Leone (``Sierra Leone 2'') were drawn from pre-existing studies to which COVID-19 vaccine questions were subsequently added.
+For example, Sierra Leone 2 has national coverage from a study on access to electricity and Uganda 1 sampled female caregivers of households in rural and semi-rural villages as part of a large ongoing cluster-RCT implemented across 13 districts.
 
 Table \ref{tab:sampling} in \protect\hyperlink{appendixd}{Appendix A} summarizes the geographic scope, sampling methodologies and survey modalities of all 15 studies.
-A detailed description of each study is included in \protect\hyperlink{appendixa}{Appendix D}.
-
-All LMIC surveys were conducted via telephone to minimize in-person contact and comply with local government social distancing guidelines.
+A detailed description of each study is included in \protect\hyperlink{appendixa}{Appendix C}.
+
+All surveys were conducted remotely to minimize in-person contact and comply with social distancing guidelines.
 Interviews were conducted by local staff in each country in local language(s).
 Surveying by phone made rapid, large-scale data collection possible.
-Surveys lasted approximately 15 to 40 minutes.
-
-Taken together, we have data from 21,844 individuals from LMICs and 24,084 from the USA and Russia, for a total of 45,928 respondents.
+In two samples, the USA and Russia, surveys occurred via online polling.
+All surveys lasted approximately 15 to 40 minutes.
+
+Taken together, we have data from 20,176 individuals from 10 LMICs and 24,084 from the USA and Russia, for a total of 44,260 respondents.
 
@@
 This was calculated combining all other answer options (``No'', ``Don't Know'' and ``Refuse'') into a single reference category.
-We estimated this outcome for each study with robust standard errors and employed sampling weights where available.
-
-In addition to study-level estimates, we combined data from all studies other than the USA and Russia to calculate an aggregate estimate for all LMIC studies.
-For these analyses, each included study received equal weight and standard errors were clustered at the study level.
-Averages in the ``All LMICs'' group then reflect the expected share across studies.
-In this combined analysis we also estimated the underlying heterogeneity of vaccine acceptance across studies using the between studies variance estimator \(\tau^2\) from a random effects model.
-
-We also conducted subgroup analyses by gender, age and education level and reported differences between groups.
-For the ``All LMICs'' analyses we calculated the average of differences between subgroups within studies with standard errors clustered at the study level.
-
-We additionally examined reported reasons for COVID-19 vaccine acceptance and hesitancy, as well as the types of actors respondents would trust when making the decision about whether to take a COVID-19 vaccine.
-Among respondents who expressed willingness to take the vaccine, we asked about several possible reasons why they would take it.
-For respondents unwilling to take the vaccine, we asked about several possible reasons why they would not take it.
-Finally, we asked all respondents, regardless of their answers to other questions, whom they would trust most to help them decide whether to get a COVID-19 vaccine.
-We report estimates of agreement with reasons for vaccine acceptance/hesitancy and trust in actors for individual studies and for the ``All LMICs'' group.
+We estimated average acceptance for each individual sample via ordinary least squares (OLS) weighted by respective study population weights and robust standard errors clustered at the level relevant for the sample.
+
+In addition to study-level estimates, we combined data from all studies other than the USA and Russia to calculate an aggregate ``All LMIC studies'' estimate.
+For these analyses, we estimated average acceptance by OLS with weights for each study normalized such that the total weight given to observations was constant across studies.
+Robust standard errors for these analyses were clustered at the study level.
+
+We note the core results would be virtually unchanged at 80.8\% (74.5--87.1) rather than 80.3\% (74.9 -85.6) using countries rather than studies as groups in the pooled analysis, that is if we set weights so that the sum of weights in each country (rather than in each study) sum to a constant and cluster standard errors at the country level (rather than the study level).
+
+In this combined analysis, we also estimated the underlying heterogeneity of vaccine acceptance across studies using the between studies variance estimator \(\tau^2\) from a random effects model.
+
+We conducted subgroup analyses by gender, age and education level and reported differences between groups.
+For age, we selected cut-offs below 25, between age 25 and 54, and above 55 years old, closely following the age breakdown proposed by recent work on COVID-19 vaccine acceptance.\textsuperscript{\protect\hyperlink{ref-lazarus2020nature}{11}} However, the lower life expectancy (63 years on average)\textsuperscript{\protect\hyperlink{ref-wbage}{63}} and younger-skewing populations (only 5\% of the population is above 65 years old)\textsuperscript{\protect\hyperlink{ref-WorldBanksubSahara}{64}} of low-income countries in particular, precluded further disaggregation at the upper end of the age distribution.
+For education, we divided the sample between respondents who had completed secondary school and those that had not.
+We defined these two groups to reflect broader schooling trends in LMICs, where out of every 100 students entering primary education, 61\% complete lower secondary education.\textsuperscript{\protect\hyperlink{ref-world2017world}{65}} The subgroup analyses estimates are calculated in exactly the same way as the overall acceptance rate---with weights again normalized to sum to a constant within each study---with the exception that the subsample used in the analysis is limited to those respondents fitting each demographic group.
+
+We then investigated stated reasons for COVID-19 vaccine acceptance and hesitancy, and the types of actors respondents would trust most when making the decision about whether to take a COVID-19 vaccine.
+We report estimates of agreement with reasons for vaccine acceptance/hesitancy and trust in actors for individual studies and for the ``All LMICs'' group, which includes all study samples except Russia and the USA.
+Estimates were calculated with the same procedure as above, varying only the quantity of interest; i.e.~one model is run for each reason why a respondent would (or would not) take the vaccine and each trusted actor.
 
 \newpage
+
+\hypertarget{data-availability-statement}{%
+\section*{Data Availability Statement}\label{data-availability-statement}}
+\addcontentsline{toc}{section}{Data Availability Statement}
+
+Individual participant data (de-identified) that underlie the results reported in this article, are available without restrictions at \url{https://github.com/wzb-ipi/covid_vaccines_nmed}.
+
+\hypertarget{code-availability}{%
+\section*{Code Availability}\label{code-availability}}
+\addcontentsline{toc}{section}{Code Availability}
+
+All code has been deposited into the publicly available GitHub repository at \url{https://github.com/wzb-ipi/covid_vaccines_nmed}.
+The code and output for all analyses can be easily inspected at \url{https://wzb-ipi.github.io/covid_vaccines_nmed/replication.html}.
+
+\hypertarget{acknowledgements}{%
+\section*{Acknowledgements}\label{acknowledgements}}
+\addcontentsline{toc}{section}{Acknowledgements}
+
+This work would not have been possible without the hard work and ingenuity of many.
+For valuable contributions to data collection during the challenging context of the global pandemic, we would like to thank:
+
+Burkina Faso: Béchir Wendemi Ouédraogo (M\&E Associate), Achille Mignondo Tchibozo (Research Manager) and Touba Bakary Pare (Senior Field Manager) at IPA Burkina Faso in Ouagadougou for their work on the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+
+Colombia: Margarita Rosa Cabra Gacia (Senior Research Associate), Laura Polanco, María Juliana Otálora (Research Analyst), Sofía Jaramillo (Research Manager) and Mery Galindo (Field Coordinator) at IPA Colombia in Bogotá for their work on the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+
+India: Bhartendu Trivedi, Yashashvi Singh, Tatheer Fatima and the field team of Morsel Research and Development.
+
+Mozambique: Alberto Arlindo, Imamo Mussa, Ismail Mussa, Frederica Mendonça and Simão Paiva from NOVAFRICA Mozambique office.
+
+Nepal: Arjun Kharel and field staff at the Centre for the Study of Labour and Mobility (CESLAM) in Kathmandu.
+
+Nigeria: Opeyemi Adeojo (Department of Sociology, University of Lagos), Deborah Anigo, Isaac Obara, Segun Fayomi, and Aishwarya Kumar at the Busara Center for Behavioral Economics, and Sarah Ryan (University of Illinois at Chicago) for research assistance.
+
+Pakistan 1: Ahsan Tariq and Shan e Muhammad Malik at the Institute for Development and Economic Alternatives (IDEAS) in Lahore as survey wing leads and Hamid Ali Tiwana for research assistance.
+
+Pakistan 2: Staff and the internal survey firm at the Centre for Economic Research Pakistan (CERP).
+
+Rwanda: Jean Leodomir Habarimana Mfura (Research and Policy Coordinator), Jean Aime Nsabimana and Gisele Manirabaruta (Field Manager) at IPA Rwanda in Kigali for their work on the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+
+Russia: Staff at Online Market Intelligence Survey Agency, Kirill Chmel (HSE University) and Vladimir Zabolotsky (HSE University and University of Bologna) for their intellectual contributions and research assistance.
+
+Sierra Leone 1: Filippo Cuccaro (Research Coordinator) and Fatoma Momoh (Senior Field Manager) at IPA Sierra Leone in Freetown for their work on the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+
+Sierra Leone 2: Sellu Kallon (Field Manager), Junisa Nabieu (Field Supervisor), Momoh Flee (Field Supervisor), Hamid Kai, Mohamed Lamin (Field Supervisor) and all enumerators at IGC-Sierra Leone Freetown office and Wageningen University's Project ``Tracking the Economic Consequences of COVID-19 in Sierra Leone''.
+
+Uganda 1: Staff at IPA Uganda, especially Sarene Shaked and Gloria Ayesiga, for their intellectual contributions, research assistance, and support throughout the Uganda 1 study.
+
+Uganda 2: Co-PIs Ana Garcia Hernandez, Leah Rosenzweig, Lily Tsai, and Elly Atuhumuza, Martin Atyera, and their team of survey enumerators and support staff at IPA Uganda.
+
+United States: Staff at Lucid (survey firm) for distributing the survey and providing the online survey sample.
+
+IGC thanks their resident country teams in Sierra Leone, Uganda, Pakistan, and Mozambique for their continued guidance, coordination of activities with researchers and direct engagement and dissemination activities with national policymakers:
+
+\begin{itemize}
+\tightlist
+\item
+  Herbert McLeod (Country Director) and Abou Bakarr Kamara (Country Economist) at IGC Sierra Leone
+\item
+  Richard Newfarmer (Country Director), Priya Manwaring (Country Economist), and Jakob Rauschendorfer (Country Economist) at IGC - Uganda
+\item
+  Ijaz Nabi (Country Director), Hina Shaikh (Country Economist), and Usman Naeem (Country Economist) at IGC - Pakistan
+\item
+  Claudio Frischtak (Country Director) and Egas Daniel (Country Economist) at IGC - Mozambique
+\end{itemize}
+
+IPA thanks staff from its global offices for their research assistance and support throughout the RECOVR survey.
+Hugo Salas (IPA Mexico) contributed to data analysis for Burkina Faso, Rwanda and Sierra Leone.
+Margarita Rosa Cabra Garcia also contributed to data analysis for Colombia.
+At IPA New York and Washington, DC, Michael Rosenbaum and Savanna Henderson provided research assistance.
+
+NOVAFRICA thanks Cátia Batista (NOVA SBE), Sandra Sequeira (LSE) and Inês Vilela (Royal Holloway, University of London and NOVAFRICA) for their intellectual contributions.
+
+Centre for Economic Research Pakistan (CERP) thanks Javaeria Qureshi (University of Illinois Chicago), Taimur Shah (CERP), and Basit Zafar (University of Michigan) for their contributions to the Economic Vulnerability Assessment (EVA) project from which the questions used in the Pakistan 2 study were drawn.
 
@@
 
-\hypertarget{data-availability-statement}{%
-\section*{Data Availability Statement}\label{data-availability-statement}}
-\addcontentsline{toc}{section}{Data Availability Statement}
-
-Individual participant data (de-identified) that underlie the results reported in this article, analytic code and replication files will be available immediately following publication to no end date for anyone who wishes to access the data and use it for any purpose in a public, open access repository.
-A replication exercise is available here \url{https://wzb-ipi.github.io/covid_vaccines/replication.html}.
-
 \hypertarget{funding}{%
@@
 \CSLLeftMargin{1. }
-\CSLRightInline{WHO. {World Health Organization} draft landscape and tracker of COVID-19 candidate vaccines. (2021).}
-
-\leavevmode\hypertarget{ref-eiu}{}%
+\CSLRightInline{World Health Organization.
+{Draft landscape and tracker of COVID-19 candidate vaccines}.
+\url{https://www.who.int/publications/m/item/draft-landscape-of-covid-19-candidate-vaccines} (2021).}
+
+\leavevmode\hypertarget{ref-track}{}%
 \CSLLeftMargin{2. }
-\CSLRightInline{EIU. More than 85 poor countries will not have widespread access to coronavirus vaccines before 2023. \emph{The Economist} (2021).}
+\CSLRightInline{McGill COVID19 Vaccine Tracker Team. {COVID-19 Vaccine Tracker}. \url{https://covid19.trackvaccines.org/vaccines/} (2021).}
+
+\leavevmode\hypertarget{ref-wouters2021challenges}{}%
+\CSLLeftMargin{3. }
+\CSLRightInline{Wouters, O. J. \emph{et al.} Challenges in ensuring global access to COVID-19 vaccines: Production, affordability, allocation, and deployment. \emph{The Lancet} (2021).}
 
 \leavevmode\hypertarget{ref-defigueiredo2020lancet}{}%
-\CSLLeftMargin{3. }
-\CSLRightInline{Figueiredo, A.
-de, Simas, C., Karafillakis, E., Paterson, P.
+\CSLLeftMargin{4. }
+\CSLRightInline{de Figueiredo, A., Simas, C., Karafillakis, E., Paterson, P.
 \& Larson, H.
 J.
-Mapping global trends in vaccine confidence and investigating barriers to vaccine uptake : A large-scale retrospective temporal modelling study.
+Mapping global trends in vaccine confidence and investigating barriers to vaccine uptake: A large-scale retrospective temporal modelling study.
 \emph{The Lancet} \textbf{396}, 898--908 (2020).}
@@
 \leavevmode\hypertarget{ref-boyon2020ipsos}{}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Boyon, N. Global attitudes on a covid vaccine. (2020).}
+\CSLLeftMargin{5. }
+\CSLRightInline{Ipsos-World Economic Forum. {Global attitudes: COVID-19 vaccines}. \url{https://www.ipsos.com/en-ro/global-attitudes-covid-19-vaccine-january-2021} (2021).}
 
 \leavevmode\hypertarget{ref-Malik2020}{}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Malik, A., McFadden, S., Elharake, J. \& Omer, S. Determinants of COVID-19 vaccine acceptance in the US. \emph{EClinicalMedicine} \textbf{26}, 100495 (2020).}
+\CSLLeftMargin{6. }
+\CSLRightInline{Malik, A., McFadden, S., Elharake, J. \& Omer, S. {Determinants of COVID-19 vaccine acceptance in the US}. \emph{EClinicalMedicine} \textbf{26}, 100495 (2020).}
+
+\leavevmode\hypertarget{ref-kreps2020factors}{}%
+\CSLLeftMargin{7. }
+\CSLRightInline{Kreps, S. \emph{et al.} {Factors associated with US adults' likelihood of accepting COVID-19 vaccination}. \emph{JAMA Network Open} \textbf{3}, e2025594--e2025594 (2020).}
+
+\leavevmode\hypertarget{ref-shekhar2021covid}{}%
+\CSLLeftMargin{8. }
+\CSLRightInline{Shekhar, R. \emph{et al.} {COVID-19 vaccine acceptance among health care workers in the United States}. \emph{Vaccines} \textbf{9}, 119 (2021).}
+
+\leavevmode\hypertarget{ref-dror2020vaccine}{}%
+\CSLLeftMargin{9. }
+\CSLRightInline{Dror, A. A. \emph{et al.} {Vaccine hesitancy: the next challenge in the fight against COVID-19}. \emph{{European Journal of Epidemiology}} \textbf{35}, 775--779 (2020).}
+
+\leavevmode\hypertarget{ref-fisher2020attitudes}{}%
+\CSLLeftMargin{10. }
+\CSLRightInline{Fisher, K. A. \emph{et al.} {Attitudes toward a potential SARS-CoV-2 vaccine: a survey of US adults}. \emph{{Annals of Internal Medicine}} \textbf{173}, 964--973 (2020).}
+
+\leavevmode\hypertarget{ref-lazarus2020nature}{}%
+\CSLLeftMargin{11. }
+\CSLRightInline{Lazarus, J. V. \emph{et al.} {A global survey of potential acceptance of a COVID-19 vaccine}. \emph{Nature medicine} \textbf{27}, 225--228 (2021).}
+
+\leavevmode\hypertarget{ref-ong2021lack}{}%
+\CSLLeftMargin{12. }
+\CSLRightInline{Ong, S.
+W.
+X., Young, B.
+E.
+\& Lye, D.
+C.
+{Lack of detail in population-level data impedes analysis of SARS-CoV-2 variants of concern and clinical outcomes}.
+\emph{The Lancet Infectious Diseases} (2021).}
+
+\leavevmode\hypertarget{ref-lancettask}{}%
+\CSLLeftMargin{13. }
+\CSLRightInline{The Lancet COVID-19 Comission Task Force on Public Health Measures to Suppress the Pandemic.
+{SARS-CoV-2 variants: the need for urgent public health action beyond vaccines}.
+\url{https://covid19commission.org/public-health-measures} (2021).}
 
 \leavevmode\hypertarget{ref-mukherjee}{}%
-\CSLLeftMargin{6. }
+\CSLLeftMargin{14. }
 \CSLRightInline{Mukherjee, S. Why does the pandemic seem to be hitting some countries harder than others? \emph{New Yorker} (2021).}
 
+\leavevmode\hypertarget{ref-brewer2007meta}{}%
+\CSLLeftMargin{15. }
+\CSLRightInline{Brewer, N.
+T.
+\emph{et al.} Meta-analysis of the relationship between risk perception and health behavior: The example of vaccination.
+\emph{Health psychology} \textbf{26}, 136 (2007).}
+
 \leavevmode\hypertarget{ref-christensen2020building}{}%
-\CSLLeftMargin{7. }
+\CSLLeftMargin{16. }
 \CSLRightInline{Christensen, D., Dube, O., Haushofer, J., Siddiqi, B.
 \& Voors, M.
-\emph{Building resilient health systems: Experimental evidence from sierra leone and the 2014 ebola outbreak}.
-(The Quarterly Journal of Economics, 2021).}
+{Building Resilient Health Systems: Experimental Evidence from Sierra Leone and the 2014 Ebola Outbreak}.
+\emph{The Quarterly Journal of Economics} \textbf{136}, 1145--1198 (2021).}
 
 \leavevmode\hypertarget{ref-Lowes2018}{}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Lowes, S. R. \& Montero, E. The legacy of colonial medicine in central africa. (2018).}
+\CSLLeftMargin{17. }
+\CSLRightInline{Lowes, S. \& Montero, E. {The legacy of colonial medicine in Central Africa}. \emph{American Economic Review} \textbf{111}, 1284--1314 (2021).}
+
+\leavevmode\hypertarget{ref-martinez2021vaccines}{}%
+\CSLLeftMargin{18. }
+\CSLRightInline{Martinez-Bravo, M. \& Stegmann, A. {In Vaccines We Trust? The Effects of the Cia's Vaccine Ruse on Immunization in Pakistan}. \emph{CEPR Discussion Paper No. DP15847} (2021).}
 
 \leavevmode\hypertarget{ref-Jegede2007}{}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Jegede, A. S. What led to the nigerian boycott of the polio vaccination campaign? \emph{PLOS Medicine} \textbf{4(3)}, (2007).}
+\CSLLeftMargin{19. }
+\CSLRightInline{Jegede, A. S. {What led to the Nigerian boycott of the polio vaccination campaign?} \emph{PLOS Medicine} \textbf{4(3)}, (2007).}
 
 \leavevmode\hypertarget{ref-BLAIR201789}{}%
-\CSLLeftMargin{10. }
+\CSLLeftMargin{20. }
 \CSLRightInline{Blair, R., Morse, B.
 \& Tsai, L.
-Public health and public trust: Survey evidence from the ebola virus disease epidemic in liberia.
+{Public health and public trust: Survey evidence from the Ebola Virus Disease epidemic in Liberia}.
 \emph{Social Science \& Medicine} \textbf{172}, 89--97 (2017).}
 
+\leavevmode\hypertarget{ref-ali2019polio}{}%
+\CSLLeftMargin{21. }
+\CSLRightInline{Ali, M. \emph{et al.} Polio vaccination controversy in pakistan. \emph{The Lancet} \textbf{394}, 915--916 (2019).}
+
+\leavevmode\hypertarget{ref-robbins2012cia}{}%
+\CSLLeftMargin{22. }
+\CSLRightInline{Robbins, A. The CIA's vaccination ruse. \emph{Journal of Public Health Policy} \textbf{33}, 387--389 (2012).}
+
+\leavevmode\hypertarget{ref-deserrano}{}%
+\CSLLeftMargin{23. }
+\CSLRightInline{Deserranno, E. \& León-Ciliotta, G. {Promotions and Productivity: The Role of Meritocracy and Pay Progression in the Public Sector}. \emph{CEPR Discussion Paper No. DP15837} (2021).}
+
+\leavevmode\hypertarget{ref-betsch2018beyond}{}%
+\CSLLeftMargin{24. }
+\CSLRightInline{Betsch, C. \emph{et al.} Beyond confidence: Development of a measure assessing the 5C psychological antecedents of vaccination. \emph{PloS one} \textbf{13}, e0208601 (2018).}
+
+\leavevmode\hypertarget{ref-domek2018measuring}{}%
+\CSLLeftMargin{25. }
+\CSLRightInline{Domek, G.
+J.
+\emph{et al.} Measuring vaccine hesitancy: Field testing the WHO SAGE working group on vaccine hesitancy survey tool in guatemala.
+\emph{Vaccine} \textbf{36}, 5273--5281 (2018).}
+
+\leavevmode\hypertarget{ref-shapiro2018vaccine}{}%
+\CSLLeftMargin{26. }
+\CSLRightInline{Shapiro, G. K. \emph{et al.} The vaccine hesitancy scale: Psychometric properties and validation. \emph{Vaccine} \textbf{36}, 660--667 (2018).}
+
+\leavevmode\hypertarget{ref-gilkey2014vaccination}{}%
+\CSLLeftMargin{27. }
+\CSLRightInline{Gilkey, M. B. \emph{et al.} The vaccination confidence scale: A brief measure of parents' vaccination beliefs. \emph{Vaccine} \textbf{32}, 6259--6265 (2014).}
+
+\leavevmode\hypertarget{ref-whodata}{}%
+\CSLLeftMargin{28. }
+\CSLRightInline{World Health Organization.
+{Data for action: achieving high uptake of COVID-19 vaccines}.
+\url{https://www.who.int/publications/i/item/WHO-2019-nCoV-vaccination-demand-planning-2021.1} (2021).}
+
 \leavevmode\hypertarget{ref-chou2020considering}{}%
-\CSLLeftMargin{11. }
+\CSLLeftMargin{29. }
 \CSLRightInline{Chou, W.-Y.
@@
 
-\leavevmode\hypertarget{ref-cdcadverse}{}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Centre for Disease Control and Prevention.
-{Local Reactions, Systemic Reactions, Adverse Events, and Serious Adverse Events: Pfizer-BioNTech COVID-19 Vaccine}.
-\url{https://www.cdc.gov/vaccines/covid-19/info-by-product/pfizer/reactogenicity.html} (2020).}
+\leavevmode\hypertarget{ref-mulligan2020phase}{}%
+\CSLLeftMargin{30. }
+\CSLRightInline{Mulligan, M. J. \emph{et al.} Phase i/II study of COVID-19 RNA vaccine BNT162b1 in adults. \emph{Nature} \textbf{586}, 589--593 (2020).}
+
+\leavevmode\hypertarget{ref-logunov2021safety}{}%
+\CSLLeftMargin{31. }
+\CSLRightInline{Logunov, D.
+Y.
+\emph{et al.} Safety and efficacy of an rAd26 and rAd5 vector-based heterologous prime-boost COVID-19 vaccine: An interim analysis of a randomised controlled phase 3 trial in russia.
+\emph{The Lancet} \textbf{397}, 671--681 (2021).}
+
+\leavevmode\hypertarget{ref-folegatti2020safety}{}%
+\CSLLeftMargin{32. }
+\CSLRightInline{Folegatti, P.
+M.
+\emph{et al.} Safety and immunogenicity of the ChAdOx1 nCoV-19 vaccine against SARS-CoV-2: A preliminary report of a phase 1/2, single-blind, randomised controlled trial.
+\emph{The Lancet} \textbf{396}, 467--478 (2020).}
+
+\leavevmode\hypertarget{ref-voysey2021safety}{}%
+\CSLLeftMargin{33. }
+\CSLRightInline{Voysey, M.
+\emph{et al.} Safety and efficacy of the ChAdOx1 nCoV-19 vaccine (AZD1222) against SARS-CoV-2: An interim analysis of four randomised controlled trials in brazil, south africa, and the UK.
+\emph{The Lancet} \textbf{397}, 99--111 (2021).}
+
+\leavevmode\hypertarget{ref-baden2021efficacy}{}%
+\CSLLeftMargin{34. }
+\CSLRightInline{Baden, L. R. \emph{et al.} Efficacy and safety of the mRNA-1273 SARS-CoV-2 vaccine. \emph{New England Journal of Medicine} \textbf{384}, 403--416 (2021).}
+
+\leavevmode\hypertarget{ref-polack2020safety}{}%
+\CSLLeftMargin{35. }
+\CSLRightInline{Polack, F. P. \emph{et al.} Safety and efficacy of the BNT162b2 mRNA covid-19 vaccine. \emph{New England Journal of Medicine} \textbf{383}, 2603--2615 (2020).}
+
+\leavevmode\hypertarget{ref-wadman2020public}{}%
+\CSLLeftMargin{36. }
+\CSLRightInline{Wadman, M. Public needs to prep for vaccine side effects. \emph{Science} \textbf{370}, 1022--1022 (2020).}
+
+\leavevmode\hypertarget{ref-callaway2020russia}{}%
+\CSLLeftMargin{37. }
+\CSLRightInline{Callaway, E. Russia's fast-track coronavirus vaccine draws outrage over safety. \emph{Nature} \textbf{584}, 334--335 (2020).}
 
 \leavevmode\hypertarget{ref-stein2017golden}{}%
-\CSLLeftMargin{13. }
+\CSLLeftMargin{38. }
 \CSLRightInline{Stein, R. A. The golden age of anti-vaccine conspiracies. \emph{Germs} \textbf{7}, 168 (2017).}
 
-\leavevmode\hypertarget{ref-wadman2020public}{}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Wadman, M. Public needs to prep for vaccine side effects. (2020).}
-
-\leavevmode\hypertarget{ref-cdcallergies}{}%
-\CSLLeftMargin{15. }
-\CSLRightInline{CDC COVID-19 Response Team \& Food and Drug Administration.
-{Allergic Reactions Including Anaphylaxis After Receipt of the First Dose of Pfizer-BioNTech COVID-19 Vaccine --- United States, December 14--23, 2020}.
-\url{https://www.cdc.gov/mmwr/volumes/70/wr/mm7002e1.htm\#:~:text=Early\%20safety\%20monitoring\%20of\%20the,nonanaphylaxis\%20allergic\%20reactions\%2C\%20based\%20on} (2021).}
-
-\leavevmode\hypertarget{ref-baden2021efficacy}{}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Baden, L. R. \emph{et al.} Efficacy and safety of the mRNA-1273 SARS-CoV-2 vaccine. \emph{New England Journal of Medicine} \textbf{384}, 403--416 (2021).}
-
-\leavevmode\hypertarget{ref-polack2020safety}{}%
-\CSLLeftMargin{17. }
-\CSLRightInline{Polack, F. P. \emph{et al.} Safety and efficacy of the BNT162b2 mRNA covid-19 vaccine. \emph{New England Journal of Medicine} \textbf{383}, 2603--2615 (2020).}
-
 \leavevmode\hypertarget{ref-loomba_measuring_2021}{}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Loomba, S., Figueiredo, A.
-de, Piatek, S.
+\CSLLeftMargin{39. }
+\CSLRightInline{Loomba, S., de Figueiredo, A., Piatek, S.
 J., Graaf, K.
@@
 
-\leavevmode\hypertarget{ref-siegrist2014role}{}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Siegrist, M. \& Zingg, A. The role of public trust during pandemics: Implications for crisis communication. \emph{European Psychologist} \textbf{19}, 23 (2014).}
-
-\leavevmode\hypertarget{ref-britten2020}{}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Britton, T., Ball, F.
-\& Trapman, P.
-A mathematical model reveals the influence of population heterogeneity on herd immunity to SARS-CoV-2.
-\emph{Science} \textbf{369}, 846--849 (2020).}
-
-\leavevmode\hypertarget{ref-haley2020}{}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Randolph, H. E. \& Barreiro, L. B. Herd immunity: Understanding COVID-19. \emph{Immunity} \textbf{52}, 737--741 (2020).}
+\leavevmode\hypertarget{ref-omer2020herd}{}%
+\CSLLeftMargin{40. }
+\CSLRightInline{Omer, S. B., Yildirim, I. \& Forman, H. P. Herd immunity and implications for SARS-CoV-2 control. \emph{Jama} \textbf{324}, 2095--2096 (2020).}
+
+\leavevmode\hypertarget{ref-aschwanden2021five}{}%
+\CSLLeftMargin{41. }
+\CSLRightInline{Aschwanden, C. Five reasons why COVID herd immunity is probably impossible. \emph{Nature} \textbf{591}, 520--522 (2021).}
+
+\leavevmode\hypertarget{ref-mcneil_2021}{}%
+\CSLLeftMargin{42. }
+\CSLRightInline{McNeil, D. G. How much herd immunity is enough? \emph{The New York Times} (2021).}
 
 \leavevmode\hypertarget{ref-mceachanetal2011}{}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{43. }
 \CSLRightInline{Mceachan, R., Conner, M., Taylor, N.
@@
 
-\leavevmode\hypertarget{ref-chen1996}{}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Chen, R. T. \& Orenstein, W. A. Epidemiologic methods in immunization programs. \emph{Epidemiologic Reviews} \textbf{18}, 99--117 (1996).}
-
-\leavevmode\hypertarget{ref-alatas2019celebrities}{}%
-\CSLLeftMargin{24. }
-\CSLRightInline{Alatas, V., Chandrasekhar, A. G., Mobius, M., Olken, B. A. \& Paladines, C. \emph{When celebrities speak: A nationwide twitter experiment promoting vaccination in indonesia}. (2019).}
+\leavevmode\hypertarget{ref-larson2011addressing}{}%
+\CSLLeftMargin{44. }
+\CSLRightInline{Larson, H. J., Cooper, L. Z., Eskola, J., Katz, S. L. \& Ratzan, S. Addressing the vaccine confidence gap. \emph{The Lancet} \textbf{378}, 526--535 (2011).}
+
+\leavevmode\hypertarget{ref-hornsey2020donald}{}%
+\CSLLeftMargin{45. }
+\CSLRightInline{Hornsey, M.
+J., Finlayson, M., Chatwood, G.
+\& Begeny, C.
+T.
+Donald trump and vaccination: The effect of political identity, conspiracist ideation and presidential tweets on vaccine hesitancy.
+\emph{Journal of Experimental Social Psychology} \textbf{88}, 103947 (2020).}
 
 \leavevmode\hypertarget{ref-bokemper2021timing}{}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{46. }
 \CSLRightInline{Bokemper, S.
@@
 
+\leavevmode\hypertarget{ref-aaslund2020responses}{}%
+\CSLLeftMargin{47. }
+\CSLRightInline{Åslund, A. Responses to the COVID-19 crisis in russia, ukraine, and belarus. \emph{Eurasian Geography and Economics} \textbf{61}, 532--545 (2020).}
+
+\leavevmode\hypertarget{ref-burki2020russian}{}%
+\CSLLeftMargin{48. }
+\CSLRightInline{Burki, T. K. The russian vaccine for COVID-19. \emph{The Lancet Respiratory Medicine} \textbf{8}, e85--e86 (2020).}
+
 \leavevmode\hypertarget{ref-milkmanetal2021a}{}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{49. }
 \CSLRightInline{Milkman, K. L. \emph{et al.} A mega-study of text-based nudges encouraging patients to get vaccinated at an upcoming doctor's appointment. (2021).}
@@
 \leavevmode\hypertarget{ref-milkmanetal2021b}{}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{50. }
 \CSLRightInline{Milkman, K. L. \emph{et al.} A mega-study of text-message nudges encouraging patients to get vaccinated at their pharmacy. (2021).}
 
+\leavevmode\hypertarget{ref-levine2021}{}%
+\CSLLeftMargin{51. }
+\CSLRightInline{Levine, G., Salifu, A., Mohammed, I.
+\& Fink, G.
+{Mobile Nudges and Financial Incentives to Improve Coverage of Timely Neonatal Vaccination in Rural Areas (GEVaP trial): A 3-armed Cluster Randomized Controlled Trial in Northern Ghana}.
+\emph{PLOS One} (2021).}
+
 \leavevmode\hypertarget{ref-gibsonetal2017}{}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Gibson, D.
 G.
-\emph{et al.} Mobile phone-delivered reminders and incentives to improve childhood immunisation coverage and timeliness in kenya (m-SIMU): A cluster randomised controlled trial.
+\emph{et al.} {Mobile phone-delivered reminders and incentives to improve childhood immunisation coverage and timeliness in Kenya (M-SIMU): a cluster randomised controlled trial}.
 \emph{The Lancet Global Health} \textbf{5}, e428--e438 (2017).}
@@
 \leavevmode\hypertarget{ref-idinsight}{}%
-\CSLLeftMargin{29. }
-\CSLRightInline{Insight, I.
+\CSLLeftMargin{53. }
+\CSLRightInline{ID Insight.
 {Impact of conditional cash transfers on routine childhood immunizations in North West Nigeria}.
@@
 \leavevmode\hypertarget{ref-Banerjee2010}{}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Banerjee, A.
@@
 \& Kothari, D.
-Improving immunisation coverage in rural india: Clustered randomised controlled evaluation of immunisation campaigns with and without incentives.
+{Improving immunisation coverage in rural India: clustered randomised controlled evaluation of immunisation campaigns with and without incentives}.
 \emph{BMJ} \textbf{340}, (2010).}
 
+\leavevmode\hypertarget{ref-brewer2017increasing}{}%
+\CSLLeftMargin{55. }
+\CSLRightInline{Brewer, N.
+T., Chapman, G.
+B., Rothman, A.
+J., Leask, J.
+\& Kempe, A.
+Increasing vaccination: Putting psychological science into action.
+\emph{Psychological Science in the Public Interest} \textbf{18}, 149--207 (2017).}
+
+\leavevmode\hypertarget{ref-betsch2013inviting}{}%
+\CSLLeftMargin{56. }
+\CSLRightInline{Betsch, C., Böhm, R.
+\& Korn, L.
+Inviting free-riders or appealing to prosocial behavior?
+Game-theoretical reflections on communicating herd immunity in vaccine advocacy.
+\emph{Health Psychology} \textbf{32}, 978 (2013).}
+
+\leavevmode\hypertarget{ref-who2020behavioral}{}%
+\CSLLeftMargin{57. }
+\CSLRightInline{World Health Organization.
+{Behavioural considerations for acceptance and uptake of COVID-19 vaccines: WHO technical advisory group on behavioural insights and sciences for health, meeting report, 15 October 2020}.
+\url{https://apps.who.int/iris/handle/10665/337335} (2020).}
+
+\leavevmode\hypertarget{ref-katzman2021primary}{}%
+\CSLLeftMargin{58. }
+\CSLRightInline{Katzman, J. G. \& Katzman, J. W. Primary care clinicians as COVID-19 vaccine ambassadors. \emph{Journal of Primary Care \& Community Health} \textbf{12}, 21501327211007026 (2021).}
+
+\leavevmode\hypertarget{ref-alatas2019celebrities}{}%
+\CSLLeftMargin{59. }
+\CSLRightInline{Alatas, V., Chandrasekhar, A.
+G., Mobius, M., Olken, B.
+A.
+\& Paladines, C.
+When celebrities speak: A nationwide twitter experiment promoting vaccination in indonesia.
+\emph{National Bureau of Economic Research} (2019).}
+
+\leavevmode\hypertarget{ref-argote2021messaging}{}%
+\CSLLeftMargin{60. }
+\CSLRightInline{Argote, P. \emph{et al.} Messaging interventions that increase COVID-19 vaccine willingness in latin america. \emph{SSRN 3812023} (2021).}
+
 \leavevmode\hypertarget{ref-beaman2021can}{}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Beaman, L., BenYishay, A., Magruder, J. \& Mobarak, A. M. \emph{Can network theory-based targeting increase technology adoption?} (2021).}
+\CSLLeftMargin{61. }
+\CSLRightInline{Beaman, L., BenYishay, A., Magruder, J. \& Mobarak, A. M. Can network theory-based targeting increase technology adoption? \emph{National Bureau of Economic Research} (2018).}
 
 \leavevmode\hypertarget{ref-karing2018social}{}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{62. }
 \CSLRightInline{Karing, A. Social signaling and childhood immunization: A field experiment in sierra leone. \emph{University of California, Berkeley Working Paper} (2018).}
 
-\leavevmode\hypertarget{ref-Duch2021}{}%
-\CSLLeftMargin{33. }
-\CSLRightInline{Duch, R. \emph{et al.} Who should be first in line for the COVID-19 vaccine? Surveys in 13 countries of the public{'}s preferences for prioritisation. \emph{medRxiv} (2021).}
-
-\leavevmode\hypertarget{ref-lazarus2020nature}{}%
-\CSLLeftMargin{34. }
-\CSLRightInline{Lazarus, J. V. \emph{et al.} A global survey of potential acceptance of a COVID-19 vaccine. \emph{Nature Medecine} 1--4 (2020).}
-
-\leavevmode\hypertarget{ref-wbinternet}{}%
-\CSLLeftMargin{35. }
-\CSLRightInline{World Bank, W. D. I. \url{https://data.worldbank.org/indicator/IT.NET.USER.ZS?locations=XO} (2019).}
+\leavevmode\hypertarget{ref-wbage}{}%
+\CSLLeftMargin{63. }
+\CSLRightInline{World Bank.
+{World Development Indicators: Life expectancy at birth, total (years) - Low \& middle income, Low income countries {[}Data file{]}}.
+\url{https://data.worldbank.org/indicator/SP.DYN.LE00.IN?locations=XO-XM} (2018).}
+
+\leavevmode\hypertarget{ref-WorldBanksubSahara}{}%
+\CSLLeftMargin{64. }
+\CSLRightInline{World Bank.
+{World Bank staff estimates based on age/sex distributions of United Nations Population Division's World Population Prospects: 2019 Revision, Population ages 65 and above (\% of total population) - Sub-Saharan Africa {[}Data file{]}}.
+\url{https://data.worldbank.org/indicator/SP.POP.65UP.TO.ZS?locations=ZG} (2019).}
+
+\leavevmode\hypertarget{ref-world2017world}{}%
+\CSLLeftMargin{65. }
+\CSLRightInline{Bank, W. \emph{World development report 2018: Learning to realize education's promise}. (The World Bank, 2017).}
+
+\leavevmode\hypertarget{ref-eiu}{}%
+\CSLLeftMargin{66. }
+\CSLRightInline{The Economist Intelligence Unit. {Q1 global forecast 2021 Coronavirus vaccines: expect delays}. \url{https://www.eiu.com/n/campaigns/q1-global-forecast-2021/} (2021).}
+
+\leavevmode\hypertarget{ref-cdcadverse}{}%
+\CSLLeftMargin{67. }
+\CSLRightInline{Centre for Disease Control and Prevention.
+{Local Reactions, Systemic Reactions, Adverse Events, and Serious Adverse Events: Pfizer-BioNTech COVID-19 Vaccine}.
+\url{https://www.cdc.gov/vaccines/covid-19/info-by-product/pfizer/reactogenicity.html} (2020).}
+
+\leavevmode\hypertarget{ref-cdcallergies}{}%
+\CSLLeftMargin{68. }
+\CSLRightInline{CDC COVID-19 Response Team \& Food and Drug Administration.
+{Allergic Reactions Including Anaphylaxis After Receipt of the First Dose of Pfizer-BioNTech COVID-19 Vaccine --- United States, December 14--23, 2020}.
+\url{https://www.cdc.gov/mmwr/volumes/70/wr/mm7002e1.htm\#:~:text=Early\%20safety\%20monitoring\%20of\%20the,nonanaphylaxis\%20allergic\%20reactions\%2C\%20based\%20on} (2021).}
+
+\leavevmode\hypertarget{ref-bowles2020countering}{}%
+\CSLLeftMargin{69. }
+\CSLRightInline{Bowles, J., Larreguy, H. \& Liu, S. Countering misinformation via WhatsApp: Preliminary evidence from the COVID-19 pandemic in zimbabwe. \emph{PloS one} \textbf{15}, e0240005 (2020).}
 
@@
 
+\begin{landscape}\begin{table}[!h]
+
+\caption{\label{tab:sampling}Summary of studies sampling}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{12em}>{\raggedright\arraybackslash}p{30em}ll}
+\toprule
+\textbf{Study} & \textbf{Date} & \textbf{Geographic scope} & \textbf{Sampling methodology} & \textbf{Survey modality} & \textbf{Weights}\\
+\midrule
+Burkina Faso & October to December 2020 & National & Random digit dialing (RDD) & Phone & Yes\\
+Colombia & August 2020 & National & Random digit dialing (RDD) & Phone & Yes\\
+India & June 2020 to January 2021 & Subnational, Slums in 2 cities & Representative sample of slum dwellers living in vicinity of a community toilet and located in Uttar Pradesh & Phone & Yes\\
+Mozambique & October to November 2020 & Subnational, 2 cities & 1) Random sample in urban and periurban markets stratified by gender and type of establishment in Maputo; 2) Random sample representative of communities in the Cabo Delgado, stratified on urban, semiurban, and rural areas & Phone & No\\
+Nepal & December 2020 & Subnational, 2 districts & Random sample of poor households from randomly selected villages in Kanchanpur & Phone & Yes\\
+Nigeria & November to December 2020 & Subnational, 1 state & 1) Random sample of individuals in Kaduna; 2) Sample of phone numbers from a phone list of Kaduna state residents & Phone & No\\
+Pakistan 1 & July to September 2020 & Subnational, 2 districts & Random sample of individuals in administrative police units in two districts of Punjab & Phone & Yes\\
+Pakistan 2 & September to October 2020 & Subnational, 1 province & Random digit dialing (RDD) on a random sample of all numerically possible mobile phone numbers in the region of Punjab & Phone & No\\
+Russia & November to December 2020 & Subnational, 61 regions & Sample recruited from the Russian online survey company OMI (Online Market Intelligence).
+Sampling targeted at having a minimum of respondents per region, as well as representation of age, gender and education groups.
+& Online & Yes\\
+Rwanda & October to November 2020 & National & Random digit dialing (RDD) & Phone & Yes\\
+Sierra Leone 1 & October 2020 & National & Random digit dialing (RDD) & Phone & Yes\\
+Sierra Leone 2 & October 2020 to January 2021 & National & A random sample of households in 195 rural towns across all 14 districts of Sierra Leone & Phone & No\\
+Uganda 1 & September to December 2020 & Subnational, 13 districts & Sample of women in households from semi-rural and rural villages across 13 districts in Uganda, selected according to the likelihood of having children & Phone & No\\
+Uganda 2 & November to December 2020 & Subnational, 1 district & Random sample of households in Kampala & Phone & No\\
+USA & December 2020 & National & Nation-wide sample of adult internet users recruited through the market research firm Lucid & Online & Yes\\
+\bottomrule
+\end{tabular}}
+\end{table}
+\end{landscape}
+
 \begin{figure}[!ht]
@@
 \end{figure}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{tab\_reasons\_y}
+\end{Highlighting}
+\end{Shaded}
 
@@
 Burkina Faso & 651 & 76 & 42 & 7\\
- &  & (73, 79) & (38, 46) & ( 5,  9)\\
+ &  & (73, 79) & (38, 46) & (5, 9)\\
 Colombia & 756 & 91 & 23 & 12\\
@@
 Mozambique & 768 & 83 & 32 & 4\\
- &  & (80, 86) & (27, 38) & ( 2,  5)\\
+ &  & (80, 86) & (27, 38) & (2, 5)\\
 Nepal & 1341 & 96 & 34 & 20\\
@@
 Rwanda & 1152 & 98 & 26 & 11\\
- &  & (97, 99) & (23, 28) & ( 9, 13)\\
+ &  & (97, 99) & (23, 28) & (9, 13)\\
 Sierra Leone 1 & 836 & 94 & 37 & 21\\
@@
 Uganda 1 & 2885 & 96 & 36 & 9\\
- &  & (95, 97) & (34, 38) & ( 8, 10)\\
+ &  & (95, 97) & (34, 38) & (8, 10)\\
 Uganda 2 & 1045 & 96 & 28 & 11\\
- &  & (95, 97) & (25, 31) & ( 9, 12)\\
+ &  & (95, 97) & (25, 31) & (9, 12)\\
 All LMICs & . & 91 & 36 & 14\\
- &  & (86, 96) & (28, 43) & ( 9, 18)\\
+ &  & (86, 96) & (28, 43) & (9, 18)\\
 Russia & 5887 & 76 & 69 & 41\\
@@
 \begin{tablenotes}
-\item Table 2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
-The number of observations and percentage correponds only to people who would take the vaccine.
+\item Table 3 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
+The number of observations and percentage corresponds only to people who would take the vaccine.
 Respondents in all countries could give more than one reason.
@@
 
-\begin{landscape}\begin{table}[!h]
-
-\caption{\label{tab:sampling}Summary of studies sampling}
-\centering
-\resizebox{\linewidth}{!}{
-\fontsize{10}{12}\selectfont
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{12em}>{\raggedright\arraybackslash}p{30em}ll}
-\toprule
-\textbf{Study} & \textbf{Geographic scope} & \textbf{Sampling methodology} & \textbf{Survey modality} & \textbf{Weights}\\
-\midrule
-Burkina Faso & National & Random digit dialing (RDD) & Phone & Yes\\
-Colombia & National & Random digit dialing (RDD) & Phone & Yes\\
-India & Subnational, Slums in 2 cities & Representative sample of slum dwellers living in vicinity of a community toilet and located in Uttar Pradesh & Phone & Yes\\
-Mozambique & Subnational, 2 cities & 1) Random sample in urban and periurban markets stratified by gender and type of establishment in Maputo; 2) Random sample representative of communities in the Cabo Delgado, stratified on urban, semiurban, and rural areas & Phone & No\\
-Nepal & Subnational, 2 districts & Random sample of poor households from randomly selected villages in Kanchanpur & Phone & Yes\\
-Nigeria & Subnational, 1 state & 1) Random sample of individuals in Kaduna; 2) Sample of phone numbers from a phone list of Kaduna state residents & Phone & No\\
-Pakistan 1 & Subnational, 2 districts & Random sample of individuals in administrative police units in two districts of Punjab & Phone & Yes\\
-Pakistan 2 & Subnational, 1 province & Random digit dialing (RDD) on a random sample of all numerically possible mobile phone numbers in the region of Punjab & Phone & No\\
-Russia & Subnational, 61 regions & Sample recruited from the Russian online survey company OMI (Online Market Intelligence).
-Sampling targeted at having a minimum of respondents per region, as well as representation of age, gender and education groups.
-& Online & Yes\\
-Rwanda & National & Random digit dialing (RDD) & Phone & Yes\\
-Sierra Leone 1 & National & Random digit dialing (RDD) & Phone & Yes\\
-Sierra Leone 2 & National & A random sample of households in 195 rural towns across all 14 districts of Sierra Leone & Phone & No\\
-Uganda 1 & Subnational, 13 districts & Sample of women in households from semi-rural and rural villages across 13 districts in Uganda, selected according to the likelihood of having children & Phone & No\\
-Uganda 2 & Subnational, 1 district & Random sample of households in Kampala & Phone & No\\
-USA & National & Nation-wide sample of adult internet users recruited through the market research firm Lucid & Online & Yes\\
-\bottomrule
-\end{tabular}}
-\end{table}
-\end{landscape}
 \begin{table}[!h]
@@
 \begin{threeparttable}
-\begin{tabular}[t]{lccccccc}
+\begin{tabular}[t]{lcccccccc}
 \toprule
-\multicolumn{1}{c}{\textbf{}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{Gender}} & \multicolumn{2}{c}{\textbf{Education}} & \multicolumn{2}{c}{\textbf{Age}} \\
-\cmidrule(l{3pt}r{3pt}){3-4} \cmidrule(l{3pt}r{3pt}){5-6} \cmidrule(l{3pt}r{3pt}){7-8}
-\textbf{Country} & \textbf{Average acceptability} & \textbf{Female} & \textbf{Male} & \textbf{> Secondary} & \textbf{Up to Secondary} & \textbf{<55} & \textbf{55+}\\
+\multicolumn{1}{c}{\textbf{}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{Gender}} & \multicolumn{2}{c}{\textbf{Education}} & \multicolumn{3}{c}{\textbf{Age}} \\
+\cmidrule(l{3pt}r{3pt}){3-4} \cmidrule(l{3pt}r{3pt}){5-6} \cmidrule(l{3pt}r{3pt}){7-9}
+\textbf{Country} & \textbf{Average acceptability} & \textbf{Female} & \textbf{Male} & \textbf{> Secondary} & \textbf{Up to Secondary} & \textbf{<25} & \textbf{25-54} & \textbf{55+}\\
 \midrule
-Burkina Faso & 66.5 & 62.1 & 68.4 & 60.8 & 70.1 & 66.0 & 61.0\\
- & (63.5, 69.5) & (56.3, 67.9) & (65.0, 71.9) & (55.9, 65.8) & (66.4, 73.8) & (57.2,  74.8) & (-6.5, 128.6)\\
-Colombia & 74.9 & 73.5 & 77.3 & 78.1 & 73.4 & 74.5 & 73.8\\
- & (72.2, 77.6) & (70.1, 77.0) & (73.0, 81.7) & (73.6, 82.5) & (70.1, 76.8) & (70.9,  78.0) & (65.0,  82.6)\\
-India & 84.6 & 80.8 & 85.6 & 89.4 & 85.8 & 84.6 & 85.1\\
- & (82.8, 86.4) & (77.6, 84.1) & (83.7, 87.5) & (83.5, 95.4) & (82.6, 88.9) & (82.8,  86.4) & (80.8,  89.4)\\
-Mozambique & 89.1 & 86.2 & 91.3 & 86.1 & 89.7 & 88.4 & 91.7\\
- & (86.5, 91.7) & (82.5, 90.0) & (88.4, 94.1) & (81.8, 90.4) & (86.5, 92.8) & (85.5,  91.3) & (88.1,  95.4)\\
-Nepal & 96.6 & 96.4 & 96.4 & . & . & 96.8 & 93.8\\
- & (95.5, 97.6) & (94.6, 98.2) & (95.1, 97.7) & . & . & (95.6,  98.0) & (90.4,  97.2)\\
-Nigeria & 76.2 & 74.9 & 77.0 & . & . & 76.3 & 74.7\\
- & (74.3, 78.2) & (71.7, 78.1) & (74.6, 79.4) & . & . & (74.3,  78.3) & (65.8,  83.6)\\
-Pakistan 1 & 76.1 & 72.2 & 80.1 & 83.6 & 74.0 & 76.0 & 80.8\\
- & (70.0, 82.3) & (65.6, 78.8) & (73.8, 86.4) & (76.6, 90.5) & (67.4, 80.5) & (69.9,  82.2) & (64.9,  96.7)\\
-Pakistan 2 & 66.5 & . & . & 71.4 & 64.2 & . & .\\
- & (64.1, 68.9) & . & . & (67.3, 75.5) & (61.2, 67.1) & . & .\\
-Rwanda & 84.9 & 79.4 & 88.0 & 71.4 & 87.7 & 85.2 & 73.3\\
- & (82.9, 86.8) & (75.8, 83.0) & (85.8, 90.2) & (65.5, 77.2) & (85.8, 89.7) & (83.3,  87.2) & (59.2,  87.3)\\
-Sierra Leone 1 & 78.0 & 74.1 & 80.1 & 74.4 & 80.2 & 78.2 & 74.0\\
- & (75.5, 80.5) & (69.5, 78.7) & (77.2, 83.1) & (70.1, 78.7) & (77.0, 83.3) & (75.7,  80.8) & (61.4,  86.6)\\
-Sierra Leone 2 & 87.9 & 88.6 & 87.7 & 88.8 & 87.8 & 87.4 & 90.0\\
- & (86.2, 89.6) & (85.7, 91.5) & (85.9, 89.5) & (85.0, 92.5) & (86.0, 89.6) & (85.5,  89.3) & (87.4,  92.6)\\
-Uganda 1 & 85.8 & 85.8 & . & 80.1 & 84.8 & 85.8 & .\\
- & (84.4, 87.2) & (84.4, 87.2) & . & (74.4, 85.9) & (83.2, 86.5) & (84.4,  87.2) & .\\
-Uganda 2 & 76.5 & 74.9 & 78.0 & 68.6 & 79.8 & 76.9 & 73.7\\
- & (74.3, 78.7) & (71.5, 78.3) & (75.2, 80.9) & (64.3, 72.9) & (77.3, 82.2) & (74.5,  79.3) & (67.3,  80.0)\\
-All LMICs & 80.3 & 79.1 & 82.7 & 77.5 & 79.8 & 81.3 & 79.3\\
- & (74.9, 85.6) & (73.3, 84.9) & (77.4, 88.0) & (71.4, 83.6) & (74.1, 85.4) & (76.1,  86.5) & (72.6,  86.0)\\
-Russia & 30.4 & 22.6 & 38.5 & 31.0 & 29.6 & 28.4 & 40.0\\
- & (29.1, 31.7) & (20.9, 24.2) & (36.5, 40.5) & (29.6, 32.5) & (27.3, 32.0) & (27.1,  29.7) & (35.9,  44.0)\\
-USA & 64.6 & 56.1 & 73.4 & 72.3 & 51.5 & 61.8 & 69.4\\
- & (61.8, 67.3) & (52.1, 60.1) & (69.8, 76.9) & (69.5, 75.0) & (46.0, 57.0) & (58.4,  65.2) & (64.8,  73.9)\\
+Burkina Faso & 66.5 & 62.1 & 68.4 & 60.8 & 70.1 & 76.0 & 63.2 & .\\
+ & (63.5, 69.5) & (56.3, 67.9) & (65.0, 71.9) & (55.9, 65.8) & (66.4, 73.8) & (58.0, 94.0) & (53.0, 73.4) & .\\
+Colombia & 74.9 & 73.5 & 77.3 & 78.1 & 73.4 & 75.4 & 74.2 & 73.8\\
+ & (72.2, 77.6) & (70.1, 77.0) & (73.0, 81.7) & (73.6, 82.5) & (70.1, 76.8) & (67.5, 83.4) & (70.2, 78.3) & (65.0, 82.6)\\
+India & 84.3 & 82.4 & 84.7 & 87.8 & 85.9 & 77.6 & 85.4 & 83.1\\
+ & (82.3, 86.3) & (79.0, 85.8) & (82.5, 87.0) & (81.1, 94.6) & (82.5, 89.2) & (71.6, 83.6) & (83.4, 87.3) & (77.6, 88.5)\\
+Mozambique & 89.1 & 86.2 & 91.3 & 86.1 & 89.7 & . & 88.3 & 91.7\\
+ & (86.5, 91.7) & (82.5, 90.0) & (88.4, 94.1) & (81.8, 90.4) & (86.5, 92.8) & . & (85.3, 91.2) & (88.1, 95.4)\\
+Nepal & 96.6 & 96.4 & 96.4 & . & . & 97.8 & 96.6 & 93.8\\
+ & (95.5, 97.6) & (94.6, 98.2) & (95.1, 97.7) & . & . & (95.7, 99.8) & (95.2, 97.9) & (90.4, 97.2)\\
+Nigeria & 76.2 & 74.9 & 77.0 & . & . & 69.0 & 77.6 & 74.7\\
+ & (74.3, 78.2) & (71.7, 78.1) & (74.6, 79.4) & . & . & (63.3, 74.7) & (75.5, 79.7) & (65.8, 83.6)\\
+Pakistan 1 & 76.1 & 72.2 & 80.1 & 83.6 & 74.0 & 86.3 & 75.6 & 80.8\\
+ & (70.0, 82.3) & (65.6, 78.8) & (73.8, 86.4) & (76.6, 90.5) & (67.4, 80.5) & (78.4, 94.1) & (69.3, 81.8) & (64.9, 96.7)\\
+Pakistan 2 & 66.5 & . & . & 71.4 & 64.2 & . & . & .\\
+ & (64.1, 68.9) & . & . & (67.3, 75.5) & (61.2, 67.1) & . & . & .\\
+Rwanda & 84.9 & 79.4 & 88.0 & 71.4 & 87.7 & 88.1 & 83.8 & 73.3\\
+ & (82.9, 86.8) & (75.8, 83.0) & (85.8, 90.2) & (65.5, 77.2) & (85.8, 89.7) & (85.0, 91.1) & (81.3, 86.3) & (59.2, 87.3)\\
+Sierra Leone 1 & 78.0 & 74.1 & 80.1 & 74.4 & 80.2 & 78.0 & 78.3 & 74.0\\
+ & (75.5, 80.5) & (69.5, 78.7) & (77.2, 83.1) & (70.1, 78.7) & (77.0, 83.3) & (72.4, 83.6) & (75.4, 81.1) & (61.4, 86.6)\\
+Sierra Leone 2 & 87.9 & 88.6 & 87.7 & 88.8 & 87.8 & 82.9 & 87.6 & 90.0\\
+ & (86.2, 89.6) & (85.7, 91.5) & (85.9, 89.5) & (85.0, 92.5) & (86.0, 89.6) & (73.9, 91.9) & (85.6, 89.5) & (87.4, 92.6)\\
+Uganda 1 & 85.8 & 85.8 & . & 80.1 & 84.8 & 85.5 & 85.9 & .\\
+ & (84.4, 87.2) & (84.4, 87.2) & . & (74.4, 85.9) & (83.2, 86.5) & (82.7, 88.4) & (84.3, 87.4) & .\\
+Uganda 2 & 76.5 & 74.9 & 78.0 & 68.6 & 79.8 & 76.5 & 77.0 & 73.7\\
+ & (74.3, 78.7) & (71.5, 78.3) & (75.2, 80.9) & (64.3, 72.9) & (77.3, 82.2) & (71.0, 82.1) & (74.4, 79.6) & (67.3, 80.0)\\
+All LMICs & 80.3 & 79.2 & 82.6 & 77.4 & 79.8 & 82.8 & 81.1 & 79.1\\
+ & (74.9, 85.6) & (73.4, 85.0) & (77.4, 87.9) & (71.4, 83.4) & (74.1, 85.4) & (76.9, 88.7) & (75.6, 86.6) & (72.5, 85.7)\\
+Russia & 30.4 & 22.6 & 38.5 & 31.0 & 29.6 & 33.5 & 27.6 & 40.0\\
+ & (29.1, 31.7) & (20.9, 24.2) & (36.5, 40.5) & (29.6, 32.5) & (27.3, 32.0) & (29.2, 37.7) & (26.2, 28.9) & (35.9, 44.0)\\
+USA & 64.6 & 56.1 & 73.4 & 72.3 & 51.5 & 51.0 & 64.9 & 69.4\\
+ & (61.8, 67.3) & (52.1, 60.1) & (69.8, 76.9) & (69.5, 75.0) & (46.0, 57.0) & (43.5, 58.6) & (61.1, 68.7) & (64.8, 73.9)\\
 \bottomrule
@@
 Burkina Faso & 651 & 76 & 42 & 7 & 6 & 19 & 2\\
- &  & (73, 79) & (38, 46) & ( 5,  9) & ( 4,  8) & (16, 22) & ( 1,  3)\\
+ &  & (73, 79) & (38, 46) & (5, 9) & (4, 8) & (16, 22) & (1, 3)\\
 Colombia & 756 & 91 & 23 & 12 & 1 & 2 & 6\\
- &  & (88, 93) & (20, 26) & (10, 14) & ( 0,  2) & ( 1,  3) & ( 4,  7)\\
+ &  & (88, 93) & (20, 26) & (10, 14) & (0, 2) & (1, 3) & (4, 7)\\
 Mozambique & 768 & 83 & 32 & 4 & . & 7 & 3\\
- &  & (80, 86) & (27, 38) & ( 2,  5) & . & ( 5,  8) & ( 2,  4)\\
+ &  & (80, 86) & (27, 38) & (2, 5) & . & (5, 8) & (2, 4)\\
 Nepal & 1341 & 96 & 34 & 20 & 2 & 3 & 7\\
- &  & (95, 98) & (32, 37) & (17, 22) & ( 1,  2) & ( 2,  4) & ( 5,  9)\\
+ &  & (95, 98) & (32, 37) & (17, 22) & (1, 2) & (2, 4) & (5, 9)\\
 Nigeria & 1424 & 89 & 35 & 21 & . & 6 & 4\\
- &  & (88, 91) & (33, 38) & (19, 23) & . & ( 4,  7) & ( 3,  5)\\
+ &  & (88, 91) & (33, 38) & (19, 23) & . & (4, 7) & (3, 5)\\
 Rwanda & 1152 & 98 & 26 & 11 & 1 & 5 & 1\\
- &  & (97, 99) & (23, 28) & ( 9, 13) & ( 0,  1) & ( 4,  6) & ( 1,  2)\\
+ &  & (97, 99) & (23, 28) & (9, 13) & (0, 1) & (4, 6) & (1, 2)\\
 Sierra Leone 1 & 836 & 94 & 37 & 21 & 12 & 23 & 7\\
- &  & (92, 96) & (34, 40) & (18, 23) & (10, 14) & (20, 25) & ( 5,  9)\\
+ &  & (92, 96) & (34, 40) & (18, 23) & (10, 14) & (20, 25) & (5, 9)\\
 Sierra Leone 2 & 1855 & 91 & 62 & 21 & 59 & . & 16\\
@@
 Uganda 1 & 2885 & 96 & 36 & 9 & . & 10 & 6\\
- &  & (95, 97) & (34, 38) & ( 8, 10) & . & ( 9, 12) & ( 5,  7)\\
+ &  & (95, 97) & (34, 38) & (8, 10) & . & (9, 12) & (5, 7)\\
 Uganda 2 & 1045 & 96 & 28 & 11 & 1 & 15 & 2\\
- &  & (95, 97) & (25, 31) & ( 9, 12) & ( 1,  2) & (13, 17) & ( 1,  3)\\
+ &  & (95, 97) & (25, 31) & (9, 12) & (1, 2) & (13, 17) & (1, 3)\\
 All LMICs & . & 91 & 36 & 14 & 12 & 10 & 5\\
- &  & (86, 96) & (28, 43) & ( 9, 18) & (-8, 31) & ( 4, 16) & ( 2,  8)\\
+ &  & (86, 96) & (28, 43) & (9, 18) & (-8, 31) & (4, 16) & (2, 8)\\
 Russia & 5887 & 76 & 69 & 41 & 11 & 6 & 18\\
- &  & (74, 78) & (67, 71) & (38, 43) & (10, 13) & ( 5,  7) & (16, 20)\\
+ &  & (74, 78) & (67, 71) & (38, 43) & (10, 13) & (5, 7) & (16, 20)\\
 USA & 1313 & 94 & 92 & 89 & . & 67 & .\\
@@
 \item Table 5 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
+The number of observations and percentage correponds only to people who would take the vaccine.
+Respondents in all countries could give more than one reason.
+A 95\% confidence interval is shown between parentheses
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
+\newpage
+
+\begin{table}[!h]
+
+\caption{\label{tab:yes1}Reasons to take the vaccine- by age groups}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{threeparttable}
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{7em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}}
+\toprule
+\multicolumn{1}{c}{\textbf{ }} & \multicolumn{3}{c}{\textbf{Self}} & \multicolumn{3}{c}{\textbf{Family}} & \multicolumn{3}{c}{\textbf{Community}} \\
+\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10}
+\textbf{Study} & \textbf{<25} & \textbf{25-54} & \textbf{55+} & \textbf{<25} & \textbf{25-54} & \textbf{55+} & \textbf{<25} & \textbf{25-54} & \textbf{55+}\\
+\midrule
+Burkina Faso & 77 & 59 & 100 & 26 & 64 & 66 & 11 & 2 & 0\\
+Conf. interval & (56, 99) & (46, 72) & (100, 100) & (4, 48) & (51, 77) & (-80, 211) & (-5, 26) & (-2, 5) & (0, 0)\\
+n & 19 & 57 & 3 & 19 & 57 & 3 & 19 & 57 & 3\\
+\hline
+Colombia & 91 & 91 & 90 & 26 & 26 & 16 & 12 & 13 & 14\\
+Conf. interval & (86, 97) & (88, 94) & (83, 97) & (17, 35) & (21, 31) & (8, 25) & (4, 20) & (9, 16) & (6, 22)\\
+n & 90 & 349 & 73 & 90 & 349 & 73 & 90 & 349 & 73\\
+\hline
+Mozambique & 62 & 84 & 80 & 50 & 32 & 34 & 12 & 4 & 2\\
+Conf. interval & (19, 106) & (81, 87) & (75, 86) & (5, 95) & (26, 38) & (27, 41) & (-17, 42) & (2, 6) & (0, 4)\\
+n & 8 & 571 & 188 & 8 & 571 & 188 & 8 & 571 & 188\\
+\hline
+Nepal & 97 & 97 & 92 & 31 & 36 & 27 & 15 & 20 & 19\\
+Conf. interval & (94, 100) & (96, 98) & (87, 97) & (25, 37) & (33, 39) & (19, 36) & (10, 20) & (17, 23) & (13, 25)\\
+n & 225 & 890 & 162 & 225 & 890 & 162 & 225 & 890 & 162\\
+\hline
+Nigeria & 91 & 89 & 94 & 31 & 36 & 31 & 22 & 21 & 21\\
+Conf. interval & (87, 95) & (87, 91) & (89, 100) & (25, 38) & (33, 39) & (20, 42) & (16, 29) & (18, 23) & (11, 31)\\
+n & 178 & 1175 & 71 & 178 & 1175 & 71 & 178 & 1175 & 71\\
+\hline
+Rwanda & 98 & 98 & 100 & 22 & 28 & 29 & 10 & 11 & 10\\
+Conf. interval & (97, 100) & (97, 99) & (100, 100) & (17, 26) & (24, 31) & (12, 46) & (7, 13) & (9, 14) & (-1, 21)\\
+n & 389 & 732 & 31 & 389 & 732 & 31 & 389 & 732 & 31\\
+\hline
+Sierra Leone 1 & 96 & 94 & 94 & 36 & 38 & 27 & 24 & 20 & 22\\
+Conf. interval & (93, 99) & (92, 95) & (86, 102) & (29, 44) & (34, 41) & (12, 42) & (17, 31) & (16, 23) & (8, 36)\\
+n & 167 & 632 & 37 & 167 & 632 & 37 & 167 & 632 & 37\\
+\hline
+Sierra Leone 2 & 87 & 90 & 93 & 52 & 62 & 62 & 29 & 22 & 18\\
+Conf. interval & (78, 97) & (88, 92) & (89, 97) & (39, 66) & (58, 67) & (56, 67) & (16, 42) & (16, 28) & (12, 25)\\
+n & 63 & 1376 & 396 & 63 & 1376 & 396 & 63 & 1376 & 396\\
+\hline
+Uganda 1 & 96 & 96 & . & 34 & 36 & . & 9 & 9 & .\\
+Conf. interval & (95, 98) & (96, 97) & . & (30, 39) & (34, 39) & . & (6, 11) & (8, 11) & .\\
+n & 526 & 2218 & . & 526 & 2218 & . & 526 & 2218 & .\\
+\hline
+Uganda 2 & 97 & 96 & 97 & 20 & 30 & 28 & 8 & 11 & 13\\
+Conf. interval & (94, 99) & (95, 97) & (94, 100) & (14, 26) & (27, 33) & (21, 36) & (4, 11) & (9, 13) & (7, 19)\\
+n & 173 & 749 & 123 & 173 & 749 & 123 & 173 & 749 & 123\\
+\hline
+All LMICs & 89 & 89 & 93 & 33 & 39 & 36 & 15 & 13 & 13\\
+Conf. interval & (81, 97) & (81, 98) & (89, 98) & (25, 41) & (29, 48) & (23, 48) & (10, 20) & (8, 18) & (7, 19)\\
+n & 1838 & 8749 & 1084 & 1838 & 8749 & 1084 & 1838 & 8749 & 1084\\
+\hline
+Russia & 67 & 76 & 81 & 74 & 68 & 68 & 46 & 40 & 38\\
+Conf. interval & (59, 74) & (73, 78) & (76, 87) & (68, 81) & (66, 71) & (62, 74) & (38, 54) & (38, 43) & (32, 44)\\
+n & 552 & 5108 & 227 & 552 & 5108 & 227 & 552 & 5108 & 227\\
+\hline
+USA & 92 & 91 & 97 & 89 & 91 & 94 & 90 & 89 & 89\\
+Conf. interval & (88, 96) & (89, 94) & (95, 99) & (83, 95) & (88, 93) & (91, 97) & (85, 95) & (86, 92) & (85, 93)\\
+n & 153 & 687 & 473 & 153 & 687 & 473 & 153 & 687 & 473\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item Table 6 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine by age groups.
 The number of observations and percentage correponds only to people who would take the vaccine.
@@
 \begin{tablenotes}
-\item Table 6 shows percentage of respondents mentioning reasons why they would not take the Covid-19 vaccine.
+\item Table 7 shows percentage of respondents mentioning reasons why they would not take the Covid-19 vaccine.
 The number of observations and percentage correponds only to people who would NOT take the vaccine.
@@
 \begin{TableNotes}
-\item Table 7 shows percentage of respondents that mention actors who they would trust the most to help them decide whether to get a COVID-19 vaccine.
+\item Table 8 shows percentage of respondents that mention actors who they would trust the most to help them decide whether to get a COVID-19 vaccine.
 For all countries the questions was asked regardless if respondent would take a vaccine, would not take it, does not know or does not respond.
@@
 
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{hist\_gender}
+\end{Highlighting}
+\end{Shaded}
+
 \includegraphics{paper_files/figure-latex/genderhist-1.pdf}
@@
 Respondents were only permitted to select one most trusted  actor or institution.
-Responses are broken down by acceptance of the COVID-19 vaccine.}
+Responses are broken down by acceptance of the COVID-19 vaccine.
+The color of the bars reflect the answer given to the question ``If a COVID-19 vaccine becomes available in [country], would you take it?'' with ``No'' and ``Don't know'' pooled together and ``All'' combined average of ``Yes'' and ``No / Don't know''}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[!ht]
+\caption{Trusted actors and institutions, broken down by vaccine acceptance \label{fig:genderhist}}
+
+\includegraphics{paper_files/figure-latex/histcattrust-1.pdf}
+
+\scriptsize{Figure 5 shows histograms of actors and institutions that respondents say they would trust most to help them decide whether or not to take the COVID-19 vaccine.
+Respondents were only permitted to select one most trusted  actor or institution.
+Responses are broken down by acceptance of the COVID-19 vaccine.
+The color of the bars reflect the answer given to the question ``If a COVID-19 vaccine becomes available in [country], would you take it?'' with ``No'' and ``Don't know'' pooled together and ``All'' combined average of ``Yes'' and ``No / Don't know''}
 \end{figure}
@@
 \midrule
-0.04 & 0.01 & 0.00 & 10 & Male & Gender\\
-0.00 & 0.01 & 0.71 & 10 & 55+ & Age\\
-0.02 & 0.03 & 0.41 & 10 & Up to secondary & Education\\
+0.04 & 0.01 & 0.00 & 10 & Male & Gender (Female)\\
+-0.02 & 0.02 & 0.43 & 10 & <25 & Age (25-54)\\
+-0.02 & 0.02 & 0.36 & 10 & <25 & Age (55+)\\
+0.02 & 0.03 & 0.38 & 10 & Up to secondary & Education (Secondary +)\\
 \bottomrule
@@
 \begin{tablenotes}
-\item Table 8 shows the results of subgroup mean differences.
-Subgroup differences were generated considering only LMICs.
-The differences in means for gender and age do not include the Uganda 1 study, which only included female respondents under the age of 55.
-p-values come from a two-sided t-test from a linear regression.
+\item Table 9 shows the results of subgroup mean differences. Subgroup differences were generated considering only LMICs. p-values come from a two-sided t-test from a linear regression.
 \end{tablenotes}
@@
 \midrule
-Burkina Faso & 977 & 1.00 & 0.00 & 0.00 & 0.88\\
-Colombia & 1,012 & 0.95 & 0.00 & 0.00 & 0.32\\
-India & 3,348 & 1.00 & 0.00 & 0.78 & 0.00\\
-Mozambique & 862 & 0.98 & 0.00 & 0.04 & 0.00\\
-Nepal & 1,389 & 1.00 & 0.05 & 1.00 & 0.05\\
-Nigeria & 1,868 & 0.98 & 0.00 & 1.00 & 0.00\\
-Pakistan 1 & 1,633 & 0.99 & 0.00 & 0.01 & 0.00\\
-Pakistan 2 & 1,492 & 1.00 & 1.00 & 0.00 & 1.00\\
-Russia & 22,125 & 1.00 & 0.00 & 0.00 & 0.00\\
-Rwanda & 1,355 & 0.90 & 0.00 & 0.00 & 0.00\\
-Sierra Leone 1 & 1,070 & 1.00 & 0.00 & 0.03 & 0.00\\
-Sierra Leone 2 & 2,110 & 1.00 & 0.00 & 0.00 & 0.01\\
-Uganda 1 & 3,362 & 0.94 & 0.00 & 0.19 & 0.05\\
-Uganda 2 & 1,366 & 1.00 & 0.00 & 0.00 & 0.00\\
-USA & 1,959 & 0.91 & 0.00 & 0.00 & 0.00\\
+Burkina Faso & 977 & 99.90 & 100.00 & 100.00 & 12.28\\
+Colombia & 1,012 & 94.66 & 100.00 & 99.90 & 68.18\\
+India & 1,680 & 100.00 & 100.00 & 20.24 & 100.00\\
+Mozambique & 862 & 97.68 & 100.00 & 96.06 & 99.77\\
+Nepal & 1,389 & 100.00 & 95.32 & 0.00 & 95.32\\
+Nigeria & 1,868 & 98.18 & 100.00 & 0.00 & 100.00\\
+Pakistan 1 & 1,633 & 98.96 & 99.76 & 99.27 & 100.00\\
+Pakistan 2 & 1,492 & 99.87 & 0.00 & 100.00 & 0.00\\
+Russia & 22,125 & 100.00 & 100.00 & 100.00 & 100.00\\
+Rwanda & 1,355 & 90.18 & 100.00 & 100.00 & 100.00\\
+Sierra Leone 1 & 1,070 & 100.00 & 100.00 & 97.01 & 100.00\\
+Sierra Leone 2 & 2,110 & 99.95 & 100.00 & 100.00 & 98.91\\
+Uganda 1 & 3,362 & 94.41 & 100.00 & 81.47 & 95.12\\
+Uganda 2 & 1,366 & 99.85 & 100.00 & 100.00 & 100.00\\
+USA & 1,959 & 90.61 & 100.00 & 100.00 & 100.00\\
 \bottomrule
@@
 \begin{tablenotes}
-\item Table 9 show the percentage of observations that are not missing values for each variable included in Figure 1.
+\item Table 10 show the proportion of observations that are not missing values for each variable included in Figure 1.
 \end{tablenotes}
 \end{threeparttable}
+\end{table}
+
+\newpage
+
+\begin{table}
+
+\caption{\label{tab:countrydiff}Differences between groups within studies}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{threeparttable}
+\begin{tabular}[t]{llllrrrr}
+\toprule
+Country & Variable & Baseline category & Group & Estimate & Std. Error & p.value & Degrees of freedom\\
+\midrule
+Burkina Faso & Age & <25 & 55+ (binary measure) & -0.05 & 0.22 & 0.83 & 119\\
+Colombia & Age & <25 & 55+ (binary measure) & -0.01 & 0.05 & 0.89 & 689\\
+India & Age & <25 & 55+ (binary measure) & -0.01 & 0.03 & 0.60 & 141\\
+Mozambique & Age & <25 & 55+ (binary measure) & 0.03 & 0.02 & 0.11 & 162\\
+Nepal & Age & <25 & 55+ (binary measure) & -0.03 & 0.02 & 0.10 & 89\\
+Nigeria & Age & <25 & 55+ (binary measure) & -0.02 & 0.05 & 0.73 & 1,867\\
+Pakistan 1 & Age & <25 & 55+ (binary measure) & 0.05 & 0.08 & 0.53 & 105\\
+Russia & Age & <25 & 55+ (binary measure) & 0.12 & 0.02 & 0.00 & 22,124\\
+Rwanda & Age & <25 & 55+ (binary measure) & -0.12 & 0.07 & 0.09 & 1,354\\
+Sierra Leone 1 & Age & <25 & 55+ (binary measure) & -0.04 & 0.06 & 0.51 & 1,069\\
+Sierra Leone 2 & Age & <25 & 55+ (binary measure) & 0.03 & 0.02 & 0.08 & 190\\
+Uganda 2 & Age & <25 & 55+ (binary measure) & -0.03 & 0.03 & 0.35 & 309\\
+USA & Age & <25 & 55+ (binary measure) & 0.08 & 0.03 & 0.01 & 1,958\\
+Burkina Faso & Age & <25 & 25-54 & -0.13 & 0.10 & 0.21 & 119\\
+Colombia & Age & <25 & 25-54 & -0.01 & 0.04 & 0.79 & 689\\
+India & Age & <25 & 25-54 & 0.08 & 0.03 & 0.01 & 141\\
+Mozambique & Age & <25 & 25-54 & -0.12 & 0.01 & 0.00 & 162\\
+Nepal & Age & <25 & 25-54 & -0.01 & 0.01 & 0.32 & 89\\
+Nigeria & Age & <25 & 25-54 & 0.09 & 0.03 & 0.01 & 1,867\\
+Pakistan 1 & Age & <25 & 25-54 & -0.11 & 0.04 & 0.00 & 105\\
+Russia & Age & <25 & 25-54 & -0.06 & 0.02 & 0.01 & 22,124\\
+Rwanda & Age & <25 & 25-54 & -0.04 & 0.02 & 0.03 & 1,354\\
+Sierra Leone 1 & Age & <25 & 25-54 & 0.00 & 0.03 & 0.94 & 1,069\\
+Sierra Leone 2 & Age & <25 & 25-54 & 0.05 & 0.04 & 0.30 & 190\\
+Uganda 1 & Age & <25 & 25-54 & 0.00 & 0.02 & 0.83 & 497\\
+Uganda 2 & Age & <25 & 25-54 & 0.00 & 0.03 & 0.89 & 309\\
+USA & Age & <25 & 25-54 & 0.14 & 0.04 & 0.00 & 1,958\\
+Burkina Faso & Age & <25 & 55+ & -0.15 & 0.24 & 0.53 & 119\\
+Colombia & Age & <25 & 55+ & -0.02 & 0.06 & 0.79 & 689\\
+India & Age & <25 & 55+ & 0.05 & 0.04 & 0.19 & 141\\
+Mozambique & Age & <25 & 55+ & -0.08 & 0.02 & 0.00 & 162\\
+Nepal & Age & <25 & 55+ & -0.04 & 0.02 & 0.06 & 89\\
+Nigeria & Age & <25 & 55+ & 0.06 & 0.05 & 0.28 & 1,867\\
+Pakistan 1 & Age & <25 & 55+ & -0.06 & 0.07 & 0.45 & 105\\
+Russia & Age & <25 & 55+ & 0.07 & 0.03 & 0.03 & 22,124\\
+Rwanda & Age & <25 & 55+ & -0.15 & 0.07 & 0.04 & 1,354\\
+Sierra Leone 1 & Age & <25 & 55+ & -0.04 & 0.07 & 0.56 & 1,069\\
+Sierra Leone 2 & Age & <25 & 55+ & 0.07 & 0.05 & 0.12 & 190\\
+Uganda 2 & Age & <25 & 55+ & -0.03 & 0.04 & 0.47 & 309\\
+USA & Age & <25 & 55+ & 0.18 & 0.04 & 0.00 & 1,958\\
+Burkina Faso & Education & Secondary + & Up to secondary & 0.09 & 0.03 & 0.00 & 976\\
+Colombia & Education & Secondary + & Up to secondary & -0.05 & 0.03 & 0.10 & 1,010\\
+India & Education & Secondary + & Up to secondary & -0.02 & 0.04 & 0.59 & 100\\
+Mozambique & Education & Secondary + & Up to secondary & 0.04 & 0.03 & 0.17 & 160\\
+Pakistan 1 & Education & Secondary + & Up to secondary & -0.10 & 0.04 & 0.01 & 105\\
+Pakistan 2 & Education & Secondary + & Up to secondary & -0.07 & 0.03 & 0.00 & 1,491\\
+Russia & Education & Secondary + & Up to secondary & -0.01 & 0.01 & 0.31 & 22,124\\
+Rwanda & Education & Secondary + & Up to secondary & 0.16 & 0.03 & 0.00 & 1,354\\
+Sierra Leone 1 & Education & Secondary + & Up to secondary & 0.06 & 0.03 & 0.03 & 1,037\\
+Sierra Leone 2 & Education & Secondary + & Up to secondary & -0.01 & 0.02 & 0.63 & 190\\
+Uganda 1 & Education & Secondary + & Up to secondary & 0.05 & 0.03 & 0.12 & 494\\
+Uganda 2 & Education & Secondary + & Up to secondary & 0.11 & 0.03 & 0.00 & 309\\
+USA & Education & Secondary + & Up to secondary & -0.21 & 0.03 & 0.00 & 1,958\\
+Burkina Faso & Gender & Female & Male & 0.06 & 0.03 & 0.06 & 976\\
+Colombia & Gender & Female & Male & 0.04 & 0.03 & 0.18 & 1,011\\
+India & Gender & Female & Male & 0.02 & 0.02 & 0.22 & 141\\
+Mozambique & Gender & Female & Male & 0.05 & 0.02 & 0.02 & 162\\
+Nepal & Gender & Female & Male & 0.00 & 0.01 & 0.98 & 89\\
+Nigeria & Gender & Female & Male & 0.02 & 0.02 & 0.30 & 1,867\\
+Pakistan 1 & Gender & Female & Male & 0.08 & 0.02 & 0.00 & 105\\
+Russia & Gender & Female & Male & 0.16 & 0.01 & 0.00 & 22,124\\
+Rwanda & Gender & Female & Male & 0.09 & 0.02 & 0.00 & 1,354\\
+Sierra Leone 1 & Gender & Female & Male & 0.06 & 0.03 & 0.03 & 1,069\\
+Sierra Leone 2 & Gender & Female & Male & -0.01 & 0.02 & 0.56 & 190\\
+Uganda 2 & Gender & Female & Male & 0.03 & 0.02 & 0.17 & 309\\
+USA & Gender & Female & Male & 0.17 & 0.03 & 0.00 & 1,958\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item Table 11 shows differences of means between groups within single studies.
+Estimates are calculated through OLS and represent the difference in the average acceptance rate between the subgroup in column Group and that in column Baseline category.
+\end{tablenotes}
+\end{threeparttable}}
 \end{table}
@@
 \begin{tablenotes}
-\item Table 10 presents question wording and answer options from answers used in Figure 1 to get estimated vaccine acceptance.
+\item Table 12 presents question wording and answer options from answers used in Figure 1 to get estimated vaccine acceptance.
 Answer options are separated by a semicolon.
@@
 \begin{tablenotes}
-\item Table 11 presents question wording and answer options used in Table 2 to get an estimated percentage of reasons to take the COVID-19 vaccine.
+\item Table 13 presents question wording and answer options used in Table 2 to get an estimated percentage of reasons to take the COVID-19 vaccine.
 Columns 'Protection: self', 'Protection: family' and  'Protection: community' show the answer options that were recoded in each category.
@@
 \begin{tablenotes}
-\item Table 12 presents question wording and answer options used in Figure 2 to get an estimated percentage of reasons not to take the COVID-19 vaccine.
+\item Table 14 presents question wording and answer options used in Figure 2 to get an estimated percentage of reasons not to take the COVID-19 vaccine.
 Columns 3-10 show the answer options that were recoded in each category.
@@
 \begin{tablenotes}
-\item Table 13 presents question wording and answer options used in Figure 3 to get the percentage of respondents mentioning each actor or instituion that they would trust to decide whether to get the COVID-19 vaccine.
+\item Table 15 presents question wording and answer options used in Figure 3 to get the percentage of respondents mentioning each actor or instituion that they would trust to decide whether to get the COVID-19 vaccine.
 Columns 3-8 show the answer options that were recoded in each category.
@@
 
-\hypertarget{appendix-c-additional-contributors}{%
-\subsection*{Appendix C: Additional contributors}\label{appendix-c-additional-contributors}}
-\addcontentsline{toc}{subsection}{Appendix C: Additional contributors}
-
-We thank Sellu Kallon and Sarah Ryan for valuable intellectual contributions and research assistance.
-
-IPA would like to thank staff in Burkina Faso, Colombia, Rwanda, Sierra Leone and the United States for their intellectual contributions, research assistance, and support throughout the RECOVR survey: Achille Mignondo Tchibozo, Michael Rosenbaum, Hugo Salas, Filippo Cuccaro, Jean Leodomir Habarimana Mfura, Doug Kirke-Smith, Savanna Henderson, Shahana Hirji, Kyle Holloway, Margarita Cabra.
-
-Russia team would like to thank staff at Online Market Intelligence survey agency and Kirill Chmel and Vladimir Zabolotsky for their intellectual contributions and research assistance.
-
 \newpage
@@
 \hypertarget{appendixa}{%
-\subsection*{Appendix D: Sample descriptions}\label{appendixa}}
-\addcontentsline{toc}{subsection}{Appendix D: Sample descriptions}
+\subsection*{Appendix C: Sample descriptions}\label{appendixa}}
+\addcontentsline{toc}{subsection}{Appendix C: Sample descriptions}
 
@@
 \emph{Survey Dates:}
-Baseline: June to July 2020, Follow-up 1: October toNovember 2020, Follow-up 2: December 16, 2020 toJanuary 18, 2021.
+Baseline: June to July 2020, Follow-up 1: October to November 2020, Follow-up 2: December 16, 2020 to January 18, 2021.
 
@@
 
-\hypertarget{pakistan-economic-vulnerability-assessment-eva-subnational-sample-sheikhupura-police-study-sample-institute-of-development-and-economic-alternatives-lahore-university-of-management-science-london-school-of-economics-princeton-university}{%
-\subsubsection*{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample, Sheikhupura Police Study Sample, Institute of Development and Economic Alternatives, Lahore University of Management Science, London School of Economics, Princeton University}\label{pakistan-economic-vulnerability-assessment-eva-subnational-sample-sheikhupura-police-study-sample-institute-of-development-and-economic-alternatives-lahore-university-of-management-science-london-school-of-economics-princeton-university}}
-\addcontentsline{toc}{subsubsection}{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample, Sheikhupura Police Study Sample, Institute of Development and Economic Alternatives, Lahore University of Management Science, London School of Economics, Princeton University}
+\hypertarget{pakistan-economic-vulnerability-assessment-eva-subnational-sample-sheikhupura-police-study-sample-institute-of-development-and-economic-alternatives-lahore-university-of-management-science-london-school-of-economics-princeton-university-pakistan-1}{%
+\subsubsection*{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample, Sheikhupura Police Study Sample, Institute of Development and Economic Alternatives, Lahore University of Management Science, London School of Economics, Princeton University (Pakistan 1)}\label{pakistan-economic-vulnerability-assessment-eva-subnational-sample-sheikhupura-police-study-sample-institute-of-development-and-economic-alternatives-lahore-university-of-management-science-london-school-of-economics-princeton-university-pakistan-1}}
+\addcontentsline{toc}{subsubsection}{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample, Sheikhupura Police Study Sample, Institute of Development and Economic Alternatives, Lahore University of Management Science, London School of Economics, Princeton University (Pakistan 1)}
 
@@
 
-\hypertarget{pakistan-economic-vulnerability-assessment-eva-subnational-sample}{%
-\subsubsection*{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample}\label{pakistan-economic-vulnerability-assessment-eva-subnational-sample}}
-\addcontentsline{toc}{subsubsection}{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample}
+\hypertarget{pakistan-economic-vulnerability-assessment-eva-subnational-sample-pakistan-2}{%
+\subsubsection*{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample (Pakistan 2)}\label{pakistan-economic-vulnerability-assessment-eva-subnational-sample-pakistan-2}}
+\addcontentsline{toc}{subsubsection}{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample (Pakistan 2)}
 
@@
 Other: \emph{Moscow, Saint Petersburg, Khanty-Mansiysk Autonomous Okrug -- Ugra}.
-The remaining 24 federal subjects were excluded from the study due to inability to enroll sample size with desired characteristics (sample size, age, gender and education group composition).
+The remaining 24 federal subjects were excluded from the study due to inability to enroll sample size with desired characteristics (sample size, age, gender and education group composition) and account for less than 14\% of the total adult population of Russia.
 
@@
 
-\hypertarget{sierra-leone-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}{%
-\paragraph*{Sierra Leone, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}\label{sierra-leone-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}}
-\addcontentsline{toc}{paragraph}{Sierra Leone, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}
+\hypertarget{sierra-leone-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa-sierra-leone-1}{%
+\paragraph*{Sierra Leone, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA) (Sierra Leone 1)}\label{sierra-leone-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa-sierra-leone-1}}
+\addcontentsline{toc}{paragraph}{Sierra Leone, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA) (Sierra Leone 1)}
 
@@
 
-\hypertarget{sierra-leone-towns-that-are-candidates-for-rural-electrification-nation-wide-sample-international-growth-centre-igc-wageningen-university-research-yale-research-initiative-on-innovation-and-scale-y-rise-wzb-berlin-social-science-center-and-columbia-university}{%
-\paragraph*{Sierra Leone, Towns that are Candidates for Rural Electrification Nation-wide sample, International Growth Centre (IGC), Wageningen University \& Research, Yale Research Initiative on Innovation and Scale (Y-RISE), WZB Berlin Social Science Center and Columbia University}\label{sierra-leone-towns-that-are-candidates-for-rural-electrification-nation-wide-sample-international-growth-centre-igc-wageningen-university-research-yale-research-initiative-on-innovation-and-scale-y-rise-wzb-berlin-social-science-center-and-columbia-university}}
-\addcontentsline{toc}{paragraph}{Sierra Leone, Towns that are Candidates for Rural Electrification Nation-wide sample, International Growth Centre (IGC), Wageningen University \& Research, Yale Research Initiative on Innovation and Scale (Y-RISE), WZB Berlin Social Science Center and Columbia University}
+\hypertarget{sierra-leone-towns-that-are-candidates-for-rural-electrification-nation-wide-sample-international-growth-centre-igc-wageningen-university-research-yale-research-initiative-on-innovation-and-scale-y-rise-wzb-berlin-social-science-center-and-columbia-university-sierra-leone-2}{%
+\paragraph*{Sierra Leone, Towns that are Candidates for Rural Electrification Nation-wide sample, International Growth Centre (IGC), Wageningen University \& Research, Yale Research Initiative on Innovation and Scale (Y-RISE), WZB Berlin Social Science Center and Columbia University (Sierra Leone 2)}\label{sierra-leone-towns-that-are-candidates-for-rural-electrification-nation-wide-sample-international-growth-centre-igc-wageningen-university-research-yale-research-initiative-on-innovation-and-scale-y-rise-wzb-berlin-social-science-center-and-columbia-university-sierra-leone-2}}
+\addcontentsline{toc}{paragraph}{Sierra Leone, Towns that are Candidates for Rural Electrification Nation-wide sample, International Growth Centre (IGC), Wageningen University \& Research, Yale Research Initiative on Innovation and Scale (Y-RISE), WZB Berlin Social Science Center and Columbia University (Sierra Leone 2)}
 
@@
 
-\hypertarget{uganda-subnational-sample-international-growth-center-trinity-college-dublin-stockholm-school-of-economics-and-misum-institute-for-international-economic-studies-stockholm-university}{%
-\paragraph*{Uganda Subnational sample, International Growth Center, Trinity College Dublin, Stockholm School of Economics and Misum, Institute for International Economic Studies, Stockholm University}\label{uganda-subnational-sample-international-growth-center-trinity-college-dublin-stockholm-school-of-economics-and-misum-institute-for-international-economic-studies-stockholm-university}}
-\addcontentsline{toc}{paragraph}{Uganda Subnational sample, International Growth Center, Trinity College Dublin, Stockholm School of Economics and Misum, Institute for International Economic Studies, Stockholm University}
+\hypertarget{uganda-subnational-sample-international-growth-center-trinity-college-dublin-stockholm-school-of-economics-and-misum-institute-for-international-economic-studies-stockholm-university-uganda-1}{%
+\paragraph*{Uganda Subnational sample, International Growth Center, Trinity College Dublin, Stockholm School of Economics and Misum, Institute for International Economic Studies, Stockholm University (Uganda 1)}\label{uganda-subnational-sample-international-growth-center-trinity-college-dublin-stockholm-school-of-economics-and-misum-institute-for-international-economic-studies-stockholm-university-uganda-1}}
+\addcontentsline{toc}{paragraph}{Uganda Subnational sample, International Growth Center, Trinity College Dublin, Stockholm School of Economics and Misum, Institute for International Economic Studies, Stockholm University (Uganda 1)}
 
@@
 
-\hypertarget{uganda-subnational-sample-wzb-berlin-social-science-center-and-columbia-university-nyu-abu-dhabi-innovations-for-poverty-action-ipa}{%
-\subsubsection*{Uganda Subnational sample, WZB Berlin Social Science Center and Columbia University, NYU Abu Dhabi, Innovations for Poverty Action (IPA)}\label{uganda-subnational-sample-wzb-berlin-social-science-center-and-columbia-university-nyu-abu-dhabi-innovations-for-poverty-action-ipa}}
-\addcontentsline{toc}{subsubsection}{Uganda Subnational sample, WZB Berlin Social Science Center and Columbia University, NYU Abu Dhabi, Innovations for Poverty Action (IPA)}
+\emph{IRB Approval:} Mildmay Uganda Research Ethics Committee (protocol number 0109-2015) on September 21, 2020.
+
+\hypertarget{uganda-subnational-sample-wzb-berlin-social-science-center-and-columbia-university-nyu-abu-dhabi-innovations-for-poverty-action-ipa-uganda-2}{%
+\subsubsection*{Uganda Subnational sample, WZB Berlin Social Science Center and Columbia University, NYU Abu Dhabi, Innovations for Poverty Action (IPA) (Uganda 2)}\label{uganda-subnational-sample-wzb-berlin-social-science-center-and-columbia-university-nyu-abu-dhabi-innovations-for-poverty-action-ipa-uganda-2}}
+\addcontentsline{toc}{subsubsection}{Uganda Subnational sample, WZB Berlin Social Science Center and Columbia University, NYU Abu Dhabi, Innovations for Poverty Action (IPA) (Uganda 2)}
 

### 2021-06-10 2_tables.R

@@ -1,16 +1,16 @@
----
-title: 'COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging: Replication Code'
-date: "30 April 2021"
-output:
-  html_document:
-    number_sections: yes
-    theme: cosmo
-    code_folding: hide
-    toc: yes
-  bookdown::html_document2: default
----
-
-```{r setup3, include=FALSE}
+#' ---
+#' title: 'COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging: Replication Code'
+#' date: "30 April 2021"
+#' output:
+#'   html_document:
+#'     number_sections: yes
+#'     theme: cosmo
+#'     code_folding: hide
+#'     toc: yes
+#'   bookdown::html_document2: default
+#' ---
+#' 
+## ----setup3, include=FALSE----------------------------------------------------
 knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
 
 if (!require(pacman)) install.packages("pacman")
@@ -23,16 +23,16 @@ options(knitr.kable.NA = '.')
 
 base_font_size <- 12
 
-```
 
-
-# Set up
-
-This code takes cleaned and aggregated data as input. Cleaning and aggregation is done in `1_cleaning.Rmd`.
-
-## Helper functions
-
-```{r}
+#' 
+#' 
+#' # Set up
+#' 
+#' This code takes cleaned and aggregated data as input. Cleaning and aggregation is done in `1_cleaning.Rmd`.
+#' 
+#' ## Helper functions
+#' 
+## -----------------------------------------------------------------------------
 
 # The helper renormalizes weights so that each study gets the 
 # same total weight even if they are missing data
@@ -111,11 +111,11 @@ age_analysis <- function(df, reason, num = "Yes", filter_by=NA){
                 weight = weight, se_type = "stata"), .groups = "drop")
 }
 
-```
 
-## Final cleaning and harmonization of weights
-
-```{r df2}
+#' 
+#' ## Final cleaning and harmonization of weights
+#' 
+## ----df2----------------------------------------------------------------------
 
 # Call data created in 1_cleaning.Rmd
 df <- readr::read_csv("2_rep_data/combined.csv", guess_max = 30000)
@@ -163,15 +163,15 @@ df2 <-
     cluster = if_else(group == "All", 
[…]

### 2021-06-22 2_tables.Rmd
update

@@
 ---
-title: 'COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging: Replication Code'
-date: "30 April 2021"
+title: 'COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries: Replication Code'
+date: "`r format(Sys.time(), '%d %B, %Y')`"
 output:
@@
 
+Code used to prepare data (prepare survey weights), run analyses and robustness checks.
+
 ```{r}
@@
     {bind_cols( tidy(.), n = nobs(.) )}
+}
+
+# Leave-X-out helper that takes data and sample_var, 
+# nests by sample_var performs LOO with loo_n observations out
+# applying loo_fun to each sample
+
+loo_helper <- 
+  function(data, 
+           sample_var, 
+           loo_n = 1,
+           loo_fun = 
+             function(dat) lm_helper(data = dat, 
+                                     formula = take_vaccine_num ~ 1, cluster = cluster,
+                                     weight = weight, se_type = "stata")
+  ) {
+
+  .var <- data[[sample_var]]
+
+  data %>% 
+    {
+      plyr::adply(.data = combn(unique(.var), loo_n), 
+                  .margins = 2, 
+                  .fun = function(x) loo_fun(.[!(.var %in% x), ]) )
+    }
 }
@@
 
+Groups variables into discrete categories and prepares survey weights.
+
 ```{r df2}
@@
 # Call data created in 1_cleaning.Rmd
-df <- readr::read_csv("2_rep_data/combined.csv", guess_max = 30000)
+df <- readr::read_csv("3_rep_data/combined.csv", guess_max = 30000)
 
@@
     age_groups_binary = ifelse(age < 55, "<55", age_groups_binary),
-    age_less24=ifelse(age<=24, 1, 0),
-    age_25_54=ifelse(age>=25 & age<=54, 1, 0),
-    age_55_more=ifelse(age>=55, 1, 0),
-    age_groups_three=ifelse(age<=24, "<25", NA),
-    age_groups_three=ifelse(age>=25 & age<=54, "25-54", age_groups_three),
-    age_groups_three=ifelse(age>=55, "55+", age_groups_three),
+    age_less24 = ifelse(age <= 24, 1, 0),
+    age_25_54 = ifelse(age >= 25 & age <= 54, 1, 0),
+    age_55_more = ifelse(age >= 55, 1, 0),
+    age_groups_three = ifelse(age <= 24, "<25", NA),
+    age_groups_three = ifelse(age >= 25 & age <= 54, "25-54", age_groups_three),
+    age_groups_three = ifelse(age >= 55, "55+", age_groups_three),
     educ_binary = if_else(educ == "More than secondary", "> Secondary", "Up to Secondary"))
@@
     general_title = "",
-    general = "Table 10 show the proportion of observations that are not missing values for each variable included in Figure 1.",
+    general = "Table S8 show the proportion of observations that are not missing values for each variable included in Figure 1.",
     threeparttable = T)
@@
     general_title = "",
-    general = "Table 9 show the percentage of observations that are not missing values for each variable included in Figure 1.",
+    general = "Table S8 show the percentage of observations that are not missing values for each variable included in Figure 1.",
     threeparttable = T)
@@
 
-## Table 1: Vaccine data from WGM, WHO
+## Table 2: Vaccine data from WGM, WHO
 
@@
 # Call data from WGM
-dfwgm <- read.csv("2_rep_data/table_wgm.csv")
+dfwgm <- read.csv("3_rep_data/table_wgm.csv")
 
 # Call data from WHO
-df_vacc_coveragebis <- read.csv("2_rep_data/vacc_cov.csv")
+df_vacc_coveragebis <- read.csv("3_rep_data/vacc_cov.csv")
 
@@
     general_title = "",
-    general = "Table 1 presents an overview of vaccination beliefs and incidence across countries in our sample.
+    general = "Table 2 presents an overview of vaccination beliefs and incidence across countries in our sample.
 Columns 2-4 and 8 use data from the Wellcome Global Monitor 2018.
@@
     general_title = "",
-    general = "Table 1 presents an overview of vaccination beliefs and incidence across countries in our sample.
+    general = "Table 2 presents an overview of vaccination beliefs and incidence across countries in our sample.
 Columns 2-5 use data from the Wellcome Global Monitor 2018.
@@
 tab_sampling <- 
-  readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
+  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select("Study" = "country", "Date"="date",
@@
 
-readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
+readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select("Study" = "country", "Date"="date",
@@
   kableExtra::row_spec(0, bold = TRUE) %>% 
-  kableExtra::column_spec(1, width = "8em") %>%
-  kableExtra::column_spec(2, width = "12em")  %>%
-  kableExtra::column_spec(3, width = "30em")
+  kableExtra::column_spec(1:2, width = "8em") %>%
+  kableExtra::column_spec(3, width = "12em")  %>%
+  kableExtra::column_spec(4, width = "30em") %>% 
+  kableExtra::landscape()
 ```
@@
 
-### Figure
+### Figure 1
 
@@
 # Education (all original categories and binary recoding)
-acc_by_educ        <- grp_analysis(df2, y = "take_vaccine_num", x = "educ")
 acc_by_educ_binary <- grp_analysis(df2, y = "take_vaccine_num", x = "educ_binary")
@@
     acc_by_educ_binary %>% rename(cat = educ_binary) %>% mutate(var = "By education"),
-    acc_by_age_binary %>% rename(cat = age_groups_binary) %>% mutate(var = "By age")) %>%
+    acc_by_age %>% rename(cat = age_groups_three) %>% mutate(var = "By age")) %>%
   dplyr::mutate(across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 1)))
@@
 tags <- 
-  readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
+  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select(group = country, tag = "Geographic scope") %>%
@@
       cat, ordered = TRUE,
-      levels = rev(c(c("Female", "Male", "Up to Secondary", 
-                       "> Secondary", "<55", "55+", "All"))),
+      levels = rev(c("Female", "Male", "Up to Secondary", 
+                       "> Secondary", "<25", "25-54", "55+", "All")),
       labels = rev(c("Female", "Male", "Up to Secondary", 
-                     "More than Secondary", "$< 55$", "$55 +$", "All"))),
+                     "More than Secondary", "$< 25$", "$25-54$", "$55 +$", "All"))),
     tag = gsub(pattern = " \\(", "\\\n\\(", tag))
@@
              levels = rev(c(sort(unique(tag)[!(unique(tag) %in% special_cases)]), special_cases))))
+
+ans_loo <- ans
+
+#Add a row averaging over only national samples
+
+nationals <- df2 %>%
+  filter(country=="Burkina Faso" |
+           country=="Colombia" |
+           country=="Rwanda" |
+           country=="Sierra Leone 1" |
+           country=="Sierra Leone 2")
+
+main_results_n <- 
+  nationals %>% 
+  dplyr::filter(dplyr::if_all(c(take_vaccine_num, cluster, weight), ~ !is.na(.))) %>% 
+  dplyr::nest_by(group) %>%
+  dplyr::summarize(
+    lm_helper(data = data, 
+              formula = take_vaccine_num ~ 1, cluster = cluster,
+              weight = weight, se_type = "stata"),
+    .groups = "drop")
+
+# Gender
+acc_by_gender_n <- grp_analysis(nationals, y = "take_vaccine_num", x = "gender")
+
+# Education (all original categories and binary recoding)
+acc_by_educ_binary_n <- grp_analysis(nationals, y = "take_vaccine_num", x = "educ_binary")
+
+# Age (all original categories and binary recoding)
+acc_by_age_n <- grp_analysis(nationals, y = "take_vaccine_num", x = "age_groups_three") %>%
+  dplyr::filter(statistic!=Inf) %>%
+  dplyr::filter(conf.low>0)
+
+ans_n <- 
+  dplyr::bind_rows(
+    main_results_n %>% mutate(cat = "All", var = "All"),
+    acc_by_gender_n %>% rename(cat = gender) %>% mutate(var = "By gender"),
+    acc_by_educ_binary_n %>% rename(cat = educ_binary) %>% mutate(var = "By education"),
+    acc_by_age_n %>% rename(cat = age_groups_three) %>% mutate(var = "By age")) %>%
+  dplyr::mutate(across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 1))) %>%
+  filter(group=="All") %>%
+  mutate(group="All LMICs (National samples)",
+         tag="All LMICs (National samples)")
+
+# Prepare df to plot. Important but ugly relevel of factors, happening all over the code
+
+ans_n %<>% 
+  # group_by(var) %>% 
+  # arrange(cat) %>%
+  dplyr::mutate(
+    var = factor(var, levels = c("All", "By gender", "By education", "By age")),
+    cat = factor(
+      cat, ordered = TRUE,
+      levels = rev(c(c("Female", "Male", "Up to Secondary", 
+                       "> Secondary", "<25", "25-54", "55+", "All"))),
+      labels = rev(c("Female", "Male", "Up to Secondary", 
+                     "More than Secondary", "$< 25$", "$25-54$", "$55 +$", "All"))),
+    tag = gsub(pattern = " \\(", "\\\n\\(", tag)) %>%
+  bind_rows(ans)
+
+special_cases <- 
+  sort(unique(ans_n$tag)[grep(unique(ans_n$tag), pattern = "All LMICs (National samples)|All LMICs|Russia|USA")])
+
+ans_n %<>% 
+  dplyr::mutate(
+    tag = 
+      factor(x = tag, ordered = TRUE,
+             levels = rev(c(sort(unique(tag)[!(unique(tag) %in% special_cases)]), special_cases))))
+
+ans_national <- ans_n %>% filter(group == "All LMICs (National samples)" & cat=="All")
 
@@
 
-#Plot
-fig_1 <- 
-  ans %>% 
+fig_1_ages <- 
+  ans_n %>% 
   ggplot(data = ., aes(x = tag, y = estimate, color = cat)) + 
@@
   guides(color = guide_legend(reverse = TRUE, nrow = 2)) +
+  geom_vline(xintercept = 4.5, color = "darkgrey") +
   geom_vline(xintercept = 3.5, color = "darkgrey") +
@@
 
-fig_1
-```
-
-```{r fig1ages}
-
-# Put them together in a single df. Make estimates "percentages" and round
-
-ans <- 
-  dplyr::bind_rows(
-    main_results %>% mutate(cat = "All", var = "All"),
-    acc_by_gender %>% rename(cat = gender) %>% mutate(var = "By gender"),
-    acc_by_educ_binary %>% rename(cat = educ_binary) %>% mutate(var = "By education"),
-    acc_by_age %>% rename(cat = age_groups_three) %>% mutate(var = "By age")) %>%
-  dplyr::mutate(across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 1)))
-
-# Join with a tags df, which includes details on the study (national or subnational)
-tags <- 
-  readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
-  dplyr::select(group = country, tag = "Geographic scope") %>%
-  dplyr::left_join(filter(ans, cat == "All"), by = "group") %>%
-  dplyr::mutate(tag = paste0(group, " (", tag, ", ", n, ")")) %>%
-  dplyr::select(group, tag)
-
-# Prepare df to plot. Important but ugly relevel of factors, happening all over the code
-
-ans %<>% 
-  dplyr::left_join(tags) %>%
-  dplyr::mutate(tag = ifelse(group == "All", "All LMICs", tag)) %>%
-  # group_by(var) %>% 
-  # arrange(cat) %>%
-  dplyr::mutate(
-    var = factor(var, levels = c("All", "By gender", "By education", "By age")),
-    cat = factor(
-      cat, ordered = TRUE,
-      levels = rev(c(c("Female", "Male", "Up to Secondary", 
-                       "> Secondary", "<25", "25-54", "55+", "All"))),
-      labels = rev(c("Female", "Male", "Up to Secondary", 
-                     "More than Secondary", "$< 25$", "$25-54$", "$55 +$", "All"))),
-    tag = gsub(pattern = " \\(", "\\\n\\(", tag))
-
-special_cases <- 
-  sort(unique(ans$tag)[grep(unique(ans$tag), pattern = "All LMICs|Russia|USA")])
-
-ans %<>% 
-  dplyr::mutate(
-    tag = 
-      factor(x = tag, ordered = TRUE,
-             levels = rev(c(sort(unique(tag)[!(unique(tag) %in% special_cases)]), special_cases))))
-
-#Colour blind palette (available palletes are smaller so we expand it)
-safe_colorblind_palette <- c("#CC6677", "#DDCC77", "#117733", "#332288", "#AA4499", 
-                             "#44AA99", "#999933", "#882255", "#661100", "#6699CC", "#888888", 
-                             "#88CCEE")
-
-#Plot
-fig_1_ages <- 
-  ans %>% 
-  ggplot(data = ., aes(x = tag, y = estimate, color = cat)) + 
-  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
-                size = .5, width = .2, position = position_dodge(0.6)) + 
-  geom_point(position = position_dodge(0.6)) +
-  facet_grid(. ~ var, scales = "free_x", space = "free") + 
-  coord_flip() +
-  guides(color = guide_legend(reverse = TRUE, nrow = 2)) +
-  geom_vline(xintercept = 3.5, color = "darkgrey") +
-  geom_vline(xintercept = 2.5, color = "darkgrey") +
-  scale_colour_manual(values = safe_colorblind_palette) +
-  labs(title = "If a COVID-19 vaccine becomes available in [country], would you take it?", 
-       color = "Subgroups", x = "") +
-  theme_bw(base_size = (base_font_size - 2)) + ylim(c(0,100)) +
-  theme(legend.position = "bottom",
-        plot.caption = element_text(hjust = 0), #Default is hjust=1
-        plot.title.position = "plot", #NEW parameter. Apply for subtitle too.
-        plot.caption.position =  "plot",
-        axis.text.y = element_text(hjust = 0))
-
 fig_1_ages
+
 ```
@@
 ```
+
+### Robustness check using leave-m-out approach
+
+The main estimates for average LMIC acceptance do not vary strongly if we exclude one or two samples at a time and re-estimate average each time
+
+```{r loo_main, fig.width=10, fig.height=7}
+
+loo_estimates <- 
+  plyr::ldply(
+    .data = list(1,2), 
+    .fun = function(x) {
+      df %>% 
+        dplyr::filter(dplyr::if_all(c(take_vaccine_num, cluster, weight), ~ !is.na(.))) %>% 
+        dplyr::filter(!(country %in% c("USA", "Russia"))) %>% 
+        loo_helper(., "country", loo_n = x) %>% 
+        dplyr::mutate(m = paste0("Leaving ", x, " out"), tag = "All", var = "All")
+    })
+
+loo_estimates <- 
+  plyr::mdply(
+    .data = expand_grid(x = c(1,2), var = c("gender", "educ_binary", "age_groups_three")), 
+    .fun = function(x, var) {
+      df2 %>% 
+        dplyr::filter(dplyr::if_all(c(take_vaccine_num, cluster, weight), ~ !is.na(.))) %>% 
+        dplyr::filter(group == "All") %>% 
+        loo_helper(., "country", 
+                   loo_n = x, 
+                   loo_fun = function(dat) grp_analysis(dat, y = "take_vaccine_num", x = var)) %>% 
+        dplyr::mutate(m = paste0("Leaving ", x, " out"), var = var)
+    }) %>% 
+  dplyr::mutate(tag = dplyr::coalesce(gender, educ_binary, age_groups_three),
+                var = plyr::mapvalues(var, 
+                                      from = c("gender", "educ_binary", "age_groups_three"),
+                                      to = c("By gender", "By education", "By age"))) %>%
+  dplyr::bind_rows(loo_estimates, .)
+
+loo_estimates %<>% 
+  dplyr::mutate(
+    var = factor(var, levels = c("All", "By gender", "By education", "By age")),
+    tag = factor(
+      tag, ordered = TRUE,
+      levels = rev(c("Female", "Male", "Up to Secondary", 
+                       "> Secondary", "<25", "25-54", "55+", "All")),
+      labels = rev(c("Female", "Male", "Up to Secondary", 
+                     "More than Secondary", "$< 25$", "$25-54$", "$55 +$", "All")))
+  ) %>% 
+  dplyr::select(var, m, tag, estimate)
+
+safe_colorblind_palette <- c("#CC6677", "#DDCC77", "#117733", "#332288", "#AA4499", 
+                             "#44AA99", "#999933", "#882255", "#661100", "#6699CC", "#888888", 
+                             "#88CCEE")
+
+ans_loo %<>% 
+  dplyr::filter(group %in% c("All", "USA", "Russia")) %>% 
+  dplyr::mutate(group = plyr::mapvalues(group, from = "All", to = "All LMIC"),
+                tag = cat)
+
+fig_hist_loo <- 
+  loo_estimates %>%
+  dplyr::mutate(estimate = estimate*100) %>% 
+  ggplot(aes(estimate, color = tag, fill = tag)) + 
+  geom_histogram(aes(y = ..density..), bins = 200, 
+                 position = "dodge", alpha = .3, size = .3) +
+  geom_vline(data = ans_loo, 
+             aes(xintercept = estimate, color = cat, linetype = group), size = .9) +
+  facet_grid_paginate(var + tag ~ m)  +
+  scale_color_manual(
+    name = "Subgroups", 
+    values = safe_colorblind_palette) + 
+  scale_fill_manual(
+    name = "Subgroups", 
+    values = safe_colorblind_palette) + 
+  scale_linetype_manual(
+    name = "Sample Average", 
+    values = c("solid", "11", "dashed")) + 
+  scale_x_continuous(n.breaks = 8, name = "estimate") +
+  scale_y_continuous(labels = scales::percent_format(scale = 1, suffix = "", accuracy = 0.1)) +
+  labs(title = "",
+       x = "") +
+  guides(color = guide_legend(reverse = TRUE, nrow = 2, keyheight = 1),
+         fill = guide_legend(reverse = TRUE, nrow = 2, keyheight = 1),
+         linetype = guide_legend(keyheight = 2)) +
+  theme_bw(base_size = (base_font_size - 2)) +
+  theme(legend.position = "bottom")
+
+fig_hist_loo
+```
+
 ### Differences in means
@@
          Std.error = std.error,
-         P.value = p.value,
+         `P-value` = p.value,
          "Degrees of freedom" = df,
@@
 
-dmeans <- diffmeans %>%
-  filter(Variable!="") %>%
-  knitr::kable(
-    digits = 2,
-    caption =  "Differences in means",
-    format = "latex", booktabs = T, linesep = "", label = "dmeans", align = "c") %>% 
-  kableExtra::kable_styling(latex_options = c("hold_position"),
-    font_size = base_font_size - 2, full_width = FALSE) %>%
-  kableExtra::row_spec(0, bold = TRUE) %>% 
-  kableExtra::footnote(
-    general_title = "",
-    general = "Table 9 shows the results of subgroup mean differences. Subgroup differences were generated considering only LMICs. p-values come from a two-sided t-test from a linear regression.",
-    threeparttable = T)
-
-diffmeans %>%
-  filter(Variable!="") %>%
-  knitr::kable(
-  caption =  "Differences in means",
-  booktabs = T, linesep = "", label = "dmeans", digits = 2) %>% 
-  kableExtra::kable_styling(full_width = FALSE) %>%
-  kableExtra::row_spec(0, bold = TRUE) %>% 
-  kableExtra::footnote(
-    general_title = "",
-    general = "Table 8 shows the results of subgroup mean differences.
-Subgroup differences were generated considering only LMICs.
-The differences in means for gender and age do not include the Uganda 1 study, which only included female respondents under the age of 55.",
-    threeparttable = T)
-
-```
-
-### Differences in means: Age with three categories
-
-```{r}
-
 diffmeans <- 
   diffmeans %>%
-  filter(Variable!="Age") %>%
+  filter(Variable != "Age") %>%
   dplyr::mutate(
@@
 dmeans <- diffmeans %>%
-  filter(Variable!="") %>%
+  filter(Variable != "") %>%
   knitr::kable(
@@
     general_title = "",
-    general = "Table 9 shows the results of subgroup mean differences. Subgroup differences were generated considering only LMICs. p-values come from a two-sided t-test from a linear regression.",
+    general = "Table S7 shows the results of subgroup mean differences. Subgroup differences were generated considering only LMICs. p-values come from a two-sided t-test from a linear regression.",
     threeparttable = T)
@@
 diffmeans %>%
-  filter(Variable!="") %>%
+  filter(Variable != "") %>%
   knitr::kable(
@@
     general_title = "",
-    general = "Table 8 shows the results of subgroup mean differences.
+    general = "Table S7 shows the results of subgroup mean differences.
 Subgroup differences were generated considering only LMICs.
@@
 
-    lapply(c("gender", "age_groups_binary", "age_groups_three", "educ_binary"), function(i){
+    lapply(c("gender", "age_groups_three", "educ_binary"), function(i){
       if (length(table(dff[[i]])) < 2)  {
@@
                             data = dff) 
-          m %>% tidy %>%
+          m %>% 
+            tidy %>%
             dplyr::select(estimate, std.error, p.value, df, term) %>%
-          mutate(n = m$nobs)
+            dplyr::mutate(n = m$nobs)
         }}
@@
   dplyr::mutate(significant = p.value <= .05) %>%
-  dplyr::mutate(term=ifelse(term=="age_groups_three25-54", "25-54", term),
-                term=ifelse(term=="age_groups_three55+", "55+", term),
-                term=ifelse(term=="educ_binaryUp to Secondary", "Up to secondary", term),
-                term=ifelse(term=="age_groups_binary55+", "55+ (binary measure)", term),
-
-                term=ifelse(term=="genderMale", "Male", term))
+  dplyr::mutate(
+    term = ifelse(term == "age_groups_three25-54", "25-54", term),
+    term = ifelse(term == "age_groups_three55+", "55+", term),
+    term = ifelse(term == "educ_binaryUp to Secondary", "Up to secondary", term),
+    term = ifelse(term == "genderMale", "Male", term))
 
@@
 
-t_country_differences1 <- country_differences %>%
-  dplyr::filter(!grepl("55+ (binary measure)", term))%>%
-  dplyr::mutate(
-                baseline=ifelse(term=="Male", "Female", NA),
-                baseline=ifelse(term=="Up to secondary", "Secondary +", baseline),
-                baseline=ifelse(is.na(baseline), "<25", baseline),
-                group=ifelse(baseline=="<25", "Age", NA),
-                group=ifelse(baseline=="Secondary +", "Education", group),
-                group=ifelse(baseline=="Female", "Gender", group),
-                estimate=round(estimate, 2),
-                std.error=round(std.error, 2),
-                p.value=round(p.value, 2)) %>%
-  dplyr::select(country, group, baseline, term, everything(), - significant)
-
-t_country_differences <- t_country_differences1 %>%
+t_country_differences <- country_differences %>%
+  dplyr::mutate(
+                baseline = ifelse(term == "Male", "Female", NA),
+                baseline = ifelse(term == "Up to secondary", "Secondary +", baseline),
+                baseline = ifelse(is.na(baseline), "<25", baseline),
+                group = ifelse(baseline == "<25", "Age", NA),
+                group = ifelse(baseline == "Secondary +", "Education", group),
+                group = ifelse(baseline == "Female", "Gender", group),
+                estimate = round(estimate, 2),
+                std.error = round(std.error, 2),
+                p.value = round(p.value, 2)) %>%
+  dplyr::select(country, group, baseline, term, everything(), -significant)
+
+t_country <- t_country_differences %>%
   kable(digits = 2, 
-        col.names= c("Country", "Variable", "Baseline category", "Group", "Estimate", "Std. Error", "p.value", "Degrees of freedom"),
+        col.names = c("Country", "Variable", "Baseline category", "Group", "Estimate", "Std. Error", "P-value", "Degrees of freedom", "N Obs"),
         caption = "Differences between groups within studies", 
@@
   kableExtra::kable_styling(latex_options = c("scale_down"), font_size = base_font_size - 2, full_width = FALSE) %>% 
-  kableExtra::footnote(
-    general_title = "",
-    general = "Table 11 shows differences of means between groups within single studies.
-Estimates are calculated through OLS and represent the difference in the average acceptance rate between the subgroup in column Group and that in column Baseline category.",
+  kableExtra::row_spec(0, bold = TRUE) %>% 
+  kableExtra::column_spec(1, width = "6em") %>% 
+  kableExtra::column_spec(2:3, width = "6em") %>% 
+  kableExtra::column_spec(4, width = "9em")  %>% 
+  kableExtra::column_spec(5:8, width = "6em") %>% 
+  kableExtra::footnote(
+    general_title = "",
+    general = "Table S9 shows differences of means between groups within single studies.
+Estimates are calculated through OLS and represent the difference in the average acceptance rate between the subgroup in column Group and that in column Baseline category.
+p-values come from a two-sided t-test from a linear regression.",
     threeparttable = T)
 
-knitr::kable(t_country_differences1, 
+knitr::kable(t_country_differences, 
              digits = 2, caption = "Differences between groups within studies ")
@@
   sei = main_results %>% filter(!(group %in% c("USA", "Russia", "All"))) %>% pull(std.error))
-mp_tau =  mp$results[2,1]
+mp_tau <- mp$results[2,1]
+mp_ratio <- sqrt(mp$results[2,1])/mp$results[1,1]
 
@@
 age_table <- 
-  acc_by_age_binary %>%
-  dplyr::mutate(
-    across(c(estimate, conf.low, conf.high), ~ format(round(100 * ., 1), nsmall = 1)),
-    conf_int = paste0("(", conf.low, ", ", conf.high, ")")) %>%
-  dplyr::select(group, age_groups_binary, estimate, conf_int) %>% 
-  tidyr::pivot_wider(names_from = age_groups_binary, 
-                     values_from = c(estimate, conf_int), 
-                     names_sep = "__")
-
-age_table <- 
   acc_by_age %>%
@@
 
+main_table_n <- 
+  main_results_n %>%
+  dplyr::mutate(
+    across(c(estimate, conf.low, conf.high), list("_main" = ~ format(round(100 * ., 1), nsmall = 1))),
+    conf_int__main = paste0("(", conf.low__main, ", ", conf.high__main, ")")) %>%
+  dplyr::select(group, estimate__main, conf_int__main)
+
+gender_table_n <- 
+  acc_by_gender_n %>%
+  dplyr::mutate(
+    across(c(estimate, conf.low, conf.high), ~ format(round(100 * ., 1), nsmall = 1)),
+    conf_int = paste0("(", conf.low, ", ", conf.high, ")")) %>%
+  dplyr::select(group, gender, estimate, conf_int) %>% 
+  tidyr::pivot_wider(names_from = gender, 
+                     values_from = c(estimate, conf_int), 
+                     names_sep = "__")
+
+educ_table_n <- 
+  acc_by_educ_binary_n %>%
+  dplyr::mutate(
+    across(c(estimate, conf.low, conf.high), ~ format(round(100 * ., 1), nsmall = 1)),
+    conf_int = paste0("(", conf.low, ", ", conf.high, ")")) %>%
+  dplyr::select(group, educ_binary, estimate, conf_int) %>% 
+  tidyr::pivot_wider(names_from = educ_binary, 
+                     values_from = c(estimate, conf_int), 
+                     names_sep = "__")
+
+age_table_n <- 
+  acc_by_age_n %>%
+  dplyr::mutate(
+    across(c(estimate, conf.low, conf.high), ~ format(round(100 * ., 1), nsmall = 1)),
+    conf_int = paste0("(", conf.low, ", ", conf.high, ")")) %>%
+  dplyr::select(group, age_groups_three, estimate, conf_int) %>% 
+  tidyr::pivot_wider(names_from = age_groups_three, 
+                     values_from = c(estimate, conf_int), 
+                     names_sep = "__")
+
+all_tables_n <- 
+  main_table_n %>% 
+  dplyr::left_join(gender_table_n) %>%
+  dplyr::left_join(educ_table_n) %>% 
+  dplyr::left_join(age_table_n) %>%
+  dplyr::filter(group=="All") %>%
+  dplyr::mutate(group="All LMICs (National)")
+
 all_tables <- 
@@
   dplyr::left_join(age_table) %>%
+  dplyr::bind_rows(all_tables_n) %>%
   dplyr::select(group, everything()) %>%
   dplyr::mutate(group = as.factor(group),
-                group = forcats::fct_relevel(group, "All", "Russia", "USA", after = Inf)) %>% 
+                group = forcats::fct_relevel(group, "All", "All LMICs (National)", "Russia", "USA", after = Inf)) %>% 
   dplyr::arrange(group) %>% 
@@
     general_title = "",
-    general = "Table 4 shows percentage of respondents willing to take the COVID-19 vaccine as plotted in Figure 1. A 95% confidence interval is shown between parentheses",
+    general = "Table S1 shows percentage of respondents willing to take the COVID-19 vaccine as plotted in Figure 1. A 95% confidence interval is shown between parentheses.",
     threeparttable = T)
@@
     general_title = "",
-    general = "Table 4 shows percentage of respondents willing to take the COVID-19 vaccine as plotted in Figure 1. A 95% confidence interval is shown between parentheses",
+    general = "Table S1 shows percentage of respondents willing to take the COVID-19 vaccine as plotted in Figure 1. A 95% confidence interval is shown between parentheses",
     threeparttable = T)
@@
     general_title = "",
-    general = "Table 3 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
+    general = "Table S2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
 The number of observations and percentage corresponds only to people who would take the vaccine.
@@
     general_title = "",
-    general = "Table 2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
+    general = "Table S2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
 The number of observations and percentage correponds only to people who would take the vaccine.
@@
     general_title = "",
-    general = "Table 5 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
+    general = "Table S3 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
 The number of observations and percentage correponds only to people who would take the vaccine.
 Respondents in all countries could give more than one reason.
-A 95% confidence interval is shown between parentheses",
+A 95% confidence interval is shown between parentheses.",
     threeparttable = T)
@@
     general_title = "",
-    general = "Table 6 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine by age groups.
+    general = "Table S4 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine by age groups.
 The number of observations and percentage correponds only to people who would take the vaccine.
 Respondents in all countries could give more than one reason.
-A 95% confidence interval is shown between parentheses",
+A 95% confidence interval is shown between parentheses.",
     threeparttable = T)
@@
     general_title = "",
-    general = "Table 2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
+    general = "Table S4 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine by age groups.
 The number of observations and percentage correponds only to people who would take the vaccine.
 Respondents in all countries could give more than one reason.
-A 95% confidence interval is shown between parentheses.
-Studies India, Pakistan 1 and Pakistan 2 are not included because they either did not include the question or were not properly harmonized with the other studies.",
+A 95% confidence interval is shown between parentheses.",
     threeparttable = T)
@@
 #Import df with tags (names of categories)
-dictionary <- read_excel("1_input_data/dictionary.xlsx")
+dictionary <- read_excel("2_input_data/dictionary.xlsx")
 
@@
   dplyr::mutate(
-    size = cut(n_sub, c(0, 50, 500, Inf), right = FALSE, include.lowest = FALSE),
-    size = forcats::fct_recode(size, "500+" = "[500,Inf)"),
+    name=ifelse(group!="All", paste0(group, " (n=", n, ")"), "All"),
+    name= gsub(pattern = " \\(", "\\\n\\(", name),
     tag = as.factor(tag),
@@
 
+special_cases <- 
+  sort(unique(no_vacc$name)[grep(unique(no_vacc$name), pattern = "All|Russia|USA")])
+
+no_vacc %<>% 
+  dplyr::mutate(
+    name = 
+      factor(x = name, ordered = TRUE,
+             levels = rev(c(sort(unique(name)[!(unique(name) %in% special_cases)]), special_cases))))
+
 fig_2 <- 
@@
   dplyr::filter(!is.na(n_sub)) %>%
-  dplyr::mutate(group = plyr::mapvalues(group, "All", "All LMICs")) %>% 
-  ggplot(aes(group, estimate, color = tag)) + 
+  dplyr::mutate(name = plyr::mapvalues(name, "All", "All LMICs")) %>% 
+  ggplot(aes(name, estimate, color = tag)) + 
   geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
                 size = .5, width = .2, position = position_dodge(0.6)) + 
-  geom_point(shape = 16, position = position_dodge(0.6), aes(size = size)) +
+  geom_point(shape = 16, position = position_dodge(0.6)) +
   facet_grid(.~tag,  space = "free", labeller = label_wrap_gen(width = 15)) +
@@
     general_title = "",
-    general = "Table 7 shows percentage of respondents mentioning reasons why they would not take the Covid-19 vaccine.
+    general = "Table S5 shows percentage of respondents mentioning reasons why they would not take the Covid-19 vaccine.
 The number of observations and percentage correponds only to people who would NOT take the vaccine.
 Respondents in all countries could give more than one reason.
-A 95% confidence interval is shown between parentheses",
+A 95% confidence interval is shown between parentheses.",
     threeparttable = T)  %>%
@@
     general_title = "",
-    general = "Table 6 shows percentage of respondents mentioning reasons why they would not take the Covid-19 vaccine.
+    general = "Table S5 shows percentage of respondents mentioning reasons why they would not take the Covid-19 vaccine.
 The number of observations and percentage correponds only to people who would NOT take the vaccine.
 Respondents in all countries could give more than one reason.
-A 95% confidence interval is shown between parentheses",
+A 95% confidence interval is shown between parentheses.",
     threeparttable = T)
@@
     general_title = "",
-    general = "Table 8 shows percentage of respondents that mention actors who they would trust the most to help them decide whether to get a COVID-19 vaccine.
+    general = "Table S6 shows percentage of respondents that mention actors who they would trust the most to help them decide whether to get a COVID-19 vaccine.
 For all countries the questions was asked regardless if respondent would take a vaccine, would not take it, does not know or does not respond.
@@
     general_title = "",
-    general = "Table 7 shows percentage of respondents that mention actors who they would trust the most to help them decide whether to get a COVID-19 vaccine.
+    general = "Table S6 shows percentage of respondents that mention actors who they would trust the most to help them decide whether to get a COVID-19 vaccine.
 For all countries the questions was asked regardless if respondent would take a vaccine, would not take it, does not know or does not respond.
@@
 tab_question1 <- 
-  readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
+  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select(
@@
     general_title = "",
-    general = "Table 12 presents question wording and answer options from answers used in Figure 1 to get estimated vaccine acceptance.
+    general = "Table S10 presents question wording and answer options from answers used in Figure 1 to get estimated vaccine acceptance.
 Answer options are separated by a semicolon.
@@
 In Russia, 'Yes, if a Russian vaccine will be available' and 'Yes, if an imported vaccine will be available' are both recoded as 'Yes'.
-In USA 'Definitely yes' and 'Probably yes' are recoded as 'Yes', and 'Probably not' and 'Definitely not' are recoded as 'No'" ,
+In USA 'Definitely yes' and 'Probably yes' are recoded as 'Yes', and 'Probably not' and 'Definitely not' are recoded as 'No'." ,
     threeparttable = T)
 
-readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
+readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select("Study" = "country", "Question Fig. 1", "Recoding Fig. 1") %>%
@@
     general_title = "",
-    general = "Table 11 presents question wording and answer options from answers used in Figure 1 to get estimated vaccine acceptance.
+    general = "Table S10 presents question wording and answer options from answers used in Figure 1 to get estimated vaccine acceptance.
 Answer options are separated by a semicolon.
@@
 In Russia, 'Yes, if a Russian vaccine will be available' and 'Yes, if an imported vaccine will be available' are both recoded as 'Yes'.
-In USA 'Definitely yes' and 'Probably yes' are recoded as 'Yes', and 'Probably not' and 'Definitely not' are recoded as 'No'" ,
+In USA 'Definitely yes' and 'Probably yes' are recoded as 'Yes', and 'Probably not' and 'Definitely not' are recoded as 'No'," ,
     threeparttable = T)
@@
 tab_question2 <- 
-  readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
+  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select(
@@
     general_title = "",
-    general = "Table 13 presents question wording and answer options used in Table 2 to get an estimated percentage of reasons to take the COVID-19 vaccine.
+    general = "Table S11 presents question wording and answer options used in Table S2 to get an estimated percentage of reasons to take the COVID-19 vaccine.
 Columns 'Protection: self', 'Protection: family' and  'Protection: community' show the answer options that were recoded in each category.
@@
 
-readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
+readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select(
@@
     general_title = "",
-    general = "Table 12 presents question wording and answer options used in Table 3 to get an estimated percentage of reasons to take the COVID-19 vaccine.
+    general = "Table S11 presents question wording and answer options used in Table S2 to get an estimated percentage of reasons to take the COVID-19 vaccine.
 Columns 'Protection: self', 'Protection: family' and  'Protection: community' show the answer options that were recoded in each category.
@@
 tab_question3 <- 
-  readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
+  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select(
@@
     general_title = "",
-    general = "Table 14 presents question wording and answer options used in Figure 2 to get an estimated percentage of reasons not to take the COVID-19 vaccine.
+    general = "Table S12 presents question wording and answer options used in Figure 2 to get an estimated percentage of reasons not to take the COVID-19 vaccine.
 Columns 3-10 show the answer options that were recoded in each category.
@@
     general_title = "",
-    general = "Table 13 presents question wording and answer options used in Figure 2 to get an estimated percentage of reasons not to take the COVID-19 vaccine.
+    general = "Table S12 presents question wording and answer options used in Figure 2 to get an estimated percentage of reasons not to take the COVID-19 vaccine.
 Columns 3-10 show the answer options that were recoded in each category.
@@
 tab_question4 <- 
-  readxl::read_excel("1_input_data/studies_info.xlsx", sheet = "sample") %>%
+  readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
   dplyr::select(
@@
     general_title = "",
-    general = "Table 15 presents question wording and answer options used in Figure 3 to get the percentage of respondents mentioning each actor or instituion that they would trust to decide whether to get the COVID-19 vaccine.
+    general = "Table S13 presents question wording and answer options used in Figure 3 to get the percentage of respondents mentioning each actor or institution that they would trust to decide whether to get the COVID-19 vaccine.
 Columns 3-8 show the answer options that were recoded in each category.
@@
     general_title = "",
-    general = "Table 14 presents question wording and answer options used in Figure 3 to get the percentage of respondents mentioning each actor or instituion that they would trust to decide whether to get the COVID-19 vaccine.
+    general = "Table S13 presents question wording and answer options used in Figure 3 to get the percentage of respondents mentioning each actor or institution that they would trust to decide whether to get the COVID-19 vaccine.
 Columns 3-8 show the answer options that were recoded in each category.
@@
 wgmdata <- 
-  readr::read_csv("1_input_data/wgm_2018_publiccsv.csv") %>% 
+  readr::read_csv("2_input_data/wgm_2018_publiccsv.csv") %>% 
   dplyr::filter(WP5 %in% c(1,9,31,35,41,63,65,76,78,80,105,157),

### 2021-06-22 4_paper_supplementary_files/temp_download.Rmd
update

@@
 
+Julio S.
+Solis Arce,^[WZB Berlin Social Science Center, $^2$Innovations for Poverty Action (IPA), $^3$International Growth Centre (IGC), $^4$Wageningen University & Research, $^5$International Center for the Study of Institutions and Development (HSE University, Moscow, Russia), $^6$Columbia University, $^7$Yale Institute for Global Health, $^8$Busara Center for Behavioral Economics, $^{10}$Department of Sociology, University of Lagos, $^{11}$Busara Nigeria, $^{12}$Agricultural and Rural Development Secretariat, Federal Capital Territory Administration (Abuja, Nigeria), $^{13}$Nova School of Business and Economics, $^{14}$The Institute for Fiscal Studies, $^{15}$Lahore University of Management Sciences, $^{16}$Innovations for Poverty Action (IPA) Uganda, $^{17}$Morsel Research & Development, $^{18}$University of St.
+Andrews,  $^{19}$Redes Peru, $^{20}$Stockholm School of Economics and Misum, $^{21}$Ghent University, Department of Economics, $^{22}$Innovations for Poverty Action (IPA) Colombia, $^{23}$Institute of Development and Economic Alternatives, $^{24}$Innovations for Poverty Action (IPA) Sierra Leone,$^{25}$NOVAFRICA, $^{26}$Trinity College Dublin, $^{27}$Institute of Public Administration and Management, University of Sierra Leone, $^{28}$Centre for the Study of Labour and Mobility (CESLAM), $^{29}$Cornell University, $^{30}$University of Illinois Chicago, $^{31}$Innovations for Poverty Action (IPA) Rwanda, $^{32}$Associação NOVAFRICA para o Desenvolvimento Empresarial e Económico de Moçambique, $^{33}$Innovations for Poverty Action (IPA) Burkina Faso, $^{34}$NYU Abu Dhabi, $^{35}$Centre for Economic Research in Pakistan (CERP), $^{36}$Yale Research Initiative on Innovation and Scale (Y-RISE), $^{37}$Princeton University, $^{38}$Institute for International Economic Studies (IIES), Stockholm University, $^{39}$Tufts University, $^{40}$University of Michigan, $^{41}$Kellogg School of Management at Northwestern University, $^{42}$London School of Economics, $^{43}$Yale University] Shana S.
+Warren,$^2$ Niccolò F.
+Meriggi,$^3$ Alexandra Scacco,$^1$ Nina McMurry,$^1$ Maarten Voors,$^4$ Georgiy Syunyaev,$^{1,5,6}$, Amyn Abdul Malik,$^7$ Samya Aboutajdine,$^3$ Opeyemi Adeojo,$^{8, 10}$ Deborah Anigo,$^{11, 12}$ Alex Armand,$^{13, 14}$ Saher Asad,$^{15}$ Martin Atyera,$^{16}$ Britta Augsburg,$^{14}$ Manisha Awasthi,$^{17}$ Gloria Eden Ayesiga,$^{16}$ Antonella Bancalari,$^{14, 18, 19}$ Martina Björkman Nyqvist,$^{20}$ Ekaterina Borisova,$^{5, 21}$ Constantin Manuel Bosancianu,$^1$ Magarita Rosa Cabra García,$^22$ Ali Cheema,$^{15, 23}$ Elliott Collins,$^{2}$ Filippo Cuccaro,$^{24}$ Ahsan Zia Farooqi,$^{23}$ Tatheer Fatima,$^{17}$ Mattia Fracchia,$^{13, 25}$ Mery Len Galindo Soria,$^{22}$ Andrea Guariso,$^{26}$ Ali Hasanain,$^{15}$ Sofía Jaramillo Arciniegas,$^{22}$ Sellu Kallon,$^{4, 27}$ Anthony Kamwesigye,$^{16}$ Arjun Kharel,$^{28}$ Sarah Kreps,$^{29}$ Madison Levine,$^{4}$ Rebecca Littman,$^{30}$ Shan-e-Mohammad Malik,$^{23}$ Gisele Manirabaruta,$^{31}$ Jean Léodomir Habarimana Mfura,$^{31}$ Fatoma Momoh,$^{24}$ Alberto Mucauque,$^{32}$ Imamo Mussa,$^{32}$ Jean Aime Nsabimana,$^{31}$ Isaac Obara,$^{8}$ María Juliana Otálora,$^{22}$ Béchir Wendemi Ouédraogo,$^{33}$ Touba Bakary Pare,$^{33}$ Melina R.
+Platas,$^{34}$ Laura Polanco,$^{22}$ Javaeria Ashraf Qureshi,$^{30}$ Mariam Raheem,$^{35}$ Vasudha Ramakrishna,$^{36}$ Ismail Rendrá,$^{32}$ Taimur Shah,$^{35}$ Sarene Eyla Shaked,$^{16}$ Jacob N.
+Shapiro, $^{37}$ Jakob Svensson,$^{38}$ Ahsan Tariq,$^{23}$ Achille Mignondo Tchibozo,$^{33}$ Hamid Ali Tiwana,$^{23}$ Bhartendu Trivedi,$^{17}$ Corey Vernot, $^{36}$ Pedro C.
+Vicente,$^{13, 25}$ Laurin B Weissinger,$^{39}$ Basit Zafar,$^{35, 40}$ Baobao Zhang,$^{29}$ Dean Karlan,$^{2, 41}$ Michael Callen,$^{42}$ Matthieu Teachout,$^{3}$ Macartan Humphreys,$^{1, 6}$ Ahmed Mushfiq Mobarak,$^{43}$ Saad B.
+Omer$^{7}$.
+
 \newpage
 
-```{r, include=FALSE} 
+```{r} 
 empty = " " 
@@
 
-We analyze COVID-19 vaccine acceptance across 15 survey samples covering ten low- and middle-income countries (LMICs) in Asia, Africa, and South America, Russia (an upper-middle-income country), and the United States, using survey responses from  `r nice(nrow(df))` individuals.
-We find considerably higher willingness to take a COVID-19 vaccine in LMIC samples (80% on average) compared to the United States (65%) and Russia (30%).
-Vaccine acceptance was primarily explained by an interest in personal protection against COVID-19, while concern about side effects was the most commonly expressed reason for reluctance.
-Health workers were the most trusted sources of information about COVID-19 vaccines.
-Our findings suggest that prioritizing vaccine distribution to LMICs should yield high returns in promoting global immunization coverage, and that vaccination campaigns in these countries should focus on translating acceptance into uptake.
-Messaging highlighting vaccine efficacy and safety, delivered by healthcare workers, may be most effective in addressing remaining hesitancy.
+We analyze COVID-19 vaccine acceptance across 15 survey samples covering ten low- and middle-income countries (LMICs) in Asia, Africa, and South America, Russia (an upper-middle-income country), and the United States, including  `r nice(nrow(df))` individuals.
+We find considerably higher willingness to take a COVID-19 vaccine in our LMIC samples (mean `r ans_mean`%; median `r ans_median`%; range of `r ans_max - ans_min`%) compared to the United States (mean `r usa_ans %>% pull(estimate)`%) and Russia (mean `r rus_ans %>% pull(estimate)`%).
+Vaccine acceptance is primarily explained by an interest in personal protection against COVID-19, while concern about side effects is the most common reason for hesitancy.
+Health workers are the most trusted sources of guidance about COVID-19 vaccines.
+Evidence from this sample of LMICs suggests that prioritizing vaccine distribution to the Global South should yield high returns in advancing global immunization coverage.
+Vaccination campaigns should focus on translating the high levels of stated acceptance into actual uptake.
+Messages highlighting vaccine efficacy and safety, delivered by healthcare workers, may be most effective for addressing remaining hesitancy.
 
@@
 
-A safe and effective vaccine against COVID-19 is a critical tool to control the pandemic.
-As of April 27, 2021, 22 vaccines had advanced to Stage 3 clinical trials [@who1] and more than a dozen vaccines had been approved in multiple countries[@track].
-For example, as of April 27, 2021, Comirnaty (BioNTech/Pfizer) had been approved in  more than 80 countries, while the AstraZeneca vaccine had the most country authorizations at 92.
-[@track] At present, however, global vaccine distribution remains highly unequal, with much of the current supply directed toward high-income countries [@wouters2021challenges].
+A safe and effective vaccine is a critical tool to control the COVID-19 pandemic.
+As of May 27, 2021, 23 vaccines had advanced to Stage 3 clinical trials [@who1] and more than a dozen had been approved in multiple countries[@track].
+The BioNTech/Pfizer (Comirnaty) vaccine, for example, has been approved in more than 80 countries, while the AstraZeneca vaccine has the most country authorizations at 98 [@track].
+At present, however, global vaccine distribution remains highly unequal, with much of the current supply directed toward high-income countries [@wouters2021challenges].
 
-While effective and equitable distribution of COVID-19 vaccines is a key policy priority, ensuring the population’s acceptance is equally important.
+While effective and equitable distribution of COVID-19 vaccines is a key policy priority, ensuring acceptance is just as important.
 Trust in vaccines and the institutions that administer them are key determinants of the success of any vaccination campaign [@defigueiredo2020lancet].
@@
 Less is known, however, about vaccine acceptance in low-income countries where large-scale vaccination has yet to begin.
-Understanding the drivers of COVID-19 vaccine acceptance is of global concern, since a lag in vaccination in any country may result in the emergence and spread of new variants that can overcome vaccine- and prior disease-conferred immunity [@ong2021lack; @lancettask].
+Understanding the drivers of COVID-19 vaccine acceptance is of global concern, since a lag in vaccination in any country may result in the emergence and spread of new variants that can overcome immunity conferred by vaccines and prior disease [@ong2021lack; @lancettask].
 
@@
 We construct a sample of low- and middle-income countries (LMICs) with wide geographic coverage across Africa, Asia and Latin America.
-We move beyond documenting vaccine acceptance rates and analyze data on the reasons for acceptance and hesitancy, which is critical for informing the design of effective vaccine distribution and messaging.
+We move beyond documenting vaccine acceptance rates to collect and analyze data on the reasons for acceptance and hesitancy, which is critical for informing the design of effective vaccine distribution and messaging.
+A summary of the main findings, limitations and implications of the study is shown in Table \ref{tab:summary}.
 
-Acceptance of childhood vaccination for common diseases---such as measles (MCV), Bacille Calmette-Guérin (BCG) and diphtheria, tetanus, and pertussis (DTP)---is generally high in LMICs, providing cause for optimism about the prospects for COVID-19 vaccine uptake.
+Acceptance of childhood vaccination for common diseases---such as measles (MCV), Bacille Calmette-Guérin (BCG) and diphtheria, tetanus, and pertussis (DTP)---is generally high in LMICs, providing grounds for optimism about the prospects for COVID-19 vaccine uptake.
 Table \ref{tab:otherv} summarizes general vaccine acceptance and coverage rates of childhood vaccines in 2018, prior to the current pandemic, for the countries included in our study.
-Agreement on the importance of childhood vaccinations is markedly higher in these LMICs compared to Russia and the United States.
-Still, existing studies on COVID-19 vaccine acceptance document substantial variation, both across and within countries, including in settings with high background levels of other vaccinations [@defigueiredo2020lancet; @lazarus2020nature; @wouters2021challenges].
+Agreement on the importance of childhood vaccinations is markedly higher in the LMICs we study compared to Russia and the United States.
+Still, existing studies on COVID-19 vaccine acceptance document substantial variation, both across and within countries, including in settings with high acceptance of other vaccinations [@defigueiredo2020lancet; @lazarus2020nature; @wouters2021challenges].
 
-This literature cites concerns about COVID-19 vaccine safety, including concerns about the rapid pace of vaccine development, as reasons for hesitancy in higher-income settings [@boyon2020ipsos; @wouters2021challenges], but other reasons  may feature more prominently in LMICs.
-For instance, reported COVID-19 mortality rates have been consistently lower in LMICs relative to higher income countries [@mukherjee].
-If individuals feel the risk of disease is less serious, they may be less willing to accept any perceived risks of vaccination [@brewer2007meta].
-Previous studies of healthcare utilization in LMICs have also highlighted factors such as healthcare quality concerns [@christensen2020building], negative historical experiences involving foreign actors  [@Lowes2018; @martinez2021vaccines], weak support from traditional leaders [@Jegede2007], and mistrust in government [@BLAIR201789] as barriers to uptake, which could apply to COVID-19 vaccination as well.
+Existing literature cites concern about COVID-19 vaccine safety, including the rapid pace of vaccine development, as a primary reason for hesitancy in higher-income settings [@boyon2020ipsos; @wouters2021challenges].
+Other reasons may feature more prominently in LMICs.
+For instance, reported COVID-19 mortality rates have been consistently lower in most LMICs relative to higher income countries [@biccard2021patient; @rice2021variation; @maeda2021puzzle].
+If individuals feel the risk of disease is less severe, they may be less willing to accept any perceived risks of vaccination [@brewer2007meta].
+Previous studies of healthcare utilization in LMICs have also highlighted factors such as negative perceptions of healthcare quality [@christensen2020building], negative historical experiences involving foreign actors  [@Lowes2018; @martinez2021vaccines], weak support from traditional leaders [@Jegede2007], and mistrust in government [@BLAIR201789] as barriers to uptake, which could apply to COVID-19 vaccination as well.
 
-To promote vaccination against COVID-19 and develop effective messaging strategies, we need to know whether people are willing to take COVID-19 vaccines, the reasons why they are willing or unwilling to do so, and the most trusted  sources in their decision-making.
+To promote vaccination against COVID-19, we need to know whether people are willing to take COVID-19 vaccines, the reasons why they are willing or unwilling to do so, and the most trusted sources of information in their decision-making.
 Our study investigates these questions using a common set of survey items deployed across 13 studies in Africa, South Asia, and Latin America: seven in low-income countries (Burkina Faso, Mozambique, Rwanda, Sierra Leone, Uganda), five in lower-middle-income countries (India, Nepal, Nigeria, Pakistan), and one in an upper-middle-income country (Colombia).
 We compare these findings to those from two countries at the forefront of vaccine research and development, Russia and the United States.
+
 To select studies to include in our sample, we conducted an internal search within Innovations for Poverty Action (IPA), the International Growth Center (IGC), and the Berlin Social Science Center (WZB) for projects with plans to collect survey data in the second half of 2020.
 Study PIs agreed to include a set of common questions about COVID-19 vaccine attitudes.
-This strategy was guided by the need to collect information quickly and cost effectively using a survey modality (phone) that was both safe given pandemic conditions and appropriate for contexts with limited internet coverage.
+This strategy was guided by the need to collect information quickly and cost-effectively using a survey modality (phone) that was both safe, given pandemic conditions, and appropriate for contexts with limited internet coverage.
 The final set of samples included in our study therefore reflects populations that fall under the current research priorities at IGC, IPA and WZB and, in the case of IPA and IGC, donors that prioritize working in the Global South.
@@
 
-Our main results are shown in Figure \@ref(fig:mainfigure1) and reproduced as [Appendix A](#appendixd) Table \ref{tab:maintabledis}.
-The first column provides overall acceptance rates in each study, while the remaining columns disaggregate acceptance rates by respondent characteristics.
-The “All LMICs” row reports averages for LMIC countries and excludes Russia and the USA.
+Our main results are shown in Figure \@ref(fig:mainfigure1) and reproduced as \hyperref[tab:maintabledis]{Supplementary Table 1}.
+The first column provides overall acceptance rates in each study, while the remaining columns disaggregate acceptance by respondent characteristics.
+The “All LMICs” row reports averages for the LMIC samples included in our study and excludes Russia and the USA.
+The “LMICs National Samples” row reports averages for just the LMIC samples with national-level geographic coverage.
 
-We document meaningful variation in vaccine acceptance across and within LMICs, but generally high levels of acceptance in LMICs overall.
-The average acceptance rate across studies was `r ans_mean`% (95% CI `r ans_mean_low`--`r ans_mean_high`%), with a median of `r ans_median`, a range of `r ans_max - ans_min` percent points and an interquartile range of `r ans_iqr`.
-Our estimate of $\tau^2$ is `r  round(mp_tau, 3)` which implies a standard deviation over country averages of  `r round(mp_tau^.5, 3)`.
+The average acceptance rate across the full set of LMIC studies is `r ans_mean`% (95% CI `r ans_mean_low`--`r ans_mean_high`%), with a median of `r ans_median`%, a range of `r ans_max - ans_min`% and an interquartile range of `r ans_iqr`%.
+Our estimate of the between-study standard deviation, $\tau$, using a random effects meta-analysis model is `r  round(sqrt(mp_tau), 3)` which represents only `r  round(100*mp_ratio, 1)`% of our estimate of the average acceptance across LMIC studies.
 
-The acceptance rate in every LMIC sample was higher than in the USA (`r usa_ans %>% pull(estimate)`%, `r usa_ans %>% pull(conf.low)`--`r usa_ans %>% pull(conf.high)`%) and Russia (`r rus_ans %>% pull(estimate)`%, `r rus_ans %>% pull(conf.low)`--`r rus_ans %>% pull(conf.high)`%).
-Reported acceptance was lowest in `r bottom_all$group[1]` (`r bottom_all$estimate[1]`% `r bottom_all$conf.low[1]`--`r bottom_all$conf.high[1]`%) and `r bottom_all$group[2]`  (`r bottom_all$estimate[2]`%, `r bottom_all$conf.low[2]`--`r bottom_all$conf.high[2]`%).
-The case of Pakistan may be linked to negative historical experiences with foreign-led vaccination campaigns [@ali2019polio; @robbins2012cia].
-This hesitancy may be particularly problematic, given the magnitude of the second wave in neighboring India just as vaccines are becoming available, with accelerating cases in Bangladesh, Pakistan and India threatening to overwhelm health infrastructure.
+The acceptance rate in every LMIC sample is higher than in the USA (`r usa_ans %>% pull(estimate)`%, CI `r usa_ans %>% pull(conf.low)`--`r usa_ans %>% pull(conf.high)`%) and Russia (`r rus_ans %>% pull(estimate)`%, CI `r rus_ans %>% pull(conf.low)`--`r rus_ans %>% pull(conf.high)`%).
+Reported acceptance is lowest in `r bottom_all$group[1]` (`r bottom_all$estimate[1]`%, CI `r bottom_all$conf.low[1]`--`r bottom_all$conf.high[1]`%) and `r bottom_all$group[2]`  (`r bottom_all$estimate[2]`%, CI `r bottom_all$conf.low[2]`--`r bottom_all$conf.high[2]`%).
+Pakistan’s relatively low acceptance rate may be linked to negative historical experiences with foreign-led vaccination campaigns [@ali2019polio; @robbins2012cia; @martinez2021vaccines].
+This hesitancy may be particularly problematic given the magnitude of the second wave in neighboring India and acceleration of cases across South Asia that threaten to overwhelm health infrastructure.
+The relatively low acceptance rate in Burkina Faso may reflect general vaccine hesitancy.
+As shown in Table \ref{tab:otherv}, fewer people believe that vaccines in general are safe in Burkina Faso than in any other country included in our study except Russia.
 
-We find limited evidence of variation across demographic subgroups in our LMIC samples, as shown in [Appendix A](#appendixd) Table \ref{tab:dmeans}.
-Women were generally less willing to accept the vaccine (average difference about `r dif_gender` points, significant at $p<.01$).
-Respondents under age 24 and less educated respondents were marginally more willing to take the vaccine, but these differences were not statistically significant.
-The acceptance advantage among the less educated was most pronounced in Rwanda, Burkina Faso, and Uganda, and stands in contrast to the USA, where more educated respondents were significantly more willing to be vaccinated.
+We find limited evidence of variation across demographic subgroups in our aggregate analysis of LMIC samples, as shown in \hyperref[tab:dmeans]{Supplementary Table 7}.
+Women are generally less willing to accept the vaccine than men (average difference about `r dif_gender` points, significant at $p<.01$).
+Respondents under age 25 and less educated respondents are marginally more willing to take the vaccine compared to older and more educated respondents, respectively, but these differences are not statistically significant.
+
+Table \hyperref[tab:countrydiff]{Supplementary Table 9} provides results disaggregated by demographic subgroups for individual studies.
+The average gender differences in the aggregate LMIC analysis are driven by the Burkina Faso, Mozambique, Pakistan 1, Rwanda and Sierra Leone 1 samples.
+However, these gender differences in acceptance are less than 10 percentage points in each of these samples, in contrast to larger gender gaps in acceptance we observe in the USA (17%) and Russia (16%).
+
+Less-educated respondents expressed significantly higher acceptance in the Burkina Faso, Rwanda, Sierra Leone 1, and Uganda 2 samples, which represent the majority of  studies from sub-Saharan Africa.
+Notably, we observe the opposite pattern in the India, Pakistan 1, and Pakistan 2 samples.
+In all three studies, acceptance is greater among more educated respondents, although this difference is not statistically significant in the India sample.
+Education is also a positive and significant predictor of acceptance in the USA.
+
+We find mixed evidence across studies with respect to the relationship between age and COVID-19 vaccine acceptance.
+In India and Nigeria, respondents younger than 25 years old are significantly less willing to take the vaccine relative to adults 25-54 years old, while in Mozambique, Pakistan 1, and Rwanda, those under 25 are significantly more willing.
+In Mozambique and Rwanda, respondents under 25 are also significantly more accepting compared to those 55 and over; however, the difference between these age groups is not statistically significant in other LMIC samples.
+In the USA and Russia, older respondents are consistently more accepting than younger respondents.
 
 To better understand the reasoning behind vaccine acceptance, we asked those who were willing to take the vaccine why they would take it.
-We summarize these results in Table \ref{tab:yes}, with additional details in [Appendix A](#appendixd) Table \ref{tab:yesall}.
-The reason most commonly given for vaccine acceptance across samples was personal protection against COVID-19 infection.
-The average across the LMIC samples was `r yes_all$estimate`% (`r yes_all$conf.low`--`r yes_all$conf.high`%).
-In every individual study, this ranked as the most popular reason.
-In distant second place among LMIC respondents was family protection with an average of `r yes_all_2$estimate`% (`r yes_all_2$conf.low`--`r yes_all_2$conf.high`%).
-In comparison to protecting oneself and one’s family,  protecting one’s community did not feature prominently among stated reasons for acceptance.
-These reasons do not vary substantially by age group, as shown in Table \ref{tab:countrydiff}.
-Self-protection also ranked as the most common reason for taking the vaccine in Russia (`r yes_rus$estimate`%, `r yes_rus$conf.low`--`r yes_rus$conf.high`%) and the USA (`r yes_usa$estimate`%, `r yes_usa$conf.low`--`r yes_usa$conf.high`%).
+We summarize these results in \hyperref[tab:yes]{Supplementary Table 2}, with additional details in \hyperref[tab:yesall]{Supplementary Table 3}.
+The reason most commonly given for vaccine acceptance across samples is personal protection against COVID-19 infection.
+The average across the LMIC samples is `r yes_all$estimate`% (CI `r yes_all$conf.low`--`r yes_all$conf.high`%) with a median of  `r yes_ %>% pull(estimate) %>% median()`% and a range of `r yes_ %>% pull(estimate) %>% max() - yes_ %>% pull(estimate) %>% min()`%.
+In every individual study, including the USA (`r yes_usa$estimate`%, CI `r yes_usa$conf.low`--`r yes_usa$conf.high`%) and Russia (`r yes_rus$estimate`%, CI `r yes_rus$conf.low`--`r yes_rus$conf.high`%), this ranks as the most cited reason.
+In distant second place in the aggregate LMIC analysis is family protection, with an average of `r yes_all_2$estimate`% (CI `r yes_all_2$conf.low`--`r yes_all_2$conf.high`%), a median of `r yes_2 %>% pull(estimate) %>% median()`% and a range of `r yes_2 %>% pull(estimate) %>% max() - yes_2 %>% pull(estimate) %>% min()`%.
+In comparison to protecting oneself and one’s family,  protecting one’s community does not feature prominently among stated reasons for acceptance.
+These reasons do not vary substantially by age group, as shown in \hyperref[tab:yes1]{Supplementary Table 4}.
 
 Figure \@ref(fig:fig2paper) summarizes the reasons given by respondents who said they were not willing to take a COVID-19 vaccine.
-Concern about side effects was the most frequently expressed reason for reluctance in our  LMIC samples.
-This concern was particularly evident among African country samples.
-In studies  `r side_top$group[1]` (`r side_top$estimate[1]`% `r side_top$conf.low[1]`--`r side_top$conf.high[1]`%), `r side_top$group[2]`  (`r side_top$estimate[2]`%, `r side_top$conf.low[2]`--`r side_top$conf.high[2]`%), `r side_top$group[3]` (`r side_top$estimate[3]`% `r side_top$conf.low[3]`--`r side_top$conf.high[3]`%) and `r side_top$group[4]` (`r side_top$estimate[4]`% `r side_top$conf.low[4]`--`r side_top$conf.high[4]`%), more than half of respondents unwilling to take the vaccine cited worries about side effects.
-Respondents in Russia (`r side_rus$estimate`%, `r side_rus$conf.low`--`r side_rus$conf.high`%) and even more in the USA (`r side_usa$estimate`%, `r side_usa$conf.low`--`r side_usa$conf.high`%), frequently reported this same concern.
+Concern about side effects is the most frequently expressed reason for reluctance in our LMIC samples.
+This concern is particularly evident among samples from sub-Saharan Africa.
+In studies  `r side_top$group[1]` (`r side_top$estimate[1]`%, CI `r side_top$conf.low[1]`--`r side_top$conf.high[1]`%), `r side_top$group[2]`  (`r side_top$estimate[2]`%, CI `r side_top$conf.low[2]`--`r side_top$conf.high[2]`%), `r side_top$group[3]` (`r side_top$estimate[3]`%, CI `r side_top$conf.low[3]`--`r side_top$conf.high[3]`%) and `r side_top$group[4]` (`r side_top$estimate[4]`%, CI `r side_top$conf.low[4]`--`r side_top$conf.high[4]`%), more than half of respondents unwilling to take the vaccine cited worries about side effects.
+Respondents in Russia (`r side_rus$estimate`%, CI `r side_rus$conf.low`--`r side_rus$conf.high`%) and even more in the USA (`r side_usa$estimate`%, CI `r side_usa$conf.low`--`r side_usa$conf.high`%), frequently report this same concern.
 
-Study samples `r effective_top$group[1]` (`r effective_top$estimate[1]`%, `r effective_top$conf.low[1]`--`r effective_top$conf.high[1]`%), `r effective_top$group[2]`  (`r effective_top$estimate[2]`%, `r effective_top$conf.low[2]`--`r effective_top$conf.high[2]`%) and `r effective_top$group[3]` (`r effective_top$estimate[3]`%, `r effective_top$conf.low[3]`--`r effective_top$conf.high[3]`%) showed relatively high levels of skepticism about vaccine effectiveness among hesitant respondents.
-This was also true in Russia (`r effective_rus$estimate`%, `r effective_rus$conf.low`--`r effective_rus$conf.high`%) and the USA (`r effective_usa$estimate`%, `r effective_usa$conf.low`--`r effective_usa$conf.high`%).
-In addition, hesitant respondents listed lack of concern about COVID-19 infection as a reason not to be vaccinated.
-Study samples `r ill_top$group[1]` (`r ill_top$estimate[1]`% `r ill_top$conf.low[1]`--`r ill_top$conf.high[1]`%), `r ill_top$group[2]`  (`r ill_top$estimate[2]`%, `r ill_top$conf.low[2]`--`r ill_top$conf.high[2]`%) and `r ill_top$group[3]` (`r ill_top$estimate[3]`% `r ill_top$conf.low[3]`--`r ill_top$conf.high[3]`%) reported high rates of this answer among hesitant respondents.
+Study samples `r effective_top$group[1]` (`r effective_top$estimate[1]`%, CI `r effective_top$conf.low[1]`--`r effective_top$conf.high[1]`%), `r effective_top$group[2]`  (`r effective_top$estimate[2]`%, CI `r effective_top$conf.low[2]`--`r effective_top$conf.high[2]`%) and `r effective_top$group[3]` (`r effective_top$estimate[3]`%, CI `r effective_top$conf.low[3]`--`r effective_top$conf.high[3]`%) show relatively high levels of skepticism about vaccine effectiveness among hesitant respondents.
+This is also true in Russia (`r effective_rus$estimate`%, CI `r effective_rus$conf.low`--`r effective_rus$conf.high`%) and the USA (`r effective_usa$estimate`%, CI `r effective_usa$conf.low`--`r effective_usa$conf.high`%).
+In addition, some hesitant respondents cite lack of concern about COVID-19 infection as a reason not to be vaccinated.
+This answer is particularly common in the `r ill_top$group[1]` (`r ill_top$estimate[1]`%, CI `r ill_top$conf.low[1]`--`r ill_top$conf.high[1]`%), `r ill_top$group[2]`  (`r ill_top$estimate[2]`%, CI `r ill_top$conf.low[2]`--`r ill_top$conf.high[2]`%) and `r ill_top$group[3]` (`r ill_top$estimate[3]`%, CI `r ill_top$conf.low[3]`--`r ill_top$conf.high[3]`%) studies.
 
 In Figure \@ref(fig:fig3paper) we report respondents’ most trusted source of guidance when deciding whether to take a COVID-19 vaccine.
-Results from Figure \@ref(fig:fig3paper) are reproduced as  [Appendix A](#appendixd) Table \ref{tab:trust}.
-[Appendix B](#appendixb) Table \ref{tab:q4} presents a complete description of response recoding from individual studies.
+Results from Figure \@ref(fig:fig3paper) are reproduced in \hyperref[tab:trust]{Supplementary Table 6}, while \hyperref[tab:q4]{Supplementary Table 13} presents a complete description of response recoding from individual studies.
 
-We find striking consistency in most trusted sources across studies.
-In all but one sample, including those from Russia and the USA, respondents identified the health system as the most trustworthy source to help them decide whether to take the COVID-19 vaccine.
-The average across LMICs was `r trust_all$estimate`% (`r trust_all$conf.low`--`r trust_all$conf.high`%).
-Respondents in `r trust_top$group[1]` (`r trust_top$estimate[1]`%, `r trust_top$conf.low[1]`--`r trust_top$conf.high[1]`%), `r trust_top$group[2]`  (`r trust_top$estimate[2]`%, `r trust_top$conf.low[2]`--`r trust_top$conf.high[2]`%) and `r trust_top$group[3]` (`r trust_top$estimate[3]`%, `r trust_top$conf.low[3]`--`r trust_top$conf.high[3]`%) cited  health workers most often.
-Sierra Leone had the highest trust in health workers and the Ministry of Health, potentially due to investments in public health following the 2014-2015 Ebola epidemic [@deserrano].
+We find striking consistency across studies.
+In all samples except Rwanda, including those from Russia and the USA, respondents identify the health system as the most trustworthy source to help them decide whether to take the COVID-19 vaccine.
+The average across LMIC samples is  `r trust_all$estimate`% (CI `r trust_all$conf.low`--`r trust_all$conf.high`%), with a median of  `r trust_%>% pull(estimate) %>% median()`% and a range of `r trust_%>% pull(estimate) %>% max() - trust_%>% pull(estimate) %>% min()`%.
+Respondents in `r trust_top$group[1]` (`r trust_top$estimate[1]`%, CI `r trust_top$conf.low[1]`--`r trust_top$conf.high[1]`%), `r trust_top$group[2]`  (`r trust_top$estimate[2]`%, CI `r trust_top$conf.low[2]`--`r trust_top$conf.high[2]`%) and `r trust_top$group[3]` (`r trust_top$estimate[3]`%, CI `r trust_top$conf.low[3]`--`r trust_top$conf.high[3]`%) cited  health workers most often.
+Sierra Leone has the highest trust in health workers and the Ministry of Health, potentially reflecting investments in public health following the 2014-2015 Ebola epidemic [@deserrano].
 
-The next most cited sources were family and/or friends in  `r trust_fam$group[1]` (`r trust_fam$estimate[1]`%, `r trust_fam$conf.low[1]`--`r trust_fam$conf.high[1]`%), `r trust_fam$group[2]`  (`r trust_fam$estimate[2]`%, `r trust_fam$conf.low[2]`--`r trust_fam$conf.high[2]`%), `r trust_fam$group[3]` (`r trust_fam$estimate[3]`%, `r trust_fam$conf.low[3]`--`r trust_fam$conf.high[3]`%) and `r trust_fam$group[4]` (`r trust_fam$estimate[4]`%, `r trust_fam$conf.low[4]`--`r trust_fam$conf.high[4]`%).
-Across the pooled samples, women were 3 percentage points more likely to rely on family and friends than male respondents, though this difference was not statistically significant (Figure \@ref(fig:genderhist) in [Appendix D](#appendixd)).
+In  `r trust_fam$group[1]` (`r trust_fam$estimate[1]`%, CI `r trust_fam$conf.low[1]`--`r trust_fam$conf.high[1]`%), `r trust_fam$group[2]`  (`r trust_fam$estimate[2]`%, CI `r trust_fam$conf.low[2]`--`r trust_fam$conf.high[2]`%), `r trust_fam$group[3]` (`r trust_fam$estimate[3]`%, CI `r trust_fam$conf.low[3]`--`r trust_fam$conf.high[3]`%) and `r trust_fam$group[4]` (`r trust_fam$estimate[4]`%, CI `r trust_fam$conf.low[4]`--`r trust_fam$conf.high[4]`%), the next most-cited sources are family and friends.
+Across the pooled samples, women are 3 percentage points more likely to rely on family and friends than male respondents, though this difference is not statistically significant (\hyperref[fig:genderhist]{Supplementary Figure 1}).
 
-By contrast, in `r trust_gov$group[1]` (`r trust_gov$estimate[1]`%, `r trust_gov$conf.low[1]`--`r trust_gov$conf.high[1]`%), `r trust_gov$group[2]`  (`r trust_gov$estimate[2]`%, `r trust_gov$conf.low[2]`--`r trust_gov$conf.high[2]`%), `r trust_gov$group[3]` (`r trust_gov$estimate[3]`%, `r trust_gov$conf.low[3]`--`r trust_gov$conf.high[3]`%) and `r trust_gov$group[4]` (`r trust_gov$estimate[4]`%, `r trust_gov$conf.low[4]`--`r trust_gov$conf.high[4]`%), government was the second most frequently cited.
-Religious leaders and celebrities were not seen as the top sources of guidance by many respondents in any sample other than Nepal, where many respondents most trusted famous people (`r trust_npl$estimate`%, `r trust_npl$conf.low`--`r trust_npl$conf.high`%).
+By contrast, in `r trust_gov$group[1]` (`r trust_gov$estimate[1]`%, CI `r trust_gov$conf.low[1]`--`r trust_gov$conf.high[1]`%), `r trust_gov$group[2]`  (`r trust_gov$estimate[2]`%, CI `r trust_gov$conf.low[2]`--`r trust_gov$conf.high[2]`%), `r trust_gov$group[3]` (`r trust_gov$estimate[3]`%, CI `r trust_gov$conf.low[3]`--`r trust_gov$conf.high[3]`%) and `r trust_gov$group[4]` (`r trust_gov$estimate[4]`%, CI `r trust_gov$conf.low[4]`--`r trust_gov$conf.high[4]`%), government is the second most frequently cited.
+Religious leaders and celebrities are not seen as the top sources of guidance by many respondents in any sample other than Nepal, where many respondents say they most trust famous people (`r trust_npl$estimate`%, CI `r trust_npl$conf.low`--`r trust_npl$conf.high`%).
 
@@
 <!-- Temp subheading: interpretation of results -->
-To our knowledge, this is the first study focusing on COVID-19 vaccine attitudes in a large set of low-income and lower-middle-income countries.
-Our findings showed variable but broadly high levels of prospective COVID-19 vaccine acceptance across LMICs, using data from `r nice(nrow(filter(df, country!="USA" | country!="Russia")))` respondents in `r length(unique(df$country))-2` studies in ten LMICs in Africa, South Asia, and Latin America.
-Acceptance across these LMIC samples  averaged `r ans_mean`%, ranging between `r ans_min`% and `r ans_max`%.
-The two benchmark countries, Russia and the USA, demonstrated lower COVID-19 vaccine acceptance, consistent with relatively lower pre-pandemic vaccine confidence.
+The current study contributes to the emerging picture of global vaccine acceptance by focusing on COVID-19 vaccine attitudes in a set of low-income and lower-middle-income countries.
+Our findings show variable but broadly high levels of prospective COVID-19 vaccine acceptance across the LMICs we study, using data from `r nice(nrow(filter(df, country!="USA" | country!="Russia")))` respondents in `r length(unique(df$country))-2` studies in ten LMICs in Africa, South Asia, and Latin America.
+Acceptance across these LMIC samples  averaged `r ans_mean`%, ranging between `r ans_min`% and `r ans_max`% with a median of `r ans_median`%.
+The two benchmark countries, Russia and the USA, demonstrate lower COVID-19 vaccine acceptance, consistent with lower pre-pandemic vaccine confidence.
 
-Many metrics and indices measure vaccine acceptance and hesitancy globally [@betsch2018beyond; @domek2018measuring; @shapiro2018vaccine; @gilkey2014vaccination,].
-Our surveys used measures employed in other COVID-19 vaccine acceptance studies [@fisher2020attitudes;  @Malik2020; @wouters2021challenges; @lazarus2020nature; @kreps2020factors; @shekhar2021covid; @dror2020vaccine] and recommended by the WHO Data for Action guidance [@whodata], allowing for meaningful cross-study and cross-country comparisons.
+Many metrics and indices measure vaccine acceptance and hesitancy globally [@betsch2018beyond; @domek2018measuring; @shapiro2018vaccine; @gilkey2014vaccination].
+Our surveys use measures employed in other COVID-19 vaccine acceptance studies [@fisher2020attitudes;  @Malik2020; @wouters2021challenges; @lazarus2020nature; @kreps2020factors; @shekhar2021covid; @dror2020vaccine] and recommended by the WHO Data for Action guidance [@whodata], allowing for meaningful cross-study and cross-country comparisons.
 We measure trust in sources of information about COVID-19 vaccination using a measure similar to that used in the Vaccine Confidence Index (VCI), a widely used survey tool [@defigueiredo2020lancet].
 
-Consistent with other studies, we find higher vaccine acceptance among men than women [@kreps2020factors; @shekhar2021covid; @dror2020vaccine;  @fisher2020attitudes; @wouters2021challenges].
+Consistent with other studies, we find higher average vaccine acceptance among men than women [@kreps2020factors; @shekhar2021covid; @dror2020vaccine;  @fisher2020attitudes; @wouters2021challenges].
 In contrast to studies focused primarily on higher-income countries, we find no consistently significant differences with respect to age [@kreps2020factors; @dror2020vaccine] or education in our LMIC samples.
 
-A key contribution of our study relative to the previous literature is its focus on the reasons why respondents express intentions to take (or refuse) a COVID-19 vaccine.
+A key contribution of our study relative to the existing literature is its focus on the reasons *why* respondents express intentions to take (or refuse) a COVID-19 vaccine.
 Other work has highlighted appeals to altruistic behavior or other prosocial motivations to promote vaccine acceptance [@chou2020considering].
-Yet we find that the potential risks and benefits to personal well-being feature much more prominently in our respondents’ reasoning, suggesting that appeals about personal protection may be more effective in LMICs.
+Yet we find that the potential risks and benefits to personal well-being feature much more prominently in our respondents’ reasoning, suggesting that appeals about personal protection may be more effective in the countries under study here.
 
-The most commonly stated reason for vaccine refusal was concern about safety (side effects).
-Around 86% of our surveys were conducted as reports from Phase 2 and 3 clinical trial data were emerging for the earliest commercially available vaccines, but prior to the first Emergency Use Authorization of any vaccine (Pfizer-BioNTech approved by the USA on December 11, 2020).
+The most commonly stated reason for vaccine refusal is concern about safety (side effects).
+The vast majority (86%) of our surveys were conducted as reports from Phase 2 and 3 clinical trial data were emerging for the earliest commercially available vaccines, but prior to the first Emergency Use Authorization of any vaccine (Pfizer-BioNTech approved by the USA on December 11, 2020).
 Early trial data showed that severe adverse effects were extremely rare [@mulligan2020phase; @logunov2021safety; @folegatti2020safety; @voysey2021safety; @baden2021efficacy; @polack2020safety], occurring in fewer than 10\% of people in clinical trials [@wadman2020public].
-Our respondents’ outsized concern about side effects could reflect the rapid pace of vaccine development, [@callaway2020russia] and limited information available about potential COVID-19 vaccine safety at the time of data collection.
+Our respondents’ concern about side effects could reflect the rapid pace of vaccine development [@callaway2020russia] and limited information available about potential COVID-19 vaccine safety at the time of data collection.
 These concerns could also reflect worries about mild, yet common and transient side effects, such as fatigue, muscle pain, joint pain and headache.
 
-Prominent media coverage of adverse events may exacerbate concerns about side effects [@stein2017golden].
+Intensive media coverage of adverse events may exacerbate concerns about side effects [@stein2017golden].
 In particular, new information about rare but severe cases of thrombosis associated with the Astra-Zeneca vaccine that appeared after our data collection period could affect hesitancy levels.
-This is of particular relevance to LMICs, which are likely to rely on the Astra-Zeneca vaccine in their immunization campaigns, through initiatives such as COVAX.
+This is of particular relevance to LMICs, which are likely to rely on the Astra-Zeneca vaccine in their immunization campaigns through initiatives such as COVAX.
 
 Concerns about vaccine efficacy, averaging approximately `r filter(effective_top, group=="All") %>% pull(estimate)`% in the LMIC samples, may also reflect a lack of information about vaccines at the time of our surveys.
-Strikingly, even in low-information environments, respondents in our samples rarely cited conspiracy theories about ulterior motives on the part of corporations, politicians or the pharmaceutical industry, despite widespread popular fears about these issues in higher-income countries [@loomba_measuring_2021].
+However, we note that respondents in our samples rarely cited conspiracy theories about ulterior motives on the part of corporations, politicians or the pharmaceutical industry, despite attention given to fears about these issues in higher-income countries [@loomba_measuring_2021].
 
 <!-- Temp subheading: limitations -->
-An important limitation of our study is that our samples are not fully nationally representative.
+Our study has several limitations, which we address here.
+First, our data are not representative of all LMICs.
+They instead represent a sample of studies in countries where our organizations could quickly and safely mobilize coordinated data collection.
+Second, samples from the countries we include here are not fully nationally representative.
 Phone surveys, while necessary during a global pandemic, do not include individuals who reside outside coverage areas, lack access to a cell phone, or do not respond to calls.
-In addition, as shown in Table \ref{tab:sampling}, several studies focus on sub-populations of interest in pre-existing studies to which questions about COVID-19 vaccination were added.
-Particular care should be taken in any attempt to extrapolate to the national population level from these samples.
-Furthermore, we emphasize that our data are not representative of all LMICs.
-They represent a convenience sample of studies in countries in which our organizations could quickly mobilize coordinated data collection.
+In addition, as shown in Table \ref{tab:sampling}, several studies focus on subnational populations of interest from pre-existing studies to which questions about COVID-19 vaccination were added.
+Particular care should be taken in extrapolating these findings to national populations.
 
-The expressed intentions to take a COVID-19 vaccine that we document in our LMIC samples, if translated into behavior, would meet or exceed the current herd immunity threshold for COVID-19 (estimated at 60-80%, based on the predominant variant in circulation in these countries [@omer2020herd; @aschwanden2021five; @mcneil_2021]).
-However, reported intent may not always convert vaccine uptake [@mceachanetal2011].
-The high salience of COVID-19 due to extensive media coverage may have increased reported intentions.
+In spite of this variation in sample composition, our main findings---of high COVID-19 vaccine acceptance in our LMIC samples relative to the USA and Russia---are remarkably consistent across studies.
+We conduct several robustness checks to probe the sensitivity of our aggregate LMIC analysis to the inclusion of particular samples.
+First, as shown in \hyperref[fig:mainloo]{Supplementary Figure 3}, we re-estimate aggregate vaccine acceptance across our LMIC samples successively dropping one and two study samples at a time.
+Regardless of which samples are excluded, the average vaccine acceptance rate among LMIC samples remains consistent and considerably higher than in the USA and Russia, demonstrating that our results are not driven by the peculiarities of one or two studies.
+Second, we repeat the same analysis excluding all samples that are sub-national in scope, which yields a mean acceptance rate of `r ans_national %>% pull(estimate)`% (CI `r ans_national %>% pull(conf.low)`--`r ans_national %>% pull(conf.high)`%), as shown in the row “All LMICs (National samples)” in Figure \@ref(fig:mainfigure1) and \hyperref[tab:maintabledis]{Supplementary Table 1}.
+
+The expressed intentions to take a COVID-19 vaccine that we document in our LMIC samples, if translated into behavior, would meet or exceed the current herd immunity threshold for COVID-19 in many, but not all, countries (estimated to be between 70 and  80%, based on the predominant variant in circulation in different countries)[@ontario; @aschwanden2021five; @mcneil_2021].
+Reported intentions may however not always translate into vaccine uptake [@mceachanetal2011].
+The high salience of COVID-19 may have increased reported intentions.
 Conversely, reports about side effects and risks associated with expedited vaccine development may have increased hesitancy.
@@
 Indeed, previous research on vaccine hesitancy has emphasized how concerns that arise surrounding vaccination campaigns are often case- and context-specific [@larson2011addressing], making it difficult to predict exactly how COVID-19 vaccines will be received in any given setting.
-The lower COVID-19 vaccine acceptance rates we observe in Russia and the USA, for example, may reflect the politicization of this specific pandemic and vaccine development [@hornsey2020donald; @bokemper2021timing; @aaslund2020responses; @burki2020russian], in addition to generally greater vaccine skepticism.
+The lower COVID-19 vaccine acceptance rates we observe in Russia and the USA, for example, may reflect the politicization of this specific pandemic and of vaccine development [@hornsey2020donald; @bokemper2021timing; @aaslund2020responses; @burki2020russian], in addition to generally greater vaccine skepticism.
 
@@
 Nonetheless, our findings suggest several concrete implications for policy relating to vaccine roll-out in LMICs.
-First and foremost, we document high levels of COVID-19 vaccine acceptance in LMICs compared to Russia and the USA.
-While global vaccine distribution has skewed heavily toward higher-income countries to date [@wouters2021challenges],  our findings suggest that prioritizing distribution to LMICs is justified not only on equity grounds, but on the expectation of “better value” in maximizing global coverage more quickly.
+First and foremost, we document high levels of COVID-19 vaccine acceptance in our LMIC samples compared to Russia and the USA.
+While global vaccine distribution has skewed heavily toward higher-income countries to date [@wouters2021challenges],  our findings suggest that prioritizing distribution to LMICs is justified not only on equity grounds, but on the expectation of higher marginal returns in maximizing global coverage more quickly.
 
-Our findings also imply that, once vaccine distribution to LMICs begins in earnest, interventions should focus on converting positive intentions into action.
-Straightforward, low-cost nudges may be particularly effective in this regard.
+The high stated acceptance rates we document also imply that, once vaccine distribution to LMICs begins in earnest, interventions should focus on converting positive intentions into action.
+Straightforward, low-cost nudges may be effective in this regard.
 Two recent large-scale studies in the USA found that vaccination appointment reminder messages from healthcare providers increased influenza vaccine uptake [@milkmanetal2021a; @milkmanetal2021b].
 Similar interventions have proven effective in increasing immunization in LMIC contexts.
-In Ghana and Kenya, vaccination reminders plus small cash incentives increased childhood immunization coverage [@levine2021; @gibsonetal2017].
+In Ghana and Kenya, vaccination reminders combined with small cash incentives increased childhood immunization coverage [@levine2021; @gibsonetal2017].
 Cash and in-kind incentives programs were also effective in Nigeria and India [@idinsight; @Banerjee2010].
 
-This recommendation is consistent with accepted frameworks, such as the WHO’s Behavioral and Social Drivers of vaccination (BeSD) model, which suggests leveraging favorable intentions through reminders and primes, and reducing access barriers when the vast majority of people intend to be vaccinated [@brewer2017increasing; @whodata].
+This recommendation is consistent with accepted frameworks, such as the WHO’s Behavioral and Social Drivers of vaccination (BeSD) model, which suggest leveraging favorable intentions through reminders and primes, and reducing access barriers when the vast majority of people intend to be vaccinated [@brewer2017increasing; @whodata].
 Particularly since COVID-19 vaccination may be more collectively than individually optimal, ease of access is critical to achieve high coverage [@betsch2013inviting].
+Availability of single-dose vaccines could be advantageous in settings with high vaccination demand but relatively low-capacity healthcare systems, as is the case in many LMICs.
 
-Our findings also suggest directions for the design and delivery of messaging to boost COVID-19 vaccine acceptance and uptake in LMICs.
-We highlight four potential implications.
-First, our data strongly support the view that respondents from LMICs prefer to follow the guidance of actors with the most relevant knowledge and expertise.
-We find high levels of trust in health workers, which suggests that social and behavioral change communication (SBCC) strategies engaging local health workers may be particularly effective in encouraging efficient and comprehensive vaccine uptake and combating remaining hesitancy [@who2020behavioral; @bokemper2021timing].
-Health workers have been the first group to receive the COVID-19 vaccine and are therefore best-positioned to share locally credible experiences of vaccination [@katzman2021primary].
-While celebrities were not identified as a particularly trustworthy source for COVID-19 advice in our study, celebrity endorsements have proven effective in other contexts and may complement a strategy that primarily focuses on health workers [@alatas2019celebrities].
+Our findings also suggest directions for the design and delivery of messaging to address remaining COVID-19 vaccine hesitancy in the countries under study here.
+Persuasion campaigns may be particularly important in countries where acceptance rates are below herd immunity thresholds.
+We highlight three potential implications for messaging below, but urge policymakers and stakeholders to utilize country-specific results to develop further strategies that may work best in their particular context.
+We also echo calls for integrating rigorous impact evaluation of vaccine hesitancy interventions in all contexts, given limited evidence to date [@dube2015strategies].
 
-Second, our findings offer guidance on the specific content of vaccine messaging that is likely to be most persuasive.
+First, our data strongly support the view that respondents from the included set of LMICs prefer to follow the guidance of actors with the most relevant knowledge and expertise.
+We find high levels of trust in health workers, which suggests that social and behavioral change communication (SBCC) strategies engaging local health workers may be particularly effective in combating remaining hesitancy [@who2020behavioral; @bokemper2021timing].
+Health workers have also been the first group to receive the COVID-19 vaccine and are therefore best positioned to share locally credible experiences of vaccination [@katzman2021primary].
+While celebrities were rarely identified as a most trustworthy source for COVID-19 advice in our study, celebrity endorsements have proven effective in other contexts and may complement a strategy that primarily focuses on health workers [@alatas2019celebrities].
+
+Second, our findings offer some guidance on the specific content of vaccine messaging that is likely to be most effective in persuading those who may be hesitant.
 Hesitant respondents were most concerned about side effects and vaccine efficacy.
-This suggests that messaging should highlight the high efficacy rates of the COVID-19 vaccines currently on the market in reducing or eliminating disease, hospitalizations, and death, and communicate accurate information about potential side effects.
-Our data also suggest that messaging should emphasize the direct protective benefits of the vaccine to the adopter, since personal protection, rather than broader concerns about protecting public health, was the top reason expressed for vaccine-acceptance by our respondents.
+This suggests that proactive messaging, initiated before large-scale vaccination campaign roll-out, should highlight the high efficacy rates of the COVID-19 vaccines currently on the market in reducing or eliminating disease, hospitalizations, and death, and communicate accurate information about potential side effects, including the rarity of severe adverse events that may have contributed to hesitancy through widespread media coverage [@goldstein2015health; @puri2020social].
 
-Third, consistent with previous studies on COVID-19 vaccination [@kreps2020factors; @shekhar2021covid; @dror2020vaccine;  @fisher2020attitudes; @wouters2021challenges] our study finds lower vaccine acceptance among women than men, suggesting that messaging strategies should focus on women.
+Third, consistent with previous studies on COVID-19 vaccination [@kreps2020factors; @shekhar2021covid; @dror2020vaccine;  @fisher2020attitudes; @wouters2021challenges] our study finds on average lower vaccine acceptance among women than men, suggesting that messaging strategies focusing on women may be important in addressing overall hesitancy.
 Recent work in Latin America on COVID-19 vaccine messaging found that the provision of basic information about the vaccines was particularly effective in persuading hesitant women [@argote2021messaging].
+More generally, countries may consider tailoring their messaging campaigns to address concerns held by more hesitant sub-populations, which vary across our samples with respect to age, gender and education.
+Additional research is needed to identify and design effective messaging campaigns in order to overcome hesitancy among specific subpopulations in each setting [@goldstein2015health; @dube2015strategies].
 
 Finally, high coverage rates of existing vaccines, coupled with respondents’ reliance on friends and family as information sources, suggest that the general pro-vaccination stance of many LMIC citizens could be leveraged to increase uptake of COVID-19 vaccines as they become available.
-Social learning strategies and norm-setting are powerful drivers of  behavior in many related sectors [@beaman2021can].
-Social signaling of positive attitudes toward and uptake of COVID-19 vaccines may also help shift social norms toward even greater immunization acceptance and two-dose completion in the community at large [@karing2018social].
+This might yield particularly strong results in Colombia and Nepal, where family members and friends are seen as an important source of advice when deciding whether to take a COVID-19 vaccine.
+Social learning strategies and norm-setting are powerful drivers of behavior in many related sectors.
+Social signaling of positive attitudes towards vaccines may help shift social norms toward even greater immunization acceptance and uptake in the community at large [@van2020using; @karing2018social; @ashraf2014no].
+As with messaging, policymakers should consider designing and evaluating social mobilization strategies targeted toward more hesitant subgroups [@jalloh2020mobilize].
+
+\clearpage
 
@@
 To examine heterogeneity across demographic strata, we collected information about gender, age, and education.
-Slight variations in question wording and answer options across studies are documented in [Appendix B](#appendixb).
+Slight variations in question wording and answer options across studies are documented in Supplementary Appendix.
 
@@
 
-Table \ref{tab:sampling} in [Appendix A](#appendixd) summarizes the geographic scope, sampling methodologies and survey modalities of all 15 studies.
-A detailed description of each study is included in [Appendix C](#appendixa).
+Table \ref{tab:sampling} summarizes the dates of data collection, geographic scope, sampling methodologies and survey modalities of all 15 studies.
 
@@
 This was calculated combining all other answer options (“No”, “Don’t Know” and “Refuse”) into a single reference category.
-We estimated average acceptance for each individual sample via ordinary least squares (OLS) weighted by respective study population weights and robust standard errors clustered at the level relevant for the sample.
+We estimated average acceptance for each individual sample via ordinary least squares (OLS) weighted by respective study population weights and using robust standard errors clustered at the level of the sampling cluster.
 
@@
 
-We note the core results would be virtually unchanged at `r round(100*unit_check$estimate[2], 1)`% (`r round(100*unit_check$conf.low[2], 1)`--`r round(100*unit_check$conf.high[2], 1)`) rather than `r round(100*unit_check$estimate[1], 1)`% (`r round(100*unit_check$conf.low[1], 1)` -`r round(100*unit_check$conf.high[1], 1)`) using countries rather than studies as groups in the pooled analysis, that is if we set weights so that the sum of weights in each country (rather than in each study) sum to a constant and cluster standard errors at the country level (rather than the study level).
+We note the core results would be virtually unchanged at `r round(100*unit_check$estimate[2], 1)`% (`r round(100*unit_check$conf.low[2], 1)`--`r round(100*unit_check$conf.high[2], 1)`) rather than `r round(100*unit_check$estimate[1], 1)`% (`r round(100*unit_check$conf.low[1], 1)` -`r round(100*unit_check$conf.high[1], 1)`) using countries rather than studies as groups in the pooled analysis, that is, if we set weights so that the sum of weights in each country (rather than in each study) sum to a constant and cluster standard errors at the country level (rather than the study level).
 
@@
 
-Burkina Faso: Béchir Wendemi Ouédraogo (M&E Associate), Achille Mignondo Tchibozo (Research Manager) and Touba Bakary Pare (Senior Field Manager) at IPA Burkina Faso in Ouagadougou for their work on the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+Burkina Faso: IPA Burkina Faso staff in Ouagadougou for their support of the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
 
-Colombia: Margarita Rosa Cabra Gacia (Senior Research Associate), Laura Polanco, María Juliana Otálora (Research Analyst), Sofía Jaramillo (Research Manager) and Mery Galindo (Field Coordinator) at IPA Colombia in Bogotá  for their work on the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+Colombia: IPA Colombia staff in Bogotá for their support of the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
 
-India: Bhartendu Trivedi, Yashashvi Singh, Tatheer Fatima and the field team of Morsel Research and Development.
+India: Pronab Sen (Country Director), Kumar Das (Programme Policy Manager) and Bijeta Mohanty (Country Economist) at IGC India and Morsel Research and Development’s field team.
 
-Mozambique: Alberto Arlindo, Imamo Mussa, Ismail Mussa, Frederica Mendonça and Simão Paiva from NOVAFRICA Mozambique office.
+Mozambique:Frederica Mendonça and Simão Paiva from NOVAFRICA Mozambique office.
 
-Nepal: Arjun Kharel and field staff at the Centre for the Study of Labour and Mobility (CESLAM) in Kathmandu.
+Nepal: Field staff at the Centre for the Study of Labour and Mobility (CESLAM) in Kathmandu.
 
-Nigeria:  Opeyemi Adeojo (Department of Sociology, University of Lagos), Deborah Anigo, Isaac Obara, Segun Fayomi, and Aishwarya Kumar at the Busara Center for Behavioral Economics, and Sarah Ryan (University of Illinois at Chicago) for research assistance.
+Nigeria:  Segun Fayomi and Aishwarya Kumar at the Busara Center for Behavioral Economics, and Sarah Ryan (University of Illinois at Chicago) for research assistance.
 
-Pakistan 1: Ahsan Tariq and Shan e Muhammad Malik at the Institute for Development and Economic Alternatives (IDEAS) in Lahore as survey wing leads and Hamid Ali Tiwana for research assistance.
+Pakistan 1: Staff at the Institute for Development and Economic Alternatives (IDEAS) in Lahore for their contributions to the Sheikhupura police study sample from which the questions used in the Pakistan 1 study were drawn.
 
-Pakistan 2: Staff and the internal survey firm at the Centre for Economic Research Pakistan (CERP).
+Pakistan 2: Staff of the internal survey firm at the Centre for Economic Research Pakistan (CERP) for their contributions to the Economic Vulnerability Assessment (EVA) project from which the questions used in the Pakistan 2 study were drawn.
 
-Rwanda: Jean Leodomir Habarimana Mfura (Research and Policy Coordinator), Jean Aime Nsabimana and Gisele Manirabaruta (Field Manager) at IPA Rwanda in Kigali for their work on the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+Rwanda: IPA Rwanda staff in Kigali for their support of the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
 
@@
 
-Sierra Leone 1: Filippo Cuccaro (Research Coordinator) and Fatoma Momoh (Senior Field Manager) at IPA Sierra Leone in Freetown for their work on the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+Sierra Leone 1: IPA Sierra Leone staff in Freetown for their support of the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
 
-Sierra Leone 2: Sellu Kallon (Field Manager), Junisa Nabieu (Field Supervisor), Momoh Flee (Field Supervisor), Hamid Kai, Mohamed Lamin (Field Supervisor) and all enumerators at IGC-Sierra Leone Freetown office and Wageningen University’s Project “Tracking the Economic Consequences of COVID-19 in Sierra Leone”.
+Sierra Leone 2: Junisa Nabieu (Field Supervisor), Momoh Flee (Field Supervisor), Hamid Kai, Mohamed Lamin (Field Supervisor) and all enumerators at IGC-Sierra Leone Freetown office and Wageningen University’s Project “Tracking the Economic Consequences of COVID-19 in Sierra Leone”.
 
-Uganda 1: Staff at IPA Uganda, especially Sarene Shaked and Gloria Ayesiga, for their intellectual contributions, research assistance, and support throughout the Uganda 1 study.
+Uganda 1: Staff at IPA Uganda for their intellectual contributions, research assistance, and support throughout the study.
 
-Uganda 2: Co-PIs Ana Garcia Hernandez, Leah Rosenzweig, Lily Tsai, and Elly Atuhumuza, Martin Atyera, and their team of survey enumerators and support staff at IPA Uganda.
+Uganda 2: Co-PIs Ana Garcia Hernandez, Paul Kiwanuka-Mukiibi, Leah Rosenzweig, Lily Tsai, and Elly Atuhumuza and the team of survey enumerators and support staff at IPA Uganda.
 
@@
 IPA thanks staff from its global offices for their research assistance and support throughout the RECOVR survey.
-Hugo Salas (IPA Mexico) contributed to data analysis for Burkina Faso, Rwanda and Sierra Leone.
-Margarita Rosa Cabra Garcia also contributed to data analysis for Colombia.
-At IPA New York and Washington, DC, Michael Rosenbaum and Savanna Henderson provided research assistance.
+At IPA New York and Washington, DC, Michael Rosenbaum and Savanna Henderson provided research support.
 
@@
 
-Centre for Economic Research Pakistan (CERP) thanks Javaeria Qureshi (University of Illinois Chicago), Taimur Shah (CERP), and Basit Zafar (University of Michigan) for their contributions to the Economic Vulnerability Assessment (EVA) project from which the questions used in the Pakistan 2 study were drawn.
-
 # Contributors {-}
-JSo, SW, NMe, AS, NMc, GS, MV and AM are co-first authors. DK, MC, MT, MH, AMM and SO are co-last authors. AMM and SO are also the corresponding authors. 
+JSo, SW, NMe, AS, NMc, GS, MV and AAM are co-first authors. DK, MC, MT, MH, AMM and SO are co-last authors. AMM and SO are also the corresponding authors. 
 DK, AMM, MT, NMe, MC, and MV conceived of the study and provided overall guidance.
-SAb and NMe led the literature search, with input from AS, NMc, SW, AMM, AM and JSo.
-SW, NMe, AS, NMc, MV, GS, AA, SA, BA, AB, EB, CMB, AC, EC, MF, AG, AK, SK, RL, MBN, MP, JSh, JSv, PV, LB, BZ, MC, SAs, AC, AF, AH, MC, MT, and MH oversaw data collection as part of other research efforts.
+SAb and NMe led the literature search, with input from AS, NMc, SW, AMM, AAM and JSo.
+SW, NMe, AS, NMc, MV, GS, AA, SA, BA, AB, EB, CMB, AC, EC, MF, AG, AK, SK, RL, MBN, MP, JQ, JSh, JSv, PV, LB, BZ, MC, SAs, AC, AF, AH, MC, MT, MH,CV, LW, BZ and BZa oversaw data collection as part of other research efforts.
+OA, DA, MA, MAw, MCG, AC, FC, GE, MG, SJA, SKa, AK, AKh, SM, GM, LM, FM, AMu, IM, JN, IO, MJO, BWO, TP, LP,  MR, IR, TS, SS, , AT, AMT, HT, and BT implemented the surveys, including training and oversight of enumerators and management of sampling for the surveys.
 SW, NMe, and MT coordinated the project across study samples.
@@
 MH supervised the data analysis.
-JSo, SW, NMe, AMM, AS, NMc and MV wrote the first draft of the manuscript, with guidance from AM and SO.
-JSo, SW, NMe, AS, NMc, MV, SAb, EB, MP, JSh, PV, BZ, MC, MT, MH, AMM and SO revised the manuscript.
+JSo, SW, NMe, AMM, AS, NMc and MV wrote the first draft of the manuscript, with guidance from AAM and SO.
+JSo, SW, NMe, AS, NMc, MV, SAb, EB, MP, JSh, PV, BZ, MC, MT, MH, AMM, AAM and SO revised the manuscript.
 All authors approved the final version of the manuscript. All authors had full access to all the data used in this study and had final responsibility for the decision to submit for publication.
@@
 
+```{=latex}
+\begin{table}[!h]
+\caption{\label{tab:summary}Policy summary}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{30em}}
+\toprule
+Background & 
+We analyze COVID-19 vaccine acceptance, hesitancy and their drivers across 15 survey samples covering ten low- and middle-income countries (LMICs) in Asia, Africa, and South America, as well as Russia and the United States, comprising `r nice(nrow(df))` individuals.
+\\
+\\
+Main findings and limitations & Willingness to take a COVID-19 vaccine is considerably higher in the LMICs in our sample than in the United States and Russia.
+The personal protective benefit of vaccination is the most frequently cited reason for vaccine acceptance.
+Concern about side effects is the most commonly cited reason for vaccine hesitancy.
+Health workers are considered the most trusted sources of guidance about COVID-19 vaccine choices.
+Our data are not representative of all LMICs, and some individual samples are not nationally representative.
+However, our main findings---of high COVID-19 vaccine acceptance in our LMIC samples relative to the USA and Russia---are remarkably consistent across samples and specifications.
+\\
+\\
+Policy implications & While global vaccine distribution has skewed heavily toward higher income countries to date, the high levels of vaccine acceptance we identify suggest that prioritizing distribution to LMICs may be an efficient way to achieve immunity on a global scale, and prevent novel variants from emerging.
+Vaccination campaigns should focus on converting positive intentions into uptake, which may require investment in ‘last-mile’ delivery.
+Engaging health workers to deliver vaccine information, leveraging pro-vaccine norms, and messaging focused on vaccine effectiveness and safety may be effective in addressing remaining hesitancy.\\
+\bottomrule
+\end{tabular}}
+\end{table}
+```
+
 \newpage
-```{r otherv, echo=FALSE}
+```{r sampling}
+tab_sampling
+```
+
+\newpage
+```{r otherv}
 tab_1b
 ```
-
-```{r sampling, echo=FALSE}
-tab_sampling
-```
+\newpage
 
@@
 Second, we list the number of observations included in the study.
+Data are presented as mean values +/- SD.
 In the plot, points represent the estimated percentage of individuals who would take the vaccine.
@@
 \end{figure}
-```
-
-```{r yes, results = "asis"}
-tab_reasons_y
 ```
@@
 \scriptsize{Figure 2 shows the percentage of respondents mentioning reasons why they would not take the COVID-19 vaccine.
+For each study, we present the sample size in parentheses.
+Data are presented as mean values +/- SD.
 In the plot, points represent the estimated percentage of individuals that would not take the vaccine or do not know if they would take the vaccine for each possible response option.
@@
 An estimated average for all studies in LMICs is also shown.
-Size of points illustrates the number of observations in each response option.
 Studies India and Pakistan 2 are not included because they either did not include the question or were not properly harmonized with the other studies.}
@@
 
-\clearpage
-
-# Supplementary Appendix {-}
-
-## Appendix A: Supplementary tables, figures and results {.unnumbered #appendixd}
-
-```{r, results = "asis", echo=FALSE}
-tab_fig1
-```
-
-\newpage
-
-```{r yesall, results = "asis", echo=FALSE}
-tab_reasons_y_all
-```
-
-\newpage
-
-```{r yesall1, results = "asis", echo=FALSE}
-tab_reasons_y_age
-```
-
-\newpage
-
-```{r no, results = "asis", echo=FALSE}
-tab_fig2
-```
-
-\newpage
-
-```{r trust, results = "asis", echo=FALSE}
-tab_trust
-```
 \newpage
@@
 ```{=latex}
-\scriptsize{Figure 4 shows histograms of actors and institutions that respondents say they would trust most to help them decide whether or not to take the COVID-19 vaccine.
+\scriptsize{Figure S1 shows histograms of actors and institutions that respondents say they would trust most to help them decide whether or not to take the COVID-19 vaccine.
+Respondents were only permitted to select one most trusted  actor or institution.
+Responses are broken down by gender of respondent.}
+\end{figure}
+```
+
+\pagebreak
+
+```{=latex}
+\begin{figure}[!ht]
+\caption{Trusted actors and institutions, broken down by vaccine acceptance \label{fig:vaccacc}}
+```
+```{r histcattrust, fig.height=9, fig.width = 10, warning = FALSE, dev='tikz'}
+fig_hist_categories
+```
+```{=latex}
+\scriptsize{Figure S2 shows histograms of actors and institutions that respondents say they would trust most to help them decide whether or not to take the COVID-19 vaccine.
 Respondents were only permitted to select one most trusted  actor or institution.
@@
 \begin{figure}[!ht]
-\caption{Trusted actors and institutions, broken down by vaccine acceptance \label{fig:genderhist}}
+\caption{Average vaccine acceptance across all LMIC countries leaving one or two study samples out
+ \label{fig:mainloo}}
 ```
-```{r histcattrust, fig.height=9, fig.width = 10, warning = FALSE, dev='tikz', echo=FALSE}
-fig_hist_categories
+```{r mainloo, fig.height=10, fig.width = 9, warning = FALSE, dev='tikz', echo = FALSE}
+fig_hist_loo
 ```
 ```{=latex}
-\scriptsize{Figure 5 shows histograms of actors and institutions that respondents say they would trust most to help them decide whether or not to take the COVID-19 vaccine.
-Respondents were only permitted to select one most trusted  actor or institution.
-Responses are broken down by acceptance of the COVID-19 vaccine.
-The color of the bars reflect the answer given to the question ``If a COVID-19 vaccine becomes available in [country], would you take it?'' with ``No'' and ``Don't know'' pooled together and ``All'' combined average of ``Yes'' and ``No / Don't know''}
+\scriptsize{Figure S3 shows distribution of estimates of average acceptance for all studies in LMICs (excluding USA and Russia) leaving one and two study samples out at a time.
+Figure also shows distributions of subgroup averages by gender, education and age leaving one and two study samples out at a time.
+To directly compare the resulting distributions to the estimates reported in Figure 1, we plot point estimates reported in Figure 1 for all LMIC studies, Russia and the US.}
 \end{figure}
+```
+\pagebreak
+
+\clearpage
+
+# Supplementary Appendix {-}
+
+\beginsupplement
+\setcounter{page}{1}
+
+\newpage
+
+```{r, results = "asis"}
+tab_fig1
+```
+
+\newpage
+
+```{r yes, results = "asis"}
+tab_reasons_y
+```
+
+\newpage
+
+```{r yesall, results = "asis"}
+tab_reasons_y_all
+```
+
+\newpage
+
+```{r yesall1, results = "asis"}
+tab_reasons_y_age
+```
+
+\newpage
+
+```{r no, results = "asis"}
+tab_fig2
+```
+
+\newpage
+
+```{r trust, results = "asis"}
+tab_trust
 ```
@@
 
-```{r, results = "asis", echo=FALSE}
+```{r, results = "asis"}
 dmeans
@@
 
-```{r, results = "asis", echo=FALSE}
+```{r, results = "asis"}
 nas
@@
 
-```{r tcds, echo=FALSE}
-t_country_differences
+```{r tcds}
+t_country
 ```
-________________
 
@@
 
-## Appendix B: Question wording and answer options per study {.unnumbered #appendixb}
+________________
 
-```{r tabq1, echo=FALSE}
+\clearpage
+
+```{r tabq1}
 tab_question1
@@
 
-```{r tabq2, echo=FALSE}
+```{r tabq2}
 tab_question2
@@
 
-```{r tabq3, echo=FALSE}
+```{r tabq3}
 tab_question3
@@
 
-```{r tabq4, echo=FALSE}
+```{r tabq4}
 tab_question4
 ```
-________________
-\newpage
-
-## Appendix C: Sample descriptions {.unnumbered #appendixa}
-
-The case history data for all countries in our sample is extracted from the Johns Hopkins University Center for Systems Science and Engineering (JHU CSSE) database.^[Dong, E., Du, H., & Gardner, L.
-(2020).
-An interactive web-based dashboard to track COVID-19 in real time.
-The Lancet infectious diseases, 20(5), 533-534.]
-
-### Burkina Faso, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA){-}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-\item First confirmed case: March 9, 2020 
-\item Number of confirmed cases 2,335 as of  October 15, 2020 
-\item Number of deaths:  65 as of October 15, 2020
-\end{itemize}
-
-\textbf{Target Population}: A random sample of all adults with mobile phone numbers in the country, based on national communications authority number allocation plans.
-
-\textbf{Original Study Design:} N/A
-
-\textbf{COVID-19 Survey Design:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share for a two-round panel survey.
-
-\emph{Sampling Frame:} All mobile phone numbers in Burkina Faso.
-
-\emph{Survey Dates:} October 15 to December 4, 2020 (Round 1 June 6-15, 2020)
-
-\emph{Sample size, tracking and attrition:}  Sample includes 977 respondents from the second round of a panel.
-In the first round conducted between June 6 to 15, 2020, 1,356 individual surveys were contacted through Random Digit Dialing (RDD) from the sampling frame of all mobile phone numbers in Burkina Faso.
-2,313 working numbers yielded 1,383 eligible respondents for a completion rate of 98\% of eligible respondents.
-
-\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.
-
-\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15608, and the Burkina Faso Institutional Ethics Committee for Health Sciences Research, approval A13-2020.
-
-### Colombia, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA) {-}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-\item First confirmed case: March 6, 2020
-\item Number of confirmed cases:  456,689 as of August 15, 2020
-\item Number of deaths:  14,810 as of August 15, 2020
-\end{itemize}
-
-\textbf{Target Population}: A random sample of all numerically possible mobile phone numbers in the country, based on national communications authority number allocation plans.
-
-\textbf{Original Study Design:} N/A
-
-\textbf{COVID-19 Survey Design:}
-
-\emph{Sampling Frame:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share.
-
-\emph{Survey Dates:} August 15-25, 2020 (Round 1 May 8-15, 2020)
-
-\emph{Sample size, tracking and attrition:} Sample includes 1,012 respondents contacted in the second round of a panel of 1,507.
-
-\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.
-
-\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15582.
-
-### India, Coping with COVID-19 in Slums: Evidence from India Subnational sample, Nova School of Business and Economics, The Institute for Fiscal Studies, University of St. Andrews {-}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-\item First confirmed case: January 30, 2020
-\item Number of confirmed cases: 198,370 as of June 1, 2020 
-\item Number of deaths: 5,608 as of June 1, 2020 
-\end{itemize}
-
-\textbf{Target Population}:  Random subset of slum populations in Lucknow and Kanpur, Uttar Pradesh, India.
-Socio-economic variables are only collected for a representative sample of the population relying on community toilets or open defecation to fulfil their sanitation needs.
-
-\textbf{Original Study Design:} Randomized controlled trial, with complete census of households within 142 slums (September to December 2017), and a series of household and caretaker surveys, objective measurements, incentivized behavioural measurements, and a Structured Community Activity, collected for a sub-set of 100 slums between April 2018 and September 2019.
-
-\emph{Intervention:} Catchment areas of CTs were randomly allocated to two interventions.
-The first intervention aimed at community toilet improvements by offering caretakers the choice of a grant to be spent for improvements in the facility.
-Following the grant, caretakers were offered a large financial reward conditional on the cleanliness of the facility.
-The second intervention added to this CT improvement awareness creation among potential users through face-to-face information sessions, leaflets, monthly reminders using voice messages sent to mobile phones, and posters hung in the CTs.
-
-\emph{Sampling Frame:} A two-step sampling was applied, first, study households from the main study sample were sampled, then households from the whole slum population were added.
-
-\emph{Survey Dates:} 
-Baseline: June to July 2020, Follow-up 1: October to November 2020, Follow-up 2:  December 16, 2020 to January 18, 2021.
-
-\emph{Sample size, tracking and attrition:} 3,991 households, with a mean of 28 households per cluster (142).
-Non-response Baseline: 25%, Attrition rate Baseline to Follow-up (1 and 2): 13%, Randomly selected replacement households for Follow-up (1 and 2): 1,277.
-
-\emph{Sampling Weights:} Included
-
-\emph{IRB Approval:} Approval was secured from London School of Economics (REC ref. 1132). The pre-analysis plan was registered on the AEA RCT registry (RCT ID AEARCTR-0006564).
-
-### Mozambique Subnational sample, International Growth Center, Nova School of Business and Economics {-}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-\item First confirmed case: March 22, 2020
-\item Number of confirmed cases:  12,777 as of October 30, 2020 
-\item Number of deaths:  91 as of October 30, 2020
-\end{itemize}
-
-\textbf{Target Population}: Microentrepreneurs in urban markets of Maputo and household heads from the province of Cabo Delgado.
-
-\textbf{Original Study Design:} Initial data were collected in-person in two different studies.
-For microentrepreneurs in Maputo, the data were collected between October 2013 and April 2014 (baseline), and between July and November 2015 (endline).^[Original study: http://catiabatista.org/bsv_mm_urban.pdf] For household heads in Cabo Delgado, the data were collected in-person between August and September 2016 (baseline), and between August and September 2017 (endline).^[Original study: https://www.aeaweb.org/articles?id=10.1257/aer.20190842]
-
-\emph{Intervention:} The first study was dedicated to analyzing the impacts of interventions targeting microentrepreneurs in urban markets on financial inclusion and literacy.
-The second study focused on the role of information to counteract the political resource curse after a substantial natural gas discovery.
-
-\emph{Sampling Frame:} The first initial sample was selected by in-field random sampling in 23 urban and periurban markets in Maputo and Matola.
-Stratification was based on the gender of the respondent and on the type of establishment (stall vs.
-store).
-The second initial sample was selected to be representative of 206 communities in the province of Cabo Delgado, randomly drawn from the list of all 421 polling locations in the sampling frame, stratified on urban, semiurban, and rural areas.
-This survey in this paper was done by phone.
-
-\emph{Survey Dates:} October 30 to November 21, 2020 (Maputo) and  November 6 to November 30, 2020 (Pemba).
-
-\emph{Sample size, tracking and attrition:} 554 microentrepreneurs from Maputo and 308 households from Cabo Delgado.
-
-\emph{Sampling Weights:} N/A
-
-\emph{IRB Approval: The approval was secured from Universidade Nova de Lisboa on July 14, 2020.
-
-### Nepal,  Western Terai Panel Survey (WTPS) Subnational sample, Yale University, Yale Research Initiative on Innovation and Scale (Y-RISE){-}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-\item First confirmed case: January 23, 2020
-
-\item Number of confirmed cases:  233,452 as of December 1, 2020 
-\item Number of deaths:   1,529 as of December 1, 2020
-\end{itemize}
-
-\textbf{Target Population}: Rural households in the districts of Kailali and Kanchanpur.
-
-\textbf{Original Study Design:} Initial baseline data was collected in-person in July of 2019, and 5 rounds of phone survey data were collected between August 12, 2019 and January 4, 2020.
-
-\emph{Sampling Frame:} The phone survey sample includes 2,636 rural households in the districts of Kailali and Kanchanpur, which represent the set of households that responded to phone surveys from an original sample of 2,935 households.
-This sample was constructed by randomly sampling 33 wards from 15 of the 20 sub-districts in Kailali and Kanchanpur and selecting a random 97 villages from within those wards.
-At the time of baseline data collection in July of 2019, 7 of these 97 villages were dropped from the sample due to flooding.
-Households belong to the bottom half of the wealth distribution in these villages, as estimated by a participatory wealth ranking exercise with members of the village.
-
-\emph{Survey Dates:}December 1st - December 11, 2020
-
-\emph{Sample size, tracking and attrition:}  1,392 households
-
-\emph{IRB Approval:} This research was approved via Yale University IRB Protocol 2000025621.
-
-### Nigeria Subnational sample, WZB Berlin Social Science Center, University of Illinois Chicago{-}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-\item First confirmed case: February 28, 2020
-\item Number of confirmed cases: 65,693 as of November 18, 2020 
-\item Number of deaths:  1,163 as of November 18, 2020 
-\end{itemize}
-
-\textbf{Target Population}: Christian and Muslim men and women, age 18 and above, living in Kaduna state, Nigeria.
-
-\textbf{Original Study Design}:  Initial data was collected from a subset of the sample in December 2019 (in person survey) and July - Aug 2020 (phone survey) as part of an experiment testing the effects of a brief radio program on inter-religious animus.
-A random walk procedure and random sampling were used within households to recruit a representative sample of adults in Kaduna town.
-The rest of the sample was recruited for the study in Aug 2020 by purchasing phone lists for residents of Kaduna State.
-
-\emph{Intervention:} The study examines the effects of a radio program and a TV drama on  inter-religious animus.
-The subset of  the sample in the radio study was randomly assigned to listen to a brief radio program on one of the following topics: (1) an inter-religious storyline, (2) an intra-religious storyline, and (3) a message about maintaining safe health practices.
-All respondents in the sample participated in a study examining the effect of viewing an inter-religious storyline unfolding over a full season of a popular TV drama, Dadin Kowa.
-The season aired from Aug - Oct 2020.
-A third of the sample were encouraged to watch Dadin Kowa, a third were encouraged to watch the TV station Africa Magic Hausa at the same time Dadin Kowa aired, and a third were in the treatment-as-usual group.
-All participants received a weekly incentivized SMS quiz from Aug - Oct 2020.
-
-\textbf{COVID-19 Survey Design:} This survey is not primarily about COVID-19, but was designed as an endline survey to follow the TV drama intervention described above.
-The goal of this survey is to measure a range of attitudinal outcomes related to Christian-Muslim relations (including prejudice, intergroup threat perceptions, dehumanization, and support for the use of violence, among others).
-We included nine of the standardized COVID-19 vaccine-related questions collected specifically for this vaccine acceptance study in the final module of the endline survey.
-
-\emph{Sampling Frame:} 950 respondents in the sample were recruited in person through a random sampling procedure in the Kaduna metropolitan area (pre-COVID).
-The remaining 1,700 respondents were recruited into the study over the phone from lists of phone numbers of Kaduna state residents that were purchased from a private vendor.
-
-\emph{Survey Dates:} November 18 - December 18, 2020.
-
-\emph{Sample size, tracking and attrition:} All 1,834 individuals who completed the endline survey are included.
-
-\emph{Sampling Weights:} N/A
-
-\emph{IRB Approval:} This study was reviewed by the IRB at the University of Pennsylvania (Protocol 834548), and it was determined on November 20, 2019 to meet the criteria for review exemption (45 CFR 46.104, category \#2).
-
-### Pakistan {-}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-\item March 6: First confirmed case: February  26, 2020 
-\item Number of confirmed cases:  271,887 as of July 24, 2020 
-\item Number of deaths:  5,787 as of July 24, 2020 
-\end{itemize}
-
-### Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample, Sheikhupura Police Study Sample, Institute of Development and Economic Alternatives, Lahore University of Management Science, London School of Economics, Princeton University (Pakistan 1) {-}
-
-\textbf{Target Population}: A representative sample of adults from 108 of 151 police beats in Sheikhupura and Nankana districts of Punjab Province.
-
-\textbf{Original Study Design:} N/A
-
-\textbf{COVID-19 Survey Design:} The EVA survey involved calls to all households in the stratified random sample for the policing study midline survey.
-
-\emph{Sampling Frame:} Households in Sheikhupura and Nankana districts.
-
-\emph{Survey Dates:} July 24 to September 9, 2020
-
-\emph{Sample size, tracking and attrition:}  Sample includes 1,473 respondents.
-
-\emph{Sampling Weights:} Post-stratification weights are computed to adjust for the sampling process, which involved stratifying first on 27 police stations, then within each police station on beats, then PPS sampling within beats using Asiapop population data.
-
-\emph{IRB Approval:} This research was approved via Princeton University IRB Protocol 7250.
-
-### Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample (Pakistan 2) {-}
-
-\textbf{Target Population}: All possible mobile phone numbers (in the province of Punjab) generated based on the local mobile phone number structure in Pakistan.
-
-\textbf{Original Study Design:} N/A
-
-\textbf{COVID-19 Survey Design:} The EVA survey involved making calls to individuals in Punjab based on random digit dialing.
-
-\emph{Sampling Frame:} Individuals with mobile phones in Punjab.
-
-\emph{Survey Dates:}  September 2 to October 13, 2020
-
-\emph{Sample size, tracking and attrition:}  Sample includes 1,492 respondents.
-
-\emph{Sampling Weights:} N/A.
-
-\emph{IRB Approval:} This research was approved by Lahore University of Management Sciences IRB Protocol LUMS-IRB/07012020SA.
-
-### Rwanda, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA){-}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
- \item First confirmed case: March 14, 2020
- \item Total cases:  5,017 as of October 22, 2020 
-\item Total deaths:  34 as of October 22, 2020 
-\end{itemize}
-
-\textbf{Target Population}: A random sample of all numerically possible mobile phone numbers in the country, based on national communications authority number allocation plans.
-
-\textbf{Original Study Design:} N/A
-
-\textbf{COVID-19 Survey Design:}Phone survey
-
- \emph{Sampling Frame:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share.
-
-\emph{Survey Dates:} October 22 to November 5, 2020 (Round 1 June 4 -12, 2020)
-
-\emph{Sample size, tracking and attrition:}Sample includes 1,355 respondents contacted in the second round of a panel of 1,480.
-
-\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.
-
-\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15591, Rwanda National Institute for Scientific Research permit No.0856/2020/10/NISR; and Rwanda National Ethics Committee approval No.16/RNEC/2020.
-
-### Russian Federation, Research on COVID-19 in Russia’s Regions (RoCiRR) Subnational  sample, International Center for the Study of Institutions and Development (HSE University, Moscow, Russia) and Economics Department of Ghent University, WZB Berlin Social Science Center, Columbia University{-}
-
-\textbf{COVID-19 Experience}
-\begin{itemize}
-\item First confirmed case: January 31, 2020
-\item Number of confirmed cases: 1,720,063 as of November 6, 2020 
-\item Number of deaths:  29,654 as of November 6, 2020 
-\end{itemize}
-
-\textbf{Target Population}: Adult internet users who reside in one of 61 federal subjects (federal cities, oblasts, republics, krais and autonomous okrug) of Russia.
-The regions included in the study are Republics: \emph{Bashkortostan, Karelia, Komi, Mariy El, Mordovia, Tatarstan, Udmurtia, Chuvashia}.
-Krais: \emph{Altai, Krasnodarsky, Krasnoyarsky, Permsky, Primorsky, Stavropolsky, Khabarovsky}.
-Oblasts: \emph{Arkhangelsk, Astrakhan, Belgorod, Bryansk, Vladimir, Volgograd, Vologda, Voronezh, Ivanovo, Irkutsk, Kaliningrad, Kaluga, Kemerovo, Kirov, Kostroma, Kurgan, Kursk, Leningrad, Lipetsk, Moscow, Murmansk, Nizhny Novgorod, Novgorod, Novosibirsk, Omsk, Orenburg, Orel, Pskov, Penza, Rostov, Ryazan, Samara, Saratov, Sverdlovsk, Smolensk, Tambov, Tver, Tomsk, Tula, Tyumen, Ulyanovsk, Chelyabinsk, Yaroslavl}.
-Other: \emph{Moscow, Saint Petersburg, Khanty-Mansiysk Autonomous Okrug -- Ugra}.
-The remaining 24 federal subjects were excluded from the study due to inability to enroll sample size with desired characteristics (sample size, age, gender and education group composition) and account for less than 14% of the total adult population of Russia.
-
-\textbf{Original Study Design:} N/A
-
-\textbf{COVID-19 Survey Design:} The study was designed to measure the impact of pandemics on Russians, mostly those who live in cities with more than 100,000 residents.
-It contains a number of questions on the personal experience, norms and values, trust in government institutions, provision of social services, and mass media use.
-Region and geolocality of every respondent are recorded.
-
-\emph{Sampling Frame:} In total 25,558 respondents received the module on vaccine acceptance.
-The sample was enrolled from the pool of Russian online survey company OMI (Online Market Intelligence).
-The sampling was specifically targeted at having a minimum of 150 respondents in each of the 61 regions and including respondents from all the main age and gender groups within each region.
-Respondents were also selected so that at least 40% of respondents did not have higher education, in accordance with higher education rates in Russia.
-Out of 25,558 recruited respondents, 22,125 completed the survey.
-Among 22,125 respondents who completed the survey, 20,821 were enrolled from the general pull of the survey company respondents, while the remaining 1,304 respondents were enrolled among residents of cities with populations below 100,000 and rural areas.
-
-\emph{Survey Dates:} November 6 - December 1, 2020
-
-\emph{Sample size, tracking and attrition:} 22,125 respondents who completed the survey with the vaccine acceptance module included.
-
-\emph{Sampling Weights:} Post-stratification weights are computed to match marginal distributions of age, gender and education among the adult population of Russia with target proportions coming from the 2019 Yearbook and 2015 Microcensus released by Russian Federal Bureau of National Statistics (Rosstat).
-
-\emph{IRB Approval:} This study was approved via Columbia University IRB Protocol IRB-AAAT4453.
-
-### Sierra Leone {-}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-        \item First confirmed case: March 20, 2020
-        \item Total cases:  2,252 as of October 2, 2020 and 3,030 as of January 20, 2021 
-        \item Total deaths:  72 as of October 2, 2020 and 77 as of January 20, 2021 
-\end{itemize}
-
-#### Sierra Leone, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA) (Sierra Leone 1) {-}
-
-\textbf{Target Population}: A random sample of all numerically possible mobile phone numbers in the country, based on national communications authority number allocation plans.
-
-\textbf{Original Study Design:} N/A
-
-\textbf{COVID-19 Survey Design:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share
-
- \emph{Sampling Frame:} All active mobile phone numbers in Sierra Leone.
-
-\emph{Survey Dates:} October 2-19, 2020 (Round 1 May 27 to June 15, 2020)
-
-\emph{Sample Size, tracking and Attrition:} Sample includes 1,070 respondents contacted in the second round of a panel of 1,304.
-
-\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.
-
-\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15592, and Sierra Leone Ethics and Scientific Review Committee approval (no approval number, letter available upon request).
-
-#### Sierra Leone, Towns that are Candidates for Rural Electrification Nation-wide sample, International Growth Centre (IGC), Wageningen University & Research, Yale Research Initiative on Innovation and Scale (Y-RISE), WZB Berlin Social Science Center and Columbia University (Sierra Leone 2) {-}
-
-\textbf{Project Title:} Sierra Leone Rural Electrification (SLRE)
-
-\textbf{Target Population}: Households in 195 rural towns across all 14 districts of Sierra Leone. Of these, 97 villages were selected to benefit from an electrification program.
-
-\textbf{Original Study Design:} Initial baseline data was collected during late 2019 and early 2020 as part of a study to assess the impact of Rural Electrification in rural towns in Sierra Leone.
-
-\emph{Intervention:} The Government of Sierra Leone (GoSL) in collaboration with the United Nations Office for Project Services (UNOPS) and international donors is implementing the Rural Renewable Energy Project (RREP).
-In its first wave, during 2017, the project provided stand-alone solar photovoltaic powered mini-grids to 54 communities across the country.
-Construction of mini-grids in a further 43 towns is ongoing.
-In RREP communities, engineers construct 6kW--36kW power mini-grids that provide reliable power year-round.
-Electricity is free for schools and clinics.
-Residential and commercial users can acquire connections from commercial operators.
-
- \emph{Village Sampling Frame:} Household data was collected in 195 towns across all 12 districts of Sierra Leone.
-The GoSL selected 97 towns with (planned) mini-grids.
-We used Propensity Score Matching to select 98 control communities.
-Within communities, respondents were randomly selected from a census roster stratified by occupation status of farmers, business owners and other occupations [47 percent, 47 percent and  7 percent].
-In each village, the intended sample was 43 households (20 farmers, 20 businesses, 3 others).
-Data was collected during June--July (108 communities) and November--December 2019 (87 communities).
-If a household on the sampling list was not available on the village visit day, we had a randomly sampled list of replacement households to survey.
-The replacement household would be the same occupation as the sampled household would have been so the sample ratio of 20-20-3 still held in each community.
-
-\textbf{COVID-19 Survey Design:}  The goal was to assess households’ degree of economic vulnerability in the face of the COVID-19 pandemic.
-
-\emph{Sampling Frame:} The COVID-19 survey data comprises 2,110 respondents from 186 towns from the original baseline survey.
-Phone surveys were attempted to all 195 rural communities from the baseline survey.
-The total baseline household sample comprised 7047 respondents.
-We recontacted all baseline respondents that listed a phone number (4,594 respondents) and obtained informed consent for the phone survey.
-We implemented several waves of the phone survey, recontracting a respondent about every month.
-In wave 7, we added questions related to Vaccine Acceptability.^[The data was first reported in https://www.theigc.org/wp-content/uploads/2020/05/Meriggi-et-al-Data-Brief-2020.pdf].
-
-\emph{Survey Dates:} October 7, 2020 to January 20, 2021 (earlier rounds included Wave 1: April 29-May 15; Wave 2: May 15-June 4; Wave 3: June 5-June 17; Wave 4: June 17-June 30; Wave 5: July 1-August 8; Wave 6: August 19-October 1).
-The median survey time was 33 minutes.
-
-\emph{Sample size, tracking and attrition:} Data collection took place between October 7 and January 20, 2021with 2,110 respondents, in 186 towns for a tracking rate of 46 percent.
-
-\emph{Sampling Weights:} None
-
-\emph{IRB Approval:} Approval was secured from Sierra Leone Ethics and Scientific Review Committee (SLERC 2904202) and Wageningen University (24062020).
-
-### Uganda {-}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-        \item First confirmed case: March 21, 2020
-        \item Total cases:  741 as of June 18, 2020 and 6,468 as of September 21, 2020         \item Total deaths:  0 as of June 18, 2020 and 63 as of September 21, 2020 
-\end{itemize}
-
-#### Uganda Subnational sample, International Growth Center, Trinity College Dublin, Stockholm School of Economics and Misum, Institute for International Economic Studies, Stockholm University (Uganda 1) {-}
-
-\textbf{Target Population}: Women from semi-rural and rural villages across 13 districts in Uganda (Iganga, Kayunga, Mbale, Mityana, Apac, Dokolo, Gulu, Adjumani, Koboko, Maracha, Nebbi, Soroti, Kumi).
-
-\textbf{Original Study Design:} Initial baseline data was collected in 2016 as part of a large cluster randomized controlled trial, with the aim of selecting households likely to have children during the study period.
-Four criterias for selection were thus used, in descending order of importance: the household has a woman that is currently pregnant, or aged 16-30 years old,  with a young child less than three years old, and/or married (formally or informally).
-In each household, the respondent was chosen as the female household head or the primary female health care giver of the household if the household head could not be found.
-
-\textbf{COVID-19 Survey Design:} The data was collected through multiple rounds of phone surveys.
-The variable measuring age was constructed by approximation, using the baseline data from 2016 and adding 4 years to the 2016 measure.
-When the baseline respondent was replaced, the initial age information was deleted.
-
-\emph{Sampling Frame:} Households were selected within 500 clusters (the village of the household).
-
-\emph{Survey Dates:} September 21 to December 06, 2020.
-
-\emph{Sample size, tracking and attrition:} Out of 2,743 respondents,  1752 were included, provided that they answered the main question about vaccine uptake.
-
-\emph{Sampling Weights:} None.
-
-\emph{IRB Approval:} Mildmay Uganda Research Ethics Committee (protocol number 0109-2015) on September 21, 2020.
-
-### Uganda Subnational sample, WZB Berlin Social Science Center and Columbia University, NYU Abu Dhabi, Innovations for Poverty Action (IPA) (Uganda 2) {-}
-
-\textbf{Target Population:} All residents of Kampala who are Ugandan citizens, above the age of 18, and agree in principle to attend a short citizen consultative meeting.
-
-\textbf{Original Study Design:} Baseline data was collected between July and October 2019 for an intervention that randomized citizen attendance to a set of 188 consultative meetings organized across Kampala.
-The meetings were organized to collect citizen preferences for the design of a forthcoming municipal citizen charter.
-The study also aimed to assess patterns of political inequality in meeting participation, dynamics, and outcomes, as well as study the subsequent effects on prosociality of being incorporated in this participatory process.
-1/3 of the sample was randomly allocated to control, while 2/3 of respondents were invited to attend a consultative meeting.
-The consultations took place between November 2019 and February 2020 across Kampala divisions.
-
-\emph{Intervention:} The intervention consisted of attendance at the consultative meeting organized a few months after baseline data collection.
-A further randomization allocated ½ of the invited participants to a meeting moderated by a local bureaucrat, while the remaining ones attended a meeting moderated by a neutral discussion leader.
-
-\textbf{COVID-19 Survey Design:} The COVID-19 survey sample comprises the 2,189 respondents to the baseline who were selected on the basis of their residence in the city.
-Having received permission to re-contact these individuals, we coordinated a 3-wave panel throughout the summer and fall of 2020, with respondents contacted via phone.
-The goal was to assess households’ degree of economic vulnerability in the face of the COVID-19 pandemic and respondents’ evaluations of performance of political actors in tackling the pandemic.
-
-\emph{Sampling Frame:} The 2,189 respondents to the baseline were randomly selected from a sampling frame of all buildings in Kampala, for which information about their geographical coordinates was available.
-After randomly selecting a set of candidate structures, interviewers sampled respondents from the subset of structures that were residential.
-
-\emph{Survey Dates:} Wave 1: June 18--July 23. Wave 2: September 4--29. Wave 3: November 23--December 12.
-
-\emph{Sample size, tracking and attrition:} Of the 2,189 respondents which we aimed to contact, we were able to reach 1,333 in Wave 1, 1,289 in Wave 2, and 1,366 in Wave 3.
-Wave 3 contained the COVID-19 vaccine module presented in this analysis.
-
-\emph{Sampling Weights:} None.
-
-\emph{IRB Approval:} The study was approved by IPA Global IRB (protocol number 15018) on May 29, 2020; WZB Berlin Social Science Center Ethics Review Board (protocol number 2020/0/91) on June 10, 2020;  NYU Abu Dhabi IRB (protocol number HRPP-2020-64) on May 27, 2020; MIT Committee on the Use of Humans as Experimental Subjects (protocol number 2005000155) on June 3, 2020; and by the Mildmay Uganda Research Ethics Committee (protocol number 0604-2019) on June 11, 2020.
-
-### United States of America Nation-wide sample, WZB Berlin Social Science Center, Cornell University, Tufts University {-}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-        \item First confirmed case: January 20, 2020
-        \item Total cases:  14,499,637 as of December 4, 2020 
-        \item Total deaths:  281,678 as of December 4, 2020 
-\end{itemize}
-
-\textbf{Target Population}: Nation-wide sample of adult internet users recruited through the market research firm Lucid.
-
-\textbf{Original Study Design:} N/A
-
-\emph{Intervention:} N/A
-
-\textbf{COVID-19 Survey Design:}This survey was part of a panel study on attitudes toward COVID-19 technologies and public health surveillance.
-
-\emph{Sampling Frame:} The Lucid Marketplace is an automated marketplace that connects researchers with willing online research participants.
-Lucid partners with a network of companies that maintain relationships with research participants by engaging them with research opportunities.
-While Lucid does not provide probability samples of the U.S.
-adult population, its quota samples approximate the marginal distributions of key demographic characteristics.
-Recent validation exercises have found that Lucid samples approximate nationally representative samples in terms of demographic characteristics and survey experiment effects.^[See for instance: https://journals.sagepub.com/doi/10.1177/2053168018822174]
-
-\emph{Survey Dates:} December 4-5, 2020
-
-\emph{Sample size, tracking and attrition:} 1,959 individual online surveys. In the main question regarding intention to take the vaccine, approximately 10% of respondents (184) did not answer 
-\emph{Sampling Weights:}  Post-stratification weights are computed to match marginal population distributions of income, age, education, gender, race and region among the US adult population, with target proportions based on the 2018 American Community Survey.
-
-\emph{IRB Approval:} This study received approval from the Cornell University IRB under Protocol #2004009569.
-
-________________
-
-\newpage
-<!--
-
-## Population description
-
-In this Appendix section we describe each sample in the study. Table XXX reports summary statistics for each sample.
-When possible, samples are compared to national averages based on Living Standards Measurement Study (LSMS) surveys for random digit dialing surveys and sampling frame summary statistics where available for subpopulation surveys.
-
-<!-- 
-```{r reptabcol}
-tab_sum_col
-```
-```{r reptabrow}
-tab_sum_row
-```
--->

### 2021-06-22 paper_files/figure-latex/fig2paper-1.tex
update

--- 2021-03-23 paper_files/figure-latex/fig2paper-1.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:30
+% Created by tikzDevice version 0.12.3.1 on 2021-06-22 11:48:16
 % !TEX encoding = UTF-8 Unicode
-\documentclass[10pt]{article}
+% !TEX program = xelatex
+
+\documentclass[fontsize=7pt,DIV=calc]{scrartcl}
 
@@
 
-\usepackage[active,tightpage,psfixbb]{preview}
+\usepackage[active,tightpage,xetex]{preview}
+
+\usepackage{fontspec,xunicode}
 
@@
 \setlength\PreviewBorder{0pt}
+
+\setmainfont{Arial}
 \begin{document}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (722.70,542.02);
-\end{scope}
-\begin{scope}
-\path[clip] ( 78.32, 67.14) rectangle (137.25,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (722.70,542.03);
+\end{scope}
+\begin{scope}
+\path[clip] ( 64.26, 25.44) rectangle (124.60,470.61);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 78.32, 67.14) rectangle (137.25,464.78);
+\path[fill=fillColor] ( 64.26, 25.44) rectangle (124.60,470.61);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 87.69, 67.14) --
-	( 87.69,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (101.09, 67.14) --
-	(101.09,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (114.48, 67.14) --
-	(114.48,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (127.88, 67.14) --
-	(127.88,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32, 83.94) --
-	(137.25, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,111.94) --
-	(137.25,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,139.95) --
-	(137.25,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,167.95) --
-	(137.25,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,195.95) --
-	(137.25,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,223.96) --
-	(137.25,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,251.96) --
-	(137.25,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,279.96) --
-	(137.25,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,307.96) --
-	(137.25,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,335.97) --
-	(137.25,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,363.97) --
-	(137.25,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,391.97) --
-	(137.25,391.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,419.98) --
-	(137.25,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,447.98) --
-	(137.25,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.00, 67.14) --
-	( 81.00,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.39, 67.14) --
-	( 94.39,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (107.79, 67.14) --
-	(107.79,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (121.18, 67.14) --
-	(121.18,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (134.58, 67.14) --
-	(134.58,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 74.80, 25.44) --
+	( 74.80,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 88.25, 25.44) --
+	( 88.25,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (101.69, 25.44) --
+	(101.69,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (115.14, 25.44) --
+	(115.14,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26, 44.25) --
+	(124.60, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26, 75.60) --
+	(124.60, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,106.95) --
+	(124.60,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,138.30) --
+	(124.60,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,169.65) --
+	(124.60,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,201.00) --
+	(124.60,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,232.35) --
+	(124.60,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,263.70) --
+	(124.60,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,295.05) --
+	(124.60,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,326.40) --
+	(124.60,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,357.75) --
+	(124.60,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,389.10) --
+	(124.60,389.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,420.45) --
+	(124.60,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,451.80) --
+	(124.60,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.08, 25.44) --
+	( 68.08,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.52, 25.44) --
+	( 81.52,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.97, 25.44) --
+	( 94.97,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (108.41, 25.44) --
+	(108.41,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (121.86, 25.44) --
+	(121.86,470.61);
 \definecolor{drawColor}{RGB}{204,102,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (111.16,137.15) --
-	(111.16,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (111.16,139.95) --
-	( 94.55,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.55,137.15) --
-	( 94.55,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (105.80,445.18) --
-	(105.80,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (105.80,447.98) --
-	(100.02,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (100.02,445.18) --
-	(100.02,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (101.14,417.18) --
-	(101.14,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (101.14,419.98) --
-	( 94.07,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.07,417.18) --
-	( 94.07,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.75,361.17) --
-	( 90.75,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.75,363.97) --
-	( 81.16,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.16,361.17) --
-	( 81.16,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.66,333.17) --
-	( 94.66,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.66,335.97) --
-	( 90.37,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.37,333.17) --
-	( 90.37,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 97.50,305.16) --
-	( 97.50,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 97.50,307.96) --
-	( 89.09,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.09,305.16) --
-	( 89.09,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (101.57,109.14) --
-	(101.57,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (101.57,111.94) --
-	( 99.86,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.86,109.14) --
-	( 99.86,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (107.95,277.16) --
-	(107.95,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (107.95,279.96) --
-	( 95.41,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.41,277.16) --
-	( 95.41,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (113.09,249.16) --
-	(113.09,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (113.09,251.96) --
-	(106.23,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (106.23,249.16) --
-	(106.23,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (116.20,221.16) --
-	(116.20,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (116.20,223.96) --
-	(107.84,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (107.84,221.16) --
-	(107.84,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (129.00,193.15) --
-	(129.00,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (129.00,195.95) --
-	(124.23,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (124.23,193.15) --
-	(124.23,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (109.13,165.15) --
-	(109.13,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (109.13,167.95) --
-	(103.61,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (103.61,165.15) --
-	(103.61,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (126.00, 81.14) --
-	(126.00, 86.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (126.00, 83.94) --
-	(120.97, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.97, 81.14) --
-	(120.97, 86.74);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 98.36,103.81) --
+	( 98.36,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 98.36,106.95) --
+	( 81.68,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.68,103.81) --
+	( 81.68,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 92.98,448.66) --
+	( 92.98,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 92.98,451.80) --
+	( 87.17,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.17,448.66) --
+	( 87.17,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.30,417.31) --
+	( 88.30,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.30,420.45) --
+	( 81.20,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.20,417.31) --
+	( 81.20,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.87,354.61) --
+	( 77.87,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.87,357.75) --
+	( 68.24,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.24,354.61) --
+	( 68.24,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.79,323.26) --
+	( 81.79,329.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.79,326.40) --
+	( 77.49,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.49,323.26) --
+	( 77.49,329.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.64,291.91) --
+	( 84.64,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.64,295.05) --
+	( 76.20,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 76.20,291.91) --
+	( 76.20,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.73, 72.46) --
+	( 88.73, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.73, 75.60) --
+	( 87.01, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.01, 72.46) --
+	( 87.01, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.13,260.56) --
+	( 95.13,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.13,263.70) --
+	( 82.54,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 82.54,260.56) --
+	( 82.54,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (100.29,229.21) --
+	(100.29,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (100.29,232.35) --
+	( 93.41,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 93.41,229.21) --
+	( 93.41,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (103.41,197.86) --
+	(103.41,204.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (103.41,201.00) --
+	( 95.02,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.02,197.86) --
+	( 95.02,204.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (116.27,166.51) --
+	(116.27,172.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (116.27,169.65) --
+	(111.48,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (111.48,166.51) --
+	(111.48,172.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.31,135.16) --
+	( 96.31,141.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.31,138.30) --
+	( 90.77,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.77,135.16) --
+	( 90.77,141.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (113.25, 41.12) --
+	(113.25, 47.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (113.25, 44.25) --
+	(108.20, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (108.20, 41.12) --
+	(108.20, 47.39);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (102.86,139.95) circle (  3.57);
-
-\path[fill=fillColor] (102.91,447.98) circle (  3.57);
-
-\path[fill=fillColor] ( 97.61,419.98) circle (  3.57);
-
-\path[fill=fillColor] ( 85.98,363.97) circle (  1.43);
-
-\path[fill=fillColor] ( 92.52,335.97) circle (  3.57);
-
-\path[fill=fillColor] ( 93.32,307.96) circle (  3.57);
-
-\path[fill=fillColor] (100.71,111.94) circle (  3.57);
-
-\path[fill=fillColor] (101.68,279.96) circle (  3.57);
-
-\path[fill=fillColor] (109.66,251.96) circle (  3.57);
-
-\path[fill=fillColor] (112.02,223.96) circle (  3.57);
-
-\path[fill=fillColor] (126.59,195.95) circle (  3.57);
-
-\path[fill=fillColor] (106.34,167.95) circle (  3.57);
-
-\path[fill=fillColor] (123.48, 83.94) circle (  3.57);
+\path[fill=fillColor] ( 90.02,106.95) circle (  1.96);
+
+\path[fill=fillColor] ( 90.07,451.80) circle (  1.96);
+
+\path[fill=fillColor] ( 84.75,420.45) circle (  1.96);
+
+\path[fill=fillColor] ( 73.08,357.75) circle (  1.96);
+
+\path[fill=fillColor] ( 79.64,326.40) circle (  1.96);
+
+\path[fill=fillColor] ( 80.45,295.05) circle (  1.96);
+
+\path[fill=fillColor] ( 87.87, 75.60) circle (  1.96);
+
+\path[fill=fillColor] ( 88.84,263.70) circle (  1.96);
+
+\path[fill=fillColor] ( 96.85,232.35) circle (  1.96);
+
+\path[fill=fillColor] ( 99.22,201.00) circle (  1.96);
+
+\path[fill=fillColor] (113.85,169.65) circle (  1.96);
+
+\path[fill=fillColor] ( 93.52,138.30) circle (  1.96);
+
+\path[fill=fillColor] (110.73, 44.25) circle (  1.96);
 \definecolor{drawColor}{RGB}{169,169,169}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,153.95) -- (137.25,153.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,125.95) -- (137.25,125.95);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 78.32, 67.14) rectangle (137.25,464.78);
-\end{scope}
-\begin{scope}
-\path[clip] (142.75, 67.14) rectangle (201.69,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,122.62) -- (124.60,122.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26, 91.27) -- (124.60, 91.27);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 64.26, 25.44) rectangle (124.60,470.61);
+\end{scope}
+\begin{scope}
+\path[clip] (130.10, 25.44) rectangle (190.45,470.61);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (142.75, 67.14) rectangle (201.69,464.78);
+\path[fill=fillColor] (130.10, 25.44) rectangle (190.45,470.61);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (152.13, 67.14) --
-	(152.13,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (165.53, 67.14) --
-	(165.53,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (178.92, 67.14) --
-	(178.92,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (192.32, 67.14) --
-	(192.32,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75, 83.94) --
-	(201.69, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,111.94) --
-	(201.69,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,139.95) --
-	(201.69,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,167.95) --
-	(201.69,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,195.95) --
-	(201.69,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,223.96) --
-	(201.69,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,251.96) --
-	(201.69,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,279.96) --
-	(201.69,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,307.96) --
-	(201.69,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,335.97) --
-	(201.69,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,363.97) --
-	(201.69,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,391.97) --
-	(201.69,391.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,419.98) --
-	(201.69,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,447.98) --
-	(201.69,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (145.43, 67.14) --
-	(145.43,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (158.83, 67.14) --
-	(158.83,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (172.22, 67.14) --
-	(172.22,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (185.62, 67.14) --
-	(185.62,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (199.01, 67.14) --
-	(199.01,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (140.64, 25.44) --
+	(140.64,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (154.09, 25.44) --
+	(154.09,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (167.54, 25.44) --
+	(167.54,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (180.98, 25.44) --
+	(180.98,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10, 44.25) --
+	(190.45, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10, 75.60) --
+	(190.45, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,106.95) --
+	(190.45,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,138.30) --
+	(190.45,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,169.65) --
+	(190.45,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,201.00) --
+	(190.45,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,232.35) --
+	(190.45,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,263.70) --
+	(190.45,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,295.05) --
+	(190.45,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,326.40) --
+	(190.45,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,357.75) --
+	(190.45,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,389.10) --
+	(190.45,389.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,420.45) --
+	(190.45,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,451.80) --
+	(190.45,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (133.92, 25.44) --
+	(133.92,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (147.37, 25.44) --
+	(147.37,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (160.81, 25.44) --
+	(160.81,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (174.26, 25.44) --
+	(174.26,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (187.70, 25.44) --
+	(187.70,470.61);
 \definecolor{drawColor}{RGB}{221,204,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (159.63,137.15) --
-	(159.63,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (159.63,139.95) --
-	(150.10,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (150.10,137.15) --
-	(150.10,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (151.33,445.18) --
-	(151.33,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (151.33,447.98) --
-	(148.11,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (148.11,445.18) --
-	(148.11,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (157.97,417.18) --
-	(157.97,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (157.97,419.98) --
-	(152.24,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (152.24,417.18) --
-	(152.24,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (154.17,361.17) --
-	(154.17,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.72,333.17) --
-	(161.72,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.72,335.97) --
-	(157.11,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (157.11,333.17) --
-	(157.11,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.19,305.16) --
-	(161.19,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (161.19,307.96) --
-	(153.10,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (153.10,305.16) --
-	(153.10,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (153.52,109.14) --
-	(153.52,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (153.52,111.94) --
-	(152.29,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (152.29,109.14) --
-	(152.29,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (154.70,277.16) --
-	(154.70,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (154.70,279.96) --
-	(146.93,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (146.93,277.16) --
-	(146.93,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (169.12,249.16) --
-	(169.12,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (169.12,251.96) --
-	(162.37,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (162.37,249.16) --
-	(162.37,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (153.04,165.15) --
-	(153.04,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (153.04,167.95) --
-	(149.24,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (149.24,165.15) --
-	(149.24,170.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (148.17,103.81) --
+	(148.17,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (148.17,106.95) --
+	(138.60,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (138.60,103.81) --
+	(138.60,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (139.84,448.66) --
+	(139.84,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (139.84,451.80) --
+	(136.61,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (136.61,448.66) --
+	(136.61,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (146.51,417.31) --
+	(146.51,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (146.51,420.45) --
+	(140.75,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (140.75,417.31) --
+	(140.75,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (142.69,354.61) --
+	(142.69,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (142.69,357.75) --
+	(133.71,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (133.71,354.61) --
+	(133.71,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.27,323.26) --
+	(150.27,329.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.27,326.40) --
+	(145.65,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (145.65,323.26) --
+	(145.65,329.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (149.73,291.91) --
+	(149.73,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (149.73,295.05) --
+	(141.61,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (141.61,291.91) --
+	(141.61,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (142.04, 72.46) --
+	(142.04, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (142.04, 75.60) --
+	(140.81, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (140.81, 72.46) --
+	(140.81, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (143.23,260.56) --
+	(143.23,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (143.23,263.70) --
+	(135.43,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (135.43,260.56) --
+	(135.43,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (157.69,229.21) --
+	(157.69,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (157.69,232.35) --
+	(150.92,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (150.92,229.21) --
+	(150.92,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (141.56,135.16) --
+	(141.56,141.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (141.56,138.30) --
+	(137.74,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (137.74,135.16) --
+	(137.74,141.43);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (154.86,139.95) circle (  3.57);
-
-\path[fill=fillColor] (149.72,447.98) circle (  3.57);
-
-\path[fill=fillColor] (155.13,419.98) circle (  3.57);
-
-\path[fill=fillColor] (149.67,363.97) circle (  1.43);
-
-\path[fill=fillColor] (159.42,335.97) circle (  3.57);
-
-\path[fill=fillColor] (157.17,307.96) circle (  3.57);
-
-\path[fill=fillColor] (152.88,111.94) circle (  3.57);
-
-\path[fill=fillColor] (150.85,279.96) circle (  3.57);
-
-\path[fill=fillColor] (165.74,251.96) circle (  3.57);
-
-\path[fill=fillColor] (151.17,167.95) circle (  3.57);
+\path[fill=fillColor] (143.39,106.95) circle (  1.96);
+
+\path[fill=fillColor] (138.22,451.80) circle (  1.96);
+
+\path[fill=fillColor] (143.66,420.45) circle (  1.96);
+
+\path[fill=fillColor] (138.17,357.75) circle (  1.96);
+
+\path[fill=fillColor] (147.96,326.40) circle (  1.96);
+
+\path[fill=fillColor] (145.70,295.05) circle (  1.96);
+
+\path[fill=fillColor] (141.40, 75.60) circle (  1.96);
+
+\path[fill=fillColor] (139.35,263.70) circle (  1.96);
+
+\path[fill=fillColor] (154.30,232.35) circle (  1.96);
+
+\path[fill=fillColor] (139.68,138.30) circle (  1.96);
 \definecolor{drawColor}{RGB}{169,169,169}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,153.95) -- (201.69,153.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,125.95) -- (201.69,125.95);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.75, 67.14) rectangle (201.69,464.78);
-\end{scope}
-\begin{scope}
-\path[clip] (207.19, 67.14) rectangle (266.13,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,122.62) -- (190.45,122.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10, 91.27) -- (190.45, 91.27);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (130.10, 25.44) rectangle (190.45,470.61);
+\end{scope}
+\begin{scope}
+\path[clip] (195.95, 25.44) rectangle (256.29,470.61);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (207.19, 67.14) rectangle (266.13,464.78);
+\path[fill=fillColor] (195.95, 25.44) rectangle (256.29,470.61);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (216.57, 67.14) --
-	(216.57,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (229.96, 67.14) --
-	(229.96,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (243.36, 67.14) --
-	(243.36,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (256.76, 67.14) --
-	(256.76,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19, 83.94) --
-	(266.13, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,111.94) --
-	(266.13,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,139.95) --
-	(266.13,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,167.95) --
-	(266.13,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,195.95) --
-	(266.13,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,223.96) --
-	(266.13,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,251.96) --
-	(266.13,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,279.96) --
-	(266.13,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,307.96) --
-	(266.13,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,335.97) --
-	(266.13,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,363.97) --
-	(266.13,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,391.97) --
-	(266.13,391.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,419.98) --
-	(266.13,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,447.98) --
-	(266.13,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.87, 67.14) --
-	(209.87,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (223.27, 67.14) --
-	(223.27,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (236.66, 67.14) --
-	(236.66,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (250.06, 67.14) --
-	(250.06,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (263.45, 67.14) --
-	(263.45,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (206.49, 25.44) --
+	(206.49,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (219.93, 25.44) --
+	(219.93,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (233.38, 25.44) --
+	(233.38,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (246.83, 25.44) --
+	(246.83,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95, 44.25) --
+	(256.29, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95, 75.60) --
+	(256.29, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95,106.95) --
+	(256.29,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95,138.30) --
+	(256.29,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95,169.65) --
+	(256.29,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95,201.00) --
+	(256.29,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95,232.35) --
+	(256.29,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95,263.70) --
+	(256.29,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95,295.05) --
+	(256.29,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95,326.40) --
+	(256.29,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95,357.75) --
+	(256.29,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95,389.10) --
+	(256.29,389.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95,420.45) --
+	(256.29,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95,451.80) --
+	(256.29,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (199.77, 25.44) --
+	(199.77,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (213.21, 25.44) --
+	(213.21,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (226.66, 25.44) --
+	(226.66,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (240.10, 25.44) --
+	(240.10,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (253.55, 25.44) --
+	(253.55,470.61);
 \definecolor{drawColor}{RGB}{17,119,51}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (219.95,137.15) --
-	(219.95,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (219.95,139.95) --
-	(213.30,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.30,137.15) --
-	(213.30,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (215.34,445.18) --
-	(215.34,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (215.34,447.98) --
-	(212.28,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (212.28,445.18) --
-	(212.28,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.30,417.18) --
-	(216.30,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.30,419.98) --
-	(211.96,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (211.96,417.18) --
-	(211.96,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.14,389.17) --
-	(213.14,394.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (228.14,361.17) --
-	(228.14,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (228.14,363.97) --
-	(213.46,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.46,361.17) --
-	(213.46,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (220.27,333.17) --
-	(220.27,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (220.27,335.97) --
-	(216.46,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (216.46,333.17) --
-	(216.46,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (230.18,305.16) --
-	(230.18,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (230.18,307.96) --
-	(221.07,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (221.07,305.16) --
-	(221.07,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.14,109.14) --
-	(213.14,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.14,111.94) --
-	(212.34,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (212.34,109.14) --
-	(212.34,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (224.93,277.16) --
-	(224.93,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (224.93,279.96) --
-	(214.86,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (214.86,277.16) --
-	(214.86,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (220.16,249.16) --
-	(220.16,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (220.16,251.96) --
-	(215.28,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (215.28,249.16) --
-	(215.28,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.03,193.15) --
-	(213.03,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.03,195.95) --
-	(210.78,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (210.78,193.15) --
-	(210.78,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.78,165.15) --
-	(213.78,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (213.78,167.95) --
-	(211.32,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (211.32,165.15) --
-	(211.32,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (233.98, 81.14) --
-	(233.98, 86.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (233.98, 83.94) --
-	(227.82, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (227.82, 81.14) --
-	(227.82, 86.74);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.88,103.81) --
+	(209.88,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.88,106.95) --
+	(203.21,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (203.21,103.81) --
+	(203.21,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.25,448.66) --
+	(205.25,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.25,451.80) --
+	(202.19,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.19,448.66) --
+	(202.19,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (206.22,417.31) --
+	(206.22,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (206.22,420.45) --
+	(201.86,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (201.86,417.31) --
+	(201.86,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (203.05,385.96) --
+	(203.05,392.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (203.05,389.10) --
+	(199.39,389.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (199.39,385.96) --
+	(199.39,392.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (218.11,354.61) --
+	(218.11,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (218.11,357.75) --
+	(203.37,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (203.37,354.61) --
+	(203.37,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (210.20,323.26) --
+	(210.20,329.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (210.20,326.40) --
+	(206.38,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (206.38,323.26) --
+	(206.38,329.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (220.15,291.91) --
+	(220.15,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (220.15,295.05) --
+	(211.01,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (211.01,291.91) --
+	(211.01,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (203.05, 72.46) --
+	(203.05, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (203.05, 75.60) --
+	(202.24, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.24, 72.46) --
+	(202.24, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.88,260.56) --
+	(214.88,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.88,263.70) --
+	(204.77,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (204.77,260.56) --
+	(204.77,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (210.09,229.21) --
+	(210.09,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (210.09,232.35) --
+	(205.20,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.20,229.21) --
+	(205.20,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.94,166.51) --
+	(202.94,172.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.94,169.65) --
+	(200.68,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (200.68,166.51) --
+	(200.68,172.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (203.69,135.16) --
+	(203.69,141.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (203.69,138.30) --
+	(201.22,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (201.22,135.16) --
+	(201.22,141.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (223.97, 41.12) --
+	(223.97, 47.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (223.97, 44.25) --
+	(217.78, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (217.78, 41.12) --
+	(217.78, 47.39);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (216.62,139.95) circle (  3.57);
-
-\path[fill=fillColor] (213.84,447.98) circle (  3.57);
-
-\path[fill=fillColor] (214.16,419.98) circle (  3.57);
-
-\path[fill=fillColor] (211.32,391.97) circle (  1.43);
-
-\path[fill=fillColor] (220.80,363.97) circle (  3.57);
-
-\path[fill=fillColor] (218.39,335.97) circle (  3.57);
-
-\path[fill=fillColor] (225.62,307.96) circle (  3.57);
-
-\path[fill=fillColor] (212.77,111.94) circle (  3.57);
-
-\path[fill=fillColor] (219.89,279.96) circle (  3.57);
-
-\path[fill=fillColor] (217.70,251.96) circle (  3.57);
-
-\path[fill=fillColor] (211.91,195.95) circle (  3.57);
-
-\path[fill=fillColor] (212.55,167.95) circle (  3.57);
-
-\path[fill=fillColor] (230.93, 83.94) circle (  3.57);
+\path[fill=fillColor] (206.54,106.95) circle (  1.96);
+
+\path[fill=fillColor] (203.75,451.80) circle (  1.96);
+
+\path[fill=fillColor] (204.07,420.45) circle (  1.96);
+
+\path[fill=fillColor] (201.22,389.10) circle (  1.96);
+
+\path[fill=fillColor] (210.74,357.75) circle (  1.96);
+
+\path[fill=fillColor] (208.32,326.40) circle (  1.96);
+
+\path[fill=fillColor] (215.58,295.05) circle (  1.96);
+
+\path[fill=fillColor] (202.67, 75.60) circle (  1.96);
+
+\path[fill=fillColor] (209.82,263.70) circle (  1.96);
+
+\path[fill=fillColor] (207.62,232.35) circle (  1.96);
+
+\path[fill=fillColor] (201.81,169.65) circle (  1.96);
+
+\path[fill=fillColor] (202.45,138.30) circle (  1.96);
+
+\path[fill=fillColor] (220.90, 44.25) circle (  1.96);
 \definecolor{drawColor}{RGB}{169,169,169}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,153.95) -- (266.13,153.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (207.19,125.95) -- (266.13,125.95);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (207.19, 67.14) rectangle (266.13,464.78);
-\end{scope}
-\begin{scope}
-\path[clip] (271.63, 67.14) rectangle (330.57,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95,122.62) -- (256.29,122.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (195.95, 91.27) -- (256.29, 91.27);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (195.95, 25.44) rectangle (256.29,470.61);
+\end{scope}
+\begin{scope}
+\path[clip] (261.79, 25.44) rectangle (322.14,470.61);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (271.63, 67.14) rectangle (330.57,464.78);
+\path[fill=fillColor] (261.79, 25.44) rectangle (322.14,470.61);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (281.01, 67.14) --
-	(281.01,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (294.40, 67.14) --
-	(294.40,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (307.80, 67.14) --
-	(307.80,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (321.19, 67.14) --
-	(321.19,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63, 83.94) --
-	(330.57, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,111.94) --
-	(330.57,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,139.95) --
-	(330.57,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,167.95) --
-	(330.57,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,195.95) --
-	(330.57,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,223.96) --
-	(330.57,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,251.96) --
-	(330.57,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,279.96) --
-	(330.57,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,307.96) --
-	(330.57,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,335.97) --
-	(330.57,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,363.97) --
-	(330.57,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,391.97) --
-	(330.57,391.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,419.98) --
-	(330.57,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,447.98) --
-	(330.57,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (274.31, 67.14) --
-	(274.31,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (287.71, 67.14) --
-	(287.71,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (301.10, 67.14) --
-	(301.10,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (314.50, 67.14) --
-	(314.50,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (327.89, 67.14) --
-	(327.89,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (272.33, 25.44) --
+	(272.33,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (285.78, 25.44) --
+	(285.78,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (299.22, 25.44) --
+	(299.22,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (312.67, 25.44) --
+	(312.67,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79, 44.25) --
+	(322.14, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79, 75.60) --
+	(322.14, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79,106.95) --
+	(322.14,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79,138.30) --
+	(322.14,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79,169.65) --
+	(322.14,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79,201.00) --
+	(322.14,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79,232.35) --
+	(322.14,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79,263.70) --
+	(322.14,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79,295.05) --
+	(322.14,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79,326.40) --
+	(322.14,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79,357.75) --
+	(322.14,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79,389.10) --
+	(322.14,389.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79,420.45) --
+	(322.14,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79,451.80) --
+	(322.14,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (265.61, 25.44) --
+	(265.61,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (279.06, 25.44) --
+	(279.06,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (292.50, 25.44) --
+	(292.50,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (305.95, 25.44) --
+	(305.95,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (319.39, 25.44) --
+	(319.39,470.61);
 \definecolor{drawColor}{RGB}{51,34,136}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (287.55,137.15) --
-	(287.55,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (287.55,139.95) --
-	(281.70,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (281.70,137.15) --
-	(281.70,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (287.06,445.18) --
-	(287.06,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (287.06,447.98) --
-	(282.40,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (282.40,445.18) --
-	(282.40,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (282.08,417.18) --
-	(282.08,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (282.08,419.98) --
-	(277.47,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (277.47,417.18) --
-	(277.47,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (296.17,389.17) --
-	(296.17,394.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (296.17,391.97) --
-	(284.28,391.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (284.28,389.17) --
-	(284.28,394.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (288.88,361.17) --
-	(288.88,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (288.88,363.97) --
-	(276.03,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (276.03,361.17) --
-	(276.03,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.79,333.17) --
-	(280.79,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.79,335.97) --
-	(277.74,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (277.74,333.17) --
-	(277.74,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (292.53,305.16) --
-	(292.53,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (292.53,307.96) --
-	(283.96,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (283.96,305.16) --
-	(283.96,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (290.97,109.14) --
-	(290.97,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (290.97,111.94) --
-	(289.37,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (289.37,109.14) --
-	(289.37,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (291.13,277.16) --
-	(291.13,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (291.13,279.96) --
-	(280.53,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.53,277.16) --
-	(280.53,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.15,249.16) --
-	(280.15,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.15,251.96) --
-	(276.56,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (276.56,249.16) --
-	(276.56,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (286.47,221.16) --
-	(286.47,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (286.47,223.96) --
-	(280.69,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (280.69,221.16) --
-	(280.69,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (289.96,193.15) --
-	(289.96,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (289.96,195.95) --
-	(284.60,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (284.60,193.15) --
-	(284.60,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (293.71,165.15) --
-	(293.71,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (293.71,167.95) --
-	(288.19,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (288.19,165.15) --
-	(288.19,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (302.49, 81.14) --
-	(302.49, 86.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (302.49, 83.94) --
-	(296.28, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (296.28, 81.14) --
-	(296.28, 86.74);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (278.89,103.81) --
+	(278.89,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (278.89,106.95) --
+	(273.03,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (273.03,103.81) --
+	(273.03,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (278.41,448.66) --
+	(278.41,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (278.41,451.80) --
+	(273.73,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (273.73,448.66) --
+	(273.73,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (273.41,417.31) --
+	(273.41,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (273.41,420.45) --
+	(268.78,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (268.78,417.31) --
+	(268.78,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (287.55,385.96) --
+	(287.55,392.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (287.55,389.10) --
+	(275.61,389.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (275.61,385.96) --
+	(275.61,392.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (280.24,354.61) --
+	(280.24,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (280.24,357.75) --
+	(267.33,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (267.33,354.61) --
+	(267.33,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (272.12,323.26) --
+	(272.12,329.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (272.12,326.40) --
+	(269.05,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (269.05,323.26) --
+	(269.05,329.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (283.90,291.91) --
+	(283.90,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (283.90,295.05) --
+	(275.29,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (275.29,291.91) --
+	(275.29,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (282.34, 72.46) --
+	(282.34, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (282.34, 75.60) --
+	(280.72, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (280.72, 72.46) --
+	(280.72, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (282.50,260.56) --
+	(282.50,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (282.50,263.70) --
+	(271.85,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (271.85,260.56) --
+	(271.85,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (271.47,229.21) --
+	(271.47,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (271.47,232.35) --
+	(267.87,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (267.87,229.21) --
+	(267.87,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (277.82,197.86) --
+	(277.82,204.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (277.82,201.00) --
+	(272.01,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (272.01,197.86) --
+	(272.01,204.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (281.31,166.51) --
+	(281.31,172.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (281.31,169.65) --
+	(275.94,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (275.94,166.51) --
+	(275.94,172.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (285.08,135.16) --
+	(285.08,141.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (285.08,138.30) --
+	(279.54,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (279.54,135.16) --
+	(279.54,141.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (293.90, 41.12) --
+	(293.90, 47.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (293.90, 44.25) --
+	(287.66, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (287.66, 41.12) --
+	(287.66, 47.39);
 \definecolor{fillColor}{RGB}{51,34,136}
 
-\path[fill=fillColor] (284.60,139.95) circle (  3.57);
-
-\path[fill=fillColor] (284.76,447.98) circle (  3.57);
-
-\path[fill=fillColor] (279.78,419.98) circle (  3.57);
-
-\path[fill=fillColor] (290.22,391.97) circle (  3.57);
-
-\path[fill=fillColor] (282.45,363.97) circle (  3.57);
-
-\path[fill=fillColor] (279.29,335.97) circle (  3.57);
-
-\path[fill=fillColor] (288.24,307.96) circle (  3.57);
-
-\path[fill=fillColor] (290.17,111.94) circle (  3.57);
-
-\path[fill=fillColor] (285.83,279.96) circle (  3.57);
-
-\path[fill=fillColor] (278.33,251.96) circle (  3.57);
-
-\path[fill=fillColor] (283.58,223.96) circle (  3.57);
-
-\path[fill=fillColor] (287.28,195.95) circle (  3.57);
-
-\path[fill=fillColor] (290.92,167.95) circle (  3.57);
-
-\path[fill=fillColor] (299.39, 83.94) circle (  3.57);
+\path[fill=fillColor] (275.94,106.95) circle (  1.96);
+
+\path[fill=fillColor] (276.10,451.80) circle (  1.96);
+
+\path[fill=fillColor] (271.10,420.45) circle (  1.96);
+
+\path[fill=fillColor] (281.58,389.10) circle (  1.96);
+
+\path[fill=fillColor] (273.78,357.75) circle (  1.96);
+
+\path[fill=fillColor] (270.61,326.40) circle (  1.96);
+
+\path[fill=fillColor] (279.59,295.05) circle (  1.96);
+
+\path[fill=fillColor] (281.53, 75.60) circle (  1.96);
+
+\path[fill=fillColor] (277.17,263.70) circle (  1.96);
+
+\path[fill=fillColor] (269.64,232.35) circle (  1.96);
+
+\path[fill=fillColor] (274.91,201.00) circle (  1.96);
+
+\path[fill=fillColor] (278.62,169.65) circle (  1.96);
+
+\path[fill=fillColor] (282.28,138.30) circle (  1.96);
+
+\path[fill=fillColor] (290.78, 44.25) circle (  1.96);
 \definecolor{drawColor}{RGB}{169,169,169}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,153.95) -- (330.57,153.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (271.63,125.95) -- (330.57,125.95);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.63, 67.14) rectangle (330.57,464.78);
-\end{scope}
-\begin{scope}
-\path[clip] (336.07, 67.14) rectangle (395.01,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79,122.62) -- (322.14,122.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (261.79, 91.27) -- (322.14, 91.27);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (261.79, 25.44) rectangle (322.14,470.61);
+\end{scope}
+\begin{scope}
+\path[clip] (327.64, 25.44) rectangle (387.98,470.61);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (336.07, 67.14) rectangle (395.01,464.78);
+\path[fill=fillColor] (327.64, 25.44) rectangle (387.98,470.61);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (345.45, 67.14) --
-	(345.45,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (358.84, 67.14) --
-	(358.84,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (372.24, 67.14) --
-	(372.24,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (385.63, 67.14) --
-	(385.63,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07, 83.94) --
-	(395.01, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,111.94) --
-	(395.01,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,139.95) --
-	(395.01,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,167.95) --
-	(395.01,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,195.95) --
-	(395.01,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,223.96) --
-	(395.01,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,251.96) --
-	(395.01,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,279.96) --
-	(395.01,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,307.96) --
-	(395.01,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,335.97) --
-	(395.01,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,363.97) --
-	(395.01,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,391.97) --
-	(395.01,391.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,419.98) --
-	(395.01,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,447.98) --
-	(395.01,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.75, 67.14) --
-	(338.75,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (352.14, 67.14) --
-	(352.14,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (365.54, 67.14) --
-	(365.54,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (378.93, 67.14) --
-	(378.93,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (392.33, 67.14) --
-	(392.33,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (338.18, 25.44) --
+	(338.18,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (351.62, 25.44) --
+	(351.62,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (365.07, 25.44) --
+	(365.07,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (378.51, 25.44) --
+	(378.51,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64, 44.25) --
+	(387.98, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64, 75.60) --
+	(387.98, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64,106.95) --
+	(387.98,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64,138.30) --
+	(387.98,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64,169.65) --
+	(387.98,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64,201.00) --
+	(387.98,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64,232.35) --
+	(387.98,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64,263.70) --
+	(387.98,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64,295.05) --
+	(387.98,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64,326.40) --
+	(387.98,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64,357.75) --
+	(387.98,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64,389.10) --
+	(387.98,389.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64,420.45) --
+	(387.98,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64,451.80) --
+	(387.98,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (331.45, 25.44) --
+	(331.45,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (344.90, 25.44) --
+	(344.90,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (358.34, 25.44) --
+	(358.34,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (371.79, 25.44) --
+	(371.79,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (385.24, 25.44) --
+	(385.24,470.61);
 \definecolor{drawColor}{RGB}{170,68,153}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (346.73,137.15) --
-	(346.73,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (346.73,139.95) --
-	(340.03,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (340.03,137.15) --
-	(340.03,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (347.96,445.18) --
-	(347.96,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (347.96,447.98) --
-	(344.00,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.00,445.18) --
-	(344.00,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (341.05,417.18) --
-	(341.05,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (341.05,419.98) --
-	(338.91,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.91,417.18) --
-	(338.91,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (353.38,361.17) --
-	(353.38,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (353.38,363.97) --
-	(340.89,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (340.89,361.17) --
-	(340.89,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (355.52,305.16) --
-	(355.52,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (355.52,307.96) --
-	(345.61,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (345.61,305.16) --
-	(345.61,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (342.66,109.14) --
-	(342.66,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (342.66,111.94) --
-	(341.75,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (341.75,109.14) --
-	(341.75,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.86,277.16) --
-	(344.86,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.86,279.96) --
-	(338.80,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.80,277.16) --
-	(338.80,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (342.39,249.16) --
-	(342.39,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (342.39,251.96) --
-	(339.61,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (339.61,249.16) --
-	(339.61,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (340.46,193.15) --
-	(340.46,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (340.46,195.95) --
-	(338.86,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.86,193.15) --
-	(338.86,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (342.07,165.15) --
-	(342.07,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (342.07,167.95) --
-	(339.77,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (339.77,165.15) --
-	(339.77,170.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.47,103.81) --
+	(339.47,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.47,106.95) --
+	(332.74,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (332.74,103.81) --
+	(332.74,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (340.70,448.66) --
+	(340.70,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (340.70,451.80) --
+	(336.72,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (336.72,448.66) --
+	(336.72,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.77,417.31) --
+	(333.77,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.77,420.45) --
+	(331.61,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (331.61,417.31) --
+	(331.61,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (346.14,354.61) --
+	(346.14,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (346.14,357.75) --
+	(333.60,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.60,354.61) --
+	(333.60,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.29,291.91) --
+	(348.29,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.29,295.05) --
+	(338.34,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (338.34,291.91) --
+	(338.34,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (335.38, 72.46) --
+	(335.38, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (335.38, 75.60) --
+	(334.47, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (334.47, 72.46) --
+	(334.47, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (337.58,260.56) --
+	(337.58,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (337.58,263.70) --
+	(331.51,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (331.51,260.56) --
+	(331.51,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (335.11,229.21) --
+	(335.11,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (335.11,232.35) --
+	(332.31,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (332.31,229.21) --
+	(332.31,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.17,166.51) --
+	(333.17,172.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (333.17,169.65) --
+	(331.56,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (331.56,166.51) --
+	(331.56,172.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (334.79,135.16) --
+	(334.79,141.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (334.79,138.30) --
+	(332.48,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (332.48,135.16) --
+	(332.48,141.43);
 \definecolor{fillColor}{RGB}{170,68,153}
 
-\path[fill=fillColor] (343.41,139.95) circle (  3.57);
-
-\path[fill=fillColor] (345.98,447.98) circle (  3.57);
-
-\path[fill=fillColor] (339.98,419.98) circle (  1.43);
-
-\path[fill=fillColor] (347.16,363.97) circle (  3.57);
-
-\path[fill=fillColor] (350.59,307.96) circle (  3.57);
-
-\path[fill=fillColor] (342.18,111.94) circle (  3.57);
-
-\path[fill=fillColor] (341.86,279.96) circle (  1.43);
-
-\path[fill=fillColor] (341.00,251.96) circle (  3.57);
-
-\path[fill=fillColor] (339.66,195.95) circle (  1.43);
-
-\path[fill=fillColor] (340.95,167.95) circle (  3.57);
+\path[fill=fillColor] (336.13,106.95) circle (  1.96);
+
+\path[fill=fillColor] (338.71,451.80) circle (  1.96);
+
+\path[fill=fillColor] (332.69,420.45) circle (  1.96);
+
+\path[fill=fillColor] (339.90,357.75) circle (  1.96);
+
+\path[fill=fillColor] (343.34,295.05) circle (  1.96);
+
+\path[fill=fillColor] (334.90, 75.60) circle (  1.96);
+
+\path[fill=fillColor] (334.57,263.70) circle (  1.96);
+
+\path[fill=fillColor] (333.71,232.35) circle (  1.96);
+
+\path[fill=fillColor] (332.37,169.65) circle (  1.96);
+
+\path[fill=fillColor] (333.66,138.30) circle (  1.96);
 \definecolor{drawColor}{RGB}{169,169,169}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,153.95) -- (395.01,153.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (336.07,125.95) -- (395.01,125.95);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (336.07, 67.14) rectangle (395.01,464.78);
-\end{scope}
-\begin{scope}
-\path[clip] (400.51, 67.14) rectangle (459.45,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64,122.62) -- (387.98,122.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (327.64, 91.27) -- (387.98, 91.27);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (327.64, 25.44) rectangle (387.98,470.61);
+\end{scope}
+\begin{scope}
+\path[clip] (393.48, 25.44) rectangle (453.82,470.61);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (400.51, 67.14) rectangle (459.45,464.78);
+\path[fill=fillColor] (393.48, 25.44) rectangle (453.82,470.61);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (409.88, 67.14) --
-	(409.88,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (423.28, 67.14) --
-	(423.28,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (436.68, 67.14) --
-	(436.68,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (450.07, 67.14) --
-	(450.07,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51, 83.94) --
-	(459.45, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,111.94) --
-	(459.45,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,139.95) --
-	(459.45,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,167.95) --
-	(459.45,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,195.95) --
-	(459.45,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,223.96) --
-	(459.45,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,251.96) --
-	(459.45,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,279.96) --
-	(459.45,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,307.96) --
-	(459.45,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,335.97) --
-	(459.45,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,363.97) --
-	(459.45,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,391.97) --
-	(459.45,391.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,419.98) --
-	(459.45,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,447.98) --
-	(459.45,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (403.19, 67.14) --
-	(403.19,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (416.58, 67.14) --
-	(416.58,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (429.98, 67.14) --
-	(429.98,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (443.37, 67.14) --
-	(443.37,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (456.77, 67.14) --
-	(456.77,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (404.02, 25.44) --
+	(404.02,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (417.47, 25.44) --
+	(417.47,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (430.91, 25.44) --
+	(430.91,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (444.36, 25.44) --
+	(444.36,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48, 44.25) --
+	(453.82, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48, 75.60) --
+	(453.82, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48,106.95) --
+	(453.82,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48,138.30) --
+	(453.82,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48,169.65) --
+	(453.82,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48,201.00) --
+	(453.82,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48,232.35) --
+	(453.82,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48,263.70) --
+	(453.82,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48,295.05) --
+	(453.82,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48,326.40) --
+	(453.82,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48,357.75) --
+	(453.82,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48,389.10) --
+	(453.82,389.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48,420.45) --
+	(453.82,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48,451.80) --
+	(453.82,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (397.30, 25.44) --
+	(397.30,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (410.74, 25.44) --
+	(410.74,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (424.19, 25.44) --
+	(424.19,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (437.63, 25.44) --
+	(437.63,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (451.08, 25.44) --
+	(451.08,470.61);
 \definecolor{drawColor}{RGB}{68,170,153}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (406.83,137.15) --
-	(406.83,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (406.83,139.95) --
-	(404.10,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.10,137.15) --
-	(404.10,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (406.19,445.18) --
-	(406.19,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (406.19,447.98) --
-	(403.99,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (403.99,445.18) --
-	(403.99,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.15,417.18) --
-	(404.15,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (408.87,361.17) --
-	(408.87,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (412.51,305.16) --
-	(412.51,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (412.51,307.96) --
-	(406.13,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (406.13,305.16) --
-	(406.13,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (405.49,109.14) --
-	(405.49,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (405.49,111.94) --
-	(404.85,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.85,109.14) --
-	(404.85,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (410.26,277.16) --
-	(410.26,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (410.26,279.96) --
-	(403.67,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (403.67,277.16) --
-	(403.67,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (405.97,249.16) --
-	(405.97,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (405.97,251.96) --
-	(403.62,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (403.62,249.16) --
-	(403.62,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (407.37,221.16) --
-	(407.37,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (407.37,223.96) --
-	(404.53,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.53,221.16) --
-	(404.53,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.90,193.15) --
-	(404.90,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.90,195.95) --
-	(403.29,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (403.29,193.15) --
-	(403.29,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.74,165.15) --
-	(404.74,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (404.74,167.95) --
-	(403.29,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (403.29,165.15) --
-	(403.29,170.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (400.95,103.81) --
+	(400.95,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (400.95,106.95) --
+	(398.21,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.21,103.81) --
+	(398.21,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (400.31,448.66) --
+	(400.31,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (400.31,451.80) --
+	(398.10,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.10,448.66) --
+	(398.10,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.27,417.31) --
+	(398.27,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.27,420.45) --
+	(396.98,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (396.98,417.31) --
+	(396.98,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (403.00,354.61) --
+	(403.00,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (403.00,357.75) --
+	(396.28,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (396.28,354.61) --
+	(396.28,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (406.66,291.91) --
+	(406.66,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (406.66,295.05) --
+	(400.26,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (400.26,291.91) --
+	(400.26,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (399.61, 72.46) --
+	(399.61, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (399.61, 75.60) --
+	(398.97, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.97, 72.46) --
+	(398.97, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.40,260.56) --
+	(404.40,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (404.40,263.70) --
+	(397.78,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (397.78,260.56) --
+	(397.78,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (400.09,229.21) --
+	(400.09,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (400.09,232.35) --
+	(397.73,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (397.73,229.21) --
+	(397.73,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (401.49,197.86) --
+	(401.49,204.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (401.49,201.00) --
+	(398.64,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.64,197.86) --
+	(398.64,204.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (399.02,166.51) --
+	(399.02,172.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (399.02,169.65) --
+	(397.41,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (397.41,166.51) --
+	(397.41,172.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.86,135.16) --
+	(398.86,141.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (398.86,138.30) --
+	(397.41,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (397.41,135.16) --
+	(397.41,141.43);
 \definecolor{fillColor}{RGB}{68,170,153}
 
-\path[fill=fillColor] (405.49,139.95) circle (  3.57);
-
-\path[fill=fillColor] (405.06,447.98) circle (  3.57);
-
-\path[fill=fillColor] (403.51,419.98) circle (  1.43);
-
-\path[fill=fillColor] (405.54,363.97) circle (  1.43);
-
-\path[fill=fillColor] (409.35,307.96) circle (  3.57);
-
-\path[fill=fillColor] (405.17,111.94) circle (  3.57);
-
-\path[fill=fillColor] (406.94,279.96) circle (  1.43);
-
-\path[fill=fillColor] (404.79,251.96) circle (  3.57);
-
-\path[fill=fillColor] (405.92,223.96) circle (  3.57);
-
-\path[fill=fillColor] (404.10,195.95) circle (  1.43);
-
-\path[fill=fillColor] (404.04,167.95) circle (  3.57);
+\path[fill=fillColor] (399.61,106.95) circle (  1.96);
+
+\path[fill=fillColor] (399.18,451.80) circle (  1.96);
+
+\path[fill=fillColor] (397.62,420.45) circle (  1.96);
+
+\path[fill=fillColor] (399.66,357.75) circle (  1.96);
+
+\path[fill=fillColor] (403.48,295.05) circle (  1.96);
+
+\path[fill=fillColor] (399.29, 75.60) circle (  1.96);
+
+\path[fill=fillColor] (401.06,263.70) circle (  1.96);
+
+\path[fill=fillColor] (398.91,232.35) circle (  1.96);
+
+\path[fill=fillColor] (400.04,201.00) circle (  1.96);
+
+\path[fill=fillColor] (398.21,169.65) circle (  1.96);
+
+\path[fill=fillColor] (398.16,138.30) circle (  1.96);
 \definecolor{drawColor}{RGB}{169,169,169}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,153.95) -- (459.45,153.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (400.51,125.95) -- (459.45,125.95);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (400.51, 67.14) rectangle (459.45,464.78);
-\end{scope}
-\begin{scope}
-\path[clip] (464.95, 67.14) rectangle (523.88,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48,122.62) -- (453.82,122.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (393.48, 91.27) -- (453.82, 91.27);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.48, 25.44) rectangle (453.82,470.61);
+\end{scope}
+\begin{scope}
+\path[clip] (459.32, 25.44) rectangle (519.67,470.61);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (464.95, 67.14) rectangle (523.88,464.78);
+\path[fill=fillColor] (459.32, 25.44) rectangle (519.67,470.61);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (474.32, 67.14) --
-	(474.32,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (487.72, 67.14) --
-	(487.72,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (501.11, 67.14) --
-	(501.11,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (514.51, 67.14) --
-	(514.51,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95, 83.94) --
-	(523.88, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,111.94) --
-	(523.88,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,139.95) --
-	(523.88,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,167.95) --
-	(523.88,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,195.95) --
-	(523.88,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,223.96) --
-	(523.88,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,251.96) --
-	(523.88,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,279.96) --
-	(523.88,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,307.96) --
-	(523.88,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,335.97) --
-	(523.88,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,363.97) --
-	(523.88,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,391.97) --
-	(523.88,391.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,419.98) --
-	(523.88,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,447.98) --
-	(523.88,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (467.63, 67.14) --
-	(467.63,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (481.02, 67.14) --
-	(481.02,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (494.42, 67.14) --
-	(494.42,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (507.81, 67.14) --
-	(507.81,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (521.21, 67.14) --
-	(521.21,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (469.86, 25.44) --
+	(469.86,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (483.31, 25.44) --
+	(483.31,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (496.76, 25.44) --
+	(496.76,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (510.20, 25.44) --
+	(510.20,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32, 44.25) --
+	(519.67, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32, 75.60) --
+	(519.67, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32,106.95) --
+	(519.67,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32,138.30) --
+	(519.67,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32,169.65) --
+	(519.67,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32,201.00) --
+	(519.67,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32,232.35) --
+	(519.67,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32,263.70) --
+	(519.67,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32,295.05) --
+	(519.67,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32,326.40) --
+	(519.67,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32,357.75) --
+	(519.67,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32,389.10) --
+	(519.67,389.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32,420.45) --
+	(519.67,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32,451.80) --
+	(519.67,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.14, 25.44) --
+	(463.14,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (476.59, 25.44) --
+	(476.59,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (490.03, 25.44) --
+	(490.03,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (503.48, 25.44) --
+	(503.48,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (516.92, 25.44) --
+	(516.92,470.61);
 \definecolor{drawColor}{RGB}{153,153,51}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (469.39,137.15) --
-	(469.39,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (469.13,445.18) --
-	(469.13,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (469.13,447.98) --
-	(467.73,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (467.73,445.18) --
-	(467.73,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (468.32,417.18) --
-	(468.32,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (470.57,361.17) --
-	(470.57,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (468.00,333.17) --
-	(468.00,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (473.63,109.14) --
-	(473.63,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (473.63,111.94) --
-	(472.56,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (472.56,109.14) --
-	(472.56,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (473.57,277.16) --
-	(473.57,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (473.57,279.96) --
-	(467.68,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (467.68,277.16) --
-	(467.68,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (468.80,249.16) --
-	(468.80,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (468.11,165.15) --
-	(468.11,170.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (464.92,103.81) --
+	(464.92,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (464.92,106.95) --
+	(463.03,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.03,103.81) --
+	(463.03,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (464.65,448.66) --
+	(464.65,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (464.65,451.80) --
+	(463.25,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.25,448.66) --
+	(463.25,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.84,417.31) --
+	(463.84,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.84,420.45) --
+	(462.93,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.93,417.31) --
+	(462.93,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (466.10,354.61) --
+	(466.10,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (466.10,357.75) --
+	(462.12,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.12,354.61) --
+	(462.12,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.52,323.26) --
+	(463.52,329.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.52,326.40) --
+	(463.03,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.03,323.26) --
+	(463.03,329.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.17, 72.46) --
+	(469.17, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.17, 75.60) --
+	(468.09, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (468.09, 72.46) --
+	(468.09, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.11,260.56) --
+	(469.11,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.11,263.70) --
+	(463.20,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.20,260.56) --
+	(463.20,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (464.33,229.21) --
+	(464.33,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (464.33,232.35) --
+	(462.93,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.93,229.21) --
+	(462.93,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.63,135.16) --
+	(463.63,141.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.63,138.30) --
+	(462.98,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.98,135.16) --
+	(462.98,141.43);
 \definecolor{fillColor}{RGB}{153,153,51}
 
-\path[fill=fillColor] (468.43,139.95) circle (  3.57);
-
-\path[fill=fillColor] (468.43,447.98) circle (  1.43);
-
-\path[fill=fillColor] (467.84,419.98) circle (  1.43);
-
-\path[fill=fillColor] (468.59,363.97) circle (  1.43);
-
-\path[fill=fillColor] (467.73,335.97) circle (  1.43);
-
-\path[fill=fillColor] (473.09,111.94) circle (  3.57);
-
-\path[fill=fillColor] (470.63,279.96) circle (  1.43);
-
-\path[fill=fillColor] (468.11,251.96) circle (  1.43);
-
-\path[fill=fillColor] (467.79,167.95) circle (  1.43);
+\path[fill=fillColor] (463.95,106.95) circle (  1.96);
+
+\path[fill=fillColor] (463.95,451.80) circle (  1.96);
+
+\path[fill=fillColor] (463.36,420.45) circle (  1.96);
+
+\path[fill=fillColor] (464.11,357.75) circle (  1.96);
+
+\path[fill=fillColor] (463.25,326.40) circle (  1.96);
+
+\path[fill=fillColor] (468.63, 75.60) circle (  1.96);
+
+\path[fill=fillColor] (466.15,263.70) circle (  1.96);
+
+\path[fill=fillColor] (463.63,232.35) circle (  1.96);
+
+\path[fill=fillColor] (463.30,138.30) circle (  1.96);
 \definecolor{drawColor}{RGB}{169,169,169}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,153.95) -- (523.88,153.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.95,125.95) -- (523.88,125.95);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (464.95, 67.14) rectangle (523.88,464.78);
-\end{scope}
-\begin{scope}
-\path[clip] (529.38, 67.14) rectangle (588.32,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32,122.62) -- (519.67,122.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (459.32, 91.27) -- (519.67, 91.27);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (459.32, 25.44) rectangle (519.67,470.61);
+\end{scope}
+\begin{scope}
+\path[clip] (525.17, 25.44) rectangle (585.51,470.61);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (529.38, 67.14) rectangle (588.32,464.78);
+\path[fill=fillColor] (525.17, 25.44) rectangle (585.51,470.61);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (538.76, 67.14) --
-	(538.76,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (552.16, 67.14) --
-	(552.16,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (565.55, 67.14) --
-	(565.55,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (578.95, 67.14) --
-	(578.95,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38, 83.94) --
-	(588.32, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,111.94) --
-	(588.32,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,139.95) --
-	(588.32,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,167.95) --
-	(588.32,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,195.95) --
-	(588.32,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,223.96) --
-	(588.32,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,251.96) --
-	(588.32,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,279.96) --
-	(588.32,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,307.96) --
-	(588.32,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,335.97) --
-	(588.32,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,363.97) --
-	(588.32,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,391.97) --
-	(588.32,391.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,419.98) --
-	(588.32,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,447.98) --
-	(588.32,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (532.06, 67.14) --
-	(532.06,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (545.46, 67.14) --
-	(545.46,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (558.85, 67.14) --
-	(558.85,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (572.25, 67.14) --
-	(572.25,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (585.64, 67.14) --
-	(585.64,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (535.71, 25.44) --
+	(535.71,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (549.15, 25.44) --
+	(549.15,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (562.60, 25.44) --
+	(562.60,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (576.05, 25.44) --
+	(576.05,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17, 44.25) --
+	(585.51, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17, 75.60) --
+	(585.51, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17,106.95) --
+	(585.51,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17,138.30) --
+	(585.51,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17,169.65) --
+	(585.51,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17,201.00) --
+	(585.51,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17,232.35) --
+	(585.51,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17,263.70) --
+	(585.51,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17,295.05) --
+	(585.51,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17,326.40) --
+	(585.51,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17,357.75) --
+	(585.51,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17,389.10) --
+	(585.51,389.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17,420.45) --
+	(585.51,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17,451.80) --
+	(585.51,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (528.99, 25.44) --
+	(528.99,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (542.43, 25.44) --
+	(542.43,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (555.88, 25.44) --
+	(555.88,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (569.32, 25.44) --
+	(569.32,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (582.77, 25.44) --
+	(582.77,470.61);
 \definecolor{drawColor}{RGB}{136,34,85}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (533.78,137.15) --
-	(533.78,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (533.08,445.18) --
-	(533.08,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (532.87,417.18) --
-	(532.87,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (532.81,109.14) --
-	(532.81,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (532.81,111.94) --
-	(532.44,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (532.44,109.14) --
-	(532.44,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (535.55,249.16) --
-	(535.55,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (535.55,251.96) --
-	(532.81,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (532.81,249.16) --
-	(532.81,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (533.24,193.15) --
-	(533.24,198.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (530.71,103.81) --
+	(530.71,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (530.71,106.95) --
+	(528.66,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (528.66,103.81) --
+	(528.66,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (530.01,448.66) --
+	(530.01,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (530.01,451.80) --
+	(528.93,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (528.93,448.66) --
+	(528.93,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (529.79,417.31) --
+	(529.79,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (529.79,420.45) --
+	(528.72,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (528.72,417.31) --
+	(528.72,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (529.74, 72.46) --
+	(529.74, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (529.74, 75.60) --
+	(529.36, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (529.36, 72.46) --
+	(529.36, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (532.48,229.21) --
+	(532.48,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (532.48,232.35) --
+	(529.74,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (529.74,229.21) --
+	(529.74,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (530.17,166.51) --
+	(530.17,172.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (530.17,169.65) --
+	(528.93,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (528.93,166.51) --
+	(528.93,172.78);
 \definecolor{fillColor}{RGB}{136,34,85}
 
-\path[fill=fillColor] (532.76,139.95) circle (  3.57);
-
-\path[fill=fillColor] (532.55,447.98) circle (  1.43);
-
-\path[fill=fillColor] (532.33,419.98) circle (  1.43);
-
-\path[fill=fillColor] (532.60,111.94) circle (  3.57);
-
-\path[fill=fillColor] (534.21,251.96) circle (  3.57);
-
-\path[fill=fillColor] (532.60,195.95) circle (  1.43);
+\path[fill=fillColor] (529.69,106.95) circle (  1.96);
+
+\path[fill=fillColor] (529.47,451.80) circle (  1.96);
+
+\path[fill=fillColor] (529.25,420.45) circle (  1.96);
+
+\path[fill=fillColor] (529.52, 75.60) circle (  1.96);
+
+\path[fill=fillColor] (531.14,232.35) circle (  1.96);
+
+\path[fill=fillColor] (529.52,169.65) circle (  1.96);
 \definecolor{drawColor}{RGB}{169,169,169}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,153.95) -- (588.32,153.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (529.38,125.95) -- (588.32,125.95);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (529.38, 67.14) rectangle (588.32,464.78);
-\end{scope}
-\begin{scope}
-\path[clip] (593.82, 67.14) rectangle (652.76,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17,122.62) -- (585.51,122.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (525.17, 91.27) -- (585.51, 91.27);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (525.17, 25.44) rectangle (585.51,470.61);
+\end{scope}
+\begin{scope}
+\path[clip] (591.01, 25.44) rectangle (651.36,470.61);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (593.82, 67.14) rectangle (652.76,464.78);
+\path[fill=fillColor] (591.01, 25.44) rectangle (651.36,470.61);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (603.20, 67.14) --
-	(603.20,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (616.59, 67.14) --
-	(616.59,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (629.99, 67.14) --
-	(629.99,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (643.39, 67.14) --
-	(643.39,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82, 83.94) --
-	(652.76, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,111.94) --
-	(652.76,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,139.95) --
-	(652.76,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,167.95) --
-	(652.76,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,195.95) --
-	(652.76,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,223.96) --
-	(652.76,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,251.96) --
-	(652.76,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,279.96) --
-	(652.76,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,307.96) --
-	(652.76,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,335.97) --
-	(652.76,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,363.97) --
-	(652.76,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,391.97) --
-	(652.76,391.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,419.98) --
-	(652.76,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,447.98) --
-	(652.76,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (596.50, 67.14) --
-	(596.50,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (609.90, 67.14) --
-	(609.90,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (623.29, 67.14) --
-	(623.29,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (636.69, 67.14) --
-	(636.69,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (650.08, 67.14) --
-	(650.08,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (601.55, 25.44) --
+	(601.55,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (615.00, 25.44) --
+	(615.00,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (628.44, 25.44) --
+	(628.44,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (641.89, 25.44) --
+	(641.89,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01, 44.25) --
+	(651.36, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01, 75.60) --
+	(651.36, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01,106.95) --
+	(651.36,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01,138.30) --
+	(651.36,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01,169.65) --
+	(651.36,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01,201.00) --
+	(651.36,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01,232.35) --
+	(651.36,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01,263.70) --
+	(651.36,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01,295.05) --
+	(651.36,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01,326.40) --
+	(651.36,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01,357.75) --
+	(651.36,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01,389.10) --
+	(651.36,389.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01,420.45) --
+	(651.36,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01,451.80) --
+	(651.36,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (594.83, 25.44) --
+	(594.83,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (608.28, 25.44) --
+	(608.28,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (621.72, 25.44) --
+	(621.72,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (635.17, 25.44) --
+	(635.17,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (648.61, 25.44) --
+	(648.61,470.61);
 \definecolor{drawColor}{RGB}{102,17,0}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (605.61,137.15) --
-	(605.61,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (605.61,139.95) --
-	(599.77,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (599.77,137.15) --
-	(599.77,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (608.34,445.18) --
-	(608.34,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (608.34,447.98) --
-	(603.84,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (603.84,445.18) --
-	(603.84,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (604.11,417.18) --
-	(604.11,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (604.11,419.98) --
-	(599.61,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (599.61,417.18) --
-	(599.61,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.36,361.17) --
-	(600.36,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.25,333.17) --
-	(600.25,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.25,335.97) --
-	(598.00,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (598.00,333.17) --
-	(598.00,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (606.90,305.16) --
-	(606.90,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (606.90,307.96) --
-	(600.31,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.31,305.16) --
-	(600.31,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (608.72,109.14) --
-	(608.72,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (608.72,111.94) --
-	(607.27,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (607.27,109.14) --
-	(607.27,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (613.17,277.16) --
-	(613.17,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (613.17,279.96) --
-	(602.66,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (602.66,277.16) --
-	(602.66,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (610.17,249.16) --
-	(610.17,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (610.17,251.96) --
-	(604.59,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (604.59,249.16) --
-	(604.59,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (599.56,221.16) --
-	(599.56,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (599.56,223.96) --
-	(597.20,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (597.20,221.16) --
-	(597.20,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (603.84,165.15) --
-	(603.84,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (603.84,167.95) --
-	(600.25,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.25,165.15) --
-	(600.25,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (601.16, 81.14) --
-	(601.16, 86.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (601.16, 83.94) --
-	(598.32, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (598.32, 81.14) --
-	(598.32, 86.74);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (603.97,103.81) --
+	(603.97,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (603.97,106.95) --
+	(598.11,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.11,103.81) --
+	(598.11,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (606.72,448.66) --
+	(606.72,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (606.72,451.80) --
+	(602.20,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (602.20,448.66) --
+	(602.20,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (602.47,417.31) --
+	(602.47,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (602.47,420.45) --
+	(597.95,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (597.95,417.31) --
+	(597.95,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.70,354.61) --
+	(598.70,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.70,357.75) --
+	(594.02,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (594.02,354.61) --
+	(594.02,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.60,323.26) --
+	(598.60,329.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.60,326.40) --
+	(596.34,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (596.34,323.26) --
+	(596.34,329.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (605.26,291.91) --
+	(605.26,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (605.26,295.05) --
+	(598.65,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.65,291.91) --
+	(598.65,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (607.09, 72.46) --
+	(607.09, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (607.09, 75.60) --
+	(605.64, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (605.64, 72.46) --
+	(605.64, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (611.56,260.56) --
+	(611.56,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (611.56,263.70) --
+	(601.02,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (601.02,260.56) --
+	(601.02,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (608.54,229.21) --
+	(608.54,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (608.54,232.35) --
+	(602.95,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (602.95,229.21) --
+	(602.95,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (597.90,197.86) --
+	(597.90,204.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (597.90,201.00) --
+	(595.53,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (595.53,197.86) --
+	(595.53,204.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (602.20,135.16) --
+	(602.20,141.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (602.20,138.30) --
+	(598.60,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.60,135.16) --
+	(598.60,141.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (599.51, 41.12) --
+	(599.51, 47.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (599.51, 44.25) --
+	(596.66, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (596.66, 41.12) --
+	(596.66, 47.39);
 \definecolor{fillColor}{RGB}{102,17,0}
 
-\path[fill=fillColor] (602.72,139.95) circle (  3.57);
-
-\path[fill=fillColor] (606.09,447.98) circle (  3.57);
-
-\path[fill=fillColor] (601.86,419.98) circle (  3.57);
-
-\path[fill=fillColor] (598.00,363.97) circle (  1.43);
-
-\path[fill=fillColor] (599.13,335.97) circle (  3.57);
-
-\path[fill=fillColor] (603.57,307.96) circle (  3.57);
-
-\path[fill=fillColor] (607.97,111.94) circle (  3.57);
-
-\path[fill=fillColor] (607.91,279.96) circle (  3.57);
-
-\path[fill=fillColor] (607.38,251.96) circle (  3.57);
-
-\path[fill=fillColor] (598.38,223.96) circle (  3.57);
-
-\path[fill=fillColor] (602.02,167.95) circle (  3.57);
-
-\path[fill=fillColor] (599.72, 83.94) circle (  3.57);
+\path[fill=fillColor] (601.07,106.95) circle (  1.96);
+
+\path[fill=fillColor] (604.46,451.80) circle (  1.96);
+
+\path[fill=fillColor] (600.21,420.45) circle (  1.96);
+
+\path[fill=fillColor] (596.34,357.75) circle (  1.96);
+
+\path[fill=fillColor] (597.47,326.40) circle (  1.96);
+
+\path[fill=fillColor] (601.93,295.05) circle (  1.96);
+
+\path[fill=fillColor] (606.34, 75.60) circle (  1.96);
+
+\path[fill=fillColor] (606.29,263.70) circle (  1.96);
+
+\path[fill=fillColor] (605.75,232.35) circle (  1.96);
+
+\path[fill=fillColor] (596.71,201.00) circle (  1.96);
+
+\path[fill=fillColor] (600.37,138.30) circle (  1.96);
+
+\path[fill=fillColor] (598.06, 44.25) circle (  1.96);
 \definecolor{drawColor}{RGB}{169,169,169}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,153.95) -- (652.76,153.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.82,125.95) -- (652.76,125.95);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (593.82, 67.14) rectangle (652.76,464.78);
-\end{scope}
-\begin{scope}
-\path[clip] (658.26, 67.14) rectangle (717.20,464.78);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01,122.62) -- (651.36,122.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.01, 91.27) -- (651.36, 91.27);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (591.01, 25.44) rectangle (651.36,470.61);
+\end{scope}
+\begin{scope}
+\path[clip] (656.86, 25.44) rectangle (717.20,470.61);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (658.26, 67.14) rectangle (717.20,464.78);
+\path[fill=fillColor] (656.86, 25.44) rectangle (717.20,470.61);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (667.64, 67.14) --
-	(667.64,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (681.03, 67.14) --
-	(681.03,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (694.43, 67.14) --
-	(694.43,464.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (707.82, 67.14) --
-	(707.82,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26, 83.94) --
-	(717.20, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,111.94) --
-	(717.20,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,139.95) --
-	(717.20,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,167.95) --
-	(717.20,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,195.95) --
-	(717.20,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,223.96) --
-	(717.20,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,251.96) --
-	(717.20,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,279.96) --
-	(717.20,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,307.96) --
-	(717.20,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,335.97) --
-	(717.20,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,363.97) --
-	(717.20,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,391.97) --
-	(717.20,391.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,419.98) --
-	(717.20,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,447.98) --
-	(717.20,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (660.94, 67.14) --
-	(660.94,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (674.34, 67.14) --
-	(674.34,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (687.73, 67.14) --
-	(687.73,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (701.13, 67.14) --
-	(701.13,464.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (714.52, 67.14) --
-	(714.52,464.78);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (667.40, 25.44) --
+	(667.40,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (680.84, 25.44) --
+	(680.84,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (694.29, 25.44) --
+	(694.29,470.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (707.73, 25.44) --
+	(707.73,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86, 44.25) --
+	(717.20, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86, 75.60) --
+	(717.20, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86,106.95) --
+	(717.20,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86,138.30) --
+	(717.20,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86,169.65) --
+	(717.20,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86,201.00) --
+	(717.20,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86,232.35) --
+	(717.20,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86,263.70) --
+	(717.20,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86,295.05) --
+	(717.20,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86,326.40) --
+	(717.20,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86,357.75) --
+	(717.20,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86,389.10) --
+	(717.20,389.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86,420.45) --
+	(717.20,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86,451.80) --
+	(717.20,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (660.67, 25.44) --
+	(660.67,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (674.12, 25.44) --
+	(674.12,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (687.57, 25.44) --
+	(687.57,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (701.01, 25.44) --
+	(701.01,470.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (714.46, 25.44) --
+	(714.46,470.61);
 \definecolor{drawColor}{RGB}{102,153,204}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (673.64,137.15) --
-	(673.64,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (673.64,139.95) --
-	(666.83,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (666.83,137.15) --
-	(666.83,142.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (667.26,445.18) --
-	(667.26,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (667.26,447.98) --
-	(663.94,447.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (663.94,445.18) --
-	(663.94,450.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (681.41,417.18) --
-	(681.41,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (681.41,419.98) --
-	(674.39,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (674.39,417.18) --
-	(674.39,422.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (677.55,389.17) --
-	(677.55,394.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (677.55,391.97) --
-	(667.48,391.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (667.48,389.17) --
-	(667.48,394.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (673.53,361.17) --
-	(673.53,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (673.53,363.97) --
-	(661.37,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (661.37,361.17) --
-	(661.37,366.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (677.60,333.17) --
-	(677.60,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (677.60,335.97) --
-	(673.00,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (673.00,333.17) --
-	(673.00,338.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (676.37,305.16) --
-	(676.37,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (676.37,307.96) --
-	(666.51,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (666.51,305.16) --
-	(666.51,310.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (664.05,109.14) --
-	(664.05,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (664.05,111.94) --
-	(663.30,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (663.30,109.14) --
-	(663.30,114.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (680.39,277.16) --
-	(680.39,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (680.39,279.96) --
-	(669.14,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (669.14,277.16) --
-	(669.14,282.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (665.60,249.16) --
-	(665.60,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (665.60,251.96) --
-	(662.44,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (662.44,249.16) --
-	(662.44,254.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (677.18,221.16) --
-	(677.18,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (677.18,223.96) --
-	(671.28,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (671.28,221.16) --
-	(671.28,226.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (666.83,193.15) --
-	(666.83,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (666.83,195.95) --
-	(663.57,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (663.57,193.15) --
-	(663.57,198.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (665.50,165.15) --
-	(665.50,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (665.50,167.95) --
-	(662.76,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (662.76,165.15) --
-	(662.76,170.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.36, 81.14) --
-	(690.36, 86.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.36, 83.94) --
-	(684.14, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (684.14, 81.14) --
-	(684.14, 86.74);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (673.42,103.81) --
+	(673.42,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (673.42,106.95) --
+	(666.59,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (666.59,103.81) --
+	(666.59,110.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (667.02,448.66) --
+	(667.02,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (667.02,451.80) --
+	(663.69,451.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (663.69,448.66) --
+	(663.69,454.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (681.22,417.31) --
+	(681.22,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (681.22,420.45) --
+	(674.17,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (674.17,417.31) --
+	(674.17,423.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (677.35,385.96) --
+	(677.35,392.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (677.35,389.10) --
+	(667.24,389.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (667.24,385.96) --
+	(667.24,392.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (673.31,354.61) --
+	(673.31,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (673.31,357.75) --
+	(661.10,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (661.10,354.61) --
+	(661.10,360.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (677.40,323.26) --
+	(677.40,329.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (677.40,326.40) --
+	(672.78,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (672.78,323.26) --
+	(672.78,329.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (676.16,291.91) --
+	(676.16,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (676.16,295.05) --
+	(666.27,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (666.27,291.91) --
+	(666.27,298.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (663.79, 72.46) --
+	(663.79, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (663.79, 75.60) --
+	(663.04, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (663.04, 72.46) --
+	(663.04, 78.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (680.20,260.56) --
+	(680.20,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (680.20,263.70) --
+	(668.90,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (668.90,260.56) --
+	(668.90,266.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (665.35,229.21) --
+	(665.35,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (665.35,232.35) --
+	(662.18,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (662.18,229.21) --
+	(662.18,235.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (676.97,197.86) --
+	(676.97,204.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (676.97,201.00) --
+	(671.05,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (671.05,197.86) --
+	(671.05,204.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (666.59,166.51) --
+	(666.59,172.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (666.59,169.65) --
+	(663.31,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (663.31,166.51) --
+	(663.31,172.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (665.25,135.16) --
+	(665.25,141.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (665.25,138.30) --
+	(662.50,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (662.50,135.16) --
+	(662.50,141.43);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (690.20, 41.12) --
+	(690.20, 47.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (690.20, 44.25) --
+	(683.96, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (683.96, 41.12) --
+	(683.96, 47.39);
 \definecolor{fillColor}{RGB}{102,153,204}
 
-\path[fill=fillColor] (670.21,139.95) circle (  3.57);
-
-\path[fill=fillColor] (665.60,447.98) circle (  3.57);
-
-\path[fill=fillColor] (677.87,419.98) circle (  3.57);
-
-\path[fill=fillColor] (672.51,391.97) circle (  3.57);
-
-\path[fill=fillColor] (667.42,363.97) circle (  3.57);
-
-\path[fill=fillColor] (675.30,335.97) circle (  3.57);
-
-\path[fill=fillColor] (671.44,307.96) circle (  3.57);
-
-\path[fill=fillColor] (663.67,111.94) circle (  3.57);
-
-\path[fill=fillColor] (674.76,279.96) circle (  3.57);
-
-\path[fill=fillColor] (663.99,251.96) circle (  3.57);
-
-\path[fill=fillColor] (674.23,223.96) circle (  3.57);
-
-\path[fill=fillColor] (665.23,195.95) circle (  3.57);
-
-\path[fill=fillColor] (664.16,167.95) circle (  3.57);
-
-\path[fill=fillColor] (687.25, 83.94) circle (  3.57);
+\path[fill=fillColor] (669.98,106.95) circle (  1.96);
+
+\path[fill=fillColor] (665.35,451.80) circle (  1.96);
+
+\path[fill=fillColor] (677.67,420.45) circle (  1.96);
+
+\path[fill=fillColor] (672.29,389.10) circle (  1.96);
+
+\path[fill=fillColor] (667.18,357.75) circle (  1.96);
+
+\path[fill=fillColor] (675.09,326.40) circle (  1.96);
+
+\path[fill=fillColor] (671.22,295.05) circle (  1.96);
+
+\path[fill=fillColor] (663.42, 75.60) circle (  1.96);
+
+\path[fill=fillColor] (674.55,263.70) circle (  1.96);
+
+\path[fill=fillColor] (663.74,232.35) circle (  1.96);
+
+\path[fill=fillColor] (674.01,201.00) circle (  1.96);
+
+\path[fill=fillColor] (664.98,169.65) circle (  1.96);
+
+\path[fill=fillColor] (663.90,138.30) circle (  1.96);
+
+\path[fill=fillColor] (687.08, 44.25) circle (  1.96);
 \definecolor{drawColor}{RGB}{169,169,169}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,153.95) -- (717.20,153.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (658.26,125.95) -- (717.20,125.95);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (658.26, 67.14) rectangle (717.20,464.78);
-\end{scope}
-\begin{scope}
-\path[clip] ( 78.32,464.78) rectangle (137.25,519.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86,122.62) -- (717.20,122.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (656.86, 91.27) -- (717.20, 91.27);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (656.86, 25.44) rectangle (717.20,470.61);
+\end{scope}
+\begin{scope}
+\path[clip] ( 64.26,470.61) rectangle (124.60,522.86);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 78.32,464.78) rectangle (137.25,519.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 64.26,470.61) rectangle (124.60,522.86);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (107.79,498.55) {Concerned};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (107.79,489.04) {about side};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (107.79,479.54) {effects};
-\end{scope}
-\begin{scope}
-\path[clip] (142.75,464.78) rectangle (201.69,519.37);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 94.43,504.12) {Concerned};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 94.43,494.62) {about side};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 94.43,485.11) {effects};
+\end{scope}
+\begin{scope}
+\path[clip] (130.10,470.61) rectangle (190.45,522.86);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (142.75,464.78) rectangle (201.69,519.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (130.10,470.61) rectangle (190.45,522.86);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.22,508.05) {Concerned};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.22,498.55) {about getting};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.22,489.04) {coronavirus};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.22,479.54) {from the};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.22,470.04) {vaccine};
-\end{scope}
-\begin{scope}
-\path[clip] (207.19,464.78) rectangle (266.13,519.37);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (160.27,513.62) {Concerned};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (160.27,504.12) {about getting};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (160.27,494.62) {coronavirus};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (160.27,485.11) {from the};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (160.27,475.61) {vaccine};
+\end{scope}
+\begin{scope}
+\path[clip] (195.95,470.61) rectangle (256.29,522.86);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (207.19,464.78) rectangle (266.13,519.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (195.95,470.61) rectangle (256.29,522.86);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (236.66,498.55) {Not concerned};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (236.66,489.04) {about getting};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (236.66,479.54) {seriously ill};
-\end{scope}
-\begin{scope}
-\path[clip] (271.63,464.78) rectangle (330.57,519.37);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (226.12,504.12) {Not concerned};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (226.12,494.62) {about getting};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (226.12,485.11) {seriously ill};
+\end{scope}
+\begin{scope}
+\path[clip] (261.79,470.61) rectangle (322.14,522.86);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (271.63,464.78) rectangle (330.57,519.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (261.79,470.61) rectangle (322.14,522.86);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (301.10,498.55) {Doesn't think};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (301.10,489.04) {vaccines are};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (301.10,479.54) {effective};
-\end{scope}
-\begin{scope}
-\path[clip] (336.07,464.78) rectangle (395.01,519.37);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (291.96,504.12) {Doesn't think};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (291.96,494.62) {vaccines are};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (291.96,485.11) {effective};
+\end{scope}
+\begin{scope}
+\path[clip] (327.64,470.61) rectangle (387.98,522.86);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (336.07,464.78) rectangle (395.01,519.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (327.64,470.61) rectangle (387.98,522.86);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (365.54,508.05) {Doesn't think};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (365.54,498.55) {Coronavirus};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (365.54,489.04) {outbreak is as};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (365.54,479.54) {serious as};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (365.54,470.04) {people say};
-\end{scope}
-\begin{scope}
-\path[clip] (400.51,464.78) rectangle (459.45,519.37);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (357.81,513.62) {Doesn't think};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (357.81,504.12) {Coronavirus};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (357.81,494.62) {outbreak is as};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (357.81,485.11) {serious as};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (357.81,475.61) {people say};
+\end{scope}
+\begin{scope}
+\path[clip] (393.48,470.61) rectangle (453.82,522.86);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (400.51,464.78) rectangle (459.45,519.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (393.48,470.61) rectangle (453.82,522.86);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (429.98,493.80) {Doesn't like};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (429.98,484.29) {needles};
-\end{scope}
-\begin{scope}
-\path[clip] (464.95,464.78) rectangle (523.88,519.37);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (423.65,499.37) {Doesn't like};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (423.65,489.86) {needles};
+\end{scope}
+\begin{scope}
+\path[clip] (459.32,470.61) rectangle (519.67,522.86);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (464.95,464.78) rectangle (523.88,519.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (459.32,470.61) rectangle (519.67,522.86);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (494.42,493.80) {Allergic to};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (494.42,484.29) {vaccines};
-\end{scope}
-\begin{scope}
-\path[clip] (529.38,464.78) rectangle (588.32,519.37);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (489.50,499.37) {Allergic to};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (489.50,489.86) {vaccines};
+\end{scope}
+\begin{scope}
+\path[clip] (525.17,470.61) rectangle (585.51,522.86);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (529.38,464.78) rectangle (588.32,519.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (525.17,470.61) rectangle (585.51,522.86);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (558.85,498.55) {Won't have};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (558.85,489.04) {time to get};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (558.85,479.54) {vaccinated};
-\end{scope}
-\begin{scope}
-\path[clip] (593.82,464.78) rectangle (652.76,519.37);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (555.34,504.12) {Won't have};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (555.34,494.62) {time to get};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (555.34,485.11) {vaccinated};
+\end{scope}
+\begin{scope}
+\path[clip] (591.01,470.61) rectangle (651.36,522.86);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (593.82,464.78) rectangle (652.76,519.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (591.01,470.61) rectangle (651.36,522.86);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (623.29,498.55) {Mentions a};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (623.29,489.04) {conspiracy};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (623.29,479.54) {theory};
-\end{scope}
-\begin{scope}
-\path[clip] (658.26,464.78) rectangle (717.20,519.37);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (621.18,504.12) {Mentions a};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (621.18,494.62) {conspiracy};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (621.18,485.11) {theory};
+\end{scope}
+\begin{scope}
+\path[clip] (656.86,470.61) rectangle (717.20,522.86);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (658.26,464.78) rectangle (717.20,519.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (656.86,470.61) rectangle (717.20,522.86);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (687.73,489.04) {Other reasons};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (687.03,494.62) {Other reasons};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.00, 64.39) --
-	( 81.00, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.39, 64.39) --
-	( 94.39, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (107.79, 64.39) --
-	(107.79, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (121.18, 64.39) --
-	(121.18, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (134.58, 64.39) --
-	(134.58, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.08, 22.69) --
+	( 68.08, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.52, 22.69) --
+	( 81.52, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.97, 22.69) --
+	( 94.97, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (108.41, 22.69) --
+	(108.41, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (121.86, 22.69) --
+	(121.86, 25.44);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 81.00, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 94.39, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (107.79, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (121.18, 56.13) {75};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (134.58, 56.13) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 68.08, 16.25) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 81.52, 16.25) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 94.97, 16.25) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (108.41, 16.25) {75};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (121.86, 16.25) {100};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (145.43, 64.39) --
-	(145.43, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (158.83, 64.39) --
-	(158.83, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (172.22, 64.39) --
-	(172.22, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (185.62, 64.39) --
-	(185.62, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (199.01, 64.39) --
-	(199.01, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (133.92, 22.69) --
+	(133.92, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (147.37, 22.69) --
+	(147.37, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (160.81, 22.69) --
+	(160.81, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (174.26, 22.69) --
+	(174.26, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (187.70, 22.69) --
+	(187.70, 25.44);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (145.43, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (158.83, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.22, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (185.62, 56.13) {75};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (199.01, 56.13) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (133.92, 16.25) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (147.37, 16.25) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (160.81, 16.25) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (174.26, 16.25) {75};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (187.70, 16.25) {100};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.87, 64.39) --
-	(209.87, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (223.27, 64.39) --
-	(223.27, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (236.66, 64.39) --
-	(236.66, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (250.06, 64.39) --
-	(250.06, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (263.45, 64.39) --
-	(263.45, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (199.77, 22.69) --
+	(199.77, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (213.21, 22.69) --
+	(213.21, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (226.66, 22.69) --
+	(226.66, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (240.10, 22.69) --
+	(240.10, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (253.55, 22.69) --
+	(253.55, 25.44);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (209.87, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (223.27, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (236.66, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (250.06, 56.13) {75};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (263.45, 56.13) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (199.77, 16.25) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (213.21, 16.25) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (226.66, 16.25) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (240.10, 16.25) {75};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (253.55, 16.25) {100};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (274.31, 64.39) --
-	(274.31, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (287.71, 64.39) --
-	(287.71, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (301.10, 64.39) --
-	(301.10, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (314.50, 64.39) --
-	(314.50, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (327.89, 64.39) --
-	(327.89, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (265.61, 22.69) --
+	(265.61, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (279.06, 22.69) --
+	(279.06, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (292.50, 22.69) --
+	(292.50, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (305.95, 22.69) --
+	(305.95, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (319.39, 22.69) --
+	(319.39, 25.44);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (274.31, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (287.71, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (301.10, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (314.50, 56.13) {75};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (327.89, 56.13) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (265.61, 16.25) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (279.06, 16.25) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (292.50, 16.25) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (305.95, 16.25) {75};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (319.39, 16.25) {100};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.75, 64.39) --
-	(338.75, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (352.14, 64.39) --
-	(352.14, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (365.54, 64.39) --
-	(365.54, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (378.93, 64.39) --
-	(378.93, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (392.33, 64.39) --
-	(392.33, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (331.45, 22.69) --
+	(331.45, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (344.90, 22.69) --
+	(344.90, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (358.34, 22.69) --
+	(358.34, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (371.79, 22.69) --
+	(371.79, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (385.24, 22.69) --
+	(385.24, 25.44);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (338.75, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (352.14, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (365.54, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (378.93, 56.13) {75};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (392.33, 56.13) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (331.45, 16.25) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (344.90, 16.25) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (358.34, 16.25) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (371.79, 16.25) {75};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (385.24, 16.25) {100};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (403.19, 64.39) --
-	(403.19, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (416.58, 64.39) --
-	(416.58, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (429.98, 64.39) --
-	(429.98, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (443.37, 64.39) --
-	(443.37, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (456.77, 64.39) --
-	(456.77, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (397.30, 22.69) --
+	(397.30, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (410.74, 22.69) --
+	(410.74, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (424.19, 22.69) --
+	(424.19, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (437.63, 22.69) --
+	(437.63, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (451.08, 22.69) --
+	(451.08, 25.44);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (403.19, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (416.58, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (429.98, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (443.37, 56.13) {75};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (456.77, 56.13) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (397.30, 16.25) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (410.74, 16.25) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (424.19, 16.25) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (437.63, 16.25) {75};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (451.08, 16.25) {100};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (467.63, 64.39) --
-	(467.63, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (481.02, 64.39) --
-	(481.02, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (494.42, 64.39) --
-	(494.42, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (507.81, 64.39) --
-	(507.81, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (521.21, 64.39) --
-	(521.21, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.14, 22.69) --
+	(463.14, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (476.59, 22.69) --
+	(476.59, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (490.03, 22.69) --
+	(490.03, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (503.48, 22.69) --
+	(503.48, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (516.92, 22.69) --
+	(516.92, 25.44);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (467.63, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (481.02, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (494.42, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (507.81, 56.13) {75};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (521.21, 56.13) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (463.14, 16.25) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (476.59, 16.25) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (490.03, 16.25) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (503.48, 16.25) {75};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (516.92, 16.25) {100};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (532.06, 64.39) --
-	(532.06, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (545.46, 64.39) --
-	(545.46, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (558.85, 64.39) --
-	(558.85, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (572.25, 64.39) --
-	(572.25, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (585.64, 64.39) --
-	(585.64, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (528.99, 22.69) --
+	(528.99, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (542.43, 22.69) --
+	(542.43, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (555.88, 22.69) --
+	(555.88, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (569.32, 22.69) --
+	(569.32, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (582.77, 22.69) --
+	(582.77, 25.44);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (532.06, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (545.46, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (558.85, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (572.25, 56.13) {75};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (585.64, 56.13) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (528.99, 16.25) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (542.43, 16.25) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (555.88, 16.25) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (569.32, 16.25) {75};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (582.77, 16.25) {100};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (596.50, 64.39) --
-	(596.50, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (609.90, 64.39) --
-	(609.90, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (623.29, 64.39) --
-	(623.29, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (636.69, 64.39) --
-	(636.69, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (650.08, 64.39) --
-	(650.08, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (594.83, 22.69) --
+	(594.83, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (608.28, 22.69) --
+	(608.28, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (621.72, 22.69) --
+	(621.72, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (635.17, 22.69) --
+	(635.17, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (648.61, 22.69) --
+	(648.61, 25.44);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (596.50, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (609.90, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (623.29, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (636.69, 56.13) {75};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (650.08, 56.13) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (594.83, 16.25) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (608.28, 16.25) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (621.72, 16.25) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (635.17, 16.25) {75};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (648.61, 16.25) {100};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (660.94, 64.39) --
-	(660.94, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (674.34, 64.39) --
-	(674.34, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (687.73, 64.39) --
-	(687.73, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (701.13, 64.39) --
-	(701.13, 67.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (714.52, 64.39) --
-	(714.52, 67.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (660.67, 22.69) --
+	(660.67, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (674.12, 22.69) --
+	(674.12, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (687.57, 22.69) --
+	(687.57, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (701.01, 22.69) --
+	(701.01, 25.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (714.46, 22.69) --
+	(714.46, 25.44);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (660.94, 56.13) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (674.34, 56.13) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (687.73, 56.13) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (701.13, 56.13) {75};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (714.52, 56.13) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (660.67, 16.25) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (674.12, 16.25) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (687.57, 16.25) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (701.01, 16.25) {75};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (714.46, 16.25) {100};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96, 80.91) {USA};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,108.91) {Russia};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,136.92) {All LMICs};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,164.92) {Uganda 2};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,192.92) {Uganda 1};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,220.93) {Sierra Leone 2};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,248.93) {Sierra Leone 1};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,276.93) {Rwanda};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,304.93) {Pakistan 1};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,332.94) {Nigeria};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,360.94) {Nepal};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,388.94) {Mozambique};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,416.95) {Colombia};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,444.95) {Burkina Faso};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05, 46.88) {USA};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05, 37.38) {(n=462)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05, 78.23) {Russia};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05, 68.73) {(n=16238)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,104.83) {All LMICs};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,140.93) {Uganda 2};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,131.43) {(n=319)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,172.28) {Uganda 1};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,162.78) {(n=289)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,203.63) {Sierra Leone 2};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,194.13) {(n=254)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,234.98) {Sierra Leone 1};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,225.48) {(n=234)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,266.33) {Rwanda};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,256.83) {(n=70)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,297.68) {Pakistan 1};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,288.18) {(n=441)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,329.03) {Nigeria};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,319.53) {(n=410)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,360.38) {Nepal};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,350.88) {(n=48)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,391.73) {Mozambique};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,382.23) {(n=74)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,423.08) {Colombia};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,413.58) {(n=202)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,454.43) {Burkina Faso};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,444.93) {(n=325)};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57, 83.94) --
-	( 78.32, 83.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,111.94) --
-	( 78.32,111.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,139.95) --
-	( 78.32,139.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,167.95) --
-	( 78.32,167.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,195.95) --
-	( 78.32,195.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,223.96) --
-	( 78.32,223.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,251.96) --
-	( 78.32,251.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,279.96) --
-	( 78.32,279.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,307.96) --
-	( 78.32,307.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,335.97) --
-	( 78.32,335.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,363.97) --
-	( 78.32,363.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,391.97) --
-	( 78.32,391.97);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,419.98) --
-	( 78.32,419.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.57,447.98) --
-	( 78.32,447.98);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 61.51, 44.25) --
+	( 64.26, 44.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 61.51, 75.60) --
+	( 64.26, 75.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 61.51,106.95) --
+	( 64.26,106.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 61.51,138.30) --
+	( 64.26,138.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 61.51,169.65) --
+	( 64.26,169.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 61.51,201.00) --
+	( 64.26,201.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 61.51,232.35) --
+	( 64.26,232.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 61.51,263.70) --
+	( 64.26,263.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 61.51,295.05) --
+	( 64.26,295.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 61.51,326.40) --
+	( 64.26,326.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 61.51,357.75) --
+	( 64.26,357.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 61.51,389.10) --
+	( 64.26,389.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 61.51,420.45) --
+	( 64.26,420.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 61.51,451.80) --
+	( 64.26,451.80);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (397.76, 44.09) {estimate};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (284.57,  5.50) rectangle (510.95, 30.95);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (390.73,  7.00) {estimate};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (290.07, 14.44) {Number of observations};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (409.70, 11.00) rectangle (424.15, 25.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[fill=fillColor] (416.92, 18.23) circle (  1.43);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (465.45, 11.00) rectangle (479.91, 25.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
-\definecolor{fillColor}{RGB}{0,0,0}
-
-\path[fill=fillColor] (472.68, 18.23) circle (  3.57);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (429.65, 15.20) {[50,500)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (485.41, 15.20) {500+};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,542.02);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  5.50,527.43) {Why would you not take the COVID-19 vaccine?};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  5.50,530.16) {Why would you not take the COVID-19 vaccine?};
 \end{scope}

### 2021-06-22 paper_files/figure-latex/genderhist-1.tex
update

--- 2021-03-23 paper_files/figure-latex/fig3paper-1.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:37
+% Created by tikzDevice version 0.12.3.1 on 2021-06-22 11:48:37
 % !TEX encoding = UTF-8 Unicode
-\documentclass[10pt]{article}
+% !TEX program = xelatex
+
+\documentclass[fontsize=7pt,DIV=calc]{scrartcl}
 
@@
 \begin{scope}
-\path[clip] ( 48.28,547.64) rectangle (371.71,627.77);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,547.64) rectangle (371.71,627.77);
+\path[clip] ( 41.25,548.04) rectangle (369.36,631.27);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 41.25,548.04) rectangle (369.36,631.27);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,560.96) --
-	(371.71,560.96);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,580.31) --
-	(371.71,580.31);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,599.67) --
-	(371.71,599.67);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,619.02) --
-	(371.71,619.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,551.28) --
-	(371.71,551.28);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,570.64) --
-	(371.71,570.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,589.99) --
-	(371.71,589.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,609.34) --
-	(371.71,609.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,547.64) --
-	( 75.24,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,547.64) --
-	(120.16,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,547.64) --
-	(165.08,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,547.64) --
-	(209.99,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,547.64) --
-	(254.91,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,547.64) --
-	(299.83,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,547.64) --
-	(344.75,627.77);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,562.24) --
+	(369.36,562.24);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,583.07) --
+	(369.36,583.07);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,603.90) --
+	(369.36,603.90);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,624.74) --
+	(369.36,624.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,551.82) --
+	(369.36,551.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,572.66) --
+	(369.36,572.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,593.49) --
+	(369.36,593.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,614.32) --
+	(369.36,614.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,548.04) --
+	( 68.60,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,548.04) --
+	(114.17,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,548.04) --
+	(159.74,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,548.04) --
+	(205.31,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,548.04) --
+	(250.88,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,548.04) --
+	(296.45,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,548.04) --
+	(342.02,631.27);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,551.28) rectangle (185.29,565.53);
-
-\path[fill=fillColor] (261.65,551.28) rectangle (275.13,552.76);
-
-\path[fill=fillColor] (216.73,551.28) rectangle (230.21,552.68);
-
-\path[fill=fillColor] (306.57,551.28) rectangle (320.05,560.26);
-
-\path[fill=fillColor] (351.49,551.28) rectangle (364.97,552.60);
-
-\path[fill=fillColor] ( 81.97,551.28) rectangle ( 95.45,591.23);
-
-\path[fill=fillColor] (126.89,551.28) rectangle (140.37,561.27);
+\path[fill=fillColor] (166.57,551.82) rectangle (180.24,567.16);
+
+\path[fill=fillColor] (257.71,551.82) rectangle (271.38,553.41);
+
+\path[fill=fillColor] (212.14,551.82) rectangle (225.81,553.32);
+
+\path[fill=fillColor] (303.28,551.82) rectangle (316.95,561.49);
+
+\path[fill=fillColor] (348.85,551.82) rectangle (362.52,553.24);
+
+\path[fill=fillColor] ( 75.43,551.82) rectangle ( 89.10,594.82);
+
+\path[fill=fillColor] (121.00,551.82) rectangle (134.67,562.57);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,551.28) rectangle (171.81,566.46);
-
-\path[fill=fillColor] (248.18,551.28) rectangle (261.65,552.83);
-
-\path[fill=fillColor] (203.26,551.28) rectangle (216.73,551.98);
-
-\path[fill=fillColor] (293.10,551.28) rectangle (306.57,555.00);
-
-\path[fill=fillColor] (338.02,551.28) rectangle (351.49,551.59);
-
-\path[fill=fillColor] ( 68.50,551.28) rectangle ( 81.97,595.49);
-
-\path[fill=fillColor] (113.42,551.28) rectangle (126.89,562.97);
+\path[fill=fillColor] (152.90,551.82) rectangle (166.57,565.74);
+
+\path[fill=fillColor] (244.04,551.82) rectangle (257.71,552.99);
+
+\path[fill=fillColor] (198.47,551.82) rectangle (212.14,553.24);
+
+\path[fill=fillColor] (289.61,551.82) rectangle (303.28,562.41);
+
+\path[fill=fillColor] (335.18,551.82) rectangle (348.85,553.32);
+
+\path[fill=fillColor] ( 61.76,551.82) rectangle ( 75.43,594.65);
+
+\path[fill=fillColor] (107.33,551.82) rectangle (121.00,563.66);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,551.28) rectangle (158.34,563.83);
-
-\path[fill=fillColor] (234.70,551.28) rectangle (248.18,552.52);
-
-\path[fill=fillColor] (189.78,551.28) rectangle (203.26,554.15);
-
-\path[fill=fillColor] (279.62,551.28) rectangle (293.10,570.72);
-
-\path[fill=fillColor] (324.54,551.28) rectangle (338.02,554.54);
-
-\path[fill=fillColor] ( 55.02,551.28) rectangle ( 68.50,582.79);
-
-\path[fill=fillColor] ( 99.94,551.28) rectangle (113.42,557.86);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,547.64) rectangle (371.71,627.77);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,462.01) rectangle (371.71,542.14);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,462.01) rectangle (371.71,542.14);
+\path[fill=fillColor] (139.23,551.82) rectangle (152.90,570.41);
+
+\path[fill=fillColor] (230.37,551.82) rectangle (244.04,554.16);
+
+\path[fill=fillColor] (184.80,551.82) rectangle (198.47,553.57);
+
+\path[fill=fillColor] (275.94,551.82) rectangle (289.61,559.41);
+
+\path[fill=fillColor] (321.51,551.82) rectangle (335.18,552.99);
+
+\path[fill=fillColor] ( 48.09,551.82) rectangle ( 61.76,595.24);
+
+\path[fill=fillColor] ( 93.66,551.82) rectangle (107.33,560.16);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,548.04) rectangle (369.36,631.27);
+\end{scope}
+\begin{scope}
+\path[clip] ( 41.25,459.31) rectangle (369.36,542.54);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 41.25,459.31) rectangle (369.36,542.54);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,475.33) --
-	(371.71,475.33);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,494.68) --
-	(371.71,494.68);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,514.04) --
-	(371.71,514.04);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,533.39) --
-	(371.71,533.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,465.65) --
-	(371.71,465.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,485.01) --
-	(371.71,485.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,504.36) --
-	(371.71,504.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,523.71) --
-	(371.71,523.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,462.01) --
-	( 75.24,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,462.01) --
-	(120.16,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,462.01) --
-	(165.08,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,462.01) --
-	(209.99,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,462.01) --
-	(254.91,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,462.01) --
-	(299.83,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,462.01) --
-	(344.75,542.14);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,473.51) --
+	(369.36,473.51);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,494.34) --
+	(369.36,494.34);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,515.17) --
+	(369.36,515.17);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,536.01) --
+	(369.36,536.01);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,463.09) --
+	(369.36,463.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,483.92) --
+	(369.36,483.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,504.76) --
+	(369.36,504.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,525.59) --
+	(369.36,525.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,459.31) --
+	( 68.60,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,459.31) --
+	(114.17,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,459.31) --
+	(159.74,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,459.31) --
+	(205.31,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,459.31) --
+	(250.88,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,459.31) --
+	(296.45,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,459.31) --
+	(342.02,542.54);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,465.65) rectangle (185.29,493.21);
-
-\path[fill=fillColor] (254.91,465.65) rectangle (275.13,465.96);
-
-\path[fill=fillColor] (216.73,465.65) rectangle (230.21,478.12);
-
-\path[fill=fillColor] (306.57,465.65) rectangle (320.05,466.04);
-
-\path[fill=fillColor] (351.49,465.65) rectangle (364.97,467.51);
-
-\path[fill=fillColor] ( 81.97,465.65) rectangle ( 95.45,499.87);
-
-\path[fill=fillColor] (126.89,465.65) rectangle (140.37,466.27);
+\path[fill=fillColor] (166.57,463.09) rectangle (180.24,492.76);
+
+\path[fill=fillColor] (250.88,463.09) rectangle (271.38,463.43);
+
+\path[fill=fillColor] (212.14,463.09) rectangle (225.81,476.76);
+
+\path[fill=fillColor] (303.28,463.09) rectangle (316.95,463.51);
+
+\path[fill=fillColor] (348.85,463.09) rectangle (362.52,465.09);
+
+\path[fill=fillColor] ( 75.43,463.09) rectangle ( 89.10,499.59);
+
+\path[fill=fillColor] (121.00,463.09) rectangle (134.67,463.76);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,465.65) rectangle (171.81,493.68);
-
-\path[fill=fillColor] (234.70,465.65) rectangle (254.91,465.96);
-
-\path[fill=fillColor] (203.26,465.65) rectangle (216.73,478.12);
-
-\path[fill=fillColor] (293.10,465.65) rectangle (306.57,466.04);
-
-\path[fill=fillColor] (338.02,465.65) rectangle (351.49,466.66);
-
-\path[fill=fillColor] ( 68.50,465.65) rectangle ( 81.97,500.26);
-
-\path[fill=fillColor] (113.42,465.65) rectangle (126.89,466.20);
+\path[fill=fillColor] (152.90,463.09) rectangle (166.57,489.84);
+
+\path[fill=fillColor] (230.37,463.09) rectangle (250.88,463.76);
+
+\path[fill=fillColor] (198.47,463.09) rectangle (212.14,476.92);
+
+\path[fill=fillColor] (289.61,463.09) rectangle (303.28,463.76);
+
+\path[fill=fillColor] (335.18,463.09) rectangle (348.85,464.09);
+
+\path[fill=fillColor] ( 61.76,463.09) rectangle ( 75.43,502.84);
+
+\path[fill=fillColor] (107.33,463.09) rectangle (121.00,463.84);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,465.65) rectangle (158.34,480.13);
-
-\path[fill=fillColor] (189.78,465.65) rectangle (203.26,478.66);
-
-\path[fill=fillColor] (279.62,465.65) rectangle (293.10,466.43);
-
-\path[fill=fillColor] (324.54,465.65) rectangle (338.02,489.81);
-
-\path[fill=fillColor] ( 55.02,465.65) rectangle ( 68.50,489.03);
-
-\path[fill=fillColor] ( 99.94,465.65) rectangle (113.42,467.28);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,462.01) rectangle (371.71,542.14);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,376.38) rectangle (371.71,456.51);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,376.38) rectangle (371.71,456.51);
+\path[fill=fillColor] (139.23,463.09) rectangle (152.90,496.84);
+
+\path[fill=fillColor] (184.80,463.09) rectangle (198.47,476.42);
+
+\path[fill=fillColor] (275.94,463.09) rectangle (289.61,463.26);
+
+\path[fill=fillColor] (321.51,463.09) rectangle (335.18,466.43);
+
+\path[fill=fillColor] ( 48.09,463.09) rectangle ( 61.76,495.26);
+
+\path[fill=fillColor] ( 93.66,463.09) rectangle (107.33,463.68);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,459.31) rectangle (369.36,542.54);
+\end{scope}
+\begin{scope}
+\path[clip] ( 41.25,370.58) rectangle (369.36,453.81);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 41.25,370.58) rectangle (369.36,453.81);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,389.70) --
-	(371.71,389.70);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,409.05) --
-	(371.71,409.05);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,428.41) --
-	(371.71,428.41);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,447.76) --
-	(371.71,447.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,380.02) --
-	(371.71,380.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,399.38) --
-	(371.71,399.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,418.73) --
-	(371.71,418.73);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,438.08) --
-	(371.71,438.08);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,376.38) --
-	( 75.24,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,376.38) --
-	(120.16,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,376.38) --
-	(165.08,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,376.38) --
-	(209.99,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,376.38) --
-	(254.91,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,376.38) --
-	(299.83,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,376.38) --
-	(344.75,456.51);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,384.78) --
+	(369.36,384.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,405.61) --
+	(369.36,405.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,426.44) --
+	(369.36,426.44);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,447.28) --
+	(369.36,447.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,374.36) --
+	(369.36,374.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,395.19) --
+	(369.36,395.19);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,416.03) --
+	(369.36,416.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,436.86) --
+	(369.36,436.86);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,370.58) --
+	( 68.60,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,370.58) --
+	(114.17,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,370.58) --
+	(159.74,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,370.58) --
+	(205.31,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,370.58) --
+	(250.88,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,370.58) --
+	(296.45,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,370.58) --
+	(342.02,453.81);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,380.02) rectangle (185.29,391.63);
-
-\path[fill=fillColor] (254.91,380.02) rectangle (275.13,380.49);
-
-\path[fill=fillColor] (216.73,380.02) rectangle (230.21,380.87);
-
-\path[fill=fillColor] (306.57,380.02) rectangle (320.05,405.72);
-
-\path[fill=fillColor] (351.49,380.02) rectangle (364.97,380.33);
-
-\path[fill=fillColor] ( 81.97,380.02) rectangle ( 95.45,397.83);
-
-\path[fill=fillColor] (126.89,380.02) rectangle (140.37,400.69);
+\path[fill=fillColor] (166.57,374.36) rectangle (180.24,386.86);
+
+\path[fill=fillColor] (257.71,374.36) rectangle (271.38,374.86);
+
+\path[fill=fillColor] (212.14,374.36) rectangle (225.81,375.28);
+
+\path[fill=fillColor] (303.28,374.36) rectangle (316.95,402.03);
+
+\path[fill=fillColor] (342.02,374.36) rectangle (362.52,374.69);
+
+\path[fill=fillColor] ( 75.43,374.36) rectangle ( 89.10,393.53);
+
+\path[fill=fillColor] (121.00,374.36) rectangle (134.67,396.61);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,380.02) rectangle (171.81,391.71);
-
-\path[fill=fillColor] (234.70,380.02) rectangle (254.91,380.56);
-
-\path[fill=fillColor] (203.26,380.02) rectangle (216.73,380.80);
-
-\path[fill=fillColor] (293.10,380.02) rectangle (306.57,404.79);
-
-\path[fill=fillColor] (338.02,380.02) rectangle (351.49,380.10);
-
-\path[fill=fillColor] ( 68.50,380.02) rectangle ( 81.97,398.45);
-
-\path[fill=fillColor] (113.42,380.02) rectangle (126.89,401.23);
+\path[fill=fillColor] (152.90,374.36) rectangle (166.57,386.19);
+
+\path[fill=fillColor] (244.04,374.36) rectangle (257.71,375.11);
+
+\path[fill=fillColor] (198.47,374.36) rectangle (212.14,375.28);
+
+\path[fill=fillColor] (289.61,374.36) rectangle (303.28,401.19);
+
+\path[fill=fillColor] (321.51,374.36) rectangle (342.02,374.86);
+
+\path[fill=fillColor] ( 61.76,374.36) rectangle ( 75.43,394.44);
+
+\path[fill=fillColor] (107.33,374.36) rectangle (121.00,396.69);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,380.02) rectangle (158.34,389.93);
-
-\path[fill=fillColor] (189.78,380.02) rectangle (203.26,382.27);
-
-\path[fill=fillColor] (279.62,380.02) rectangle (293.10,421.21);
-
-\path[fill=fillColor] (324.54,380.02) rectangle (338.02,384.28);
-
-\path[fill=fillColor] ( 55.02,380.02) rectangle ( 68.50,387.84);
-
-\path[fill=fillColor] ( 99.94,380.02) rectangle (113.42,392.10);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,376.38) rectangle (371.71,456.51);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,290.75) rectangle (371.71,370.88);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,290.75) rectangle (371.71,370.88);
+\path[fill=fillColor] (139.23,374.36) rectangle (152.90,388.03);
+
+\path[fill=fillColor] (230.37,374.36) rectangle (244.04,374.53);
+
+\path[fill=fillColor] (184.80,374.36) rectangle (198.47,375.19);
+
+\path[fill=fillColor] (275.94,374.36) rectangle (289.61,403.53);
+
+\path[fill=fillColor] ( 48.09,374.36) rectangle ( 61.76,391.69);
+
+\path[fill=fillColor] ( 93.66,374.36) rectangle (107.33,396.53);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,370.58) rectangle (369.36,453.81);
+\end{scope}
+\begin{scope}
+\path[clip] ( 41.25,281.85) rectangle (369.36,365.08);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 41.25,281.85) rectangle (369.36,365.08);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,304.07) --
-	(371.71,304.07);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,323.42) --
-	(371.71,323.42);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,342.78) --
-	(371.71,342.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,362.13) --
-	(371.71,362.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,294.39) --
-	(371.71,294.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,313.74) --
-	(371.71,313.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,333.10) --
-	(371.71,333.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,352.45) --
-	(371.71,352.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,290.75) --
-	( 75.24,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,290.75) --
-	(120.16,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,290.75) --
-	(165.08,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,290.75) --
-	(209.99,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,290.75) --
-	(254.91,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,290.75) --
-	(299.83,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,290.75) --
-	(344.75,370.88);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,296.05) --
+	(369.36,296.05);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,316.88) --
+	(369.36,316.88);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,337.71) --
+	(369.36,337.71);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,358.55) --
+	(369.36,358.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,285.63) --
+	(369.36,285.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,306.46) --
+	(369.36,306.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,327.30) --
+	(369.36,327.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,348.13) --
+	(369.36,348.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,281.85) --
+	( 68.60,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,281.85) --
+	(114.17,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,281.85) --
+	(159.74,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,281.85) --
+	(205.31,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,281.85) --
+	(250.88,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,281.85) --
+	(296.45,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,281.85) --
+	(342.02,365.08);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,294.39) rectangle (185.29,296.79);
-
-\path[fill=fillColor] (254.91,294.39) rectangle (275.13,294.39);
-
-\path[fill=fillColor] (216.73,294.39) rectangle (230.21,295.71);
-
-\path[fill=fillColor] (306.57,294.39) rectangle (320.05,298.88);
-
-\path[fill=fillColor] ( 81.97,294.39) rectangle ( 95.45,363.52);
+\path[fill=fillColor] (166.57,285.63) rectangle (180.24,288.21);
+
+\path[fill=fillColor] (250.88,285.63) rectangle (271.38,285.63);
+
+\path[fill=fillColor] (212.14,285.63) rectangle (225.81,287.05);
+
+\path[fill=fillColor] (303.28,285.63) rectangle (316.95,290.46);
+
+\path[fill=fillColor] ( 75.43,285.63) rectangle ( 89.10,360.05);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,294.39) rectangle (171.81,296.71);
-
-\path[fill=fillColor] (234.70,294.39) rectangle (254.91,294.47);
-
-\path[fill=fillColor] (203.26,294.39) rectangle (216.73,295.09);
-
-\path[fill=fillColor] (293.10,294.39) rectangle (306.57,295.86);
-
-\path[fill=fillColor] ( 68.50,294.39) rectangle ( 81.97,367.24);
+\path[fill=fillColor] (152.90,285.63) rectangle (166.57,287.88);
+
+\path[fill=fillColor] (230.37,285.63) rectangle (250.88,285.71);
+
+\path[fill=fillColor] (198.47,285.63) rectangle (212.14,287.13);
+
+\path[fill=fillColor] (289.61,285.63) rectangle (303.28,291.13);
+
+\path[fill=fillColor] ( 61.76,285.63) rectangle ( 75.43,359.63);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,294.39) rectangle (158.34,297.41);
-
-\path[fill=fillColor] (189.78,294.39) rectangle (203.26,300.20);
-
-\path[fill=fillColor] (279.62,294.39) rectangle (293.10,320.63);
-
-\path[fill=fillColor] ( 55.02,294.39) rectangle ( 68.50,336.74);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,290.75) rectangle (371.71,370.88);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,205.12) rectangle (371.71,285.25);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,205.12) rectangle (371.71,285.25);
+\path[fill=fillColor] (139.23,285.63) rectangle (152.90,289.30);
+
+\path[fill=fillColor] (184.80,285.63) rectangle (198.47,286.88);
+
+\path[fill=fillColor] (275.94,285.63) rectangle (289.61,288.38);
+
+\path[fill=fillColor] ( 48.09,285.63) rectangle ( 61.76,361.30);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,281.85) rectangle (369.36,365.08);
+\end{scope}
+\begin{scope}
+\path[clip] ( 41.25,193.12) rectangle (369.36,276.35);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 41.25,193.12) rectangle (369.36,276.35);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,218.44) --
-	(371.71,218.44);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,237.79) --
-	(371.71,237.79);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,257.14) --
-	(371.71,257.14);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,276.50) --
-	(371.71,276.50);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,208.76) --
-	(371.71,208.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,228.11) --
-	(371.71,228.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,247.47) --
-	(371.71,247.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,266.82) --
-	(371.71,266.82);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,205.12) --
-	( 75.24,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,205.12) --
-	(120.16,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,205.12) --
-	(165.08,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,205.12) --
-	(209.99,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,205.12) --
-	(254.91,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,205.12) --
-	(299.83,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,205.12) --
-	(344.75,285.25);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,207.32) --
+	(369.36,207.32);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,228.15) --
+	(369.36,228.15);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,248.98) --
+	(369.36,248.98);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,269.81) --
+	(369.36,269.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,196.90) --
+	(369.36,196.90);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,217.73) --
+	(369.36,217.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,238.57) --
+	(369.36,238.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,259.40) --
+	(369.36,259.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,193.12) --
+	( 68.60,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,193.12) --
+	(114.17,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,193.12) --
+	(159.74,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,193.12) --
+	(205.31,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,193.12) --
+	(250.88,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,193.12) --
+	(296.45,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,193.12) --
+	(342.02,276.35);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,208.76) rectangle (185.29,221.77);
-
-\path[fill=fillColor] (261.65,208.76) rectangle (275.13,209.92);
-
-\path[fill=fillColor] (216.73,208.76) rectangle (230.21,212.86);
-
-\path[fill=fillColor] (306.57,208.76) rectangle (320.05,216.97);
-
-\path[fill=fillColor] (351.49,208.76) rectangle (364.97,210.62);
-
-\path[fill=fillColor] ( 81.97,208.76) rectangle ( 95.45,246.00);
-
-\path[fill=fillColor] (126.89,208.76) rectangle (140.37,223.70);
+\path[fill=fillColor] (166.57,196.90) rectangle (180.24,210.90);
+
+\path[fill=fillColor] (257.71,196.90) rectangle (271.38,198.15);
+
+\path[fill=fillColor] (212.14,196.90) rectangle (225.81,201.32);
+
+\path[fill=fillColor] (303.28,196.90) rectangle (316.95,205.73);
+
+\path[fill=fillColor] (348.85,196.90) rectangle (362.52,198.90);
+
+\path[fill=fillColor] ( 75.43,196.90) rectangle ( 89.10,236.90);
+
+\path[fill=fillColor] (121.00,196.90) rectangle (134.67,212.98);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,208.76) rectangle (171.81,221.77);
-
-\path[fill=fillColor] (248.18,208.76) rectangle (261.65,209.92);
-
-\path[fill=fillColor] (203.26,208.76) rectangle (216.73,212.24);
-
-\path[fill=fillColor] (293.10,208.76) rectangle (306.57,214.10);
-
-\path[fill=fillColor] (338.02,208.76) rectangle (351.49,209.69);
-
-\path[fill=fillColor] ( 68.50,208.76) rectangle ( 81.97,248.47);
-
-\path[fill=fillColor] (113.42,208.76) rectangle (126.89,225.48);
+\path[fill=fillColor] (152.90,196.90) rectangle (166.57,209.82);
+
+\path[fill=fillColor] (244.04,196.90) rectangle (257.71,198.32);
+
+\path[fill=fillColor] (198.47,196.90) rectangle (212.14,201.23);
+
+\path[fill=fillColor] (289.61,196.90) rectangle (303.28,206.07);
+
+\path[fill=fillColor] (335.18,196.90) rectangle (348.85,198.98);
+
+\path[fill=fillColor] ( 61.76,196.90) rectangle ( 75.43,236.90);
+
+\path[fill=fillColor] (107.33,196.90) rectangle (121.00,213.73);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,208.76) rectangle (158.34,220.53);
-
-\path[fill=fillColor] (234.70,208.76) rectangle (248.18,210.00);
-
-\path[fill=fillColor] (189.78,208.76) rectangle (203.26,215.50);
-
-\path[fill=fillColor] (279.62,208.76) rectangle (293.10,228.97);
-
-\path[fill=fillColor] (324.54,208.76) rectangle (338.02,216.42);
-
-\path[fill=fillColor] ( 55.02,208.76) rectangle ( 68.50,233.92);
-
-\path[fill=fillColor] ( 99.94,208.76) rectangle (113.42,217.12);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,205.12) rectangle (371.71,285.25);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,119.49) rectangle (371.71,199.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,119.49) rectangle (371.71,199.62);
+\path[fill=fillColor] (139.23,196.90) rectangle (152.90,212.73);
+
+\path[fill=fillColor] (230.37,196.90) rectangle (244.04,198.07);
+
+\path[fill=fillColor] (184.80,196.90) rectangle (198.47,201.48);
+
+\path[fill=fillColor] (275.94,196.90) rectangle (289.61,204.98);
+
+\path[fill=fillColor] (321.51,196.90) rectangle (335.18,198.82);
+
+\path[fill=fillColor] ( 48.09,196.90) rectangle ( 61.76,236.65);
+
+\path[fill=fillColor] ( 93.66,196.90) rectangle (107.33,211.82);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,193.12) rectangle (369.36,276.35);
+\end{scope}
+\begin{scope}
+\path[clip] ( 41.25,104.39) rectangle (369.36,187.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 41.25,104.39) rectangle (369.36,187.62);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,132.81) --
-	(371.71,132.81);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,152.16) --
-	(371.71,152.16);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,171.51) --
-	(371.71,171.51);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,190.87) --
-	(371.71,190.87);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,123.13) --
-	(371.71,123.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,142.48) --
-	(371.71,142.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,161.84) --
-	(371.71,161.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,181.19) --
-	(371.71,181.19);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,119.49) --
-	( 75.24,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,119.49) --
-	(120.16,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,119.49) --
-	(165.08,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,119.49) --
-	(209.99,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,119.49) --
-	(254.91,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,119.49) --
-	(299.83,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,119.49) --
-	(344.75,199.62);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,118.59) --
+	(369.36,118.59);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,139.42) --
+	(369.36,139.42);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,160.25) --
+	(369.36,160.25);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,181.08) --
+	(369.36,181.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,108.17) --
+	(369.36,108.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,129.00) --
+	(369.36,129.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,149.84) --
+	(369.36,149.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,170.67) --
+	(369.36,170.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,104.39) --
+	( 68.60,187.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,104.39) --
+	(114.17,187.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,104.39) --
+	(159.74,187.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,104.39) --
+	(205.31,187.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,104.39) --
+	(250.88,187.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,104.39) --
+	(296.45,187.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,104.39) --
+	(342.02,187.62);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,123.13) rectangle (185.29,132.03);
-
-\path[fill=fillColor] (216.73,123.13) rectangle (230.21,124.99);
-
-\path[fill=fillColor] (306.57,123.13) rectangle (320.05,140.08);
-
-\path[fill=fillColor] (344.75,123.13) rectangle (364.97,123.21);
-
-\path[fill=fillColor] ( 81.97,123.13) rectangle ( 95.45,149.84);
-
-\path[fill=fillColor] (126.89,123.13) rectangle (140.37,146.12);
+\path[fill=fillColor] (166.57,108.17) rectangle (180.24,117.75);
+
+\path[fill=fillColor] (212.14,108.17) rectangle (225.81,110.17);
+
+\path[fill=fillColor] (303.28,108.17) rectangle (316.95,126.42);
+
+\path[fill=fillColor] (342.02,108.17) rectangle (362.52,108.25);
+
+\path[fill=fillColor] ( 75.43,108.17) rectangle ( 89.10,136.92);
+
+\path[fill=fillColor] (121.00,108.17) rectangle (134.67,132.92);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,123.13) rectangle (171.81,129.86);
-
-\path[fill=fillColor] (203.26,123.13) rectangle (216.73,124.45);
-
-\path[fill=fillColor] (293.10,123.13) rectangle (306.57,137.53);
-
-\path[fill=fillColor] ( 68.50,123.13) rectangle ( 81.97,152.62);
-
-\path[fill=fillColor] (113.42,123.13) rectangle (126.89,148.68);
+\path[fill=fillColor] (152.90,108.17) rectangle (166.57,117.09);
+
+\path[fill=fillColor] (198.47,108.17) rectangle (212.14,109.84);
+
+\path[fill=fillColor] (289.61,108.17) rectangle (303.28,128.50);
+
+\path[fill=fillColor] (321.51,108.17) rectangle (342.02,108.25);
+
+\path[fill=fillColor] ( 61.76,108.17) rectangle ( 75.43,135.50);
+
+\path[fill=fillColor] (107.33,108.17) rectangle (121.00,133.17);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,123.13) rectangle (158.34,137.61);
-
-\path[fill=fillColor] (189.78,123.13) rectangle (203.26,126.38);
-
-\path[fill=fillColor] (279.62,123.13) rectangle (293.10,146.59);
-
-\path[fill=fillColor] (324.54,123.13) rectangle (344.75,123.28);
-
-\path[fill=fillColor] ( 55.02,123.13) rectangle ( 68.50,142.72);
-
-\path[fill=fillColor] ( 99.94,123.13) rectangle (113.42,139.62);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,119.49) rectangle (371.71,199.62);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,547.64) rectangle (717.20,627.77);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (393.78,547.64) rectangle (717.20,627.77);
+\path[fill=fillColor] (139.23,108.17) rectangle (152.90,118.42);
+
+\path[fill=fillColor] (184.80,108.17) rectangle (198.47,110.42);
+
+\path[fill=fillColor] (275.94,108.17) rectangle (289.61,124.25);
+
+\path[fill=fillColor] ( 48.09,108.17) rectangle ( 61.76,138.42);
+
+\path[fill=fillColor] ( 93.66,108.17) rectangle (107.33,132.67);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,104.39) rectangle (369.36,187.62);
+\end{scope}
+\begin{scope}
+\path[clip] (389.10,548.04) rectangle (717.20,631.27);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (389.10,548.04) rectangle (717.20,631.27);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,560.96) --
-	(717.20,560.96);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,580.31) --
-	(717.20,580.31);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,599.67) --
-	(717.20,599.67);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,619.02) --
-	(717.20,619.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,551.28) --
-	(717.20,551.28);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,570.64) --
-	(717.20,570.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,589.99) --
-	(717.20,589.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,609.34) --
-	(717.20,609.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,547.64) --
-	(420.73,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,547.64) --
-	(465.65,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,547.64) --
-	(510.57,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,547.64) --
-	(555.49,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,547.64) --
-	(600.41,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,547.64) --
-	(645.33,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,547.64) --
-	(690.25,627.77);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,562.24) --
+	(717.20,562.24);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,583.07) --
+	(717.20,583.07);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,603.90) --
+	(717.20,603.90);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,624.74) --
+	(717.20,624.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,551.82) --
+	(717.20,551.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,572.66) --
+	(717.20,572.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,593.49) --
+	(717.20,593.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,614.32) --
+	(717.20,614.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,548.04) --
+	(416.44,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,548.04) --
+	(462.01,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,548.04) --
+	(507.58,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,548.04) --
+	(553.15,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,548.04) --
+	(598.72,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,548.04) --
+	(644.29,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,548.04) --
+	(689.86,631.27);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (517.31,551.28) rectangle (530.78,579.62);
-
-\path[fill=fillColor] (607.15,551.28) rectangle (620.62,552.60);
-
-\path[fill=fillColor] (562.23,551.28) rectangle (575.70,552.68);
-
-\path[fill=fillColor] (696.99,551.28) rectangle (710.46,558.17);
-
-\path[fill=fillColor] (427.47,551.28) rectangle (440.94,581.71);
-
-\path[fill=fillColor] (472.39,551.28) rectangle (485.86,560.26);
+\path[fill=fillColor] (514.41,551.82) rectangle (528.09,582.32);
+
+\path[fill=fillColor] (605.55,551.82) rectangle (619.22,553.24);
+
+\path[fill=fillColor] (559.98,551.82) rectangle (573.65,553.32);
+
+\path[fill=fillColor] (696.69,551.82) rectangle (710.36,559.24);
+
+\path[fill=fillColor] (423.27,551.82) rectangle (436.95,584.57);
+
+\path[fill=fillColor] (468.84,551.82) rectangle (482.52,561.49);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (503.83,551.28) rectangle (517.31,579.85);
-
-\path[fill=fillColor] (593.67,551.28) rectangle (607.15,552.60);
-
-\path[fill=fillColor] (548.75,551.28) rectangle (562.23,551.98);
-
-\path[fill=fillColor] (683.51,551.28) rectangle (696.99,556.16);
-
-\path[fill=fillColor] (413.99,551.28) rectangle (427.47,583.33);
-
-\path[fill=fillColor] (458.91,551.28) rectangle (472.39,561.12);
+\path[fill=fillColor] (500.74,551.82) rectangle (514.41,582.24);
+
+\path[fill=fillColor] (591.88,551.82) rectangle (605.55,553.99);
+
+\path[fill=fillColor] (546.31,551.82) rectangle (559.98,553.24);
+
+\path[fill=fillColor] (683.02,551.82) rectangle (696.69,560.32);
+
+\path[fill=fillColor] (409.60,551.82) rectangle (423.27,581.74);
+
+\path[fill=fillColor] (455.17,551.82) rectangle (468.84,562.74);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (490.36,551.28) rectangle (503.83,578.77);
-
-\path[fill=fillColor] (580.19,551.28) rectangle (593.67,552.37);
-
-\path[fill=fillColor] (535.27,551.28) rectangle (548.75,555.39);
-
-\path[fill=fillColor] (670.03,551.28) rectangle (683.51,565.84);
-
-\path[fill=fillColor] (400.52,551.28) rectangle (413.99,575.67);
-
-\path[fill=fillColor] (445.44,551.28) rectangle (458.91,557.17);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,547.64) rectangle (717.20,627.77);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,462.01) rectangle (717.20,542.14);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (393.78,462.01) rectangle (717.20,542.14);
+\path[fill=fillColor] (487.07,551.82) rectangle (500.74,582.40);
+
+\path[fill=fillColor] (578.21,551.82) rectangle (591.88,552.74);
+
+\path[fill=fillColor] (532.64,551.82) rectangle (546.31,553.41);
+
+\path[fill=fillColor] (669.35,551.82) rectangle (683.02,558.66);
+
+\path[fill=fillColor] (395.93,551.82) rectangle (409.60,586.32);
+
+\path[fill=fillColor] (441.50,551.82) rectangle (455.17,560.82);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.10,548.04) rectangle (717.20,631.27);
+\end{scope}
+\begin{scope}
+\path[clip] (389.10,459.31) rectangle (717.20,542.54);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (389.10,459.31) rectangle (717.20,542.54);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,475.33) --
-	(717.20,475.33);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,494.68) --
-	(717.20,494.68);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,514.04) --
-	(717.20,514.04);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,533.39) --
-	(717.20,533.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,465.65) --
-	(717.20,465.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,485.01) --
-	(717.20,485.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,504.36) --
-	(717.20,504.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,523.71) --
-	(717.20,523.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,462.01) --
-	(420.73,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,462.01) --
-	(465.65,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,462.01) --
-	(510.57,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,462.01) --
-	(555.49,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,462.01) --
-	(600.41,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,462.01) --
-	(645.33,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,462.01) --
-	(690.25,542.14);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,473.51) --
+	(717.20,473.51);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,494.34) --
+	(717.20,494.34);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,515.17) --
+	(717.20,515.17);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,536.01) --
+	(717.20,536.01);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,463.09) --
+	(717.20,463.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,483.92) --
+	(717.20,483.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,504.76) --
+	(717.20,504.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,525.59) --
+	(717.20,525.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,459.31) --
+	(416.44,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,459.31) --
+	(462.01,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,459.31) --
+	(507.58,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,459.31) --
+	(553.15,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,459.31) --
+	(598.72,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,459.31) --
+	(644.29,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,459.31) --
+	(689.86,542.54);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (517.31,465.65) rectangle (530.78,471.85);
-
-\path[fill=fillColor] (562.23,465.65) rectangle (575.70,471.85);
-
-\path[fill=fillColor] (652.07,465.65) rectangle (665.54,468.67);
-
-\path[fill=fillColor] (696.99,465.65) rectangle (710.46,468.90);
-
-\path[fill=fillColor] (427.47,465.65) rectangle (440.94,510.55);
-
-\path[fill=fillColor] (472.39,465.65) rectangle (485.86,479.59);
+\path[fill=fillColor] (514.41,463.09) rectangle (528.09,469.76);
+
+\path[fill=fillColor] (559.98,463.09) rectangle (573.65,469.76);
+
+\path[fill=fillColor] (651.12,463.09) rectangle (664.79,466.34);
+
+\path[fill=fillColor] (696.69,463.09) rectangle (710.36,466.59);
+
+\path[fill=fillColor] (423.27,463.09) rectangle (436.95,511.42);
+
+\path[fill=fillColor] (468.84,463.09) rectangle (482.52,478.09);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (503.83,465.65) rectangle (517.31,470.53);
-
-\path[fill=fillColor] (548.75,465.65) rectangle (562.23,469.60);
-
-\path[fill=fillColor] (638.59,465.65) rectangle (652.07,467.67);
-
-\path[fill=fillColor] (683.51,465.65) rectangle (696.99,466.12);
-
-\path[fill=fillColor] (413.99,465.65) rectangle (427.47,515.04);
-
-\path[fill=fillColor] (458.91,465.65) rectangle (472.39,482.37);
+\path[fill=fillColor] (500.74,463.09) rectangle (514.41,468.26);
+
+\path[fill=fillColor] (546.31,463.09) rectangle (559.98,469.18);
+
+\path[fill=fillColor] (637.45,463.09) rectangle (651.12,466.93);
+
+\path[fill=fillColor] (683.02,463.09) rectangle (696.69,466.76);
+
+\path[fill=fillColor] (409.60,463.09) rectangle (423.27,512.17);
+
+\path[fill=fillColor] (455.17,463.09) rectangle (468.84,478.59);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (490.36,465.65) rectangle (503.83,476.41);
-
-\path[fill=fillColor] (535.27,465.65) rectangle (548.75,479.43);
-
-\path[fill=fillColor] (625.11,465.65) rectangle (638.59,472.23);
-
-\path[fill=fillColor] (670.03,465.65) rectangle (683.51,478.50);
-
-\path[fill=fillColor] (400.52,465.65) rectangle (413.99,494.76);
-
-\path[fill=fillColor] (445.44,465.65) rectangle (458.91,469.99);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,462.01) rectangle (717.20,542.14);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,376.38) rectangle (717.20,456.51);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (393.78,376.38) rectangle (717.20,456.51);
+\path[fill=fillColor] (487.07,463.09) rectangle (500.74,472.18);
+
+\path[fill=fillColor] (532.64,463.09) rectangle (546.31,470.59);
+
+\path[fill=fillColor] (623.78,463.09) rectangle (637.45,465.43);
+
+\path[fill=fillColor] (669.35,463.09) rectangle (683.02,466.26);
+
+\path[fill=fillColor] (395.93,463.09) rectangle (409.60,510.09);
+
+\path[fill=fillColor] (441.50,463.09) rectangle (455.17,477.34);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.10,459.31) rectangle (717.20,542.54);
+\end{scope}
+\begin{scope}
+\path[clip] (389.10,370.58) rectangle (717.20,453.81);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (389.10,370.58) rectangle (717.20,453.81);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,389.70) --
-	(717.20,389.70);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,409.05) --
-	(717.20,409.05);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,428.41) --
-	(717.20,428.41);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,447.76) --
-	(717.20,447.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,380.02) --
-	(717.20,380.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,399.38) --
-	(717.20,399.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,418.73) --
-	(717.20,418.73);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,438.08) --
-	(717.20,438.08);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,376.38) --
-	(420.73,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,376.38) --
-	(465.65,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,376.38) --
-	(510.57,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,376.38) --
-	(555.49,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,376.38) --
-	(600.41,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,376.38) --
-	(645.33,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,376.38) --
-	(690.25,456.51);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,384.78) --
+	(717.20,384.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,405.61) --
+	(717.20,405.61);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,426.44) --
+	(717.20,426.44);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,447.28) --
+	(717.20,447.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,374.36) --
+	(717.20,374.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,395.19) --
+	(717.20,395.19);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,416.03) --
+	(717.20,416.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,436.86) --
+	(717.20,436.86);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,370.58) --
+	(416.44,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,370.58) --
+	(462.01,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,370.58) --
+	(507.58,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,370.58) --
+	(553.15,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,370.58) --
+	(598.72,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,370.58) --
+	(644.29,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,370.58) --
+	(689.86,453.81);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (517.31,380.02) rectangle (530.78,386.53);
-
-\path[fill=fillColor] (607.15,380.02) rectangle (620.62,380.41);
-
-\path[fill=fillColor] (562.23,380.02) rectangle (575.70,383.66);
-
-\path[fill=fillColor] (652.07,380.02) rectangle (665.54,386.91);
-
-\path[fill=fillColor] (696.99,380.02) rectangle (710.46,380.87);
-
-\path[fill=fillColor] (427.47,380.02) rectangle (440.94,414.08);
-
-\path[fill=fillColor] (472.39,380.02) rectangle (485.86,405.18);
+\path[fill=fillColor] (514.41,374.36) rectangle (528.09,381.36);
+
+\path[fill=fillColor] (605.55,374.36) rectangle (619.22,374.78);
+
+\path[fill=fillColor] (559.98,374.36) rectangle (573.65,378.28);
+
+\path[fill=fillColor] (651.12,374.36) rectangle (664.79,381.78);
+
+\path[fill=fillColor] (696.69,374.36) rectangle (710.36,375.28);
+
+\path[fill=fillColor] (423.27,374.36) rectangle (436.95,411.03);
+
+\path[fill=fillColor] (468.84,374.36) rectangle (482.52,401.44);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (503.83,380.02) rectangle (517.31,385.67);
-
-\path[fill=fillColor] (593.67,380.02) rectangle (607.15,380.41);
-
-\path[fill=fillColor] (548.75,380.02) rectangle (562.23,382.96);
-
-\path[fill=fillColor] (638.59,380.02) rectangle (652.07,382.42);
-
-\path[fill=fillColor] (683.51,380.02) rectangle (696.99,380.64);
-
-\path[fill=fillColor] (413.99,380.02) rectangle (427.47,416.87);
-
-\path[fill=fillColor] (458.91,380.02) rectangle (472.39,408.59);
+\path[fill=fillColor] (500.74,374.36) rectangle (514.41,380.19);
+
+\path[fill=fillColor] (591.88,374.36) rectangle (605.55,374.61);
+
+\path[fill=fillColor] (546.31,374.36) rectangle (559.98,377.94);
+
+\path[fill=fillColor] (637.45,374.36) rectangle (651.12,382.11);
+
+\path[fill=fillColor] (683.02,374.36) rectangle (696.69,375.44);
+
+\path[fill=fillColor] (409.60,374.36) rectangle (423.27,410.28);
+
+\path[fill=fillColor] (455.17,374.36) rectangle (468.84,403.36);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (490.36,380.02) rectangle (503.83,389.39);
-
-\path[fill=fillColor] (580.19,380.02) rectangle (593.67,380.41);
-
-\path[fill=fillColor] (535.27,380.02) rectangle (548.75,385.98);
-
-\path[fill=fillColor] (625.11,380.02) rectangle (638.59,402.78);
-
-\path[fill=fillColor] (670.03,380.02) rectangle (683.51,381.73);
-
-\path[fill=fillColor] (400.52,380.02) rectangle (413.99,404.10);
-
-\path[fill=fillColor] (445.44,380.02) rectangle (458.91,393.26);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,376.38) rectangle (717.20,456.51);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,290.75) rectangle (717.20,370.88);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (393.78,290.75) rectangle (717.20,370.88);
+\path[fill=fillColor] (487.07,374.36) rectangle (500.74,383.44);
+
+\path[fill=fillColor] (578.21,374.36) rectangle (591.88,375.11);
+
+\path[fill=fillColor] (532.64,374.36) rectangle (546.31,378.86);
+
+\path[fill=fillColor] (623.78,374.36) rectangle (637.45,381.11);
+
+\path[fill=fillColor] (669.35,374.36) rectangle (683.02,375.11);
+
+\path[fill=fillColor] (395.93,374.36) rectangle (409.60,412.36);
+
+\path[fill=fillColor] (441.50,374.36) rectangle (455.17,398.03);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.10,370.58) rectangle (717.20,453.81);
+\end{scope}
+\begin{scope}
+\path[clip] (389.10,281.85) rectangle (717.20,365.08);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (389.10,281.85) rectangle (717.20,365.08);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,304.07) --
-	(717.20,304.07);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,323.42) --
-	(717.20,323.42);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,342.78) --
-	(717.20,342.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,362.13) --
-	(717.20,362.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,294.39) --
-	(717.20,294.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,313.74) --
-	(717.20,313.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,333.10) --
-	(717.20,333.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,352.45) --
-	(717.20,352.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,290.75) --
-	(420.73,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,290.75) --
-	(465.65,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,290.75) --
-	(510.57,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,290.75) --
-	(555.49,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,290.75) --
-	(600.41,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,290.75) --
-	(645.33,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,290.75) --
-	(690.25,370.88);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,296.05) --
+	(717.20,296.05);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,316.88) --
+	(717.20,316.88);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,337.71) --
+	(717.20,337.71);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,358.55) --
+	(717.20,358.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,285.63) --
+	(717.20,285.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,306.46) --
+	(717.20,306.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,327.30) --
+	(717.20,327.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,348.13) --
+	(717.20,348.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,281.85) --
+	(416.44,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,281.85) --
+	(462.01,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,281.85) --
+	(507.58,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,281.85) --
+	(553.15,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,281.85) --
+	(598.72,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,281.85) --
+	(644.29,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,281.85) --
+	(689.86,365.08);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (517.31,294.39) rectangle (530.78,301.75);
-
-\path[fill=fillColor] (607.15,294.39) rectangle (620.62,298.73);
-
-\path[fill=fillColor] (562.23,294.39) rectangle (575.70,299.97);
-
-\path[fill=fillColor] (652.07,294.39) rectangle (665.54,302.29);
-
-\path[fill=fillColor] (690.25,294.39) rectangle (710.46,294.47);
-
-\path[fill=fillColor] (427.47,294.39) rectangle (440.94,321.49);
-
-\path[fill=fillColor] (472.39,294.39) rectangle (485.86,319.47);
+\path[fill=fillColor] (514.41,285.63) rectangle (528.09,293.55);
+
+\path[fill=fillColor] (605.55,285.63) rectangle (619.22,290.30);
+
+\path[fill=fillColor] (559.98,285.63) rectangle (573.65,291.63);
+
+\path[fill=fillColor] (651.12,285.63) rectangle (664.79,294.13);
+
+\path[fill=fillColor] (696.69,285.63) rectangle (710.36,285.71);
+
+\path[fill=fillColor] (423.27,285.63) rectangle (436.95,314.80);
+
+\path[fill=fillColor] (468.84,285.63) rectangle (482.52,312.63);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (503.83,294.39) rectangle (517.31,301.98);
-
-\path[fill=fillColor] (593.67,294.39) rectangle (607.15,298.26);
-
-\path[fill=fillColor] (548.75,294.39) rectangle (562.23,299.81);
-
-\path[fill=fillColor] (638.59,294.39) rectangle (652.07,297.10);
-
-\path[fill=fillColor] (413.99,294.39) rectangle (427.47,324.04);
-
-\path[fill=fillColor] (458.91,294.39) rectangle (472.39,322.65);
+\path[fill=fillColor] (500.74,285.63) rectangle (514.41,293.05);
+
+\path[fill=fillColor] (591.88,285.63) rectangle (605.55,290.80);
+
+\path[fill=fillColor] (546.31,285.63) rectangle (559.98,291.55);
+
+\path[fill=fillColor] (637.45,285.63) rectangle (651.12,294.63);
+
+\path[fill=fillColor] (683.02,285.63) rectangle (696.69,285.71);
+
+\path[fill=fillColor] (409.60,285.63) rectangle (423.27,314.05);
+
+\path[fill=fillColor] (455.17,285.63) rectangle (468.84,312.96);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (490.36,294.39) rectangle (503.83,300.97);
-
-\path[fill=fillColor] (580.19,294.39) rectangle (593.67,300.20);
-
-\path[fill=fillColor] (535.27,294.39) rectangle (548.75,300.43);
-
-\path[fill=fillColor] (625.11,294.39) rectangle (638.59,319.16);
-
-\path[fill=fillColor] (670.03,294.39) rectangle (690.25,294.86);
-
-\path[fill=fillColor] (400.52,294.39) rectangle (413.99,313.36);
-
-\path[fill=fillColor] (445.44,294.39) rectangle (458.91,309.18);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,290.75) rectangle (717.20,370.88);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,205.12) rectangle (717.20,285.25);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (393.78,205.12) rectangle (717.20,285.25);
+\path[fill=fillColor] (487.07,285.63) rectangle (500.74,293.96);
+
+\path[fill=fillColor] (578.21,285.63) rectangle (591.88,289.71);
+
+\path[fill=fillColor] (532.64,285.63) rectangle (546.31,291.71);
+
+\path[fill=fillColor] (623.78,285.63) rectangle (637.45,293.63);
+
+\path[fill=fillColor] (669.35,285.63) rectangle (683.02,285.71);
+
+\path[fill=fillColor] (395.93,285.63) rectangle (409.60,315.63);
+
+\path[fill=fillColor] (441.50,285.63) rectangle (455.17,312.30);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.10,281.85) rectangle (717.20,365.08);
+\end{scope}
+\begin{scope}
+\path[clip] (389.10,193.12) rectangle (717.20,276.35);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (389.10,193.12) rectangle (717.20,276.35);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,218.44) --
-	(717.20,218.44);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,237.79) --
-	(717.20,237.79);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,257.14) --
-	(717.20,257.14);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,276.50) --
-	(717.20,276.50);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,208.76) --
-	(717.20,208.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,228.11) --
-	(717.20,228.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,247.47) --
-	(717.20,247.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,266.82) --
-	(717.20,266.82);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,205.12) --
-	(420.73,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,205.12) --
-	(465.65,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,205.12) --
-	(510.57,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,205.12) --
-	(555.49,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,205.12) --
-	(600.41,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,205.12) --
-	(645.33,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,205.12) --
-	(690.25,285.25);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,207.32) --
+	(717.20,207.32);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,228.15) --
+	(717.20,228.15);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,248.98) --
+	(717.20,248.98);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,269.81) --
+	(717.20,269.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,196.90) --
+	(717.20,196.90);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,217.73) --
+	(717.20,217.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,238.57) --
+	(717.20,238.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,259.40) --
+	(717.20,259.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,193.12) --
+	(416.44,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,193.12) --
+	(462.01,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,193.12) --
+	(507.58,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,193.12) --
+	(553.15,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,193.12) --
+	(598.72,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,193.12) --
+	(644.29,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,193.12) --
+	(689.86,276.35);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (517.31,208.76) rectangle (530.78,230.51);
-
-\path[fill=fillColor] (607.15,208.76) rectangle (620.62,212.55);
-
-\path[fill=fillColor] (562.23,208.76) rectangle (575.70,210.46);
-
-\path[fill=fillColor] (652.07,208.76) rectangle (665.54,221.61);
-
-\path[fill=fillColor] (427.47,208.76) rectangle (440.94,236.63);
-
-\path[fill=fillColor] (472.39,208.76) rectangle (485.86,218.28);
+\path[fill=fillColor] (514.41,196.90) rectangle (528.09,220.32);
+
+\path[fill=fillColor] (605.55,196.90) rectangle (619.22,200.98);
+
+\path[fill=fillColor] (559.98,196.90) rectangle (573.65,198.73);
+
+\path[fill=fillColor] (651.12,196.90) rectangle (664.79,210.73);
+
+\path[fill=fillColor] (423.27,196.90) rectangle (436.95,226.90);
+
+\path[fill=fillColor] (468.84,196.90) rectangle (482.52,207.15);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (503.83,208.76) rectangle (517.31,221.53);
-
-\path[fill=fillColor] (593.67,208.76) rectangle (607.15,211.93);
-
-\path[fill=fillColor] (548.75,208.76) rectangle (562.23,210.31);
-
-\path[fill=fillColor] (638.59,208.76) rectangle (652.07,213.25);
-
-\path[fill=fillColor] (413.99,208.76) rectangle (427.47,245.22);
-
-\path[fill=fillColor] (458.91,208.76) rectangle (472.39,227.65);
+\path[fill=fillColor] (500.74,196.90) rectangle (514.41,219.65);
+
+\path[fill=fillColor] (591.88,196.90) rectangle (605.55,200.82);
+
+\path[fill=fillColor] (546.31,196.90) rectangle (559.98,198.90);
+
+\path[fill=fillColor] (637.45,196.90) rectangle (651.12,209.65);
+
+\path[fill=fillColor] (409.60,196.90) rectangle (423.27,227.40);
+
+\path[fill=fillColor] (455.17,196.90) rectangle (468.84,208.23);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (490.36,208.76) rectangle (503.83,234.38);
-
-\path[fill=fillColor] (580.19,208.76) rectangle (593.67,212.86);
-
-\path[fill=fillColor] (535.27,208.76) rectangle (548.75,210.46);
-
-\path[fill=fillColor] (625.11,208.76) rectangle (638.59,225.25);
-
-\path[fill=fillColor] (400.52,208.76) rectangle (413.99,232.84);
-
-\path[fill=fillColor] (445.44,208.76) rectangle (458.91,214.10);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,205.12) rectangle (717.20,285.25);
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,547.64) rectangle (393.78,627.77);
+\path[fill=fillColor] (487.07,196.90) rectangle (500.74,220.90);
+
+\path[fill=fillColor] (578.21,196.90) rectangle (591.88,201.15);
+
+\path[fill=fillColor] (532.64,196.90) rectangle (546.31,198.48);
+
+\path[fill=fillColor] (623.78,196.90) rectangle (637.45,211.82);
+
+\path[fill=fillColor] (395.93,196.90) rectangle (409.60,226.40);
+
+\path[fill=fillColor] (441.50,196.90) rectangle (455.17,205.98);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.10,193.12) rectangle (717.20,276.35);
+\end{scope}
+\begin{scope}
+\path[clip] (374.86,548.04) rectangle (389.10,631.27);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,547.64) rectangle (393.78,627.77);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (374.86,548.04) rectangle (389.10,631.27);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,587.71) {Colombia};
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,462.01) rectangle (393.78,542.14);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (384.10,589.65) {Colombia};
+\end{scope}
+\begin{scope}
+\path[clip] (374.86,459.31) rectangle (389.10,542.54);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,462.01) rectangle (393.78,542.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (374.86,459.31) rectangle (389.10,542.54);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,502.08) {Nigeria};
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,376.38) rectangle (393.78,456.51);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (384.10,500.92) {Nigeria};
+\end{scope}
+\begin{scope}
+\path[clip] (374.86,370.58) rectangle (389.10,453.81);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,376.38) rectangle (393.78,456.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (374.86,370.58) rectangle (389.10,453.81);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,416.45) {Sierra Leone 1};
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,290.75) rectangle (393.78,370.88);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (384.10,412.19) {Sierra Leone 1};
+\end{scope}
+\begin{scope}
+\path[clip] (374.86,281.85) rectangle (389.10,365.08);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,290.75) rectangle (393.78,370.88);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (374.86,281.85) rectangle (389.10,365.08);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,330.81) {Uganda 2};
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,205.12) rectangle (393.78,285.25);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (384.10,323.46) {Uganda 2};
+\end{scope}
+\begin{scope}
+\path[clip] (374.86,193.12) rectangle (389.10,276.35);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,205.12) rectangle (393.78,285.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (374.86,193.12) rectangle (389.10,276.35);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,245.18) {Russia};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,547.64) rectangle ( 48.28,627.77);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (384.10,234.73) {Russia};
+\end{scope}
+\begin{scope}
+\path[clip] ( 27.01,548.04) rectangle ( 41.25,631.27);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,547.64) rectangle ( 48.28,627.77);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 27.01,548.04) rectangle ( 41.25,631.27);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,587.71) {Burkina Faso};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,462.01) rectangle ( 48.28,542.14);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.26,589.65) {Burkina Faso};
+\end{scope}
+\begin{scope}
+\path[clip] ( 27.01,459.31) rectangle ( 41.25,542.54);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,462.01) rectangle ( 48.28,542.14);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 27.01,459.31) rectangle ( 41.25,542.54);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,502.08) {Nepal};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,376.38) rectangle ( 48.28,456.51);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.26,500.92) {Nepal};
+\end{scope}
+\begin{scope}
+\path[clip] ( 27.01,370.58) rectangle ( 41.25,453.81);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,376.38) rectangle ( 48.28,456.51);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 27.01,370.58) rectangle ( 41.25,453.81);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,416.45) {Rwanda};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,290.75) rectangle ( 48.28,370.88);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.26,412.19) {Rwanda};
+\end{scope}
+\begin{scope}
+\path[clip] ( 27.01,281.85) rectangle ( 41.25,365.08);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,290.75) rectangle ( 48.28,370.88);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 27.01,281.85) rectangle ( 41.25,365.08);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,330.81) {Sierra Leone 2};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,205.12) rectangle ( 48.28,285.25);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.26,323.46) {Sierra Leone 2};
+\end{scope}
+\begin{scope}
+\path[clip] ( 27.01,193.12) rectangle ( 41.25,276.35);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,205.12) rectangle ( 48.28,285.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 27.01,193.12) rectangle ( 41.25,276.35);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,245.18) {All LMICs};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,119.49) rectangle ( 48.28,199.62);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.26,234.73) {All LMICs};
+\end{scope}
+\begin{scope}
+\path[clip] ( 27.01,104.39) rectangle ( 41.25,187.62);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,119.49) rectangle ( 48.28,199.62);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 27.01,104.39) rectangle ( 41.25,187.62);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,159.55) {USA};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,116.74) --
-	( 75.24,119.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,116.74) --
-	(120.16,119.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,116.74) --
-	(165.08,119.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,116.74) --
-	(209.99,119.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,116.74) --
-	(254.91,119.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,116.74) --
-	(299.83,119.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,116.74) --
-	(344.75,119.49);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.26,146.00) {USA};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,101.64) --
+	( 68.60,104.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,101.64) --
+	(114.17,104.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,101.64) --
+	(159.74,104.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,101.64) --
+	(205.31,104.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,101.64) --
+	(250.88,104.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,101.64) --
+	(296.45,104.39);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,101.64) --
+	(342.02,104.39);
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 78.27,114.54) {Health workers};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (118.43,114.54) {Government or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (127.94,114.54) {MoH};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (163.35,114.54) {Family or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.86,114.54) {Friends};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (198.77,114.54) {Famous person,};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (208.27,114.54) {religious leader};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (217.78,114.54) {or traditional};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (227.28,114.54) {healers};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (248.44,114.54) {Newspapers,};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (257.95,114.54) {radio or online};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (267.45,114.54) {groups};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (302.86,114.54) {Other};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (343.03,114.54) {Don't know or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (352.54,114.54) {Refuse};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,202.37) --
-	(420.73,205.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,202.37) --
-	(465.65,205.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,202.37) --
-	(510.57,205.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,202.37) --
-	(555.49,205.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,202.37) --
-	(600.41,205.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,202.37) --
-	(645.33,205.12);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,202.37) --
-	(690.25,205.12);
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 70.72, 99.44) {Health workers};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (111.53, 99.44) {Government or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (121.04, 99.44) {MoH};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (157.10, 99.44) {Family or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (166.61, 99.44) {Friends};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (193.17, 99.44) {Famous person,};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (202.67, 99.44) {religious leader};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (212.18, 99.44) {or traditional};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (221.68, 99.44) {healers};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (243.49, 99.44) {Newspapers,};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (253.00, 99.44) {radio or online};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (262.50, 99.44) {groups};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (298.57, 99.44) {Other};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (339.38, 99.44) {Don't know or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (348.89, 99.44) {Refuse};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,190.37) --
+	(416.44,193.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,190.37) --
+	(462.01,193.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,190.37) --
+	(507.58,193.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,190.37) --
+	(553.15,193.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,190.37) --
+	(598.72,193.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,190.37) --
+	(644.29,193.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,190.37) --
+	(689.86,193.12);
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (423.76,200.17) {Health workers};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (463.93,200.17) {Government or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (473.43,200.17) {MoH};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (508.85,200.17) {Family or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (518.35,200.17) {Friends};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (544.26,200.17) {Famous person,};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (553.77,200.17) {religious leader};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (563.27,200.17) {or traditional};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (572.78,200.17) {healers};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (593.93,200.17) {Newspapers,};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (603.44,200.17) {radio or online};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (612.94,200.17) {groups};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (648.36,200.17) {Other};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (688.53,200.17) {Don't know or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (698.03,200.17) {Refuse};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (418.56,188.17) {Health workers};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (459.38,188.17) {Government or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (468.88,188.17) {MoH};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (504.95,188.17) {Family or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (514.45,188.17) {Friends};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (541.01,188.17) {Famous person,};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (550.52,188.17) {religious leader};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (560.02,188.17) {or traditional};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (569.53,188.17) {healers};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (591.34,188.17) {Newspapers,};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (600.84,188.17) {radio or online};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (610.34,188.17) {groups};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (646.41,188.17) {Other};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (687.23,188.17) {Don't know or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (696.73,188.17) {Refuse};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,548.25) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,567.61) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,586.96) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,606.31) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,551.28) --
-	( 31.71,551.28);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,570.64) --
-	( 31.71,570.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,589.99) --
-	( 31.71,589.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,609.34) --
-	( 31.71,609.34);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,549.70) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,570.53) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,591.37) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,612.20) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,551.82) --
+	( 27.01,551.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,572.66) --
+	( 27.01,572.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,593.49) --
+	( 27.01,593.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,614.32) --
+	( 27.01,614.32);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,462.62) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,481.98) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,501.33) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,520.68) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,465.65) --
-	( 31.71,465.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,485.01) --
-	( 31.71,485.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,504.36) --
-	( 31.71,504.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,523.71) --
-	( 31.71,523.71);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,460.97) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,481.80) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,502.64) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,523.47) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,463.09) --
+	( 27.01,463.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,483.92) --
+	( 27.01,483.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,504.76) --
+	( 27.01,504.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,525.59) --
+	( 27.01,525.59);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,376.99) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,396.35) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,415.70) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,435.05) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,380.02) --
-	( 31.71,380.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,399.38) --
-	( 31.71,399.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,418.73) --
-	( 31.71,418.73);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,438.08) --
-	( 31.71,438.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,372.24) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,393.07) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,413.91) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,434.74) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,374.36) --
+	( 27.01,374.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,395.19) --
+	( 27.01,395.19);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,416.03) --
+	( 27.01,416.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,436.86) --
+	( 27.01,436.86);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,291.36) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,310.71) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,330.07) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,349.42) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,294.39) --
-	( 31.71,294.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,313.74) --
-	( 31.71,313.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,333.10) --
-	( 31.71,333.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,352.45) --
-	( 31.71,352.45);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,283.51) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,304.34) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,325.17) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,346.01) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,285.63) --
+	( 27.01,285.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,306.46) --
+	( 27.01,306.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,327.30) --
+	( 27.01,327.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,348.13) --
+	( 27.01,348.13);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,205.73) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,225.08) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,244.44) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,263.79) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,208.76) --
-	( 31.71,208.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,228.11) --
-	( 31.71,228.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,247.47) --
-	( 31.71,247.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,266.82) --
-	( 31.71,266.82);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,194.78) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,215.61) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,236.44) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,257.28) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,196.90) --
+	( 27.01,196.90);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,217.73) --
+	( 27.01,217.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,238.57) --
+	( 27.01,238.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,259.40) --
+	( 27.01,259.40);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,120.10) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,139.45) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,158.81) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,178.16) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,123.13) --
-	( 31.71,123.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,142.48) --
-	( 31.71,142.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,161.84) --
-	( 31.71,161.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,181.19) --
-	( 31.71,181.19);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,106.05) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,126.88) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,147.71) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,168.55) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,108.17) --
+	( 27.01,108.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,129.00) --
+	( 27.01,129.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,149.84) --
+	( 27.01,149.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,170.67) --
+	( 27.01,170.67);
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,373.63) {estimate};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (276.12,  5.50) rectangle (489.36, 30.95);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 10.80,367.83) {estimate};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (298.62,  5.50) rectangle (459.84, 30.95);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (281.62, 14.44) {Answer};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (322.65, 11.00) rectangle (337.10, 25.45);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (304.12, 15.58) {Answer};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (337.84, 11.00) rectangle (352.29, 25.45);
 \end{scope}
@@
 
-\path[fill=fillColor] (323.36, 11.71) rectangle (336.39, 24.74);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (409.32, 11.00) rectangle (423.78, 25.45);
+\path[fill=fillColor] (338.55, 11.71) rectangle (351.58, 24.74);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (384.80, 11.00) rectangle (399.25, 25.45);
 \end{scope}
@@
 
-\path[fill=fillColor] (410.03, 11.71) rectangle (423.07, 24.74);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (448.02, 11.00) rectangle (462.48, 25.45);
+\path[fill=fillColor] (385.51, 11.71) rectangle (398.54, 24.74);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (425.21, 11.00) rectangle (439.66, 25.45);
 \end{scope}
@@
 
-\path[fill=fillColor] (448.73, 11.71) rectangle (461.77, 24.74);
+\path[fill=fillColor] (425.92, 11.71) rectangle (438.95, 24.74);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (342.60, 15.20) {No, Don't know};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (357.79, 16.11) {Female};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (429.28, 15.20) {Yes};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (404.75, 16.11) {Male};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (467.98, 15.20) {Any};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (445.16, 16.11) {All};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  5.50,635.84) {Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine?};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.32] at (  5.50,638.57) {Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine?};
 \end{scope}

### 2021-06-22 paper_files/figure-latex/mainfigure1-1.tex
update

--- 2021-03-23 paper_files/figure-latex/mainfigure1-1.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:22
+% Created by tikzDevice version 0.12.3.1 on 2021-06-22 11:48:04
 % !TEX encoding = UTF-8 Unicode
-\documentclass[10pt]{article}
+% !TEX program = xelatex
+
+\documentclass[fontsize=7pt,DIV=calc]{scrartcl}
 
@@
 \begin{scope}
-\path[clip] (152.00, 76.80) rectangle (271.61,506.36);
+\path[clip] (123.21, 72.04) rectangle (250.02,511.66);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (152.00, 76.80) rectangle (271.61,506.36);
+\path[fill=fillColor] (123.21, 72.04) rectangle (250.02,511.66);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (171.03, 76.80) --
-	(171.03,506.36);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (198.21, 76.80) --
-	(198.21,506.36);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (225.40, 76.80) --
-	(225.40,506.36);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (252.58, 76.80) --
-	(252.58,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00, 92.71) --
-	(271.61, 92.71);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,119.23) --
-	(271.61,119.23);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,145.75) --
-	(271.61,145.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,172.26) --
-	(271.61,172.26);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,198.78) --
-	(271.61,198.78);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,225.29) --
-	(271.61,225.29);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,251.81) --
-	(271.61,251.81);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,278.33) --
-	(271.61,278.33);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,304.84) --
-	(271.61,304.84);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,331.36) --
-	(271.61,331.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,357.87) --
-	(271.61,357.87);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,384.39) --
-	(271.61,384.39);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,410.91) --
-	(271.61,410.91);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,437.42) --
-	(271.61,437.42);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,463.94) --
-	(271.61,463.94);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (152.00,490.45) --
-	(271.61,490.45);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (157.44, 76.80) --
-	(157.44,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (184.62, 76.80) --
-	(184.62,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (211.80, 76.80) --
-	(211.80,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (238.99, 76.80) --
-	(238.99,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (266.17, 76.80) --
-	(266.17,506.36);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (143.39, 72.04) --
+	(143.39,511.66);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (172.21, 72.04) --
+	(172.21,511.66);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (201.03, 72.04) --
+	(201.03,511.66);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (229.84, 72.04) --
+	(229.84,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21, 87.37) --
+	(250.02, 87.37);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,112.93) --
+	(250.02,112.93);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,138.49) --
+	(250.02,138.49);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,164.05) --
+	(250.02,164.05);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,189.61) --
+	(250.02,189.61);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,215.17) --
+	(250.02,215.17);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,240.73) --
+	(250.02,240.73);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,266.29) --
+	(250.02,266.29);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,291.85) --
+	(250.02,291.85);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,317.41) --
+	(250.02,317.41);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,342.97) --
+	(250.02,342.97);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,368.53) --
+	(250.02,368.53);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,394.09) --
+	(250.02,394.09);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,419.65) --
+	(250.02,419.65);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,445.21) --
+	(250.02,445.21);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,470.77) --
+	(250.02,470.77);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (123.21,496.33) --
+	(250.02,496.33);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (128.98, 72.04) --
+	(128.98,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (157.80, 72.04) --
+	(157.80,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (186.62, 72.04) --
+	(186.62,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (215.44, 72.04) --
+	(215.44,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (244.25, 72.04) --
+	(244.25,511.66);
 \definecolor{drawColor}{RGB}{204,102,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (250.51,143.09) --
-	(250.51,148.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (250.51,145.75) --
-	(238.88,145.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (238.88,143.09) --
-	(238.88,148.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (233.01,487.80) --
-	(233.01,493.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (233.01,490.45) --
-	(226.48,490.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (226.48,487.80) --
-	(226.48,493.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (241.81,461.29) --
-	(241.81,466.59);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (241.81,463.94) --
-	(235.94,463.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (235.94,461.29) --
-	(235.94,466.59);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (251.38,434.77) --
-	(251.38,440.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (251.38,437.42) --
-	(247.47,437.42);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (247.47,434.77) --
-	(247.47,440.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (257.15,408.25) --
-	(257.15,413.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (257.15,410.91) --
-	(251.49,410.91);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (251.49,408.25) --
-	(251.49,413.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (263.56,381.74) --
-	(263.56,387.04);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (263.56,384.39) --
-	(261.28,384.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (261.28,381.74) --
-	(261.28,387.04);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (242.47,355.22) --
-	(242.47,360.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (242.47,357.87) --
-	(238.23,357.87);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (238.23,355.22) --
-	(238.23,360.52);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (246.92,328.71) --
-	(246.92,334.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (246.92,331.36) --
-	(233.55,331.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (233.55,328.71) --
-	(233.55,334.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (232.35,302.19) --
-	(232.35,307.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (232.35,304.84) --
-	(227.13,304.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (227.13,302.19) --
-	(227.13,307.49);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (191.91,116.58) --
-	(191.91,121.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (191.91,119.23) --
-	(189.08,119.23);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (189.08,116.58) --
-	(189.08,121.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (251.82,275.67) --
-	(251.82,280.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (251.82,278.33) --
-	(247.58,278.33);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (247.58,275.67) --
-	(247.58,280.98);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (244.97,249.16) --
-	(244.97,254.46);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (244.97,251.81) --
-	(239.53,251.81);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (239.53,249.16) --
-	(239.53,254.46);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.86,222.64) --
-	(254.86,227.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.86,225.29) --
-	(251.17,225.29);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (251.17,222.64) --
-	(251.17,227.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (252.25,196.13) --
-	(252.25,201.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (252.25,198.78) --
-	(249.21,198.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (249.21,196.13) --
-	(249.21,201.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (243.01,169.61) --
-	(243.01,174.91);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (243.01,172.26) --
-	(238.23,172.26);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (238.23,169.61) --
-	(238.23,174.91);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (230.61, 90.06) --
-	(230.61, 95.37);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (230.61, 92.71) --
-	(224.63, 92.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (224.63, 90.06) --
-	(224.63, 95.37);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (231.57,135.93) --
+	(231.57,141.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (231.57,138.49) --
+	(207.25,138.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (207.25,135.93) --
+	(207.25,141.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (227.65,161.49) --
+	(227.65,166.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (227.65,164.05) --
+	(215.32,164.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (215.32,161.49) --
+	(215.32,166.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.10,493.77) --
+	(209.10,498.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.10,496.33) --
+	(202.18,496.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.18,493.77) --
+	(202.18,498.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (218.43,468.21) --
+	(218.43,473.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (218.43,470.77) --
+	(212.21,470.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (212.21,468.21) --
+	(212.21,473.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (228.46,442.65) --
+	(228.46,447.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (228.46,445.21) --
+	(223.85,445.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (223.85,442.65) --
+	(223.85,447.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (234.69,417.09) --
+	(234.69,422.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (234.69,419.65) --
+	(228.69,419.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (228.69,417.09) --
+	(228.69,422.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (241.49,391.53) --
+	(241.49,396.64);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (241.49,394.09) --
+	(239.07,394.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (239.07,391.53) --
+	(239.07,396.64);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (219.12,365.97) --
+	(219.12,371.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (219.12,368.53) --
+	(214.63,368.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.63,365.97) --
+	(214.63,371.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (223.85,340.41) --
+	(223.85,345.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (223.85,342.97) --
+	(209.67,342.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (209.67,340.41) --
+	(209.67,345.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (208.40,314.85) --
+	(208.40,319.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (208.40,317.41) --
+	(202.87,317.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (202.87,314.85) --
+	(202.87,319.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (165.52,110.37) --
+	(165.52,115.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (165.52,112.93) --
+	(162.52,112.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (162.52,110.37) --
+	(162.52,115.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.04,289.29) --
+	(229.04,294.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.04,291.85) --
+	(224.54,291.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (224.54,289.29) --
+	(224.54,294.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (221.78,263.73) --
+	(221.78,268.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (221.78,266.29) --
+	(216.01,266.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (216.01,263.73) --
+	(216.01,268.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (232.27,238.17) --
+	(232.27,243.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (232.27,240.73) --
+	(228.35,240.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (228.35,238.17) --
+	(228.35,243.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.50,212.61) --
+	(229.50,217.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.50,215.17) --
+	(226.27,215.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (226.27,212.61) --
+	(226.27,217.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (219.70,187.05) --
+	(219.70,192.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (219.70,189.61) --
+	(214.63,189.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (214.63,187.05) --
+	(214.63,192.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (206.56, 84.82) --
+	(206.56, 89.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (206.56, 87.37) --
+	(200.22, 87.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (200.22, 84.82) --
+	(200.22, 89.93);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (244.75,145.75) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (229.74,490.45) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (238.88,463.94) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (249.43,437.42) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (254.32,410.91) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (262.47,384.39) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (240.29,357.87) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (240.18,331.36) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (229.74,304.84) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.49,119.23) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (249.75,278.33) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (242.25,251.81) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (253.01,225.29) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (250.73,198.78) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (240.62,172.26) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (227.68, 92.71) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (219.35,138.49) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (221.55,164.05) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (205.64,496.33) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (215.32,470.77) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (226.16,445.21) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (231.69,419.65) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (240.34,394.09) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (216.82,368.53) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (216.70,342.97) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (205.64,317.41) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.02,112.93) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (226.85,291.85) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (218.89,266.29) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (230.31,240.73) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (227.89,215.17) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (217.16,189.61) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (203.45, 87.37) circle (  1.96);
 \definecolor{drawColor}{RGB}{169,169,169}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (152.00,159.00) -- (271.61,159.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (152.00,132.49) -- (271.61,132.49);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (123.21,176.83) -- (250.02,176.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (123.21,151.27) -- (250.02,151.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (123.21,125.71) -- (250.02,125.71);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] (152.00, 76.80) rectangle (271.61,506.36);
-\end{scope}
-\begin{scope}
-\path[clip] (276.61, 76.80) rectangle (396.21,506.36);
+\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] (123.21, 72.04) rectangle (250.02,511.66);
+\end{scope}
+\begin{scope}
+\path[clip] (255.02, 72.04) rectangle (381.82,511.66);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (276.61, 76.80) rectangle (396.21,506.36);
+\path[fill=fillColor] (255.02, 72.04) rectangle (381.82,511.66);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (295.64, 76.80) --
-	(295.64,506.36);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (322.82, 76.80) --
-	(322.82,506.36);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (350.00, 76.80) --
-	(350.00,506.36);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (377.19, 76.80) --
-	(377.19,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61, 92.71) --
-	(396.21, 92.71);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,119.23) --
-	(396.21,119.23);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,145.75) --
-	(396.21,145.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,172.26) --
-	(396.21,172.26);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,198.78) --
-	(396.21,198.78);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,225.29) --
-	(396.21,225.29);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,251.81) --
-	(396.21,251.81);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,278.33) --
-	(396.21,278.33);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,304.84) --
-	(396.21,304.84);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,331.36) --
-	(396.21,331.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,357.87) --
-	(396.21,357.87);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,384.39) --
-	(396.21,384.39);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,410.91) --
-	(396.21,410.91);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,437.42) --
-	(396.21,437.42);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,463.94) --
-	(396.21,463.94);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (276.61,490.45) --
-	(396.21,490.45);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (282.04, 76.80) --
-	(282.04,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (309.23, 76.80) --
-	(309.23,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (336.41, 76.80) --
-	(336.41,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (363.59, 76.80) --
-	(363.59,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (390.78, 76.80) --
-	(390.78,506.36);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (374.36,148.40) --
-	(374.36,151.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (374.36,149.72) --
-	(361.75,149.72);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (361.75,148.40) --
-	(361.75,151.05);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (377.73,140.44) --
-	(377.73,143.09);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (377.73,141.77) --
-	(366.20,141.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (366.20,140.44) --
-	(366.20,143.09);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (355.87,493.10) --
-	(355.87,495.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (355.87,494.43) --
-	(343.26,494.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (343.26,493.10) --
-	(343.26,495.76);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (360.22,485.15) --
-	(360.22,487.80);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (360.22,486.48) --
-	(352.72,486.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (352.72,485.15) --
-	(352.72,487.80);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (365.77,466.59) --
-	(365.77,469.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (365.77,467.91) --
-	(358.27,467.91);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (358.27,466.59) --
-	(358.27,469.24);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (370.88,458.63) --
-	(370.88,461.29);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (370.88,459.96) --
-	(361.42,459.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (361.42,458.63) --
-	(361.42,461.29);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (373.49,440.07) --
-	(373.49,442.72);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (373.49,441.40) --
-	(366.42,441.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (366.42,440.07) --
-	(366.42,442.72);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (377.19,432.12) --
-	(377.19,434.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (377.19,433.44) --
-	(373.05,433.44);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (373.05,432.12) --
-	(373.05,434.77);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (379.90,413.56) --
-	(379.90,416.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (379.90,414.88) --
-	(371.75,414.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (371.75,413.56) --
-	(371.75,416.21);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (384.36,405.60) --
-	(384.36,408.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (384.36,406.93) --
-	(378.16,406.93);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (378.16,405.60) --
-	(378.16,408.25);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (388.82,387.04) --
-	(388.82,389.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (388.82,388.37) --
-	(384.91,388.37);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (384.91,387.04) --
-	(384.91,389.69);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (388.28,379.09) --
-	(388.28,381.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (388.28,380.41) --
-	(385.45,380.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (385.45,379.09) --
-	(385.45,381.74);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (366.97,360.52) --
-	(366.97,363.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (366.97,361.85) --
-	(360.01,361.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (360.01,360.52) --
-	(360.01,363.18);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (368.38,352.57) --
-	(368.38,355.22);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (368.38,353.90) --
-	(363.16,353.90);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (363.16,352.57) --
-	(363.16,355.22);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (367.73,334.01) --
-	(367.73,336.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (367.73,335.33) --
-	(353.37,335.33);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (353.37,334.01) --
-	(353.37,336.66);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (375.99,326.05) --
-	(375.99,328.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (375.99,327.38) --
-	(362.29,327.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (362.29,326.05) --
-	(362.29,328.71);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (308.36,121.88) --
-	(308.36,124.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (308.36,123.21) --
-	(304.77,123.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (304.77,121.88) --
-	(304.77,124.53);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (326.08,113.93) --
-	(326.08,116.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (326.08,115.25) --
-	(321.73,115.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (321.73,113.93) --
-	(321.73,116.58);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (372.29,280.98) --
-	(372.29,283.63);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (372.29,282.30) --
-	(364.46,282.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (364.46,280.98) --
-	(364.46,283.63);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (380.12,273.02) --
-	(380.12,275.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (380.12,274.35) --
-	(375.34,274.35);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (375.34,273.02) --
-	(375.34,275.67);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (367.62,254.46) --
-	(367.62,257.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (367.62,255.79) --
-	(357.61,255.79);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (357.61,254.46) --
-	(357.61,257.11);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (372.40,246.51) --
-	(372.40,249.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (372.40,247.83) --
-	(365.99,247.83);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (365.99,246.51) --
-	(365.99,249.16);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (381.54,227.95) --
-	(381.54,230.60);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (381.54,229.27) --
-	(375.23,229.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (375.23,227.95) --
-	(375.23,230.60);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (379.36,219.99) --
-	(379.36,222.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (379.36,221.32) --
-	(375.45,221.32);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (375.45,219.99) --
-	(375.45,222.64);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (376.86,196.13) --
-	(376.86,201.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (376.86,198.78) --
-	(373.82,198.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (373.82,196.13) --
-	(373.82,201.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (367.18,174.91) --
-	(367.18,177.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (367.18,176.24) --
-	(359.79,176.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (359.79,174.91) --
-	(359.79,177.56);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (370.01,166.96) --
-	(370.01,169.61);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (370.01,168.28) --
-	(363.81,168.28);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (363.81,166.96) --
-	(363.81,169.61);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (347.39, 95.37) --
-	(347.39, 98.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (347.39, 96.69) --
-	(338.69, 96.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (338.69, 95.37) --
-	(338.69, 98.02);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (365.66, 87.41) --
-	(365.66, 90.06);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (365.66, 88.74) --
-	(357.94, 88.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (357.94, 87.41) --
-	(357.94, 90.06);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (275.19, 72.04) --
+	(275.19,511.66);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (304.01, 72.04) --
+	(304.01,511.66);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (332.83, 72.04) --
+	(332.83,511.66);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (361.65, 72.04) --
+	(361.65,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02, 87.37) --
+	(381.82, 87.37);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,112.93) --
+	(381.82,112.93);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,138.49) --
+	(381.82,138.49);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,164.05) --
+	(381.82,164.05);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,189.61) --
+	(381.82,189.61);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,215.17) --
+	(381.82,215.17);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,240.73) --
+	(381.82,240.73);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,266.29) --
+	(381.82,266.29);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,291.85) --
+	(381.82,291.85);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,317.41) --
+	(381.82,317.41);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,342.97) --
+	(381.82,342.97);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,368.53) --
+	(381.82,368.53);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,394.09) --
+	(381.82,394.09);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,419.65) --
+	(381.82,419.65);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,445.21) --
+	(381.82,445.21);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,470.77) --
+	(381.82,470.77);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (255.02,496.33) --
+	(381.82,496.33);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (260.78, 72.04) --
+	(260.78,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (289.60, 72.04) --
+	(289.60,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (318.42, 72.04) --
+	(318.42,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (347.24, 72.04) --
+	(347.24,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (376.06, 72.04) --
+	(376.06,511.66);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (361.65,141.05) --
+	(361.65,143.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (361.65,142.32) --
+	(334.10,142.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (334.10,141.05) --
+	(334.10,143.60);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (364.99,133.38) --
+	(364.99,135.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (364.99,134.66) --
+	(341.71,134.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (341.71,133.38) --
+	(341.71,135.93);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (358.77,166.61) --
+	(358.77,169.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (358.77,167.88) --
+	(345.39,167.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (345.39,166.61) --
+	(345.39,169.16);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (362.11,158.94) --
+	(362.11,161.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (362.11,160.22) --
+	(350.01,160.22);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (350.01,158.94) --
+	(350.01,161.49);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.05,498.88) --
+	(339.05,501.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (339.05,500.16) --
+	(325.68,500.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (325.68,498.88) --
+	(325.68,501.44);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (343.67,491.21) --
+	(343.67,493.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (343.67,492.49) --
+	(335.71,492.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (335.71,491.21) --
+	(335.71,493.77);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (349.54,473.32) --
+	(349.54,475.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (349.54,474.60) --
+	(341.59,474.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (341.59,473.32) --
+	(341.59,475.88);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (354.96,465.65) --
+	(354.96,468.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (354.96,466.93) --
+	(344.93,466.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (344.93,465.65) --
+	(344.93,468.21);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (359.69,447.76) --
+	(359.69,450.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (359.69,449.04) --
+	(351.85,449.04);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (351.85,447.76) --
+	(351.85,450.32);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (361.07,440.09) --
+	(361.07,442.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (361.07,441.37) --
+	(355.89,441.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (355.89,440.09) --
+	(355.89,442.65);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (364.53,422.20) --
+	(364.53,424.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (364.53,423.48) --
+	(355.89,423.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (355.89,422.20) --
+	(355.89,424.76);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.26,414.53) --
+	(369.26,417.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.26,415.81) --
+	(362.69,415.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (362.69,414.53) --
+	(362.69,417.09);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (373.98,396.64) --
+	(373.98,399.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (373.98,397.92) --
+	(369.83,397.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (369.83,396.64) --
+	(369.83,399.20);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (373.41,388.98) --
+	(373.41,391.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (373.41,390.25) --
+	(370.41,390.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (370.41,388.98) --
+	(370.41,391.53);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (350.81,371.08) --
+	(350.81,373.64);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (350.81,372.36) --
+	(343.44,372.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (343.44,371.08) --
+	(343.44,373.64);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (352.31,363.42) --
+	(352.31,365.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (352.31,364.69) --
+	(346.78,364.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (346.78,363.42) --
+	(346.78,365.97);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (351.62,345.52) --
+	(351.62,348.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (351.62,346.80) --
+	(336.40,346.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (336.40,345.52) --
+	(336.40,348.08);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (360.38,337.86) --
+	(360.38,340.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (360.38,339.13) --
+	(345.86,339.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (345.86,337.86) --
+	(345.86,340.41);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (288.68,115.49) --
+	(288.68,118.04);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (288.68,116.76) --
+	(284.87,116.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (284.87,115.49) --
+	(284.87,118.04);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (307.47,107.82) --
+	(307.47,110.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (307.47,109.10) --
+	(302.86,109.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (302.86,107.82) --
+	(302.86,110.37);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (356.46,294.40) --
+	(356.46,296.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (356.46,295.68) --
+	(348.16,295.68);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.16,294.40) --
+	(348.16,296.96);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (364.76,286.74) --
+	(364.76,289.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (364.76,288.01) --
+	(359.69,288.01);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (359.69,286.74) --
+	(359.69,289.29);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (351.50,268.84) --
+	(351.50,271.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (351.50,270.12) --
+	(340.90,270.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (340.90,268.84) --
+	(340.90,271.40);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (356.58,261.18) --
+	(356.58,263.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (356.58,262.45) --
+	(349.78,262.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (349.78,261.18) --
+	(349.78,263.73);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (366.26,243.28) --
+	(366.26,245.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (366.26,244.56) --
+	(359.57,244.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (359.57,243.28) --
+	(359.57,245.84);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (363.95,235.62) --
+	(363.95,238.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (363.95,236.90) --
+	(359.80,236.90);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (359.80,235.62) --
+	(359.80,238.17);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (361.30,212.61) --
+	(361.30,217.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (361.30,215.17) --
+	(358.08,215.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (358.08,212.61) --
+	(358.08,217.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (351.04,192.17) --
+	(351.04,194.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (351.04,193.44) --
+	(343.20,193.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (343.20,192.17) --
+	(343.20,194.72);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (354.04,184.50) --
+	(354.04,187.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (354.04,185.78) --
+	(347.47,185.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (347.47,184.50) --
+	(347.47,187.05);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (330.06, 89.93) --
+	(330.06, 92.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (330.06, 91.21) --
+	(320.84, 91.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (320.84, 89.93) --
+	(320.84, 92.48);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (349.43, 82.26) --
+	(349.43, 84.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (349.43, 83.54) --
+	(341.24, 83.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (341.24, 82.26) --
+	(341.24, 84.82);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (347.82,142.32) circle (  1.96);
 \definecolor{drawColor}{RGB}{153,153,51}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (368.05,149.72) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (353.35,134.66) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (352.08,167.88) circle (  1.96);
+\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{fillColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (356.00,160.22) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (332.37,500.16) circle (  1.96);
+\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{fillColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (339.63,492.49) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (345.51,474.60) circle (  1.96);
+\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{fillColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (349.89,466.93) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (355.77,449.04) circle (  1.96);
+\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{fillColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (358.42,441.37) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (360.15,423.48) circle (  1.96);
+\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{fillColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (366.03,415.81) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (371.91,397.92) circle (  1.96);
+\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{fillColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (371.91,390.25) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (347.12,372.36) circle (  1.96);
+\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{fillColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (349.54,364.69) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (344.01,346.80) circle (  1.96);
+\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{fillColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (353.12,339.13) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (286.83,116.76) circle (  1.96);
+\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{fillColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (305.16,109.10) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (352.31,295.68) circle (  1.96);
+\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{fillColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.23,288.01) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (346.20,270.12) circle (  1.96);
+\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{fillColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (353.12,262.45) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.92,244.56) circle (  1.96);
+\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{fillColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (361.88,236.90) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (359.69,215.17) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (347.12,193.44) circle (  1.96);
+\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{fillColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (350.70,185.78) circle (  1.96);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (325.45, 91.21) circle (  1.96);
+\definecolor{drawColor}{RGB}{153,153,51}
+\definecolor{fillColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (345.39, 83.54) circle (  1.96);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (255.02,176.83) -- (381.82,176.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (255.02,151.27) -- (381.82,151.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (255.02,125.71) -- (381.82,125.71);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] (255.02, 72.04) rectangle (381.82,511.66);
+\end{scope}
+\begin{scope}
+\path[clip] (386.82, 72.04) rectangle (513.63,511.66);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (386.82, 72.04) rectangle (513.63,511.66);
+\definecolor{drawColor}{gray}{0.92}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (407.00, 72.04) --
+	(407.00,511.66);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (435.81, 72.04) --
+	(435.81,511.66);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (464.63, 72.04) --
+	(464.63,511.66);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (493.45, 72.04) --
+	(493.45,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82, 87.37) --
+	(513.63, 87.37);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,112.93) --
+	(513.63,112.93);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,138.49) --
+	(513.63,138.49);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,164.05) --
+	(513.63,164.05);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,189.61) --
+	(513.63,189.61);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,215.17) --
+	(513.63,215.17);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,240.73) --
+	(513.63,240.73);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,266.29) --
+	(513.63,266.29);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,291.85) --
+	(513.63,291.85);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,317.41) --
+	(513.63,317.41);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,342.97) --
+	(513.63,342.97);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,368.53) --
+	(513.63,368.53);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,394.09) --
+	(513.63,394.09);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,419.65) --
+	(513.63,419.65);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,445.21) --
+	(513.63,445.21);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,470.77) --
+	(513.63,470.77);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (386.82,496.33) --
+	(513.63,496.33);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (392.59, 72.04) --
+	(392.59,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (421.41, 72.04) --
+	(421.41,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (450.22, 72.04) --
+	(450.22,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (479.04, 72.04) --
+	(479.04,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (507.86, 72.04) --
+	(507.86,511.66);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (493.22,133.38) --
+	(493.22,135.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (493.22,134.66) --
+	(464.17,134.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (464.17,133.38) --
+	(464.17,135.93);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (496.22,141.05) --
+	(496.22,143.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (496.22,142.32) --
+	(473.05,142.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (473.05,141.05) --
+	(473.05,143.60);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (488.73,158.94) --
+	(488.73,161.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (488.73,160.22) --
+	(474.89,160.22);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (474.89,158.94) --
+	(474.89,161.49);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (491.03,166.61) --
+	(491.03,169.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (491.03,167.88) --
+	(478.01,167.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (478.01,166.61) --
+	(478.01,169.16);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (468.44,491.21) --
+	(468.44,493.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (468.44,492.49) --
+	(457.03,492.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (457.03,491.21) --
+	(457.03,493.77);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (477.66,498.88) --
+	(477.66,501.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (477.66,500.16) --
+	(469.13,500.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.13,498.88) --
+	(469.13,501.44);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (487.69,465.65) --
+	(487.69,468.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (487.69,466.93) --
+	(477.43,466.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (477.43,465.65) --
+	(477.43,468.21);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (481.12,473.32) --
+	(481.12,475.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (481.12,474.60) --
+	(473.39,474.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (473.39,473.32) --
+	(473.39,475.88);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (501.64,440.09) --
+	(501.64,442.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (501.64,441.37) --
+	(486.08,441.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (486.08,440.09) --
+	(486.08,442.65);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (495.41,447.76) --
+	(495.41,450.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (495.41,449.04) --
+	(487.69,449.04);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (487.69,447.76) --
+	(487.69,450.32);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (496.80,414.53) --
+	(496.80,417.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (496.80,415.81) --
+	(486.88,415.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (486.88,414.53) --
+	(486.88,417.09);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (499.56,422.20) --
+	(499.56,424.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (499.56,423.48) --
+	(492.30,423.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (492.30,422.20) --
+	(492.30,424.76);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (496.91,337.86) --
+	(496.91,340.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (496.91,339.13) --
+	(480.89,339.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (480.89,337.86) --
+	(480.89,340.41);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (485.38,345.52) --
+	(485.38,348.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (485.38,346.80) --
+	(470.28,346.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (470.28,345.52) --
+	(470.28,348.08);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (479.62,312.30) --
+	(479.62,314.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (479.62,313.57) --
+	(470.17,313.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (470.17,312.30) --
+	(470.17,314.85);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.94,319.96) --
+	(469.94,322.52);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (469.94,321.24) --
+	(463.14,321.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (463.14,319.96) --
+	(463.14,322.52);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (430.05,107.82) --
+	(430.05,110.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (430.05,109.10) --
+	(426.71,109.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (426.71,107.82) --
+	(426.71,110.37);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (429.47,115.49) --
+	(429.47,118.04);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (429.47,116.76) --
+	(424.06,116.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (424.06,115.49) --
+	(424.06,118.04);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (481.58,286.74) --
+	(481.58,289.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (481.58,288.01) --
+	(468.09,288.01);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (468.09,286.74) --
+	(468.09,289.29);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (495.99,294.40) --
+	(495.99,296.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (495.99,295.68) --
+	(491.49,295.68);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (491.49,294.40) --
+	(491.49,296.96);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (483.31,261.18) --
+	(483.31,263.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (483.31,262.45) --
+	(473.39,262.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (473.39,261.18) --
+	(473.39,263.73);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (488.61,268.84) --
+	(488.61,271.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (488.61,270.12) --
+	(481.35,270.12);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (481.35,268.84) --
+	(481.35,271.40);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (499.22,235.62) --
+	(499.22,238.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (499.22,236.90) --
+	(490.57,236.90);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (490.57,235.62) --
+	(490.57,238.17);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (495.87,243.28) --
+	(495.87,245.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (495.87,244.56) --
+	(491.72,244.56);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (491.72,243.28) --
+	(491.72,245.84);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (491.61,210.06) --
+	(491.61,212.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (491.61,211.34) --
+	(478.35,211.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (478.35,210.06) --
+	(478.35,212.61);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (492.30,217.73) --
+	(492.30,220.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (492.30,219.00) --
+	(488.50,219.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (488.50,217.73) --
+	(488.50,220.28);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (476.62,184.50) --
+	(476.62,187.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (476.62,185.78) --
+	(466.71,185.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (466.71,184.50) --
+	(466.71,187.05);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (487.34,192.17) --
+	(487.34,194.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (487.34,193.44) --
+	(481.69,193.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (481.69,192.17) --
+	(481.69,194.72);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (479.04, 82.26) --
+	(479.04, 84.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (479.04, 83.54) --
+	(472.70, 83.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (472.70, 82.26) --
+	(472.70, 84.82);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (458.29, 89.93) --
+	(458.29, 92.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (458.29, 91.21) --
+	(445.61, 91.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (445.61, 89.93) --
+	(445.61, 92.48);
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (478.70,134.66) circle (  1.96);
 \definecolor{drawColor}{RGB}{68,170,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (371.97,141.77) circle (  1.96);
-\definecolor{drawColor}{RGB}{153,153,51}
-\definecolor{fillColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (349.57,494.43) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (484.58,142.32) circle (  1.96);
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (481.81,160.22) circle (  1.96);
 \definecolor{drawColor}{RGB}{68,170,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (356.42,486.48) circle (  1.96);
-\definecolor{drawColor}{RGB}{153,153,51}
-\definecolor{fillColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (361.96,467.91) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (484.58,167.88) circle (  1.96);
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (462.67,492.49) circle (  1.96);
 \definecolor{drawColor}{RGB}{68,170,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (366.10,459.96) circle (  1.96);
-\definecolor{drawColor}{RGB}{153,153,51}
-\definecolor{fillColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.90,441.40) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (473.39,500.16) circle (  1.96);
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (482.62,466.93) circle (  1.96);
 \definecolor{drawColor}{RGB}{68,170,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.12,433.44) circle (  1.96);
-\definecolor{drawColor}{RGB}{153,153,51}
-\definecolor{fillColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.77,414.88) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (477.20,474.60) circle (  1.96);
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.80,441.37) circle (  1.96);
 \definecolor{drawColor}{RGB}{68,170,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (381.32,406.93) circle (  1.96);
-\definecolor{drawColor}{RGB}{153,153,51}
-\definecolor{fillColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.86,388.37) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (491.61,449.04) circle (  1.96);
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (491.84,415.81) circle (  1.96);
 \definecolor{drawColor}{RGB}{68,170,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (386.86,380.41) circle (  1.96);
-\definecolor{drawColor}{RGB}{153,153,51}
-\definecolor{fillColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.49,361.85) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (495.99,423.48) circle (  1.96);
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (488.96,339.13) circle (  1.96);
 \definecolor{drawColor}{RGB}{68,170,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (365.77,353.90) circle (  1.96);
-\definecolor{drawColor}{RGB}{153,153,51}
-\definecolor{fillColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (360.55,335.33) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (477.89,346.80) circle (  1.96);
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (474.89,313.57) circle (  1.96);
 \definecolor{drawColor}{RGB}{68,170,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.14,327.38) circle (  1.96);
-\definecolor{drawColor}{RGB}{153,153,51}
-\definecolor{fillColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (306.62,123.21) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (466.59,321.24) circle (  1.96);
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (428.32,109.10) circle (  1.96);
 \definecolor{drawColor}{RGB}{68,170,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (323.91,115.25) circle (  1.96);
-\definecolor{drawColor}{RGB}{153,153,51}
-\definecolor{fillColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (368.38,282.30) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (426.71,116.76) circle (  1.96);
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (474.89,288.01) circle (  1.96);
 \definecolor{drawColor}{RGB}{68,170,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (377.73,274.35) circle (  1.96);
-\definecolor{drawColor}{RGB}{153,153,51}
-\definecolor{fillColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (362.62,255.79) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.68,295.68) circle (  1.96);
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (478.35,262.45) circle (  1.96);
 \definecolor{drawColor}{RGB}{68,170,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (369.14,247.83) circle (  1.96);
-\definecolor{drawColor}{RGB}{153,153,51}
-\definecolor{fillColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (378.38,229.27) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.04,270.12) circle (  1.96);
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (494.95,236.90) circle (  1.96);
 \definecolor{drawColor}{RGB}{68,170,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (377.40,221.32) circle (  1.96);
-\definecolor{drawColor}{RGB}{153,153,51}
-\definecolor{fillColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (375.34,198.78) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (363.49,176.24) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.80,244.56) circle (  1.96);
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (484.92,211.34) circle (  1.96);
 \definecolor{drawColor}{RGB}{68,170,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (366.86,168.28) circle (  1.96);
-\definecolor{drawColor}{RGB}{153,153,51}
-\definecolor{fillColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (343.04, 96.69) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (490.34,219.00) circle (  1.96);
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (471.67,185.78) circle (  1.96);
 \definecolor{drawColor}{RGB}{68,170,153}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (361.85, 88.74) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (484.58,193.44) circle (  1.96);
+\definecolor{drawColor}{RGB}{170,68,153}
+\definecolor{fillColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (475.93, 83.54) circle (  1.96);
+\definecolor{drawColor}{RGB}{68,170,153}
+\definecolor{fillColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (451.95, 91.21) circle (  1.96);
 \definecolor{drawColor}{RGB}{169,169,169}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (276.61,159.00) -- (396.21,159.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (276.61,132.49) -- (396.21,132.49);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (386.82,176.83) -- (513.63,176.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (386.82,151.27) -- (513.63,151.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (386.82,125.71) -- (513.63,125.71);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] (276.61, 76.80) rectangle (396.21,506.36);
-\end{scope}
-\begin{scope}
-\path[clip] (401.21, 76.80) rectangle (520.82,506.36);
+\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] (386.82, 72.04) rectangle (513.63,511.66);
+\end{scope}
+\begin{scope}
+\path[clip] (518.63, 72.04) rectangle (645.43,511.66);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (401.21, 76.80) rectangle (520.82,506.36);
+\path[fill=fillColor] (518.63, 72.04) rectangle (645.43,511.66);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (420.24, 76.80) --
-	(420.24,506.36);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (447.43, 76.80) --
-	(447.43,506.36);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (474.61, 76.80) --
-	(474.61,506.36);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (501.79, 76.80) --
-	(501.79,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21, 92.71) --
-	(520.82, 92.71);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,119.23) --
-	(520.82,119.23);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,145.75) --
-	(520.82,145.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,172.26) --
-	(520.82,172.26);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,198.78) --
-	(520.82,198.78);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,225.29) --
-	(520.82,225.29);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,251.81) --
-	(520.82,251.81);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,278.33) --
-	(520.82,278.33);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,304.84) --
-	(520.82,304.84);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,331.36) --
-	(520.82,331.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,357.87) --
-	(520.82,357.87);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,384.39) --
-	(520.82,384.39);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,410.91) --
-	(520.82,410.91);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,437.42) --
-	(520.82,437.42);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,463.94) --
-	(520.82,463.94);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (401.21,490.45) --
-	(520.82,490.45);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (406.65, 76.80) --
-	(406.65,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (433.84, 76.80) --
-	(433.84,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (461.02, 76.80) --
-	(461.02,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (488.20, 76.80) --
-	(488.20,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (515.39, 76.80) --
-	(515.39,506.36);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (497.55,140.44) --
-	(497.55,143.09);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (497.55,141.77) --
-	(484.29,141.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (484.29,140.44) --
-	(484.29,143.09);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (499.51,148.40) --
-	(499.51,151.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (499.51,149.72) --
-	(487.22,149.72);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (487.22,148.40) --
-	(487.22,151.05);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (478.20,485.15) --
-	(478.20,487.80);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (478.20,486.48) --
-	(467.43,486.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (467.43,485.15) --
-	(467.43,487.80);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (486.90,493.10) --
-	(486.90,495.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (486.90,494.43) --
-	(478.85,494.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (478.85,493.10) --
-	(478.85,495.76);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (496.36,458.63) --
-	(496.36,461.29);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (496.36,459.96) --
-	(486.68,459.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (486.68,458.63) --
-	(486.68,461.29);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (490.16,466.59) --
-	(490.16,469.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (490.16,467.91) --
-	(482.87,467.91);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (482.87,466.59) --
-	(482.87,469.24);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.38,432.12) --
-	(510.38,434.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.38,433.44) --
-	(497.44,433.44);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (497.44,432.12) --
-	(497.44,434.77);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (503.32,440.07) --
-	(503.32,442.72);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (503.32,441.40) --
-	(496.47,441.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (496.47,440.07) --
-	(496.47,442.72);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (504.95,405.60) --
-	(504.95,408.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (504.95,406.93) --
-	(495.60,406.93);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (495.60,405.60) --
-	(495.60,408.25);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (507.56,413.56) --
-	(507.56,416.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (507.56,414.88) --
-	(500.71,414.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (500.71,413.56) --
-	(500.71,416.21);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (505.06,326.05) --
-	(505.06,328.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (505.06,327.38) --
-	(489.94,327.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (489.94,326.05) --
-	(489.94,328.71);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (494.18,334.01) --
-	(494.18,336.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (494.18,335.33) --
-	(479.94,335.33);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (479.94,334.01) --
-	(479.94,336.66);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (488.75,299.54) --
-	(488.75,302.19);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (488.75,300.86) --
-	(479.83,300.86);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (479.83,299.54) --
-	(479.83,302.19);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (479.61,307.49) --
-	(479.61,310.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (479.61,308.82) --
-	(473.20,308.82);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (473.20,307.49) --
-	(473.20,310.14);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (441.99,113.93) --
-	(441.99,116.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (441.99,115.25) --
-	(438.84,115.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (438.84,113.93) --
-	(438.84,116.58);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (441.45,121.88) --
-	(441.45,124.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (441.45,123.21) --
-	(436.34,123.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (436.34,121.88) --
-	(436.34,124.53);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (490.59,273.02) --
-	(490.59,275.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (490.59,274.35) --
-	(477.87,274.35);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (477.87,273.02) --
-	(477.87,275.67);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (504.19,280.98) --
-	(504.19,283.63);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (504.19,282.30) --
-	(499.95,282.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (499.95,280.98) --
-	(499.95,283.63);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (492.23,246.51) --
-	(492.23,249.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (492.23,247.83) --
-	(482.87,247.83);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (482.87,246.51) --
-	(482.87,249.16);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (497.23,254.46) --
-	(497.23,257.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (497.23,255.79) --
-	(490.38,255.79);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (490.38,254.46) --
-	(490.38,257.11);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (507.23,219.99) --
-	(507.23,222.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (507.23,221.32) --
-	(499.08,221.32);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (499.08,219.99) --
-	(499.08,222.64);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (504.08,227.95) --
-	(504.08,230.60);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (504.08,229.27) --
-	(500.16,229.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (500.16,227.95) --
-	(500.16,230.60);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (500.05,193.47) --
-	(500.05,196.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (500.05,194.80) --
-	(487.55,194.80);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (487.55,193.47) --
-	(487.55,196.13);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (500.71,201.43) --
-	(500.71,204.08);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (500.71,202.75) --
-	(497.12,202.75);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (497.12,201.43) --
-	(497.12,204.08);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (485.92,166.96) --
-	(485.92,169.61);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (485.92,168.28) --
-	(476.57,168.28);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (476.57,166.96) --
-	(476.57,169.61);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (496.03,174.91) --
-	(496.03,177.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (496.03,176.24) --
-	(490.70,176.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (490.70,174.91) --
-	(490.70,177.56);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (488.20, 87.41) --
-	(488.20, 90.06);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (488.20, 88.74) --
-	(482.22, 88.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (482.22, 87.41) --
-	(482.22, 90.06);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (468.63, 95.37) --
-	(468.63, 98.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (468.63, 96.69) --
-	(456.67, 96.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (456.67, 95.37) --
-	(456.67, 98.02);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (538.80, 72.04) --
+	(538.80,511.66);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (567.62, 72.04) --
+	(567.62,511.66);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (596.44, 72.04) --
+	(596.44,511.66);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (625.26, 72.04) --
+	(625.26,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63, 87.37) --
+	(645.43, 87.37);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,112.93) --
+	(645.43,112.93);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,138.49) --
+	(645.43,138.49);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,164.05) --
+	(645.43,164.05);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,189.61) --
+	(645.43,189.61);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,215.17) --
+	(645.43,215.17);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,240.73) --
+	(645.43,240.73);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,266.29) --
+	(645.43,266.29);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,291.85) --
+	(645.43,291.85);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,317.41) --
+	(645.43,317.41);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,342.97) --
+	(645.43,342.97);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,368.53) --
+	(645.43,368.53);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,394.09) --
+	(645.43,394.09);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,419.65) --
+	(645.43,419.65);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,445.21) --
+	(645.43,445.21);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,470.77) --
+	(645.43,470.77);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (518.63,496.33) --
+	(645.43,496.33);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (524.39, 72.04) --
+	(524.39,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (553.21, 72.04) --
+	(553.21,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (582.03, 72.04) --
+	(582.03,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (610.85, 72.04) --
+	(610.85,511.66);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (639.67, 72.04) --
+	(639.67,511.66);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (624.33,142.75) --
+	(624.33,144.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (624.33,143.60) --
+	(609.00,143.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (609.00,142.75) --
+	(609.00,144.45);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (627.22,137.64) --
+	(627.22,139.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (627.22,138.49) --
+	(600.13,138.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (600.13,137.64) --
+	(600.13,139.34);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (624.91,132.53) --
+	(624.91,134.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (624.91,133.38) --
+	(595.52,133.38);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (595.52,132.53) --
+	(595.52,134.23);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (626.64,168.31) --
+	(626.64,170.01);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (626.64,169.16) --
+	(613.04,169.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (613.04,168.31) --
+	(613.04,170.01);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (624.22,163.20) --
+	(624.22,164.90);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (624.22,164.05) --
+	(611.54,164.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (611.54,163.20) --
+	(611.54,164.90);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (623.18,158.09) --
+	(623.18,159.79);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (623.18,158.94) --
+	(607.97,158.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (607.97,158.09) --
+	(607.97,159.79);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (632.75,498.88) --
+	(632.75,501.44);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (632.75,500.16) --
+	(591.25,500.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.25,498.88) --
+	(591.25,501.44);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (609.00,491.21) --
+	(609.00,493.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (609.00,492.49) --
+	(585.49,492.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (585.49,491.21) --
+	(585.49,493.77);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (620.53,475.03) --
+	(620.53,476.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (620.53,475.88) --
+	(602.20,475.88);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (602.20,475.03) --
+	(602.20,476.73);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (614.65,469.91) --
+	(614.65,471.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (614.65,470.77) --
+	(605.31,470.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (605.31,469.91) --
+	(605.31,471.62);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (619.61,464.80) --
+	(619.61,466.51);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (619.61,465.65) --
+	(599.32,465.65);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (599.32,464.80) --
+	(599.32,466.51);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (620.76,449.47) --
+	(620.76,451.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (620.76,450.32) --
+	(606.93,450.32);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (606.93,449.47) --
+	(606.93,451.17);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (625.03,444.35) --
+	(625.03,446.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (625.03,445.21) --
+	(620.53,445.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (620.53,444.35) --
+	(620.53,446.06);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (626.41,439.24) --
+	(626.41,440.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (626.41,440.09) --
+	(613.84,440.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (613.84,439.24) --
+	(613.84,440.95);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (629.52,422.20) --
+	(629.52,424.76);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (629.52,423.48) --
+	(622.72,423.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (622.72,422.20) --
+	(622.72,424.76);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (634.36,414.53) --
+	(634.36,417.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (634.36,415.81) --
+	(625.95,415.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (625.95,414.53) --
+	(625.95,417.09);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (639.44,398.35) --
+	(639.44,400.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (639.44,399.20) --
+	(634.71,399.20);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (634.71,398.35) --
+	(634.71,400.05);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (637.25,393.23) --
+	(637.25,394.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (637.25,394.09) --
+	(634.13,394.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (634.13,393.23) --
+	(634.13,394.94);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (636.44,388.12) --
+	(636.44,389.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (636.44,388.98) --
+	(628.60,388.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (628.60,388.12) --
+	(628.60,389.83);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (610.50,372.79) --
+	(610.50,374.49);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (610.50,373.64) --
+	(597.36,373.64);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (597.36,372.79) --
+	(597.36,374.49);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (616.27,367.68) --
+	(616.27,369.38);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (616.27,368.53) --
+	(611.42,368.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (611.42,367.68) --
+	(611.42,369.38);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (620.76,362.56) --
+	(620.76,364.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (620.76,363.42) --
+	(600.24,363.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (600.24,362.56) --
+	(600.24,364.27);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (632.86,347.23) --
+	(632.86,348.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (632.86,348.08) --
+	(614.77,348.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (614.77,347.23) --
+	(614.77,348.93);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (618.69,342.12) --
+	(618.69,343.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (618.69,342.97) --
+	(604.28,342.97);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (604.28,342.12) --
+	(604.28,343.82);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (635.86,337.00) --
+	(635.86,338.71);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (635.86,337.86) --
+	(599.20,337.86);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (599.20,337.00) --
+	(599.20,338.71);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (567.85,117.19) --
+	(567.85,118.89);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (567.85,118.04) --
+	(558.05,118.04);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (558.05,117.19) --
+	(558.05,118.89);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (557.70,112.08) --
+	(557.70,113.78);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (557.70,112.93) --
+	(554.59,112.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (554.59,112.08) --
+	(554.59,113.78);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (575.11,106.97) --
+	(575.11,108.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (575.11,107.82) --
+	(565.77,107.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (565.77,106.97) --
+	(565.77,108.67);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (629.41,296.11) --
+	(629.41,297.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (629.41,296.96) --
+	(622.37,296.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (622.37,296.11) --
+	(622.37,297.81);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (623.87,291.00) --
+	(623.87,292.70);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (623.87,291.85) --
+	(618.11,291.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (618.11,291.00) --
+	(618.11,292.70);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (625.03,285.88) --
+	(625.03,287.59);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (625.03,286.74) --
+	(592.63,286.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (592.63,285.88) --
+	(592.63,287.59);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (620.76,270.55) --
+	(620.76,272.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (620.76,271.40) --
+	(607.85,271.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (607.85,270.55) --
+	(607.85,272.25);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (617.88,265.44) --
+	(617.88,267.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (617.88,266.29) --
+	(611.31,266.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (611.31,265.44) --
+	(611.31,267.14);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (624.22,260.32) --
+	(624.22,262.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (624.22,261.18) --
+	(595.17,261.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (595.17,260.32) --
+	(595.17,262.03);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (630.33,244.99) --
+	(630.33,246.69);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (630.33,245.84) --
+	(609.58,245.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (609.58,244.99) --
+	(609.58,246.69);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (627.56,239.88) --
+	(627.56,241.58);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (627.56,240.73) --
+	(623.07,240.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (623.07,239.88) --
+	(623.07,241.58);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (631.14,234.77) --
+	(631.14,236.47);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (631.14,235.62) --
+	(625.14,235.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (625.14,234.77) --
+	(625.14,236.47);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (626.29,217.73) --
+	(626.29,220.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (626.29,219.00) --
+	(619.72,219.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (619.72,217.73) --
+	(619.72,220.28);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (625.14,210.06) --
+	(625.14,212.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (625.14,211.34) --
+	(621.57,211.34);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (621.57,210.06) --
+	(621.57,212.61);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (619.03,193.87) --
+	(619.03,195.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (619.03,194.72) --
+	(606.24,194.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (606.24,193.87) --
+	(606.24,195.57);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (616.15,188.76) --
+	(616.15,190.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (616.15,189.61) --
+	(610.16,189.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (610.16,188.76) --
+	(610.16,190.46);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (616.61,183.65) --
+	(616.61,185.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (616.61,184.50) --
+	(601.97,184.50);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (601.97,183.65) --
+	(601.97,185.35);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.94, 91.63) --
+	(591.94, 93.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (591.94, 92.48) --
+	(574.54, 92.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (574.54, 91.63) --
+	(574.54, 93.33);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (603.58, 86.52) --
+	(603.58, 88.22);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (603.58, 87.37) --
+	(594.82, 87.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (594.82, 86.52) --
+	(594.82, 88.22);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (609.58, 81.41) --
+	(609.58, 83.11);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (609.58, 82.26) --
+	(599.09, 82.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (599.09, 81.41) --
+	(599.09, 83.11);
 \definecolor{drawColor}{RGB}{51,34,136}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (490.92,141.77) circle (  1.96);
-\definecolor{drawColor}{RGB}{170,68,153}
-\definecolor{fillColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.42,149.72) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (616.73,143.60) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (613.61,138.49) circle (  1.96);
+\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{fillColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (610.16,133.38) circle (  1.96);
 \definecolor{drawColor}{RGB}{51,34,136}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (472.76,486.48) circle (  1.96);
-\definecolor{drawColor}{RGB}{170,68,153}
-\definecolor{fillColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (482.87,494.43) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (619.84,169.16) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (617.88,164.05) circle (  1.96);
+\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{fillColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (615.57,158.94) circle (  1.96);
 \definecolor{drawColor}{RGB}{51,34,136}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (491.57,459.96) circle (  1.96);
-\definecolor{drawColor}{RGB}{170,68,153}
-\definecolor{fillColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (486.46,467.91) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (612.00,500.16) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (597.24,492.49) circle (  1.96);
 \definecolor{drawColor}{RGB}{51,34,136}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (503.86,433.44) circle (  1.96);
-\definecolor{drawColor}{RGB}{170,68,153}
-\definecolor{fillColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (499.95,441.40) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (611.31,475.88) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (609.92,470.77) circle (  1.96);
+\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{fillColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (609.46,465.65) circle (  1.96);
 \definecolor{drawColor}{RGB}{51,34,136}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (500.27,406.93) circle (  1.96);
-\definecolor{drawColor}{RGB}{170,68,153}
-\definecolor{fillColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (504.19,414.88) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (613.84,450.32) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (622.84,445.21) circle (  1.96);
+\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{fillColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (620.18,440.09) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (626.18,423.48) circle (  1.96);
+\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{fillColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (630.10,415.81) circle (  1.96);
 \definecolor{drawColor}{RGB}{51,34,136}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (497.55,327.38) circle (  1.96);
-\definecolor{drawColor}{RGB}{170,68,153}
-\definecolor{fillColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.11,335.33) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (637.13,399.20) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (635.75,394.09) circle (  1.96);
+\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{fillColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (632.52,388.98) circle (  1.96);
 \definecolor{drawColor}{RGB}{51,34,136}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (484.29,300.86) circle (  1.96);
-\definecolor{drawColor}{RGB}{170,68,153}
-\definecolor{fillColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (476.46,308.82) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (603.93,373.64) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (613.84,368.53) circle (  1.96);
+\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{fillColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (610.50,363.42) circle (  1.96);
 \definecolor{drawColor}{RGB}{51,34,136}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (440.36,115.25) circle (  1.96);
-\definecolor{drawColor}{RGB}{170,68,153}
-\definecolor{fillColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (438.84,123.21) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (623.87,348.08) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (611.54,342.97) circle (  1.96);
+\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{fillColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (617.53,337.86) circle (  1.96);
 \definecolor{drawColor}{RGB}{51,34,136}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (484.29,274.35) circle (  1.96);
-\definecolor{drawColor}{RGB}{170,68,153}
-\definecolor{fillColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (502.01,282.30) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (563.01,118.04) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (556.21,112.93) circle (  1.96);
+\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{fillColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (570.50,107.82) circle (  1.96);
 \definecolor{drawColor}{RGB}{51,34,136}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (487.55,247.83) circle (  1.96);
-\definecolor{drawColor}{RGB}{170,68,153}
-\definecolor{fillColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.86,255.79) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (625.95,296.96) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (620.99,291.85) circle (  1.96);
+\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{fillColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (608.89,286.74) circle (  1.96);
 \definecolor{drawColor}{RGB}{51,34,136}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (503.21,221.32) circle (  1.96);
-\definecolor{drawColor}{RGB}{170,68,153}
-\definecolor{fillColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (502.12,229.27) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (614.31,271.40) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (614.65,266.29) circle (  1.96);
+\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{fillColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (609.69,261.18) circle (  1.96);
 \definecolor{drawColor}{RGB}{51,34,136}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.75,194.80) circle (  1.96);
-\definecolor{drawColor}{RGB}{170,68,153}
-\definecolor{fillColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (498.86,202.75) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (619.95,245.84) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (625.37,240.73) circle (  1.96);
+\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{fillColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (628.14,235.62) circle (  1.96);
 \definecolor{drawColor}{RGB}{51,34,136}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (481.24,168.28) circle (  1.96);
-\definecolor{drawColor}{RGB}{170,68,153}
-\definecolor{fillColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (493.42,176.24) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (622.95,219.00) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (623.41,211.34) circle (  1.96);
 \definecolor{drawColor}{RGB}{51,34,136}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (485.27, 88.74) circle (  1.96);
-\definecolor{drawColor}{RGB}{170,68,153}
-\definecolor{fillColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (462.65, 96.69) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (612.58,194.72) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (613.15,189.61) circle (  1.96);
+\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{fillColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (609.35,184.50) circle (  1.96);
+\definecolor{drawColor}{RGB}{51,34,136}
+\definecolor{fillColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (583.18, 92.48) circle (  1.96);
+\definecolor{drawColor}{RGB}{17,119,51}
+\definecolor{fillColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (599.20, 87.37) circle (  1.96);
+\definecolor{drawColor}{RGB}{221,204,119}
+\definecolor{fillColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (604.39, 82.26) circle (  1.96);
 \definecolor{drawColor}{RGB}{169,169,169}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (401.21,159.00) -- (520.82,159.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (401.21,132.49) -- (520.82,132.49);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (518.63,176.83) -- (645.43,176.83);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (518.63,151.27) -- (645.43,151.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (518.63,125.71) -- (645.43,125.71);
 \definecolor{drawColor}{gray}{0.20}
 
-\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] (401.21, 76.80) rectangle (520.82,506.36);
-\end{scope}
-\begin{scope}
-\path[clip] (525.82, 76.80) rectangle (645.43,506.36);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (525.82, 76.80) rectangle (645.43,506.36);
-\definecolor{drawColor}{gray}{0.92}
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (544.85, 76.80) --
-	(544.85,506.36);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (572.03, 76.80) --
-	(572.03,506.36);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (599.22, 76.80) --
-	(599.22,506.36);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (626.40, 76.80) --
-	(626.40,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82, 92.71) --
-	(645.43, 92.71);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,119.23) --
-	(645.43,119.23);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,145.75) --
-	(645.43,145.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,172.26) --
-	(645.43,172.26);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,198.78) --
-	(645.43,198.78);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,225.29) --
-	(645.43,225.29);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,251.81) --
-	(645.43,251.81);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,278.33) --
-	(645.43,278.33);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,304.84) --
-	(645.43,304.84);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,331.36) --
-	(645.43,331.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,357.87) --
-	(645.43,357.87);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,384.39) --
-	(645.43,384.39);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,410.91) --
-	(645.43,410.91);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,437.42) --
-	(645.43,437.42);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,463.94) --
-	(645.43,463.94);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (525.82,490.45) --
-	(645.43,490.45);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (531.26, 76.80) --
-	(531.26,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (558.44, 76.80) --
-	(558.44,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (585.63, 76.80) --
-	(585.63,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (612.81, 76.80) --
-	(612.81,506.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (639.99, 76.80) --
-	(639.99,506.36);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (625.31,148.40) --
-	(625.31,151.05);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (625.31,149.72) --
-	(614.01,149.72);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (614.01,148.40) --
-	(614.01,151.05);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (624.77,140.44) --
-	(624.77,143.09);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (624.77,141.77) --
-	(610.20,141.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (610.20,140.44) --
-	(610.20,143.09);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (612.59,493.10) --
-	(612.59,495.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (612.59,494.43) --
-	(593.46,494.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (593.46,493.10) --
-	(593.46,495.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (616.07,466.59) --
-	(616.07,469.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (616.07,467.91) --
-	(608.35,467.91);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (608.35,466.59) --
-	(608.35,469.24);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (621.07,458.63) --
-	(621.07,461.29);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (621.07,459.96) --
-	(601.94,459.96);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (601.94,458.63) --
-	(601.94,461.29);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (625.21,440.07) --
-	(625.21,442.72);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (625.21,441.40) --
-	(621.29,441.40);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (621.29,440.07) --
-	(621.29,442.72);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (628.47,432.12) --
-	(628.47,434.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (628.47,433.44) --
-	(619.12,433.44);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (619.12,432.12) --
-	(619.12,434.77);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (630.53,413.56) --
-	(630.53,416.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (630.53,414.88) --
-	(624.23,414.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (624.23,413.56) --
-	(624.23,416.21);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (634.99,405.60) --
-	(634.99,408.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (634.99,406.93) --
-	(627.05,406.93);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (627.05,405.60) --
-	(627.05,408.25);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (637.82,387.04) --
-	(637.82,389.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (637.82,388.37) --
-	(635.21,388.37);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (635.21,387.04) --
-	(635.21,389.69);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (636.95,379.09) --
-	(636.95,381.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (636.95,380.41) --
-	(629.55,380.41);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (629.55,379.09) --
-	(629.55,381.74);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (616.40,360.52) --
-	(616.40,363.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (616.40,361.85) --
-	(612.05,361.85);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (612.05,360.52) --
-	(612.05,363.18);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (622.16,352.57) --
-	(622.16,355.22);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (622.16,353.90) --
-	(602.81,353.90);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (602.81,352.57) --
-	(602.81,355.22);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (620.64,334.01) --
-	(620.64,336.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (620.64,335.33) --
-	(607.26,335.33);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (607.26,334.01) --
-	(607.26,336.66);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (636.41,326.05) --
-	(636.41,328.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (636.41,327.38) --
-	(601.83,327.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (601.83,326.05) --
-	(601.83,328.71);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (563.55,121.88) --
-	(563.55,124.53);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (563.55,123.21) --
-	(560.73,123.21);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (560.73,121.88) --
-	(560.73,124.53);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (579.10,113.93) --
-	(579.10,116.58);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (579.10,115.25) --
-	(570.29,115.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (570.29,113.93) --
-	(570.29,116.58);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (626.08,280.98) --
-	(626.08,283.63);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (626.08,282.30) --
-	(621.83,282.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (621.83,280.98) --
-	(621.83,283.63);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (626.18,273.02) --
-	(626.18,275.67);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (626.18,274.35) --
-	(595.63,274.35);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (595.63,273.02) --
-	(595.63,275.67);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (619.12,254.46) --
-	(619.12,257.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (619.12,255.79) --
-	(613.57,255.79);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (613.57,254.46) --
-	(613.57,257.11);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (625.42,246.51) --
-	(625.42,249.16);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (625.42,247.83) --
-	(598.02,247.83);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (598.02,246.51) --
-	(598.02,249.16);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (628.36,227.95) --
-	(628.36,230.60);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (628.36,229.27) --
-	(624.23,229.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (624.23,227.95) --
-	(624.23,230.60);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (631.95,219.99) --
-	(631.95,222.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (631.95,221.32) --
-	(626.29,221.32);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (626.29,219.99) --
-	(626.29,222.64);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (626.08,196.13) --
-	(626.08,201.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (626.08,198.78) --
-	(623.03,198.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (623.03,196.13) --
-	(623.03,201.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (617.49,174.91) --
-	(617.49,177.56);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (617.49,176.24) --
-	(612.27,176.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (612.27,174.91) --
-	(612.27,177.56);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (618.25,166.96) --
-	(618.25,169.61);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (618.25,168.28) --
-	(604.44,168.28);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (604.44,166.96) --
-	(604.44,169.61);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (602.15, 95.37) --
-	(602.15, 98.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (602.15, 96.69) --
-	(594.76, 96.69);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (594.76, 95.37) --
-	(594.76, 98.02);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (611.61, 87.41) --
-	(611.61, 90.06);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (611.61, 88.74) --
-	(601.72, 88.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (601.72, 87.41) --
-	(601.72, 90.06);
-\definecolor{drawColor}{RGB}{17,119,51}
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (619.66,149.72) circle (  1.96);
-\definecolor{drawColor}{RGB}{221,204,119}
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (617.49,141.77) circle (  1.96);
-\definecolor{drawColor}{RGB}{17,119,51}
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (603.02,494.43) circle (  1.96);
-\definecolor{drawColor}{RGB}{221,204,119}
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (597.59,486.48) circle (  1.96);
-\definecolor{drawColor}{RGB}{17,119,51}
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (612.27,467.91) circle (  1.96);
-\definecolor{drawColor}{RGB}{221,204,119}
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (611.50,459.96) circle (  1.96);
-\definecolor{drawColor}{RGB}{17,119,51}
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (623.25,441.40) circle (  1.96);
-\definecolor{drawColor}{RGB}{221,204,119}
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (623.79,433.44) circle (  1.96);
-\definecolor{drawColor}{RGB}{17,119,51}
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (627.38,414.88) circle (  1.96);
-\definecolor{drawColor}{RGB}{221,204,119}
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (630.97,406.93) circle (  1.96);
-\definecolor{drawColor}{RGB}{17,119,51}
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (636.51,388.37) circle (  1.96);
-\definecolor{drawColor}{RGB}{221,204,119}
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (633.25,380.41) circle (  1.96);
-\definecolor{drawColor}{RGB}{17,119,51}
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (614.22,361.85) circle (  1.96);
-\definecolor{drawColor}{RGB}{221,204,119}
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (612.48,353.90) circle (  1.96);
-\definecolor{drawColor}{RGB}{17,119,51}
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (613.90,335.33) circle (  1.96);
-\definecolor{drawColor}{RGB}{221,204,119}
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (619.12,327.38) circle (  1.96);
-\definecolor{drawColor}{RGB}{17,119,51}
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (562.14,123.21) circle (  1.96);
-\definecolor{drawColor}{RGB}{221,204,119}
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (574.75,115.25) circle (  1.96);
-\definecolor{drawColor}{RGB}{17,119,51}
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (623.90,282.30) circle (  1.96);
-\definecolor{drawColor}{RGB}{221,204,119}
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (610.96,274.35) circle (  1.96);
-\definecolor{drawColor}{RGB}{17,119,51}
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (616.29,255.79) circle (  1.96);
-\definecolor{drawColor}{RGB}{221,204,119}
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (611.72,247.83) circle (  1.96);
-\definecolor{drawColor}{RGB}{17,119,51}
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (626.29,229.27) circle (  1.96);
-\definecolor{drawColor}{RGB}{221,204,119}
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (629.12,221.32) circle (  1.96);
-\definecolor{drawColor}{RGB}{17,119,51}
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (624.55,198.78) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (614.88,176.24) circle (  1.96);
-\definecolor{drawColor}{RGB}{221,204,119}
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (611.40,168.28) circle (  1.96);
-\definecolor{drawColor}{RGB}{17,119,51}
-\definecolor{fillColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (598.46, 96.69) circle (  1.96);
-\definecolor{drawColor}{RGB}{221,204,119}
-\definecolor{fillColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (606.72, 88.74) circle (  1.96);
-\definecolor{drawColor}{RGB}{169,169,169}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (525.82,159.00) -- (645.43,159.00);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (525.82,132.49) -- (645.43,132.49);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] (525.82, 76.80) rectangle (645.43,506.36);
-\end{scope}
-\begin{scope}
-\path[clip] (152.00,506.36) rectangle (271.61,521.43);
+\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] (518.63, 72.04) rectangle (645.43,511.66);
+\end{scope}
+\begin{scope}
+\path[clip] (123.21,511.66) rectangle (250.02,524.61);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (152.00,506.36) rectangle (271.61,521.43);
+\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (123.21,511.66) rectangle (250.02,524.61);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (211.80,511.14) {All};
-\end{scope}
-\begin{scope}
-\path[clip] (276.61,506.36) rectangle (396.21,521.43);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (186.62,516.21) {All};
+\end{scope}
+\begin{scope}
+\path[clip] (255.02,511.66) rectangle (381.82,524.61);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (276.61,506.36) rectangle (396.21,521.43);
+\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (255.02,511.66) rectangle (381.82,524.61);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (336.41,511.14) {By gender};
-\end{scope}
-\begin{scope}
-\path[clip] (401.21,506.36) rectangle (520.82,521.43);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (318.42,516.21) {By gender};
+\end{scope}
+\begin{scope}
+\path[clip] (386.82,511.66) rectangle (513.63,524.61);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (401.21,506.36) rectangle (520.82,521.43);
+\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (386.82,511.66) rectangle (513.63,524.61);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (461.02,511.14) {By education};
-\end{scope}
-\begin{scope}
-\path[clip] (525.82,506.36) rectangle (645.43,521.43);
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (450.22,516.21) {By education};
+\end{scope}
+\begin{scope}
+\path[clip] (518.63,511.66) rectangle (645.43,524.61);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (525.82,506.36) rectangle (645.43,521.43);
+\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (518.63,511.66) rectangle (645.43,524.61);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (585.63,511.14) {By age};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (582.03,516.21) {By age};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round] (157.44, 74.30) --
-	(157.44, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (184.62, 74.30) --
-	(184.62, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (211.80, 74.30) --
-	(211.80, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (238.99, 74.30) --
-	(238.99, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (266.17, 74.30) --
-	(266.17, 76.80);
+\path[draw=drawColor,line width= 0.5pt,line join=round] (128.98, 69.54) --
+	(128.98, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (157.80, 69.54) --
+	(157.80, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (186.62, 69.54) --
+	(186.62, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (215.44, 69.54) --
+	(215.44, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (244.25, 69.54) --
+	(244.25, 72.04);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (157.44, 66.79) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (184.62, 66.79) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (211.80, 66.79) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (238.99, 66.79) {75};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (266.17, 66.79) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (128.98, 63.68) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (157.80, 63.68) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (186.62, 63.68) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (215.44, 63.68) {75};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (244.25, 63.68) {100};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round] (282.04, 74.30) --
-	(282.04, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (309.23, 74.30) --
-	(309.23, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (336.41, 74.30) --
-	(336.41, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (363.59, 74.30) --
-	(363.59, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (390.78, 74.30) --
-	(390.78, 76.80);
+\path[draw=drawColor,line width= 0.5pt,line join=round] (260.78, 69.54) --
+	(260.78, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (289.60, 69.54) --
+	(289.60, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (318.42, 69.54) --
+	(318.42, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (347.24, 69.54) --
+	(347.24, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (376.06, 69.54) --
+	(376.06, 72.04);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (282.04, 66.79) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (309.23, 66.79) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (336.41, 66.79) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (363.59, 66.79) {75};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (390.78, 66.79) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (260.78, 63.68) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (289.60, 63.68) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (318.42, 63.68) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (347.24, 63.68) {75};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (376.06, 63.68) {100};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round] (406.65, 74.30) --
-	(406.65, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (433.84, 74.30) --
-	(433.84, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (461.02, 74.30) --
-	(461.02, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (488.20, 74.30) --
-	(488.20, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (515.39, 74.30) --
-	(515.39, 76.80);
+\path[draw=drawColor,line width= 0.5pt,line join=round] (392.59, 69.54) --
+	(392.59, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (421.41, 69.54) --
+	(421.41, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (450.22, 69.54) --
+	(450.22, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (479.04, 69.54) --
+	(479.04, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (507.86, 69.54) --
+	(507.86, 72.04);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (406.65, 66.79) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (433.84, 66.79) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (461.02, 66.79) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (488.20, 66.79) {75};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (515.39, 66.79) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (392.59, 63.68) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (421.41, 63.68) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (450.22, 63.68) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (479.04, 63.68) {75};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (507.86, 63.68) {100};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round] (531.26, 74.30) --
-	(531.26, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (558.44, 74.30) --
-	(558.44, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (585.63, 74.30) --
-	(585.63, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (612.81, 74.30) --
-	(612.81, 76.80);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (639.99, 74.30) --
-	(639.99, 76.80);
+\path[draw=drawColor,line width= 0.5pt,line join=round] (524.39, 69.54) --
+	(524.39, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (553.21, 69.54) --
+	(553.21, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (582.03, 69.54) --
+	(582.03, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (610.85, 69.54) --
+	(610.85, 72.04);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (639.67, 69.54) --
+	(639.67, 72.04);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (531.26, 66.79) {0};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (558.44, 66.79) {25};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (585.63, 66.79) {50};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (612.81, 66.79) {75};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (639.99, 66.79) {100};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (524.39, 63.68) {0};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (553.21, 63.68) {25};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (582.03, 63.68) {50};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (610.85, 63.68) {75};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (639.67, 63.68) {100};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33, 94.28) {USA};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33, 85.64) {(National, 1959)};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,120.79) {Russia};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,112.15) {(Subnational, 61 regions, 22125)};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,142.99) {All LMICs};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,173.83) {Uganda 2};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,165.19) {(Subnational, 1 district, 1366)};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,200.34) {Uganda 1};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,191.70) {(Subnational, 13 districts, 3362)};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,226.86) {Sierra Leone 2};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,218.22) {(National, 2110)};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,253.37) {Sierra Leone 1};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,244.73) {(National, 1070)};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,279.89) {Rwanda};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,271.25) {(National, 1355)};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,306.41) {Pakistan 2};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,297.77) {(Subnational, 1 province, 1492)};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,332.92) {Pakistan 1};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,324.28) {(Subnational, 2 districts, 1633)};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,359.44) {Nigeria};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,350.80) {(Subnational, 1 state, 1868)};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,385.95) {Nepal};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,377.31) {(Subnational, 2 districts, 1389)};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,412.47) {Mozambique};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,403.83) {(Subnational, 2 cities, 862)};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,438.99) {India};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,430.35) {(Subnational, Slums in 2 cities, 3348)};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,465.50) {Colombia};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,456.86) {(National, 1012)};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,492.02) {Burkina Faso};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 16.33,483.38) {(National, 977)};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68, 89.76) {USA};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68, 81.12) {(National, 1959)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,115.32) {Russia};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,106.68) {(Subnational, 61 regions, 22125)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,140.88) {All LMICs};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,132.24) {(National samples)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,162.12) {All LMICs};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,192.00) {Uganda 2};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,183.36) {(Subnational, 1 district, 1366)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,217.56) {Uganda 1};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,208.92) {(Subnational, 13 districts, 3362)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,243.12) {Sierra Leone 2};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,234.48) {(National, 2110)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,268.68) {Sierra Leone 1};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,260.04) {(National, 1070)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,294.24) {Rwanda};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,285.60) {(National, 1355)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,319.80) {Pakistan 2};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,311.16) {(Subnational, 1 province, 1492)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,345.36) {Pakistan 1};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,336.72) {(Subnational, 2 districts, 1633)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,370.92) {Nigeria};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,362.28) {(Subnational, 1 state, 1868)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,396.48) {Nepal};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,387.84) {(Subnational, 2 districts, 1389)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,422.04) {Mozambique};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,413.40) {(Subnational, 2 cities, 862)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,447.60) {India};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,438.96) {(Subnational, Slums in 2 cities, 1680)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,473.16) {Colombia};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,464.52) {(National, 1012)};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,498.72) {Burkina Faso};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 13.68,490.08) {(National, 977)};
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50, 92.71) --
-	(152.00, 92.71);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,119.23) --
-	(152.00,119.23);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,145.75) --
-	(152.00,145.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,172.26) --
-	(152.00,172.26);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,198.78) --
-	(152.00,198.78);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,225.29) --
-	(152.00,225.29);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,251.81) --
-	(152.00,251.81);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,278.33) --
-	(152.00,278.33);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,304.84) --
-	(152.00,304.84);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,331.36) --
-	(152.00,331.36);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,357.87) --
-	(152.00,357.87);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,384.39) --
-	(152.00,384.39);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,410.91) --
-	(152.00,410.91);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,437.42) --
-	(152.00,437.42);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,463.94) --
-	(152.00,463.94);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (149.50,490.45) --
-	(152.00,490.45);
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71, 87.37) --
+	(123.21, 87.37);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,112.93) --
+	(123.21,112.93);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,138.49) --
+	(123.21,138.49);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,164.05) --
+	(123.21,164.05);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,189.61) --
+	(123.21,189.61);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,215.17) --
+	(123.21,215.17);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,240.73) --
+	(123.21,240.73);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,266.29) --
+	(123.21,266.29);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,291.85) --
+	(123.21,291.85);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,317.41) --
+	(123.21,317.41);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,342.97) --
+	(123.21,342.97);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,368.53) --
+	(123.21,368.53);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,394.09) --
+	(123.21,394.09);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,419.65) --
+	(123.21,419.65);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,445.21) --
+	(123.21,445.21);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,470.77) --
+	(123.21,470.77);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (120.71,496.33) --
+	(123.21,496.33);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (398.71, 55.85) {estimate};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (384.32, 55.27) {estimate};
 \end{scope}
@@
 
-\path[fill=fillColor] (258.71,  5.00) rectangle (538.72, 43.91);
+\path[fill=fillColor] (256.56,  5.00) rectangle (512.09, 43.91);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (263.71, 21.01) {Subgroups};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (261.56, 22.04) {Subgroups};
 \end{scope}
@@
 
-\path[fill=fillColor] (314.33, 24.45) rectangle (328.79, 38.91);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
-\definecolor{drawColor}{RGB}{153,153,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (315.78, 31.68) -- (327.34, 31.68);
+\path[fill=fillColor] (302.90, 24.45) rectangle (317.35, 38.91);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (304.34, 31.68) -- (315.90, 31.68);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{136,34,85}
+\definecolor{fillColor}{RGB}{136,34,85}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (310.12, 31.68) circle (  1.96);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (302.90, 10.00) rectangle (317.35, 24.45);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{153,153,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (304.34, 17.23) -- (315.90, 17.23);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (321.56, 31.68) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (310.12, 17.23) circle (  1.96);
 \end{scope}
@@
 
-\path[fill=fillColor] (314.33, 10.00) rectangle (328.79, 24.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
-\definecolor{drawColor}{RGB}{68,170,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (315.78, 17.23) -- (327.34, 17.23);
+\path[fill=fillColor] (346.90, 24.45) rectangle (361.35, 38.91);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{68,170,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.35, 31.68) -- (359.91, 31.68);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (321.56, 17.23) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (354.13, 31.68) circle (  1.96);
 \end{scope}
@@
 
-\path[fill=fillColor] (363.34, 24.45) rectangle (377.79, 38.91);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
-\definecolor{drawColor}{RGB}{170,68,153}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (364.78, 31.68) -- (376.35, 31.68);
+\path[fill=fillColor] (346.90, 10.00) rectangle (361.35, 24.45);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{170,68,153}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (348.35, 17.23) -- (359.91, 17.23);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (370.56, 31.68) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (354.13, 17.23) circle (  1.96);
 \end{scope}
@@
 
-\path[fill=fillColor] (363.34, 10.00) rectangle (377.79, 24.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
-\definecolor{drawColor}{RGB}{51,34,136}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (364.78, 17.23) -- (376.35, 17.23);
+\path[fill=fillColor] (431.22, 24.45) rectangle (445.68, 38.91);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{51,34,136}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (432.67, 31.68) -- (444.23, 31.68);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (370.56, 17.23) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (438.45, 31.68) circle (  1.96);
 \end{scope}
@@
 
-\path[fill=fillColor] (462.93, 24.45) rectangle (477.38, 38.91);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
-\definecolor{drawColor}{RGB}{17,119,51}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.37, 31.68) -- (475.94, 31.68);
+\path[fill=fillColor] (431.22, 10.00) rectangle (445.68, 24.45);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{17,119,51}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (432.67, 17.23) -- (444.23, 17.23);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (470.16, 31.68) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (438.45, 17.23) circle (  1.96);
 \end{scope}
@@
 
-\path[fill=fillColor] (462.93, 10.00) rectangle (477.38, 24.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
-\definecolor{drawColor}{RGB}{221,204,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (464.37, 17.23) -- (475.94, 17.23);
+\path[fill=fillColor] (476.35, 24.45) rectangle (490.80, 38.91);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{221,204,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (477.79, 31.68) -- (489.35, 31.68);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (470.16, 17.23) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (483.57, 31.68) circle (  1.96);
 \end{scope}
@@
 
-\path[fill=fillColor] (503.83, 24.45) rectangle (518.28, 38.91);
+\path[fill=fillColor] (476.35, 10.00) rectangle (490.80, 24.45);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (505.27, 31.68) -- (516.84, 31.68);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (477.79, 17.23) -- (489.35, 17.23);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (511.05, 31.68) circle (  1.96);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (483.57, 17.23) circle (  1.96);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (333.79, 28.93) {Female};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (322.35, 29.75) {Female};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (333.79, 14.47) {Male};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (322.35, 15.30) {Male};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (382.79, 28.93) {Up to Secondary};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (366.35, 29.75) {Up to Secondary};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (382.79, 14.47) {More than Secondary};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (366.35, 15.30) {More than Secondary};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (482.38, 28.93) {$< 55$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (450.68, 29.75) {$< 25$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (482.38, 14.47) {$55 +$};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (450.68, 15.30) {$25-54$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (523.28, 28.93) {All};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (495.80, 29.75) {$55 +$};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.20] at (  5.00,528.76) {If a COVID-19 vaccine becomes available in [country], would you take it?};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (495.80, 15.30) {All};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (650.43,542.02);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.20] at (  5.00,531.24) {If a COVID-19 vaccine becomes available in [country], would you take it?};
 \end{scope}

### 2021-06-22 2_tables.R

@@ -1,2295 +1,0 @@
-#' ---
-#' title: 'COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging: Replication Code'
-#' date: "30 April 2021"
-#' output:
-#'   html_document:
-#'     number_sections: yes
-#'     theme: cosmo
-#'     code_folding: hide
-#'     toc: yes
-#'   bookdown::html_document2: default
-#' ---
-#' 
-## ----setup3, include=FALSE----------------------------------------------------
-knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
-
-if (!require(pacman)) install.packages("pacman")
-
-pacman::p_load(tidyverse, magrittr, knitr, kableExtra, DT, lazyeval, 
-               labelled, forcats, readxl, googledrive, estimatr, ggforce, fastDummies,
-               stringr, RColorBrewer, readstata13, metaplus, sjlabelled, ggrepel, tikzDevice)
-
-options(knitr.kable.NA = '.')
-
-base_font_size <- 12
-
-
-#' 
-#' 
-#' # Set up
-#' 
-#' This code takes cleaned and aggregated data as input. Cleaning and aggregation is done in `1_cleaning.Rmd`.
-#' 
-#' ## Helper functions
-#' 
-## -----------------------------------------------------------------------------
-
-# The helper renormalizes weights so that each study gets the 
-# same total weight even if they are missing data
-
-study_weighting <- function(data)
-  data %>% 
-    dplyr::group_by(country) %>% 
-    dplyr::mutate(weight = weight/sum(weight)) %>% 
-    dplyr::ungroup() 
-
-lm_helper <- function(data,...) {
-  data %>% 
-    study_weighting() %>% 
-    estimatr::lm_robust(data = .,...) %>% 
-    {bind_cols( tidy(.), n = nobs(.) )}
-}
-
-# Subgroup analysis : Function to apply analysis function over groups
-
-grp_analysis <- function(df, y, x)
-  
-  df %>%
-    dplyr::filter(if_all(c(all_of(x), all_of(y), cluster, weight), ~ !is.na(.))) %>%
-    dplyr::nest_by(group, get(x)) %>%
-    dplyr::summarize(
-      lm_helper(data = data, 
-                formula = as.formula(paste0(y, "~ 1")), cluster = cluster,
-                weight = weight, se_type = "stata"), .groups = "drop") %>% 
-    dplyr::rename(!!x := "get(x)")
-  
-
-
[…]

### 2021-06-22 paper.Rmd
update

--- 2021-03-23 paper.Rmd
@@
 ---
-title: "COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging"
-author:
-- name: Julio S. Solís Arce, BA^[First author]
-  affiliation: WZB Berlin Social Science Center
-  number: 1
-- name: Shana S. Warren, PhD\(^*\)
-  affiliation: Innovations for Poverty Action (IPA)
-  number: 2
-- name: Niccoló F. Meriggi, MSc\(^*\)
-  affiliation: International Growth Centre (IGC)
-  number: 3
-- name: Alexandra Scacco, PhD\(^*\)
-  number: 1
-- name: Nina McMurry, PhD\(^*\)
-  number: 1
-- name: Maarten Voors, PhD\(^*\)
-  affiliation: Wageningen University & Research
-  number: 4
-- name: Georgiy Syunyaev, MPhil\(^*\)
-  affiliation: International Center for the Study of Institutions and Development (HSE University, Moscow, Russia)
-  number: [1, ", ", 5, ", ",  24]
-- name: Amyn Abdul Malik, PhD\(^*\)
-  affiliation: Yale Institute for Global Health
-  number: 6
-- name: Samya Aboutajdine, MA
-  number: 3
-- name: Alex Armand, PhD
-  affiliation: Nova School of Business and Economics
-  number: 7
-- name: Saher Asad, PhD
-  affiliation: Lahore University of Management Sciences
-  number: 8
-- name: Britta Augsburg, PhD
-  affiliation: The Institute for Fiscal Studies
-  number: 9
-- name: Antonella Bancalari, PhD
-  affiliation: University of St. Andrews & The Institute for Fiscal Studies
-  number: 10
-- name: Martina Björkman Nyqvist, PhD
-  affiliation: Stockholm School of Economics and Misum
-  number: 11
-- name: Ekaterina Borisova, PhD
-  affiliation: Economics Department of Ghent University
-  number: [5, ", ", 12]
-- name: Constantin Manuel Bosancianu, PhD
-  number: 1
-- name: Ali Cheema, PhD
-  affiliation: Institute of Development and Economic Alternatives
-  number: [8, ", ", 13]
-- name: Elliott Collins, PhD
-  number: 2
-- name: Ahsan Zia Farooqi, MA
-  number: 13
-- name: Mattia Fracchia, MA
-  number: 7
-- name: Andrea Guariso, PhD
-  affiliation: Trinity College Dublin
-  number: 14
-- name: Ali Hasanain, PhD
-  number: 8
-- name: Anthony Kamwesigye, BSc
-  number: 2
-- name: Sarah Kreps, PhD
-  affiliation: Cornell University
-  number: 15
-- name: Madison Levine, MSc
-  number: 4 
-- name: Rebecca Littman, PhD
-  affiliation: University of Illinois Chicago
-  number: 16
-- name: Melina Platas, PhD
-  affiliation: NYU Abu Dhabi
-  number: 17
-- name: Vasudha Ramakrishna, MSc
-  affiliation: Yale Research Initiative on Innovation and Scale (Y-RISE)
-  number: 18
-- name: Jacob N. Shapiro, PhD
-  affiliation: Princeton University
-  number: 19
-- name: Jakob Svensson, PhD
-  affiliation: Institute for International Economic Studies (IIES), Stockholm University
-  number: 20
-- name: Corey Vernot, BS
-  number: 18
-- name: Pedro C. Vicente, PhD
-  number: 7
-- name: Laurin B Weissinger, DPhil
-  affiliation: Tufts University
-  number: 21
-- name: Baobao Zhang, PhD
-  number: 15
-- name: Dean Karlan, PhD^[Last author]
-  affiliation: Kellogg School of Management at Northwestern University
-  number: [2, ", ", 22]
-- name: Michael Callen, PhD\(^\dagger\)
-  affiliation: London School of Economics
-  number: [3, ", ", 23]
-- name: Matthieu Teachout, PhD\(^\dagger\)
-  number: 3
-- name: Macartan Humphreys, PhD\(^\dagger\)
-  affiliation: Columbia University
-  number: [1, ", ", 24]
-- name: Saad B. Omer, PhD^[Corresponding author. 1 Church Street, New Haven, CT 06510. Phone  203 432 3656.  Email  \href{mailto:saad.omer@yale.edu}{saad.omer@yale.edu}]
-  number: 6
-- name: Ahmed Mushfiq Mobarak, PhD^[Corresponding author. 165 Whitney Avenue, New Haven, CT 06520-8200. Phone 203 432 5787. Email  \href{mailto:ahmed.mobarak@yale.edu}{ahmed.mobarak@yale.edu}]
-  affiliation: Yale University
-  number: 25
+title: "COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries"
 output: 
@@
     keep_tex: true
+    latex_engine: xelatex
     pandoc_args:
@@
       mathptmx: null
-      fontenc: ["T1"]
   bookdown::word_document2: default
@@
 header-includes:
+  - \setmainfont{Arial}
+  - \renewcommand{\familydefault}{\sfdefault}
   - \usepackage{titlesec}
+  - \usepackage{hyperref}
   - \titleformat*{\subsection}{\normalsize\bfseries}
   - \titleformat*{\section}{\large\bfseries}
+  - \usepackage{float} \floatplacement{figure}{H} 
+  - \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 # linestretch: 1.5
@@
 
-googledrive::drive_download(file = "NatureMedicine Covid vaccine hesitancy", 
+googledrive::drive_download(file = "NatureMedicine Covid vaccine hesitancy FINAL", 
                             path = "4_paper_supplementary_files/Intro Vaccine.txt", overwrite = TRUE)
@@
 
+options( tikzDefaultEngine = 'xetex',
+         tikzXelatexPackages = c(getOption("tikzXelatexPackages"),
+                                 "\\setmainfont{Arial}\n"),
+         tikzDocumentDeclaration = "% !TEX program = xelatex\n
+\\documentclass[fontsize=7pt,DIV=calc]{scrartcl}\n")
+
 ```

### 2021-06-22 paper.tex
no google drive
paper
update

@@
 \hypersetup{
-  pdftitle={COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging},
+  pdftitle={COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries},
   colorlinks=true,
@@
 \setcounter{secnumdepth}{5}
+\setmainfont{Arial}
+\renewcommand{\familydefault}{\sfdefault}
 \usepackage{titlesec}
+\usepackage{hyperref}
 \titleformat*{\subsection}{\normalsize\bfseries}
 \titleformat*{\section}{\large\bfseries}
+\usepackage{float} \floatplacement{figure}{H}
+\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
 \usepackage[font={bf,normalsize}]{caption}
 \usepackage{mathptmx}
-\usepackage[T1]{fontenc}
 \usepackage{booktabs}
@@
 \usepackage{makecell}
+\usepackage{xcolor}
 \ifLuaTeX
@@
 
-\title{COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging}
-    \usepackage{authblk}
-    \renewcommand\Authfont{\fontsize{10}{14.4}\selectfont}
-    \renewcommand\Affilfont{\fontsize{8.5}{10.8}\itshape}
-                                        \author[1]{Julio S. Solís Arce, BA\footnote{First author}}
-                                                            \affil{WZB Berlin Social Science Center}
-                                                                                \author[2]{Shana S. Warren, PhD\(^*\)}
-                                                            \affil{Innovations for Poverty Action (IPA)}
-                                                                                \author[3]{Niccoló F. Meriggi, MSc\(^*\)}
-                                                            \affil{International Growth Centre (IGC)}
-                                                                                \author[1]{Alexandra Scacco, PhD\(^*\)}
-                                                                            \author[1]{Nina McMurry, PhD\(^*\)}
-                                                                            \author[4]{Maarten Voors, PhD\(^*\)}
-                                                            \affil{Wageningen University \& Research}
-                                                                                \author[1,5,24]{Georgiy Syunyaev, MPhil\(^*\)}
-                                                            \affil{International Center for the Study of Institutions and Development (HSE University, Moscow, Russia)}
-                                                                                \author[6]{Amyn Abdul Malik, PhD\(^*\)}
-                                                            \affil{Yale Institute for Global Health}
-                                                                                \author[3]{Samya Aboutajdine, MA}
-                                                                            \author[7]{Alex Armand, PhD}
-                                                            \affil{Nova School of Business and Economics}
-                                                                                \author[8]{Saher Asad, PhD}
-                                                            \affil{Lahore University of Management Sciences}
-                                                                                \author[9]{Britta Augsburg, PhD}
-                                                            \affil{The Institute for Fiscal Studies}
-                                                                                \author[10]{Antonella Bancalari, PhD}
-                                                            \affil{University of St.~Andrews \& The Institute for Fiscal Studies}
-                                                                                \author[11]{Martina Björkman Nyqvist, PhD}
-                                                            \affil{Stockholm School of Economics and Misum}
-                                                                                \author[5,12]{Ekaterina Borisova, PhD}
-                                                            \affil{Economics Department of Ghent University}
-                                                                                \author[1]{Constantin Manuel Bosancianu, PhD}
-                                                                            \author[8,13]{Ali Cheema, PhD}
-                                                            \affil{Institute of Development and Economic Alternatives}
-                                                                                \author[2]{Elliott Collins, PhD}
-                                                                            \author[13]{Ahsan Zia Farooqi, MA}
-                                                                            \author[7]{Mattia Fracchia, MA}
-                                                                            \author[14]{Andrea Guariso, PhD}
-                                                            \affil{Trinity College Dublin}
-                                                                                \author[8]{Ali Hasanain, PhD}
-                                                                            \author[2]{Anthony Kamwesigye, BSc}
-                                                                            \author[15]{Sarah Kreps, PhD}
-                                                            \affil{Cornell University}
-                                                                                \author[4]{Madison Levine, MSc}
-                                                                            \author[16]{Rebecca Littman, PhD}
-                                                            \affil{University of Illinois Chicago}
-                                                                                \author[17]{Melina Platas, PhD}
-                                                            \affil{NYU Abu Dhabi}
-                                                                                \author[18]{Vasudha Ramakrishna, MSc}
-                                                            \affil{Yale Research Initiative on Innovation and Scale (Y-RISE)}
-                                                                                \author[19]{Jacob N. Shapiro, PhD}
-                                                            \affil{Princeton University}
-                                                                                \author[20]{Jakob Svensson, PhD}
-                                                            \affil{Institute for International Economic Studies (IIES), Stockholm University}
-                                                                                \author[18]{Corey Vernot, BS}
-                                                                            \author[7]{Pedro C. Vicente, PhD}
-                                                                            \author[21]{Laurin B Weissinger, DPhil}
-                                                            \affil{Tufts University}
-                                                                                \author[15]{Baobao Zhang, PhD}
-                                                                            \author[2,22]{Dean Karlan, PhD\footnote{Last author}}
-                                                            \affil{Kellogg School of Management at Northwestern University}
-                                                                                \author[3,23]{Michael Callen, PhD\(^\dagger\)}
-                                                            \affil{London School of Economics}
-                                                                                \author[3]{Matthieu Teachout, PhD\(^\dagger\)}
-                                                                            \author[1,24]{Macartan Humphreys, PhD\(^\dagger\)}
-                                                            \affil{Columbia University}
-                                                                                \author[6]{Saad B.
-Omer, PhD\footnote{Corresponding author.
-1 Church Street, New Haven, CT 06510.
-Phone 203 432 3656.
-Email \href{mailto:saad.omer@yale.edu}{saad.omer@yale.edu}}}
-                                                                            \author[25]{Ahmed Mushfiq Mobarak, PhD\footnote{Corresponding author.
-165 Whitney Avenue, New Haven, CT 06520-8200.
-Phone 203 432 5787.
-Email \href{mailto:ahmed.mobarak@yale.edu}{ahmed.mobarak@yale.edu}}}
-                                                            \affil{Yale University}
-                                            \date{}
+\title{COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries}
+\author{}
+\date{\vspace{-2.5em}}
 
@@
 \maketitle
+
+﻿
+
+Julio S.
+Solis Arce,\footnote{WZB Berlin Social Science Center, \(^2\)Innovations for Poverty Action (IPA), \(^3\)International Growth Centre (IGC), \(^4\)Wageningen University \& Research, \(^5\)International Center for the Study of Institutions and Development (HSE University, Moscow, Russia), \(^6\)Columbia University, \(^7\)Yale Institute for Global Health, \(^8\)Busara Center for Behavioral Economics, \(^{10}\)Department of Sociology, University of Lagos, \(^{11}\)Busara Nigeria, \(^{12}\)Agricultural and Rural Development Secretariat, Federal Capital Territory Administration (Abuja, Nigeria), \(^{13}\)Nova School of Business and Economics, \(^{14}\)The Institute for Fiscal Studies, \(^{15}\)Lahore University of Management Sciences, \(^{16}\)Innovations for Poverty Action (IPA) Uganda, \(^{17}\)Morsel Research \& Development, \(^{18}\)University of St.~Andrews, \(^{19}\)Redes Peru, \(^{20}\)Stockholm School of Economics and Misum, \(^{21}\)Ghent University, Department of Economics, \(^{22}\)Innovations for Poverty Action (IPA) Colombia, \(^{23}\)Institute of Development and Economic Alternatives, \(^{24}\)Innovations for Poverty Action (IPA) Sierra Leone,\(^{25}\)NOVAFRICA, \(^{26}\)Trinity College Dublin, \(^{27}\)Institute of Public Administration and Management, University of Sierra Leone, \(^{28}\)Centre for the Study of Labour and Mobility (CESLAM), \(^{29}\)Cornell University, \(^{30}\)University of Illinois Chicago, \(^{31}\)Innovations for Poverty Action (IPA) Rwanda, \(^{32}\)Associação NOVAFRICA para o Desenvolvimento Empresarial e Económico de Moçambique, \(^{33}\)Innovations for Poverty Action (IPA) Burkina Faso, \(^{34}\)NYU Abu Dhabi, \(^{35}\)Centre for Economic Research in Pakistan (CERP), \(^{36}\)Yale Research Initiative on Innovation and Scale (Y-RISE), \(^{37}\)Princeton University, \(^{38}\)Institute for International Economic Studies (IIES), Stockholm University, \(^{39}\)Tufts University, \(^{40}\)University of Michigan, \(^{41}\)Kellogg School of Management at Northwestern University, \(^{42}\)London School of Economics, \(^{43}\)Yale University} Shana S.
+Warren,\(^2\) Niccolò F.
+Meriggi,\(^3\) Alexandra Scacco,\(^1\) Nina McMurry,\(^1\) Maarten Voors,\(^4\) Georgiy Syunyaev,\(^{1,5,6}\), Amyn Abdul Malik,\(^7\) Samya Aboutajdine,\(^3\) Opeyemi Adeojo,\(^{8, 10}\) Deborah Anigo,\(^{11, 12}\) Alex Armand,\(^{13, 14}\) Saher Asad,\(^{15}\) Martin Atyera,\(^{16}\) Britta Augsburg,\(^{14}\) Manisha Awasthi,\(^{17}\) Gloria Eden Ayesiga,\(^{16}\) Antonella Bancalari,\(^{14, 18, 19}\) Martina Björkman Nyqvist,\(^{20}\) Ekaterina Borisova,\(^{5, 21}\) Constantin Manuel Bosancianu,\(^1\) Magarita Rosa Cabra García,\(^22\) Ali Cheema,\(^{15, 23}\) Elliott Collins,\(^{2}\) Filippo Cuccaro,\(^{24}\) Ahsan Zia Farooqi,\(^{23}\) Tatheer Fatima,\(^{17}\) Mattia Fracchia,\(^{13, 25}\) Mery Len Galindo Soria,\(^{22}\) Andrea Guariso,\(^{26}\) Ali Hasanain,\(^{15}\) Sofía Jaramillo Arciniegas,\(^{22}\) Sellu Kallon,\(^{4, 27}\) Anthony Kamwesigye,\(^{16}\) Arjun Kharel,\(^{28}\) Sarah Kreps,\(^{29}\) Madison Levine,\(^{4}\) Rebecca Littman,\(^{30}\) Shan-e-Mohammad Malik,\(^{23}\) Gisele Manirabaruta,\(^{31}\) Jean Léodomir Habarimana Mfura,\(^{31}\) Fatoma Momoh,\(^{24}\) Alberto Mucauque,\(^{32}\) Imamo Mussa,\(^{32}\) Jean Aime Nsabimana,\(^{31}\) Isaac Obara,\(^{8}\) María Juliana Otálora,\(^{22}\) Béchir Wendemi Ouédraogo,\(^{33}\) Touba Bakary Pare,\(^{33}\) Melina R.
+Platas,\(^{34}\) Laura Polanco,\(^{22}\) Javaeria Ashraf Qureshi,\(^{30}\) Mariam Raheem,\(^{35}\) Vasudha Ramakrishna,\(^{36}\) Ismail Rendrá,\(^{32}\) Taimur Shah,\(^{35}\) Sarene Eyla Shaked,\(^{16}\) Jacob N.
+Shapiro, \(^{37}\) Jakob Svensson,\(^{38}\) Ahsan Tariq,\(^{23}\) Achille Mignondo Tchibozo,\(^{33}\) Hamid Ali Tiwana,\(^{23}\) Bhartendu Trivedi,\(^{17}\) Corey Vernot, \(^{36}\) Pedro C.
+Vicente,\(^{13, 25}\) Laurin B Weissinger,\(^{39}\) Basit Zafar,\(^{35, 40}\) Baobao Zhang,\(^{29}\) Dean Karlan,\(^{2, 41}\) Michael Callen,\(^{42}\) Matthieu Teachout,\(^{3}\) Macartan Humphreys,\(^{1, 6}\) Ahmed Mushfiq Mobarak,\(^{43}\) Saad B.
+Omer\(^{7}\).
 
@@
 
-We analyze COVID-19 vaccine acceptance across 15 survey samples covering ten low- and middle-income countries (LMICs) in Asia, Africa, and South America, and two higher income countries (Russia and the United States).
-Standardized survey responses were collected from `45,928individuals.
-We find generally high willingness to take a COVID-19 vaccine in LMIC samples (80\% on average), considerably higher than in the United States (65\%) and Russia (30\%).
-Vaccine acceptance was primarily explained by an interest in personal protection against the disease, while concern about side effects was the most commonly expressed reason for reluctance.
-Health workers were the most trusted sources of information about COVID-19 vaccines.
-Our findings suggest that prioritizing efficient and equitable vaccine distribution to LMICs should yield high returns in promoting global immunization.
-Interventions to promote vaccination in these contexts should focus on translating intentions into uptake and involve trusted health workers.
+We analyze COVID-19 vaccine acceptance across 15 survey samples covering ten low- and middle-income countries (LMICs) in Asia, Africa, and South America, Russia (an upper-middle-income country), and the United States, including 44,260 individuals.
+We find considerably higher willingness to take a COVID-19 vaccine in our LMIC samples (mean 80.3\%; median 78\%; range of 30.1\%) compared to the United States (mean 64.6\%) and Russia (mean 30.4\%).
+Vaccine acceptance is primarily explained by an interest in personal protection against COVID-19, while concern about side effects is the most common reason for hesitancy.
+Health workers are the most trusted sources of guidance about COVID-19 vaccines.
+Evidence from this sample of LMICs suggests that prioritizing vaccine distribution to the Global South should yield high returns in advancing global immunization coverage.
+Vaccination campaigns should focus on translating the high levels of stated acceptance into actual uptake.
+Messages highlighting vaccine efficacy and safety, delivered by healthcare workers, may be most effective for addressing remaining hesitancy.
 
@@
 
-A safe and effective vaccine against COVID-19 is a critical tool to control the pandemic.
-As of March 2, 2021, there were 76 vaccines in clinical development and 16 had advanced to Stage 3 clinical trials.\textsuperscript{\protect\hyperlink{ref-who1}{1}} Following clinical trials, several vaccines have been approved in multiple countries and are being distributed across the globe.
-At present, global vaccine distribution remains highly unequal, with much of the current supply directed toward high-income countries.\textsuperscript{\protect\hyperlink{ref-eiu}{2}}
-
-While effective and equitable distribution of the vaccines is a key policy priority, ensuring the population's acceptance is equally important.
-Acceptance of vaccines and trust in the institutions that administer them are likely key determinants of the success of any vaccination campaign.\textsuperscript{\protect\hyperlink{ref-defigueiredo2020lancet}{3}} Several studies investigate high-income country residents' willingness to take a potential COVID-19 vaccine.\textsuperscript{\protect\hyperlink{ref-boyon2020ipsos}{4},\protect\hyperlink{ref-Malik2020}{5}} Little is known about acceptance rates in low- and middle-income countries (LMICs), however, where the majority of the world's population resides.
-
-Acceptance of childhood vaccination for common diseases ---such as measles (MCV), Bacille Calmette-Guérin (BCG) and diphtheria, tetanus, and pertussis (DTP)---is generally high in LMICs, providing reasons for optimism about future uptake of COVID-19 vaccines.
-Table \ref{tab:otherv} summarizes general vaccine acceptance and uptake of common childhood vaccines for the countries included in our study.
-Still, existing studies on COVID-19 vaccine acceptance document large variation, both across and within countries, including in settings where overall vaccination rates are high.\textsuperscript{\protect\hyperlink{ref-boyon2020ipsos}{4}} These studies highlight concerns about COVID-19 vaccine safety, and particularly concerns about the speed of vaccine development, as reasons for hesitancy in higher income settings.
-Similar concerns may apply in LMICs.
-
-Additional reasons for hesitancy may feature more prominently in LMIC settings.
-Reported COVID-19 mortality rates have consistently been lower in LMICs relative to higher income countries.\textsuperscript{\protect\hyperlink{ref-mukherjee}{6}} If individuals in LMICs feel the risk of disease is less serious, they may be less inclined to accept perceived risks associated with taking a recently-developed vaccine.
-Previous studies have also highlighted factors such as concerns about healthcare quality,\textsuperscript{\protect\hyperlink{ref-christensen2020building}{7}} negative historical experiences,\textsuperscript{\protect\hyperlink{ref-Lowes2018}{8}} weak support from traditional leaders,\textsuperscript{\protect\hyperlink{ref-Jegede2007}{9}} and mistrust in government\textsuperscript{\protect\hyperlink{ref-BLAIR201789}{10}} as barriers to healthcare utilization in LMICs.
-
-Understanding factors that may lead people in LMICs to reject COVID-19 vaccination is of global concern, since a lag in vaccination in the developing world could facilitate the spread of new variants of the virus to other countries.
-
-In order to effectively promote vaccination against COVID-19 and devise messaging strategies, we need to know if people are willing to take COVID-19 vaccines, the reasons why they are willing or unwilling to do so, and the factors influencing their decision-making.
-For this purpose, we developed and deployed a common set of questions across 15 studies in ten LMICs in Africa (Burkina Faso, Mozambique, Nigeria, Rwanda, Sierra Leone, Uganda), Asia (India, Nepal, Pakistan), and Latin America (Colombia).
-We compare these findings in LMICs to those from two higher income countries (Russia and the United States).
+A safe and effective vaccine is a critical tool to control the COVID-19 pandemic.
+As of May 27, 2021, 23 vaccines had advanced to Stage 3 clinical trials\textsuperscript{\protect\hyperlink{ref-who1}{1}} and more than a dozen had been approved in multiple countries\textsuperscript{\protect\hyperlink{ref-track}{2}}.
+The BioNTech/Pfizer (Comirnaty) vaccine, for example, has been approved in more than 80 countries, while the AstraZeneca vaccine has the most country authorizations at 98.\textsuperscript{\protect\hyperlink{ref-track}{2}} At present, however, global vaccine distribution remains highly unequal, with much of the current supply directed toward high-income countries.\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3}}
+
+While effective and equitable distribution of COVID-19 vaccines is a key policy priority, ensuring acceptance is just as important.
+Trust in vaccines and the institutions that administer them are key determinants of the success of any vaccination campaign.\textsuperscript{\protect\hyperlink{ref-defigueiredo2020lancet}{4}} Several studies have investigated willingness to take a potential COVID-19 vaccine in high-income countries,\textsuperscript{\protect\hyperlink{ref-boyon2020ipsos}{5}--\protect\hyperlink{ref-fisher2020attitudes}{10}} and some studies have included middle-income countries.\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3},\protect\hyperlink{ref-lazarus2020nature}{11}} Less is known, however, about vaccine acceptance in low-income countries where large-scale vaccination has yet to begin.
+Understanding the drivers of COVID-19 vaccine acceptance is of global concern, since a lag in vaccination in any country may result in the emergence and spread of new variants that can overcome immunity conferred by vaccines and prior disease.\textsuperscript{\protect\hyperlink{ref-ong2021lack}{12},\protect\hyperlink{ref-lancettask}{13}}
+
+Our study complements the emerging global picture of COVID-19 vaccine acceptance by focusing primarily on lower income countries.
+We construct a sample of low- and middle-income countries (LMICs) with wide geographic coverage across Africa, Asia and Latin America.
+We move beyond documenting vaccine acceptance rates to collect and analyze data on the reasons for acceptance and hesitancy, which is critical for informing the design of effective vaccine distribution and messaging.
+A summary of the main findings, limitations and implications of the study is shown in Table \ref{tab:summary}.
+
+Acceptance of childhood vaccination for common diseases---such as measles (MCV), Bacille Calmette-Guérin (BCG) and diphtheria, tetanus, and pertussis (DTP)---is generally high in LMICs, providing grounds for optimism about the prospects for COVID-19 vaccine uptake.
+Table \ref{tab:otherv} summarizes general vaccine acceptance and coverage rates of childhood vaccines in 2018, prior to the current pandemic, for the countries included in our study.
+Agreement on the importance of childhood vaccinations is markedly higher in the LMICs we study compared to Russia and the United States.
+Still, existing studies on COVID-19 vaccine acceptance document substantial variation, both across and within countries, including in settings with high acceptance of other vaccinations.\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3},\protect\hyperlink{ref-defigueiredo2020lancet}{4},\protect\hyperlink{ref-lazarus2020nature}{11}}
+
+Existing literature cites concern about COVID-19 vaccine safety, including the rapid pace of vaccine development, as a primary reason for hesitancy in higher-income settings.\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3},\protect\hyperlink{ref-boyon2020ipsos}{5}} Other reasons may feature more prominently in LMICs.
+For instance, reported COVID-19 mortality rates have been consistently lower in most LMICs relative to higher income countries.\textsuperscript{\protect\hyperlink{ref-biccard2021patient}{14}--\protect\hyperlink{ref-maeda2021puzzle}{16}} If individuals feel the risk of disease is less severe, they may be less willing to accept any perceived risks of vaccination.\textsuperscript{\protect\hyperlink{ref-brewer2007meta}{17}} Previous studies of healthcare utilization in LMICs have also highlighted factors such as negative perceptions of healthcare quality,\textsuperscript{\protect\hyperlink{ref-christensen2020building}{18}} negative historical experiences involving foreign actors,\textsuperscript{\protect\hyperlink{ref-Lowes2018}{19},\protect\hyperlink{ref-martinez2021vaccines}{20}} weak support from traditional leaders,\textsuperscript{\protect\hyperlink{ref-Jegede2007}{21}} and mistrust in government\textsuperscript{\protect\hyperlink{ref-BLAIR201789}{22}} as barriers to uptake, which could apply to COVID-19 vaccination as well.
+
+To promote vaccination against COVID-19, we need to know whether people are willing to take COVID-19 vaccines, the reasons why they are willing or unwilling to do so, and the most trusted sources of information in their decision-making.
+Our study investigates these questions using a common set of survey items deployed across 13 studies in Africa, South Asia, and Latin America: seven in low-income countries (Burkina Faso, Mozambique, Rwanda, Sierra Leone, Uganda), five in lower-middle-income countries (India, Nepal, Nigeria, Pakistan), and one in an upper-middle-income country (Colombia).
+We compare these findings to those from two countries at the forefront of vaccine research and development, Russia and the United States.
+
+To select studies to include in our sample, we conducted an internal search within Innovations for Poverty Action (IPA), the International Growth Center (IGC), and the Berlin Social Science Center (WZB) for projects with plans to collect survey data in the second half of 2020.
+Study PIs agreed to include a set of common questions about COVID-19 vaccine attitudes.
+This strategy was guided by the need to collect information quickly and cost-effectively using a survey modality (phone) that was both safe, given pandemic conditions, and appropriate for contexts with limited internet coverage.
+The final set of samples included in our study therefore reflects populations that fall under the current research priorities at IGC, IPA and WZB and, in the case of IPA and IGC, donors that prioritize working in the Global South.
 
@@
 
-Our main results are shown in Figure \ref{fig:mainfigure1} and reproduced as Table \ref{tab:maintabledis} in \protect\hyperlink{appendixd}{Appendix A}.
-The first column provides overall acceptance rates in each study, while the remaining columns show acceptance rates disaggregated by respondent characteristics.
-The ``All LMICs'' row reports averages for LMIC countries only (and so excludes Russia and the US).
-
-We document meaningful variation in vaccine acceptance across and within LMICs, but generally high levels of acceptance in LMICs overall.
-The average acceptance across studies is 80.3\% (95\% CI 74.9--85.6), with a median of 78, a range of 30.1 percent points and an interquartile range of 9.7.
-Our estimate of \(\tau^2\) is 0.007 which implies a standard deviation over country averages of 0.084.
-
-The acceptance rate in every LMIC sample is higher than in USA (64.6\%, 61.8--67.3) and Russia (30.4\%, 29.1--31.7).
-
-We find limited evidence of variation across demographic subgroups in LMICs, as shown in Table \ref{tab:dmeans}.
-Women were generally less willing to accept the vaccine (average difference about 4.3 points, significant at \(p<.01\)).
-Younger respondents (defined as aged \textless55 given younger-skewing populations in LMICs) were marginally more willing to take the vaccine, but this difference was not statistically significant.
-Less educated people were on average more willing to take the vaccine in LMICs, but this difference was not significant.
+Our main results are shown in Figure \ref{fig:mainfigure1} and reproduced as \hyperref[tab:maintabledis]{Supplementary Table 1}.
+The first column provides overall acceptance rates in each study, while the remaining columns disaggregate acceptance by respondent characteristics.
+The ``All LMICs'' row reports averages for the LMIC samples included in our study and excludes Russia and the USA.
+The ``LMICs National Samples'' row reports averages for just the LMIC samples with national-level geographic coverage.
+
+The average acceptance rate across the full set of LMIC studies is 80.3\% (95\% CI 74.9--85.6\%), with a median of 78\%, a range of 30.1\% and an interquartile range of 9.7\%.
+Our estimate of the between-study standard deviation, \(\tau\), using a random effects meta-analysis model is 0.084 which represents only 10.5\% of our estimate of the average acceptance across LMIC studies.
+
+The acceptance rate in every LMIC sample is higher than in the USA (64.6\%, CI 61.8--67.3\%) and Russia (30.4\%, CI 29.1--31.7\%).
+Reported acceptance is lowest in Burkina Faso (66.5\%, CI 63.5--69.5\%) and Pakistan 2 (66.5\%, CI 64.1--68.9\%).
+Pakistan's relatively low acceptance rate may be linked to negative historical experiences with foreign-led vaccination campaigns.\textsuperscript{\protect\hyperlink{ref-martinez2021vaccines}{20},\protect\hyperlink{ref-ali2019polio}{23},\protect\hyperlink{ref-robbins2012cia}{24}} This hesitancy may be particularly problematic given the magnitude of the second wave in neighboring India and acceleration of cases across South Asia that threaten to overwhelm health infrastructure.
+The relatively low acceptance rate in Burkina Faso may reflect general vaccine hesitancy.
+As shown in Table \ref{tab:otherv}, fewer people believe that vaccines in general are safe in Burkina Faso than in any other country included in our study except Russia.
+
+We find limited evidence of variation across demographic subgroups in our aggregate analysis of LMIC samples, as shown in \hyperref[tab:dmeans]{Supplementary Table 7}.
+Women are generally less willing to accept the vaccine than men (average difference about 4.2 points, significant at \(p<.01\)).
+Respondents under age 25 and less educated respondents are marginally more willing to take the vaccine compared to older and more educated respondents, respectively, but these differences are not statistically significant.
+
+Table \hyperref[tab:countrydiff]{Supplementary Table 9} provides results disaggregated by demographic subgroups for individual studies.
+The average gender differences in the aggregate LMIC analysis are driven by the Burkina Faso, Mozambique, Pakistan 1, Rwanda and Sierra Leone 1 samples.
+However, these gender differences in acceptance are less than 10 percentage points in each of these samples, in contrast to larger gender gaps in acceptance we observe in the USA (17\%) and Russia (16\%).
+
+Less-educated respondents expressed significantly higher acceptance in the Burkina Faso, Rwanda, Sierra Leone 1, and Uganda 2 samples, which represent the majority of studies from sub-Saharan Africa.
+Notably, we observe the opposite pattern in the India, Pakistan 1, and Pakistan 2 samples.
+In all three studies, acceptance is greater among more educated respondents, although this difference is not statistically significant in the India sample.
+Education is also a positive and significant predictor of acceptance in the USA.
+
+We find mixed evidence across studies with respect to the relationship between age and COVID-19 vaccine acceptance.
+In India and Nigeria, respondents younger than 25 years old are significantly less willing to take the vaccine relative to adults 25-54 years old, while in Mozambique, Pakistan 1, and Rwanda, those under 25 are significantly more willing.
+In Mozambique and Rwanda, respondents under 25 are also significantly more accepting compared to those 55 and over; however, the difference between these age groups is not statistically significant in other LMIC samples.
+In the USA and Russia, older respondents are consistently more accepting than younger respondents.
 
 To better understand the reasoning behind vaccine acceptance, we asked those who were willing to take the vaccine why they would take it.
-We summarize in Table \ref{tab:yes}, with more details in Table \ref{tab:yesall}.
-
-The most common reason given for vaccine acceptance was personal protection against COVID-19 infection.
-The average across LMICs was 91\% (86--96).
-In every individual study, it ranked as the first reason.
-In distant second place, LMIC respondents reported willingness to take the COVID-19 vaccine in order to protect their families.
-The average across LMICs was 36\% (28--43).
-In comparison to self-protection, protecting the community did not feature prominently among the stated reasons.
-
-Self-protection also ranked as the most commonly expressed reason for taking the vaccine in Russia (76\%, 74--78) and the USA (94\%, 92--95).
-
-This evidence contrasts with appeals to altruistic behavior and prosocial motivations in order to promote vaccine acceptance.\textsuperscript{\protect\hyperlink{ref-chou2020considering}{11}} The risks and benefits to personal well-being feature much more prominently in people's stated reasons for vaccine acceptance.
-
-Figure \ref{fig:fig2paper} summarizes the reasons given among respondents who said they were not willing to take a Covid vaccine.
-
-The most common reason expressed for reluctance to take the vaccine in LMIC studies was concern about side effects.
-For studies Uganda 1 (85.1\% 80.7--89.6), Sierra Leone 2 (57.9\%, 50.1--65.7), Sierra Leone 1 (53.5\% 47.1--59.9) and Uganda 2 (47.3\% 42.2--52.5), more than half of those respondents unwilling to take the vaccine mentioned this reason.
-Respondents in Russia (36.8\%, 35.2--38.4) and the USA (79.3\%, 74.6--84), reported high levels of this same concern.
-
-While serious adverse events that are life-threatening or require hospitalization are very rare, with only .6\% of respondents reporting at least one side effect in the Pfizer vaccine trial,\textsuperscript{\protect\hyperlink{ref-cdcadverse}{12}} one potential explanation for the outsized concern about side effects could be the lack of widespread information about features of the vaccine at the time of data collection.
-Media coverage of the few cases of serious adverse events and spread of fake news may contribute as well.\textsuperscript{\protect\hyperlink{ref-stein2017golden}{13}}
-
-Concerns about side effects could also be due to a concern about mild side effects from experiences with other vaccines.
-In the case of available COVID-19 vaccines, we now know that mild side effects are common but transient.
-These include fatigue, muscle pain, joint pain and headache, which were severe in fewer than 10\% of people in the clinical trials of tens of thousands.
-Severe fever occurred in fewer than 2\% of them.\textsuperscript{\protect\hyperlink{ref-wadman2020public}{14}}
-
-Allergic reactions from the COVID-19 vaccine seem to be extremely rare.
-Data from trials of the Pfizer-BioNTech vaccines shows that anaphylaxis after reported administration occurs at a rate of 11.1 cases per million vaccine doses administered.\textsuperscript{\protect\hyperlink{ref-cdcallergies}{15}} Our data reflects this -- no more than 6\% of respondents expressed concern about allergies in any of our LMIC studies.
-
-Other concerns that make many respondents unwilling to take the vaccine could be countered by accurately presenting the scientific data to the public.
-Studies Uganda 2 (31\%, 25.9--36.2), Mozambique (29.7\%, 18.6--40.8) and Pakistan 1 (26\%, 18--34) showed relatively high levels of skepticism about vaccine effectiveness.
-This is also true for respondents in Russia (29.6\%, 28.1--31.1) and the USA (46.8\%, 41--52.6).
-Recent clinical trials reveal very high rates of vaccine efficacy,\textsuperscript{\protect\hyperlink{ref-baden2021efficacy}{16},\protect\hyperlink{ref-polack2020safety}{17}} and clearly communicating these results to the public is a high priority.
-In contrast, conspiracy theories were rarely mentioned by respondents in any of our study samples, in spite of widespread popular discourse about anti-vaxxer movements and theories in higher-income countries.\textsuperscript{\protect\hyperlink{ref-loomba_measuring_2021}{18}}
-
-Finally, respondents in some studies downplayed the seriousness of this disease, and listed this as a reason not to be vaccinated.
-Studies USA (39.3\% 33.5--45), Pakistan 1 (29.4\%, 20.9--37.9) and Nepal (20.4\% 6.7--34.1) reported high rates of respondents citing lack of concern as a reason they were hesitant.
-
-The analysis above identifies the nature of the information gaps that any vaccine messaging should target, while in Figure \ref{fig:fig3paper} we try to identify the actors who are best placed to deliver those messages.
-We asked respondents about their most trusted source of information when deciding whether to take the vaccine, because these sources are vital to disease control strategies during public health emergencies.\textsuperscript{\protect\hyperlink{ref-siegrist2014role}{19}} Results from Figure \ref{fig:fig3paper} are reproduced as Table \ref{tab:trust} in \protect\hyperlink{appendixd}{Appendix A}.
-
-We find striking consistency across countries.
-In all but one study, respondents identified the health system as the most trustworthy source to help them decide whether or not to take the COVID-19 vaccine (with the exception of Rwanda, where the government in general was identified as the most trusted source, with the health system a close second).
-Family and friends were the next most important reference points in most samples.
-Across samples, women were 3 percentage points more likely to rely on family and friends than male respondents, though this difference was not significant at conventional levels (Figure \ref{fig:genderhist} in \protect\hyperlink{appendixd}{Appendix D}).
-By contrast, endorsements by religious leaders or celebrity figures were not seen as important sources of influence in any sample other than Nepal.
+We summarize these results in \hyperref[tab:yes]{Supplementary Table 2}, with additional details in \hyperref[tab:yesall]{Supplementary Table 3}.
+The reason most commonly given for vaccine acceptance across samples is personal protection against COVID-19 infection.
+The average across the LMIC samples is 91\% (CI 86--96\%) with a median of 92.5\% and a range of 22\%.
+In every individual study, including the USA (94\%, CI 92--95\%) and Russia (76\%, CI 74--78\%), this ranks as the most cited reason.
+In distant second place in the aggregate LMIC analysis is family protection, with an average of 36\% (CI 28--43\%), a median of 34.5\% and a range of 39\%.
+In comparison to protecting oneself and one's family, protecting one's community does not feature prominently among stated reasons for acceptance.
+These reasons do not vary substantially by age group, as shown in \hyperref[tab:yes1]{Supplementary Table 4}.
+
+Figure \ref{fig:fig2paper} summarizes the reasons given by respondents who said they were not willing to take a COVID-19 vaccine.
+Concern about side effects is the most frequently expressed reason for reluctance in our LMIC samples.
+This concern is particularly evident among samples from sub-Saharan Africa.
+In studies Uganda 1 (85.1\%, CI 80.7--89.6\%), Sierra Leone 2 (57.9\%, CI 50.1--65.7\%), Sierra Leone 1 (53.5\%, CI 47.1--59.9\%) and Uganda 2 (47.3\%, CI 42.2--52.5\%), more than half of respondents unwilling to take the vaccine cited worries about side effects.
+Respondents in Russia (36.8\%, CI 35.2--38.4\%) and even more in the USA (79.3\%, CI 74.6--84\%), frequently report this same concern.
+
+Study samples Uganda 2 (31\%, CI 25.9--36.2\%), Mozambique (29.7\%, CI 18.6--40.8\%) and Pakistan 1 (26\%, CI 18--34\%) show relatively high levels of skepticism about vaccine effectiveness among hesitant respondents.
+This is also true in Russia (29.6\%, CI 28.1--31.1\%) and the USA (46.8\%, CI 41--52.6\%).
+In addition, some hesitant respondents cite lack of concern about COVID-19 infection as a reason not to be vaccinated.
+This answer is particularly common in the USA (39.3\%, CI 33.5--45\%), Pakistan 1 (29.4\%, CI 20.9--37.9\%) and Nepal (20.4\%, CI 6.7--34.1\%) studies.
+
+In Figure \ref{fig:fig3paper} we report respondents' most trusted source of guidance when deciding whether to take a COVID-19 vaccine.
+Results from Figure \ref{fig:fig3paper} are reproduced in \hyperref[tab:trust]{Supplementary Table 6}, while \hyperref[tab:q4]{Supplementary Table 13} presents a complete description of response recoding from individual studies.
+
+We find striking consistency across studies.
+In all samples except Rwanda, including those from Russia and the USA, respondents identify the health system as the most trustworthy source to help them decide whether to take the COVID-19 vaccine.
+The average across LMIC samples is 48.1\% (CI 31.6--64.5\%), with a median of 44.1\% and a range of 66.3\%.
+Respondents in Sierra Leone 2 (89.3\%, CI 87.2--91.5\%), Nigeria (58\%, CI 55.7--60.2\%) and Burkina Faso (51.6\%, CI 48.5--54.8\%) cited health workers most often.
+Sierra Leone has the highest trust in health workers and the Ministry of Health, potentially reflecting investments in public health following the 2014-2015 Ebola epidemic.\textsuperscript{\protect\hyperlink{ref-deserrano}{25}}
+
+In Colombia (36.6\%, CI 33.5--39.7\%), Nepal (35.6\%, CI 32.9--38.3\%), Russia (28.1\%, CI 26.8--29.3\%) and Burkina Faso (18.4\%, CI 16--20.9\%), the next most-cited sources are family and friends.
+Across the pooled samples, women are 3 percentage points more likely to rely on family and friends than male respondents, though this difference is not statistically significant (\hyperref[fig:genderhist]{Supplementary Figure 1}).
+
+By contrast, in Sierra Leone 1 (32.5\%, CI 29.7--35.4\%), Uganda 2 (32.4\%, CI 29.9--35\%), USA (29.7\%, CI 27--32.3\%) and Nigeria (18\%, CI 16.2--19.8\%), government is the second most frequently cited.
+Religious leaders and celebrities are not seen as the top sources of guidance by many respondents in any sample other than Nepal, where many respondents say they most trust famous people (16.1\%, CI 13.3--18.9\%).
+
+Finally, we highlight two idiosyncratic, yet frequently mentioned, trusted sources of information in deciding whether to take a COVID-19 vaccine.
+In Rwanda, 34\% of respondents would most trust ``themselves'' for guidance, the most frequent response in this sample.
+In the USA, 14\% of respondents cited Joe Biden, then president-elect and therefore excluded from the ``government'' category, as their most trusted source.
 
@@
 
-To our knowledge, this is the first study documenting rates of expressed COVID-19 vaccine acceptance and hesitancy in a large set of LMICs.
-Our findings show variable but broadly high levels of prospective COVID-19 vaccine acceptance across LMICs using data from 45,928 respondents in 13 original household surveys from Africa (Burkina Faso, Mozambique, Nigeria, Rwanda, Sierra Leone, Uganda), Asia (Bangladesh, India, Nepal, Pakistan), and Latin America (Colombia).
-Acceptance across LMIC averages 80.3, ranging between 66.5 and 96.6.
-We document considerably lower levels of acceptance in Russia and the United States.
-
-Patterns of COVID-19 vaccine hesitancy are not well predicted by existing measures of concerns about the safety of other vaccines (e.g., the Wellcome Global Monitor shown in Table \ref{tab:otherv}).
-Compared with other vaccines, COVID-19 vaccine acceptance is lower and more variable across LMIC samples.
-This suggests that concerns may apply specifically to COVID-19 vaccines rather than to vaccination more broadly.
-
-Our study also documents reasons why respondents express intentions to take (or not take) a COVID-19 vaccine.
-The main reason expressed for willingness to take such a vaccine was to protect oneself.
-The most common reasons offered by those unwilling to take the vaccine were concerns about safety (side effects) and efficacy.
-Across all contexts, health care workers were the most trusted source of information about vaccines.
-
-Our study samples offer an important window into the motivations underlying COVID-19 vaccine acceptance in LMICs, but our data are not fully nationally representative.
-Random digit dial samples and follow-up phone surveys, while necessary during a global pandemic, do not include individuals who reside outside coverage areas, who do not own or cannot operate cell phones, or who choose not to respond to telephone surveys.
-Care should also be taken in any attempt to extrapolate to the population level from the samples representative of narrow subpopulations.
-
-If intentions reported in our LMIC samples translated into actual vaccination uptake, the rates would far exceed the range of what would be required for COVID-19 herd immunity (40-67\% in recent estimates).\textsuperscript{\protect\hyperlink{ref-britten2020}{20},\protect\hyperlink{ref-haley2020}{21}} However, reported intent may not materialize into actual vaccine adoption.\textsuperscript{\protect\hyperlink{ref-mceachanetal2011}{22}} The high salience of COVID-19 due to extensive media coverage and government mitigation efforts and excitement around vaccine release may have increased reported intention.\textsuperscript{\protect\hyperlink{ref-chen1996}{23}} Results from the first COVID-19 vaccine Phase 3 clinical trial were announced before some surveys were fielded; during others, subsequent approvals were granted.
-The fast-moving information environment may change people's perceptions about vaccines by the time they are widely available in LMICs.
-
-Nonetheless, our findings provide some specific guidance on how to design messaging to boost COVID-19 vaccine acceptance and uptake in LMICs.
-Our data have implications for both what the content of the message should be, and who should deliver the message.
-
-First, high levels of trust in the advice of health workers and governments on COVID-19 vaccine decision-making suggest that social and behavioral change communication (SBCC) strategies that engage local health workers may be particularly effective tools to encourage timely and complete vaccine uptake, and to combat remaining vaccine hesitancy.
-The literature has explored messaging strategies to promote welfare-improving behaviors, with considerable attention paid to celebrity endorsements.\textsuperscript{\protect\hyperlink{ref-alatas2019celebrities}{24}} Our data strongly support the view\textsuperscript{\protect\hyperlink{ref-bokemper2021timing}{25}} that those with the most relevant expertise - as opposed to celebrities or general opinion leaders - are most trusted on this specific topic and are therefore best positioned to deliver the message.
-
-Second, the average COVID-19 vaccine acceptance rate across our LMIC samples is high, approximately 80.3\%.
-Given such positive intentions, there may be high returns to investing in straightforward ``last-mile'' nudges that help citizens convert intentions into actions.
-Reminder messages from healthcare providers and messages alerting patients that vaccines have been reserved for them at an upcoming appointment may provide a low-cost encouragement to initiate and complete two-dose COVID-19 vaccinations, as was found in two recent large-scale studies in the United States.\textsuperscript{\protect\hyperlink{ref-milkmanetal2021a}{26},\protect\hyperlink{ref-milkmanetal2021b}{27}} Similarly, childhood vaccination reminders plus cash incentives in Kenya substantially increased full immunization,\textsuperscript{\protect\hyperlink{ref-gibsonetal2017}{28}} and cash and in-kind incentive programs in Nigeria and India have also proven effective.\textsuperscript{\protect\hyperlink{ref-idinsight}{29},\protect\hyperlink{ref-Banerjee2010}{30}}
-
-Third, high coverage rates of existing vaccines, coupled with respondents' reliance on friends and family as information sources, suggest that the general pro-vaccination stance of many citizens could be leveraged to convert intent to uptake.
-Social learning strategies and norm-setting are powerful drivers of information diffusion and behavior change in many related sectors.\textsuperscript{\protect\hyperlink{ref-beaman2021can}{31}} Social signalling of positive attitudes toward COVID-19 vaccines may also help shift social norms toward even greater immunization acceptance and two-dose completion in the community at large.\textsuperscript{\protect\hyperlink{ref-karing2018social}{32}}
-
-Finally, our findings offer guidance on the specific content of vaccine messaging that is likely to be most persuasive.
-Messaging should highlight the high efficacy rates of the COVID-19 vaccines currently on the market in reducing or eliminating disease, hospitalizations and death.
-Alluding to clinical data that addresses people's concerns about potential side effects should be prioritized.
-Messaging should also emphasize the direct protective benefits of the vaccine to the adopter.
+The current study contributes to the emerging picture of global vaccine acceptance by focusing on COVID-19 vaccine attitudes in a set of low-income and lower-middle-income countries.
+Our findings show variable but broadly high levels of prospective COVID-19 vaccine acceptance across the LMICs we study, using data from 44,260 respondents in 13 studies in ten LMICs in Africa, South Asia, and Latin America.
+Acceptance across these LMIC samples averaged 80.3\%, ranging between 66.5\% and 96.6\% with a median of 78\%.
+The two benchmark countries, Russia and the USA, demonstrate lower COVID-19 vaccine acceptance, consistent with lower pre-pandemic vaccine confidence.
+
+Many metrics and indices measure vaccine acceptance and hesitancy globally.\textsuperscript{\protect\hyperlink{ref-betsch2018beyond}{26}--\protect\hyperlink{ref-gilkey2014vaccination}{29}} Our surveys use measures employed in other COVID-19 vaccine acceptance studies\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3},\protect\hyperlink{ref-Malik2020}{6}--\protect\hyperlink{ref-lazarus2020nature}{11}} and recommended by the WHO Data for Action guidance,\textsuperscript{\protect\hyperlink{ref-whodata}{30}} allowing for meaningful cross-study and cross-country comparisons.
+We measure trust in sources of information about COVID-19 vaccination using a measure similar to that used in the Vaccine Confidence Index (VCI), a widely used survey tool.\textsuperscript{\protect\hyperlink{ref-defigueiredo2020lancet}{4}}
+
+Consistent with other studies, we find higher average vaccine acceptance among men than women.\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3},\protect\hyperlink{ref-kreps2020factors}{7}--\protect\hyperlink{ref-fisher2020attitudes}{10}} In contrast to studies focused primarily on higher-income countries, we find no consistently significant differences with respect to age\textsuperscript{\protect\hyperlink{ref-kreps2020factors}{7},\protect\hyperlink{ref-dror2020vaccine}{9}} or education in our LMIC samples.
+
+A key contribution of our study relative to the existing literature is its focus on the reasons \emph{why} respondents express intentions to take (or refuse) a COVID-19 vaccine.
+Other work has highlighted appeals to altruistic behavior or other prosocial motivations to promote vaccine acceptance.\textsuperscript{\protect\hyperlink{ref-chou2020considering}{31}} Yet we find that the potential risks and benefits to personal well-being feature much more prominently in our respondents' reasoning, suggesting that appeals about personal protection may be more effective in the countries under study here.
+
+The most commonly stated reason for vaccine refusal is concern about safety (side effects).
+The vast majority (86\%) of our surveys were conducted as reports from Phase 2 and 3 clinical trial data were emerging for the earliest commercially available vaccines, but prior to the first Emergency Use Authorization of any vaccine (Pfizer-BioNTech approved by the USA on December 11, 2020).
+Early trial data showed that severe adverse effects were extremely rare,\textsuperscript{\protect\hyperlink{ref-mulligan2020phase}{32}--\protect\hyperlink{ref-polack2020safety}{37}} occurring in fewer than 10\% of people in clinical trials.\textsuperscript{\protect\hyperlink{ref-wadman2020public}{38}} Our respondents' concern about side effects could reflect the rapid pace of vaccine development\textsuperscript{\protect\hyperlink{ref-callaway2020russia}{39}} and limited information available about potential COVID-19 vaccine safety at the time of data collection.
+These concerns could also reflect worries about mild, yet common and transient side effects, such as fatigue, muscle pain, joint pain and headache.
+
+Intensive media coverage of adverse events may exacerbate concerns about side effects.\textsuperscript{\protect\hyperlink{ref-stein2017golden}{40}} In particular, new information about rare but severe cases of thrombosis associated with the Astra-Zeneca vaccine that appeared after our data collection period could affect hesitancy levels.
+This is of particular relevance to LMICs, which are likely to rely on the Astra-Zeneca vaccine in their immunization campaigns through initiatives such as COVAX.
+
+Concerns about vaccine efficacy, averaging approximately 19.2\% in the LMIC samples, may also reflect a lack of information about vaccines at the time of our surveys.
+However, we note that respondents in our samples rarely cited conspiracy theories about ulterior motives on the part of corporations, politicians or the pharmaceutical industry, despite attention given to fears about these issues in higher-income countries.\textsuperscript{\protect\hyperlink{ref-loomba_measuring_2021}{41}}
+
+Our study has several limitations, which we address here.
+First, our data are not representative of all LMICs.
+They instead represent a sample of studies in countries where our organizations could quickly and safely mobilize coordinated data collection.
+Second, samples from the countries we include here are not fully nationally representative.
+Phone surveys, while necessary during a global pandemic, do not include individuals who reside outside coverage areas, lack access to a cell phone, or do not respond to calls.
+In addition, as shown in Table \ref{tab:sampling}, several studies focus on subnational populations of interest from pre-existing studies to which questions about COVID-19 vaccination were added.
+Particular care should be taken in extrapolating these findings to national populations.
+
+In spite of this variation in sample composition, our main findings---of high COVID-19 vaccine acceptance in our LMIC samples relative to the USA and Russia---are remarkably consistent across studies.
+We conduct several robustness checks to probe the sensitivity of our aggregate LMIC analysis to the inclusion of particular samples.
+First, as shown in \hyperref[fig:mainloo]{Supplementary Figure 3}, we re-estimate aggregate vaccine acceptance across our LMIC samples successively dropping one and two study samples at a time.
+Regardless of which samples are excluded, the average vaccine acceptance rate among LMIC samples remains consistent and considerably higher than in the USA and Russia, demonstrating that our results are not driven by the peculiarities of one or two studies.
+Second, we repeat the same analysis excluding all samples that are sub-national in scope, which yields a mean acceptance rate of 78.4\% (CI 67.9--89\%), as shown in the row ``All LMICs (National samples)'' in Figure \ref{fig:mainfigure1} and \hyperref[tab:maintabledis]{Supplementary Table 1}.
+
+The expressed intentions to take a COVID-19 vaccine that we document in our LMIC samples, if translated into behavior, would meet or exceed the current herd immunity threshold for COVID-19 in many, but not all, countries (estimated to be between 70 and 80\%, based on the predominant variant in circulation in different countries)\textsuperscript{\protect\hyperlink{ref-ontario}{42}--\protect\hyperlink{ref-mcneil_2021}{44}}.
+Reported intentions may however not always translate into vaccine uptake.\textsuperscript{\protect\hyperlink{ref-mceachanetal2011}{45}} The high salience of COVID-19 may have increased reported intentions.
+Conversely, reports about side effects and risks associated with expedited vaccine development may have increased hesitancy.
+The fast-moving pandemic and vaccine development context may change perceptions about vaccines by the time they are widely available in LMICs.
+
+Indeed, previous research on vaccine hesitancy has emphasized how concerns that arise surrounding vaccination campaigns are often case- and context-specific,\textsuperscript{\protect\hyperlink{ref-larson2011addressing}{46}} making it difficult to predict exactly how COVID-19 vaccines will be received in any given setting.
+The lower COVID-19 vaccine acceptance rates we observe in Russia and the USA, for example, may reflect the politicization of this specific pandemic and of vaccine development,\textsuperscript{\protect\hyperlink{ref-hornsey2020donald}{47}--\protect\hyperlink{ref-burki2020russian}{50}} in addition to generally greater vaccine skepticism.
+
+Nonetheless, our findings suggest several concrete implications for policy relating to vaccine roll-out in LMICs.
+First and foremost, we document high levels of COVID-19 vaccine acceptance in our LMIC samples compared to Russia and the USA.
+While global vaccine distribution has skewed heavily toward higher-income countries to date,\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3}} our findings suggest that prioritizing distribution to LMICs is justified not only on equity grounds, but on the expectation of higher marginal returns in maximizing global coverage more quickly.
+
+The high stated acceptance rates we document also imply that, once vaccine distribution to LMICs begins in earnest, interventions should focus on converting positive intentions into action.
+Straightforward, low-cost nudges may be effective in this regard.
+Two recent large-scale studies in the USA found that vaccination appointment reminder messages from healthcare providers increased influenza vaccine uptake.\textsuperscript{\protect\hyperlink{ref-milkmanetal2021a}{51},\protect\hyperlink{ref-milkmanetal2021b}{52}} Similar interventions have proven effective in increasing immunization in LMIC contexts.
+In Ghana and Kenya, vaccination reminders combined with small cash incentives increased childhood immunization coverage.\textsuperscript{\protect\hyperlink{ref-levine2021}{53},\protect\hyperlink{ref-gibsonetal2017}{54}} Cash and in-kind incentives programs were also effective in Nigeria and India.\textsuperscript{\protect\hyperlink{ref-idinsight}{55},\protect\hyperlink{ref-Banerjee2010}{56}}
+
+This recommendation is consistent with accepted frameworks, such as the WHO's Behavioral and Social Drivers of vaccination (BeSD) model, which suggest leveraging favorable intentions through reminders and primes, and reducing access barriers when the vast majority of people intend to be vaccinated.\textsuperscript{\protect\hyperlink{ref-whodata}{30},\protect\hyperlink{ref-brewer2017increasing}{57}} Particularly since COVID-19 vaccination may be more collectively than individually optimal, ease of access is critical to achieve high coverage.\textsuperscript{\protect\hyperlink{ref-betsch2013inviting}{58}} Availability of single-dose vaccines could be advantageous in settings with high vaccination demand but relatively low-capacity healthcare systems, as is the case in many LMICs.
+
+Our findings also suggest directions for the design and delivery of messaging to address remaining COVID-19 vaccine hesitancy in the countries under study here.
+Persuasion campaigns may be particularly important in countries where acceptance rates are below herd immunity thresholds.
+We highlight three potential implications for messaging below, but urge policymakers and stakeholders to utilize country-specific results to develop further strategies that may work best in their particular context.
+We also echo calls for integrating rigorous impact evaluation of vaccine hesitancy interventions in all contexts, given limited evidence to date.\textsuperscript{\protect\hyperlink{ref-dube2015strategies}{59}}
+
+First, our data strongly support the view that respondents from the included set of LMICs prefer to follow the guidance of actors with the most relevant knowledge and expertise.
+We find high levels of trust in health workers, which suggests that social and behavioral change communication (SBCC) strategies engaging local health workers may be particularly effective in combating remaining hesitancy.\textsuperscript{\protect\hyperlink{ref-bokemper2021timing}{48},\protect\hyperlink{ref-who2020behavioral}{60}} Health workers have also been the first group to receive the COVID-19 vaccine and are therefore best positioned to share locally credible experiences of vaccination.\textsuperscript{\protect\hyperlink{ref-katzman2021primary}{61}} While celebrities were rarely identified as a most trustworthy source for COVID-19 advice in our study, celebrity endorsements have proven effective in other contexts and may complement a strategy that primarily focuses on health workers.\textsuperscript{\protect\hyperlink{ref-alatas2019celebrities}{62}}
+
+Second, our findings offer some guidance on the specific content of vaccine messaging that is likely to be most effective in persuading those who may be hesitant.
+Hesitant respondents were most concerned about side effects and vaccine efficacy.
+This suggests that proactive messaging, initiated before large-scale vaccination campaign roll-out, should highlight the high efficacy rates of the COVID-19 vaccines currently on the market in reducing or eliminating disease, hospitalizations, and death, and communicate accurate information about potential side effects, including the rarity of severe adverse events that may have contributed to hesitancy through widespread media coverage.\textsuperscript{\protect\hyperlink{ref-goldstein2015health}{63},\protect\hyperlink{ref-puri2020social}{64}}
+
+Third, consistent with previous studies on COVID-19 vaccination\textsuperscript{\protect\hyperlink{ref-wouters2021challenges}{3},\protect\hyperlink{ref-kreps2020factors}{7}--\protect\hyperlink{ref-fisher2020attitudes}{10}} our study finds on average lower vaccine acceptance among women than men, suggesting that messaging strategies focusing on women may be important in addressing overall hesitancy.
+Recent work in Latin America on COVID-19 vaccine messaging found that the provision of basic information about the vaccines was particularly effective in persuading hesitant women.\textsuperscript{\protect\hyperlink{ref-argote2021messaging}{65}} More generally, countries may consider tailoring their messaging campaigns to address concerns held by more hesitant sub-populations, which vary across our samples with respect to age, gender and education.
+Additional research is needed to identify and design effective messaging campaigns in order to overcome hesitancy among specific subpopulations in each setting.\textsuperscript{\protect\hyperlink{ref-dube2015strategies}{59},\protect\hyperlink{ref-goldstein2015health}{63}}
+
+Finally, high coverage rates of existing vaccines, coupled with respondents' reliance on friends and family as information sources, suggest that the general pro-vaccination stance of many LMIC citizens could be leveraged to increase uptake of COVID-19 vaccines as they become available.
+This might yield particularly strong results in Colombia and Nepal, where family members and friends are seen as an important source of advice when deciding whether to take a COVID-19 vaccine.
+Social learning strategies and norm-setting are powerful drivers of behavior in many related sectors.
+Social signaling of positive attitudes towards vaccines may help shift social norms toward even greater immunization acceptance and uptake in the community at large.\textsuperscript{\protect\hyperlink{ref-van2020using}{66}--\protect\hyperlink{ref-ashraf2014no}{68}} As with messaging, policymakers should consider designing and evaluating social mobilization strategies targeted toward more hesitant subgroups.\textsuperscript{\protect\hyperlink{ref-jalloh2020mobilize}{69}}
+
+\clearpage
 
@@
 {[}the COVID-19 vaccine{]}''.
-Finally, regardless of their expressed willingness to take the vaccine, we asked about actors and institutions who would be influential in their decision.
-The question was worded in the following way: ``Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available?''.
-To examine heterogeneity across demographic strata, we collected information about the gender, age, and education level of each respondent.
-Slight variations in questions wording and answer options across studies are documented in \protect\hyperlink{appendixb}{Appendix B}.
+Finally, regardless of their expressed willingness to take the vaccine, we asked about actors and institutions that would be most influential in their decision: ``Which of the following people would you trust MOST to help you decide whether you would get a COVID-19 vaccine, if one becomes available?'' following.\textsuperscript{\protect\hyperlink{ref-defigueiredo2020lancet}{4}} To examine heterogeneity across demographic strata, we collected information about gender, age, and education.
+Slight variations in question wording and answer options across studies are documented in Supplementary Appendix.
 
@@
 The remaining eight studies targeted sub-national populations.
-One study from Pakistan (``Pakistan 2'') used RDD to reach a representative sample of active mobile phone users in Punjab province.
-Respondents in Mozambique, Nigeria, ``Pakistan 1'', ``Uganda 1'',``Uganda 2'', India, Nepal and ``Sierra Leone 2'' were drawn from pre-existing studies to which COVID-19 vaccine questions were subsequently added.
-For example, ``Sierra Leone 2'' has national coverage from a study on access to electricity and ``Uganda 1'' sampled female caregivers of households in rural and semi-rural villages as part of a large ongoing cluster-RCT implemented across 13 districts.
-
-Table \ref{tab:sampling} in \protect\hyperlink{appendixd}{Appendix A} summarizes the geographic scope, sampling methodologies and survey modalities of all 15 studies.
-A detailed description of each study is included in \protect\hyperlink{appendixa}{Appendix D}.
-
-All LMIC surveys were conducted via telephone to minimize in-person contact and comply with local government social distancing guidelines.
+One study from Pakistan (``Pakistan 2'') used RDD in Punjab province.
+Respondents in Mozambique, Nigeria, Pakistan (``Pakistan 1''), Uganda (``Uganda 1'',``Uganda 2''), India, Nepal and Sierra Leone (``Sierra Leone 2'') were drawn from pre-existing studies to which COVID-19 vaccine questions were subsequently added.
+For example, Sierra Leone 2 has national coverage from a study on access to electricity and Uganda 1 sampled female caregivers of households in rural and semi-rural villages as part of a large ongoing cluster-RCT implemented across 13 districts.
+
+Table \ref{tab:sampling} summarizes the dates of data collection, geographic scope, sampling methodologies and survey modalities of all 15 studies.
+
+All surveys were conducted remotely to minimize in-person contact and comply with social distancing guidelines.
 Interviews were conducted by local staff in each country in local language(s).
 Surveying by phone made rapid, large-scale data collection possible.
-Surveys lasted approximately 15 to 40 minutes.
-
-Taken together, we have data from 21,844 individuals from LMICs and 24,084 from the USA and Russia, for a total of 45,928 respondents.
+In two samples, the USA and Russia, surveys occurred via online polling.
+All surveys lasted approximately 15 to 40 minutes.
+
+Taken together, we have data from 20,176 individuals from 10 LMICs and 24,084 from the USA and Russia, for a total of 44,260 respondents.
 
@@
 This was calculated combining all other answer options (``No'', ``Don't Know'' and ``Refuse'') into a single reference category.
-We estimated this outcome for each study with robust standard errors and employed sampling weights where available.
-
-In addition to study-level estimates, we combined data from all studies other than the USA and Russia to calculate an aggregate estimate for all LMIC studies.
-For these analyses, each included study received equal weight and standard errors were clustered at the study level.
-Averages in the ``All LMICs'' group then reflect the expected share across studies.
-In this combined analysis we also estimated the underlying heterogeneity of vaccine acceptance across studies using the between studies variance estimator \(\tau^2\) from a random effects model.
-
-We also conducted subgroup analyses by gender, age and education level and reported differences between groups.
-For the ``All LMICs'' analyses we calculated the average of differences between subgroups within studies with standard errors clustered at the study level.
-
-We additionally examined reported reasons for COVID-19 vaccine acceptance and hesitancy, as well as the types of actors respondents would trust when making the decision about whether to take a COVID-19 vaccine.
-Among respondents who expressed willingness to take the vaccine, we asked about several possible reasons why they would take it.
-For respondents unwilling to take the vaccine, we asked about several possible reasons why they would not take it.
-Finally, we asked all respondents, regardless of their answers to other questions, whom they would trust most to help them decide whether to get a COVID-19 vaccine.
-We report estimates of agreement with reasons for vaccine acceptance/hesitancy and trust in actors for individual studies and for the ``All LMICs'' group.
+We estimated average acceptance for each individual sample via ordinary least squares (OLS) weighted by respective study population weights and using robust standard errors clustered at the level of the sampling cluster.
+
+In addition to study-level estimates, we combined data from all studies other than the USA and Russia to calculate an aggregate ``All LMIC studies'' estimate.
+For these analyses, we estimated average acceptance by OLS with weights for each study normalized such that the total weight given to observations was constant across studies.
+Robust standard errors for these analyses were clustered at the study level.
+
+We note the core results would be virtually unchanged at 80.8\% (74.5--87.1) rather than 80.3\% (74.9 -85.6) using countries rather than studies as groups in the pooled analysis, that is, if we set weights so that the sum of weights in each country (rather than in each study) sum to a constant and cluster standard errors at the country level (rather than the study level).
+
+In this combined analysis, we also estimated the underlying heterogeneity of vaccine acceptance across studies using the between studies variance estimator \(\tau^2\) from a random effects model.
+
+We conducted subgroup analyses by gender, age and education level and reported differences between groups.
+For age, we selected cut-offs below 25, between age 25 and 54, and above 55 years old, closely following the age breakdown proposed by recent work on COVID-19 vaccine acceptance.\textsuperscript{\protect\hyperlink{ref-lazarus2020nature}{11}} However, the lower life expectancy (63 years on average)\textsuperscript{\protect\hyperlink{ref-wbage}{70}} and younger-skewing populations (only 5\% of the population is above 65 years old)\textsuperscript{\protect\hyperlink{ref-WorldBanksubSahara}{71}} of low-income countries in particular, precluded further disaggregation at the upper end of the age distribution.
+For education, we divided the sample between respondents who had completed secondary school and those that had not.
+We defined these two groups to reflect broader schooling trends in LMICs, where out of every 100 students entering primary education, 61\% complete lower secondary education.\textsuperscript{\protect\hyperlink{ref-world2017world}{72}} The subgroup analyses estimates are calculated in exactly the same way as the overall acceptance rate---with weights again normalized to sum to a constant within each study---with the exception that the subsample used in the analysis is limited to those respondents fitting each demographic group.
+
+We then investigated stated reasons for COVID-19 vaccine acceptance and hesitancy, and the types of actors respondents would trust most when making the decision about whether to take a COVID-19 vaccine.
+We report estimates of agreement with reasons for vaccine acceptance/hesitancy and trust in actors for individual studies and for the ``All LMICs'' group, which includes all study samples except Russia and the USA.
+Estimates were calculated with the same procedure as above, varying only the quantity of interest; i.e.~one model is run for each reason why a respondent would (or would not) take the vaccine and each trusted actor.
 
 \newpage
+
+\hypertarget{data-availability-statement}{%
+\section*{Data Availability Statement}\label{data-availability-statement}}
+\addcontentsline{toc}{section}{Data Availability Statement}
+
+Individual participant data (de-identified) that underlie the results reported in this article, are available without restrictions at \url{https://github.com/wzb-ipi/covid_vaccines_nmed}.
+
+\hypertarget{code-availability}{%
+\section*{Code Availability}\label{code-availability}}
+\addcontentsline{toc}{section}{Code Availability}
+
+All code has been deposited into the publicly available GitHub repository at \url{https://github.com/wzb-ipi/covid_vaccines_nmed}.
+The code and output for all analyses can be easily inspected at \url{https://wzb-ipi.github.io/covid_vaccines_nmed/replication.html}.
+
+\hypertarget{acknowledgements}{%
+\section*{Acknowledgements}\label{acknowledgements}}
+\addcontentsline{toc}{section}{Acknowledgements}
+
+This work would not have been possible without the hard work and ingenuity of many.
+For valuable contributions to data collection during the challenging context of the global pandemic, we would like to thank:
+
+Burkina Faso: IPA Burkina Faso staff in Ouagadougou for their support of the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+
+Colombia: IPA Colombia staff in Bogotá for their support of the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+
+India: Pronab Sen (Country Director), Kumar Das (Programme Policy Manager) and Bijeta Mohanty (Country Economist) at IGC India and Morsel Research and Development's field team.
+
+Mozambique:Frederica Mendonça and Simão Paiva from NOVAFRICA Mozambique office.
+
+Nepal: Field staff at the Centre for the Study of Labour and Mobility (CESLAM) in Kathmandu.
+
+Nigeria: Segun Fayomi and Aishwarya Kumar at the Busara Center for Behavioral Economics, and Sarah Ryan (University of Illinois at Chicago) for research assistance.
+
+Pakistan 1: Staff at the Institute for Development and Economic Alternatives (IDEAS) in Lahore for their contributions to the Sheikhupura police study sample from which the questions used in the Pakistan 1 study were drawn.
+
+Pakistan 2: Staff of the internal survey firm at the Centre for Economic Research Pakistan (CERP) for their contributions to the Economic Vulnerability Assessment (EVA) project from which the questions used in the Pakistan 2 study were drawn.
+
+Rwanda: IPA Rwanda staff in Kigali for their support of the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+
+Russia: Staff at Online Market Intelligence Survey Agency, Kirill Chmel (HSE University) and Vladimir Zabolotsky (HSE University and University of Bologna) for their intellectual contributions and research assistance.
+
+Sierra Leone 1: IPA Sierra Leone staff in Freetown for their support of the RECOVR (Research for Effective Covid Response) survey from which the questions used in this study were drawn.
+
+Sierra Leone 2: Junisa Nabieu (Field Supervisor), Momoh Flee (Field Supervisor), Hamid Kai, Mohamed Lamin (Field Supervisor) and all enumerators at IGC-Sierra Leone Freetown office and Wageningen University's Project ``Tracking the Economic Consequences of COVID-19 in Sierra Leone''.
+
+Uganda 1: Staff at IPA Uganda for their intellectual contributions, research assistance, and support throughout the study.
+
+Uganda 2: Co-PIs Ana Garcia Hernandez, Paul Kiwanuka-Mukiibi, Leah Rosenzweig, Lily Tsai, and Elly Atuhumuza and the team of survey enumerators and support staff at IPA Uganda.
+
+United States: Staff at Lucid (survey firm) for distributing the survey and providing the online survey sample.
+
+IGC thanks their resident country teams in Sierra Leone, Uganda, Pakistan, and Mozambique for their continued guidance, coordination of activities with researchers and direct engagement and dissemination activities with national policymakers:
+
+\begin{itemize}
+\tightlist
+\item
+  Herbert McLeod (Country Director) and Abou Bakarr Kamara (Country Economist) at IGC Sierra Leone
+\item
+  Richard Newfarmer (Country Director), Priya Manwaring (Country Economist), and Jakob Rauschendorfer (Country Economist) at IGC - Uganda
+\item
+  Ijaz Nabi (Country Director), Hina Shaikh (Country Economist), and Usman Naeem (Country Economist) at IGC - Pakistan
+\item
+  Claudio Frischtak (Country Director) and Egas Daniel (Country Economist) at IGC - Mozambique
+\end{itemize}
+
+IPA thanks staff from its global offices for their research assistance and support throughout the RECOVR survey.
+At IPA New York and Washington, DC, Michael Rosenbaum and Savanna Henderson provided research support.
+
+NOVAFRICA thanks Cátia Batista (NOVA SBE), Sandra Sequeira (LSE) and Inês Vilela (Royal Holloway, University of London and NOVAFRICA) for their intellectual contributions.
 
@@
 
-JSo, SW, NMe, AS, NMc, GS, MV and AM are co-first authors. DK, MC, MT, MH, AMM and SO are co-last authors. AMM and SO are also the corresponding authors.
+JSo, SW, NMe, AS, NMc, GS, MV and AAM are co-first authors. DK, MC, MT, MH, AMM and SO are co-last authors. AMM and SO are also the corresponding authors.
 DK, AMM, MT, NMe, MC, and MV conceived of the study and provided overall guidance.
-SAb and NMe led the literature search, with input from AS, NMc, SW, AMM, AM and JSo.
-SW, NMe, AS, NMc, MV, GS, AA, SA, BA, AB,EB, CMB, AC, EC, MF, AG, AK, SK, RL, MBN, MP, JSh, JSv, PV, LB, BZ, MC, SAs, AC, AF, AH, MC, MT, and MH oversaw data collection as part of other research efforts.
+SAb and NMe led the literature search, with input from AS, NMc, SW, AMM, AAM and JSo.
+SW, NMe, AS, NMc, MV, GS, AA, SA, BA, AB, EB, CMB, AC, EC, MF, AG, AK, SK, RL, MBN, MP, JQ, JSh, JSv, PV, LB, BZ, MC, SAs, AC, AF, AH, MC, MT, MH,CV, LW, BZ and BZa oversaw data collection as part of other research efforts.
+OA, DA, MA, MAw, MCG, AC, FC, GE, MG, SJA, SKa, AK, AKh, SM, GM, LM, FM, AMu, IM, JN, IO, MJO, BWO, TP, LP, MR, IR, TS, SS, , AT, AMT, HT, and BT implemented the surveys, including training and oversight of enumerators and management of sampling for the surveys.
 SW, NMe, and MT coordinated the project across study samples.
-The following verified the underlying data for individual study samples: EC (Burkina Faso, Colombia, Rwanda, Sierra Leone 1), BA (India), AS and RL (Nigeria), AG and MBN (Uganda 1), CMB and MH (Uganda 2), NMe and MV (Sierra Leone 2), GS (Russia), MF (Mozambique), AF and JSh (Pakistan 1), SAs (Pakistan 2), CV (Nepal), and NMc (USA).
+The following verified the underlying data for individual study samples: EC (Burkina Faso, Colombia, Rwanda, Sierra Leone 1), BA and AB (India), AS and RL (Nigeria), AG, JSv and MBN (Uganda 1), CMB and MH (Uganda 2), NMe and MV (Sierra Leone 2), GS (Russia), MF (Mozambique), AF and JSh (Pakistan 1), SAs (Pakistan 2), CV (Nepal), and NMc (USA).
 JSo, GS, MH and SA collated and processed all datasets used for the analysis.
@@
 MH supervised the data analysis.
-JSo, SW, NMe, AMM, AS, NMc and MV wrote the first draft of the manuscript, with guidance from AM and SO.
-JSo, SW, NMe, AS, NMc, MV, SAb, EB, MP, JSh, PV, BZ, MC, MT, MH, AMM and SO revised the manuscript.
+JSo, SW, NMe, AMM, AS, NMc and MV wrote the first draft of the manuscript, with guidance from AAM and SO.
+JSo, SW, NMe, AS, NMc, MV, SAb, EB, MP, JSh, PV, BZ, MC, MT, MH, AMM, AAM and SO revised the manuscript.
 All authors approved the final version of the manuscript. All authors had full access to all the data used in this study and had final responsibility for the decision to submit for publication.
-
-\hypertarget{data-availability-statement}{%
-\section*{Data Availability Statement}\label{data-availability-statement}}
-\addcontentsline{toc}{section}{Data Availability Statement}
-
-Individual participant data (de-identified) that underlie the results reported in this article, analytic code and replication files will be available immediately following publication to no end date for anyone who wishes to access the data and use it for any purpose in a public, open access repository.
-A replication exercise is available here \url{https://wzb-ipi.github.io/covid_vaccines/replication.html}.
 
@@
 \leavevmode\hypertarget{ref-boyon2020ipsos}{}%
-\CSLLeftMargin{4. }
-\CSLRightInline{Boyon, N. Global attitudes on a covid vaccine. (2020).}
+\CSLLeftMargin{5. }
+\CSLRightInline{Ipsos-World Economic Forum. {Global attitudes: COVID-19 vaccines}. \url{https://www.ipsos.com/en-ro/global-attitudes-covid-19-vaccine-january-2021} (2021).}
 
 \leavevmode\hypertarget{ref-Malik2020}{}%
-\CSLLeftMargin{5. }
-\CSLRightInline{Malik, A., McFadden, S., Elharake, J. \& Omer, S. Determinants of COVID-19 vaccine acceptance in the US. \emph{EClinicalMedicine} \textbf{26}, 100495 (2020).}
-
-\leavevmode\hypertarget{ref-mukherjee}{}%
 \CSLLeftMargin{6. }
-\CSLRightInline{Mukherjee, S. Why does the pandemic seem to be hitting some countries harder than others? \emph{New Yorker} (2021).}
+\CSLRightInline{Malik, A., McFadden, S., Elharake, J. \& Omer, S. {Determinants of COVID-19 vaccine acceptance in the US}. \emph{EClinicalMedicine} \textbf{26}, 100495 (2020).}
+
+\leavevmode\hypertarget{ref-kreps2020factors}{}%
+\CSLLeftMargin{7. }
+\CSLRightInline{Kreps, S. \emph{et al.} {Factors associated with US adults' likelihood of accepting COVID-19 vaccination}. \emph{JAMA Network Open} \textbf{3}, e2025594--e2025594 (2020).}
+
+\leavevmode\hypertarget{ref-shekhar2021covid}{}%
+\CSLLeftMargin{8. }
+\CSLRightInline{Shekhar, R. \emph{et al.} {COVID-19 vaccine acceptance among health care workers in the United States}. \emph{Vaccines} \textbf{9}, 119 (2021).}
+
+\leavevmode\hypertarget{ref-dror2020vaccine}{}%
+\CSLLeftMargin{9. }
+\CSLRightInline{Dror, A. A. \emph{et al.} {Vaccine hesitancy: the next challenge in the fight against COVID-19}. \emph{{European Journal of Epidemiology}} \textbf{35}, 775--779 (2020).}
+
+\leavevmode\hypertarget{ref-fisher2020attitudes}{}%
+\CSLLeftMargin{10. }
+\CSLRightInline{Fisher, K. A. \emph{et al.} {Attitudes toward a potential SARS-CoV-2 vaccine: a survey of US adults}. \emph{{Annals of Internal Medicine}} \textbf{173}, 964--973 (2020).}
+
+\leavevmode\hypertarget{ref-lazarus2020nature}{}%
+\CSLLeftMargin{11. }
+\CSLRightInline{Lazarus, J. V. \emph{et al.} {A global survey of potential acceptance of a COVID-19 vaccine}. \emph{Nature medicine} \textbf{27}, 225--228 (2021).}
+
+\leavevmode\hypertarget{ref-ong2021lack}{}%
+\CSLLeftMargin{12. }
+\CSLRightInline{Ong, S.
+W.
+X., Young, B.
+E.
+\& Lye, D.
+C.
+{Lack of detail in population-level data impedes analysis of SARS-CoV-2 variants of concern and clinical outcomes}.
+\emph{The Lancet Infectious Diseases} (2021).}
+
+\leavevmode\hypertarget{ref-lancettask}{}%
+\CSLLeftMargin{13. }
+\CSLRightInline{The Lancet COVID-19 Comission Task Force on Public Health Measures to Suppress the Pandemic.
+{SARS-CoV-2 variants: the need for urgent public health action beyond vaccines}.
+\url{https://covid19commission.org/public-health-measures} (2021).}
+
+\leavevmode\hypertarget{ref-biccard2021patient}{}%
+\CSLLeftMargin{14. }
+\CSLRightInline{Biccard, B.
+M.
+\emph{et al.} Patient care and clinical outcomes for patients with COVID-19 infection admitted to african high-care or intensive care units (ACCCOS): A multicentre, prospective, observational cohort study.
+\emph{The Lancet} \textbf{397}, 1885--1894 (2021).}
+
+\leavevmode\hypertarget{ref-rice2021variation}{}%
+\CSLLeftMargin{15. }
+\CSLRightInline{Rice, B. L. \emph{et al.} Variation in SARS-CoV-2 outbreaks across sub-saharan africa. \emph{Nature Medicine} \textbf{27}, 447--453 (2021).}
+
+\leavevmode\hypertarget{ref-maeda2021puzzle}{}%
+\CSLLeftMargin{16. }
+\CSLRightInline{Maeda, J. M. \& Nkengasong, J. N. The puzzle of the COVID-19 pandemic in africa. \emph{Science} \textbf{371}, 27--28 (2021).}
+
+\leavevmode\hypertarget{ref-brewer2007meta}{}%
+\CSLLeftMargin{17. }
+\CSLRightInline{Brewer, N.
+T.
+\emph{et al.} Meta-analysis of the relationship between risk perception and health behavior: The example of vaccination.
+\emph{Health psychology} \textbf{26}, 136 (2007).}
 
 \leavevmode\hypertarget{ref-christensen2020building}{}%
-\CSLLeftMargin{7. }
+\CSLLeftMargin{18. }
 \CSLRightInline{Christensen, D., Dube, O., Haushofer, J., Siddiqi, B.
 \& Voors, M.
-\emph{Building resilient health systems: Experimental evidence from sierra leone and the 2014 ebola outbreak}.
-(The Quarterly Journal of Economics, 2021).}
+{Building Resilient Health Systems: Experimental Evidence from Sierra Leone and the 2014 Ebola Outbreak}.
+\emph{The Quarterly Journal of Economics} \textbf{136}, 1145--1198 (2021).}
 
 \leavevmode\hypertarget{ref-Lowes2018}{}%
-\CSLLeftMargin{8. }
-\CSLRightInline{Lowes, S. R. \& Montero, E. The legacy of colonial medicine in central africa. (2018).}
+\CSLLeftMargin{19. }
+\CSLRightInline{Lowes, S. \& Montero, E. {The legacy of colonial medicine in Central Africa}. \emph{American Economic Review} \textbf{111}, 1284--1314 (2021).}
+
+\leavevmode\hypertarget{ref-martinez2021vaccines}{}%
+\CSLLeftMargin{20. }
+\CSLRightInline{Martinez-Bravo, M. \& Stegmann, A. {In Vaccines We Trust? The Effects of the Cia's Vaccine Ruse on Immunization in Pakistan}. \emph{CEPR Discussion Paper No. DP15847} (2021).}
 
 \leavevmode\hypertarget{ref-Jegede2007}{}%
-\CSLLeftMargin{9. }
-\CSLRightInline{Jegede, A. S. What led to the nigerian boycott of the polio vaccination campaign? \emph{PLOS Medicine} \textbf{4(3)}, (2007).}
+\CSLLeftMargin{21. }
+\CSLRightInline{Jegede, A. S. {What led to the Nigerian boycott of the polio vaccination campaign?} \emph{PLOS Medicine} \textbf{4(3)}, (2007).}
 
 \leavevmode\hypertarget{ref-BLAIR201789}{}%
-\CSLLeftMargin{10. }
+\CSLLeftMargin{22. }
 \CSLRightInline{Blair, R., Morse, B.
 \& Tsai, L.
-Public health and public trust: Survey evidence from the ebola virus disease epidemic in liberia.
+{Public health and public trust: Survey evidence from the Ebola Virus Disease epidemic in Liberia}.
 \emph{Social Science \& Medicine} \textbf{172}, 89--97 (2017).}
 
+\leavevmode\hypertarget{ref-ali2019polio}{}%
+\CSLLeftMargin{23. }
+\CSLRightInline{Ali, M. \emph{et al.} Polio vaccination controversy in pakistan. \emph{The Lancet} \textbf{394}, 915--916 (2019).}
+
+\leavevmode\hypertarget{ref-robbins2012cia}{}%
+\CSLLeftMargin{24. }
+\CSLRightInline{Robbins, A. The CIA's vaccination ruse. \emph{Journal of Public Health Policy} \textbf{33}, 387--389 (2012).}
+
+\leavevmode\hypertarget{ref-deserrano}{}%
+\CSLLeftMargin{25. }
+\CSLRightInline{Deserranno, E. \& León-Ciliotta, G. {Promotions and Productivity: The Role of Meritocracy and Pay Progression in the Public Sector}. \emph{CEPR Discussion Paper No. DP15837} (2021).}
+
+\leavevmode\hypertarget{ref-betsch2018beyond}{}%
+\CSLLeftMargin{26. }
+\CSLRightInline{Betsch, C. \emph{et al.} Beyond confidence: Development of a measure assessing the 5C psychological antecedents of vaccination. \emph{PloS one} \textbf{13}, e0208601 (2018).}
+
+\leavevmode\hypertarget{ref-domek2018measuring}{}%
+\CSLLeftMargin{27. }
+\CSLRightInline{Domek, G.
+J.
+\emph{et al.} Measuring vaccine hesitancy: Field testing the WHO SAGE working group on vaccine hesitancy survey tool in guatemala.
+\emph{Vaccine} \textbf{36}, 5273--5281 (2018).}
+
+\leavevmode\hypertarget{ref-shapiro2018vaccine}{}%
+\CSLLeftMargin{28. }
+\CSLRightInline{Shapiro, G. K. \emph{et al.} The vaccine hesitancy scale: Psychometric properties and validation. \emph{Vaccine} \textbf{36}, 660--667 (2018).}
+
+\leavevmode\hypertarget{ref-gilkey2014vaccination}{}%
+\CSLLeftMargin{29. }
+\CSLRightInline{Gilkey, M. B. \emph{et al.} The vaccination confidence scale: A brief measure of parents' vaccination beliefs. \emph{Vaccine} \textbf{32}, 6259--6265 (2014).}
+
+\leavevmode\hypertarget{ref-whodata}{}%
+\CSLLeftMargin{30. }
+\CSLRightInline{World Health Organization.
+{Data for action: achieving high uptake of COVID-19 vaccines}.
+\url{https://www.who.int/publications/i/item/WHO-2019-nCoV-vaccination-demand-planning-2021.1} (2021).}
+
 \leavevmode\hypertarget{ref-chou2020considering}{}%
-\CSLLeftMargin{11. }
+\CSLLeftMargin{31. }
 \CSLRightInline{Chou, W.-Y.
@@
 
-\leavevmode\hypertarget{ref-cdcadverse}{}%
-\CSLLeftMargin{12. }
-\CSLRightInline{Centre for Disease Control and Prevention.
-{Local Reactions, Systemic Reactions, Adverse Events, and Serious Adverse Events: Pfizer-BioNTech COVID-19 Vaccine}.
-\url{https://www.cdc.gov/vaccines/covid-19/info-by-product/pfizer/reactogenicity.html} (2020).}
+\leavevmode\hypertarget{ref-mulligan2020phase}{}%
+\CSLLeftMargin{32. }
+\CSLRightInline{Mulligan, M. J. \emph{et al.} Phase i/II study of COVID-19 RNA vaccine BNT162b1 in adults. \emph{Nature} \textbf{586}, 589--593 (2020).}
+
+\leavevmode\hypertarget{ref-logunov2021safety}{}%
+\CSLLeftMargin{33. }
+\CSLRightInline{Logunov, D.
+Y.
+\emph{et al.} Safety and efficacy of an rAd26 and rAd5 vector-based heterologous prime-boost COVID-19 vaccine: An interim analysis of a randomised controlled phase 3 trial in russia.
+\emph{The Lancet} \textbf{397}, 671--681 (2021).}
+
+\leavevmode\hypertarget{ref-folegatti2020safety}{}%
+\CSLLeftMargin{34. }
+\CSLRightInline{Folegatti, P.
+M.
+\emph{et al.} Safety and immunogenicity of the ChAdOx1 nCoV-19 vaccine against SARS-CoV-2: A preliminary report of a phase 1/2, single-blind, randomised controlled trial.
+\emph{The Lancet} \textbf{396}, 467--478 (2020).}
+
+\leavevmode\hypertarget{ref-voysey2021safety}{}%
+\CSLLeftMargin{35. }
+\CSLRightInline{Voysey, M.
+\emph{et al.} Safety and efficacy of the ChAdOx1 nCoV-19 vaccine (AZD1222) against SARS-CoV-2: An interim analysis of four randomised controlled trials in brazil, south africa, and the UK.
+\emph{The Lancet} \textbf{397}, 99--111 (2021).}
+
+\leavevmode\hypertarget{ref-baden2021efficacy}{}%
+\CSLLeftMargin{36. }
+\CSLRightInline{Baden, L. R. \emph{et al.} Efficacy and safety of the mRNA-1273 SARS-CoV-2 vaccine. \emph{New England Journal of Medicine} \textbf{384}, 403--416 (2021).}
+
+\leavevmode\hypertarget{ref-polack2020safety}{}%
+\CSLLeftMargin{37. }
+\CSLRightInline{Polack, F. P. \emph{et al.} Safety and efficacy of the BNT162b2 mRNA covid-19 vaccine. \emph{New England Journal of Medicine} \textbf{383}, 2603--2615 (2020).}
+
+\leavevmode\hypertarget{ref-wadman2020public}{}%
+\CSLLeftMargin{38. }
+\CSLRightInline{Wadman, M. Public needs to prep for vaccine side effects. \emph{Science} \textbf{370}, 1022--1022 (2020).}
+
+\leavevmode\hypertarget{ref-callaway2020russia}{}%
+\CSLLeftMargin{39. }
+\CSLRightInline{Callaway, E. Russia's fast-track coronavirus vaccine draws outrage over safety. \emph{Nature} \textbf{584}, 334--335 (2020).}
 
 \leavevmode\hypertarget{ref-stein2017golden}{}%
-\CSLLeftMargin{13. }
+\CSLLeftMargin{40. }
 \CSLRightInline{Stein, R. A. The golden age of anti-vaccine conspiracies. \emph{Germs} \textbf{7}, 168 (2017).}
 
-\leavevmode\hypertarget{ref-wadman2020public}{}%
-\CSLLeftMargin{14. }
-\CSLRightInline{Wadman, M. Public needs to prep for vaccine side effects. (2020).}
-
-\leavevmode\hypertarget{ref-cdcallergies}{}%
-\CSLLeftMargin{15. }
-\CSLRightInline{CDC COVID-19 Response Team \& Food and Drug Administration.
-{Allergic Reactions Including Anaphylaxis After Receipt of the First Dose of Pfizer-BioNTech COVID-19 Vaccine --- United States, December 14--23, 2020}.
-\url{https://www.cdc.gov/mmwr/volumes/70/wr/mm7002e1.htm\#:~:text=Early\%20safety\%20monitoring\%20of\%20the,nonanaphylaxis\%20allergic\%20reactions\%2C\%20based\%20on} (2021).}
-
-\leavevmode\hypertarget{ref-baden2021efficacy}{}%
-\CSLLeftMargin{16. }
-\CSLRightInline{Baden, L. R. \emph{et al.} Efficacy and safety of the mRNA-1273 SARS-CoV-2 vaccine. \emph{New England Journal of Medicine} \textbf{384}, 403--416 (2021).}
-
-\leavevmode\hypertarget{ref-polack2020safety}{}%
-\CSLLeftMargin{17. }
-\CSLRightInline{Polack, F. P. \emph{et al.} Safety and efficacy of the BNT162b2 mRNA covid-19 vaccine. \emph{New England Journal of Medicine} \textbf{383}, 2603--2615 (2020).}
-
 \leavevmode\hypertarget{ref-loomba_measuring_2021}{}%
-\CSLLeftMargin{18. }
-\CSLRightInline{Loomba, S., Figueiredo, A.
-de, Piatek, S.
+\CSLLeftMargin{41. }
+\CSLRightInline{Loomba, S., de Figueiredo, A., Piatek, S.
 J., Graaf, K.
@@
 
-\leavevmode\hypertarget{ref-siegrist2014role}{}%
-\CSLLeftMargin{19. }
-\CSLRightInline{Siegrist, M. \& Zingg, A. The role of public trust during pandemics: Implications for crisis communication. \emph{European Psychologist} \textbf{19}, 23 (2014).}
-
-\leavevmode\hypertarget{ref-britten2020}{}%
-\CSLLeftMargin{20. }
-\CSLRightInline{Britton, T., Ball, F.
-\& Trapman, P.
-A mathematical model reveals the influence of population heterogeneity on herd immunity to SARS-CoV-2.
-\emph{Science} \textbf{369}, 846--849 (2020).}
-
-\leavevmode\hypertarget{ref-haley2020}{}%
-\CSLLeftMargin{21. }
-\CSLRightInline{Randolph, H. E. \& Barreiro, L. B. Herd immunity: Understanding COVID-19. \emph{Immunity} \textbf{52}, 737--741 (2020).}
+\leavevmode\hypertarget{ref-ontario}{}%
+\CSLLeftMargin{42. }
+\CSLRightInline{Public Health Ontario.
+{COVID-19- What We Know So Far About\ldots{} Herd Immunity}.
+\url{https://www.publichealthontario.ca/-/media/documents/ncov/covid-wwksf/2021/02/wwksf-herd-immunity.pdf?la=en} (2021).}
+
+\leavevmode\hypertarget{ref-aschwanden2021five}{}%
+\CSLLeftMargin{43. }
+\CSLRightInline{Aschwanden, C. Five reasons why COVID herd immunity is probably impossible. \emph{Nature} \textbf{591}, 520--522 (2021).}
+
+\leavevmode\hypertarget{ref-mcneil_2021}{}%
+\CSLLeftMargin{44. }
+\CSLRightInline{McNeil, D. G. How much herd immunity is enough? \emph{The New York Times} (2021).}
 
 \leavevmode\hypertarget{ref-mceachanetal2011}{}%
-\CSLLeftMargin{22. }
+\CSLLeftMargin{45. }
 \CSLRightInline{Mceachan, R., Conner, M., Taylor, N.
@@
 
-\leavevmode\hypertarget{ref-chen1996}{}%
-\CSLLeftMargin{23. }
-\CSLRightInline{Chen, R. T. \& Orenstein, W. A. Epidemiologic methods in immunization programs. \emph{Epidemiologic Reviews} \textbf{18}, 99--117 (1996).}
-
-\leavevmode\hypertarget{ref-alatas2019celebrities}{}%
-\CSLLeftMargin{24. }
-\CSLRightInline{Alatas, V., Chandrasekhar, A. G., Mobius, M., Olken, B. A. \& Paladines, C. \emph{When celebrities speak: A nationwide twitter experiment promoting vaccination in indonesia}. (2019).}
+\leavevmode\hypertarget{ref-larson2011addressing}{}%
+\CSLLeftMargin{46. }
+\CSLRightInline{Larson, H. J., Cooper, L. Z., Eskola, J., Katz, S. L. \& Ratzan, S. Addressing the vaccine confidence gap. \emph{The Lancet} \textbf{378}, 526--535 (2011).}
+
+\leavevmode\hypertarget{ref-hornsey2020donald}{}%
+\CSLLeftMargin{47. }
+\CSLRightInline{Hornsey, M.
+J., Finlayson, M., Chatwood, G.
+\& Begeny, C.
+T.
+Donald trump and vaccination: The effect of political identity, conspiracist ideation and presidential tweets on vaccine hesitancy.
+\emph{Journal of Experimental Social Psychology} \textbf{88}, 103947 (2020).}
 
 \leavevmode\hypertarget{ref-bokemper2021timing}{}%
-\CSLLeftMargin{25. }
+\CSLLeftMargin{48. }
 \CSLRightInline{Bokemper, S.
@@
 
+\leavevmode\hypertarget{ref-aaslund2020responses}{}%
+\CSLLeftMargin{49. }
+\CSLRightInline{Åslund, A. Responses to the COVID-19 crisis in russia, ukraine, and belarus. \emph{Eurasian Geography and Economics} \textbf{61}, 532--545 (2020).}
+
+\leavevmode\hypertarget{ref-burki2020russian}{}%
+\CSLLeftMargin{50. }
+\CSLRightInline{Burki, T. K. The russian vaccine for COVID-19. \emph{The Lancet Respiratory Medicine} \textbf{8}, e85--e86 (2020).}
+
 \leavevmode\hypertarget{ref-milkmanetal2021a}{}%
-\CSLLeftMargin{26. }
+\CSLLeftMargin{51. }
 \CSLRightInline{Milkman, K. L. \emph{et al.} A mega-study of text-based nudges encouraging patients to get vaccinated at an upcoming doctor's appointment. (2021).}
@@
 \leavevmode\hypertarget{ref-milkmanetal2021b}{}%
-\CSLLeftMargin{27. }
+\CSLLeftMargin{52. }
 \CSLRightInline{Milkman, K. L. \emph{et al.} A mega-study of text-message nudges encouraging patients to get vaccinated at their pharmacy. (2021).}
 
+\leavevmode\hypertarget{ref-levine2021}{}%
+\CSLLeftMargin{53. }
+\CSLRightInline{Levine, G., Salifu, A., Mohammed, I.
+\& Fink, G.
+{Mobile Nudges and Financial Incentives to Improve Coverage of Timely Neonatal Vaccination in Rural Areas (GEVaP trial): A 3-armed Cluster Randomized Controlled Trial in Northern Ghana}.
+\emph{PLOS One} (2021).}
+
 \leavevmode\hypertarget{ref-gibsonetal2017}{}%
-\CSLLeftMargin{28. }
+\CSLLeftMargin{54. }
 \CSLRightInline{Gibson, D.
 G.
-\emph{et al.} Mobile phone-delivered reminders and incentives to improve childhood immunisation coverage and timeliness in kenya (m-SIMU): A cluster randomised controlled trial.
+\emph{et al.} {Mobile phone-delivered reminders and incentives to improve childhood immunisation coverage and timeliness in Kenya (M-SIMU): a cluster randomised controlled trial}.
 \emph{The Lancet Global Health} \textbf{5}, e428--e438 (2017).}
@@
 \leavevmode\hypertarget{ref-idinsight}{}%
-\CSLLeftMargin{29. }
-\CSLRightInline{Insight, I.
+\CSLLeftMargin{55. }
+\CSLRightInline{ID Insight.
 {Impact of conditional cash transfers on routine childhood immunizations in North West Nigeria}.
@@
 \leavevmode\hypertarget{ref-Banerjee2010}{}%
-\CSLLeftMargin{30. }
+\CSLLeftMargin{56. }
 \CSLRightInline{Banerjee, A.
@@
 \& Kothari, D.
-Improving immunisation coverage in rural india: Clustered randomised controlled evaluation of immunisation campaigns with and without incentives.
+{Improving immunisation coverage in rural India: clustered randomised controlled evaluation of immunisation campaigns with and without incentives}.
 \emph{BMJ} \textbf{340}, (2010).}
 
-\leavevmode\hypertarget{ref-beaman2021can}{}%
-\CSLLeftMargin{31. }
-\CSLRightInline{Beaman, L., BenYishay, A., Magruder, J. \& Mobarak, A. M. \emph{Can network theory-based targeting increase technology adoption?} (2021).}
+\leavevmode\hypertarget{ref-brewer2017increasing}{}%
+\CSLLeftMargin{57. }
+\CSLRightInline{Brewer, N.
+T., Chapman, G.
+B., Rothman, A.
+J., Leask, J.
+\& Kempe, A.
+Increasing vaccination: Putting psychological science into action.
+\emph{Psychological Science in the Public Interest} \textbf{18}, 149--207 (2017).}
+
+\leavevmode\hypertarget{ref-betsch2013inviting}{}%
+\CSLLeftMargin{58. }
+\CSLRightInline{Betsch, C., Böhm, R.
+\& Korn, L.
+Inviting free-riders or appealing to prosocial behavior?
+Game-theoretical reflections on communicating herd immunity in vaccine advocacy.
+\emph{Health Psychology} \textbf{32}, 978 (2013).}
+
+\leavevmode\hypertarget{ref-dube2015strategies}{}%
+\CSLLeftMargin{59. }
+\CSLRightInline{Dubé, E., Gagnon, D., MacDonald, N. E. \& others. Strategies intended to address vaccine hesitancy: Review of published reviews. \emph{Vaccine} \textbf{33}, 4191--4203 (2015).}
+
+\leavevmode\hypertarget{ref-who2020behavioral}{}%
+\CSLLeftMargin{60. }
+\CSLRightInline{World Health Organization.
+{Behavioural considerations for acceptance and uptake of COVID-19 vaccines: WHO technical advisory group on behavioural insights and sciences for health, meeting report, 15 October 2020}.
+\url{https://apps.who.int/iris/handle/10665/337335} (2020).}
+
+\leavevmode\hypertarget{ref-katzman2021primary}{}%
+\CSLLeftMargin{61. }
+\CSLRightInline{Katzman, J. G. \& Katzman, J. W. Primary care clinicians as COVID-19 vaccine ambassadors. \emph{Journal of Primary Care \& Community Health} \textbf{12}, 21501327211007026 (2021).}
+
+\leavevmode\hypertarget{ref-alatas2019celebrities}{}%
+\CSLLeftMargin{62. }
+\CSLRightInline{Alatas, V., Chandrasekhar, A.
+G., Mobius, M., Olken, B.
+A.
+\& Paladines, C.
+When celebrities speak: A nationwide twitter experiment promoting vaccination in indonesia.
+\emph{National Bureau of Economic Research} (2019).}
+
+\leavevmode\hypertarget{ref-goldstein2015health}{}%
+\CSLLeftMargin{63. }
+\CSLRightInline{Goldstein, S., MacDonald, N. E., Guirguis, S. \& others. Health communication and vaccine hesitancy. \emph{Vaccine} \textbf{33}, 4212--4214 (2015).}
+
+\leavevmode\hypertarget{ref-puri2020social}{}%
+\CSLLeftMargin{64. }
+\CSLRightInline{Puri, N., Coomes, E.
+A., Haghbayan, H.
+\& Gunaratne, K.
+Social media and vaccine hesitancy: New updates for the era of COVID-19 and globalized infectious diseases.
+\emph{Human Vaccines \& Immunotherapeutics} 1--8 (2020).}
+
+\leavevmode\hypertarget{ref-argote2021messaging}{}%
+\CSLLeftMargin{65. }
+\CSLRightInline{Argote, P. \emph{et al.} Messaging interventions that increase COVID-19 vaccine willingness in latin america. \emph{SSRN 3812023} (2021).}
+
+\leavevmode\hypertarget{ref-van2020using}{}%
+\CSLLeftMargin{66. }
+\CSLRightInline{Van Bavel, J. J. \emph{et al.} Using social and behavioural science to support COVID-19 pandemic response. \emph{Nature human behaviour} \textbf{4}, 460--471 (2020).}
 
 \leavevmode\hypertarget{ref-karing2018social}{}%
-\CSLLeftMargin{32. }
+\CSLLeftMargin{67. }
 \CSLRightInline{Karing, A. Social signaling and childhood immunization: A field experiment in sierra leone. \emph{University of California, Berkeley Working Paper} (2018).}
 
-\leavevmode\hypertarget{ref-Duch2021}{}%
-\CSLLeftMargin{33. }
-\CSLRightInline{Duch, R. \emph{et al.} Who should be first in line for the COVID-19 vaccine? Surveys in 13 countries of the public{'}s preferences for prioritisation. \emph{medRxiv} (2021).}
-
-\leavevmode\hypertarget{ref-lazarus2020nature}{}%
-\CSLLeftMargin{34. }
-\CSLRightInline{Lazarus, J. V. \emph{et al.} A global survey of potential acceptance of a COVID-19 vaccine. \emph{Nature Medecine} 1--4 (2020).}
-
-\leavevmode\hypertarget{ref-wbinternet}{}%
-\CSLLeftMargin{35. }
-\CSLRightInline{World Bank, W. D. I. \url{https://data.worldbank.org/indicator/IT.NET.USER.ZS?locations=XO} (2019).}
+\leavevmode\hypertarget{ref-ashraf2014no}{}%
+\CSLLeftMargin{68. }
+\CSLRightInline{Ashraf, N., Bandiera, O.
+\& Jack, B.
+K.
+No margin, no mission?
+A field experiment on incentives for public service delivery.
+\emph{Journal of public economics} \textbf{120}, 1--17 (2014).}
+
+\leavevmode\hypertarget{ref-jalloh2020mobilize}{}%
+\CSLLeftMargin{69. }
+\CSLRightInline{Jalloh, M.
+F., Wilhelm, E., Abad, N.
+\& Prybylski, D.
+Mobilize to vaccinate: Lessons learned from social mobilization for immunization in low and middle-income countries.
+\emph{Human vaccines \& immunotherapeutics} \textbf{16}, 1208--1214 (2020).}
+
+\leavevmode\hypertarget{ref-wbage}{}%
+\CSLLeftMargin{70. }
+\CSLRightInline{World Bank.
+{World Development Indicators: Life expectancy at birth, total (years) - Low \& middle income, Low income countries {[}Data file{]}}.
+\url{https://data.worldbank.org/indicator/SP.DYN.LE00.IN?locations=XO-XM} (2018).}
+
+\leavevmode\hypertarget{ref-WorldBanksubSahara}{}%
+\CSLLeftMargin{71. }
+\CSLRightInline{World Bank.
+{World Bank staff estimates based on age/sex distributions of United Nations Population Division's World Population Prospects: 2019 Revision, Population ages 65 and above (\% of total population) - Sub-Saharan Africa {[}Data file{]}}.
+\url{https://data.worldbank.org/indicator/SP.POP.65UP.TO.ZS?locations=ZG} (2019).}
+
+\leavevmode\hypertarget{ref-world2017world}{}%
+\CSLLeftMargin{72. }
+\CSLRightInline{Bank, W. \emph{World development report 2018: Learning to realize education's promise}. (The World Bank, 2017).}
+
+\leavevmode\hypertarget{ref-mukherjee}{}%
+\CSLLeftMargin{73. }
+\CSLRightInline{Mukherjee, S. Why does the pandemic seem to be hitting some countries harder than others? \emph{New Yorker} (2021).}
+
+\leavevmode\hypertarget{ref-dong2020interactive}{}%
+\CSLLeftMargin{74. }
+\CSLRightInline{Dong, E., Du, H. \& Gardner, L. An interactive web-based dashboard to track COVID-19 in real time. \emph{The Lancet infectious diseases} \textbf{20}, 533--534 (2020).}
+
+\leavevmode\hypertarget{ref-coppock2019validating}{}%
+\CSLLeftMargin{75. }
+\CSLRightInline{Coppock, A.
+\& McClellan, O.
+A.
+Validating the demographic, political, psychological, and experimental results obtained from a new source of online survey respondents.
+\emph{Research \& Politics} \textbf{6}, 2053168018822174 (2019).}
 
 \end{CSLReferences}
+
+\begin{table}[!h]
+\caption{\label{tab:summary}Policy summary}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{30em}}
+\toprule
+Background & 
+We analyze COVID-19 vaccine acceptance, hesitancy and their drivers across 15 survey samples covering ten low- and middle-income countries (LMICs) in Asia, Africa, and South America, as well as Russia and the United States, comprising 44,260 individuals.
+\\
+\\
+Main findings and limitations & Willingness to take a COVID-19 vaccine is considerably higher in the LMICs in our sample than in the United States and Russia.
+The personal protective benefit of vaccination is the most frequently cited reason for vaccine acceptance.
+Concern about side effects is the most commonly cited reason for vaccine hesitancy.
+Health workers are considered the most trusted sources of guidance about COVID-19 vaccine choices.
+Our data are not representative of all LMICs, and some individual samples are not nationally representative.
+However, our main findings---of high COVID-19 vaccine acceptance in our LMIC samples relative to the USA and Russia---are remarkably consistent across samples and specifications.
+\\
+\\
+Policy implications & While global vaccine distribution has skewed heavily toward higher income countries to date, the high levels of vaccine acceptance we identify suggest that prioritizing distribution to LMICs may be an efficient way to achieve immunity on a global scale, and prevent novel variants from emerging.
+Vaccination campaigns should focus on converting positive intentions into uptake, which may require investment in ‘last-mile’ delivery.
+Engaging health workers to deliver vaccine information, leveraging pro-vaccine norms, and messaging focused on vaccine effectiveness and safety may be effective in addressing remaining hesitancy.\\
+\bottomrule
+\end{tabular}}
+\end{table}
+
+\newpage
+
+\begin{landscape}\begin{table}[!h]
+
+\caption{\label{tab:sampling}Summary of studies sampling}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{12em}>{\raggedright\arraybackslash}p{30em}ll}
+\toprule
+\textbf{Study} & \textbf{Date} & \textbf{Geographic scope} & \textbf{Sampling methodology} & \textbf{Survey modality} & \textbf{Weights}\\
+\midrule
+Burkina Faso & October 15 to December 4, 2020 & National & Random digit dialing (RDD) & Phone & Yes\\
+Colombia & August 15-25, 2020 & National & Random digit dialing (RDD) & Phone & Yes\\
+India & June 17, 2020 to January 18, 2021 & Subnational, Slums in 2 cities & Representative sample of slum dwellers living in vicinity of a community toilet and located in Uttar Pradesh & Phone & Yes\\
+Mozambique & October 30 to November 30, 2020 & Subnational, 2 cities & Random sample in urban and periurban markets stratified by gender and type of establishment in Maputo; and random sample representative of communities in the Cabo Delgado, stratified on urban, semiurban, and rural areas & Phone & No\\
+Nepal & December 1-11, 2020 & Subnational, 2 districts & Random sample of poor households from randomly selected villages in Kanchanpur & Phone & Yes\\
+Nigeria & November 18 to December 18, 2020 & Subnational, 1 state & Random sample of individuals in Kaduna; and Sample of phone numbers from a phone list of Kaduna state residents & Phone & No\\
+Pakistan 1 & July 24 to September 9, 2020 & Subnational, 2 districts & Random sample of individuals in administrative police units in two districts of Punjab & Phone & Yes\\
+Pakistan 2 & September 2 to October 13, 2020 & Subnational, 1 province & Random digit dialing (RDD) on a random sample of all numerically possible mobile phone numbers in the region of Punjab & Phone & No\\
+Russia & November 6 to December 1, 2020 & Subnational, 61 regions & Sample recruited from the Russian online survey company OMI (Online Market Intelligence).
+Sampling targeted at having a minimum of respondents per region, as well as representation of age, gender and education groups.
+& Online & Yes\\
+Rwanda & October 22 to November 15, 2020 & National & Random digit dialing (RDD) & Phone & Yes\\
+Sierra Leone 1 & October 2-19, 2020 & National & Random digit dialing (RDD) & Phone & Yes\\
+Sierra Leone 2 & October 7, 2020 to January 20, 2021 & National & A random sample of households in 195 rural towns across all 14 districts of Sierra Leone & Phone & No\\
+Uganda 1 & September 21 to December 6, 2020 & Subnational, 13 districts & Sample of women in households from semi-rural and rural villages across 13 districts in Uganda, selected according to the likelihood of having children & Phone & No\\
+Uganda 2 & November 23 to December 12, 2020 & Subnational, 1 district & Random sample of households in Kampala & Phone & No\\
+USA & December 4-5, 2020 & National & Nation-wide sample of adult internet users recruited through the market research firm Lucid & Online & Yes\\
+\bottomrule
+\end{tabular}}
+\end{table}
+\end{landscape}
 
@@
 \begin{tablenotes}
-\item Table 1 presents an overview of vaccination beliefs and incidence across countries in our sample.
+\item Table 2 presents an overview of vaccination beliefs and incidence across countries in our sample.
 Columns 2-4 and 8 use data from the Wellcome Global Monitor 2018.
@@
 \end{landscape}
+\newpage
 
@@
 \end{figure}
+
+\begin{figure}[!ht]
+\caption{Reasons not to take the vaccine \label{fig:fig2paper}}
+
+\includegraphics{paper_files/figure-latex/fig2paper-1.pdf}
+
+\scriptsize{Figure 2 shows the percentage of respondents mentioning reasons why they would not take the COVID-19 vaccine.
+For each study, we present the sample size in parentheses.
+Data are presented as mean values +/- SD.
+In the plot, points represent the estimated percentage of individuals that would not take the vaccine or do not know if they would take the vaccine for each possible response option.
+Bars around each point indicate a 95\% confidence interval for the estimate.
+An estimated average for all studies in LMICs is also shown.
+Studies India and Pakistan 2 are not included because they either did not include the question or were not properly harmonized with the other studies.}
+\end{figure}
+
+\begin{figure}[!ht]
+\caption{Trusted actors and institutions, broken down by expressed willingness to take a COVID-19 vaccine \label{fig:fig3paper}}
+
+\newpage
+
+\includegraphics{paper_files/figure-latex/fig3paper-1.pdf}
+\newpage
+
+\scriptsize{Figure 3 shows histograms of actors and institutions respondents say they would trust most to help them decide whether to take the COVID-19 vaccine.
+Respondents were only permitted to select one most trusted actor or institution.
+Studies India, Mozambique, Pakistan 1, Pakistan 2 and Uganda 1 are not included because they either did not include the question or were not properly harmonized with the other studies.}
+\end{figure}
+
+\newpage
+
+\begin{figure}[!ht]
+\caption{Trusted actors and institutions, broken down by gender \label{fig:genderhist}}
+
+\includegraphics{paper_files/figure-latex/genderhist-1.pdf}
+
+\scriptsize{Figure S1 shows histograms of actors and institutions that respondents say they would trust most to help them decide whether or not to take the COVID-19 vaccine.
+Respondents were only permitted to select one most trusted  actor or institution.
+Responses are broken down by gender of respondent.}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[!ht]
+\caption{Trusted actors and institutions, broken down by vaccine acceptance \label{fig:vaccacc}}
+
+\includegraphics{paper_files/figure-latex/histcattrust-1.pdf}
+
+\scriptsize{Figure S2 shows histograms of actors and institutions that respondents say they would trust most to help them decide whether or not to take the COVID-19 vaccine.
+Respondents were only permitted to select one most trusted  actor or institution.
+Responses are broken down by acceptance of the COVID-19 vaccine.
+The color of the bars reflect the answer given to the question ``If a COVID-19 vaccine becomes available in [country], would you take it?'' with ``No'' and ``Don't know'' pooled together and ``All'' combined average of ``Yes'' and ``No / Don't know''}
+\end{figure}
+
+\pagebreak
+
+\begin{figure}[!ht]
+\caption{Average vaccine acceptance across all LMIC countries leaving one or two study samples out
+ \label{fig:mainloo}}
+
+\includegraphics{paper_files/figure-latex/mainloo-1.pdf}
+
+\scriptsize{Figure S3 shows distribution of estimates of average acceptance for all studies in LMICs (excluding USA and Russia) leaving one and two study samples out at a time.
+Figure also shows distributions of subgroup averages by gender, education and age leaving one and two study samples out at a time.
+To directly compare the resulting distributions to the estimates reported in Figure 1, we plot point estimates reported in Figure 1 for all LMIC studies, Russia and the US.}
+\end{figure}
+
+\pagebreak
+
+\clearpage
+
+\hypertarget{supplementary-appendix}{%
+\section*{Supplementary Appendix}\label{supplementary-appendix}}
+\addcontentsline{toc}{section}{Supplementary Appendix}
+
+\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}
+\setcounter{page}{1}
+
+\newpage
+
+\begin{table}[!h]
+
+\caption{\label{tab:maintabledis}If a COVID-19 vaccine becomes available in [country], would you take it? Disaggregated by subgroups}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{threeparttable}
+\begin{tabular}[t]{lcccccccc}
+\toprule
+\multicolumn{1}{c}{\textbf{}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{Gender}} & \multicolumn{2}{c}{\textbf{Education}} & \multicolumn{3}{c}{\textbf{Age}} \\
+\cmidrule(l{3pt}r{3pt}){3-4} \cmidrule(l{3pt}r{3pt}){5-6} \cmidrule(l{3pt}r{3pt}){7-9}
+\textbf{Country} & \textbf{Average acceptability} & \textbf{Female} & \textbf{Male} & \textbf{> Secondary} & \textbf{Up to Secondary} & \textbf{<25} & \textbf{25-54} & \textbf{55+}\\
+\midrule
+Burkina Faso & 66.5 & 62.1 & 68.4 & 60.8 & 70.1 & 76.0 & 63.2 & .\\
+ & (63.5, 69.5) & (56.3, 67.9) & (65.0, 71.9) & (55.9, 65.8) & (66.4, 73.8) & (58.0, 94.0) & (53.0, 73.4) & .\\
+Colombia & 74.9 & 73.5 & 77.3 & 78.1 & 73.4 & 75.4 & 74.2 & 73.8\\
+ & (72.2, 77.6) & (70.1, 77.0) & (73.0, 81.7) & (73.6, 82.5) & (70.1, 76.8) & (67.5, 83.4) & (70.2, 78.3) & (65.0, 82.6)\\
+India & 84.3 & 82.4 & 84.7 & 87.8 & 85.9 & 77.6 & 85.4 & 83.1\\
+ & (82.3, 86.3) & (79.0, 85.8) & (82.5, 87.0) & (81.1, 94.6) & (82.5, 89.2) & (71.6, 83.6) & (83.4, 87.3) & (77.6, 88.5)\\
+Mozambique & 89.1 & 86.2 & 91.3 & 86.1 & 89.7 & . & 88.3 & 91.7\\
+ & (86.5, 91.7) & (82.5, 90.0) & (88.4, 94.1) & (81.8, 90.4) & (86.5, 92.8) & . & (85.3, 91.2) & (88.1, 95.4)\\
+Nepal & 96.6 & 96.4 & 96.4 & . & . & 97.8 & 96.6 & 93.8\\
+ & (95.5, 97.6) & (94.6, 98.2) & (95.1, 97.7) & . & . & (95.7, 99.8) & (95.2, 97.9) & (90.4, 97.2)\\
+Nigeria & 76.2 & 74.9 & 77.0 & . & . & 69.0 & 77.6 & 74.7\\
+ & (74.3, 78.2) & (71.7, 78.1) & (74.6, 79.4) & . & . & (63.3, 74.7) & (75.5, 79.7) & (65.8, 83.6)\\
+Pakistan 1 & 76.1 & 72.2 & 80.1 & 83.6 & 74.0 & 86.3 & 75.6 & 80.8\\
+ & (70.0, 82.3) & (65.6, 78.8) & (73.8, 86.4) & (76.6, 90.5) & (67.4, 80.5) & (78.4, 94.1) & (69.3, 81.8) & (64.9, 96.7)\\
+Pakistan 2 & 66.5 & . & . & 71.4 & 64.2 & . & . & .\\
+ & (64.1, 68.9) & . & . & (67.3, 75.5) & (61.2, 67.1) & . & . & .\\
+Rwanda & 84.9 & 79.4 & 88.0 & 71.4 & 87.7 & 88.1 & 83.8 & 73.3\\
+ & (82.9, 86.8) & (75.8, 83.0) & (85.8, 90.2) & (65.5, 77.2) & (85.8, 89.7) & (85.0, 91.1) & (81.3, 86.3) & (59.2, 87.3)\\
+Sierra Leone 1 & 78.0 & 74.1 & 80.1 & 74.4 & 80.2 & 78.0 & 78.3 & 74.0\\
+ & (75.5, 80.5) & (69.5, 78.7) & (77.2, 83.1) & (70.1, 78.7) & (77.0, 83.3) & (72.4, 83.6) & (75.4, 81.1) & (61.4, 86.6)\\
+Sierra Leone 2 & 87.9 & 88.6 & 87.7 & 88.8 & 87.8 & 82.9 & 87.6 & 90.0\\
+ & (86.2, 89.6) & (85.7, 91.5) & (85.9, 89.5) & (85.0, 92.5) & (86.0, 89.6) & (73.9, 91.9) & (85.6, 89.5) & (87.4, 92.6)\\
+Uganda 1 & 85.8 & 85.8 & . & 80.1 & 84.8 & 85.5 & 85.9 & .\\
+ & (84.4, 87.2) & (84.4, 87.2) & . & (74.4, 85.9) & (83.2, 86.5) & (82.7, 88.4) & (84.3, 87.4) & .\\
+Uganda 2 & 76.5 & 74.9 & 78.0 & 68.6 & 79.8 & 76.5 & 77.0 & 73.7\\
+ & (74.3, 78.7) & (71.5, 78.3) & (75.2, 80.9) & (64.3, 72.9) & (77.3, 82.2) & (71.0, 82.1) & (74.4, 79.6) & (67.3, 80.0)\\
+All LMICs & 80.3 & 79.2 & 82.6 & 77.4 & 79.8 & 82.8 & 81.1 & 79.1\\
+ & (74.9, 85.6) & (73.4, 85.0) & (77.4, 87.9) & (71.4, 83.4) & (74.1, 85.4) & (76.9, 88.7) & (75.6, 86.6) & (72.5, 85.7)\\
+All LMICs (National) & 78.4 & 75.5 & 80.3 & 74.7 & 79.8 & 80.1 & 77.4 & 74.4\\
+ & (67.9, 89.0) & (63.6, 87.5) & (70.2, 90.4) & (62.1, 87.3) & (69.8, 89.9) & (73.4, 86.7) & (65.7, 89.2) & (61.7, 87.2)\\
+Russia & 30.4 & 22.6 & 38.5 & 31.0 & 29.6 & 33.5 & 27.6 & 40.0\\
+ & (29.1, 31.7) & (20.9, 24.2) & (36.5, 40.5) & (29.6, 32.5) & (27.3, 32.0) & (29.2, 37.7) & (26.2, 28.9) & (35.9, 44.0)\\
+USA & 64.6 & 56.1 & 73.4 & 72.3 & 51.5 & 51.0 & 64.9 & 69.4\\
+ & (61.8, 67.3) & (52.1, 60.1) & (69.8, 76.9) & (69.5, 75.0) & (46.0, 57.0) & (43.5, 58.6) & (61.1, 68.7) & (64.8, 73.9)\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item Table S1 shows percentage of respondents willing to take the COVID-19 vaccine as plotted in Figure 1. A 95\% confidence interval is shown between parentheses.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
+\newpage
 
@@
 \begin{tablenotes}
-\item Table 2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
-The number of observations and percentage correponds only to people who would take the vaccine.
+\item Table S2 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
+The number of observations and percentage corresponds only to people who would take the vaccine.
 Respondents in all countries could give more than one reason.
@@
 \end{threeparttable}
-\end{table}
-
-\begin{figure}[!ht]
-\caption{Reasons not to take the vaccine \label{fig:fig2paper}}
-
-\includegraphics{paper_files/figure-latex/fig2paper-1.pdf}
-
-\scriptsize{Figure 2 shows the percentage of respondents mentioning reasons why they would not take the COVID-19 vaccine.
-In the plot, points represent the estimated percentage of individuals that would not take the vaccine or do not know if they would take the vaccine for each possible response option.
-Bars around each point indicate a 95\% confidence interval for the estimate.
-An estimated average for all studies in LMICs is also shown.
-Size of points illustrates the number of observations in each response option.
-Studies India and Pakistan 2 are not included because they either did not include the question or were not properly harmonized with the other studies.}
-\end{figure}
-
-\begin{figure}[!ht]
-\caption{Trusted actors and institutions, broken down by expressed willingness to take a COVID-19 vaccine \label{fig:fig3paper}}
-
-\newpage
-
-\includegraphics{paper_files/figure-latex/fig3paper-1.pdf}
-\newpage
-
-\scriptsize{Figure 3 shows histograms of actors and institutions respondents say they would trust most to help them decide whether to take the COVID-19 vaccine.
-Respondents were only permitted to select one most trusted actor or institution.
-Studies India, Mozambique, Pakistan 1, Pakistan 2 and Uganda 1 are not included because they either did not include the question or were not properly harmonized with the other studies.}
-\end{figure}
-
-\clearpage
-
-\hypertarget{supplementary-appendix}{%
-\section*{Supplementary Appendix}\label{supplementary-appendix}}
-\addcontentsline{toc}{section}{Supplementary Appendix}
-
-\hypertarget{appendixd}{%
-\subsection*{Appendix A: Supplementary tables, figures and results}\label{appendixd}}
-\addcontentsline{toc}{subsection}{Appendix A: Supplementary tables, figures and results}
-
-\begin{landscape}\begin{table}[!h]
-
-\caption{\label{tab:sampling}Summary of studies sampling}
-\centering
-\resizebox{\linewidth}{!}{
-\fontsize{10}{12}\selectfont
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{12em}>{\raggedright\arraybackslash}p{30em}ll}
-\toprule
-\textbf{Study} & \textbf{Geographic scope} & \textbf{Sampling methodology} & \textbf{Survey modality} & \textbf{Weights}\\
-\midrule
-Burkina Faso & National & Random digit dialing (RDD) & Phone & Yes\\
-Colombia & National & Random digit dialing (RDD) & Phone & Yes\\
-India & Subnational, Slums in 2 cities & Representative sample of slum dwellers living in vicinity of a community toilet and located in Uttar Pradesh & Phone & Yes\\
-Mozambique & Subnational, 2 cities & 1) Random sample in urban and periurban markets stratified by gender and type of establishment in Maputo; 2) Random sample representative of communities in the Cabo Delgado, stratified on urban, semiurban, and rural areas & Phone & No\\
-Nepal & Subnational, 2 districts & Random sample of poor households from randomly selected villages in Kanchanpur & Phone & Yes\\
-Nigeria & Subnational, 1 state & 1) Random sample of individuals in Kaduna; 2) Sample of phone numbers from a phone list of Kaduna state residents & Phone & No\\
-Pakistan 1 & Subnational, 2 districts & Random sample of individuals in administrative police units in two districts of Punjab & Phone & Yes\\
-Pakistan 2 & Subnational, 1 province & Random digit dialing (RDD) on a random sample of all numerically possible mobile phone numbers in the region of Punjab & Phone & No\\
-Russia & Subnational, 61 regions & Sample recruited from the Russian online survey company OMI (Online Market Intelligence).
-Sampling targeted at having a minimum of respondents per region, as well as representation of age, gender and education groups.
-& Online & Yes\\
-Rwanda & National & Random digit dialing (RDD) & Phone & Yes\\
-Sierra Leone 1 & National & Random digit dialing (RDD) & Phone & Yes\\
-Sierra Leone 2 & National & A random sample of households in 195 rural towns across all 14 districts of Sierra Leone & Phone & No\\
-Uganda 1 & Subnational, 13 districts & Sample of women in households from semi-rural and rural villages across 13 districts in Uganda, selected according to the likelihood of having children & Phone & No\\
-Uganda 2 & Subnational, 1 district & Random sample of households in Kampala & Phone & No\\
-USA & National & Nation-wide sample of adult internet users recruited through the market research firm Lucid & Online & Yes\\
-\bottomrule
-\end{tabular}}
-\end{table}
-\end{landscape}
-\begin{table}[!h]
-
-\caption{\label{tab:maintabledis}If a COVID-19 vaccine becomes available in [country], would you take it? Disaggregated by subgroups}
-\centering
-\resizebox{\linewidth}{!}{
-\fontsize{10}{12}\selectfont
-\begin{threeparttable}
-\begin{tabular}[t]{lccccccc}
-\toprule
-\multicolumn{1}{c}{\textbf{}} & \multicolumn{1}{c}{\textbf{}} & \multicolumn{2}{c}{\textbf{Gender}} & \multicolumn{2}{c}{\textbf{Education}} & \multicolumn{2}{c}{\textbf{Age}} \\
-\cmidrule(l{3pt}r{3pt}){3-4} \cmidrule(l{3pt}r{3pt}){5-6} \cmidrule(l{3pt}r{3pt}){7-8}
-\textbf{Country} & \textbf{Average acceptability} & \textbf{Female} & \textbf{Male} & \textbf{> Secondary} & \textbf{Up to Secondary} & \textbf{<55} & \textbf{55+}\\
-\midrule
-Burkina Faso & 66.5 & 62.1 & 68.4 & 60.8 & 70.1 & 66.0 & 61.0\\
- & (63.5, 69.5) & (56.3, 67.9) & (65.0, 71.9) & (55.9, 65.8) & (66.4, 73.8) & (57.2,  74.8) & (-6.5, 128.6)\\
-Colombia & 74.9 & 73.5 & 77.3 & 78.1 & 73.4 & 74.5 & 73.8\\
- & (72.2, 77.6) & (70.1, 77.0) & (73.0, 81.7) & (73.6, 82.5) & (70.1, 76.8) & (70.9,  78.0) & (65.0,  82.6)\\
-India & 84.6 & 80.8 & 85.6 & 89.4 & 85.8 & 84.6 & 85.1\\
- & (82.8, 86.4) & (77.6, 84.1) & (83.7, 87.5) & (83.5, 95.4) & (82.6, 88.9) & (82.8,  86.4) & (80.8,  89.4)\\
-Mozambique & 89.1 & 86.2 & 91.3 & 86.1 & 89.7 & 88.4 & 91.7\\
- & (86.5, 91.7) & (82.5, 90.0) & (88.4, 94.1) & (81.8, 90.4) & (86.5, 92.8) & (85.5,  91.3) & (88.1,  95.4)\\
-Nepal & 96.6 & 96.4 & 96.4 & . & . & 96.8 & 93.8\\
- & (95.5, 97.6) & (94.6, 98.2) & (95.1, 97.7) & . & . & (95.6,  98.0) & (90.4,  97.2)\\
-Nigeria & 76.2 & 74.9 & 77.0 & . & . & 76.3 & 74.7\\
- & (74.3, 78.2) & (71.7, 78.1) & (74.6, 79.4) & . & . & (74.3,  78.3) & (65.8,  83.6)\\
-Pakistan 1 & 76.1 & 72.2 & 80.1 & 83.6 & 74.0 & 76.0 & 80.8\\
- & (70.0, 82.3) & (65.6, 78.8) & (73.8, 86.4) & (76.6, 90.5) & (67.4, 80.5) & (69.9,  82.2) & (64.9,  96.7)\\
-Pakistan 2 & 66.5 & . & . & 71.4 & 64.2 & . & .\\
- & (64.1, 68.9) & . & . & (67.3, 75.5) & (61.2, 67.1) & . & .\\
-Rwanda & 84.9 & 79.4 & 88.0 & 71.4 & 87.7 & 85.2 & 73.3\\
- & (82.9, 86.8) & (75.8, 83.0) & (85.8, 90.2) & (65.5, 77.2) & (85.8, 89.7) & (83.3,  87.2) & (59.2,  87.3)\\
-Sierra Leone 1 & 78.0 & 74.1 & 80.1 & 74.4 & 80.2 & 78.2 & 74.0\\
- & (75.5, 80.5) & (69.5, 78.7) & (77.2, 83.1) & (70.1, 78.7) & (77.0, 83.3) & (75.7,  80.8) & (61.4,  86.6)\\
-Sierra Leone 2 & 87.9 & 88.6 & 87.7 & 88.8 & 87.8 & 87.4 & 90.0\\
- & (86.2, 89.6) & (85.7, 91.5) & (85.9, 89.5) & (85.0, 92.5) & (86.0, 89.6) & (85.5,  89.3) & (87.4,  92.6)\\
-Uganda 1 & 85.8 & 85.8 & . & 80.1 & 84.8 & 85.8 & .\\
- & (84.4, 87.2) & (84.4, 87.2) & . & (74.4, 85.9) & (83.2, 86.5) & (84.4,  87.2) & .\\
-Uganda 2 & 76.5 & 74.9 & 78.0 & 68.6 & 79.8 & 76.9 & 73.7\\
- & (74.3, 78.7) & (71.5, 78.3) & (75.2, 80.9) & (64.3, 72.9) & (77.3, 82.2) & (74.5,  79.3) & (67.3,  80.0)\\
-All LMICs & 80.3 & 79.1 & 82.7 & 77.5 & 79.8 & 81.3 & 79.3\\
- & (74.9, 85.6) & (73.3, 84.9) & (77.4, 88.0) & (71.4, 83.6) & (74.1, 85.4) & (76.1,  86.5) & (72.6,  86.0)\\
-Russia & 30.4 & 22.6 & 38.5 & 31.0 & 29.6 & 28.4 & 40.0\\
- & (29.1, 31.7) & (20.9, 24.2) & (36.5, 40.5) & (29.6, 32.5) & (27.3, 32.0) & (27.1,  29.7) & (35.9,  44.0)\\
-USA & 64.6 & 56.1 & 73.4 & 72.3 & 51.5 & 61.8 & 69.4\\
- & (61.8, 67.3) & (52.1, 60.1) & (69.8, 76.9) & (69.5, 75.0) & (46.0, 57.0) & (58.4,  65.2) & (64.8,  73.9)\\
-\bottomrule
-\end{tabular}
-\begin{tablenotes}
-\item Table 4 shows percentage of respondents willing to take the COVID-19 vaccine as plotted in Figure 1. A 95\% confidence interval is shown between parentheses
-\end{tablenotes}
-\end{threeparttable}}
 \end{table}
@@
 \begin{tablenotes}
-\item Table 5 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
+\item Table S3 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine.
 The number of observations and percentage correponds only to people who would take the vaccine.
 Respondents in all countries could give more than one reason.
-A 95\% confidence interval is shown between parentheses
+A 95\% confidence interval is shown between parentheses.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
+\newpage
+
+\begin{table}[!h]
+
+\caption{\label{tab:yes1}Reasons to take the vaccine- by age groups}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{threeparttable}
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{7em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{5em}}
+\toprule
+\multicolumn{1}{c}{\textbf{ }} & \multicolumn{3}{c}{\textbf{Self}} & \multicolumn{3}{c}{\textbf{Family}} & \multicolumn{3}{c}{\textbf{Community}} \\
+\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10}
+\textbf{Study} & \textbf{<25} & \textbf{25-54} & \textbf{55+} & \textbf{<25} & \textbf{25-54} & \textbf{55+} & \textbf{<25} & \textbf{25-54} & \textbf{55+}\\
+\midrule
+Burkina Faso & 77 & 59 & 100 & 26 & 64 & 66 & 11 & 2 & 0\\
+Conf. interval & (56, 99) & (46, 72) & (100, 100) & (4, 48) & (51, 77) & (-80, 211) & (-5, 26) & (-2, 5) & (0, 0)\\
+n & 19 & 57 & 3 & 19 & 57 & 3 & 19 & 57 & 3\\
+\midrule
+Colombia & 91 & 91 & 90 & 26 & 26 & 16 & 12 & 13 & 14\\
+Conf. interval & (86, 97) & (88, 94) & (83, 97) & (17, 35) & (21, 31) & (8, 25) & (4, 20) & (9, 16) & (6, 22)\\
+n & 90 & 349 & 73 & 90 & 349 & 73 & 90 & 349 & 73\\
+\midrule
+Mozambique & 62 & 84 & 80 & 50 & 32 & 34 & 12 & 4 & 2\\
+Conf. interval & (19, 106) & (81, 87) & (75, 86) & (5, 95) & (26, 38) & (27, 41) & (-17, 42) & (2, 6) & (0, 4)\\
+n & 8 & 571 & 188 & 8 & 571 & 188 & 8 & 571 & 188\\
+\midrule
+Nepal & 97 & 97 & 92 & 31 & 36 & 27 & 15 & 20 & 19\\
+Conf. interval & (94, 100) & (96, 98) & (87, 97) & (25, 37) & (33, 39) & (19, 36) & (10, 20) & (17, 23) & (13, 25)\\
+n & 225 & 890 & 162 & 225 & 890 & 162 & 225 & 890 & 162\\
+\midrule
+Nigeria & 91 & 89 & 94 & 31 & 36 & 31 & 22 & 21 & 21\\
+Conf. interval & (87, 95) & (87, 91) & (89, 100) & (25, 38) & (33, 39) & (20, 42) & (16, 29) & (18, 23) & (11, 31)\\
+n & 178 & 1175 & 71 & 178 & 1175 & 71 & 178 & 1175 & 71\\
+\midrule
+Rwanda & 98 & 98 & 100 & 22 & 28 & 29 & 10 & 11 & 10\\
+Conf. interval & (97, 100) & (97, 99) & (100, 100) & (17, 26) & (24, 31) & (12, 46) & (7, 13) & (9, 14) & (-1, 21)\\
+n & 389 & 732 & 31 & 389 & 732 & 31 & 389 & 732 & 31\\
+\midrule
+Sierra Leone 1 & 96 & 94 & 94 & 36 & 38 & 27 & 24 & 20 & 22\\
+Conf. interval & (93, 99) & (92, 95) & (86, 102) & (29, 44) & (34, 41) & (12, 42) & (17, 31) & (16, 23) & (8, 36)\\
+n & 167 & 632 & 37 & 167 & 632 & 37 & 167 & 632 & 37\\
+\midrule
+Sierra Leone 2 & 87 & 90 & 93 & 52 & 62 & 62 & 29 & 22 & 18\\
+Conf. interval & (78, 97) & (88, 92) & (89, 97) & (39, 66) & (58, 67) & (56, 67) & (16, 42) & (16, 28) & (12, 25)\\
+n & 63 & 1376 & 396 & 63 & 1376 & 396 & 63 & 1376 & 396\\
+\midrule
+Uganda 1 & 96 & 96 & . & 34 & 36 & . & 9 & 9 & .\\
+Conf. interval & (95, 98) & (96, 97) & . & (30, 39) & (34, 39) & . & (6, 11) & (8, 11) & .\\
+n & 526 & 2218 & . & 526 & 2218 & . & 526 & 2218 & .\\
+\midrule
+Uganda 2 & 97 & 96 & 97 & 20 & 30 & 28 & 8 & 11 & 13\\
+Conf. interval & (94, 99) & (95, 97) & (94, 100) & (14, 26) & (27, 33) & (21, 36) & (4, 11) & (9, 13) & (7, 19)\\
+n & 173 & 749 & 123 & 173 & 749 & 123 & 173 & 749 & 123\\
+\midrule
+All LMICs & 89 & 89 & 93 & 33 & 39 & 36 & 15 & 13 & 13\\
+Conf. interval & (81, 97) & (81, 98) & (89, 98) & (25, 41) & (29, 48) & (23, 48) & (10, 20) & (8, 18) & (7, 19)\\
+n & 1838 & 8749 & 1084 & 1838 & 8749 & 1084 & 1838 & 8749 & 1084\\
+\midrule
+Russia & 67 & 76 & 81 & 74 & 68 & 68 & 46 & 40 & 38\\
+Conf. interval & (59, 74) & (73, 78) & (76, 87) & (68, 81) & (66, 71) & (62, 74) & (38, 54) & (38, 43) & (32, 44)\\
+n & 552 & 5108 & 227 & 552 & 5108 & 227 & 552 & 5108 & 227\\
+\midrule
+USA & 92 & 91 & 97 & 89 & 91 & 94 & 90 & 89 & 89\\
+Conf. interval & (88, 96) & (89, 94) & (95, 99) & (83, 95) & (88, 93) & (91, 97) & (85, 95) & (86, 92) & (85, 93)\\
+n & 153 & 687 & 473 & 153 & 687 & 473 & 153 & 687 & 473\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item Table S4 shows percentage of respondents mentioning reasons why they would take the Covid-19 vaccine by age groups.
+The number of observations and percentage correponds only to people who would take the vaccine.
+Respondents in all countries could give more than one reason.
+A 95\% confidence interval is shown between parentheses.
 \end{tablenotes}
@@
 \begin{tablenotes}
-\item Table 6 shows percentage of respondents mentioning reasons why they would not take the Covid-19 vaccine.
+\item Table S5 shows percentage of respondents mentioning reasons why they would not take the Covid-19 vaccine.
 The number of observations and percentage correponds only to people who would NOT take the vaccine.
 Respondents in all countries could give more than one reason.
-A 95\% confidence interval is shown between parentheses
+A 95\% confidence interval is shown between parentheses.
 \end{tablenotes}
@@
 \begin{TableNotes}
-\item Table 7 shows percentage of respondents that mention actors who they would trust the most to help them decide whether to get a COVID-19 vaccine.
+\item Table S6 shows percentage of respondents that mention actors who they would trust the most to help them decide whether to get a COVID-19 vaccine.
 For all countries the questions was asked regardless if respondent would take a vaccine, would not take it, does not know or does not respond.
@@
 \end{landscape}
-\newpage
-
-\begin{figure}[!ht]
-\caption{Trusted actors and institutions, broken down by gender \label{fig:genderhist}}
-
-\includegraphics{paper_files/figure-latex/genderhist-1.pdf}
-
-\scriptsize{Figure 4 shows histograms of actors and institutions that respondents say they would trust most to help them decide whether or not to take the COVID-19 vaccine.
-Respondents were only permitted to select one most trusted  actor or institution.
-Responses are broken down by acceptance of the COVID-19 vaccine.}
-\end{figure}
 
@@
 \toprule
-\textbf{Estimate} & \textbf{Std.error} & \textbf{P.value} & \textbf{Degrees of freedom} & \textbf{Baseline category} & \textbf{Variable}\\
-\midrule
-0.04 & 0.01 & 0.00 & 10 & Male & Gender\\
-0.00 & 0.01 & 0.71 & 10 & 55+ & Age\\
-0.02 & 0.03 & 0.41 & 10 & Up to secondary & Education\\
+\textbf{Estimate} & \textbf{Std.error} & \textbf{P-value} & \textbf{Degrees of freedom} & \textbf{Baseline category} & \textbf{Variable}\\
+\midrule
+0.04 & 0.01 & 0.00 & 10 & Male & Gender (Female)\\
+-0.02 & 0.02 & 0.43 & 10 & <25 & Age (25-54)\\
+-0.02 & 0.02 & 0.36 & 10 & <25 & Age (55+)\\
+0.02 & 0.03 & 0.38 & 10 & Up to secondary & Education (Secondary +)\\
 \bottomrule
@@
 \begin{tablenotes}
-\item Table 8 shows the results of subgroup mean differences.
-Subgroup differences were generated considering only LMICs.
-The differences in means for gender and age do not include the Uganda 1 study, which only included female respondents under the age of 55.
-p-values come from a two-sided t-test from a linear regression.
+\item Table S7 shows the results of subgroup mean differences. Subgroup differences were generated considering only LMICs. p-values come from a two-sided t-test from a linear regression.
 \end{tablenotes}
@@
 \begin{tablenotes}
-\item Table 9 show the percentage of observations that are not missing values for each variable included in Figure 1.
+\item Table S8 show the proportion of observations that are not missing values for each variable included in Figure 1.
 \end{tablenotes}
@@
 
+\newpage
+
+\begin{table}
+
+\caption{\label{tab:countrydiff}Differences between groups within studies}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{threeparttable}
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{9em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}r}
+\toprule
+\textbf{Country} & \textbf{Variable} & \textbf{Baseline category} & \textbf{Group} & \textbf{Estimate} & \textbf{Std. Error} & \textbf{P-value} & \textbf{Degrees of freedom} & \textbf{N Obs}\\
+\midrule
+Burkina Faso & Age & <25 & 25-54 & -0.13 & 0.10 & 0.21 & 119 & 120\\
+Colombia & Age & <25 & 25-54 & -0.01 & 0.04 & 0.79 & 689 & 690\\
+India & Age & <25 & 25-54 & 0.08 & 0.03 & 0.01 & 141 & 1,680\\
+Mozambique & Age & <25 & 25-54 & -0.12 & 0.01 & 0.00 & 162 & 860\\
+Nepal & Age & <25 & 25-54 & -0.01 & 0.01 & 0.32 & 89 & 1,324\\
+Nigeria & Age & <25 & 25-54 & 0.09 & 0.03 & 0.01 & 1,867 & 1,868\\
+Pakistan 1 & Age & <25 & 25-54 & -0.11 & 0.04 & 0.00 & 105 & 1,633\\
+Russia & Age & <25 & 25-54 & -0.06 & 0.02 & 0.01 & 22,124 & 22,125\\
+Rwanda & Age & <25 & 25-54 & -0.04 & 0.02 & 0.03 & 1,354 & 1,355\\
+Sierra Leone 1 & Age & <25 & 25-54 & 0.00 & 0.03 & 0.94 & 1,069 & 1,070\\
+Sierra Leone 2 & Age & <25 & 25-54 & 0.05 & 0.04 & 0.30 & 190 & 2,087\\
+Uganda 1 & Age & <25 & 25-54 & 0.00 & 0.02 & 0.83 & 497 & 3,198\\
+Uganda 2 & Age & <25 & 25-54 & 0.00 & 0.03 & 0.89 & 309 & 1,366\\
+USA & Age & <25 & 25-54 & 0.14 & 0.04 & 0.00 & 1,958 & 1,959\\
+Burkina Faso & Age & <25 & 55+ & -0.15 & 0.24 & 0.53 & 119 & 120\\
+Colombia & Age & <25 & 55+ & -0.02 & 0.06 & 0.79 & 689 & 690\\
+India & Age & <25 & 55+ & 0.05 & 0.04 & 0.19 & 141 & 1,680\\
+Mozambique & Age & <25 & 55+ & -0.08 & 0.02 & 0.00 & 162 & 860\\
+Nepal & Age & <25 & 55+ & -0.04 & 0.02 & 0.06 & 89 & 1,324\\
+Nigeria & Age & <25 & 55+ & 0.06 & 0.05 & 0.28 & 1,867 & 1,868\\
+Pakistan 1 & Age & <25 & 55+ & -0.06 & 0.07 & 0.45 & 105 & 1,633\\
+Russia & Age & <25 & 55+ & 0.07 & 0.03 & 0.03 & 22,124 & 22,125\\
+Rwanda & Age & <25 & 55+ & -0.15 & 0.07 & 0.04 & 1,354 & 1,355\\
+Sierra Leone 1 & Age & <25 & 55+ & -0.04 & 0.07 & 0.56 & 1,069 & 1,070\\
+Sierra Leone 2 & Age & <25 & 55+ & 0.07 & 0.05 & 0.12 & 190 & 2,087\\
+Uganda 2 & Age & <25 & 55+ & -0.03 & 0.04 & 0.47 & 309 & 1,366\\
+USA & Age & <25 & 55+ & 0.18 & 0.04 & 0.00 & 1,958 & 1,959\\
+Burkina Faso & Education & Secondary + & Up to secondary & 0.09 & 0.03 & 0.00 & 976 & 977\\
+Colombia & Education & Secondary + & Up to secondary & -0.05 & 0.03 & 0.10 & 1,010 & 1,011\\
+India & Education & Secondary + & Up to secondary & -0.02 & 0.04 & 0.59 & 100 & 340\\
+Mozambique & Education & Secondary + & Up to secondary & 0.04 & 0.03 & 0.17 & 160 & 828\\
+Pakistan 1 & Education & Secondary + & Up to secondary & -0.10 & 0.04 & 0.01 & 105 & 1,621\\
+Pakistan 2 & Education & Secondary + & Up to secondary & -0.07 & 0.03 & 0.00 & 1,491 & 1,492\\
+Russia & Education & Secondary + & Up to secondary & -0.01 & 0.01 & 0.31 & 22,124 & 22,125\\
+Rwanda & Education & Secondary + & Up to secondary & 0.16 & 0.03 & 0.00 & 1,354 & 1,355\\
+Sierra Leone 1 & Education & Secondary + & Up to secondary & 0.06 & 0.03 & 0.03 & 1,037 & 1,038\\
+Sierra Leone 2 & Education & Secondary + & Up to secondary & -0.01 & 0.02 & 0.63 & 190 & 2,110\\
+Uganda 1 & Education & Secondary + & Up to secondary & 0.05 & 0.03 & 0.12 & 494 & 2,739\\
+Uganda 2 & Education & Secondary + & Up to secondary & 0.11 & 0.03 & 0.00 & 309 & 1,366\\
+USA & Education & Secondary + & Up to secondary & -0.21 & 0.03 & 0.00 & 1,958 & 1,959\\
+Burkina Faso & Gender & Female & Male & 0.06 & 0.03 & 0.06 & 976 & 977\\
+Colombia & Gender & Female & Male & 0.04 & 0.03 & 0.18 & 1,011 & 1,012\\
+India & Gender & Female & Male & 0.02 & 0.02 & 0.22 & 141 & 1,680\\
+Mozambique & Gender & Female & Male & 0.05 & 0.02 & 0.02 & 162 & 862\\
+Nepal & Gender & Female & Male & 0.00 & 0.01 & 0.98 & 89 & 1,324\\
+Nigeria & Gender & Female & Male & 0.02 & 0.02 & 0.30 & 1,867 & 1,868\\
+Pakistan 1 & Gender & Female & Male & 0.08 & 0.02 & 0.00 & 105 & 1,629\\
+Russia & Gender & Female & Male & 0.16 & 0.01 & 0.00 & 22,124 & 22,125\\
+Rwanda & Gender & Female & Male & 0.09 & 0.02 & 0.00 & 1,354 & 1,355\\
+Sierra Leone 1 & Gender & Female & Male & 0.06 & 0.03 & 0.03 & 1,069 & 1,070\\
+Sierra Leone 2 & Gender & Female & Male & -0.01 & 0.02 & 0.56 & 190 & 2,110\\
+Uganda 2 & Gender & Female & Male & 0.03 & 0.02 & 0.17 & 309 & 1,366\\
+USA & Gender & Female & Male & 0.17 & 0.03 & 0.00 & 1,958 & 1,959\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item Table S9 shows differences of means between groups within single studies.
+Estimates are calculated through OLS and represent the difference in the average acceptance rate between the subgroup in column Group and that in column Baseline category.
+p-values come from a two-sided t-test from a linear regression.
+\end{tablenotes}
+\end{threeparttable}}
+\end{table}
+
+\pagebreak
+
 \begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
 
-\pagebreak
-
-\hypertarget{appendixb}{%
-\subsection*{Appendix B: Question wording and answer options per study}\label{appendixb}}
-\addcontentsline{toc}{subsection}{Appendix B: Question wording and answer options per study}
+\clearpage
 
@@
 \begin{tablenotes}
-\item Table 10 presents question wording and answer options from answers used in Figure 1 to get estimated vaccine acceptance.
+\item Table S10 presents question wording and answer options from answers used in Figure 1 to get estimated vaccine acceptance.
 Answer options are separated by a semicolon.
@@
 In Russia, 'Yes, if a Russian vaccine will be available' and 'Yes, if an imported vaccine will be available' are both recoded as 'Yes'.
-In USA 'Definitely yes' and 'Probably yes' are recoded as 'Yes', and 'Probably not' and 'Definitely not' are recoded as 'No'
+In USA 'Definitely yes' and 'Probably yes' are recoded as 'Yes', and 'Probably not' and 'Definitely not' are recoded as 'No'.
 \end{tablenotes}
@@
 \begin{tablenotes}
-\item Table 11 presents question wording and answer options used in Table 2 to get an estimated percentage of reasons to take the COVID-19 vaccine.
+\item Table S11 presents question wording and answer options used in Table S2 to get an estimated percentage of reasons to take the COVID-19 vaccine.
 Columns 'Protection: self', 'Protection: family' and  'Protection: community' show the answer options that were recoded in each category.
@@
 Sierra Leone 2 & Why would you not take it?
-& I will not take a vaccine because I am concerned about side effects & I will not take a vaccine because I am not concerned about the risk associated with me/my relatives getting COVID-19ne is & I will not take a vaccine because I am not concerned about the risk associated with me/my relatives getting COVID-19 & I will not take a vaccine because they are not effective & .
+& I will not take a vaccine because I am concerned about side effects & I will not take a vaccine because I am not concerned about the risk associated with me/my relatives getting COVID-19 & I will not take a vaccine because I am not concerned about the risk associated with me/my relatives getting COVID-19 & I will not take a vaccine because they are not effective & .
 & I will not take a vaccine because I don't like needles & .
@@
 \begin{tablenotes}
-\item Table 12 presents question wording and answer options used in Figure 2 to get an estimated percentage of reasons not to take the COVID-19 vaccine.
+\item Table S12 presents question wording and answer options used in Figure 2 to get an estimated percentage of reasons not to take the COVID-19 vaccine.
 Columns 3-10 show the answer options that were recoded in each category.
@@
 \begin{tablenotes}
-\item Table 13 presents question wording and answer options used in Figure 3 to get the percentage of respondents mentioning each actor or instituion that they would trust to decide whether to get the COVID-19 vaccine.
+\item Table S13 presents question wording and answer options used in Figure 3 to get the percentage of respondents mentioning each actor or institution that they would trust to decide whether to get the COVID-19 vaccine.
 Columns 3-8 show the answer options that were recoded in each category.
@@
 
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-\hypertarget{appendix-c-additional-contributors}{%
-\subsection*{Appendix C: Additional contributors}\label{appendix-c-additional-contributors}}
-\addcontentsline{toc}{subsection}{Appendix C: Additional contributors}
-
-We thank Sellu Kallon and Sarah Ryan for valuable intellectual contributions and research assistance.
-
-IPA would like to thank staff in Burkina Faso, Colombia, Rwanda, Sierra Leone and the United States for their intellectual contributions, research assistance, and support throughout the RECOVR survey: Achille Mignondo Tchibozo, Michael Rosenbaum, Hugo Salas, Filippo Cuccaro, Jean Leodomir Habarimana Mfura, Doug Kirke-Smith, Savanna Henderson, Shahana Hirji, Kyle Holloway, Margarita Cabra.
-
-Russia team would like to thank staff at Online Market Intelligence survey agency and Kirill Chmel and Vladimir Zabolotsky for their intellectual contributions and research assistance.
-
-\newpage
-
-\hypertarget{appendixa}{%
-\subsection*{Appendix D: Sample descriptions}\label{appendixa}}
-\addcontentsline{toc}{subsection}{Appendix D: Sample descriptions}
-
-The case history data for all countries in our sample is extracted from the Johns Hopkins University Center for Systems Science and Engineering (JHU CSSE) database.\footnote{Dong, E., Du, H., \& Gardner, L.
-(2020).
-An interactive web-based dashboard to track COVID-19 in real time.
-The Lancet infectious diseases, 20(5), 533-534.}
-
-\hypertarget{burkina-faso-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}{%
-\subsubsection*{Burkina Faso, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}\label{burkina-faso-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}}
-\addcontentsline{toc}{subsubsection}{Burkina Faso, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-\item First confirmed case: March 9, 2020 
-\item Number of confirmed cases 2,335 as of  October 15, 2020 
-\item Number of deaths:  65 as of October 15, 2020
-\end{itemize}
-
-\textbf{Target Population}: A random sample of all adults with mobile phone numbers in the country, based on national communications authority number allocation plans.
-
-\textbf{Original Study Design:} N/A
-
-\textbf{COVID-19 Survey Design:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share for a two-round panel survey.
-
-\emph{Sampling Frame:} All mobile phone numbers in Burkina Faso.
-
-\emph{Survey Dates:} October 15 to December 4, 2020 (Round 1 June 6-15, 2020)
-
-\emph{Sample size, tracking and attrition:} Sample includes 977 respondents from the second round of a panel.
-In the first round conducted between June 6 to 15, 2020, 1,356 individual surveys were contacted through Random Digit Dialing (RDD) from the sampling frame of all mobile phone numbers in Burkina Faso.
-2,313 working numbers yielded 1,383 eligible respondents for a completion rate of 98\% of eligible respondents.
-
-\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.
-
-\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15608, and the Burkina Faso Institutional Ethics Committee for Health Sciences Research, approval A13-2020.
-
-\hypertarget{colombia-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}{%
-\subsubsection*{Colombia, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}\label{colombia-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}}
-\addcontentsline{toc}{subsubsection}{Colombia, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-\item First confirmed case: March 6, 2020
-\item Number of confirmed cases:  456,689 as of August 15, 2020
-\item Number of deaths:  14,810 as of August 15, 2020
-\end{itemize}
-
-\textbf{Target Population}: A random sample of all numerically possible mobile phone numbers in the country, based on national communications authority number allocation plans.
-
-\textbf{Original Study Design:} N/A
-
-\textbf{COVID-19 Survey Design:}
-
-\emph{Sampling Frame:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share.
-
-\emph{Survey Dates:} August 15-25, 2020 (Round 1 May 8-15, 2020)
-
-\emph{Sample size, tracking and attrition:} Sample includes 1,012 respondents contacted in the second round of a panel of 1,507.
-
-\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.
-
-\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15582.
-
-\hypertarget{india-coping-with-covid-19-in-slums-evidence-from-india-subnational-sample-nova-school-of-business-and-economics-the-institute-for-fiscal-studies-university-of-st.-andrews}{%
-\subsubsection*{India, Coping with COVID-19 in Slums: Evidence from India Subnational sample, Nova School of Business and Economics, The Institute for Fiscal Studies, University of St.~Andrews}\label{india-coping-with-covid-19-in-slums-evidence-from-india-subnational-sample-nova-school-of-business-and-economics-the-institute-for-fiscal-studies-university-of-st.-andrews}}
-\addcontentsline{toc}{subsubsection}{India, Coping with COVID-19 in Slums: Evidence from India Subnational sample, Nova School of Business and Economics, The Institute for Fiscal Studies, University of St.~Andrews}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-\item First confirmed case: January 30, 2020
-\item Number of confirmed cases: 198,370 as of June 1, 2020 
-\item Number of deaths: 5,608 as of June 1, 2020 
-\end{itemize}
-
-\textbf{Target Population}: Random subset of slum populations in Lucknow and Kanpur, Uttar Pradesh, India.
-Socio-economic variables are only collected for a representative sample of the population relying on community toilets or open defecation to fulfil their sanitation needs.
-
-\textbf{Original Study Design:} Randomized controlled trial, with complete census of households within 142 slums (September to December 2017), and a series of household and caretaker surveys, objective measurements, incentivized behavioural measurements, and a Structured Community Activity, collected for a sub-set of 100 slums between April 2018 and September 2019.
-
-\emph{Intervention:} Catchment areas of CTs were randomly allocated to two interventions.
-The first intervention aimed at community toilet improvements by offering caretakers the choice of a grant to be spent for improvements in the facility.
-Following the grant, caretakers were offered a large financial reward conditional on the cleanliness of the facility.
-The second intervention added to this CT improvement awareness creation among potential users through face-to-face information sessions, leaflets, monthly reminders using voice messages sent to mobile phones, and posters hung in the CTs.
-
-\emph{Sampling Frame:} A two-step sampling was applied, first, study households from the main study sample were sampled, then households from the whole slum population were added.
-
-\emph{Survey Dates:}
-Baseline: June to July 2020, Follow-up 1: October toNovember 2020, Follow-up 2: December 16, 2020 toJanuary 18, 2021.
-
-\emph{Sample size, tracking and attrition:} 3,991 households, with a mean of 28 households per cluster (142).
-Non-response Baseline: 25\%, Attrition rate Baseline to Follow-up (1 and 2): 13\%, Randomly selected replacement households for Follow-up (1 and 2): 1,277.
-
-\emph{Sampling Weights:} Included
-
-\emph{IRB Approval:} Approval was secured from London School of Economics (REC ref. 1132). The pre-analysis plan was registered on the AEA RCT registry (RCT ID AEARCTR-0006564).
-
-\hypertarget{mozambique-subnational-sample-international-growth-center-nova-school-of-business-and-economics}{%
-\subsubsection*{Mozambique Subnational sample, International Growth Center, Nova School of Business and Economics}\label{mozambique-subnational-sample-international-growth-center-nova-school-of-business-and-economics}}
-\addcontentsline{toc}{subsubsection}{Mozambique Subnational sample, International Growth Center, Nova School of Business and Economics}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-\item First confirmed case: March 22, 2020
-\item Number of confirmed cases:  12,777 as of October 30, 2020 
-\item Number of deaths:  91 as of October 30, 2020
-\end{itemize}
-
-\textbf{Target Population}: Microentrepreneurs in urban markets of Maputo and household heads from the province of Cabo Delgado.
-
-\textbf{Original Study Design:} Initial data were collected in-person in two different studies.
-For microentrepreneurs in Maputo, the data were collected between October 2013 and April 2014 (baseline), and between July and November 2015 (endline).\footnote{Original study: \url{http://catiabatista.org/bsv_mm_urban.pdf}} For household heads in Cabo Delgado, the data were collected in-person between August and September 2016 (baseline), and between August and September 2017 (endline).\footnote{Original study: \url{https://www.aeaweb.org/articles?id=10.1257/aer.20190842}}
-
-\emph{Intervention:} The first study was dedicated to analyzing the impacts of interventions targeting microentrepreneurs in urban markets on financial inclusion and literacy.
-The second study focused on the role of information to counteract the political resource curse after a substantial natural gas discovery.
-
-\emph{Sampling Frame:} The first initial sample was selected by in-field random sampling in 23 urban and periurban markets in Maputo and Matola.
-Stratification was based on the gender of the respondent and on the type of establishment (stall vs.~store).
-The second initial sample was selected to be representative of 206 communities in the province of Cabo Delgado, randomly drawn from the list of all 421 polling locations in the sampling frame, stratified on urban, semiurban, and rural areas.
-This survey in this paper was done by phone.
-
-\emph{Survey Dates:} October 30 to November 21, 2020 (Maputo) and November 6 to November 30, 2020 (Pemba).
-
-\emph{Sample size, tracking and attrition:} 554 microentrepreneurs from Maputo and 308 households from Cabo Delgado.
-
-\emph{Sampling Weights:} N/A
-
-\textbackslash emph\{IRB Approval: The approval was secured from Universidade Nova de Lisboa on July 14, 2020.
-
-\hypertarget{nepal-western-terai-panel-survey-wtps-subnational-sample-yale-university-yale-research-initiative-on-innovation-and-scale-y-rise}{%
-\subsubsection*{Nepal, Western Terai Panel Survey (WTPS) Subnational sample, Yale University, Yale Research Initiative on Innovation and Scale (Y-RISE)}\label{nepal-western-terai-panel-survey-wtps-subnational-sample-yale-university-yale-research-initiative-on-innovation-and-scale-y-rise}}
-\addcontentsline{toc}{subsubsection}{Nepal, Western Terai Panel Survey (WTPS) Subnational sample, Yale University, Yale Research Initiative on Innovation and Scale (Y-RISE)}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-\item First confirmed case: January 23, 2020
-
-\item Number of confirmed cases:  233,452 as of December 1, 2020 
-\item Number of deaths:   1,529 as of December 1, 2020
-\end{itemize}
-
-\textbf{Target Population}: Rural households in the districts of Kailali and Kanchanpur.
-
-\textbf{Original Study Design:} Initial baseline data was collected in-person in July of 2019, and 5 rounds of phone survey data were collected between August 12, 2019 and January 4, 2020.
-
-\emph{Sampling Frame:} The phone survey sample includes 2,636 rural households in the districts of Kailali and Kanchanpur, which represent the set of households that responded to phone surveys from an original sample of 2,935 households.
-This sample was constructed by randomly sampling 33 wards from 15 of the 20 sub-districts in Kailali and Kanchanpur and selecting a random 97 villages from within those wards.
-At the time of baseline data collection in July of 2019, 7 of these 97 villages were dropped from the sample due to flooding.
-Households belong to the bottom half of the wealth distribution in these villages, as estimated by a participatory wealth ranking exercise with members of the village.
-
-\emph{Survey Dates:}December 1st - December 11, 2020
-
-\emph{Sample size, tracking and attrition:} 1,392 households
-
-\emph{IRB Approval:} This research was approved via Yale University IRB Protocol 2000025621.
-
-\hypertarget{nigeria-subnational-sample-wzb-berlin-social-science-center-university-of-illinois-chicago}{%
-\subsubsection*{Nigeria Subnational sample, WZB Berlin Social Science Center, University of Illinois Chicago}\label{nigeria-subnational-sample-wzb-berlin-social-science-center-university-of-illinois-chicago}}
-\addcontentsline{toc}{subsubsection}{Nigeria Subnational sample, WZB Berlin Social Science Center, University of Illinois Chicago}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-\item First confirmed case: February 28, 2020
-\item Number of confirmed cases: 65,693 as of November 18, 2020 
-\item Number of deaths:  1,163 as of November 18, 2020 
-\end{itemize}
-
-\textbf{Target Population}: Christian and Muslim men and women, age 18 and above, living in Kaduna state, Nigeria.
-
-\textbf{Original Study Design}: Initial data was collected from a subset of the sample in December 2019 (in person survey) and July - Aug 2020 (phone survey) as part of an experiment testing the effects of a brief radio program on inter-religious animus.
-A random walk procedure and random sampling were used within households to recruit a representative sample of adults in Kaduna town.
-The rest of the sample was recruited for the study in Aug 2020 by purchasing phone lists for residents of Kaduna State.
-
-\emph{Intervention:} The study examines the effects of a radio program and a TV drama on inter-religious animus.
-The subset of the sample in the radio study was randomly assigned to listen to a brief radio program on one of the following topics: (1) an inter-religious storyline, (2) an intra-religious storyline, and (3) a message about maintaining safe health practices.
-All respondents in the sample participated in a study examining the effect of viewing an inter-religious storyline unfolding over a full season of a popular TV drama, Dadin Kowa.
-The season aired from Aug - Oct 2020.
-A third of the sample were encouraged to watch Dadin Kowa, a third were encouraged to watch the TV station Africa Magic Hausa at the same time Dadin Kowa aired, and a third were in the treatment-as-usual group.
-All participants received a weekly incentivized SMS quiz from Aug - Oct 2020.
-
-\textbf{COVID-19 Survey Design:} This survey is not primarily about COVID-19, but was designed as an endline survey to follow the TV drama intervention described above.
-The goal of this survey is to measure a range of attitudinal outcomes related to Christian-Muslim relations (including prejudice, intergroup threat perceptions, dehumanization, and support for the use of violence, among others).
-We included nine of the standardized COVID-19 vaccine-related questions collected specifically for this vaccine acceptance study in the final module of the endline survey.
-
-\emph{Sampling Frame:} 950 respondents in the sample were recruited in person through a random sampling procedure in the Kaduna metropolitan area (pre-COVID).
-The remaining 1,700 respondents were recruited into the study over the phone from lists of phone numbers of Kaduna state residents that were purchased from a private vendor.
-
-\emph{Survey Dates:} November 18 - December 18, 2020.
-
-\emph{Sample size, tracking and attrition:} All 1,834 individuals who completed the endline survey are included.
-
-\emph{Sampling Weights:} N/A
-
-\emph{IRB Approval:} This study was reviewed by the IRB at the University of Pennsylvania (Protocol 834548), and it was determined on November 20, 2019 to meet the criteria for review exemption (45 CFR 46.104, category \#2).
-
-\hypertarget{pakistan}{%
-\subsubsection*{Pakistan}\label{pakistan}}
-\addcontentsline{toc}{subsubsection}{Pakistan}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-\item March 6: First confirmed case: February  26, 2020 
-\item Number of confirmed cases:  271,887 as of July 24, 2020 
-\item Number of deaths:  5,787 as of July 24, 2020 
-\end{itemize}
-
-\hypertarget{pakistan-economic-vulnerability-assessment-eva-subnational-sample-sheikhupura-police-study-sample-institute-of-development-and-economic-alternatives-lahore-university-of-management-science-london-school-of-economics-princeton-university}{%
-\subsubsection*{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample, Sheikhupura Police Study Sample, Institute of Development and Economic Alternatives, Lahore University of Management Science, London School of Economics, Princeton University}\label{pakistan-economic-vulnerability-assessment-eva-subnational-sample-sheikhupura-police-study-sample-institute-of-development-and-economic-alternatives-lahore-university-of-management-science-london-school-of-economics-princeton-university}}
-\addcontentsline{toc}{subsubsection}{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample, Sheikhupura Police Study Sample, Institute of Development and Economic Alternatives, Lahore University of Management Science, London School of Economics, Princeton University}
-
-\textbf{Target Population}: A representative sample of adults from 108 of 151 police beats in Sheikhupura and Nankana districts of Punjab Province.
-
-\textbf{Original Study Design:} N/A
-
-\textbf{COVID-19 Survey Design:} The EVA survey involved calls to all households in the stratified random sample for the policing study midline survey.
-
-\emph{Sampling Frame:} Households in Sheikhupura and Nankana districts.
-
-\emph{Survey Dates:} July 24 to September 9, 2020
-
-\emph{Sample size, tracking and attrition:} Sample includes 1,473 respondents.
-
-\emph{Sampling Weights:} Post-stratification weights are computed to adjust for the sampling process, which involved stratifying first on 27 police stations, then within each police station on beats, then PPS sampling within beats using Asiapop population data.
-
-\emph{IRB Approval:} This research was approved via Princeton University IRB Protocol 7250.
-
-\hypertarget{pakistan-economic-vulnerability-assessment-eva-subnational-sample}{%
-\subsubsection*{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample}\label{pakistan-economic-vulnerability-assessment-eva-subnational-sample}}
-\addcontentsline{toc}{subsubsection}{Pakistan, Economic Vulnerability Assessment (EVA) Subnational sample}
-
-\textbf{Target Population}: All possible mobile phone numbers (in the province of Punjab) generated based on the local mobile phone number structure in Pakistan.
-
-\textbf{Original Study Design:} N/A
-
-\textbf{COVID-19 Survey Design:} The EVA survey involved making calls to individuals in Punjab based on random digit dialing.
-
-\emph{Sampling Frame:} Individuals with mobile phones in Punjab.
-
-\emph{Survey Dates:} September 2 to October 13, 2020
-
-\emph{Sample size, tracking and attrition:} Sample includes 1,492 respondents.
-
-\emph{Sampling Weights:} N/A.
-
-\emph{IRB Approval:} This research was approved by Lahore University of Management Sciences IRB Protocol LUMS-IRB/07012020SA.
-
-\hypertarget{rwanda-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}{%
-\subsubsection*{Rwanda, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}\label{rwanda-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}}
-\addcontentsline{toc}{subsubsection}{Rwanda, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
- \item First confirmed case: March 14, 2020
- \item Total cases:  5,017 as of October 22, 2020 
-\item Total deaths:  34 as of October 22, 2020 
-\end{itemize}
-
-\textbf{Target Population}: A random sample of all numerically possible mobile phone numbers in the country, based on national communications authority number allocation plans.
-
-\textbf{Original Study Design:} N/A
-
-\textbf{COVID-19 Survey Design:}Phone survey
-
-\emph{Sampling Frame:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share.
-
-\emph{Survey Dates:} October 22 to November 5, 2020 (Round 1 June 4 -12, 2020)
-
-\emph{Sample size, tracking and attrition:}Sample includes 1,355 respondents contacted in the second round of a panel of 1,480.
-
-\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.
-
-\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15591, Rwanda National Institute for Scientific Research permit No.0856/2020/10/NISR; and Rwanda National Ethics Committee approval No.16/RNEC/2020.
-
-\hypertarget{russian-federation-research-on-covid-19-in-russias-regions-rocirr-subnational-sample-international-center-for-the-study-of-institutions-and-development-hse-university-moscow-russia-and-economics-department-of-ghent-university-wzb-berlin-social-science-center-columbia-university}{%
-\subsubsection*{Russian Federation, Research on COVID-19 in Russia's Regions (RoCiRR) Subnational sample, International Center for the Study of Institutions and Development (HSE University, Moscow, Russia) and Economics Department of Ghent University, WZB Berlin Social Science Center, Columbia University}\label{russian-federation-research-on-covid-19-in-russias-regions-rocirr-subnational-sample-international-center-for-the-study-of-institutions-and-development-hse-university-moscow-russia-and-economics-department-of-ghent-university-wzb-berlin-social-science-center-columbia-university}}
-\addcontentsline{toc}{subsubsection}{Russian Federation, Research on COVID-19 in Russia's Regions (RoCiRR) Subnational sample, International Center for the Study of Institutions and Development (HSE University, Moscow, Russia) and Economics Department of Ghent University, WZB Berlin Social Science Center, Columbia University}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-\item First confirmed case: January 31, 2020
-\item Number of confirmed cases: 1,720,063 as of November 6, 2020 
-\item Number of deaths:  29,654 as of November 6, 2020 
-\end{itemize}
-
-\textbf{Target Population}: Adult internet users who reside in one of 61 federal subjects (federal cities, oblasts, republics, krais and autonomous okrug) of Russia.
-The regions included in the study are Republics: \emph{Bashkortostan, Karelia, Komi, Mariy El, Mordovia, Tatarstan, Udmurtia, Chuvashia}.
-Krais: \emph{Altai, Krasnodarsky, Krasnoyarsky, Permsky, Primorsky, Stavropolsky, Khabarovsky}.
-Oblasts: \emph{Arkhangelsk, Astrakhan, Belgorod, Bryansk, Vladimir, Volgograd, Vologda, Voronezh, Ivanovo, Irkutsk, Kaliningrad, Kaluga, Kemerovo, Kirov, Kostroma, Kurgan, Kursk, Leningrad, Lipetsk, Moscow, Murmansk, Nizhny Novgorod, Novgorod, Novosibirsk, Omsk, Orenburg, Orel, Pskov, Penza, Rostov, Ryazan, Samara, Saratov, Sverdlovsk, Smolensk, Tambov, Tver, Tomsk, Tula, Tyumen, Ulyanovsk, Chelyabinsk, Yaroslavl}.
-Other: \emph{Moscow, Saint Petersburg, Khanty-Mansiysk Autonomous Okrug -- Ugra}.
-The remaining 24 federal subjects were excluded from the study due to inability to enroll sample size with desired characteristics (sample size, age, gender and education group composition).
-
-\textbf{Original Study Design:} N/A
-
-\textbf{COVID-19 Survey Design:} The study was designed to measure the impact of pandemics on Russians, mostly those who live in cities with more than 100,000 residents.
-It contains a number of questions on the personal experience, norms and values, trust in government institutions, provision of social services, and mass media use.
-Region and geolocality of every respondent are recorded.
-
-\emph{Sampling Frame:} In total 25,558 respondents received the module on vaccine acceptance.
-The sample was enrolled from the pool of Russian online survey company OMI (Online Market Intelligence).
-The sampling was specifically targeted at having a minimum of 150 respondents in each of the 61 regions and including respondents from all the main age and gender groups within each region.
-Respondents were also selected so that at least 40\% of respondents did not have higher education, in accordance with higher education rates in Russia.
-Out of 25,558 recruited respondents, 22,125 completed the survey.
-Among 22,125 respondents who completed the survey, 20,821 were enrolled from the general pull of the survey company respondents, while the remaining 1,304 respondents were enrolled among residents of cities with populations below 100,000 and rural areas.
-
-\emph{Survey Dates:} November 6 - December 1, 2020
-
-\emph{Sample size, tracking and attrition:} 22,125 respondents who completed the survey with the vaccine acceptance module included.
-
-\emph{Sampling Weights:} Post-stratification weights are computed to match marginal population distributions of age, gender and education with target proportions coming from the 2019 Yearbook and 2015 Microcensus released by Russian Federal Bureau of National Statistics (Rosstat).
-
-\emph{IRB Approval:} This study was approved via Columbia University IRB Protocol IRB-AAAT4453.
-
-\hypertarget{sierra-leone}{%
-\subsubsection*{Sierra Leone}\label{sierra-leone}}
-\addcontentsline{toc}{subsubsection}{Sierra Leone}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-        \item First confirmed case: March 20, 2020
-        \item Total cases:  2,252 as of October 2, 2020 and 3,030 as of January 20, 2021 
-        \item Total deaths:  72 as of October 2, 2020 and 77 as of January 20, 2021 
-\end{itemize}
-
-\hypertarget{sierra-leone-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}{%
-\paragraph*{Sierra Leone, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}\label{sierra-leone-research-for-effective-covid-19-responses-recovr-national-rdd-sample-innovations-for-poverty-action-ipa}}
-\addcontentsline{toc}{paragraph}{Sierra Leone, Research for Effective COVID-19 Responses (RECOVR) National RDD Sample, Innovations for Poverty Action (IPA)}
-
-\textbf{Target Population}: A random sample of all numerically possible mobile phone numbers in the country, based on national communications authority number allocation plans.
-
-\textbf{Original Study Design:} N/A
-
-\textbf{COVID-19 Survey Design:} Numbers were called via random digit dialing (RDD), stratified by mobile network operator market share
-
-\emph{Sampling Frame:} All active mobile phone numbers in Sierra Leone.
-
-\emph{Survey Dates:} October 2-19, 2020 (Round 1 May 27 to June 15, 2020)
-
-\emph{Sample Size, tracking and Attrition:} Sample includes 1,070 respondents contacted in the second round of a panel of 1,304.
-
-\emph{Sampling Weights:} Post-stratification weights are computed to adjust for differential attrition between the first and second rounds of the RDD panel, weighting on gender, region, and educational attainment.
-
-\emph{IRB Approval:} This research was approved via IPA IRB Protocol 15592, and Sierra Leone Ethics and Scientific Review Committee approval (no approval number, letter available upon request).
-
-\hypertarget{sierra-leone-towns-that-are-candidates-for-rural-electrification-nation-wide-sample-international-growth-centre-igc-wageningen-university-research-yale-research-initiative-on-innovation-and-scale-y-rise-wzb-berlin-social-science-center-and-columbia-university}{%
-\paragraph*{Sierra Leone, Towns that are Candidates for Rural Electrification Nation-wide sample, International Growth Centre (IGC), Wageningen University \& Research, Yale Research Initiative on Innovation and Scale (Y-RISE), WZB Berlin Social Science Center and Columbia University}\label{sierra-leone-towns-that-are-candidates-for-rural-electrification-nation-wide-sample-international-growth-centre-igc-wageningen-university-research-yale-research-initiative-on-innovation-and-scale-y-rise-wzb-berlin-social-science-center-and-columbia-university}}
-\addcontentsline{toc}{paragraph}{Sierra Leone, Towns that are Candidates for Rural Electrification Nation-wide sample, International Growth Centre (IGC), Wageningen University \& Research, Yale Research Initiative on Innovation and Scale (Y-RISE), WZB Berlin Social Science Center and Columbia University}
-
-\textbf{Project Title:} Sierra Leone Rural Electrification (SLRE)
-
-\textbf{Target Population}: Households in 195 rural towns across all 14 districts of Sierra Leone. Of these, 97 villages were selected to benefit from an electrification program.
-
-\textbf{Original Study Design:} Initial baseline data was collected during late 2019 and early 2020 as part of a study to assess the impact of Rural Electrification in rural towns in Sierra Leone.
-
-\emph{Intervention:} The Government of Sierra Leone (GoSL) in collaboration with the United Nations Office for Project Services (UNOPS) and international donors is implementing the Rural Renewable Energy Project (RREP).
-In its first wave, during 2017, the project provided stand-alone solar photovoltaic powered mini-grids to 54 communities across the country.
-Construction of mini-grids in a further 43 towns is ongoing.
-In RREP communities, engineers construct 6kW--36kW power mini-grids that provide reliable power year-round.
-Electricity is free for schools and clinics.
-Residential and commercial users can acquire connections from commercial operators.
-
-\emph{Village Sampling Frame:} Household data was collected in 195 towns across all 12 districts of Sierra Leone.
-The GoSL selected 97 towns with (planned) mini-grids.
-We used Propensity Score Matching to select 98 control communities.
-Within communities, respondents were randomly selected from a census roster stratified by occupation status of farmers, business owners and other occupations {[}47 percent, 47 percent and 7 percent{]}.
-In each village, the intended sample was 43 households (20 farmers, 20 businesses, 3 others).
-Data was collected during June--July (108 communities) and November--December 2019 (87 communities).
-If a household on the sampling list was not available on the village visit day, we had a randomly sampled list of replacement households to survey.
-The replacement household would be the same occupation as the sampled household would have been so the sample ratio of 20-20-3 still held in each community.
-
-\textbf{COVID-19 Survey Design:} The goal was to assess households' degree of economic vulnerability in the face of the COVID-19 pandemic.
-
-\emph{Sampling Frame:} The COVID-19 survey data comprises 2,110 respondents from 186 towns from the original baseline survey.
-Phone surveys were attempted to all 195 rural communities from the baseline survey.
-The total baseline household sample comprised 7047 respondents.
-We recontacted all baseline respondents that listed a phone number (4,594 respondents) and obtained informed consent for the phone survey.
-We implemented several waves of the phone survey, recontracting a respondent about every month.
-In wave 7, we added questions related to Vaccine Acceptability.\footnote{The data was first reported in \url{https://www.theigc.org/wp-content/uploads/2020/05/Meriggi-et-al-Data-Brief-2020.pdf}}.
-
-\emph{Survey Dates:} October 7, 2020 and January 20, 2021 (earlier rounds included Wave 1: April 29-May 15; Wave 2: May 15-June 4; Wave 3: June 5-June 17; Wave 4: June 17-June 30; Wave 5: July 1-August 8; Wave 6: August 19-October 1).
-The median survey time was 33 minutes.
-
-\emph{Sample size, tracking and attrition:} Data collection took place between October 7 and January 20, 2021with 2,110 respondents, in 186 towns for a tracking rate of 46 percent.
-
-\emph{Sampling Weights:} None
-
-\emph{IRB Approval:} Approval was secured from Sierra Leone Ethics and Scientific Review Committee (SLERC 2904202) and Wageningen University (24062020).
-
-\hypertarget{uganda}{%
-\subsubsection*{Uganda}\label{uganda}}
-\addcontentsline{toc}{subsubsection}{Uganda}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-        \item First confirmed case: March 21, 2020
-        \item Total cases:  741 as of June 18, 2020 and 6,468 as of September 21, 2020         \item Total deaths:  0 as of June 18, 2020 and 63 as of September 21, 2020 
-\end{itemize}
-
-\hypertarget{uganda-subnational-sample-international-growth-center-trinity-college-dublin-stockholm-school-of-economics-and-misum-institute-for-international-economic-studies-stockholm-university}{%
-\paragraph*{Uganda Subnational sample, International Growth Center, Trinity College Dublin, Stockholm School of Economics and Misum, Institute for International Economic Studies, Stockholm University}\label{uganda-subnational-sample-international-growth-center-trinity-college-dublin-stockholm-school-of-economics-and-misum-institute-for-international-economic-studies-stockholm-university}}
-\addcontentsline{toc}{paragraph}{Uganda Subnational sample, International Growth Center, Trinity College Dublin, Stockholm School of Economics and Misum, Institute for International Economic Studies, Stockholm University}
-
-\textbf{Target Population}: Women from semi-rural and rural villages across 13 districts in Uganda (Iganga, Kayunga, Mbale, Mityana, Apac, Dokolo, Gulu, Adjumani, Koboko, Maracha, Nebbi, Soroti, Kumi).
-
-\textbf{Original Study Design:} Initial baseline data was collected in 2016 as part of a large cluster randomized controlled trial, with the aim of selecting households likely to have children during the study period.
-Four criterias for selection were thus used, in descending order of importance: the household has a woman that is currently pregnant, or aged 16-30 years old, with a young child less than three years old, and/or married (formally or informally).
-In each household, the respondent was chosen as the female household head or the primary female health care giver of the household if the household head could not be found.
-
-\textbf{COVID-19 Survey Design:} The data was collected through multiple rounds of phone surveys.
-The variable measuring age was constructed by approximation, using the baseline data from 2016 and adding 4 years to the 2016 measure.
-When the baseline respondent was replaced, the initial age information was deleted.
-
-\emph{Sampling Frame:} Households were selected within 500 clusters (the village of the household).
-
-\emph{Survey Dates:} September 21 to December 06, 2020.
-
-\emph{Sample size, tracking and attrition:} Out of 2,743 respondents, 1752 were included, provided that they answered the main question about vaccine uptake.
-
-\emph{Sampling Weights:} None.
-
-\hypertarget{uganda-subnational-sample-wzb-berlin-social-science-center-and-columbia-university-nyu-abu-dhabi-innovations-for-poverty-action-ipa}{%
-\subsubsection*{Uganda Subnational sample, WZB Berlin Social Science Center and Columbia University, NYU Abu Dhabi, Innovations for Poverty Action (IPA)}\label{uganda-subnational-sample-wzb-berlin-social-science-center-and-columbia-university-nyu-abu-dhabi-innovations-for-poverty-action-ipa}}
-\addcontentsline{toc}{subsubsection}{Uganda Subnational sample, WZB Berlin Social Science Center and Columbia University, NYU Abu Dhabi, Innovations for Poverty Action (IPA)}
-
-\textbf{Target Population:} All residents of Kampala who are Ugandan citizens, above the age of 18, and agree in principle to attend a short citizen consultative meeting.
-
-\textbf{Original Study Design:} Baseline data was collected between July and October 2019 for an intervention that randomized citizen attendance to a set of 188 consultative meetings organized across Kampala.
-The meetings were organized to collect citizen preferences for the design of a forthcoming municipal citizen charter.
-The study also aimed to assess patterns of political inequality in meeting participation, dynamics, and outcomes, as well as study the subsequent effects on prosociality of being incorporated in this participatory process.
-1/3 of the sample was randomly allocated to control, while 2/3 of respondents were invited to attend a consultative meeting.
-The consultations took place between November 2019 and February 2020 across Kampala divisions.
-
-\emph{Intervention:} The intervention consisted of attendance at the consultative meeting organized a few months after baseline data collection.
-A further randomization allocated ½ of the invited participants to a meeting moderated by a local bureaucrat, while the remaining ones attended a meeting moderated by a neutral discussion leader.
-
-\textbf{COVID-19 Survey Design:} The COVID-19 survey sample comprises the 2,189 respondents to the baseline who were selected on the basis of their residence in the city.
-Having received permission to re-contact these individuals, we coordinated a 3-wave panel throughout the summer and fall of 2020, with respondents contacted via phone.
-The goal was to assess households' degree of economic vulnerability in the face of the COVID-19 pandemic and respondents' evaluations of performance of political actors in tackling the pandemic.
-
-\emph{Sampling Frame:} The 2,189 respondents to the baseline were randomly selected from a sampling frame of all buildings in Kampala, for which information about their geographical coordinates was available.
-After randomly selecting a set of candidate structures, interviewers sampled respondents from the subset of structures that were residential.
-
-\emph{Survey Dates:} Wave 1: June 18--July 23. Wave 2: September 4--29. Wave 3: November 23--December 12.
-
-\emph{Sample size, tracking and attrition:} Of the 2,189 respondents which we aimed to contact, we were able to reach 1,333 in Wave 1, 1,289 in Wave 2, and 1,366 in Wave 3.
-Wave 3 contained the COVID-19 vaccine module presented in this analysis.
-
-\emph{Sampling Weights:} None.
-
-\emph{IRB Approval:} The study was approved by IPA Global IRB (protocol number 15018) on May 29, 2020; WZB Berlin Social Science Center Ethics Review Board (protocol number 2020/0/91) on June 10, 2020; NYU Abu Dhabi IRB (protocol number HRPP-2020-64) on May 27, 2020; MIT Committee on the Use of Humans as Experimental Subjects (protocol number 2005000155) on June 3, 2020; and by the Mildmay Uganda Research Ethics Committee (protocol number 0604-2019) on June 11, 2020.
-
-\hypertarget{united-states-of-america-nation-wide-sample-wzb-berlin-social-science-center-cornell-university-tufts-university}{%
-\subsubsection*{United States of America Nation-wide sample, WZB Berlin Social Science Center, Cornell University, Tufts University}\label{united-states-of-america-nation-wide-sample-wzb-berlin-social-science-center-cornell-university-tufts-university}}
-\addcontentsline{toc}{subsubsection}{United States of America Nation-wide sample, WZB Berlin Social Science Center, Cornell University, Tufts University}
-
-\textbf{COVID-19 Experience}
-
-\begin{itemize}
-        \item First confirmed case: January 20, 2020
-        \item Total cases:  14,499,637 as of December 4, 2020 
-        \item Total deaths:  281,678 as of December 4, 2020 
-\end{itemize}
-
-\textbf{Target Population}: Nation-wide sample of adult internet users recruited through the market research firm Lucid.
-
-\textbf{Original Study Design:} N/A
-
-\emph{Intervention:} N/A
-
-\textbf{COVID-19 Survey Design:}This survey was part of a panel study on attitudes toward COVID-19 technologies and public health surveillance.
-
-\emph{Sampling Frame:} The Lucid Marketplace is an automated marketplace that connects researchers with willing online research participants.
-Lucid partners with a network of companies that maintain relationships with research participants by engaging them with research opportunities.
-While Lucid does not provide probability samples of the U.S.
-adult population, its quota samples approximate the marginal distributions of key demographic characteristics.
-Recent validation exercises have found that Lucid samples approximate nationally representative samples in terms of demographic characteristics and survey experiment effects.\footnote{See for instance: \url{https://journals.sagepub.com/doi/10.1177/2053168018822174}}
-
-\emph{Survey Dates:} December 4-5, 2020
-
-\emph{Sample size, tracking and attrition:} 1,959 individual online surveys. In the main question regarding intention to take the vaccine, approximately 10\% of respondents (184) did not answer
-\emph{Sampling Weights:} Post-stratification weights are computed to match marginal population distributions of income, age, education, gender, race and region among the US adult population, with target proportions based on the 2018 American Community Survey.
-
-\emph{IRB Approval:} This study received approval from the Cornell University IRB under Protocol \#2004009569.
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-\newpage
-
 \end{document}

### 2021-06-22 paper_files/figure-latex/fig3paper-1.tex
update

@@
-% Created by tikzDevice version 0.12.3.1 on 2021-05-04 13:13:00
+% Created by tikzDevice version 0.12.3.1 on 2021-06-22 11:48:27
 % !TEX encoding = UTF-8 Unicode
-\documentclass[10pt]{article}
+% !TEX program = xelatex
+
+\documentclass[fontsize=7pt,DIV=calc]{scrartcl}
 
@@
 \begin{scope}
-\path[clip] ( 48.28,541.57) rectangle (371.71,627.77);
+\path[clip] ( 41.25,541.96) rectangle (369.36,631.27);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 48.28,541.57) rectangle (371.71,627.77);
+\path[fill=fillColor] ( 41.25,541.96) rectangle (369.36,631.27);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,556.45) --
-	(371.71,556.45);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,578.39) --
-	(371.71,578.39);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,600.33) --
-	(371.71,600.33);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,622.27) --
-	(371.71,622.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,545.48) --
-	(371.71,545.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,567.42) --
-	(371.71,567.42);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,589.36) --
-	(371.71,589.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,611.30) --
-	(371.71,611.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,541.57) --
-	( 75.24,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,541.57) --
-	(120.16,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,541.57) --
-	(165.08,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,541.57) --
-	(209.99,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,541.57) --
-	(254.91,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,541.57) --
-	(299.83,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,541.57) --
-	(344.75,627.77);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,557.39) --
+	(369.36,557.39);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,580.12) --
+	(369.36,580.12);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,602.85) --
+	(369.36,602.85);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,625.57) --
+	(369.36,625.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,546.02) --
+	(369.36,546.02);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,568.75) --
+	(369.36,568.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,591.48) --
+	(369.36,591.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,614.21) --
+	(369.36,614.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,541.96) --
+	( 68.60,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,541.96) --
+	(114.17,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,541.96) --
+	(159.74,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,541.96) --
+	(205.31,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,541.96) --
+	(250.88,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,541.96) --
+	(296.45,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,541.96) --
+	(342.02,631.27);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (144.86,545.48) rectangle (185.29,561.63);
-
-\path[fill=fillColor] (234.70,545.48) rectangle (275.13,547.15);
-
-\path[fill=fillColor] (189.78,545.48) rectangle (230.21,547.06);
-
-\path[fill=fillColor] (279.62,545.48) rectangle (320.05,555.66);
-
-\path[fill=fillColor] (324.54,545.48) rectangle (364.97,546.98);
-
-\path[fill=fillColor] ( 55.02,545.48) rectangle ( 95.45,590.77);
-
-\path[fill=fillColor] ( 99.94,545.48) rectangle (140.37,556.81);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,541.57) rectangle (371.71,627.77);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,449.86) rectangle (371.71,536.07);
+\path[fill=fillColor] (139.23,546.02) rectangle (180.24,562.75);
+
+\path[fill=fillColor] (230.37,546.02) rectangle (271.38,547.75);
+
+\path[fill=fillColor] (184.80,546.02) rectangle (225.81,547.66);
+
+\path[fill=fillColor] (275.94,546.02) rectangle (316.95,556.57);
+
+\path[fill=fillColor] (321.51,546.02) rectangle (362.52,547.57);
+
+\path[fill=fillColor] ( 48.09,546.02) rectangle ( 89.10,592.94);
+
+\path[fill=fillColor] ( 93.66,546.02) rectangle (134.67,557.75);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,541.96) rectangle (369.36,631.27);
+\end{scope}
+\begin{scope}
+\path[clip] ( 41.25,447.16) rectangle (369.36,536.46);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 48.28,449.86) rectangle (371.71,536.07);
+\path[fill=fillColor] ( 41.25,447.16) rectangle (369.36,536.46);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,464.75) --
-	(371.71,464.75);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,486.69) --
-	(371.71,486.69);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,508.63) --
-	(371.71,508.63);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,530.57) --
-	(371.71,530.57);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,453.78) --
-	(371.71,453.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,475.72) --
-	(371.71,475.72);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,497.66) --
-	(371.71,497.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,519.60) --
-	(371.71,519.60);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,449.86) --
-	( 75.24,536.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,449.86) --
-	(120.16,536.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,449.86) --
-	(165.08,536.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,449.86) --
-	(209.99,536.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,449.86) --
-	(254.91,536.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,449.86) --
-	(299.83,536.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,449.86) --
-	(344.75,536.07);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,462.58) --
+	(369.36,462.58);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,485.31) --
+	(369.36,485.31);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,508.04) --
+	(369.36,508.04);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,530.77) --
+	(369.36,530.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,451.22) --
+	(369.36,451.22);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,473.95) --
+	(369.36,473.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,496.67) --
+	(369.36,496.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,519.40) --
+	(369.36,519.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,447.16) --
+	( 68.60,536.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,447.16) --
+	(114.17,536.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,447.16) --
+	(159.74,536.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,447.16) --
+	(205.31,536.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,447.16) --
+	(250.88,536.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,447.16) --
+	(296.45,536.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,447.16) --
+	(342.02,536.46);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (144.86,453.78) rectangle (185.29,485.02);
-
-\path[fill=fillColor] (234.70,453.78) rectangle (275.13,454.13);
-
-\path[fill=fillColor] (189.78,453.78) rectangle (230.21,467.91);
-
-\path[fill=fillColor] (279.62,453.78) rectangle (320.05,454.22);
-
-\path[fill=fillColor] (324.54,453.78) rectangle (364.97,455.88);
-
-\path[fill=fillColor] ( 55.02,453.78) rectangle ( 95.45,492.57);
-
-\path[fill=fillColor] ( 99.94,453.78) rectangle (140.37,454.48);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,449.86) rectangle (371.71,536.07);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,358.15) rectangle (371.71,444.36);
+\path[fill=fillColor] (139.23,451.22) rectangle (180.24,483.58);
+
+\path[fill=fillColor] (230.37,451.22) rectangle (271.38,451.58);
+
+\path[fill=fillColor] (184.80,451.22) rectangle (225.81,465.85);
+
+\path[fill=fillColor] (275.94,451.22) rectangle (316.95,451.67);
+
+\path[fill=fillColor] (321.51,451.22) rectangle (362.52,453.40);
+
+\path[fill=fillColor] ( 48.09,451.22) rectangle ( 89.10,491.40);
+
+\path[fill=fillColor] ( 93.66,451.22) rectangle (134.67,451.94);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,447.16) rectangle (369.36,536.46);
+\end{scope}
+\begin{scope}
+\path[clip] ( 41.25,352.35) rectangle (369.36,441.66);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 48.28,358.15) rectangle (371.71,444.36);
+\path[fill=fillColor] ( 41.25,352.35) rectangle (369.36,441.66);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,373.04) --
-	(371.71,373.04);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,394.98) --
-	(371.71,394.98);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,416.92) --
-	(371.71,416.92);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,438.86) --
-	(371.71,438.86);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,362.07) --
-	(371.71,362.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,384.01) --
-	(371.71,384.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,405.95) --
-	(371.71,405.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,427.89) --
-	(371.71,427.89);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,358.15) --
-	( 75.24,444.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,358.15) --
-	(120.16,444.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,358.15) --
-	(165.08,444.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,358.15) --
-	(209.99,444.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,358.15) --
-	(254.91,444.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,358.15) --
-	(299.83,444.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,358.15) --
-	(344.75,444.36);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,367.78) --
+	(369.36,367.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,390.50) --
+	(369.36,390.50);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,413.23) --
+	(369.36,413.23);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,435.96) --
+	(369.36,435.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,356.41) --
+	(369.36,356.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,379.14) --
+	(369.36,379.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,401.87) --
+	(369.36,401.87);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,424.60) --
+	(369.36,424.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,352.35) --
+	( 68.60,441.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,352.35) --
+	(114.17,441.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,352.35) --
+	(159.74,441.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,352.35) --
+	(205.31,441.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,352.35) --
+	(250.88,441.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,352.35) --
+	(296.45,441.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,352.35) --
+	(342.02,441.66);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (144.86,362.07) rectangle (185.29,375.24);
-
-\path[fill=fillColor] (234.70,362.07) rectangle (275.13,362.60);
-
-\path[fill=fillColor] (189.78,362.07) rectangle (230.21,363.04);
-
-\path[fill=fillColor] (279.62,362.07) rectangle (320.05,391.21);
-
-\path[fill=fillColor] (324.54,362.07) rectangle (364.97,362.42);
-
-\path[fill=fillColor] ( 55.02,362.07) rectangle ( 95.45,382.26);
-
-\path[fill=fillColor] ( 99.94,362.07) rectangle (140.37,385.50);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,358.15) rectangle (371.71,444.36);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,266.45) rectangle (371.71,352.65);
+\path[fill=fillColor] (139.23,356.41) rectangle (180.24,370.05);
+
+\path[fill=fillColor] (230.37,356.41) rectangle (271.38,356.96);
+
+\path[fill=fillColor] (184.80,356.41) rectangle (225.81,357.41);
+
+\path[fill=fillColor] (275.94,356.41) rectangle (316.95,386.59);
+
+\path[fill=fillColor] (321.51,356.41) rectangle (362.52,356.77);
+
+\path[fill=fillColor] ( 48.09,356.41) rectangle ( 89.10,377.32);
+
+\path[fill=fillColor] ( 93.66,356.41) rectangle (134.67,380.69);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,352.35) rectangle (369.36,441.66);
+\end{scope}
+\begin{scope}
+\path[clip] ( 41.25,257.55) rectangle (369.36,346.85);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 48.28,266.45) rectangle (371.71,352.65);
+\path[fill=fillColor] ( 41.25,257.55) rectangle (369.36,346.85);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,281.33) --
-	(371.71,281.33);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,303.27) --
-	(371.71,303.27);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,325.21) --
-	(371.71,325.21);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,347.15) --
-	(371.71,347.15);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,270.36) --
-	(371.71,270.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,292.30) --
-	(371.71,292.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,314.24) --
-	(371.71,314.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,336.18) --
-	(371.71,336.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,266.45) --
-	( 75.24,352.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,266.45) --
-	(120.16,352.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,266.45) --
-	(165.08,352.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,266.45) --
-	(209.99,352.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,266.45) --
-	(254.91,352.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,266.45) --
-	(299.83,352.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,266.45) --
-	(344.75,352.65);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,272.97) --
+	(369.36,272.97);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,295.70) --
+	(369.36,295.70);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,318.43) --
+	(369.36,318.43);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,341.16) --
+	(369.36,341.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,261.60) --
+	(369.36,261.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,284.33) --
+	(369.36,284.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,307.06) --
+	(369.36,307.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,329.79) --
+	(369.36,329.79);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,257.55) --
+	( 68.60,346.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,257.55) --
+	(114.17,346.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,257.55) --
+	(159.74,346.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,257.55) --
+	(205.31,346.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,257.55) --
+	(250.88,346.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,257.55) --
+	(296.45,346.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,257.55) --
+	(342.02,346.85);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (144.86,270.36) rectangle (185.29,273.09);
-
-\path[fill=fillColor] (234.70,270.36) rectangle (275.13,270.36);
-
-\path[fill=fillColor] (189.78,270.36) rectangle (230.21,271.86);
-
-\path[fill=fillColor] (279.62,270.36) rectangle (320.05,275.46);
-
-\path[fill=fillColor] ( 55.02,270.36) rectangle ( 95.45,348.73);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,266.45) rectangle (371.71,352.65);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,174.74) rectangle (371.71,260.95);
+\path[fill=fillColor] (139.23,261.60) rectangle (180.24,264.42);
+
+\path[fill=fillColor] (230.37,261.60) rectangle (271.38,261.60);
+
+\path[fill=fillColor] (184.80,261.60) rectangle (225.81,263.15);
+
+\path[fill=fillColor] (275.94,261.60) rectangle (316.95,266.88);
+
+\path[fill=fillColor] ( 48.09,261.60) rectangle ( 89.10,342.79);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,257.55) rectangle (369.36,346.85);
+\end{scope}
+\begin{scope}
+\path[clip] ( 41.25,162.74) rectangle (369.36,252.05);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 48.28,174.74) rectangle (371.71,260.95);
+\path[fill=fillColor] ( 41.25,162.74) rectangle (369.36,252.05);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,189.63) --
-	(371.71,189.63);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,211.57) --
-	(371.71,211.57);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,233.51) --
-	(371.71,233.51);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,255.45) --
-	(371.71,255.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,178.66) --
-	(371.71,178.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,200.60) --
-	(371.71,200.60);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,222.54) --
-	(371.71,222.54);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,244.48) --
-	(371.71,244.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,174.74) --
-	( 75.24,260.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,174.74) --
-	(120.16,260.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,174.74) --
-	(165.08,260.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,174.74) --
-	(209.99,260.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,174.74) --
-	(254.91,260.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,174.74) --
-	(299.83,260.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,174.74) --
-	(344.75,260.95);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,178.16) --
+	(369.36,178.16);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,200.89) --
+	(369.36,200.89);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,223.62) --
+	(369.36,223.62);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,246.35) --
+	(369.36,246.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,166.80) --
+	(369.36,166.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,189.53) --
+	(369.36,189.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,212.26) --
+	(369.36,212.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,234.98) --
+	(369.36,234.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,162.74) --
+	( 68.60,252.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,162.74) --
+	(114.17,252.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,162.74) --
+	(159.74,252.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,162.74) --
+	(205.31,252.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,162.74) --
+	(250.88,252.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,162.74) --
+	(296.45,252.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,162.74) --
+	(342.02,252.05);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (144.86,178.66) rectangle (185.29,193.40);
-
-\path[fill=fillColor] (234.70,178.66) rectangle (275.13,179.97);
-
-\path[fill=fillColor] (189.78,178.66) rectangle (230.21,183.31);
-
-\path[fill=fillColor] (279.62,178.66) rectangle (320.05,187.96);
-
-\path[fill=fillColor] (324.54,178.66) rectangle (364.97,180.76);
-
-\path[fill=fillColor] ( 55.02,178.66) rectangle ( 95.45,220.87);
-
-\path[fill=fillColor] ( 99.94,178.66) rectangle (140.37,195.60);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,174.74) rectangle (371.71,260.95);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28, 83.03) rectangle (371.71,169.24);
+\path[fill=fillColor] (139.23,166.80) rectangle (180.24,182.07);
+
+\path[fill=fillColor] (230.37,166.80) rectangle (271.38,168.16);
+
+\path[fill=fillColor] (184.80,166.80) rectangle (225.81,171.62);
+
+\path[fill=fillColor] (275.94,166.80) rectangle (316.95,176.44);
+
+\path[fill=fillColor] (321.51,166.80) rectangle (362.52,168.98);
+
+\path[fill=fillColor] ( 48.09,166.80) rectangle ( 89.10,210.53);
+
+\path[fill=fillColor] ( 93.66,166.80) rectangle (134.67,184.34);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,162.74) rectangle (369.36,252.05);
+\end{scope}
+\begin{scope}
+\path[clip] ( 41.25, 67.93) rectangle (369.36,157.24);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 48.28, 83.03) rectangle (371.71,169.24);
+\path[fill=fillColor] ( 41.25, 67.93) rectangle (369.36,157.24);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28, 97.92) --
-	(371.71, 97.92);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,119.86) --
-	(371.71,119.86);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,141.80) --
-	(371.71,141.80);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,163.74) --
-	(371.71,163.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28, 86.95) --
-	(371.71, 86.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,108.89) --
-	(371.71,108.89);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,130.83) --
-	(371.71,130.83);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,152.77) --
-	(371.71,152.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24, 83.03) --
-	( 75.24,169.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16, 83.03) --
-	(120.16,169.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08, 83.03) --
-	(165.08,169.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99, 83.03) --
-	(209.99,169.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91, 83.03) --
-	(254.91,169.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83, 83.03) --
-	(299.83,169.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75, 83.03) --
-	(344.75,169.24);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25, 83.36) --
+	(369.36, 83.36);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,106.09) --
+	(369.36,106.09);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,128.81) --
+	(369.36,128.81);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,151.54) --
+	(369.36,151.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25, 71.99) --
+	(369.36, 71.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25, 94.72) --
+	(369.36, 94.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,117.45) --
+	(369.36,117.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,140.18) --
+	(369.36,140.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60, 67.93) --
+	( 68.60,157.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17, 67.93) --
+	(114.17,157.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74, 67.93) --
+	(159.74,157.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31, 67.93) --
+	(205.31,157.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88, 67.93) --
+	(250.88,157.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45, 67.93) --
+	(296.45,157.24);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02, 67.93) --
+	(342.02,157.24);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (144.86, 86.95) rectangle (185.29, 97.04);
-
-\path[fill=fillColor] (189.78, 86.95) rectangle (230.21, 89.06);
-
-\path[fill=fillColor] (279.62, 86.95) rectangle (320.05,106.17);
-
-\path[fill=fillColor] (324.54, 86.95) rectangle (364.97, 87.04);
-
-\path[fill=fillColor] ( 55.02, 86.95) rectangle ( 95.45,117.23);
-
-\path[fill=fillColor] ( 99.94, 86.95) rectangle (140.37,113.02);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28, 83.03) rectangle (371.71,169.24);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,541.57) rectangle (717.20,627.77);
+\path[fill=fillColor] (139.23, 71.99) rectangle (180.24, 82.45);
+
+\path[fill=fillColor] (184.80, 71.99) rectangle (225.81, 74.17);
+
+\path[fill=fillColor] (275.94, 71.99) rectangle (316.95, 91.90);
+
+\path[fill=fillColor] (321.51, 71.99) rectangle (362.52, 72.08);
+
+\path[fill=fillColor] ( 48.09, 71.99) rectangle ( 89.10,103.36);
+
+\path[fill=fillColor] ( 93.66, 71.99) rectangle (134.67, 98.99);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25, 67.93) rectangle (369.36,157.24);
+\end{scope}
+\begin{scope}
+\path[clip] (389.10,541.96) rectangle (717.20,631.27);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (393.78,541.57) rectangle (717.20,627.77);
+\path[fill=fillColor] (389.10,541.96) rectangle (717.20,631.27);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,556.45) --
-	(717.20,556.45);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,578.39) --
-	(717.20,578.39);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,600.33) --
-	(717.20,600.33);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,622.27) --
-	(717.20,622.27);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,545.48) --
-	(717.20,545.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,567.42) --
-	(717.20,567.42);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,589.36) --
-	(717.20,589.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,611.30) --
-	(717.20,611.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,541.57) --
-	(420.73,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,541.57) --
-	(465.65,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,541.57) --
-	(510.57,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,541.57) --
-	(555.49,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,541.57) --
-	(600.41,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,541.57) --
-	(645.33,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,541.57) --
-	(690.25,627.77);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,557.39) --
+	(717.20,557.39);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,580.12) --
+	(717.20,580.12);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,602.85) --
+	(717.20,602.85);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,625.57) --
+	(717.20,625.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,546.02) --
+	(717.20,546.02);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,568.75) --
+	(717.20,568.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,591.48) --
+	(717.20,591.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,614.21) --
+	(717.20,614.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,541.96) --
+	(416.44,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,541.96) --
+	(462.01,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,541.96) --
+	(507.58,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,541.96) --
+	(553.15,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,541.96) --
+	(598.72,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,541.96) --
+	(644.29,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,541.96) --
+	(689.86,631.27);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (490.36,545.48) rectangle (530.78,577.60);
-
-\path[fill=fillColor] (580.19,545.48) rectangle (620.62,546.98);
-
-\path[fill=fillColor] (535.27,545.48) rectangle (575.70,547.06);
-
-\path[fill=fillColor] (670.03,545.48) rectangle (710.46,553.30);
-
-\path[fill=fillColor] (400.52,545.48) rectangle (440.94,579.97);
-
-\path[fill=fillColor] (445.44,545.48) rectangle (485.86,555.66);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,541.57) rectangle (717.20,627.77);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,449.86) rectangle (717.20,536.07);
+\path[fill=fillColor] (487.07,546.02) rectangle (528.09,579.30);
+
+\path[fill=fillColor] (578.21,546.02) rectangle (619.22,547.57);
+
+\path[fill=fillColor] (532.64,546.02) rectangle (573.65,547.66);
+
+\path[fill=fillColor] (669.35,546.02) rectangle (710.36,554.11);
+
+\path[fill=fillColor] (395.93,546.02) rectangle (436.95,581.75);
+
+\path[fill=fillColor] (441.50,546.02) rectangle (482.52,556.57);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.10,541.96) rectangle (717.20,631.27);
+\end{scope}
+\begin{scope}
+\path[clip] (389.10,447.16) rectangle (717.20,536.46);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (393.78,449.86) rectangle (717.20,536.07);
+\path[fill=fillColor] (389.10,447.16) rectangle (717.20,536.46);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,464.75) --
-	(717.20,464.75);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,486.69) --
-	(717.20,486.69);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,508.63) --
-	(717.20,508.63);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,530.57) --
-	(717.20,530.57);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,453.78) --
-	(717.20,453.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,475.72) --
-	(717.20,475.72);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,497.66) --
-	(717.20,497.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,519.60) --
-	(717.20,519.60);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,449.86) --
-	(420.73,536.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,449.86) --
-	(465.65,536.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,449.86) --
-	(510.57,536.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,449.86) --
-	(555.49,536.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,449.86) --
-	(600.41,536.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,449.86) --
-	(645.33,536.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,449.86) --
-	(690.25,536.07);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,462.58) --
+	(717.20,462.58);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,485.31) --
+	(717.20,485.31);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,508.04) --
+	(717.20,508.04);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,530.77) --
+	(717.20,530.77);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,451.22) --
+	(717.20,451.22);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,473.95) --
+	(717.20,473.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,496.67) --
+	(717.20,496.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,519.40) --
+	(717.20,519.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,447.16) --
+	(416.44,536.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,447.16) --
+	(462.01,536.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,447.16) --
+	(507.58,536.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,447.16) --
+	(553.15,536.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,447.16) --
+	(598.72,536.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,447.16) --
+	(644.29,536.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,447.16) --
+	(689.86,536.46);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (490.36,453.78) rectangle (530.78,460.80);
-
-\path[fill=fillColor] (535.27,453.78) rectangle (575.70,460.80);
-
-\path[fill=fillColor] (625.11,453.78) rectangle (665.54,457.20);
-
-\path[fill=fillColor] (670.03,453.78) rectangle (710.46,457.46);
-
-\path[fill=fillColor] (400.52,453.78) rectangle (440.94,504.68);
-
-\path[fill=fillColor] (445.44,453.78) rectangle (485.86,469.57);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,449.86) rectangle (717.20,536.07);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,358.15) rectangle (717.20,444.36);
+\path[fill=fillColor] (487.07,451.22) rectangle (528.09,458.49);
+
+\path[fill=fillColor] (532.64,451.22) rectangle (573.65,458.49);
+
+\path[fill=fillColor] (623.78,451.22) rectangle (664.79,454.76);
+
+\path[fill=fillColor] (669.35,451.22) rectangle (710.36,455.04);
+
+\path[fill=fillColor] (395.93,451.22) rectangle (436.95,503.95);
+
+\path[fill=fillColor] (441.50,451.22) rectangle (482.52,467.58);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.10,447.16) rectangle (717.20,536.46);
+\end{scope}
+\begin{scope}
+\path[clip] (389.10,352.35) rectangle (717.20,441.66);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (393.78,358.15) rectangle (717.20,444.36);
+\path[fill=fillColor] (389.10,352.35) rectangle (717.20,441.66);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,373.04) --
-	(717.20,373.04);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,394.98) --
-	(717.20,394.98);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,416.92) --
-	(717.20,416.92);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,438.86) --
-	(717.20,438.86);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,362.07) --
-	(717.20,362.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,384.01) --
-	(717.20,384.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,405.95) --
-	(717.20,405.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,427.89) --
-	(717.20,427.89);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,358.15) --
-	(420.73,444.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,358.15) --
-	(465.65,444.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,358.15) --
-	(510.57,444.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,358.15) --
-	(555.49,444.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,358.15) --
-	(600.41,444.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,358.15) --
-	(645.33,444.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,358.15) --
-	(690.25,444.36);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,367.78) --
+	(717.20,367.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,390.50) --
+	(717.20,390.50);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,413.23) --
+	(717.20,413.23);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,435.96) --
+	(717.20,435.96);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,356.41) --
+	(717.20,356.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,379.14) --
+	(717.20,379.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,401.87) --
+	(717.20,401.87);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,424.60) --
+	(717.20,424.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,352.35) --
+	(416.44,441.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,352.35) --
+	(462.01,441.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,352.35) --
+	(507.58,441.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,352.35) --
+	(553.15,441.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,352.35) --
+	(598.72,441.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,352.35) --
+	(644.29,441.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,352.35) --
+	(689.86,441.66);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (490.36,362.07) rectangle (530.78,369.44);
-
-\path[fill=fillColor] (580.19,362.07) rectangle (620.62,362.51);
-
-\path[fill=fillColor] (535.27,362.07) rectangle (575.70,366.20);
-
-\path[fill=fillColor] (625.11,362.07) rectangle (665.54,369.88);
-
-\path[fill=fillColor] (670.03,362.07) rectangle (710.46,363.04);
-
-\path[fill=fillColor] (400.52,362.07) rectangle (440.94,400.69);
-
-\path[fill=fillColor] (445.44,362.07) rectangle (485.86,390.59);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,358.15) rectangle (717.20,444.36);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,266.45) rectangle (717.20,352.65);
+\path[fill=fillColor] (487.07,356.41) rectangle (528.09,364.05);
+
+\path[fill=fillColor] (578.21,356.41) rectangle (619.22,356.87);
+
+\path[fill=fillColor] (532.64,356.41) rectangle (573.65,360.68);
+
+\path[fill=fillColor] (623.78,356.41) rectangle (664.79,364.50);
+
+\path[fill=fillColor] (669.35,356.41) rectangle (710.36,357.41);
+
+\path[fill=fillColor] (395.93,356.41) rectangle (436.95,396.41);
+
+\path[fill=fillColor] (441.50,356.41) rectangle (482.52,385.96);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.10,352.35) rectangle (717.20,441.66);
+\end{scope}
+\begin{scope}
+\path[clip] (389.10,257.55) rectangle (717.20,346.85);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (393.78,266.45) rectangle (717.20,352.65);
+\path[fill=fillColor] (389.10,257.55) rectangle (717.20,346.85);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,281.33) --
-	(717.20,281.33);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,303.27) --
-	(717.20,303.27);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,325.21) --
-	(717.20,325.21);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,347.15) --
-	(717.20,347.15);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,270.36) --
-	(717.20,270.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,292.30) --
-	(717.20,292.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,314.24) --
-	(717.20,314.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,336.18) --
-	(717.20,336.18);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,266.45) --
-	(420.73,352.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,266.45) --
-	(465.65,352.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,266.45) --
-	(510.57,352.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,266.45) --
-	(555.49,352.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,266.45) --
-	(600.41,352.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,266.45) --
-	(645.33,352.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,266.45) --
-	(690.25,352.65);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,272.97) --
+	(717.20,272.97);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,295.70) --
+	(717.20,295.70);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,318.43) --
+	(717.20,318.43);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,341.16) --
+	(717.20,341.16);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,261.60) --
+	(717.20,261.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,284.33) --
+	(717.20,284.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,307.06) --
+	(717.20,307.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,329.79) --
+	(717.20,329.79);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,257.55) --
+	(416.44,346.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,257.55) --
+	(462.01,346.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,257.55) --
+	(507.58,346.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,257.55) --
+	(553.15,346.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,257.55) --
+	(598.72,346.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,257.55) --
+	(644.29,346.85);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,257.55) --
+	(689.86,346.85);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (490.36,270.36) rectangle (530.78,278.70);
-
-\path[fill=fillColor] (580.19,270.36) rectangle (620.62,275.28);
-
-\path[fill=fillColor] (535.27,270.36) rectangle (575.70,276.68);
-
-\path[fill=fillColor] (625.11,270.36) rectangle (665.54,279.32);
-
-\path[fill=fillColor] (670.03,270.36) rectangle (710.46,270.45);
-
-\path[fill=fillColor] (400.52,270.36) rectangle (440.94,301.08);
-
-\path[fill=fillColor] (445.44,270.36) rectangle (485.86,298.80);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,266.45) rectangle (717.20,352.65);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,174.74) rectangle (717.20,260.95);
+\path[fill=fillColor] (487.07,261.60) rectangle (528.09,270.24);
+
+\path[fill=fillColor] (578.21,261.60) rectangle (619.22,266.70);
+
+\path[fill=fillColor] (532.64,261.60) rectangle (573.65,268.15);
+
+\path[fill=fillColor] (623.78,261.60) rectangle (664.79,270.88);
+
+\path[fill=fillColor] (669.35,261.60) rectangle (710.36,261.70);
+
+\path[fill=fillColor] (395.93,261.60) rectangle (436.95,293.42);
+
+\path[fill=fillColor] (441.50,261.60) rectangle (482.52,291.06);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.10,257.55) rectangle (717.20,346.85);
+\end{scope}
+\begin{scope}
+\path[clip] (389.10,162.74) rectangle (717.20,252.05);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] (393.78,174.74) rectangle (717.20,260.95);
+\path[fill=fillColor] (389.10,162.74) rectangle (717.20,252.05);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,189.63) --
-	(717.20,189.63);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,211.57) --
-	(717.20,211.57);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,233.51) --
-	(717.20,233.51);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,255.45) --
-	(717.20,255.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,178.66) --
-	(717.20,178.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,200.60) --
-	(717.20,200.60);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,222.54) --
-	(717.20,222.54);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,244.48) --
-	(717.20,244.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,174.74) --
-	(420.73,260.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,174.74) --
-	(465.65,260.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,174.74) --
-	(510.57,260.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,174.74) --
-	(555.49,260.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,174.74) --
-	(600.41,260.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,174.74) --
-	(645.33,260.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,174.74) --
-	(690.25,260.95);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,178.16) --
+	(717.20,178.16);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,200.89) --
+	(717.20,200.89);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,223.62) --
+	(717.20,223.62);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,246.35) --
+	(717.20,246.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,166.80) --
+	(717.20,166.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,189.53) --
+	(717.20,189.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,212.26) --
+	(717.20,212.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,234.98) --
+	(717.20,234.98);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,162.74) --
+	(416.44,252.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,162.74) --
+	(462.01,252.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,162.74) --
+	(507.58,252.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,162.74) --
+	(553.15,252.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,162.74) --
+	(598.72,252.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,162.74) --
+	(644.29,252.05);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,162.74) --
+	(689.86,252.05);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (490.36,178.66) rectangle (530.78,203.32);
-
-\path[fill=fillColor] (580.19,178.66) rectangle (620.62,182.96);
-
-\path[fill=fillColor] (535.27,178.66) rectangle (575.70,180.59);
-
-\path[fill=fillColor] (625.11,178.66) rectangle (665.54,193.23);
-
-\path[fill=fillColor] (400.52,178.66) rectangle (440.94,210.25);
-
-\path[fill=fillColor] (445.44,178.66) rectangle (485.86,189.45);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,174.74) rectangle (717.20,260.95);
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,541.57) rectangle (393.78,627.77);
+\path[fill=fillColor] (487.07,166.80) rectangle (528.09,192.35);
+
+\path[fill=fillColor] (578.21,166.80) rectangle (619.22,171.25);
+
+\path[fill=fillColor] (532.64,166.80) rectangle (573.65,168.80);
+
+\path[fill=fillColor] (623.78,166.80) rectangle (664.79,181.89);
+
+\path[fill=fillColor] (395.93,166.80) rectangle (436.95,199.53);
+
+\path[fill=fillColor] (441.50,166.80) rectangle (482.52,177.98);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.10,162.74) rectangle (717.20,252.05);
+\end{scope}
+\begin{scope}
+\path[clip] (374.86,541.96) rectangle (389.10,631.27);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,541.57) rectangle (393.78,627.77);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (374.86,541.96) rectangle (389.10,631.27);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,584.67) {Colombia};
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,449.86) rectangle (393.78,536.07);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (384.10,586.62) {Colombia};
+\end{scope}
+\begin{scope}
+\path[clip] (374.86,447.16) rectangle (389.10,536.46);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,449.86) rectangle (393.78,536.07);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (374.86,447.16) rectangle (389.10,536.46);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,492.96) {Nigeria};
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,358.15) rectangle (393.78,444.36);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (384.10,491.81) {Nigeria};
+\end{scope}
+\begin{scope}
+\path[clip] (374.86,352.35) rectangle (389.10,441.66);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,358.15) rectangle (393.78,444.36);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (374.86,352.35) rectangle (389.10,441.66);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,401.26) {Sierra Leone 1};
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,266.45) rectangle (393.78,352.65);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (384.10,397.00) {Sierra Leone 1};
+\end{scope}
+\begin{scope}
+\path[clip] (374.86,257.55) rectangle (389.10,346.85);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,266.45) rectangle (393.78,352.65);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (374.86,257.55) rectangle (389.10,346.85);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,309.55) {Uganda 2};
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,174.74) rectangle (393.78,260.95);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (384.10,302.20) {Uganda 2};
+\end{scope}
+\begin{scope}
+\path[clip] (374.86,162.74) rectangle (389.10,252.05);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (377.21,174.74) rectangle (393.78,260.95);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (374.86,162.74) rectangle (389.10,252.05);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (388.52,217.84) {Russia};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,541.57) rectangle ( 48.28,627.77);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at (384.10,207.39) {Russia};
+\end{scope}
+\begin{scope}
+\path[clip] ( 27.01,541.96) rectangle ( 41.25,631.27);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,541.57) rectangle ( 48.28,627.77);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 27.01,541.96) rectangle ( 41.25,631.27);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,584.67) {Burkina Faso};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,449.86) rectangle ( 48.28,536.07);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.26,586.62) {Burkina Faso};
+\end{scope}
+\begin{scope}
+\path[clip] ( 27.01,447.16) rectangle ( 41.25,536.46);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,449.86) rectangle ( 48.28,536.07);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 27.01,447.16) rectangle ( 41.25,536.46);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,492.96) {Nepal};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,358.15) rectangle ( 48.28,444.36);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.26,491.81) {Nepal};
+\end{scope}
+\begin{scope}
+\path[clip] ( 27.01,352.35) rectangle ( 41.25,441.66);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,358.15) rectangle ( 48.28,444.36);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 27.01,352.35) rectangle ( 41.25,441.66);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,401.26) {Rwanda};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,266.45) rectangle ( 48.28,352.65);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.26,397.00) {Rwanda};
+\end{scope}
+\begin{scope}
+\path[clip] ( 27.01,257.55) rectangle ( 41.25,346.85);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,266.45) rectangle ( 48.28,352.65);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 27.01,257.55) rectangle ( 41.25,346.85);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,309.55) {Sierra Leone 2};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71,174.74) rectangle ( 48.28,260.95);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.26,302.20) {Sierra Leone 2};
+\end{scope}
+\begin{scope}
+\path[clip] ( 27.01,162.74) rectangle ( 41.25,252.05);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71,174.74) rectangle ( 48.28,260.95);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 27.01,162.74) rectangle ( 41.25,252.05);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,217.84) {All LMICs};
-\end{scope}
-\begin{scope}
-\path[clip] ( 31.71, 83.03) rectangle ( 48.28,169.24);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.26,207.39) {All LMICs};
+\end{scope}
+\begin{scope}
+\path[clip] ( 27.01, 67.93) rectangle ( 41.25,157.24);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 31.71, 83.03) rectangle ( 48.28,169.24);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 27.01, 67.93) rectangle ( 41.25,157.24);
 \definecolor{drawColor}{gray}{0.10}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 43.03,126.14) {USA};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24, 80.28) --
-	( 75.24, 83.03);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16, 80.28) --
-	(120.16, 83.03);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08, 80.28) --
-	(165.08, 83.03);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99, 80.28) --
-	(209.99, 83.03);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91, 80.28) --
-	(254.91, 83.03);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83, 80.28) --
-	(299.83, 83.03);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75, 80.28) --
-	(344.75, 83.03);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 36.26,112.59) {USA};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60, 65.18) --
+	( 68.60, 67.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17, 65.18) --
+	(114.17, 67.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74, 65.18) --
+	(159.74, 67.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31, 65.18) --
+	(205.31, 67.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88, 65.18) --
+	(250.88, 67.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45, 65.18) --
+	(296.45, 67.93);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02, 65.18) --
+	(342.02, 67.93);
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 78.27, 78.08) {Health workers};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (118.43, 78.08) {Government or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (127.94, 78.08) {MoH};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (163.35, 78.08) {Family or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (172.86, 78.08) {Friends};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (198.77, 78.08) {Famous person,};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (208.27, 78.08) {religious leader};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (217.78, 78.08) {or traditional};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (227.28, 78.08) {healers};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (248.44, 78.08) {Newspapers,};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (257.95, 78.08) {radio or online};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (267.45, 78.08) {groups};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (302.86, 78.08) {Other};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (343.03, 78.08) {Don't know or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (352.54, 78.08) {Refuse};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,171.99) --
-	(420.73,174.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,171.99) --
-	(465.65,174.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,171.99) --
-	(510.57,174.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,171.99) --
-	(555.49,174.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,171.99) --
-	(600.41,174.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,171.99) --
-	(645.33,174.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,171.99) --
-	(690.25,174.74);
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 70.72, 62.98) {Health workers};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (111.53, 62.98) {Government or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (121.04, 62.98) {MoH};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (157.10, 62.98) {Family or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (166.61, 62.98) {Friends};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (193.17, 62.98) {Famous person,};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (202.67, 62.98) {religious leader};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (212.18, 62.98) {or traditional};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (221.68, 62.98) {healers};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (243.49, 62.98) {Newspapers,};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (253.00, 62.98) {radio or online};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (262.50, 62.98) {groups};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (298.57, 62.98) {Other};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (339.38, 62.98) {Don't know or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (348.89, 62.98) {Refuse};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,159.99) --
+	(416.44,162.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,159.99) --
+	(462.01,162.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,159.99) --
+	(507.58,162.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,159.99) --
+	(553.15,162.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,159.99) --
+	(598.72,162.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,159.99) --
+	(644.29,162.74);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,159.99) --
+	(689.86,162.74);
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (423.76,169.79) {Health workers};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (463.93,169.79) {Government or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (473.43,169.79) {MoH};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (508.85,169.79) {Family or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (518.35,169.79) {Friends};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (544.26,169.79) {Famous person,};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (553.77,169.79) {religious leader};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (563.27,169.79) {or traditional};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (572.78,169.79) {healers};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (593.93,169.79) {Newspapers,};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (603.44,169.79) {radio or online};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (612.94,169.79) {groups};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (648.36,169.79) {Other};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (688.53,169.79) {Don't know or};
-
-\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (698.03,169.79) {Refuse};
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (418.56,157.79) {Health workers};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (459.38,157.79) {Government or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (468.88,157.79) {MoH};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (504.95,157.79) {Family or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (514.45,157.79) {Friends};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (541.01,157.79) {Famous person,};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (550.52,157.79) {religious leader};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (560.02,157.79) {or traditional};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (569.53,157.79) {healers};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (591.34,157.79) {Newspapers,};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (600.84,157.79) {radio or online};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (610.34,157.79) {groups};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (646.41,157.79) {Other};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (687.23,157.79) {Don't know or};
+
+\node[text=drawColor,rotate= 90.00,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.88] at (696.73,157.79) {Refuse};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,542.45) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,564.39) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,586.33) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,608.27) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,545.48) --
-	( 31.71,545.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,567.42) --
-	( 31.71,567.42);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,589.36) --
-	( 31.71,589.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,611.30) --
-	( 31.71,611.30);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,543.90) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,566.63) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,589.36) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,612.09) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,546.02) --
+	( 27.01,546.02);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,568.75) --
+	( 27.01,568.75);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,591.48) --
+	( 27.01,591.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,614.21) --
+	( 27.01,614.21);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,450.75) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,472.69) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,494.63) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,516.57) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,453.78) --
-	( 31.71,453.78);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,475.72) --
-	( 31.71,475.72);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,497.66) --
-	( 31.71,497.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,519.60) --
-	( 31.71,519.60);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,449.10) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,471.82) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,494.55) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,517.28) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,451.22) --
+	( 27.01,451.22);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,473.95) --
+	( 27.01,473.95);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,496.67) --
+	( 27.01,496.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,519.40) --
+	( 27.01,519.40);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,359.04) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,380.98) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,402.92) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,424.86) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,362.07) --
-	( 31.71,362.07);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,384.01) --
-	( 31.71,384.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,405.95) --
-	( 31.71,405.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,427.89) --
-	( 31.71,427.89);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,354.29) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,377.02) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,399.75) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,422.48) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,356.41) --
+	( 27.01,356.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,379.14) --
+	( 27.01,379.14);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,401.87) --
+	( 27.01,401.87);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,424.60) --
+	( 27.01,424.60);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,267.33) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,289.27) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,311.21) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,333.15) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,270.36) --
-	( 31.71,270.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,292.30) --
-	( 31.71,292.30);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,314.24) --
-	( 31.71,314.24);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,336.18) --
-	( 31.71,336.18);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,259.48) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,282.21) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,304.94) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,327.67) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,261.60) --
+	( 27.01,261.60);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,284.33) --
+	( 27.01,284.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,307.06) --
+	( 27.01,307.06);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,329.79) --
+	( 27.01,329.79);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,175.63) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,197.57) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,219.51) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,241.45) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,178.66) --
-	( 31.71,178.66);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,200.60) --
-	( 31.71,200.60);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,222.54) --
-	( 31.71,222.54);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,244.48) --
-	( 31.71,244.48);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,164.68) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,187.41) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,210.13) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,232.86) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,166.80) --
+	( 27.01,166.80);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,189.53) --
+	( 27.01,189.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,212.26) --
+	( 27.01,212.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,234.98) --
+	( 27.01,234.98);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96, 83.92) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,105.86) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,127.80) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,149.74) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96, 86.95) --
-	( 31.71, 86.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,108.89) --
-	( 31.71,108.89);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,130.83) --
-	( 31.71,130.83);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,152.77) --
-	( 31.71,152.77);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05, 69.87) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05, 92.60) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,115.33) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,138.06) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26, 71.99) --
+	( 27.01, 71.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26, 94.72) --
+	( 27.01, 94.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,117.45) --
+	( 27.01,117.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,140.18) --
+	( 27.01,140.18);
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,355.40) {estimate};
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 10.80,349.60) {estimate};
 \end{scope}

### 2021-06-22 paper_files/figure-latex/histcattrust-1.tex
update files
update

--- 2021-03-23 paper_files/figure-latex/fig3paper-1.tex
@@
-% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:37
+% Created by tikzDevice version 0.12.3.1 on 2021-06-22 11:48:47
 % !TEX encoding = UTF-8 Unicode
-\documentclass[10pt]{article}
+% !TEX program = xelatex
+
+\documentclass[fontsize=7pt,DIV=calc]{scrartcl}
 
@@
 \begin{scope}
-\path[clip] ( 48.28,547.64) rectangle (371.71,627.77);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,547.64) rectangle (371.71,627.77);
+\path[clip] ( 41.25,548.04) rectangle (369.36,631.27);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 41.25,548.04) rectangle (369.36,631.27);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,560.96) --
-	(371.71,560.96);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,580.31) --
-	(371.71,580.31);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,599.67) --
-	(371.71,599.67);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,619.02) --
-	(371.71,619.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,551.28) --
-	(371.71,551.28);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,570.64) --
-	(371.71,570.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,589.99) --
-	(371.71,589.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,609.34) --
-	(371.71,609.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,547.64) --
-	( 75.24,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,547.64) --
-	(120.16,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,547.64) --
-	(165.08,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,547.64) --
-	(209.99,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,547.64) --
-	(254.91,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,547.64) --
-	(299.83,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,547.64) --
-	(344.75,627.77);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,561.87) --
+	(369.36,561.87);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,581.98) --
+	(369.36,581.98);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,602.08) --
+	(369.36,602.08);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,622.18) --
+	(369.36,622.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,551.82) --
+	(369.36,551.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,571.92) --
+	(369.36,571.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,592.03) --
+	(369.36,592.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,612.13) --
+	(369.36,612.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,548.04) --
+	( 68.60,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,548.04) --
+	(114.17,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,548.04) --
+	(159.74,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,548.04) --
+	(205.31,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,548.04) --
+	(250.88,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,548.04) --
+	(296.45,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,548.04) --
+	(342.02,631.27);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,551.28) rectangle (185.29,565.53);
-
-\path[fill=fillColor] (261.65,551.28) rectangle (275.13,552.76);
-
-\path[fill=fillColor] (216.73,551.28) rectangle (230.21,552.68);
-
-\path[fill=fillColor] (306.57,551.28) rectangle (320.05,560.26);
-
-\path[fill=fillColor] (351.49,551.28) rectangle (364.97,552.60);
-
-\path[fill=fillColor] ( 81.97,551.28) rectangle ( 95.45,591.23);
-
-\path[fill=fillColor] (126.89,551.28) rectangle (140.37,561.27);
+\path[fill=fillColor] (166.57,551.82) rectangle (180.24,566.62);
+
+\path[fill=fillColor] (257.71,551.82) rectangle (271.38,553.35);
+
+\path[fill=fillColor] (212.14,551.82) rectangle (225.81,553.27);
+
+\path[fill=fillColor] (303.28,551.82) rectangle (316.95,561.15);
+
+\path[fill=fillColor] (348.85,551.82) rectangle (362.52,553.19);
+
+\path[fill=fillColor] ( 75.43,551.82) rectangle ( 89.10,593.31);
+
+\path[fill=fillColor] (121.00,551.82) rectangle (134.67,562.20);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,551.28) rectangle (171.81,566.46);
-
-\path[fill=fillColor] (248.18,551.28) rectangle (261.65,552.83);
-
-\path[fill=fillColor] (203.26,551.28) rectangle (216.73,551.98);
-
-\path[fill=fillColor] (293.10,551.28) rectangle (306.57,555.00);
-
-\path[fill=fillColor] (338.02,551.28) rectangle (351.49,551.59);
-
-\path[fill=fillColor] ( 68.50,551.28) rectangle ( 81.97,595.49);
-
-\path[fill=fillColor] (113.42,551.28) rectangle (126.89,562.97);
+\path[fill=fillColor] (152.90,551.82) rectangle (166.57,567.58);
+
+\path[fill=fillColor] (244.04,551.82) rectangle (257.71,553.43);
+
+\path[fill=fillColor] (198.47,551.82) rectangle (212.14,552.55);
+
+\path[fill=fillColor] (289.61,551.82) rectangle (303.28,555.68);
+
+\path[fill=fillColor] (335.18,551.82) rectangle (348.85,552.14);
+
+\path[fill=fillColor] ( 61.76,551.82) rectangle ( 75.43,597.74);
+
+\path[fill=fillColor] (107.33,551.82) rectangle (121.00,563.96);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,551.28) rectangle (158.34,563.83);
-
-\path[fill=fillColor] (234.70,551.28) rectangle (248.18,552.52);
-
-\path[fill=fillColor] (189.78,551.28) rectangle (203.26,554.15);
-
-\path[fill=fillColor] (279.62,551.28) rectangle (293.10,570.72);
-
-\path[fill=fillColor] (324.54,551.28) rectangle (338.02,554.54);
-
-\path[fill=fillColor] ( 55.02,551.28) rectangle ( 68.50,582.79);
-
-\path[fill=fillColor] ( 99.94,551.28) rectangle (113.42,557.86);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,547.64) rectangle (371.71,627.77);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,462.01) rectangle (371.71,542.14);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,462.01) rectangle (371.71,542.14);
+\path[fill=fillColor] (139.23,551.82) rectangle (152.90,564.85);
+
+\path[fill=fillColor] (230.37,551.82) rectangle (244.04,553.11);
+
+\path[fill=fillColor] (184.80,551.82) rectangle (198.47,554.80);
+
+\path[fill=fillColor] (275.94,551.82) rectangle (289.61,572.01);
+
+\path[fill=fillColor] (321.51,551.82) rectangle (335.18,555.20);
+
+\path[fill=fillColor] ( 48.09,551.82) rectangle ( 61.76,584.55);
+
+\path[fill=fillColor] ( 93.66,551.82) rectangle (107.33,558.66);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,548.04) rectangle (369.36,631.27);
+\end{scope}
+\begin{scope}
+\path[clip] ( 41.25,459.31) rectangle (369.36,542.54);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 41.25,459.31) rectangle (369.36,542.54);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,475.33) --
-	(371.71,475.33);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,494.68) --
-	(371.71,494.68);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,514.04) --
-	(371.71,514.04);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,533.39) --
-	(371.71,533.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,465.65) --
-	(371.71,465.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,485.01) --
-	(371.71,485.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,504.36) --
-	(371.71,504.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,523.71) --
-	(371.71,523.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,462.01) --
-	( 75.24,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,462.01) --
-	(120.16,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,462.01) --
-	(165.08,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,462.01) --
-	(209.99,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,462.01) --
-	(254.91,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,462.01) --
-	(299.83,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,462.01) --
-	(344.75,542.14);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,473.14) --
+	(369.36,473.14);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,493.25) --
+	(369.36,493.25);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,513.35) --
+	(369.36,513.35);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,533.45) --
+	(369.36,533.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,463.09) --
+	(369.36,463.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,483.19) --
+	(369.36,483.19);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,503.30) --
+	(369.36,503.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,523.40) --
+	(369.36,523.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,459.31) --
+	( 68.60,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,459.31) --
+	(114.17,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,459.31) --
+	(159.74,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,459.31) --
+	(205.31,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,459.31) --
+	(250.88,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,459.31) --
+	(296.45,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,459.31) --
+	(342.02,542.54);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,465.65) rectangle (185.29,493.21);
-
-\path[fill=fillColor] (254.91,465.65) rectangle (275.13,465.96);
-
-\path[fill=fillColor] (216.73,465.65) rectangle (230.21,478.12);
-
-\path[fill=fillColor] (306.57,465.65) rectangle (320.05,466.04);
-
-\path[fill=fillColor] (351.49,465.65) rectangle (364.97,467.51);
-
-\path[fill=fillColor] ( 81.97,465.65) rectangle ( 95.45,499.87);
-
-\path[fill=fillColor] (126.89,465.65) rectangle (140.37,466.27);
+\path[fill=fillColor] (166.57,463.09) rectangle (180.24,491.72);
+
+\path[fill=fillColor] (250.88,463.09) rectangle (271.38,463.41);
+
+\path[fill=fillColor] (212.14,463.09) rectangle (225.81,476.04);
+
+\path[fill=fillColor] (303.28,463.09) rectangle (316.95,463.49);
+
+\path[fill=fillColor] (348.85,463.09) rectangle (362.52,465.02);
+
+\path[fill=fillColor] ( 75.43,463.09) rectangle ( 89.10,498.63);
+
+\path[fill=fillColor] (121.00,463.09) rectangle (134.67,463.74);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,465.65) rectangle (171.81,493.68);
-
-\path[fill=fillColor] (234.70,465.65) rectangle (254.91,465.96);
-
-\path[fill=fillColor] (203.26,465.65) rectangle (216.73,478.12);
-
-\path[fill=fillColor] (293.10,465.65) rectangle (306.57,466.04);
-
-\path[fill=fillColor] (338.02,465.65) rectangle (351.49,466.66);
-
-\path[fill=fillColor] ( 68.50,465.65) rectangle ( 81.97,500.26);
-
-\path[fill=fillColor] (113.42,465.65) rectangle (126.89,466.20);
+\path[fill=fillColor] (152.90,463.09) rectangle (166.57,492.20);
+
+\path[fill=fillColor] (230.37,463.09) rectangle (250.88,463.41);
+
+\path[fill=fillColor] (198.47,463.09) rectangle (212.14,476.04);
+
+\path[fill=fillColor] (289.61,463.09) rectangle (303.28,463.49);
+
+\path[fill=fillColor] (335.18,463.09) rectangle (348.85,464.14);
+
+\path[fill=fillColor] ( 61.76,463.09) rectangle ( 75.43,499.03);
+
+\path[fill=fillColor] (107.33,463.09) rectangle (121.00,463.65);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,465.65) rectangle (158.34,480.13);
-
-\path[fill=fillColor] (189.78,465.65) rectangle (203.26,478.66);
-
-\path[fill=fillColor] (279.62,465.65) rectangle (293.10,466.43);
-
-\path[fill=fillColor] (324.54,465.65) rectangle (338.02,489.81);
-
-\path[fill=fillColor] ( 55.02,465.65) rectangle ( 68.50,489.03);
-
-\path[fill=fillColor] ( 99.94,465.65) rectangle (113.42,467.28);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,462.01) rectangle (371.71,542.14);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,376.38) rectangle (371.71,456.51);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,376.38) rectangle (371.71,456.51);
+\path[fill=fillColor] (139.23,463.09) rectangle (152.90,478.13);
+
+\path[fill=fillColor] (184.80,463.09) rectangle (198.47,476.60);
+
+\path[fill=fillColor] (275.94,463.09) rectangle (289.61,463.90);
+
+\path[fill=fillColor] (321.51,463.09) rectangle (335.18,488.18);
+
+\path[fill=fillColor] ( 48.09,463.09) rectangle ( 61.76,487.38);
+
+\path[fill=fillColor] ( 93.66,463.09) rectangle (107.33,464.78);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,459.31) rectangle (369.36,542.54);
+\end{scope}
+\begin{scope}
+\path[clip] ( 41.25,370.58) rectangle (369.36,453.81);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 41.25,370.58) rectangle (369.36,453.81);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,389.70) --
-	(371.71,389.70);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,409.05) --
-	(371.71,409.05);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,428.41) --
-	(371.71,428.41);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,447.76) --
-	(371.71,447.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,380.02) --
-	(371.71,380.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,399.38) --
-	(371.71,399.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,418.73) --
-	(371.71,418.73);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,438.08) --
-	(371.71,438.08);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,376.38) --
-	( 75.24,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,376.38) --
-	(120.16,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,376.38) --
-	(165.08,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,376.38) --
-	(209.99,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,376.38) --
-	(254.91,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,376.38) --
-	(299.83,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,376.38) --
-	(344.75,456.51);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,384.41) --
+	(369.36,384.41);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,404.51) --
+	(369.36,404.51);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,424.62) --
+	(369.36,424.62);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,444.72) --
+	(369.36,444.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,374.36) --
+	(369.36,374.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,394.46) --
+	(369.36,394.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,414.57) --
+	(369.36,414.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,434.67) --
+	(369.36,434.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,370.58) --
+	( 68.60,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,370.58) --
+	(114.17,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,370.58) --
+	(159.74,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,370.58) --
+	(205.31,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,370.58) --
+	(250.88,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,370.58) --
+	(296.45,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,370.58) --
+	(342.02,453.81);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,380.02) rectangle (185.29,391.63);
-
-\path[fill=fillColor] (254.91,380.02) rectangle (275.13,380.49);
-
-\path[fill=fillColor] (216.73,380.02) rectangle (230.21,380.87);
-
-\path[fill=fillColor] (306.57,380.02) rectangle (320.05,405.72);
-
-\path[fill=fillColor] (351.49,380.02) rectangle (364.97,380.33);
-
-\path[fill=fillColor] ( 81.97,380.02) rectangle ( 95.45,397.83);
-
-\path[fill=fillColor] (126.89,380.02) rectangle (140.37,400.69);
+\path[fill=fillColor] (166.57,374.36) rectangle (180.24,386.42);
+
+\path[fill=fillColor] (250.88,374.36) rectangle (271.38,374.84);
+
+\path[fill=fillColor] (212.14,374.36) rectangle (225.81,375.25);
+
+\path[fill=fillColor] (303.28,374.36) rectangle (316.95,401.06);
+
+\path[fill=fillColor] (348.85,374.36) rectangle (362.52,374.68);
+
+\path[fill=fillColor] ( 75.43,374.36) rectangle ( 89.10,392.86);
+
+\path[fill=fillColor] (121.00,374.36) rectangle (134.67,395.83);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,380.02) rectangle (171.81,391.71);
-
-\path[fill=fillColor] (234.70,380.02) rectangle (254.91,380.56);
-
-\path[fill=fillColor] (203.26,380.02) rectangle (216.73,380.80);
-
-\path[fill=fillColor] (293.10,380.02) rectangle (306.57,404.79);
-
-\path[fill=fillColor] (338.02,380.02) rectangle (351.49,380.10);
-
-\path[fill=fillColor] ( 68.50,380.02) rectangle ( 81.97,398.45);
-
-\path[fill=fillColor] (113.42,380.02) rectangle (126.89,401.23);
+\path[fill=fillColor] (152.90,374.36) rectangle (166.57,386.50);
+
+\path[fill=fillColor] (230.37,374.36) rectangle (250.88,374.92);
+
+\path[fill=fillColor] (198.47,374.36) rectangle (212.14,375.17);
+
+\path[fill=fillColor] (289.61,374.36) rectangle (303.28,400.09);
+
+\path[fill=fillColor] (335.18,374.36) rectangle (348.85,374.44);
+
+\path[fill=fillColor] ( 61.76,374.36) rectangle ( 75.43,393.50);
+
+\path[fill=fillColor] (107.33,374.36) rectangle (121.00,396.39);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,380.02) rectangle (158.34,389.93);
-
-\path[fill=fillColor] (189.78,380.02) rectangle (203.26,382.27);
-
-\path[fill=fillColor] (279.62,380.02) rectangle (293.10,421.21);
-
-\path[fill=fillColor] (324.54,380.02) rectangle (338.02,384.28);
-
-\path[fill=fillColor] ( 55.02,380.02) rectangle ( 68.50,387.84);
-
-\path[fill=fillColor] ( 99.94,380.02) rectangle (113.42,392.10);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,376.38) rectangle (371.71,456.51);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,290.75) rectangle (371.71,370.88);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,290.75) rectangle (371.71,370.88);
+\path[fill=fillColor] (139.23,374.36) rectangle (152.90,384.65);
+
+\path[fill=fillColor] (184.80,374.36) rectangle (198.47,376.69);
+
+\path[fill=fillColor] (275.94,374.36) rectangle (289.61,417.14);
+
+\path[fill=fillColor] (321.51,374.36) rectangle (335.18,378.78);
+
+\path[fill=fillColor] ( 48.09,374.36) rectangle ( 61.76,382.48);
+
+\path[fill=fillColor] ( 93.66,374.36) rectangle (107.33,386.91);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,370.58) rectangle (369.36,453.81);
+\end{scope}
+\begin{scope}
+\path[clip] ( 41.25,281.85) rectangle (369.36,365.08);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 41.25,281.85) rectangle (369.36,365.08);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,304.07) --
-	(371.71,304.07);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,323.42) --
-	(371.71,323.42);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,342.78) --
-	(371.71,342.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,362.13) --
-	(371.71,362.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,294.39) --
-	(371.71,294.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,313.74) --
-	(371.71,313.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,333.10) --
-	(371.71,333.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,352.45) --
-	(371.71,352.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,290.75) --
-	( 75.24,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,290.75) --
-	(120.16,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,290.75) --
-	(165.08,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,290.75) --
-	(209.99,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,290.75) --
-	(254.91,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,290.75) --
-	(299.83,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,290.75) --
-	(344.75,370.88);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,295.68) --
+	(369.36,295.68);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,315.78) --
+	(369.36,315.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,335.89) --
+	(369.36,335.89);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,355.99) --
+	(369.36,355.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,285.63) --
+	(369.36,285.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,305.73) --
+	(369.36,305.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,325.84) --
+	(369.36,325.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,345.94) --
+	(369.36,345.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,281.85) --
+	( 68.60,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,281.85) --
+	(114.17,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,281.85) --
+	(159.74,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,281.85) --
+	(205.31,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,281.85) --
+	(250.88,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,281.85) --
+	(296.45,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,281.85) --
+	(342.02,365.08);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,294.39) rectangle (185.29,296.79);
-
-\path[fill=fillColor] (254.91,294.39) rectangle (275.13,294.39);
-
-\path[fill=fillColor] (216.73,294.39) rectangle (230.21,295.71);
-
-\path[fill=fillColor] (306.57,294.39) rectangle (320.05,298.88);
-
-\path[fill=fillColor] ( 81.97,294.39) rectangle ( 95.45,363.52);
+\path[fill=fillColor] (166.57,285.63) rectangle (180.24,288.12);
+
+\path[fill=fillColor] (250.88,285.63) rectangle (271.38,285.63);
+
+\path[fill=fillColor] (212.14,285.63) rectangle (225.81,287.00);
+
+\path[fill=fillColor] (303.28,285.63) rectangle (316.95,290.29);
+
+\path[fill=fillColor] ( 75.43,285.63) rectangle ( 89.10,357.44);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,294.39) rectangle (171.81,296.71);
-
-\path[fill=fillColor] (234.70,294.39) rectangle (254.91,294.47);
-
-\path[fill=fillColor] (203.26,294.39) rectangle (216.73,295.09);
-
-\path[fill=fillColor] (293.10,294.39) rectangle (306.57,295.86);
-
-\path[fill=fillColor] ( 68.50,294.39) rectangle ( 81.97,367.24);
+\path[fill=fillColor] (152.90,285.63) rectangle (166.57,288.04);
+
+\path[fill=fillColor] (230.37,285.63) rectangle (250.88,285.71);
+
+\path[fill=fillColor] (198.47,285.63) rectangle (212.14,286.35);
+
+\path[fill=fillColor] (289.61,285.63) rectangle (303.28,287.16);
+
+\path[fill=fillColor] ( 61.76,285.63) rectangle ( 75.43,361.30);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,294.39) rectangle (158.34,297.41);
-
-\path[fill=fillColor] (189.78,294.39) rectangle (203.26,300.20);
-
-\path[fill=fillColor] (279.62,294.39) rectangle (293.10,320.63);
-
-\path[fill=fillColor] ( 55.02,294.39) rectangle ( 68.50,336.74);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,290.75) rectangle (371.71,370.88);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,205.12) rectangle (371.71,285.25);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,205.12) rectangle (371.71,285.25);
+\path[fill=fillColor] (139.23,285.63) rectangle (152.90,288.77);
+
+\path[fill=fillColor] (184.80,285.63) rectangle (198.47,291.66);
+
+\path[fill=fillColor] (275.94,285.63) rectangle (289.61,312.89);
+
+\path[fill=fillColor] ( 48.09,285.63) rectangle ( 61.76,329.61);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,281.85) rectangle (369.36,365.08);
+\end{scope}
+\begin{scope}
+\path[clip] ( 41.25,193.12) rectangle (369.36,276.35);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 41.25,193.12) rectangle (369.36,276.35);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,218.44) --
-	(371.71,218.44);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,237.79) --
-	(371.71,237.79);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,257.14) --
-	(371.71,257.14);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,276.50) --
-	(371.71,276.50);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,208.76) --
-	(371.71,208.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,228.11) --
-	(371.71,228.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,247.47) --
-	(371.71,247.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,266.82) --
-	(371.71,266.82);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,205.12) --
-	( 75.24,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,205.12) --
-	(120.16,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,205.12) --
-	(165.08,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,205.12) --
-	(209.99,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,205.12) --
-	(254.91,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,205.12) --
-	(299.83,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,205.12) --
-	(344.75,285.25);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,206.95) --
+	(369.36,206.95);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,227.05) --
+	(369.36,227.05);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,247.16) --
+	(369.36,247.16);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,267.26) --
+	(369.36,267.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,196.90) --
+	(369.36,196.90);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,217.00) --
+	(369.36,217.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,237.10) --
+	(369.36,237.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,257.21) --
+	(369.36,257.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,193.12) --
+	( 68.60,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,193.12) --
+	(114.17,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,193.12) --
+	(159.74,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,193.12) --
+	(205.31,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,193.12) --
+	(250.88,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,193.12) --
+	(296.45,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,193.12) --
+	(342.02,276.35);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,208.76) rectangle (185.29,221.77);
-
-\path[fill=fillColor] (261.65,208.76) rectangle (275.13,209.92);
-
-\path[fill=fillColor] (216.73,208.76) rectangle (230.21,212.86);
-
-\path[fill=fillColor] (306.57,208.76) rectangle (320.05,216.97);
-
-\path[fill=fillColor] (351.49,208.76) rectangle (364.97,210.62);
-
-\path[fill=fillColor] ( 81.97,208.76) rectangle ( 95.45,246.00);
-
-\path[fill=fillColor] (126.89,208.76) rectangle (140.37,223.70);
+\path[fill=fillColor] (166.57,196.90) rectangle (180.24,210.41);
+
+\path[fill=fillColor] (257.71,196.90) rectangle (271.38,198.11);
+
+\path[fill=fillColor] (212.14,196.90) rectangle (225.81,201.16);
+
+\path[fill=fillColor] (303.28,196.90) rectangle (316.95,205.42);
+
+\path[fill=fillColor] (348.85,196.90) rectangle (362.52,198.83);
+
+\path[fill=fillColor] ( 75.43,196.90) rectangle ( 89.10,235.58);
+
+\path[fill=fillColor] (121.00,196.90) rectangle (134.67,212.42);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,208.76) rectangle (171.81,221.77);
-
-\path[fill=fillColor] (248.18,208.76) rectangle (261.65,209.92);
-
-\path[fill=fillColor] (203.26,208.76) rectangle (216.73,212.24);
-
-\path[fill=fillColor] (293.10,208.76) rectangle (306.57,214.10);
-
-\path[fill=fillColor] (338.02,208.76) rectangle (351.49,209.69);
-
-\path[fill=fillColor] ( 68.50,208.76) rectangle ( 81.97,248.47);
-
-\path[fill=fillColor] (113.42,208.76) rectangle (126.89,225.48);
+\path[fill=fillColor] (152.90,196.90) rectangle (166.57,210.41);
+
+\path[fill=fillColor] (244.04,196.90) rectangle (257.71,198.11);
+
+\path[fill=fillColor] (198.47,196.90) rectangle (212.14,200.52);
+
+\path[fill=fillColor] (289.61,196.90) rectangle (303.28,202.45);
+
+\path[fill=fillColor] (335.18,196.90) rectangle (348.85,197.87);
+
+\path[fill=fillColor] ( 61.76,196.90) rectangle ( 75.43,238.15);
+
+\path[fill=fillColor] (107.33,196.90) rectangle (121.00,214.27);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,208.76) rectangle (158.34,220.53);
-
-\path[fill=fillColor] (234.70,208.76) rectangle (248.18,210.00);
-
-\path[fill=fillColor] (189.78,208.76) rectangle (203.26,215.50);
-
-\path[fill=fillColor] (279.62,208.76) rectangle (293.10,228.97);
-
-\path[fill=fillColor] (324.54,208.76) rectangle (338.02,216.42);
-
-\path[fill=fillColor] ( 55.02,208.76) rectangle ( 68.50,233.92);
-
-\path[fill=fillColor] ( 99.94,208.76) rectangle (113.42,217.12);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,205.12) rectangle (371.71,285.25);
-\end{scope}
-\begin{scope}
-\path[clip] ( 48.28,119.49) rectangle (371.71,199.62);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] ( 48.28,119.49) rectangle (371.71,199.62);
+\path[fill=fillColor] (139.23,196.90) rectangle (152.90,209.12);
+
+\path[fill=fillColor] (230.37,196.90) rectangle (244.04,198.19);
+
+\path[fill=fillColor] (184.80,196.90) rectangle (198.47,203.90);
+
+\path[fill=fillColor] (275.94,196.90) rectangle (289.61,217.89);
+
+\path[fill=fillColor] (321.51,196.90) rectangle (335.18,204.86);
+
+\path[fill=fillColor] ( 48.09,196.90) rectangle ( 61.76,223.03);
+
+\path[fill=fillColor] ( 93.66,196.90) rectangle (107.33,205.58);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,193.12) rectangle (369.36,276.35);
+\end{scope}
+\begin{scope}
+\path[clip] ( 41.25,104.39) rectangle (369.36,187.62);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 41.25,104.39) rectangle (369.36,187.62);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,132.81) --
-	(371.71,132.81);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,152.16) --
-	(371.71,152.16);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,171.51) --
-	(371.71,171.51);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] ( 48.28,190.87) --
-	(371.71,190.87);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,123.13) --
-	(371.71,123.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,142.48) --
-	(371.71,142.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,161.84) --
-	(371.71,161.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 48.28,181.19) --
-	(371.71,181.19);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 75.24,119.49) --
-	( 75.24,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (120.16,119.49) --
-	(120.16,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (165.08,119.49) --
-	(165.08,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (209.99,119.49) --
-	(209.99,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (254.91,119.49) --
-	(254.91,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (299.83,119.49) --
-	(299.83,199.62);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (344.75,119.49) --
-	(344.75,199.62);
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,118.22) --
+	(369.36,118.22);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,138.32) --
+	(369.36,138.32);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,158.43) --
+	(369.36,158.43);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] ( 41.25,178.53) --
+	(369.36,178.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,108.17) --
+	(369.36,108.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,128.27) --
+	(369.36,128.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,148.37) --
+	(369.36,148.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.25,168.48) --
+	(369.36,168.48);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.60,104.39) --
+	( 68.60,187.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (114.17,104.39) --
+	(114.17,187.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (159.74,104.39) --
+	(159.74,187.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (205.31,104.39) --
+	(205.31,187.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (250.88,104.39) --
+	(250.88,187.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (296.45,104.39) --
+	(296.45,187.62);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (342.02,104.39) --
+	(342.02,187.62);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (171.81,123.13) rectangle (185.29,132.03);
-
-\path[fill=fillColor] (216.73,123.13) rectangle (230.21,124.99);
-
-\path[fill=fillColor] (306.57,123.13) rectangle (320.05,140.08);
-
-\path[fill=fillColor] (344.75,123.13) rectangle (364.97,123.21);
-
-\path[fill=fillColor] ( 81.97,123.13) rectangle ( 95.45,149.84);
-
-\path[fill=fillColor] (126.89,123.13) rectangle (140.37,146.12);
+\path[fill=fillColor] (166.57,108.17) rectangle (180.24,117.42);
+
+\path[fill=fillColor] (212.14,108.17) rectangle (225.81,110.10);
+
+\path[fill=fillColor] (303.28,108.17) rectangle (316.95,125.78);
+
+\path[fill=fillColor] (342.02,108.17) rectangle (362.52,108.25);
+
+\path[fill=fillColor] ( 75.43,108.17) rectangle ( 89.10,135.91);
+
+\path[fill=fillColor] (121.00,108.17) rectangle (134.67,132.05);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (158.34,123.13) rectangle (171.81,129.86);
-
-\path[fill=fillColor] (203.26,123.13) rectangle (216.73,124.45);
-
-\path[fill=fillColor] (293.10,123.13) rectangle (306.57,137.53);
-
-\path[fill=fillColor] ( 68.50,123.13) rectangle ( 81.97,152.62);
-
-\path[fill=fillColor] (113.42,123.13) rectangle (126.89,148.68);
+\path[fill=fillColor] (152.90,108.17) rectangle (166.57,115.17);
+
+\path[fill=fillColor] (198.47,108.17) rectangle (212.14,109.54);
+
+\path[fill=fillColor] (289.61,108.17) rectangle (303.28,123.13);
+
+\path[fill=fillColor] ( 61.76,108.17) rectangle ( 75.43,138.81);
+
+\path[fill=fillColor] (107.33,108.17) rectangle (121.00,134.70);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (144.86,123.13) rectangle (158.34,137.61);
-
-\path[fill=fillColor] (189.78,123.13) rectangle (203.26,126.38);
-
-\path[fill=fillColor] (279.62,123.13) rectangle (293.10,146.59);
-
-\path[fill=fillColor] (324.54,123.13) rectangle (344.75,123.28);
-
-\path[fill=fillColor] ( 55.02,123.13) rectangle ( 68.50,142.72);
-
-\path[fill=fillColor] ( 99.94,123.13) rectangle (113.42,139.62);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 48.28,119.49) rectangle (371.71,199.62);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,547.64) rectangle (717.20,627.77);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (393.78,547.64) rectangle (717.20,627.77);
+\path[fill=fillColor] (139.23,108.17) rectangle (152.90,123.21);
+
+\path[fill=fillColor] (184.80,108.17) rectangle (198.47,111.55);
+
+\path[fill=fillColor] (275.94,108.17) rectangle (289.61,132.53);
+
+\path[fill=fillColor] (321.51,108.17) rectangle (342.02,108.33);
+
+\path[fill=fillColor] ( 48.09,108.17) rectangle ( 61.76,128.51);
+
+\path[fill=fillColor] ( 93.66,108.17) rectangle (107.33,125.30);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.25,104.39) rectangle (369.36,187.62);
+\end{scope}
+\begin{scope}
+\path[clip] (389.10,548.04) rectangle (717.20,631.27);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (389.10,548.04) rectangle (717.20,631.27);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,560.96) --
-	(717.20,560.96);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,580.31) --
-	(717.20,580.31);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,599.67) --
-	(717.20,599.67);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,619.02) --
-	(717.20,619.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,551.28) --
-	(717.20,551.28);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,570.64) --
-	(717.20,570.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,589.99) --
-	(717.20,589.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,609.34) --
-	(717.20,609.34);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,547.64) --
-	(420.73,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,547.64) --
-	(465.65,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,547.64) --
-	(510.57,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,547.64) --
-	(555.49,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,547.64) --
-	(600.41,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,547.64) --
-	(645.33,627.77);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,547.64) --
-	(690.25,627.77);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,561.87) --
+	(717.20,561.87);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,581.98) --
+	(717.20,581.98);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,602.08) --
+	(717.20,602.08);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,622.18) --
+	(717.20,622.18);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,551.82) --
+	(717.20,551.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,571.92) --
+	(717.20,571.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,592.03) --
+	(717.20,592.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,612.13) --
+	(717.20,612.13);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,548.04) --
+	(416.44,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,548.04) --
+	(462.01,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,548.04) --
+	(507.58,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,548.04) --
+	(553.15,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,548.04) --
+	(598.72,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,548.04) --
+	(644.29,631.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,548.04) --
+	(689.86,631.27);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (517.31,551.28) rectangle (530.78,579.62);
-
-\path[fill=fillColor] (607.15,551.28) rectangle (620.62,552.60);
-
-\path[fill=fillColor] (562.23,551.28) rectangle (575.70,552.68);
-
-\path[fill=fillColor] (696.99,551.28) rectangle (710.46,558.17);
-
-\path[fill=fillColor] (427.47,551.28) rectangle (440.94,581.71);
-
-\path[fill=fillColor] (472.39,551.28) rectangle (485.86,560.26);
+\path[fill=fillColor] (514.41,551.82) rectangle (528.09,581.25);
+
+\path[fill=fillColor] (605.55,551.82) rectangle (619.22,553.19);
+
+\path[fill=fillColor] (559.98,551.82) rectangle (573.65,553.27);
+
+\path[fill=fillColor] (696.69,551.82) rectangle (710.36,558.98);
+
+\path[fill=fillColor] (423.27,551.82) rectangle (436.95,583.42);
+
+\path[fill=fillColor] (468.84,551.82) rectangle (482.52,561.15);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (503.83,551.28) rectangle (517.31,579.85);
-
-\path[fill=fillColor] (593.67,551.28) rectangle (607.15,552.60);
-
-\path[fill=fillColor] (548.75,551.28) rectangle (562.23,551.98);
-
-\path[fill=fillColor] (683.51,551.28) rectangle (696.99,556.16);
-
-\path[fill=fillColor] (413.99,551.28) rectangle (427.47,583.33);
-
-\path[fill=fillColor] (458.91,551.28) rectangle (472.39,561.12);
+\path[fill=fillColor] (500.74,551.82) rectangle (514.41,581.49);
+
+\path[fill=fillColor] (591.88,551.82) rectangle (605.55,553.19);
+
+\path[fill=fillColor] (546.31,551.82) rectangle (559.98,552.55);
+
+\path[fill=fillColor] (683.02,551.82) rectangle (696.69,556.89);
+
+\path[fill=fillColor] (409.60,551.82) rectangle (423.27,585.11);
+
+\path[fill=fillColor] (455.17,551.82) rectangle (468.84,562.03);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (490.36,551.28) rectangle (503.83,578.77);
-
-\path[fill=fillColor] (580.19,551.28) rectangle (593.67,552.37);
-
-\path[fill=fillColor] (535.27,551.28) rectangle (548.75,555.39);
-
-\path[fill=fillColor] (670.03,551.28) rectangle (683.51,565.84);
-
-\path[fill=fillColor] (400.52,551.28) rectangle (413.99,575.67);
-
-\path[fill=fillColor] (445.44,551.28) rectangle (458.91,557.17);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,547.64) rectangle (717.20,627.77);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,462.01) rectangle (717.20,542.14);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (393.78,462.01) rectangle (717.20,542.14);
+\path[fill=fillColor] (487.07,551.82) rectangle (500.74,580.37);
+
+\path[fill=fillColor] (578.21,551.82) rectangle (591.88,552.95);
+
+\path[fill=fillColor] (532.64,551.82) rectangle (546.31,556.08);
+
+\path[fill=fillColor] (669.35,551.82) rectangle (683.02,566.94);
+
+\path[fill=fillColor] (395.93,551.82) rectangle (409.60,577.15);
+
+\path[fill=fillColor] (441.50,551.82) rectangle (455.17,557.93);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.10,548.04) rectangle (717.20,631.27);
+\end{scope}
+\begin{scope}
+\path[clip] (389.10,459.31) rectangle (717.20,542.54);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (389.10,459.31) rectangle (717.20,542.54);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,475.33) --
-	(717.20,475.33);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,494.68) --
-	(717.20,494.68);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,514.04) --
-	(717.20,514.04);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,533.39) --
-	(717.20,533.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,465.65) --
-	(717.20,465.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,485.01) --
-	(717.20,485.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,504.36) --
-	(717.20,504.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,523.71) --
-	(717.20,523.71);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,462.01) --
-	(420.73,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,462.01) --
-	(465.65,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,462.01) --
-	(510.57,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,462.01) --
-	(555.49,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,462.01) --
-	(600.41,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,462.01) --
-	(645.33,542.14);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,462.01) --
-	(690.25,542.14);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,473.14) --
+	(717.20,473.14);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,493.25) --
+	(717.20,493.25);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,513.35) --
+	(717.20,513.35);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,533.45) --
+	(717.20,533.45);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,463.09) --
+	(717.20,463.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,483.19) --
+	(717.20,483.19);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,503.30) --
+	(717.20,503.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,523.40) --
+	(717.20,523.40);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,459.31) --
+	(416.44,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,459.31) --
+	(462.01,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,459.31) --
+	(507.58,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,459.31) --
+	(553.15,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,459.31) --
+	(598.72,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,459.31) --
+	(644.29,542.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,459.31) --
+	(689.86,542.54);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (517.31,465.65) rectangle (530.78,471.85);
-
-\path[fill=fillColor] (562.23,465.65) rectangle (575.70,471.85);
-
-\path[fill=fillColor] (652.07,465.65) rectangle (665.54,468.67);
-
-\path[fill=fillColor] (696.99,465.65) rectangle (710.46,468.90);
-
-\path[fill=fillColor] (427.47,465.65) rectangle (440.94,510.55);
-
-\path[fill=fillColor] (472.39,465.65) rectangle (485.86,479.59);
+\path[fill=fillColor] (514.41,463.09) rectangle (528.09,469.52);
+
+\path[fill=fillColor] (559.98,463.09) rectangle (573.65,469.52);
+
+\path[fill=fillColor] (651.12,463.09) rectangle (664.79,466.23);
+
+\path[fill=fillColor] (696.69,463.09) rectangle (710.36,466.47);
+
+\path[fill=fillColor] (423.27,463.09) rectangle (436.95,509.73);
+
+\path[fill=fillColor] (468.84,463.09) rectangle (482.52,477.57);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (503.83,465.65) rectangle (517.31,470.53);
-
-\path[fill=fillColor] (548.75,465.65) rectangle (562.23,469.60);
-
-\path[fill=fillColor] (638.59,465.65) rectangle (652.07,467.67);
-
-\path[fill=fillColor] (683.51,465.65) rectangle (696.99,466.12);
-
-\path[fill=fillColor] (413.99,465.65) rectangle (427.47,515.04);
-
-\path[fill=fillColor] (458.91,465.65) rectangle (472.39,482.37);
+\path[fill=fillColor] (500.74,463.09) rectangle (514.41,468.16);
+
+\path[fill=fillColor] (546.31,463.09) rectangle (559.98,467.19);
+
+\path[fill=fillColor] (637.45,463.09) rectangle (651.12,465.18);
+
+\path[fill=fillColor] (683.02,463.09) rectangle (696.69,463.57);
+
+\path[fill=fillColor] (409.60,463.09) rectangle (423.27,514.39);
+
+\path[fill=fillColor] (455.17,463.09) rectangle (468.84,480.46);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (490.36,465.65) rectangle (503.83,476.41);
-
-\path[fill=fillColor] (535.27,465.65) rectangle (548.75,479.43);
-
-\path[fill=fillColor] (625.11,465.65) rectangle (638.59,472.23);
-
-\path[fill=fillColor] (670.03,465.65) rectangle (683.51,478.50);
-
-\path[fill=fillColor] (400.52,465.65) rectangle (413.99,494.76);
-
-\path[fill=fillColor] (445.44,465.65) rectangle (458.91,469.99);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,462.01) rectangle (717.20,542.14);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,376.38) rectangle (717.20,456.51);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (393.78,376.38) rectangle (717.20,456.51);
+\path[fill=fillColor] (487.07,463.09) rectangle (500.74,474.27);
+
+\path[fill=fillColor] (532.64,463.09) rectangle (546.31,477.40);
+
+\path[fill=fillColor] (623.78,463.09) rectangle (637.45,469.93);
+
+\path[fill=fillColor] (669.35,463.09) rectangle (683.02,476.44);
+
+\path[fill=fillColor] (395.93,463.09) rectangle (409.60,493.33);
+
+\path[fill=fillColor] (441.50,463.09) rectangle (455.17,467.59);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.10,459.31) rectangle (717.20,542.54);
+\end{scope}
+\begin{scope}
+\path[clip] (389.10,370.58) rectangle (717.20,453.81);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (389.10,370.58) rectangle (717.20,453.81);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,389.70) --
-	(717.20,389.70);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,409.05) --
-	(717.20,409.05);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,428.41) --
-	(717.20,428.41);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,447.76) --
-	(717.20,447.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,380.02) --
-	(717.20,380.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,399.38) --
-	(717.20,399.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,418.73) --
-	(717.20,418.73);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,438.08) --
-	(717.20,438.08);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,376.38) --
-	(420.73,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,376.38) --
-	(465.65,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,376.38) --
-	(510.57,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,376.38) --
-	(555.49,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,376.38) --
-	(600.41,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,376.38) --
-	(645.33,456.51);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,376.38) --
-	(690.25,456.51);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,384.41) --
+	(717.20,384.41);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,404.51) --
+	(717.20,404.51);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,424.62) --
+	(717.20,424.62);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,444.72) --
+	(717.20,444.72);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,374.36) --
+	(717.20,374.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,394.46) --
+	(717.20,394.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,414.57) --
+	(717.20,414.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,434.67) --
+	(717.20,434.67);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,370.58) --
+	(416.44,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,370.58) --
+	(462.01,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,370.58) --
+	(507.58,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,370.58) --
+	(553.15,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,370.58) --
+	(598.72,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,370.58) --
+	(644.29,453.81);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,370.58) --
+	(689.86,453.81);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (517.31,380.02) rectangle (530.78,386.53);
-
-\path[fill=fillColor] (607.15,380.02) rectangle (620.62,380.41);
-
-\path[fill=fillColor] (562.23,380.02) rectangle (575.70,383.66);
-
-\path[fill=fillColor] (652.07,380.02) rectangle (665.54,386.91);
-
-\path[fill=fillColor] (696.99,380.02) rectangle (710.46,380.87);
-
-\path[fill=fillColor] (427.47,380.02) rectangle (440.94,414.08);
-
-\path[fill=fillColor] (472.39,380.02) rectangle (485.86,405.18);
+\path[fill=fillColor] (514.41,374.36) rectangle (528.09,381.12);
+
+\path[fill=fillColor] (605.55,374.36) rectangle (619.22,374.76);
+
+\path[fill=fillColor] (559.98,374.36) rectangle (573.65,378.14);
+
+\path[fill=fillColor] (651.12,374.36) rectangle (664.79,381.52);
+
+\path[fill=fillColor] (696.69,374.36) rectangle (710.36,375.25);
+
+\path[fill=fillColor] (423.27,374.36) rectangle (436.95,409.74);
+
+\path[fill=fillColor] (468.84,374.36) rectangle (482.52,400.49);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (503.83,380.02) rectangle (517.31,385.67);
-
-\path[fill=fillColor] (593.67,380.02) rectangle (607.15,380.41);
-
-\path[fill=fillColor] (548.75,380.02) rectangle (562.23,382.96);
-
-\path[fill=fillColor] (638.59,380.02) rectangle (652.07,382.42);
-
-\path[fill=fillColor] (683.51,380.02) rectangle (696.99,380.64);
-
-\path[fill=fillColor] (413.99,380.02) rectangle (427.47,416.87);
-
-\path[fill=fillColor] (458.91,380.02) rectangle (472.39,408.59);
+\path[fill=fillColor] (500.74,374.36) rectangle (514.41,380.23);
+
+\path[fill=fillColor] (591.88,374.36) rectangle (605.55,374.76);
+
+\path[fill=fillColor] (546.31,374.36) rectangle (559.98,377.42);
+
+\path[fill=fillColor] (637.45,374.36) rectangle (651.12,376.85);
+
+\path[fill=fillColor] (683.02,374.36) rectangle (696.69,375.00);
+
+\path[fill=fillColor] (409.60,374.36) rectangle (423.27,412.64);
+
+\path[fill=fillColor] (455.17,374.36) rectangle (468.84,404.03);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (490.36,380.02) rectangle (503.83,389.39);
-
-\path[fill=fillColor] (580.19,380.02) rectangle (593.67,380.41);
-
-\path[fill=fillColor] (535.27,380.02) rectangle (548.75,385.98);
-
-\path[fill=fillColor] (625.11,380.02) rectangle (638.59,402.78);
-
-\path[fill=fillColor] (670.03,380.02) rectangle (683.51,381.73);
-
-\path[fill=fillColor] (400.52,380.02) rectangle (413.99,404.10);
-
-\path[fill=fillColor] (445.44,380.02) rectangle (458.91,393.26);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,376.38) rectangle (717.20,456.51);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,290.75) rectangle (717.20,370.88);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (393.78,290.75) rectangle (717.20,370.88);
+\path[fill=fillColor] (487.07,374.36) rectangle (500.74,384.09);
+
+\path[fill=fillColor] (578.21,374.36) rectangle (591.88,374.76);
+
+\path[fill=fillColor] (532.64,374.36) rectangle (546.31,380.55);
+
+\path[fill=fillColor] (623.78,374.36) rectangle (637.45,398.00);
+
+\path[fill=fillColor] (669.35,374.36) rectangle (683.02,376.13);
+
+\path[fill=fillColor] (395.93,374.36) rectangle (409.60,399.37);
+
+\path[fill=fillColor] (441.50,374.36) rectangle (455.17,388.11);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.10,370.58) rectangle (717.20,453.81);
+\end{scope}
+\begin{scope}
+\path[clip] (389.10,281.85) rectangle (717.20,365.08);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (389.10,281.85) rectangle (717.20,365.08);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,304.07) --
-	(717.20,304.07);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,323.42) --
-	(717.20,323.42);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,342.78) --
-	(717.20,342.78);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,362.13) --
-	(717.20,362.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,294.39) --
-	(717.20,294.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,313.74) --
-	(717.20,313.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,333.10) --
-	(717.20,333.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,352.45) --
-	(717.20,352.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,290.75) --
-	(420.73,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,290.75) --
-	(465.65,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,290.75) --
-	(510.57,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,290.75) --
-	(555.49,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,290.75) --
-	(600.41,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,290.75) --
-	(645.33,370.88);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,290.75) --
-	(690.25,370.88);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,295.68) --
+	(717.20,295.68);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,315.78) --
+	(717.20,315.78);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,335.89) --
+	(717.20,335.89);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,355.99) --
+	(717.20,355.99);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,285.63) --
+	(717.20,285.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,305.73) --
+	(717.20,305.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,325.84) --
+	(717.20,325.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,345.94) --
+	(717.20,345.94);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,281.85) --
+	(416.44,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,281.85) --
+	(462.01,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,281.85) --
+	(507.58,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,281.85) --
+	(553.15,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,281.85) --
+	(598.72,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,281.85) --
+	(644.29,365.08);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,281.85) --
+	(689.86,365.08);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (517.31,294.39) rectangle (530.78,301.75);
-
-\path[fill=fillColor] (607.15,294.39) rectangle (620.62,298.73);
-
-\path[fill=fillColor] (562.23,294.39) rectangle (575.70,299.97);
-
-\path[fill=fillColor] (652.07,294.39) rectangle (665.54,302.29);
-
-\path[fill=fillColor] (690.25,294.39) rectangle (710.46,294.47);
-
-\path[fill=fillColor] (427.47,294.39) rectangle (440.94,321.49);
-
-\path[fill=fillColor] (472.39,294.39) rectangle (485.86,319.47);
+\path[fill=fillColor] (514.41,285.63) rectangle (528.09,293.27);
+
+\path[fill=fillColor] (605.55,285.63) rectangle (619.22,290.13);
+
+\path[fill=fillColor] (559.98,285.63) rectangle (573.65,291.42);
+
+\path[fill=fillColor] (651.12,285.63) rectangle (664.79,293.83);
+
+\path[fill=fillColor] (689.86,285.63) rectangle (710.36,285.71);
+
+\path[fill=fillColor] (423.27,285.63) rectangle (436.95,313.77);
+
+\path[fill=fillColor] (468.84,285.63) rectangle (482.52,311.68);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (503.83,294.39) rectangle (517.31,301.98);
-
-\path[fill=fillColor] (593.67,294.39) rectangle (607.15,298.26);
-
-\path[fill=fillColor] (548.75,294.39) rectangle (562.23,299.81);
-
-\path[fill=fillColor] (638.59,294.39) rectangle (652.07,297.10);
-
-\path[fill=fillColor] (413.99,294.39) rectangle (427.47,324.04);
-
-\path[fill=fillColor] (458.91,294.39) rectangle (472.39,322.65);
+\path[fill=fillColor] (500.74,285.63) rectangle (514.41,293.51);
+
+\path[fill=fillColor] (591.88,285.63) rectangle (605.55,289.65);
+
+\path[fill=fillColor] (546.31,285.63) rectangle (559.98,291.26);
+
+\path[fill=fillColor] (637.45,285.63) rectangle (651.12,288.45);
+
+\path[fill=fillColor] (409.60,285.63) rectangle (423.27,316.43);
+
+\path[fill=fillColor] (455.17,285.63) rectangle (468.84,314.98);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (490.36,294.39) rectangle (503.83,300.97);
-
-\path[fill=fillColor] (580.19,294.39) rectangle (593.67,300.20);
-
-\path[fill=fillColor] (535.27,294.39) rectangle (548.75,300.43);
-
-\path[fill=fillColor] (625.11,294.39) rectangle (638.59,319.16);
-
-\path[fill=fillColor] (670.03,294.39) rectangle (690.25,294.86);
-
-\path[fill=fillColor] (400.52,294.39) rectangle (413.99,313.36);
-
-\path[fill=fillColor] (445.44,294.39) rectangle (458.91,309.18);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,290.75) rectangle (717.20,370.88);
-\end{scope}
-\begin{scope}
-\path[clip] (393.78,205.12) rectangle (717.20,285.25);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (393.78,205.12) rectangle (717.20,285.25);
+\path[fill=fillColor] (487.07,285.63) rectangle (500.74,292.47);
+
+\path[fill=fillColor] (578.21,285.63) rectangle (591.88,291.66);
+
+\path[fill=fillColor] (532.64,285.63) rectangle (546.31,291.90);
+
+\path[fill=fillColor] (623.78,285.63) rectangle (637.45,311.36);
+
+\path[fill=fillColor] (669.35,285.63) rectangle (689.86,286.11);
+
+\path[fill=fillColor] (395.93,285.63) rectangle (409.60,305.33);
+
+\path[fill=fillColor] (441.50,285.63) rectangle (455.17,300.99);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.10,281.85) rectangle (717.20,365.08);
+\end{scope}
+\begin{scope}
+\path[clip] (389.10,193.12) rectangle (717.20,276.35);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (389.10,193.12) rectangle (717.20,276.35);
 \definecolor{drawColor}{gray}{0.92}
 
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,218.44) --
-	(717.20,218.44);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,237.79) --
-	(717.20,237.79);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,257.14) --
-	(717.20,257.14);
-
-\path[draw=drawColor,line width= 0.3pt,line join=round] (393.78,276.50) --
-	(717.20,276.50);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,208.76) --
-	(717.20,208.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,228.11) --
-	(717.20,228.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,247.47) --
-	(717.20,247.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (393.78,266.82) --
-	(717.20,266.82);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (420.73,205.12) --
-	(420.73,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (465.65,205.12) --
-	(465.65,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (510.57,205.12) --
-	(510.57,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (555.49,205.12) --
-	(555.49,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (600.41,205.12) --
-	(600.41,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (645.33,205.12) --
-	(645.33,285.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (690.25,205.12) --
-	(690.25,285.25);
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,206.95) --
+	(717.20,206.95);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,227.05) --
+	(717.20,227.05);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,247.16) --
+	(717.20,247.16);
+
+\path[draw=drawColor,line width= 0.3pt,line join=round] (389.10,267.26) --
+	(717.20,267.26);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,196.90) --
+	(717.20,196.90);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,217.00) --
+	(717.20,217.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,237.10) --
+	(717.20,237.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (389.10,257.21) --
+	(717.20,257.21);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (416.44,193.12) --
+	(416.44,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (462.01,193.12) --
+	(462.01,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (507.58,193.12) --
+	(507.58,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (553.15,193.12) --
+	(553.15,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (598.72,193.12) --
+	(598.72,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (644.29,193.12) --
+	(644.29,276.35);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (689.86,193.12) --
+	(689.86,276.35);
 \definecolor{fillColor}{RGB}{221,204,119}
 
-\path[fill=fillColor] (517.31,208.76) rectangle (530.78,230.51);
-
-\path[fill=fillColor] (607.15,208.76) rectangle (620.62,212.55);
-
-\path[fill=fillColor] (562.23,208.76) rectangle (575.70,210.46);
-
-\path[fill=fillColor] (652.07,208.76) rectangle (665.54,221.61);
-
-\path[fill=fillColor] (427.47,208.76) rectangle (440.94,236.63);
-
-\path[fill=fillColor] (472.39,208.76) rectangle (485.86,218.28);
+\path[fill=fillColor] (514.41,196.90) rectangle (528.09,219.50);
+
+\path[fill=fillColor] (605.55,196.90) rectangle (619.22,200.84);
+
+\path[fill=fillColor] (559.98,196.90) rectangle (573.65,198.67);
+
+\path[fill=fillColor] (651.12,196.90) rectangle (664.79,210.25);
+
+\path[fill=fillColor] (423.27,196.90) rectangle (436.95,225.85);
+
+\path[fill=fillColor] (468.84,196.90) rectangle (482.52,206.79);
 \definecolor{fillColor}{RGB}{17,119,51}
 
-\path[fill=fillColor] (503.83,208.76) rectangle (517.31,221.53);
-
-\path[fill=fillColor] (593.67,208.76) rectangle (607.15,211.93);
-
-\path[fill=fillColor] (548.75,208.76) rectangle (562.23,210.31);
-
-\path[fill=fillColor] (638.59,208.76) rectangle (652.07,213.25);
-
-\path[fill=fillColor] (413.99,208.76) rectangle (427.47,245.22);
-
-\path[fill=fillColor] (458.91,208.76) rectangle (472.39,227.65);
+\path[fill=fillColor] (500.74,196.90) rectangle (514.41,210.17);
+
+\path[fill=fillColor] (591.88,196.90) rectangle (605.55,200.20);
+
+\path[fill=fillColor] (546.31,196.90) rectangle (559.98,198.51);
+
+\path[fill=fillColor] (637.45,196.90) rectangle (651.12,201.56);
+
+\path[fill=fillColor] (409.60,196.90) rectangle (423.27,234.77);
+
+\path[fill=fillColor] (455.17,196.90) rectangle (468.84,216.52);
 \definecolor{fillColor}{RGB}{204,102,119}
 
-\path[fill=fillColor] (490.36,208.76) rectangle (503.83,234.38);
-
-\path[fill=fillColor] (580.19,208.76) rectangle (593.67,212.86);
-
-\path[fill=fillColor] (535.27,208.76) rectangle (548.75,210.46);
-
-\path[fill=fillColor] (625.11,208.76) rectangle (638.59,225.25);
-
-\path[fill=fillColor] (400.52,208.76) rectangle (413.99,232.84);
-
-\path[fill=fillColor] (445.44,208.76) rectangle (458.91,214.10);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (393.78,205.12) rectangle (717.20,285.25);
-\end{scope}
-\begin{scope}
-\path[clip] (377.21,547.64) rectangle (393.78,627.77);
+\path[fill=fillColor] (487.07,196.90) rectangle (500.74,223.52);
+
+\path[fill=fillColor] (578.21,196.90) rectangle (591.88,201.16);
+
+\path[fill=fillColor] (532.64,196.90) rectangle (546.31,198.67);
+
+\path[fill=fillColor] (623.78,196.90) rectangle (637.45,214.03);
+
+\path[fill=fillColor] (395.93,196.90) rectangle (409.60,221.91);
+
+\path[fill=fillColor] (441.50,196.90) rectangle (455.17,202.45);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (389.10,193.12) rectangle (717.20,276.35);
+\end{scope}
+\begin{scope}
+\path[clip] (374.86,548.04) rectangle (389.10,631.27);
 \definecolor{drawColor}{gray}{0.20}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,548.25) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,567.61) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,586.96) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,606.31) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,551.28) --
-	( 31.71,551.28);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,570.64) --
-	( 31.71,570.64);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,589.99) --
-	( 31.71,589.99);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,609.34) --
-	( 31.71,609.34);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,549.70) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,569.80) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,589.91) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,610.01) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,551.82) --
+	( 27.01,551.82);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,571.92) --
+	( 27.01,571.92);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,592.03) --
+	( 27.01,592.03);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,612.13) --
+	( 27.01,612.13);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,462.62) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,481.98) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,501.33) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,520.68) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,465.65) --
-	( 31.71,465.65);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,485.01) --
-	( 31.71,485.01);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,504.36) --
-	( 31.71,504.36);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,523.71) --
-	( 31.71,523.71);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,460.97) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,481.07) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,501.17) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,521.28) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,463.09) --
+	( 27.01,463.09);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,483.19) --
+	( 27.01,483.19);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,503.30) --
+	( 27.01,503.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,523.40) --
+	( 27.01,523.40);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,376.99) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,396.35) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,415.70) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,435.05) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,380.02) --
-	( 31.71,380.02);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,399.38) --
-	( 31.71,399.38);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,418.73) --
-	( 31.71,418.73);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,438.08) --
-	( 31.71,438.08);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,372.24) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,392.34) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,412.44) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,432.55) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,374.36) --
+	( 27.01,374.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,394.46) --
+	( 27.01,394.46);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,414.57) --
+	( 27.01,414.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,434.67) --
+	( 27.01,434.67);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,291.36) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,310.71) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,330.07) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,349.42) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,294.39) --
-	( 31.71,294.39);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,313.74) --
-	( 31.71,313.74);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,333.10) --
-	( 31.71,333.10);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,352.45) --
-	( 31.71,352.45);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,283.51) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,303.61) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,323.71) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,343.82) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,285.63) --
+	( 27.01,285.63);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,305.73) --
+	( 27.01,305.73);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,325.84) --
+	( 27.01,325.84);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,345.94) --
+	( 27.01,345.94);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,205.73) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,225.08) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,244.44) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,263.79) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,208.76) --
-	( 31.71,208.76);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,228.11) --
-	( 31.71,228.11);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,247.47) --
-	( 31.71,247.47);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,266.82) --
-	( 31.71,266.82);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,194.78) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,214.88) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,234.98) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,255.09) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,196.90) --
+	( 27.01,196.90);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,217.00) --
+	( 27.01,217.00);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,237.10) --
+	( 27.01,237.10);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,257.21) --
+	( 27.01,257.21);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,120.10) {0};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,139.45) {25};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,158.81) {50};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 17.96,178.16) {75};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,123.13) --
-	( 31.71,123.13);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,142.48) --
-	( 31.71,142.48);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,161.84) --
-	( 31.71,161.84);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.96,181.19) --
-	( 31.71,181.19);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,106.05) {0};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,126.15) {25};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,146.25) {50};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at ( 15.05,166.35) {75};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,108.17) --
+	( 27.01,108.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,128.27) --
+	( 27.01,128.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,148.37) --
+	( 27.01,148.37);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 24.26,168.48) --
+	( 27.01,168.48);
 \end{scope}
@@
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,373.63) {estimate};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (276.12,  5.50) rectangle (489.36, 30.95);
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 10.80,367.83) {estimate};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (285.48,  5.50) rectangle (472.97, 30.95);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (281.62, 14.44) {Answer};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (322.65, 11.00) rectangle (337.10, 25.45);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at (290.98, 15.58) {Answer};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (324.70, 11.00) rectangle (339.15, 25.45);
 \end{scope}
@@
 
-\path[fill=fillColor] (323.36, 11.71) rectangle (336.39, 24.74);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (409.32, 11.00) rectangle (423.78, 25.45);
+\path[fill=fillColor] (325.41, 11.71) rectangle (338.44, 24.74);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (398.94, 11.00) rectangle (413.39, 25.45);
 \end{scope}
@@
 
-\path[fill=fillColor] (410.03, 11.71) rectangle (423.07, 24.74);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (448.02, 11.00) rectangle (462.48, 25.45);
+\path[fill=fillColor] (399.65, 11.71) rectangle (412.68, 24.74);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (722.70,650.43);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (434.93, 11.00) rectangle (449.39, 25.45);
 \end{scope}
@@
 
-\path[fill=fillColor] (448.73, 11.71) rectangle (461.77, 24.74);
+\path[fill=fillColor] (435.65, 11.71) rectangle (448.68, 24.74);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (342.60, 15.20) {No, Don't know};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (344.65, 16.11) {No, Don't know};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (429.28, 15.20) {Yes};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (418.89, 16.11) {Yes};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (467.98, 15.20) {Any};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.88] at (454.89, 16.11) {Any};
 \end{scope}

### 2021-07-01 2_tables.Rmd
check and comment

@@
     toc: yes
+    toc_float: yes
+    self_contained: yes
   bookdown::html_document2: default
+keywords: vaccine hesitancy
 ---
@@
 
+This replication file and ancillary data and code are hosted at https://github.com/wzb-ipi/covid_vaccines_nmed
+
 # Set up
@@
 This code takes cleaned and aggregated data as input. Cleaning and aggregation is done in `1_cleaning.Rmd`.
+
+Aggregated data can be downloaded directly from: https://wzb-ipi.github.io/covid_vaccines_nmed/combined.csv
 
@@
            loo_fun = 
-             function(dat) lm_helper(data = dat, 
-                                     formula = take_vaccine_num ~ 1, cluster = cluster,
-                                     weight = weight, se_type = "stata")
+             function(dat) 
+               lm_helper(data = dat, 
+                         formula = take_vaccine_num ~ 1, 
+                         cluster = cluster,
+                         weight = weight, 
+                         se_type = "stata")
   ) {
@@
 
+  # Data is recombined and loo_fun applied to each combination 
   data %>% 
@@
 }
+
+# Illustration of loo_helper
+# loo_helper(
+#   data = data.frame(country = 1:3, Y = 1:3),
+#   loo_n = 2,
+#   sample_var = "country",
+#   loo_fun = function(dat) mean(dat$Y) 
+# )
 
@@
 
-## Final cleaning and harmonization of weights
-
-Groups variables into discrete categories and prepares survey weights.
+## Data preparation
+
+Load data:
 
@@
 
+```
+
+Groups variables into discrete categories and prepares survey weights.
+
+```{r}
 # If no cluster information given for a study then individuals are clusters 
@@
 
-```{r, fig.height = 13, fig.width = 6}
+```{r, fig.height = 13, fig.width = 15}
 df %>% 
@@
 # Tables and Figures
+
+The following code produces all figures and tables from the paper as well as cited statistics and supplementary material.
 
@@
 
+# Loo estimates for all LMIC respondents
 loo_estimates <- 
@@
     })
+
+# Loo estimates broken down by category (appended to above)
 
@@
 
+# Clean up labels
 loo_estimates %<>% 
@@
 # Analysis of differences in means only LMICs
-# Notice that Uganda 1 is dropped, because of it does not have reference categories for gender or age
+# Notice that Uganda 1 is dropped, because it does not have reference categories for gender or age
 # Notice that we are using df (and not df2) as data, since it does not include "All"
@@
 
-## Reasons to take or not to take
-
-### Table: Reasons to take the vaccine.
+## Reasons
+
+### Table: Reasons to take
 
@@
 ```
-## Reasons to take by age
+
+### Reasons to take (by age)
+
 ```{r, fig.width = 10, fig.height = 7}
@@
 
-## Figure 2: reasons not to take
-
-### Figure
+### Figure 2: reasons not to take
 
@@
 
-## Figure 3: Trust vaccines
-
-### Figure
+## Trust
+
+### Main figure (Fig 3)
 
@@
 
-## Figure broken down by acceptance
+### ...by acceptance
 
@@
 
-### By gender
+### ...by gender
 
@@
 
-### Table version
+### Trusted Sources Table
 

### 2021-07-02 2_tables.Rmd
cleaning of code

@@
 ```{r setup3, include=FALSE}
+
 knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
@@
 
-lm_helper <- function(data,...) {
+lm_helper <- function(data,
+                      ...) {
   data %>% 
@@
 
-loo_helper <- 
-  function(data, 
+loo_helper <- function(data, 
                        sample_var, 
@@
                                      weight = weight, 
-                         se_type = "stata")
-  ) {
+                                     se_type = "stata")) {
 
@@
 
-# Illustration of loo_helper
+# # Illustration of loo_helper
 # loo_helper(
@@
 
-grp_analysis <- function(df, y, x)
-
+grp_analysis <- function(df, 
+                         y, 
+                         x) {
   df %>%
@@
     dplyr::rename(!!x := "get(x)")
+}
 
@@
 
-reasons_together <- function(df, reason, num = "Yes")
-
+reasons_together <- function(df, 
+                             reason, 
+                             num = "Yes") {
   df %>%
@@
                 weight = weight, se_type = "stata"), .groups = "drop")
-
-reasons_together_subgroup <- function(df, reason, num = "Yes", 
-                                      dem_group = NA, dem_subgroup = NA){
+}
+
+reasons_together_subgroup <- function(df, 
+                                      reason, num = "Yes", 
+                                      dem_group = NA, 
+                                      dem_subgroup = NA) {
 
@@
 
-age_analysis <- function(df, reason, num = "Yes", filter_by=NA){
+age_analysis <- function(df, 
+                         reason, 
+                         num = "Yes", 
+                         filter_by = NA) {
   df %>%
-    dplyr::filter({{filter_by}}==1)  %>%
+    dplyr::filter({{filter_by}} == 1)  %>%
     dplyr::filter(take_vaccine %in% num, 
@@
          weight_replace = mean(weight, rm.na = TRUE),
-         weight = if_else(is.na(weight), if_else(is.na(weight_replace), 1, weight_replace), weight),
+         weight = if_else(is.na(weight), 
+                          if_else(is.na(weight_replace), 1, weight_replace), 
+                          weight),
          weight = weight/sum(weight)) %>% 
@@
   dplyr::mutate(
-    age_groups = as.character(cut(x = age, breaks = c(-Inf, 18, 30, 45, 60, +Inf), right = F)),
+    age_groups = 
+      as.character(cut(x = age, breaks = c(-Inf, 18, 30, 45, 60, +Inf), right = F)),
     age_groups_binary = ifelse(age >= 55, "55+", NA),
@@
             gender_na = mean(!is.na(gender))*100,
-            educ_na= mean(!is.na(educ))*100,
-            age_na= mean(!is.na(age))*100) %>%
+            educ_na = mean(!is.na(educ))*100,
+            age_na = mean(!is.na(age))*100) %>%
   kable(digits = 2, 
-        col.names= c("Country", "N obs", "Take vaccine", "Gender", "Education", "Age"),
+        col.names = c("Country", "N obs", "Take vaccine", "Gender", "Education", "Age"),
         caption = "Observations and missingness patterns", 
@@
   summarize(n = n(),
-            take_vaccine_na = mean(!is.na(take_vaccine)) *100,
-            gender_na = mean(is.na(gender))*100,
-            educ_na= mean(is.na(educ))*100,
-            age_na= mean(is.na(age))*100) %>%
+            take_vaccine_na = mean(!is.na(take_vaccine)) * 100,
+            gender_na = mean(is.na(gender)) * 100,
+            educ_na = mean(is.na(educ)) * 100,
+            age_na = mean(is.na(age)) * 100) %>%
   kable(digits = 2, 
-        col.names= c("Country", "N obs", "Take vaccine", "Gender", "Education", "Age"),
+        col.names = c("Country", "N obs", "Take vaccine", "Gender", "Education", "Age"),
         caption = "Observations and missingness patterns.", 
@@
   readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
-  dplyr::select("Study" = "country", "Date"="date",
+  dplyr::select("Study" = "country", "Date" = "date",
                 "Geographic scope", "Sampling methodology", "Survey modality", "Weights") %>%
@@
 readxl::read_excel("2_input_data/studies_info.xlsx", sheet = "sample") %>%
-  dplyr::select("Study" = "country", "Date"="date",
+  dplyr::select("Study" = "country", "Date" = "date",
                 "Geographic scope", "Sampling methodology", "Survey modality", "Weights") %>%
@@
 # Age (all original categories and binary recoding)
-acc_by_age <- grp_analysis(df2, y = "take_vaccine_num", x = "age_groups_three") %>%
-  dplyr::filter(statistic!=Inf) %>%
-  dplyr::filter(conf.low>0)
+acc_by_age <- 
+  grp_analysis(df2, y = "take_vaccine_num", x = "age_groups_three") %>%
+  dplyr::filter(statistic != Inf) %>%
+  dplyr::filter(conf.low > 0)
+
 acc_by_age_binary <- grp_analysis(df2, y = "take_vaccine_num", x = "age_groups_binary")
@@
 
-nationals <- df2 %>%
-  filter(country=="Burkina Faso" |
-           country=="Colombia" |
-           country=="Rwanda" |
-           country=="Sierra Leone 1" |
-           country=="Sierra Leone 2")
+nationals <- 
+  df2 %>%
+  dplyr::filter(country == "Burkina Faso" |
+           country == "Colombia" |
+           country == "Rwanda" |
+           country == "Sierra Leone 1" |
+           country == "Sierra Leone 2")
 
@@
 # Age (all original categories and binary recoding)
-acc_by_age_n <- grp_analysis(nationals, y = "take_vaccine_num", x = "age_groups_three") %>%
-  dplyr::filter(statistic!=Inf) %>%
-  dplyr::filter(conf.low>0)
+acc_by_age_n <- 
+  grp_analysis(nationals, y = "take_vaccine_num", x = "age_groups_three") %>%
+  dplyr::filter(statistic != Inf) %>%
+  dplyr::filter(conf.low > 0)
 
@@
   dplyr::mutate(across(c(conf.low, conf.high, estimate), ~ round(. * 100, digits = 1))) %>%
-  filter(group=="All") %>%
-  mutate(group="All LMICs (National samples)",
-         tag="All LMICs (National samples)")
+  filter(group == "All") %>%
+  mutate(group = "All LMICs (National samples)",
+         tag = "All LMICs (National samples)")
 
@@
 
-ans_national <- ans_n %>% filter(group == "All LMICs (National samples)" & cat=="All")
+ans_national <- 
+  ans_n %>% 
+  dplyr::filter(group == "All LMICs (National samples)" & cat == "All")
 
@@
   scale_x_continuous(n.breaks = 8, name = "estimate") +
-  scale_y_continuous(labels = scales::percent_format(scale = 1, suffix = "", accuracy = 0.1)) +
+  scale_y_continuous(
+    labels = scales::percent_format(scale = 1, suffix = "", accuracy = 0.1)) +
   labs(title = "",
@@
 fig_hist_loo
+
 ```
@@
   dplyr::left_join(age_table_n) %>%
-  dplyr::filter(group=="All") %>%
-  dplyr::mutate(group="All LMICs (National)")
+  dplyr::filter(group == "All") %>%
+  dplyr::mutate(group = "All LMICs (National)")
 
@@
   dplyr::select(group, estimate, conf_int, outcome, n) %>%
-  tidyr::pivot_wider(names_from = outcome, values_from = c(estimate, conf_int, n), names_sep = "__") %>%
+  tidyr::pivot_wider(names_from = outcome, 
+                     values_from = c(estimate, conf_int, n), 
+                     names_sep = "__") %>%
   tidyr::pivot_longer(cols = c(starts_with("estimate__"), starts_with("conf_int__")),
@@
   yes_vacc2 %>%
-  knitr::kable(col.names = cnames,
+  knitr::kable(
+    col.names = cnames,
     caption = "Reasons to take the vaccine", format = "latex", booktabs = T, 
@@
 yes_vacc2 %>%
-  knitr::kable(col.names = cnames,
+  knitr::kable(
+    col.names = cnames,
     caption = "\\label{yes}Reasons to take the vaccine", 
     booktabs = T, linesep = "", 
-      format.args = list(big.mark = ",", scientific = FALSE)) %>% 
+    format.args = list(big.mark = ",", scientific = FALSE),
+    align = "lcccc") %>% 
   kableExtra::kable_styling(full_width = FALSE) %>%
@@
 yes_vacc_age_1 <- 
-  lapply(yes_vars, age_analysis, df = df2, num = "Yes", filter_by=`age_less24`) %>%
+  lapply(yes_vars, age_analysis, df = df2, num = "Yes", filter_by = `age_less24`) %>%
   dplyr::bind_rows() %>%
-  mutate(age="<25")
+  mutate(age = "<25")
 
 yes_vacc_age_2 <- 
-  lapply(yes_vars, age_analysis, df = df2, num = "Yes", filter_by=`age_25_54`) %>%
+  lapply(yes_vars, age_analysis, df = df2, num = "Yes", filter_by = `age_25_54`) %>%
   dplyr::bind_rows() %>%
-  mutate(age="25-54")
+  mutate(age = "25-54")
 
 yes_vacc_age_3 <- 
-  lapply(yes_vars, age_analysis, df = df2, num = "Yes", filter_by=`age_55_more`) %>%
+  lapply(yes_vars, age_analysis, df = df2, num = "Yes", filter_by = `age_55_more`) %>%
   dplyr::bind_rows() %>%
-  mutate(age="55+")
+  mutate(age = "55+")
 
@@
                                   ", ", conf.high, ")"),
-                n=as.character(n)) %>%
+                n = as.character(n)) %>%
   dplyr::select(group, estimate, conf_int, outcome, age, n) %>%
@@
   dplyr::filter(grepl("yes_vaccine_1", type)) %>%
-  mutate(type=ifelse(grepl("estimate", type), "estimate", type),
-         type=ifelse(grepl("conf_int", type), "conf_int", type),
-         type=ifelse(grepl("n__", type), "n", type))
+  dplyr::mutate(type = ifelse(grepl("estimate", type), "estimate", type),
+         type = ifelse(grepl("conf_int", type), "conf_int", type),
+         type = ifelse(grepl("n__", type), "n", type))
 
 y2 <- yes_vacc_age %>%
-  dplyr::filter(grepl("yes_vaccine_2", type))%>%
-  mutate(type=ifelse(grepl("estimate", type), "estimate", type),
-         type=ifelse(grepl("conf_int", type), "conf_int", type),
-         type=ifelse(grepl("n__", type), "n", type))
+  dplyr::filter(grepl("yes_vaccine_2", type)) %>%
+  dplyr::mutate(type = ifelse(grepl("estimate", type), "estimate", type),
+         type = ifelse(grepl("conf_int", type), "conf_int", type),
+         type = ifelse(grepl("n__", type), "n", type))
 
 y3 <- yes_vacc_age %>%
-  dplyr::filter(grepl("yes_vaccine_3", type))%>%
-  mutate(type=ifelse(grepl("estimate", type), "estimate", type),
-         type=ifelse(grepl("conf_int", type), "conf_int", type),
-         type=ifelse(grepl("n__", type), "n", type))
-
-yes_vacc_age <- left_join(y1, y2, by=c("group", "type")) %>%
-  left_join(y3, by=c("group", "type")) %>% 
+  dplyr::filter(grepl("yes_vaccine_3", type)) %>%
+  dplyr::mutate(type = ifelse(grepl("estimate", type), "estimate", type),
+         type = ifelse(grepl("conf_int", type), "conf_int", type),
+         type = ifelse(grepl("n__", type), "n", type))
+
+yes_vacc_age <- 
+  dplyr::left_join(y1, y2, by = c("group", "type")) %>%
+  dplyr::left_join(y3, by = c("group", "type")) %>% 
   dplyr::mutate(
@@
   dplyr::arrange(group) %>% 
-  dplyr::mutate(across(c(group), ~ifelse(type == "conf_int", "Conf. interval", as.character(.))),
+  dplyr::mutate(
+    across(c(group), 
+           ~ifelse(type == "conf_int", "Conf. interval", as.character(.))),
     across(c(group), ~ifelse(type == "n", "n", as.character(.))),
@@
   yes_vacc_age %>%
-  knitr::kable(col.names = cnames,
-      caption = "Reasons to take the vaccine- by age groups", format = "latex", booktabs = T, 
+  knitr::kable(
+    col.names = cnames,
+    caption = "Reasons to take the vaccine- by age groups", 
+    format = "latex", booktabs = T, 
     linesep = "", label = "yes1", 
@@
                             font_size = base_font_size - 2, full_width = FALSE) %>%
-  kableExtra::add_header_above(c(" " = 1, "Self" = 3, "Family" = 3, "Community" = 3), bold = TRUE) %>% 
+  kableExtra::add_header_above(c(" " = 1, "Self" = 3, "Family" = 3, "Community" = 3), 
+                               bold = TRUE) %>% 
   kableExtra::row_spec(0, bold = TRUE) %>% 
@@
 yes_vacc_age %>%
-  knitr::kable(col.names = cnames,
+  knitr::kable(
+    col.names = cnames,
     caption = "\\label{yes1}Reasons to take the vaccine", 
     booktabs = T, linesep = "", 
-      format.args = list(big.mark = ",", scientific = FALSE)) %>% 
+    format.args = list(big.mark = ",", scientific = FALSE),
+    align = c("l", rep("c", 9))) %>% 
   kableExtra::kable_styling(full_width = FALSE) %>%
-  kableExtra::add_header_above(c(" " = 1, "Self" = 3, "Family" = 3, "Community" = 3), bold = TRUE) %>% 
+  kableExtra::add_header_above(c(" " = 1, "Self" = 3, "Family" = 3, "Community" = 3), 
+                               bold = TRUE) %>% 
   kableExtra::row_spec(0, bold = TRUE) %>% 
@@
   dplyr::mutate(
-    name=ifelse(group!="All", paste0(group, " (n=", n, ")"), "All"),
-    name= gsub(pattern = " \\(", "\\\n\\(", name),
+    name = ifelse(group != "All", paste0(group, " (n=", n, ")"), "All"),
+    name = gsub(pattern = " \\(", "\\\n\\(", name),
     tag = as.factor(tag),
-    tag = 
-      forcats::fct_relevel(tag,  
+    tag = forcats::fct_relevel(
+      tag,  
       "Concerned about side effects", 
@@
 fig_2
+
 ```
@@
     booktabs = T, linesep = "", 
-    format.args = list(big.mark = ",",scientific = FALSE)) %>%
+    format.args = list(big.mark = ",",scientific = FALSE),
+    align = c("l", rep("c", 11))) %>%
   kableExtra::kable_styling(full_width = F) %>%
@@
     threeparttable = T)
+
 ```
@@
     trust_recode_1 = ifelse(trust_vaccine_1 == 1 | trust_vaccine_2 == 1, 1, 0),
-    trust_recode_1 = ifelse((country=="Nigeria"| country=="USA") & is.na(trust_recode_1), 0, trust_recode_1),
-
+    trust_recode_1 = ifelse((country == "Nigeria" | country == "USA") &
+                              is.na(trust_recode_1), 0, trust_recode_1),
     trust_recode_2 = ifelse(trust_vaccine_8 == 1 | trust_vaccine_9 == 1, 1, 0),
-    trust_recode_2 = ifelse((country=="Sierra Leone 2") & is.na(trust_recode_2), 0, trust_recode_2),
-
+    trust_recode_2 = ifelse((country == "Sierra Leone 2") & 
+                              is.na(trust_recode_2), 0, trust_recode_2),
     trust_recode_3 = ifelse(trust_vaccine_3 == 1 | 
@@
                               trust_vaccine_4 == 1, 1, 0),
-    trust_recode_3 = ifelse((country=="Nigeria"| country=="USA" | country=="Russia") & is.na(trust_recode_3), 0, trust_recode_3),
-
+    trust_recode_3 = 
+      ifelse((country == "Nigeria" | country == "USA" | country == "Russia") & 
+               is.na(trust_recode_3), 0, trust_recode_3),
     trust_recode_4 = ifelse(trust_vaccine_666 == 1 | trust_vaccine_other == 1, 1, 0),
-    trust_recode_4 = ifelse((country=="Burkina Faso"| country=="Sierra Leone 2" | country=="Russia") & is.na(trust_recode_4), 0, trust_recode_4),
-
+    trust_recode_4 = 
+      ifelse((country == "Burkina Faso" | 
+                country == "Sierra Leone 2" | 
+                country == "Russia") & 
+               is.na(trust_recode_4), 0, trust_recode_4),
     trust_recode_5 = ifelse(trust_vaccine_dk == 1 | 
@@
                               trust_vaccine_nr == 1, 1, 0),
-    trust_recode_5 = ifelse((country=="Nigeria"| country=="Sierra Leone 2" | country=="USA") & is.na(trust_recode_5), 0, trust_recode_5))
+    trust_recode_5 = 
+      ifelse((country == "Nigeria" | country == "Sierra Leone 2" | country == "USA") &
+               is.na(trust_recode_5), 0, trust_recode_5))
 
@@
   dplyr::mutate(group = plyr::mapvalues(group, "All", "All LMICs")) %>% 
-  dplyr::filter(sub=="Any") %>% 
+  dplyr::filter(sub == "Any") %>% 
   ggplot(aes(estimate, tag)) + 
-  geom_bar(stat = "identity", position = "dodge", fill="#DDCC77") + 
+  geom_bar(stat = "identity", position = "dodge", fill = "#DDCC77") + 
   facet_wrap(~group, ncol = 2, strip.position = "left")  +
@@
 fig_hist2
+
 ```
@@
 
-trust <- filter(trust_vacc_together, sub=="Any")
+trust <- filter(trust_vacc_together, sub == "Any")
 
@@
   trust %>% 
-  dplyr::filter(group == "All" & tag=="Health workers") %>%
+  dplyr::filter(group == "All" & tag == "Health workers") %>%
   dplyr::arrange(desc(estimate))
@@
   trust %>% 
-  dplyr::filter(group != "All" & group != "USA" & group != "Russia" & tag == "Health workers")
+  dplyr::filter(group != "All" & group != "USA" & 
+                  group != "Russia" & tag == "Health workers")
 
@@
   trust %>% 
-  dplyr::filter(group == "Nepal" & tag=="Famous person, religious leader or traditional healers") %>%
+  dplyr::filter(
+    group == "Nepal" & 
+      tag == "Famous person, religious leader or traditional healers") %>%
   dplyr::arrange(desc(estimate))
@@
   trust %>% 
-  dplyr::filter(group != "All" & group!="Rwanda" & tag == "Government or MoH") %>%
+  dplyr::filter(group != "All" & group != "Rwanda" & tag == "Government or MoH") %>%
   dplyr::arrange(desc(estimate))
@@
 fig_hist_categories
+
 ```
@@
     df2 %>% 
-      dplyr::filter(group != "All" & group != "USA" & group != "Russia" & group != "Uganda 1") %>% 
+      dplyr::filter(group != "All" & group != "USA" & 
+                      group != "Russia" & group != "Uganda 1") %>% 
       estimatr::lm_robust(as.formula(paste(i, "~gender")),
@@
       tidy %>% 
-      dplyr::select(estimate, std.error, p.value, df, term)%>%
+      dplyr::select(estimate, std.error, p.value, df, term) %>%
       dplyr::mutate(outcome = paste(i))
@@
         dplyr::select(group, n, type, "Take vaccine?", starts_with("trust_")) %>%
-        dplyr::filter(!(group %in% c("Mozambique", "Pakistan 1", "Pakistan 2", "Uganda 1", "India")))
-    }
-  ) %>% 
+        dplyr::filter(!(group %in% c("Mozambique", "Pakistan 1", 
+                                     "Pakistan 2", "Uganda 1", "India")))
+    }) %>% 
   dplyr::mutate(
@@
     caption = "COVID-19 Vaccination Decision-making: most trusted source", 
-    format.args = list(big.mark = ",", scientific = FALSE)) %>% 
+    format.args = list(big.mark = ",", scientific = FALSE),
+    align = c("l", rep("c", 9))) %>% 
   kableExtra::kable_styling(full_width = FALSE) %>%

### 2021-07-11 2_tables.Rmd
add updated loo_main.jpeg without latex code

@@
       labels = rev(c("Female", "Male", "Up to Secondary", 
-                     "More than Secondary", "$< 25$", "$25-54$", "$55 +$", "All")))
+                     "More than Secondary", "<25 yr", "25-54 yr", "55+ yr", "All")))
   ) %>% 
@@
 safe_colorblind_palette <- c("#CC6677", "#DDCC77", "#117733", "#332288", "#AA4499", 
-                             "#44AA99", "#999933", "#882255", "#661100", "#6699CC", "#888888", 
-                             "#88CCEE")
+                             "#44AA99", "#999933", "#882255", "#661100", "#6699CC",
+                             "#888888", "#88CCEE")
 
@@
   dplyr::filter(group %in% c("All", "USA", "Russia")) %>% 
-  dplyr::mutate(group = plyr::mapvalues(group, from = "All", to = "All LMIC"),
+  dplyr::mutate(
+    group = plyr::mapvalues(group, from = "All", to = "All LMIC"),
+    cat = plyr::mapvalues(cat, from = c("$< 25$", "$25-54$", "$55 +$"),
+                          to = c("<25 yr", "25-54 yr", "55+ yr")),
     tag = cat)

### 2021-07-17 2_tables.Rmd
clean up
1_cleaning.Rmd preserved but not called
3_main_text.Rmd called rather than call to googledrive
removal of legacy files

@@
 title: 'COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries: Replication Code'
-date: "`r format(Sys.time(), '%d %B, %Y')`"
+date: "1 July 2021"
 output:

### 2021-07-17 3_main_text.Rmd
clean up
1_cleaning.Rmd preserved but not called
3_main_text.Rmd called rather than call to googledrive
removal of legacy files

--- 2021-06-22 4_paper_supplementary_files/temp_download.Rmd
@@
-<!-- KEEP ALL REVISIONS IN SUGGESTING MODE FOR VERSION CONTROL - DO NOT ACCEPT CHANGES -->
 <!-- COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging -->

### 2021-07-17 paper.Rmd
clean up
1_cleaning.Rmd preserved but not called
3_main_text.Rmd called rather than call to googledrive
removal of legacy files

@@
     pandoc_args:
-      - --template=4_paper_supplementary_files/mytemplate.latex
+      - --template=4_files/mytemplate.latex
     toc: false
@@
   bookdown::word_document2: default
-bibliography: 4_paper_supplementary_files/bib_final.bib
-csl: 4_paper_supplementary_files/nature.csl
+bibliography: 4_files/bib_final.bib
+csl: 4_files/nature.csl
 header-includes:
@@
 
-```
-
-```{r load_gdoc, include = FALSE, eval = TRUE}
-
-googledrive::drive_download(file = "NatureMedicine Covid vaccine hesitancy FINAL", 
-                            path = "4_paper_supplementary_files/Intro Vaccine.txt", overwrite = TRUE)
-
-file.rename(from = "4_paper_supplementary_files/Intro Vaccine.txt", 
-            to = "4_paper_supplementary_files/temp_download.Rmd")
-
 knitr::opts_chunk$set(echo = FALSE)
@@
 
-```{r main_text, child = "4_paper_supplementary_files/temp_download.Rmd"}
+```{r main_text, child = "3_main_text.Rmd"}
 
